### 2021-02-09 SupplementaryMaterial/Acknowledgments.tex
update

% Place acknowledgments below.
%First of all, I would like to thank my advisor Prof. Dinghao Wu for the continuous support of my Ph.D. study. I had a very hard time during the pandemic. Without his encouragement and support, I could not have finished the program. I also thank Dinghao for inviting me to Switzerland during his sabbatical leave. A large portion of the research presented in the dissertation was finished when I worked in Switzerland. The knowledge and skills I learned from him will also help me make progress in my future career.

%Beside my advisor, I would like to thank my committee members, Prof. Peng Liu, Prof. Sencun Zhu, Prof. Benjamin Hanrahan, and Prof. James R. Larus for their time, reviewing my dissertation.

%I would also like to thank Dr. Kang Li, Mr. Zhaofeng Chen, Dr. Mingshen Sun, Dr. Greg Zaverucha and Dr. Brian LaMacchia for their help during my internship at Baidu X-Lab and Microsoft Research Lab.  I also thank my friends and collaborators at Penn State University and EPFL.

%This research was supported in part by by the National Science Foundation (NSF) under grant CNS-1652790, and the Office of Naval Research (ONR) under grants N00014-16-1-2912, N00014-16-1-2265, and N00014-17-1-2894.

%Any opinions, conclusions in the paper do not reflect the views of funding agencies.

\bibliographystyle{IEEEtran}
\bibliography{refs}

%\newpage
%\clearpage
%\appendices
%\setcounter{section}{0}
%\section*{Supplementary Materials to Submission \#63}
%\setcounter{section}{1}
%\setcounter{page}{1}
%\input{sections/appendix}

\end{document}

### 2021-02-09 SupplementaryMaterial/Acknowledgments.tex
update

@@
 % Place acknowledgments below.
-%First of all, I would like to thank my advisor Prof.
+First of all, I would like to thank my advisor Prof.
 Dinghao Wu for the continuous support of my Ph.D.
@@
 
-%Beside my advisor, I would like to thank my committee members, Prof. Peng Liu, Prof. Sencun Zhu, Prof. Benjamin Hanrahan, and Prof. James R. Larus for their time, reviewing my dissertation.
+Beside my advisor, I would like to thank my committee members, Prof. Peng Liu, Prof. Sencun Zhu, Prof. Benjamin Hanrahan, and Prof. James R. Larus for their time, reviewing my dissertation.
 
-%I would also like to thank Dr.
+I would also like to thank Dr.
 Kang Li, Mr.
@@
 
-%This research was supported in part by by the National Science Foundation (NSF) under grant CNS-1652790, and the Office of Naval Research (ONR) under grants N00014-16-1-2912, N00014-16-1-2265, and N00014-17-1-2894.
-
-%Any opinions, conclusions in the paper do not reflect the views of funding agencies.
-
-\bibliographystyle{IEEEtran}
-\bibliography{refs}
-
-%\newpage
-%\clearpage
-%\appendices
-%\setcounter{section}{0}
-%\section*{Supplementary Materials to Submission \#63}
-%\setcounter{section}{1}
-%\setcounter{page}{1}
-%\input{sections/appendix}
-
-\end{document}
+This research was supported in part by by the National Science Foundation (NSF) under grant CNS-1652790, and the Office of Naval Research (ONR) under grants N00014-16-1-2912, N00014-16-1-2265, and N00014-17-1-2894.
+Any opinions, conclusions in the paper do not reflect the views of funding agencies.

### 2021-02-09 SupplementaryMaterial/Abstract.tex
update

% Place abstract below.

\vspace{-0.3in}
Side-channel

### 2021-02-09 SupplementaryMaterial/Abstract.tex
update

@@
 \vspace{-0.3in}
-Side-channel
+Side-channel attacks can leak secret information unconsciously from non-functional characteristics, e.g., time, power, and memory usage.
+Similar to many other vulnerabilities in software, attackers exploit the flaws in designs of hardware and implementations of software.
+Contrary to the the hardware countermeasures, which usually need changes to the complex underlying hardware, software solutions are more easier to adopt in many scenarios.
+This dissertation study various aspects of the side-channel vulnerabilities.
+
+The first step is to identify side-channel leakages.

### 2021-02-12 SupplementaryMaterial/Abstract.tex
update dissertations

@@
 
-The first step is to identify side-channel leakages.
+The dissertation first introduces a new method to detect address-based side-channel in the binary code.
+While existing approaches can identify side-channel leakages in real-world programs.
+We notice that while some existing work can detect side-channel leakages.
+Many of them are computationally expensive and apply some domain knowledge to simplify the analysis.
+We examine the bottleneck of current symbolic approaches and scaling it production-system crypto analysis.
+The evaluation results confirm that the approach is much faster than the state of art tools while identifying all the known leakages reported by previous tools.
+
+Second, while current side-channel detection work is able to identify numerous potential vulnerabilities.
+However, in practice, many such vulnerabilities leak a negligible amount of sensitive information, and thus developers are often reluctant to address them.
+Existing tools do not provide information to evaluate a leak’s severity, such as the number of leaked bits.
+To address this issue, we propose a new program analysis method to precisely quantify the leaked information in a single-trace attack through side-channels.
+It can identify covert information flows in programs that expose confidential information and can reason about security flaws that would otherwise be difficult, if not impossible, for a developer to find.
+We model an attacker’s observation of each leakage site as a constraint.
+We use symbolic execution to generate these constraints and then run Monte Carlo sampling to estimate the number of leaked bits for each leakage site.
+By applying the Central Limit Theorem, we provide an error bound for these estimations.
+The evaluation results shows that our method can successfully distinguish severe leakages from many negligible leakages.
+
+Third, we extend our approach to quantify side-channel leakages from multiple trace attacks.
+In this work, we present MME, an address-based side-channel detection and quantification tool that can quantify the side-channel leakages in a conservation but precise way.
+Contrary to previous side-channel detection tools, our approach can identify those really severe side-channel leakages without false positives.
+Moreover, our tools can estimate the total effect of multiple leakage sites as well.
+MME consists of three steps.
+First, the target program is running with a number of the sensitive inputs to record the memory access under different inputs.
+Second, the long address traces are split into several segments based on the location in the source code.
+Finally, we analyze the memory-access information from those segments and compare the address access information with the original source code.
+Based on the channel capacity between the original secrets and the observation of the attacker, we quantify the information leakages for each leakage site.
+We evaluate MME with OpenSSL, mbedTLS, TinyDNN and GTK.
+Our evaluation results show MME is effective in identifying and quantifying side-channel leakages.

### 2021-02-12 Chapter-1/Chapter-1.tex
update

% !TEX root = ../YourName-Dissertation.tex

\chapter{Introduction} \label{chapter1:introduction}

Side channels are inevitable in modern computer systems as the sensitive
information may be leaked through many kinds of inadvertent behaviors, such as power,
electromagnetic radiation, and even
sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}.
Among them, software-based side channel attacks, such as cache attacks, memory page
attacks, and controlled-channel attacks, are especially common and have been
studied for
years~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}. These
attacks result from vulnerable software and shared hardware components.
By observing program outputs or hardware behaviors, attackers can infer program
execution flows that manipulate secrets and guess secrets such as encryption
keys~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.

\section{Limitations of Existing Side Channel Vulnerability Detection Works}
Regarding the root cause of software-based side channel attacks, many of them originate
from two specific circumstances: data flow from secrets to load
addresses and data flow from secrets to branch conditions. We refer to them as
 secret-dependent memory-access and control-flow, respectively. A
central problem is eliminating these two code patterns. 
Recent
works~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946},
find plenty of side-channel vulnerabilities. For example,
DATA~\cite{217537} reports 2,246 potential leakage site for the RSA
implementation in OpenSSL\@. 
%After some inspections, 1,510 leakages are dismissed. But it
%still leaves 460 data-access leakages and 278 control-flow leakages. 
However, we find most of the reported vulnerabilities are not fixed because
of the following reasons.
First, many side-channels vulnerable implementations have better performance.
Those vulnerabilities are well-known for years. For example,
Symmetric encryptions like AES and DES still uses lookup tables (T-tables), which
is fast but notoriously known to be vulnerable to side channels.
As for asymmetric encryptions, most implementations of RSA, adopt the CRT optimization,
which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}.
Second, side-channels are numerous and it is hard to fix all these vulnerabilities,
let alone the majority of them are negligible. 
That is, some vulnerabilities can result in the key being 
entirely compromised~\cite{184415, aumuller2002fault}, but many other vulnerabilities prove to be less
severe in reality. Therefore, we need a proper quantification metric to 
assess the sensitive level of side-channel vulnerabilities.

Previous attempts like static methods~\cite{182946,5207642}, usually with
abstract interpretations, can give a leakage upper bound, which is useful to
justify the implementation is secure if they report zero or little leakage.
However, they cannot indicate how severe the leakage is because of the
over-approximation method they apply. For example, CacheAudit~\cite{182946} reports that the upper
bound leakage of AES-128 exceeds the original key size! The dynamic methods take
another approach with a concrete input and run the program in a real
environment. Although they are very precise in terms of actual leakages, no
existing tool can precisely assess the severity of the vulnerabilities in production
software.

To overcome these limitations, we propose a novel method to quantify information
leakages precisely. Unlike previous works that only consider the
``average'' information leakage, we study the problem based on real attack
scenarios. The average information leakage model assumes the target program has
\emph{variable} or \emph{random} sensitive information as inputs when an attack is
launched. However, for real-world attacks, an adversary may run the target
problem with the \emph{fixed} unknown sensitive information
as the input. Therefore, the previous threat model cannot model real attack
scenarios. In contrast, our method is more precise and fine-grained. 
We quantify
the amount of leaked information as the cardinality of the set of possible
inputs based on attackers' observations.
Before an attack, an adversary has a large but finite input space. Every time
when the adversary observes a leakage site, he can eliminate some potential
inputs and reduce the size of the input space. The smaller the input space is,
the more information is obtained. In an extreme case, if the size of the
input space reduces to one, the adversary can uniquely determine the input, 
which means all the secret information (e.g., the whole secret key) is
leaked. By counting the number of distinct inputs, we can quantify the
information leakage precisely.

We use constraints generated from symbolic execution to model the relation 
between the original sensitive input
and the attacker's observations. Symbolic execution can
provide fine-grained information but is usually believed to be an expensive
operation in terms of performance. Therefore, existing dynamic symbolic
execution works~\cite{203878,236338,Brotzman19Casym} either only analyze
small programs or apply some domain knowledge~\cite{203878} to simplify the analysis. We
systematically exam the bottleneck of the trace-oriented symbolic execution and optimize it
to be scalable to real-world cryptosystems.

We apply the above technique and build a tool called \tool{},
%\footnote{CleverHans is a horse that can ``count''. Our tool uses an advanced
%%method to count the number of leaked bits from side channels.} 
to discover potential information leakage sites as well as estimate how
many bits they can leak for each leakage site. 
First, we collect dynamic execution traces for each target
libraries and then run symbolic execution on each instruction. In this way, we model
each side-channel leakage as a logic formula. The sensitive input is divided into
several independent bytes, and each byte is regarded as a unique and free symbol. Those
formulas can precisely model side-channel vulnerabilities. Then we use the conjunction
of those formulas to model the same leaks in the source code but appears in the different location of
the execution trace file (e.g., leakages inside a loop).
Finally, we introduce Monte Carlo
sampling method to estimate the single and combined information leakage.

We apply \tool{} on both symmetric and asymmetric ciphers from real-world crypto
libraries, including OpenSSL, mbed TLS and Monocypher\@. The experimental result confirms
that \tool{} can precisely identify previously known vulnerabilities, report
how much information is leaked and which byte in the original sensitive buffer
is leaked. We also test \tool{} on side-channel free algorithms. \tool{} has no
false positives.
Although some of the analyzed crypto libraries have a number of
side-channels, they actually leak very little information. Also, we also show the
of widely deployed software countermeasures can mitigate side channels.
\tool\ also discovers new vulnerabilities. With the help of \tool{}, we confirm
that those vulnerabilities are severe.

In summary, we make the following contributions:

\begin{itemize}
      \item We propose a novel method that can quantify fine-grained leaked
            information from side-channel vulnerabilities to match real attack
            scenarios. Our method is different from previous ones in that we
            model real attack scenarios more precisely, while the previous
            research only models the ``average'' or ``random'' case. 
            We transfer the information quantification problem into a counting
            problem and use the Monte Carlo sampling method to estimate the
            information leakage.
            % compared to previous results and
            %%   We model each side-channel vulnerabilities as math formulas %
            %and mutiple side-channel vulnerabilities can be seen as the %
            %conjunction of those formulas, which precisely models the % program
            %semantics.

      %%\item  Some initial results indicate the sampling
      %%     method suffers from the curse of dimensionality problem. Therefore, we
      %%      design a guided sampling method and provide the
      %%      corresponding error estimate.

      \item We implement the proposed method into a practical tool and apply it
            on several real-world software. \tool{} successfully identifies
            memory-related side-channel vulnerabilities and calculates the
            corresponding information leakage. 
            Our results are surprisingly different, much more useful in practice.
            The information leakage results
            provide detailed information that can help developers to fix the
            reported vulnerabilities.
\end{itemize}

\section{Trace-oriented Binary Analysis}
Binary analysis is the process of automatically inferring program behaviors from
the binary executable.
It plays a critical role from a security viewpoint. For many programs, like malware, Commercial off-the-shelf (COTS) application, source code are typically not
available. Besides, some low-level information, including memory accesses and cache
accesses, is only available on the binary code level. As many side-channel vulnerabilities
are typically low-level problem, we believe binary analysis are more suitable than
source code level analysis.

Binary analysis can be categorized into two groups depending when the analysis is
launched.
\begin{itemize}
    \item Static Analysis infer analyzing the binary program without running it. Previous studies focus on addressing several open problems, including identifying
    function entry points~\cite{184521, Wang17a}, resolving indirect jumps, disambiguating code and data and solving alias memory address. Static analysis
    lacks the run-time information, which may lead to false positives and false 
    negatives. However, static analysis typically can have better coverage as it can
    reason about every possible execution paths.
    \item Dynamic Analysis involving analyzing a binary code as it executes. Tools
    that perform dynamic analysis usually need to instrument the binary code.  
    Although dynamic analysis can only reason only one execution path. It is usually more precise than static analysis.
\end{itemize}

In this dissertation, we detected side-channel vulnerabilities by trace-based analysis.
It consists of two steps. The first step, called online trace logging, collect run-time
information for the targeted program under the dynamic binary instrumentation (DBI)
to collect necessary information. The second step, called offline analysis, run
several analysis (e.g., taint analysis, symbolic analysis) on the top of traces.

Existing binary analysis frameworks, like Angr, BAP and Bitblaze combine both static
and dynamic analyses, are applicable to a series of tasks. However, those frameworks
are not suitable for the following reasons. 
\begin{itemize}
    \item Existing binary analysis frameworks transfer the machine code into
    architecture-independent intermediate representatives (IR) and then run the
    analysis. The IR design, which simplify the implementation and support multiple
    architectures, introduces imprecision to the analysis results as well because some
    information like cache accesses, control-flow transfers are lost during the IR
    transformation.
    \item Coverage is one of the concerns when they design the frameworks. 
    As a result, they rely on constraint solvers to find different inputs that can
    trigger different paths. As constraint solving is known for time-consuming. It is
    one of the obstacles to make analyses salable.
    However, we will show for many tasks, like binary similarity comparisons and side-channel vulnerability detection. We can
    reduce the call to the solver just by fuzzing the formula. The design will
    significantly reduce the overhead.
\end{itemize}
To solve the above problem, we propose Phoenix, a trace-oriented binary analysis
framework. Phoenix is a dynamic binary analysis framework that provide several 
functioning including dynamic symbolic execution engine, dynamic taint analysis
engine, AST representation of X86 and binding for STP solvers. It run 
execution on the top X86 instructions and symbolically reason the program behaviours.
Our preliminary results show that Phoenix has a better performance compared to 
many existing works, which makes it scalable to real-world applications.

\section{Dissertation Organization}
The rest of the dissertation is organized as follows. We first present relevant backgrounds and related works in Chapter~\ref{chapter1}. We then propose our works in
Chapter~\ref{chapter2}. Chapter~\ref{chapter3} and Chapter~\ref{chapter4} introduce
our recent progress about the proposed work.

### 2021-02-14 Chapter-1/Chapter-1.tex
update

@@
 
-\section{Limitations of Existing Side Channel Vulnerability Detection Works}
+\section{Side-channel}
+
+\subsection{Attacks}
+
+\subsection{Defense}
+
 Regarding the root cause of software-based side channel attacks, many of them originate
@@
 
-\section{Trace-oriented Binary Analysis}
+\section{Binary Analysis}
 Binary analysis is the process of automatically inferring program behaviors from

### 2021-02-14 Chapter-2/Chapter-2.tex
update

% !TEX root = ../YourName-Dissertation.tex

\chapter{Background}

\section{Address-based Side-channel Attacks}

\section{Information Theory}

\section{Binary Analysis}

### 2021-02-15 Chapter-3/Chapter-3.tex
init
update

--- 2021-02-14 Chapter-2/Chapter-2.tex
@@
 
-\chapter{Background}
+\chapter{Scalable Side-channel Vulnerability Detection}
+\section{Motivation}
+While there are several existing work on side-channel leakage detections, we find it very hard to apply existing methods to identify controlled-channel attacks.
+According to Table~\ref{table:related_work}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction.
+\begin{table*}
+    \centering
+    \caption{Existing leakage detection tool only evaluate them on cryptography library.
+1.
+Most recent work only evaluates their approaches on cryptography libraries.
+2.
+All of them can not reason about the total effect of multiple leakages.}
+    \label{table:related_work}
 
-\section{Address-based Side-channel Attacks}
+    \begin{tabular}{lllcclc}
+    \toprule
+    Tool & S/D & Method  & AVX/SIMD  & Multiple & Evaluation & Available \\ \midrule
+    CacheAudit~\cite{doychev2015cacheaudit} & Static  & Abstraction  & \xmark & \xmark & Crypto Algorithm  & \cmark \\ 
+    CacheD~\cite{wang2017cached} & Dynamic  & Symbolic Execution + Taint Analysis  & \xmark & \xmark & Libgcrypt, OpenSSL & \xmark \\
+    CachSym~\cite{brotzman2019casym} & Static & Symbolic Execution  & \xmark & \xmark & Crypto Snippet & \xmark \\
+    CacheS~\cite{wang2019identifying} & Static & Abstract Interpretation & \xmark & \xmark & Libgcrypt, OpenSSL, mbedTLS & \xmark \\
+    DATA~\cite{weiser2018data} & Dynamic & Trace Alignment + Comparison & \cmark & \xmark & OpenSSL, PyCrypto & \cmark \\
+    ctgrind~\cite{langley2010ctgrind} & Dynamic & Taint Analysis & \cmark & \xmark & Crypto Library & \cmark \\
+    Satcco~\cite{xiao2017stacco} & Dynamic & Trace Comparison & \cmark & \xmark & OpenSSL, GnuTLS, mbedTLS, WolfTLS, LibreSSL & \xmark \\
+    ANABLEPS~\cite{wang2019time} & Dynamic & Trace Comparison & \cmark & \xmark & Deep Learning, gsl, Hunspell, PNG, Freetype, QRcodegen, Genometools & \xmark \\
+    MicroWalk~\cite{wichelmann2018microwalk} & Dynamic & Trace Comparison & \cmark & \xmark & Intel IPP, Microsoft CNG & \cmark \\ 
+    \bottomrule
+    \end{tabular}
 
-\section{Information Theory}
+    \end{table*}
 
-\section{Binary Analysis}
+\section{Threat Model}
+
+\section{Examples}
+
+\section{Math Notations}
+
+\section{Scalability}
+
+\section{Evaluation}
+
+\section{Discussion}

### 2021-02-15 Chapter-2/Chapter-2.tex
update

@@
 
-\chapter{Background}
+\chapter{Background and Related Work}
 
 \section{Address-based Side-channel Attacks}
+Side channels can leak sensitive information
+unconsciously through different execution behaviors caused by shared 
+hardware components (e.g., CPU cache, TLB, and
+DRAM) in modern computer systems~\cite{ge2018survey,szefer2019survey}.
 
+For example, cached-based
+side-channels~\cite{yarom2017cachebleed,191010,184415,,Osvik2006,liu2015last,184415,liu2015last}
+rely on the time difference between cache misses and cache hits. We introduce two
+common attack strategies, namely Prime+Probe~\cite{liu2015last} and
+Flush+Reload~\cite{184415}. Prime+Probe targets a single cache set. An
+attacker preloads the cache set with its own data and waits until the victim
+executes the program. If the victim accesses the cache set and evicts part of
+the data, the attacker will experience a slow measurement. 
+While Flush+Reload targets a
+single cache line, it requires the attacker and victim share some memory. 
+During the ``flush'' stage, the attacker flushes the ``monitored
+memory'' from the cache and waits for the victim to access the memory,
+who will load the sensitive information to the cache line. In the next phase,
+the attacker reloads the ``monitored memory''. By measuring the time difference
+brought by cache hit and miss, the attacker can further infer the sensitive information.
+Some other types of side-channels target different hardware
+layers other than CPU cache. For example, the controlled-channel
+attack~\cite{7163052}, where an attacker works in the kernel space, can infer
+sensitive data in shielding systems by observing the page fault sequences
+after restricting some code and data pages.
+
+\begin{figure}[]
+
+    \noindent\begin{minipage}{0.45\linewidth}
+        \noindent
+        \begin{lstlisting}[numbers = none]
+unsigned long long r;
+int secret[32];
+...
+while(i>0){
+    r = (r * r) % n;
+    if(secret[--i] == 1)
+        r = (r * x) % n;   
+}
+        \end{lstlisting}
+\vspace*{-9pt}
+        \caption{Secret-dependent control-flow transfers}
+        \label{fig:secret:cf}
+    \end{minipage}
+    \hfill
+    \begin{minipage}{0.45\linewidth}
+        \begin{lstlisting}[numbers = none]
+static char Fsb[256] = {...}
+... 
+uint32_t a = *RK++ ^ \ 
+(FSb[(secret)) ^
+(FSb[(secret >> 8)] << 8 ) ^
+(FSb[(secret >>16)] << 16 ) ^
+(FSb[(secret >>24)] << 24 );
+...
+        \end{lstlisting}
+\vspace*{-9pt}
+        \caption{Secret-dependent memory accesses}
+        \label{fig:secret:da}
+    \end{minipage}
+\vspace*{-12pt}
+\end{figure}
+
+The key intuition is that above side-channel attacks happen when a
+program accesses different memory addresses if the program has different
+sensitive inputs. As shown in Figure~\ref{fig:secret:cf} and Figure~\ref{fig:secret:da}, 
+if a program shows different patterns in
+control transfers or data accesses when the program processes different
+sensitive inputs, the program could possibly have side channels vulnerabilities.
+Different kinds of side-channels can be exploited to retrieve information in
+various granularities. For example, cache channels can observe cache
+accesses at the level of cache sets~\cite{liu2015last}, cache lines~\cite{184415} or other granularities. 
+Other kinds of side-channels like controlled-channel attack~\cite{7163052},
+can observe the memory access at the level of memory pages.
 \section{Information Theory}
+This section presents a short introduction on information theory. For a detailed tutorial, we recommend users refer to the following literature.
+
+Given an event $e$ that occurs with the probability $p(e)$, we receive
+\begin{displaymath}
+    I = - \log_2p(e)
+\end{displaymath}
+bits of information by knowing the event $e$ happens according to information theory~\cite{shannon1948mathematical}. 
+Considering a char variable $a$
+with one byte storage size in a C program, its value ranges from 0 to 255.
+Assume $a$ has a uniform distribution. If we observe that
+$a$ equals $1$, the probability of this observation is $\frac{1}{256}$. So 
+we get $-\log(\frac{1}{256}) = 8$ bits information, which is exactly the size
+of a char variable in the C program.
+
+Existing works on information leakage quantification typically use Shannon
+entropy~\cite{clark2007static,Wichelmann:2018:MFF:3274694.3274741},
+min-entropy~\cite{10.1007/978-3-642-00596-1_21}, and max-entropy~\cite{182946,
+Doychev:2017:RAS:3062341.3062388}. In these frameworks, the input sensitive
+information $K$ is considered as a random variable.
+
+Let $k$ be one of the possible
+value of $K$. The Shannon entropy $H(K)$ is defined as
+\begin{displaymath}
+    H(K) = - \sum_{k {\in} K}p(k)\log_2(p(k))
+\end{displaymath}
+
+Shannon entropy can be used to quantify the initial uncertainty about the
+sensitive information. It measures the amount of information in a system.
+
+Min-entropy describes the information leaks for a program with the most likely input. 
+For example, min-entropy can be used to describe the
+best chance of success in guessing one's password using the
+most common password. %, which is defined as
+\begin{displaymath}
+    \mathit{min\text{-}entropy} = - \log_2(p_{\mathit{max}})
+\end{displaymath}
+
+Max-entropy is defined solely on the number of possible observations.
+%It is equal to $-\log_2{n}$.
+\begin{displaymath}
+    \mathit{max\text{-}entropy} = -\log_2{n}
+\end{displaymath}
+As it is easy to compute, most recent works~\cite{182946,Doychev:2017:RAS:3062341.3062388} use max-entropy as the definition of
+the amount of leaked information.
+
+To illustrate how these definitions work, we consider the code
+fragment in Figure~\ref{fig:side-channel}. It has two secret-dependent
+control-flows, A and B.
+
+\begin{figure}[h!]
+\centering
+\begin{lstlisting}[xleftmargin=.03\textwidth,xrightmargin=.01\textwidth]
+uint8_t key[2], t1, t2;
+get_key(key);              // 0 <= key[0], key[1] < 256
+t1 = key[0] + key[1];
+t2 = key[0] - key[1];
+if (t1 < 4){               // leakage site A
+    foo();    
+}                          
+if (t2 > 0){               // leakage site B     
+    doo();    
+}                          
+\end{lstlisting}
+\vspace*{-1pt}
+    \caption{Side-channel leakage}
+    \label{fig:side-channel}
+\end{figure}
+In this paper we assume an attacker can observe the secret-dependent control-flows in Figure~\ref{fig:side-channel}.
+Therefore, an attacker can have two different observations for each leak site
+depending on the value of the $\mathit{key}$: $A$ for function \textsf{foo} is executed, 
+$\neg A$ for function \textsf{foo} is not executed, $B$ for function \textsf{doo} is
+executed, and $\neg B$ for function \textsf{doo} is not executed. Now the
+question is how much information can be leaked from the above code if an
+attacker knows which branch is executed?
+
+\begin{table}[ht]
+    \centering\small\footnotesize
+    \caption{The distribution of observation}\label{shtable}
+    \vspace*{-0pt}
+%    \resizebox{\columnwidth}{!}{
+    \begin{tabular}{l|cc|cc}
+        \hline
+
+        Observation ($o$)   & $A$ & $\neg A$ & $B$ & $\neg B$ \\ \hline
+        Number of Solutions & 65526       & 10        & 32768     & 32768           \\ \hline
+        Possibility (p)     & 0.9998      & 0.0002    & 0.5    & 0.5       \\
+        \hline
+    \end{tabular}
+%        }
+\end{table}
+
+Assuming $\mathit{key}$ is uniformly distributed, we can calculate the corresponding
+possibility by counting the number of possible inputs. Table~\ref{shtable}
+describes the probability of each observation. We use the above three types of 
+leakage metrics to calculate the amount of leaked information for leak A and leak B.
+
+\vspace{3pt}
+\textbf{Min Entropy.}
+As $p_{A\mathit{max}} = 0.9998$ and $p_{B\mathit{max}} = 0.5$, 
+with the definition, min-entropy equals to
+\begin{align*}
+    \mathit{min\text{-}entropy_A} & = -\log_2{0.9998} = 0.000\ \mathrm{bits} \\
+    \mathit{min\text{-}entropy_B} & = -\log_2{0.5} = 1.000\ \mathrm{bits}
+\end{align*}
+
+\textbf{Max Entropy.}
+Depending on the value of key, the code can run two different branches for each leakage site. 
+Therefore, with the max entropy
+definition, both leakage sites leak
+
+\begin{displaymath}
+    \mathit{max\text{-}entropy} = -\log_2{2} = 1.000\ \mathrm{bits}
+\end{displaymath}
+
+\textbf{Shannon Entropy.}
+Based on Shannon entropy, the respective amount of information in A and B equals to
+{\footnotesize
+\begin{align*}
+    \mathit{Shannon\text{-}entropy_A} & = -(0.9998*\log_{2}0.9998      \\
+                                    & \qquad+ 0.0002*\log_{2}0.0002)  \\
+                                    & = 0.000\ \mathrm{bits}         \\
+    \mathit{Shannon\text{-}entropy_B} & = -(0.5*\log_{2}0.5      \\
+                                    & \qquad+ 0.5*\log_{2}0.5)        \\
+                                    & = 1.000\ \mathrm{bits}                             
+\end{align*}
+}
+In the next section, we will show that these measures work well only
+theoretically in a static analysis setting. 
+Generally, they do not apply to dynamic analysis or real
+settings. We will present that the static or theoretical results could be
+dramatically different from the real world, and we do need a better method to
+quantify the information leakage from a practical point of view.
 

### 2021-02-15 Chapter-2/Chapter-2.tex
update

@@
 can observe the memory access at the level of memory pages.
+
+\subsection{Cache-level Channel}
+Cache-based channels rely on the time difference between cache misses and cache hits. Cache channel attacks can observe cache accesses at the level of cache sets, cache lines or other granularities. 
+We introduce two common attack strategies, namely Prime+Probe and
+Flush+Reload. Prime+Probe targets a single cache set. An
+attacker preloads the cache set with its own data and waits until the victim
+executes the program. If the victim accesses the cache set and evicts part of
+the data, the attacker will experience a slow measurement. 
+While Flush+Reload targets a single cache line, it requires the attacker and victim share some memory. During the ``flush'' stage, the attacker flushes the ``monitored
+memory'' from the cache and waits for the victim to access the memory,
+who will load the sensitive information to the cache line. In the next phase,
+the attacker reloads the ``monitored memory''. By measuring the time difference
+brought by cache hit and miss, the attacker can further infer the sensitive information. Some other types of side-channels target different hardware
+layers other than CPU cache.
+
+\subsection{Page-level Channel}
+Recent studies also shows the attacks can observe the memory access at the granularity of memory pages.
+One example is the controlled-channel attack~\cite{xu2015controlled}, where a privileged adversary try to infer the sensitive information by manipulating the enclave page access.
+Those kinds of attacks usually happen on the shielding system.
+A malicious OS can proactively revoke a virtual enclave memory page from the memory.
+If the victim enclave program accesses the memory table, then the adversary can know which page is accessed by observing the page fault sequence.
+While the granularity of the controlled-channel attacks is very coarse grained, the controlled-channel attacks allow the attacker to have a noise-free observation.
+Examples of other attacks exploits page cache maintained by the OS, TLB also shares the same granularity.
+
+In this paper, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs).
+To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.
+
+\begin{table}
+    \centering
+    \caption{Due to the page limit, we only shows some representations of the vast side-channel attacks: Attacks, the shared hardware resources with attackers, the granularity of the attacker can observe, is there any published attacks on non-cryptography library and if the type of attack can exploit multiple leakage sites.}
+    \label{table:side_channel_attack}
+    \resizebox{\columnwidth}{!}{%
+
+    \begin{tabular}{lllcc}
+    \toprule
+    Attacks & Shared Resources & Granularity  & Non-Crpyto & Multiple   \\ \midrule
+    CacheBleed~\cite{yarom2017cachebleed} & Cache & Sub Cache Line (<64 B)  & \xmark & \xmark \\ 
+    CopyCat~\cite{moghimi2020copycat} & Page Tables   & Instruction   & \xmark &  \xmark \\
+    Prime + Probe~\cite{liu2015last} & Cache & Cache Set (64-512 B)  & \cmark &   \xmark \\
+    Prime + Abort~\cite{disselkoen2017prime+} & Cache  & Cache Set (64-512 B) & \cmark &  \xmark   \\
+    Flush + Reload~\cite{yarom2014flush+} & Cache & Cache Line (64 B) & \cmark  &  \cmark \\
+    Flush + Flush~\cite{gruss2016flush+} & Cache & Cache Line (64 B) & \cmark & \xmark  \\
+    Controlled-channel Attack~\cite{xu2015controlled} & Page Tables & Page (4KB) & \cmark & \xmark \\
+    TLBleed~\cite{gras_translation_2018} & MMUs & TLB Set (4KB) & \cmark  & \xmark \\
+    Page Cache Attacks~\cite{gruss2019page} & Page Cache &  Page (4KB) & \xmark &  \cmark \\ 
+    \bottomrule
+    \end{tabular}
+    }
+    \end{table}
 \section{Information Theory}
@@
 
-\section{Binary Analysis}
+Let $k$ be one of the possible
+value of $K$. The Shannon entropy $H(K)$ is defined as
+\begin{equation}\label{eq1}
+    H(K) = - \sum_{k {\in} K}p(k)\log_2(k)
+\end{equation}
+
+Shannon entropy can be used to quantify the initial uncertainty about the sensitive information.
+It measures the amount of information in a system.
+For example, an AES encryption program takes a 128-bit key as the input.
+Suppose every key has the equal opportunity and $p_k = 1/ 2^{128}$, then the encryption system has $128 \, \mathit{bits}$ information according to Shannon entropy.
+
+In the paper, we use the channel capacity to describe the information leakages through a channel.
+In information theory, the channel capacity is used to quantify the rate of information can be reliably transmitted over a channel.
+If we use $K$ to represent the input secrets and $O$ to represent the output observation.
+The channel capacity ($C$) is defined as
+
+\begin{equation}\label{eq2}
+C(K;O) = \max_{p(x)} I(K;O)
+\end{equation}
+Here $I(K;O)$ is the mutual information between $K$ and $O$.  
+\begin{equation} \label{eq3}
+    I(K;O) = \sum_{k {\in} K}{\sum_{o {\in} O}{p(k, o)\log_2\frac{p(k, o)}{p(k)p(o)}}}
+\end{equation}
+
+While the general case of channel capacity is hard to execute, we consider the two special channels.
+
+\subsection{Noiseless Lossless Channel}
+The channel of the system is noiseless and lossless if
+
+\begin{equation} \label{eq:1}
+    C(K;O) = \max_{p(k)} I(K;O) = \max_{p(k)} H|O| =\max_{p(k)} H|K|
+\end{equation}
+$|K|$ represents the number of symbols in $K$.
+
+Figure~\ref{fig:channel}a shows the example of the type of the channel.
+Under the circumstance, we always have $P(o_i/k_i) = 1$ and $P(k_i/o_i) = 1$.
+As we can see, the channel have the unique output ($o \in O$) for every input ($k \in K$).
+
+\begin{figure}
+    \begin{minipage}{0.48\linewidth}
+    \resizebox{\linewidth}{!}{
+
+     \begin{tikzpicture}[ele/.style={fill=black,circle,minimum width=.8pt,inner sep=1pt},every fit/.style={ellipse,draw,inner sep=-2pt}]
+      \node[ele,label=left:{\LARGE $k_1$}] (a1) at (0,4) {};    
+      \node[ele,label=left:{\LARGE $k_2$}] (a2) at (0,3) {};    
+      \node[ele,label=left:{\LARGE $k_3$}] (a3) at (0,2) {};
+      \node[ele,label=left:{\LARGE $k_4$}] (a4) at (0,1) {};
+
+      \node[ele,,label=right:{\LARGE $o_1$}] (b1) at (4,4) {};
+      \node[ele,,label=right:{\LARGE $o_2$}] (b2) at (4,3) {};
+      \node[ele,,label=right:{\LARGE $o_3$}] (b3) at (4,2) {};
+      \node[ele,,label=right:{\LARGE $o_4$}] (b4) at (4,1) {};
+
+      \node[draw,fit= (a1) (a2) (a3) (a4),minimum width=2cm] {} ;
+      \node[draw,fit= (b1) (b2) (b3) (b4),minimum width=2cm] {} ;  
+      \draw[->,thick,shorten <=2pt,shorten >=2pt] (a1) -- (b1);
+      \draw[->,thick,shorten <=2pt,shorten >=2] (a2) -- (b2);
+      \draw[->,thick,shorten <=2pt,shorten >=2] (a3) -- (b3);
+      \draw[->,thick,shorten <=2pt,shorten >=2] (a4) -- (b4);
+     \end{tikzpicture}
+    }
+    \caption*{(a) Noiseless Lossless}
+    \end{minipage}
+    \hfill
+    \begin{minipage}{0.48\linewidth}
+    \resizebox{\linewidth}{!}{
+
+     \begin{tikzpicture}[ele/.style={fill=black,circle,minimum width=.8pt,inner sep=1pt},every fit/.style={ellipse,draw,inner sep=-2pt}]
+      \node[ele,label=left:{\LARGE $k_1$}] (a1) at (0,4) {};    
+      \node[ele,label=left:{\LARGE $k_2$}] (a2) at (0,3) {};    
+      \node[ele,label=left:{\LARGE $k_3$}] (a3) at (0,2) {};
+      \node[ele,label=left:{\LARGE $k_4$}] (a4) at (0,1) {};
+
+      \node[ele,,label=right:{\LARGE $o_1$}] (b1) at (4,4) {};
+      \node[ele,,label=right:{\LARGE $o_2$}] (b2) at (4,3) {};
+      \node[ele,,label=right:{\LARGE $o_3$}] (b3) at (4,2) {};
+      \node[ele,,label=right:{\LARGE $o_4$}] (b4) at (4,1) {};
+
+      \node[draw,fit= (a1) (a2) (a3) (a4),minimum width=2cm] {} ;
+      \node[draw,fit= (b1) (b2) (b3) (b4),minimum width=2cm] {} ;  
+      \draw[->,thick,shorten <=2pt,shorten >=2pt] (a1) -- (b1);
+      \draw[->,thick,shorten <=2pt,shorten >=2] (a2) -- (b2);
+      \draw[->,thick,shorten <=2pt,shorten >=2] (a3) -- (b2);
+      \draw[->,thick,shorten <=2pt,shorten >=2] (a4) -- (b2);
+     \end{tikzpicture}
+     }
+     \caption*{(b) Noiseless Loss}
+     \end{minipage}
+    \caption{Two Kinds of Channels}\label{fig:channel}
+    \end{figure}
+
+\subsection{Noiseless Loss Channel}
+In reality, noiseless loss channel is more common. We define the channel is noiseless loss if
+
+\begin{equation} \label{eq:2}
+    C(K;O) = \max_{p(x)} I(K;O) = \max_{p(x)} H |O| = \log_2 {|O|}
+\end{equation}
+
+Figure~\ref{fig:channel}b  shows the example of the type of the channel.
+Once the input symbol is determined, the output symbol is also determine.
+As we can see, the channel have the unique output ($o \in O$) for every input ($k \in K$).

### 2021-02-15 Chapter-3/Chapter-3.tex
update

@@
 \section{Math Notations}
+e now discuss how to model observations ($O$), which are the direct information
+that an adversary can get during the attack.
 
+During the execution, a program ($\beta$) have many temporary values ($t_i \in
+T$). Once $\beta$ (program), $k$ (secret), and $m$ (message, public) are
+determined, $t_i$ is also fixed. Therefore, $ t_i = f_i(\beta, k, m)$, where $f_
+i$ is a function that maps between $t_i$ and ($\beta$, $k$, $m$).
+
+In the paper, we consider two code patterns that can be exploited by an attacker,
+\emph{secret-dependent control transfers} and \emph{secret-dependent data
+accesses}. In other words, an adversary has observations based on control-flows
+and data accesses.
+
+\subsection{Secret-dependent Control Transfers}
+We think a control-flow is secret-dependent if different input sensitive keys
+($K$) can lead to different branch conditions. Therefore,
+We define a branch is secret-dependent if:
+$$\exists k_{i1}, k_{i2} \in K, \,f_i(\beta, k_{i1}, m) \neq f_i(\beta, k_{i2}, m)$$
+
+An adversary can observe which branch the code executes, if the branch condition
+equals to $t_b$. We use the constraint $c_i : f_i(\beta, k, m) = t_b$ to model
+the observation ($o$) on secret-dependent control-transfers.
+
+\subsection{Secret-dependent Data Accesses}
+Similar to secret-dependent control-flow transfers, a data access operation is
+secret-dependent if different input sensitive keys ($K$) can lead to different
+memory addresses. We use the model from CacheD~\cite{203878}. The low $L$ bits
+of the address are irrelevant in side-channels.
+
+We consider a data access is secret-dependent if:
+$$\exists k_{i1}, k_{i2} \in K, \,f_i(\beta, k_{i1}, m) >> L \neq f_i(\beta, k_{i2}, m) >> L$$
+
+If the memory access equals to $t_b$, we can use the constraint $c_i :
+f_i(\beta, k, m) >> L = t_b >> L$ to model the observation on secret-dependent
+data accesses.
+
+With the above definitions, we can model an attacker's observation by a series of math
+formulas. For example, in Figure~\ref{fig:side-channel}, if an attacker observes
+the code executes the branch 1, we have $c_5: k_1 + k_2 < 4$ to describe an
+attacker's knowledge and $K^{o5} = \{k_1,\, k_2\,|\, (k_1 + k_2) < 4\}$. If an
+attacker observes the code executes the branch 2, we have $c_8: k_1 - k_2 > 0$
+and $K^{o8} = \{k_1,\, k_2\,|\, (k_1 - k_2) > 0\}$.
 \section{Scalability}
+\subsection{Trace-oriented Symbolic Execution}
+While symbolic execution can capture fine-grained semantics of programs, it
+is also notorious for its unbearable performance cost. Previous trace-oriented
+symbolic execution based
+works~\cite{203878,Chattopadhyay:2017:QIL:3127041.3127044} all have large
+performance bottlenecks. As a result, those approaches either only apply to
+small-size programs~\cite{Chattopadhyay:2017:QIL:3127041.3127044} or apply some
+domain knowledge to simplify the analysis. 
+%Those tools interpret each
+%instruction and update memory cells and registers with formulas that
+%captured the semantics of the execution and search different input values that
+%can lead to different execution behaviors using constraint solver. 
+We implement
+the approach presented in \S\ref{sec:trace-qif} and model the side-channels as
+formulas. While the tool can finish analyzing some simple cases like AES, it can
+not handle complicated cases like RSA.
+We observe that finding side-channels using symbolic execution is different from
+traditional general symbolic execution and can be optimized to be as efficient
+as other methods with approaches below.
 
+\subsection{Interpret Instructions Symbolically}
+Existing binary analysis tools~\cite{shoshitaishvili2016state,
+10.1007/978-3-642-22110-1_37} usually translate machine instructions into
+intermediate languages (IR) to simplify analysis. 
+The reason is that the number of machine instructions is
+enormous, and the semantics of each instruction is complex. Intel Developer
+Manual~\cite{intelsys} introduces more than 1000 different x86 instructions. 
+IR typically has fewer instructions compared to the original machine ISA\@.
+However, the IR layer, which predigest the implementation
+and reduce the workload of those tools, is not suitable for side-channels 
+analysis. Memory-based side-channels are very low issues. So, in general,
+IR-based or source code side-channels analyses are not accurate enough.
+In many cases, compilers can use conditional moves or bitwise operations to eliminate
+branches. Also, as some IRs are not a superset or a subset of ISA, 
+it is hard to rule out conditional jumps introduced by IR and add real branches 
+eliminated by IR transformations.
+
+Moreover, the IR design introduces significant overhead~\cite{217563}.
+Transferring machine instructions into IR is time-consuming. For example,
+REIL IR~\cite{dullien2009reil}, adopted in CacheS~\cite{236338}, has multiple
+transform processes, from binary to VEX IR, BAP IR, and finally REIL IR\@. 
+Also, IR increases the total number of instructions. For example, x86
+instruction \textit{test eax, eax} transfers into 18 REIL IR instructions. If we
+assume the time of symbolically executing grows as the number of instructions increase, the
+design of adopting IR layers can introduce large overhead.
+
+\vspace*{2pt}
+\textbf{Our Solution to Challenge C2:}
+We adopt the approach from QSYM~\cite{217563} and implement the symbolic execution
+directly on the top of x86 instructions. Table~\ref{scala:ir} shows that
+eliminating the IR layer can reduce the number of instructions executed during
+the analysis.
+
+\begin{table}%[ht]
+      \centering\small\footnotesize
+      \caption{The number of x86,  % instructions and the number of 
+             REIL IR, and VEX IR instructions on the traces of crypto programs.}
+      \label{scala:ir}
+\vspace*{-1pt}
+      \resizebox{\columnwidth}{!}{%
+
+            \begin{tabular}{cccc}
+                  \hline
+                                    & \begin{tabular}[c]{@{}c@{}}Number of\\ x86 Instructions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Number of\\ VEX IR\end{tabular} & \begin{tabular}[c]{@{}c@{}}Number of\\ REIL IR\end{tabular} \\ \hline
+                  AES OpenSSL 0.9.7 & $1,704$                   & $23,938$ (15x)            & $62,045$ (36x)            \\
+                  DES OpenSSL 0.9.7 & $2,976$                   & $41,897$ (15x)            & $100,365$ (33x)           \\
+                  RSA OpenSSL 0.9.7 & $1.6*10^7$                & $2.4*10^8$ (15x)          & $5.9*10^8$ (37x)          \\
+                  RSA mbedTLS 2.5  & $2.2*10^7$                & $3.1*10^8$ (15x)          & $8.6*10^8$  (39x)         \\ \hline
+            \end{tabular}
+      }
+\end{table}
+
+\subsection{Constraint Solving}
+As discussed in \S\ref{side-channel:condition}, the problem of identifying
+side-channels can be reduced to the question below.
+
+\begin{quote}
+      \textit{Can we find two different input variables $k_1, k_2 \in K$ that
+            satisfy the formula $f_a(k_1) \neq f_a(k_2)$?}
+\end{quote}
+
+Existing approach relies on satisfiability modulo theories (SMT) solvers (e.g,
+Z3~\cite{DeMoura:2008:ZES:1792734.1792766}) to find satisfying $k_1$ and $k_2$.
+We argue that while it is a universal approach to solving constraints with SMT
+solvers, for constraints with the above formats, using custom heuristics and
+testing is much more efficient in practice. Constraint solving is a decision
+problem expressed in logic formulas. SMT solvers transfer the inputted SMT
+formula into the boolean conjunctive normal form (CNF) and feed it into the
+internal boolean satisfiability problem (SAT) solver. The translation process,
+called ``bit blasting'', is time-consuming. Also, as the SAT problem is a
+well-known NP-complete problem, it is also hard to deal when it comes to
+realistic uses with huge formulas. Despite the rapid development of SMT solvers
+in recent years, constraint solving remains one of the obstacles to achieve the
+scalability for real-world cryptosystems.
+
+\vspace*{2pt}
+\textbf{Our Solution to Challenge C3:}
+Instead of feeding the formula $f_a(k_1) \neq f_a(k_2)$ into a SMT solver, we
+just randomly pick up $k_1, k_2 \in K$ and test them if they can satisfy the
+formula. Our solution is based on the following intuition. For most combination
+of $(k_{1}, k_{2} )$, the formula $f_a(k_1) \neq f_a(k_2)$ holds. As long as
+$f_a$ is not a constant function, such $k_1, k_2$ must exist. For example,
+suppose each time we only have 5\% chance to find such $k_1, k_2$, then after we
+test with different input combination with 100 times, we have $1 -
+(1-0.05)^{100} = 99.6\%$ chance find such $k_1, k_2$. Such random algorithms
+work well for our problem.
 \section{Evaluation}

### 2021-02-15 Chapter-4/Chapter-4.tex
init
add

--- 2021-02-14 Chapter-2/Chapter-2.tex
@@
 
-\chapter{Background}
+\chapter{Precise Analysis on Single-trace Attacks}
 
-\section{Address-based Side-channel Attacks}
+\section{Introduction}
+Side channels are ubiquitous in modern computer systems as sensitive
+information can leak through many mechanisms such as power,
+electromagnetic radiation, and even
+sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}.
+Among them, software side-channel attacks, such as cache attacks, memory page
+attacks, and controlled-channel attacks, are especially problematic as they do not require physical proximity~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}. These
+attacks arises from shared micro-architectural components in a computer processor.
+By observing inadvertent interactions between two programs, attackers can infer program
+execution flows that manipulate secrets and guess secrets such as encryption
+keys~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.
 
-\section{Information Theory}
+%% to deal with side channels, we can protect or detect them and detection is better
+%%arious countermeasures have been proposed to defend against software-based
+%%side-channel attacks. Hardware-level solutions, such as reducing shared
+%%resources, adopting oblivious RAM, and using transnational
+%%memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need new
+%%hardware features and changes in modern complex computer systems, which are
+%%impractical and hard to adopt in reality. Therefore, a promising and
+%%universal direction is software countermeasures, detecting and eliminating
+%%side-channel vulnerabilities from code base.
 
-\section{Binary Analysis}
+Many side-channel attacks originate
+in two code patterns: data flow from secrets to load
+addresses and data flow from secrets to branch conditions. We refer to them as
+secret-dependent data accesses and control flows, respectively.
+
+Recent work~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946}
+can detect many side-channel vulnerabilities. For example,
+DATA~\cite{217537} reports 2,248 potential leakage sites for the RSA
+implementation in OpenSSL 1.1.0f\@. 
+Further analysis shows 1,510 leaks can be dismissed. But that
+leaves 460 data-access leaks and 278 control-flow leaks. 
+Many of these vulnerabilities have not been fixed by developers for a variety of reasons.
+First, some vulnerable implementations perform better. For example,
+RSA implementations usually adopt the CRT optimization,
+which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}.
+Second, fixing vulnerabilities can introduce new 
+weaknesses.
+Third, most vulnerabilities pose a negligible risk. 
+Although some vulnerabilities result in the key being 
+entirely compromised~\cite{184415, aumuller2002fault}, 
+many others are less
+severe in reality. Therefore, we need a proper quantification metric to 
+assess the sensitivity of side-channel vulnerabilities,
+so a developer can efficiently triage them.
+
+Previous work~\cite{182946,5207642} can identify numerous leakages or even provide an upper bound on the amount of leakage, which is useful to verify that an implementation is secure if it incurs zero leakage.
+However, these techniques cannot quantify the severity of a leak because they over approximate the leakage. For example, CacheAudit~\cite{182946} 
+reports that the upper-bound leakage of AES-128 exceeds the original key size.
+Besides, existing side-channel quantification work~\cite{182946,5207642} assumes an attacker runs the target program multiple times with different
+input secrets and calculates an ``average'' estimation, which is different from real attack scenarios when the secret that an attacker wants to retrieve is fixed.
+As a consequence, those results are less useful to assess the severity level of each leakage site.
+
+To overcome these limitations, we propose a novel method to quantify information 
+leakage precisely. We quantify the number of bits that can leak during a real 
+execution and define the amount of leaked information as the cardinality of 
+possible secrets based on an attacker's observation. Before an attack, an adversary has a large but finite input space. 
+Whenever the adversary observes a leakage site, they can eliminate some impossible 
+inputs and reduce the input space's size.
+In an extreme case, if the input space's size reduces to one, an adversary has determined the input, which means all secret information (e.g., the entire secret key) is
+leaked. By counting the number of inputs~\cite{10.1007/11499107_24}, we can quantify the information leakage precisely.
+We use symbolic execution to generate constraints to model the relation 
+between the original sensitive input and an attacker's observations. 
+Symbolic execution provides fine-grained information, but it is expensive
+to compute. Therefore, prior symbolic
+execution work~\cite{203878,236338,Brotzman19Casym} either analyzes only
+small programs or applies domain knowledge~\cite{203878} to simplify the analysis. We
+examine the bottleneck of the trace-oriented symbolic execution and optimize it
+to work for real-world crypto-systems.
+
+We have implemented the proposed technique in a tool called \tool{} and demonstrated 
+it on real-world crypto libraries, including OpenSSL, 
+mbedTLS, Libgcrypt, and Monocypher.
+We collect execution traces of these libraries and apply 
+symbolic execution to each instruction. We model
+each side-channel leak as a logic formula. These
+formulas precisely model side-channel vulnerabilities. 
+Then we use the conjunction of those formulas to model the 
+leaks at a statement that appears in different location in
+the execution trace file (e.g., leaks inside a loop).
+Finally, we introduce a Monte Carlo sampling method to estimate 
+the information leakage. 
+The experimental results confirm
+that \tool{} precisely identifies previously known vulnerabilities and 
+reports how much information is leaked and which byte in the original sensitive 
+buffer is leaked. We also test \tool{} on side-channel-free algorithms. 
+\tool{} produces no false positives.
+The result also shows the newer version of crypto libraries leak less information 
+than earlier versions.
+\tool{} also discovers new vulnerabilities. With the help of \tool{}, 
+we confirm that some of these vulnerabilities are severe.
+
+%Based on the fixed attack target, we classify the software-based side-channel
+%vulnerabilities into two categories: 1.\textit{secret-dependent control-flow
+%transfers} and 2.\textit{secret-dependent data accesses} and model them with
+%math formulas which constrain the value of sensitive information. We quantify
+%the amount of leaked information as the number of possible solutions that are
+%reduced after applying each constrains.
+
+%Our method can identify and quantify address-based sensitive information
+%leakage sites in real-world applications automatically. Adversaries can exploit
+%different control-flow transfers and data-access patterns when the program
+%processes different sensitive data. We refer them as the potential information
+%leakage sites. Our tool can discover and estimate those potential information
+%leakage sites as well as how many bits they can leak. We are also able to
+%report precisely how many bits can be leaked in total if an attacker observes
+%more than one site. We run symbolic execution on execution traces. We model
+%each side-channel leakage as a math formula. The sensitive input is divided
+%into several independent bytes and each byte is regarded as a unique symbol.
+%Those formulas can precisely model every the side-channel vulnerability. In
+%other words, if the application has a different sensitive input but still
+%satisfies the formula, the code can still leak the same information.  
+%Those information leakage sites may spread in the whole program and their
+%leakages may not be dependent. Simply adding them up can only get a coarse
+%upper bound estimate. In order to accurately calculate the total information
+%leakage, we must know the dependent relationships among those multiple leakages
+%sites. Therefore, we introduce a monte carlo sampling method to estimate the
+%total information leakage.
+
+In summary, we make the following contributions:
+
+\begin{itemize}
+      \item We propose a novel method that can quantify fine-grained leaked
+            information from side-channel vulnerabilities that result from actual attack
+            scenarios. Our approach differs from previous ones in that we
+            model real attack scenarios for one execution. 
+            We model the information quantification problem as a counting problem 
+            and use a Monte Carlo sampling method to estimate the information leakage.
+
+      \item We implement the method into a tool and apply it
+            to several pieces of real software. \tool{} successfully identifies
+            previous unknown and known side-channel vulnerabilities and calculates the corresponding information leakage. 
+            Our results are useful in practice.
+            The leakage estimates and the corresponding trigger inputs can 
+            help developers to triage and fix the vulnerabilities.
+\end{itemize}
+
+\section{Threat Model}
+
+We assume that an attacker shares the same hardware platform with the target.
+The attacker attempts to retrieve sensitive information through address-based
+side-channel attacks. The attacker has no direct access to the target's memory or cache,
+but it can probe its memory or cache at each program point. In reality, the
+attacker will face many possible obstacles such as the noisy observations 
+of the memory or cache. However, for this project, we assume
+the attacker has noise-free observations as in previous work~\cite{203878,182946,Brotzman19Casym}. 
+The threat model captures most cache-based and address-based side-channel attacks. 
+We only consider deterministic programs and assume an attacker 
+has access to the source code or binary executable of the target program.
+
+\section{Quantification}
+
+In this section, we discuss how \tool{} quantifies the amount of leaked
+information. We first present the limitation of existing quantification metrics.
+Then, we introduce our model, the mathematical notation used in the
+paper, and our method.
+
+\subsection{Problem Setting}
+Existing static side-channel quantification
+works~\cite{182946,Wichelmann:2018:MFF:3274694.3274741,zhang2010sidebuster,bang2016string} define information
+leakage using max entropy or Shannon entropy.  If zero bits of
+information leakage is reported, a program is secure.
+However, when a tool using these metrics reports leakage, it is the ``average'' leakage.
+In a real attack, the leakage could be dramatically different.
+
+ \begin{figure}[h!]
+    \vspace*{-5pt}
+    \centering
+    \begin{lstlisting}[xleftmargin=.03\textwidth,xrightmargin=.01\textwidth]
+char key[9] = input();
+if(strcmp(key, "password"))   // leakage site C
+    pass();                   // branch 1
+else
+    fail();                   // branch 2
+\end{lstlisting}
+\vspace*{-10pt}
+    \caption{A dummy password checker}
+    \label{fig:password-checker}
+\vspace*{-5pt}
+\end{figure}
+
+Consider a password checker sketched in Figure~\ref{fig:password-checker}.
+The password checker takes an 8-byte char array (exclude \textsf{NULL} character) 
+and checks if the input is the correct password. If an attacker uses a side-channel attack to determine that the code executes branch
+$\{{1\}}$, they can infer the password equals to
+``password'', in which case the attacker retrieves the full password.
+Therefore, the total leaked information should be 64 bits, which equals to the
+size of the original sensitive input when the code executes branch
+$1$.
+
+However, prior static approaches cannot precisely capture the amount of leakage. According to the definition of Shannon entropy, the leakage will be
+$\frac{1}{2^{64}}*\log_{2}\frac{1}{2^{64}} + \frac{2^{64}-1}{2^{64}}
+*\log_{2}\frac{2^{64}-1}{2^{64}} \approx 0$ bits. Max-entropy is defined from the
+number of possible observations. Because the program has two
+branches, tools based on max-entropy will report the code has a $\log_2{2} = 1$
+bit leakage.
+
+\section{Approximate Model Counting}
+\label{MCreasons}
+%According to
+%Definition~\ref{def} introduced in \S\ref{sec:trace-qif},
+%the problem of quantifying the amount of leaked information can be reduced to
+%the problem of computing the number of items in $K^o$. However, we find that while
+%there are various propositional model counters (e.g., \#SAT), they are not
+%sufficient scalable for production cryptosystem analysis.
+%there is no open source modulo theories counter (\#SMT) available.
+
+%One straightforward method approximating the number of solutions is based on Monte Carlo
+%sampling. However, the number of satisfying values could be exponentially small.
+%Consider the formula $f_i\equiv{k_1} = 1\land{k_2} = 2\land{k_3} = 3\land{k_4} =
+%4$, where $k_1$, $k_2$, $k_3$, and $k_4$ each represents one byte in the
+%original sensitive input buffer, there is only one satisfying solution of total
+%$2^{32}$ possible values, which requires exponentially many samples to get a
+%tight bound. Monte Carlo method also suffers from the curse of dimensionality.
+%For example, the length of an RSA private key can be as long as 4096 bits. If we
+%take each byte (8 bits) in the original buffer as one symbol, the formula can
+%have as many as 512 symbols.
+
+%\vspace*{2pt}
+%\textbf{Our Solution to Challenge C3:}
+%We adopt multiple-step Monte Carlo sampling methods to count the number of
+%possible inputs that satisfy the logic formula groups. The key idea is to split
+%those constraints into several small formulas and sample them independently.
+%We will introduce the method in the following subsection.
+
+%\subsection{Information Leakage Estimation}
+
+\newcommand{\addr}[1]{{l}_{#1}}
+\renewcommand{\addr}[1]{{\gamma}_{#1}}
+\renewcommand{\addr}[1]{{\zeta}_{#1}}
+\renewcommand{\addr}[1]{{\xi}_{#1}}
+
+In this section, we present the algorithm to calculate the information leakage
+based on Definition~\ref{def} (\S\ref{sec:trace-qif}), answering to
+\textbf{Challenge C3}.
+
+\subsection{Problem Statement}
+For each leakage site, we model it with a constraint using the
+method presented in~\S\ref{side-channel:condition}. Suppose the address of the
+leakage site is $\addr{i}$, we use $c_{\addr{i}}$ to denote the constraint
+that models its side-channel leakage. 
+%For
+%multiple leakage sites, we take the conjunction of those constraints to
+%represent those leakage sites.
+
+According to the Definition~\ref{def}, to calculate the amount of leaked
+information, the key is to calculate the cardinality
+of $K^o$. Suppose an attacker can observe $n$ leakage sites, and each leakage
+site has the following constraints: $c_{\addr{1}}, c_{\addr{2}}, \ldots,
+c_{\addr{n}}$ respectively. The total leakage can be calculated from the constraint
+$c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}}) = c_{\addr{1}} \land c_{\addr{2}}
+\land \ldots \land c_{\addr{n}}$. 
+%%The problem of estimating the total leaked
+%%information can be reduced to the problem of counting the number of different
+%%solutions that satisfies the constraint
+%%$c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}})$. 
+A simple method is to pick elements $k$ from $K$ and check if an
+element is also contained in $K^o$. Assume $q$ elements satisfy this condition. In
+expectation, we can use $\frac{k}{q}$ to approximate the value of
+$\frac{|K|}{|K^o|}$.
+
+However, the above sampling method fails in practice due to the following two problems:
+
+\begin{enumerate}
+      \item The curse of dimensionality problem. $c_t({\addr{1}},\ldots,{\addr{n}})$ is
+            the conjunction of many constraints. Therefore, the input variables
+            of each constraints will also be the input variables of the
+            $c_t({\addr{1}},\ldots,{\addr{n}})$. The sampling method fails
+            as $n$ grows.
+
+            %For example, if the program has $2$ input whose size is 
+            %one byte, the whole search space is a $256^2$ cube. If we want
+            %the sampling distance between each point equals to $d$, we need
+            %$256^2d$ points. If the program has $10$ byte input, we need
+            %$256^{10}d$ points if we still we want the sampling distance equals
+            %to $d$.
+
+      \item The number of satisfying assignments could be exponentially small.
+            According to Chernoff bound, we need exponentially many samples to
+            get a tight bound. 
+            %On an extreme situation, if the constraint only
+            %has one unique satisfying solution, the simple Monte Carlo method
+            %cannot find the satisfying assignment even after sampling many
+            %points.
+\end{enumerate}
+
+However, despite above two problems, we also observe two characteristics of the
+problem:
+\begin{enumerate}
+      \item $c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}})$ is the conjunction of
+            several short constraints $c_{\addr{i}}$. The set containing the
+            input variables of $c_{\addr{i}}$ is the subset of the input
+            variables of $c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}})$. Some
+            constraints have completely different input variables from other
+            constraints.
+
+            \item Each time when we sample $c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}})$
+            with a point, the sampling result is \emph{Satisfied} or not \emph{Not Satisfied}.
+            The outcome does not depend on the result of 
+            previous experiments. Also, as the amount of leaked information is calculated
+            by a $\log$ function, we need not exactly count the number of solutions for 
+            a given constraint.
+            %\item For each constraint $F(C_{{addr}_i})$, the satisfying assignments
+            %are close to each other, which means if we find one satisfying assignment, we 
+            %are more likely to find other satisfying assignments nearby than randomly
+            %pick one point in the whole searching space.
+
+\end{enumerate}
+
+In regard to the above problems, we present our methods. First, we split
+$c_t(\addr{1},\addr{2},\ldots,\addr{n})$ into several independent constraint
+groups. After that, we run a multi-step sampling method for each constraint.
+
+\subsection{Maximum Independent Partition}
+
+For a constraint $c_{\addr{i}}$, we define function $\pi$, which maps the
+constraint into a set of different input symbols. For example, $\pi(k1 + k2 >
+128) = \{k1, k2\}$.
+
+\begin{mydef}[]
+      \label{independentC}
+      Given two constraints $c_m$ and $c_n$, we call them independent iff
+      $$\pi(c_m) \cap \pi(c_n) = \emptyset$$
+\end{mydef}
+
+Based on the Definition~\ref{independentC}, we can split the constraint
+$c_t(\addr{1},\addr{2},\ldots,\addr{n})$ into several independent constraints.
+There are many partitions. For our project, we are interested in the following
+one.
+
+\begin{mydef}\label{Goodpartition}
+      For the constraint $c_t(\addr{1},\addr{2},\ldots,\addr{n})$,
+      we call the constraint group
+      $g_{1}, g_{2}, \ldots, g_{m}$
+      the maximum independent partition of $c_t(\addr{1},\addr{2},\ldots,\addr{n})$ iff
+      \begin{enumerate}
+            \item $g_{1} \land g_{2} \land \ldots \land g_{m} = c_t(\addr{1},\addr{2},\ldots,\addr{n})$
+            \item $\forall i, j \in \{1, \ldots, m\} \quad \textrm{and} \quad
+                        i \neq j,\quad\pi(g_{i}) \cap \pi(g_{j}) = \emptyset $
+            \item For any other partitions  $h_{1}, h_{2}, \ldots, h_{m'}$ satisfy 1) and
+                  2), $m \geq m'$
+      \end{enumerate}
+
+\end{mydef}
+
+The reason we want a good partition of constraints is we want to reduce
+the dimensions. For example,
+a good partition of $F: ({k_1} = 1)\land({k_2} = 2)\land({k_3} > 4)\land({k_3} - {k_4} > 10)$ would be
+$g_{1}: ({k_1} = 1)\quad g_{2}: ({k_2} = 2)\quad g_{3}: ({k_3} > 4) \land
+({k_3} - {k_4} > 10)$  
+We can sample each constraint independently and combine them
+with Theorem~\ref{IndependentConstraint}.
+
+\begin{theorem}
+      \label{IndependentConstraint}
+      Let $g_{1}, g_{2}, \ldots, g_{m}$ be a maximum independent partition of
+      $c_t(\addr{1},\addr{2},\ldots,\addr{n})$.
+      $K_c$ is the input set that satisfies constraint $c$. We have the following
+      equation in regard to the size of $K_c$
+      $$|K_{c_t(\addr{1},\addr{2},\ldots,\addr{n})}| = |K_{g_{1}}|*|K_{g_{2}}|*\ldots*|K_{g_{n}}|$$
+\end{theorem}
+\vspace{-3pt}
+With Theorem~\ref{IndependentConstraint}, we change the problem of
+counting the number of solutions to a complicated constraint in a high-dimension
+space into counting solutions to several small constraints. We compute the
+maximum independent partition by iterating each $\addr{i}$ and applying the function
+$\pi$ over the constraint $\addr{i}$.
+
+%% We apply the following
+%% algorithm~\ref{algo:max-inde} to get the Maximum Independent Partition of the
+%% $c_t(\addr{1},\addr{2},\ldots,\addr{n})$.
+
+%% \IncMargin{1em}
+%% \begin{algorithm}[h]
+%%       \DontPrintSemicolon
+%%       \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
+%%       \Input{$c_t(\addr{1},\addr{2},\ldots,\addr{n}) = c_{\addr{1}} \land c_{\addr{2}} \land \ldots \land c_{\addr{m}}$}
+%%       \Output{The Maximum Independent Partition of $G = \{g_{1}, g_{2}  , \ldots,  g_{m} \}$ }
+%%       \For{$i\leftarrow 1$ \KwTo $n$}
+%%       {
+%%             $S_{c_i}$ $\leftarrow$ $\pi(c_{\addr{i}})$ \;
+%%             \For{$g_{i} \in G$}
+%%             {
+%%                   $S_{g_i}$ $\leftarrow$ $\pi(g_{i})$ \;
+%%                   $S$ $\leftarrow$ $S_{C_i} \cap S_{G_i}$  \;
+%%                   \If{$S \neq \emptyset$}
+%%                   {
+%%                         $g_{i} \leftarrow g_{i} \land g_{\addr{i}}$ \;
+%%                         \textbf{break} \;
+%%                   }
+%%                   Insert $c_{\addr{i}}$ to $G$
+%%             }
+%%       }
+%%       \caption{The Maximum Independent Partition}
+%%       \label{algo:max-inde}
+%% \end{algorithm}
+%% \DecMargin{1em}
+
+\subsection{Multiple-step Monte Carlo Sampling}
+
+After we split those constraints into several small constraints, we count the
+number of solutions for each constraint. Even though the dimension has been
+significantly reduced by the previous step, this is still a \#P problem. 
+%For our
+%project, we apply the approximate counting instead of exact counting for two
+%reasons. First, we do not need to have a very precise result of the exact number
+%of total solutions since the information is defined with a logarithmic function.
+%We do not need to distinguish between constraints having $10^{10}$ or $10^{10} +
+%10$ solutions; they are very close to after taking logarithmic. Second, the
+%precise model counting approaches, like Davis-Putnam-Logemann-Loveland (DPLL)
+%search, have difficulty scaling up to large problem sizes.
+
+We apply the ``counting by sampling'' method. For
+the constraint $g_{i}= c_{i_1} \land c_{i_2} \land ,\ldots, \land c_{i_j} \land
+,\ldots, \land c_{i_m}$, if the solution satisfies $g_{i}$, it should also
+satisfy any constraint from $c_{i_1}$ to $c_{i_m}$. In other words, $K_{c_gi}$
+should be the subset of $K_{c_1}$, $K_{c_2}$, \ldots , $K_{c_m}$. We notice that
+$c_i$ usually has fewer inputs than $g_{i}$. For example, if
+$c_{i_j}$ has only one 8-bit input variable, we can find the exact solution set
+$K_{c_{i_j}}$ of $c_{i_j}$ by trying every possible 256 solution. After that,
+we only generate random input numbers for the other input variables in
+constraint $g_{i}$. With this simple yet effective trick, we reduce the number of input
+while still ensuring accuracy.
+
+%% the algorithm
+%\IncMargin{1em}
+%\begin{algorithm}
+%\SetAlgoLined
+%\DontPrintSemicolon
+
+%\KwIn{{The constraint $G_{i}= C_{i_1} \land C_{i_2}
+%\land \ldots \land C_{i_m}$}}    
+%\KwOut{{The number of assignments that satisfy $G_{i}$ $|K_{G_{i}}|$}}
+
+%\SetKwProg{RW}{RandomWalk}{}{}
+%\SetKwProg{MM}{MetropolisMove}{}{} 
+%$n$: the number of sampling times \;
+%$P$: a probability generator \;
+%$k$: the input assignment \;
+%$n_{s}$: the number of satisfying assignments \;
+%$\#k$: the satisfying number of k \fixme{this number is not used syntactically} \; 
+%Initialization: \;
+%$\#{k_0}$ $\leftarrow$ $\sum_{j=1}^{m}C_{i_j}(k_0)$ \;
+%\For{$t\leftarrow 1$ \KwTo $n$} {
+%      $p$ $\leftarrow$ $P$ \;
+%      \If{$p \geq 0.5$}
+%      {
+%        $v$ $\leftarrow$ \RW{$v$} {}
+%      }
+%      \Else{
+%            $v$ $\leftarrow$ \MM{$v$} {}
+%      }
+%      \If{$v$ satisfies $G_{i}$}
+%      {$n_{s}$ $\leftarrow$ $n_{s} + 1$}
+%}
+%$|K_{G_{i}}|$ $\leftarrow$ $n_s|K| / n$
+%\caption{Metropolis Sampling}
+%\end{algorithm}
+%\DecMargin{1em}
+
+\subsection{Error Estimation}
+\label{sssec:errest}
+Our result has a probabilistic guarantee that the error of the estimated amount of leaked 
+information is less than 1 bit under the Central Limit Theorem (CLT) and uncertainty
+propagation theorem.
+
+Let $n$ be the number of samples and $n_s$ be the number of samples that satisfy
+the constraint $C$. Then we get $\hat{p} = \frac{n_s}{n}$. If we repeat the
+experiment multiple times, each time we get a $\hat{p}$. As each
+$\hat{p}$ is independent and identically distributed, according to the central limit
+theorem, the mean value should follow the normal distribution
+$ \frac{\bar{p}-E(p)}{\sigma\sqrt{n}} \rightarrow N(0,1) $. Here $E(p)$ is the
+mean value of $p$, and $\sigma$ is the standard variance of $p$. If we use the
+observed value $\hat{p}$ to calculate the standard deviation, we can claim that
+we have 95\%\footnote{For a normal distribution, 95\% of variable $\Delta p$ fall within two sigmas of the mean.} 
+confidence that the error $\Delta p= \bar{p} - E(p)$ falls in the interval:
+$$ |\Delta p| \leq 1.96\sqrt{\frac{ \hat{p} (1- \hat{p} )}{n}}$$
+
+Since we use $L = \log_{2}p$ to estimate the amount of leaked information, we
+can have the following error propagation formula $\Delta L = \frac{\Delta
+p}{p\ln2}$ by taking the derivative from Definition~\ref{def}. For \tool, we want the error of estimated leaked
+information ($\Delta L$) to be less than 1 bit. So we get $\frac{\Delta
+p}{p\ln2} \leq 1$. Therefore, as long as $ n \geq \frac{1.96^2(1-p)}{p(\ln2)^2}$, we have
+95\% confidence that the error of estimated leaked information is less than 1 bit.
+During the simulation, if $n$ and $p$ satisfy this inequality, the Monte Carlo
+simulation will terminate.

### 2021-02-15 Chapter-1/Chapter-1.tex
init
update

@@
 Side channels are inevitable in modern computer systems as the sensitive
-information may be leaked through many kinds of inadvertent behaviors, such as power,
-electromagnetic radiation, and even
+information may be leaked through many kinds of inadvertent behaviors, such as power, electromagnetic radiation, and even
 sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}.
-Among them, software-based side channel attacks, such as cache attacks, memory page
-attacks, and controlled-channel attacks, are especially common and have been
-studied for
-years~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}. These
+Among them, address-based side channel attacks, such as cache attacks, memory page attacks, and controlled-channel attacks, are especially common and have been studied for years~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}.
+These
 attacks result from vulnerable software and shared hardware components.
@@
 
-\section{Side-channel}
+In this chapter, we first introduce two code patterns that can be exploited to retrieve sensitive information.
+After that, we discuss some common attacks and corresponding defense strategies.
+The limitations of existing work motivate the research in the dissertation.
+Finally, we summarize the contributions of the dissertation.
 
-\subsection{Attacks}
+\section{Side-channel Attacks}
+\begin{figure}[tbp]
+\begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
+int secret[32];
+...
+while(i>0){
+    r = (r * r) % n;
+    if(secret[--i] == 1)
+        r = (r * x) % n;   
+}
+\end{lstlisting}
+\caption{Secret-dependent control-flow transfers}
+\label{fig:secret:cf}
+\end{figure}
 
-\subsection{Defense}
+\begin{figure}[tbp]
+\begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
+static char FSb[256] = {...}
+... 
+uint32_t a = *RK++ ^ \ 
+(FSb[(secret)) ^
+(FSb[(secret >> 8)] << 8 ) ^
+(FSb[(secret >>16)] << 16 ) ^
+(FSb[(secret >>24)] << 24 );
+...
+\end{lstlisting}
+\caption{Secret-dependent data accesses}
+\label{fig:secret:da}
+\end{figure}
+
+\section{Current Defense}
 
@@
 
+\section{Contribution}
+
 \section{Dissertation Organization}

### 2021-02-16 Chapter-1/Chapter-1.tex
update

@@
 
-\section{Side-channel Attacks}
-\begin{figure}[tbp]
+\section{Address-based Side-channel Attacks}
+Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses.
+Most of the attack allows the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim.
+As a result, while the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.
+
+Cache channels rely on the time difference between cache misses and cache hits.
+A cache channel works when the victim program and the attacker's program shares some sized chunks like cache lines or cache sets.
+Recent studies shows that an attacker can even observe the address access at a finer granularity (e.g., CacheBleed).
+Page-level side-channels allow attackers observe the memory access at the granularity of memory pages.
+
+In this dissertation, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs).
+To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.
+
+When we examine those side-channel attacks, many of them stem from the two code patterns, \emph{secret-dependent control-flow transfers} and \emph{secret-dependent data accesses}.
+\begin{figure}[h]
 \begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
@@
 
-\begin{figure}[tbp]
+Secret-dependent control-flow transfers happen when the value of secret can affect which branch the code executes.
+Figure~\ref{fig:secret:cf} shows an example.
+Depending on the value of \textsf{secret}, the code may or may not execute the code at line 6.
+As attackers, they can retrieve some information based on the execution control-flow.
+
+\begin{figure}[h]
 \begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
@@
 
-\section{Current Defense}
+Secret-dependent data accesses happen when the value of the secret can affect which memory cell the code reads or writes.
+Figure~\ref{fig:secret:da} shows an example.
+\textsf{FSb} is an array.
+Depending on the value of \textsf{secret}, the code may read or write different item in the array.
+
+\section{Defense}
 

### 2021-02-16 Chapter-1/Chapter-1.tex
update

@@
 \textsf{FSb} is an array.
-Depending on the value of \textsf{secret}, the code may read or write different item in the array.
+Depending on the value of \textsf{secret}, the code may read or write different items in the array.
 
 \section{Defense}
+Both hardware~\cite{Page2005PartitionedCA,
+Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
+236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
+brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
+been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
+accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
+architecture~\cite{tiwari2011crafting}, require changes to complex processors and are complex to adopt. On the contrary, software approaches are
+usually easy to implement. Coppens et
+al.~\cite{Coppens:2009:PMT:1607723.1608124} uses a compiler
+to eliminate key-dependent control-flow transfers. Crane et
+al.~\cite{crane2015thwarting} mitigated side-channels by randomizing software.
+As for crypto libraries, the basic idea is to eliminate key-dependent
+control-flow transfers and data accesses. Common approaches include
+bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
+control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.
 
@@
 find plenty of side-channel vulnerabilities. For example,
-DATA~\cite{217537} reports 2,246 potential leakage site for the RSA
+DATA~\cite{217537} reports 2,246 potential leakage sites for the RSA
 implementation in OpenSSL\@. 

### 2021-02-16 Chapter-1/Chapter-1.tex
update

@@
 
-\section{Address-based Side-channel Attacks}
+\section{Address-based Side-channel}
+\subsection{Attack}
 Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses.
@@
 
-\section{Defense}
+\subsection{Defense}
+
 Both hardware~\cite{Page2005PartitionedCA,
@@
 accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
-architecture~\cite{tiwari2011crafting}, require changes to complex processors and are complex to adopt. On the contrary, software approaches are
-usually easy to implement. Coppens et
+architecture~\cite{tiwari2011crafting}, require changes to complex processors and are complex to adopt.
+
+On the contrary, software approaches are
+usually easy to implement. By removing the above two kinds of code patterns, developers protect their 
+code from a seris of side-channel attacks.
+Coppens et
 al.~\cite{Coppens:2009:PMT:1607723.1608124} uses a compiler
@@
 
-\section{Binary Analysis}
-Binary analysis is the process of automatically inferring program behaviors from
-the binary executable.
-It plays a critical role from a security viewpoint. For many programs, like malware, Commercial off-the-shelf (COTS) application, source code are typically not
-available. Besides, some low-level information, including memory accesses and cache
-accesses, is only available on the binary code level. As many side-channel vulnerabilities
-are typically low-level problem, we believe binary analysis are more suitable than
-source code level analysis.
-
-Binary analysis can be categorized into two groups depending when the analysis is
-launched.
-\begin{itemize}
-    \item Static Analysis infer analyzing the binary program without running it. Previous studies focus on addressing several open problems, including identifying
-    function entry points~\cite{184521, Wang17a}, resolving indirect jumps, disambiguating code and data and solving alias memory address. Static analysis
-    lacks the run-time information, which may lead to false positives and false 
-    negatives. However, static analysis typically can have better coverage as it can
-    reason about every possible execution paths.
-    \item Dynamic Analysis involving analyzing a binary code as it executes. Tools
-    that perform dynamic analysis usually need to instrument the binary code.  
-    Although dynamic analysis can only reason only one execution path. It is usually more precise than static analysis.
-\end{itemize}
-
-In this dissertation, we detected side-channel vulnerabilities by trace-based analysis.
-It consists of two steps. The first step, called online trace logging, collect run-time
-information for the targeted program under the dynamic binary instrumentation (DBI)
-to collect necessary information. The second step, called offline analysis, run
-several analysis (e.g., taint analysis, symbolic analysis) on the top of traces.
-
-Existing binary analysis frameworks, like Angr, BAP and Bitblaze combine both static
-and dynamic analyses, are applicable to a series of tasks. However, those frameworks
-are not suitable for the following reasons. 
-\begin{itemize}
-    \item Existing binary analysis frameworks transfer the machine code into
-    architecture-independent intermediate representatives (IR) and then run the
-    analysis. The IR design, which simplify the implementation and support multiple
-    architectures, introduces imprecision to the analysis results as well because some
-    information like cache accesses, control-flow transfers are lost during the IR
-    transformation.
-    \item Coverage is one of the concerns when they design the frameworks. 
-    As a result, they rely on constraint solvers to find different inputs that can
-    trigger different paths. As constraint solving is known for time-consuming. It is
-    one of the obstacles to make analyses salable.
-    However, we will show for many tasks, like binary similarity comparisons and side-channel vulnerability detection. We can
-    reduce the call to the solver just by fuzzing the formula. The design will
-    significantly reduce the overhead.
-\end{itemize}
-To solve the above problem, we propose Phoenix, a trace-oriented binary analysis
-framework. Phoenix is a dynamic binary analysis framework that provide several 
-functioning including dynamic symbolic execution engine, dynamic taint analysis
-engine, AST representation of X86 and binding for STP solvers. It run 
-execution on the top X86 instructions and symbolically reason the program behaviours.
-Our preliminary results show that Phoenix has a better performance compared to 
-many existing works, which makes it scalable to real-world applications.
-
 \section{Contribution}

### 2021-02-16 Chapter-2/Chapter-2.tex
update

@@
 As we can see, the channel have the unique output ($o \in O$) for every input ($k \in K$).
+
+\section{Binary Analysis}
+Binary analysis is the process of automatically inferring program behaviors from
+the binary executable.
+It plays a critical role from a security viewpoint. For many programs, like malware, Commercial off-the-shelf (COTS) application, source code are typically not
+available. Besides, some low-level information, including memory accesses and cache
+accesses, is only available on the binary code level. As many side-channel vulnerabilities
+are typically low-level problem, we believe binary analysis are more suitable than
+source code level analysis.
+
+Binary analysis can be categorized into two groups depending when the analysis is
+launched.
+\begin{itemize}
+    \item Static Analysis infer analyzing the binary program without running it. Previous studies focus on addressing several open problems, including identifying
+    function entry points~\cite{184521, Wang17a}, resolving indirect jumps, disambiguating code and data and solving alias memory address. Static analysis
+    lacks the run-time information, which may lead to false positives and false 
+    negatives. However, static analysis typically can have better coverage as it can
+    reason about every possible execution paths.
+    \item Dynamic Analysis involving analyzing a binary code as it executes. Tools
+    that perform dynamic analysis usually need to instrument the binary code.  
+    Although dynamic analysis can only reason only one execution path. It is usually more precise than static analysis.
+\end{itemize}
+
+In this dissertation, we detected side-channel vulnerabilities by trace-based analysis.
+It consists of two steps. The first step, called online trace logging, collect run-time
+information for the targeted program under the dynamic binary instrumentation (DBI)
+to collect necessary information. The second step, called offline analysis, run
+several analysis (e.g., taint analysis, symbolic analysis) on the top of traces.
+
+Existing binary analysis frameworks, like Angr, BAP and Bitblaze combine both static
+and dynamic analyses, are applicable to a series of tasks. However, those frameworks
+are not suitable for the following reasons. 
+\begin{itemize}
+    \item Existing binary analysis frameworks transfer the machine code into
+    architecture-independent intermediate representatives (IR) and then run the
+    analysis. The IR design, which simplify the implementation and support multiple
+    architectures, introduces imprecision to the analysis results as well because some
+    information like cache accesses, control-flow transfers are lost during the IR
+    transformation.
+    \item Coverage is one of the concerns when they design the frameworks. 
+    As a result, they rely on constraint solvers to find different inputs that can
+    trigger different paths. As constraint solving is known for time-consuming. It is
+    one of the obstacles to make analyses salable.
+    However, we will show for many tasks, like binary similarity comparisons and side-channel vulnerability detection. We can
+    reduce the call to the solver just by fuzzing the formula. The design will
+    significantly reduce the overhead.
+\end{itemize}
+To solve the above problem, we propose Phoenix, a trace-oriented binary analysis
+framework. Phoenix is a dynamic binary analysis framework that provide several 
+functioning including dynamic symbolic execution engine, dynamic taint analysis
+engine, AST representation of X86 and binding for STP solvers. It run 
+execution on the top X86 instructions and symbolically reason the program behaviours.
+Our preliminary results show that Phoenix has a better performance compared to 
+many existing works, which makes it scalable to real-world applications.

### 2021-02-16 Chapter-1/Chapter-1.tex
update

@@
 
-\chapter{Introduction} \label{chapter1:introduction}
+\chapter{Introduction} \label{chapter1}
 
@@
 On the contrary, software approaches are
-usually easy to implement. By removing the above two kinds of code patterns, developers protect their 
-code from a seris of side-channel attacks.
-Coppens et
-al.~\cite{Coppens:2009:PMT:1607723.1608124} uses a compiler
-to eliminate key-dependent control-flow transfers. Crane et
-al.~\cite{crane2015thwarting} mitigated side-channels by randomizing software.
-As for crypto libraries, the basic idea is to eliminate key-dependent
-control-flow transfers and data accesses. Common approaches include
-bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
-control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.
+usually easy to implement. The basic idea is to eliminate key-dependent
+control-flow transfers and data accesses. By removing the above two kinds of code patterns, developers protect their 
+code from a series of side-channel attacks.
 
-Regarding the root cause of software-based side channel attacks, many of them originate
-from two specific circumstances: data flow from secrets to load
-addresses and data flow from secrets to branch conditions. We refer to them as
- secret-dependent memory-access and control-flow, respectively. A
-central problem is eliminating these two code patterns. 
-Recent
-works~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946},
-find plenty of side-channel vulnerabilities. For example,
-DATA~\cite{217537} reports 2,246 potential leakage sites for the RSA
-implementation in OpenSSL\@. 
-%After some inspections, 1,510 leakages are dismissed. But it
-%still leaves 460 data-access leakages and 278 control-flow leakages. 
-However, we find most of the reported vulnerabilities are not fixed because
-of the following reasons.
-First, many side-channels vulnerable implementations have better performance.
-Those vulnerabilities are well-known for years. For example,
-Symmetric encryptions like AES and DES still uses lookup tables (T-tables), which
-is fast but notoriously known to be vulnerable to side channels.
-As for asymmetric encryptions, most implementations of RSA, adopt the CRT optimization,
-which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}.
-Second, side-channels are numerous and it is hard to fix all these vulnerabilities,
-let alone the majority of them are negligible. 
-That is, some vulnerabilities can result in the key being 
-entirely compromised~\cite{184415, aumuller2002fault}, but many other vulnerabilities prove to be less
-severe in reality. Therefore, we need a proper quantification metric to 
-assess the sensitive level of side-channel vulnerabilities.
+However, it is still hard to apply software approaches in practice due to the following reasons.
 
-Previous attempts like static methods~\cite{182946,5207642}, usually with
-abstract interpretations, can give a leakage upper bound, which is useful to
-justify the implementation is secure if they report zero or little leakage.
-However, they cannot indicate how severe the leakage is because of the
-over-approximation method they apply. For example, CacheAudit~\cite{182946} reports that the upper
-bound leakage of AES-128 exceeds the original key size! The dynamic methods take
-another approach with a concrete input and run the program in a real
-environment. Although they are very precise in terms of actual leakages, no
-existing tool can precisely assess the severity of the vulnerabilities in production
-software.
+\begin{itemize}
+    \item It is hard to identify side-channel vulnerabilities in real-world software.
+In general, many side-channel vulnerabilities are low-level problems.
+Control-flows or memory accesses may not be side-channel vulnerabilities if they are independent of original secret inputs.
+Recent work can identify side-channel leakages.
+But those tools can only work on small programs or need to apply some domain knowledge to simplify the analysis.
+    \item Side-channel vulnerabilities are ubiquitous.
+While some vulnerabilities can result in the key being entirely compromised, many other vulnerabilities are hard to exploit.
+Moreover, some vulnerable implementations perform better.
+Recent work can identify thousands of leaked points, but most of them are not patched by developers because those leakages are either false positives or leaked very little information.
+\end{itemize}
 
-To overcome these limitations, we propose a novel method to quantify information
-leakages precisely. Unlike previous works that only consider the
-``average'' information leakage, we study the problem based on real attack
-scenarios. The average information leakage model assumes the target program has
-\emph{variable} or \emph{random} sensitive information as inputs when an attack is
-launched. However, for real-world attacks, an adversary may run the target
-problem with the \emph{fixed} unknown sensitive information
-as the input. Therefore, the previous threat model cannot model real attack
-scenarios. In contrast, our method is more precise and fine-grained. 
-We quantify
-the amount of leaked information as the cardinality of the set of possible
-inputs based on attackers' observations.
-Before an attack, an adversary has a large but finite input space. Every time
-when the adversary observes a leakage site, he can eliminate some potential
-inputs and reduce the size of the input space. The smaller the input space is,
-the more information is obtained. In an extreme case, if the size of the
-input space reduces to one, the adversary can uniquely determine the input, 
-which means all the secret information (e.g., the whole secret key) is
-leaked. By counting the number of distinct inputs, we can quantify the
-information leakage precisely.
-
-We use constraints generated from symbolic execution to model the relation 
-between the original sensitive input
-and the attacker's observations. Symbolic execution can
-provide fine-grained information but is usually believed to be an expensive
-operation in terms of performance. Therefore, existing dynamic symbolic
-execution works~\cite{203878,236338,Brotzman19Casym} either only analyze
-small programs or apply some domain knowledge~\cite{203878} to simplify the analysis. We
-systematically exam the bottleneck of the trace-oriented symbolic execution and optimize it
-to be scalable to real-world cryptosystems.
-
-We apply the above technique and build a tool called \tool{},
-%\footnote{CleverHans is a horse that can ``count''. Our tool uses an advanced
-%%method to count the number of leaked bits from side channels.} 
-to discover potential information leakage sites as well as estimate how
-many bits they can leak for each leakage site. 
-First, we collect dynamic execution traces for each target
-libraries and then run symbolic execution on each instruction. In this way, we model
-each side-channel leakage as a logic formula. The sensitive input is divided into
-several independent bytes, and each byte is regarded as a unique and free symbol. Those
-formulas can precisely model side-channel vulnerabilities. Then we use the conjunction
-of those formulas to model the same leaks in the source code but appears in the different location of
-the execution trace file (e.g., leakages inside a loop).
-Finally, we introduce Monte Carlo
-sampling method to estimate the single and combined information leakage.
-
-We apply \tool{} on both symmetric and asymmetric ciphers from real-world crypto
-libraries, including OpenSSL, mbed TLS and Monocypher\@. The experimental result confirms
-that \tool{} can precisely identify previously known vulnerabilities, report
-how much information is leaked and which byte in the original sensitive buffer
-is leaked. We also test \tool{} on side-channel free algorithms. \tool{} has no
-false positives.
-Although some of the analyzed crypto libraries have a number of
-side-channels, they actually leak very little information. Also, we also show the
-of widely deployed software countermeasures can mitigate side channels.
-\tool\ also discovers new vulnerabilities. With the help of \tool{}, we confirm
-that those vulnerabilities are severe.
-
-In summary, we make the following contributions:
+\section{Contribution}
+To address the above problems, we make the following contributions in this dissertations:
 
@@
     \item We propose a novel method that can quantify fine-grained leaked
-            information from side-channel vulnerabilities to match real attack
-            scenarios. Our method is different from previous ones in that we
-            model real attack scenarios more precisely, while the previous
-            research only models the ``average'' or ``random'' case. 
-            We transfer the information quantification problem into a counting
-            problem and use the Monte Carlo sampling method to estimate the
-            information leakage.
-            % compared to previous results and
-            %%   We model each side-channel vulnerabilities as math formulas %
-            %and mutiple side-channel vulnerabilities can be seen as the %
-            %conjunction of those formulas, which precisely models the % program
-            %semantics.
-
-      %%\item  Some initial results indicate the sampling
-      %%     method suffers from the curse of dimensionality problem. Therefore, we
-      %%      design a guided sampling method and provide the
-      %%      corresponding error estimate.
-
-      \item We implement the proposed method into a practical tool and apply it
-            on several real-world software. \tool{} successfully identifies
-            memory-related side-channel vulnerabilities and calculates the
-            corresponding information leakage. 
-            Our results are surprisingly different, much more useful in practice.
-            The information leakage results
-            provide detailed information that can help developers to fix the
-            reported vulnerabilities.
+    information from side-channel vulnerabilities that result from actual attack
+    scenarios in a single trace attack. Our approach differs from previous ones in that we
+    model real attack scenarios for one execution. 
+    We model the information quantification problem as a counting problem 
+    and use a Monte Carlo sampling method to estimate the information leakage.
+    \item We implement the method into a tool and apply it
+    to several pieces of real software. \tool{} successfully identifies
+    previous unknown and known side-channel vulnerabilities and calculates the corresponding information leakage. 
+    Our results are useful in practice.
+    The leakage estimates and the corresponding trigger inputs can 
+    help developers to triage and fix the vulnerabilities.
+    \item We propose a novel method that can detect and analyze the effect of each side-channel leakage sites automatically.
+Our analysis combine information from both the source code and the run-time execution, which makes the method more effective in finding the leakages.
+The method can combine multiple leakage sites to retrieve more information as well.
+    \item We analyze the amount of information leakage from side-channel vulnerabilities based on the channel capacity.
+We propose a method that can estimate the lower bound of information leakages.
+The theory can serve as the foundation of the future work on quantify the information leakage based on the fuzzing.
+    \item We implement the above method in a tool called \ctool{} and evaluate the tool with several benchmarks and several real-world applications such as OpenSSL, mbedTLS, TinyDNN, and GTK.
+The results show that our tool can detect and quantify the side-channel leakages effectively.
+Moreover, the leakage reports given by the \ctool{} can help developers fix the reported vulnerabilities.
 \end{itemize}
-
-\section{Contribution}
 

### 2021-02-16 Chapter-2/Chapter-2.tex
update

@@
 
-\chapter{Background and Related Work}
+\chapter{Background and Related Work}\label{chapter2}
 
@@
 For example, cached-based
-side-channels~\cite{yarom2017cachebleed,191010,184415,,Osvik2006,liu2015last,184415,liu2015last}
+side-channels~\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last,184415}
 rely on the time difference between cache misses and cache hits. We introduce two
@@
      \begin{tikzpicture}[ele/.style={fill=black,circle,minimum width=.8pt,inner sep=1pt},every fit/.style={ellipse,draw,inner sep=-2pt}]
-      \node[ele,label=left:{\LARGE $k_1$}] (a1) at (0,4) {};    
-      \node[ele,label=left:{\LARGE $k_2$}] (a2) at (0,3) {};    
-      \node[ele,label=left:{\LARGE $k_3$}] (a3) at (0,2) {};
-      \node[ele,label=left:{\LARGE $k_4$}] (a4) at (0,1) {};
+      \node[ele,label=left:{\normalsize $k_1$}] (a1) at (0,4) {};    
+      \node[ele,label=left:{\normalsize $k_2$}] (a2) at (0,3) {};    
+      \node[ele,label=left:{\normalsize $k_3$}] (a3) at (0,2) {};
+      \node[ele,label=left:{\normalsize $k_4$}] (a4) at (0,1) {};
 
-      \node[ele,,label=right:{\LARGE $o_1$}] (b1) at (4,4) {};
-      \node[ele,,label=right:{\LARGE $o_2$}] (b2) at (4,3) {};
-      \node[ele,,label=right:{\LARGE $o_3$}] (b3) at (4,2) {};
-      \node[ele,,label=right:{\LARGE $o_4$}] (b4) at (4,1) {};
+      \node[ele,,label=right:{\normalsize $o_1$}] (b1) at (4,4) {};
+      \node[ele,,label=right:{\normalsize $o_2$}] (b2) at (4,3) {};
+      \node[ele,,label=right:{\normalsize $o_3$}] (b3) at (4,2) {};
+      \node[ele,,label=right:{\normalsize $o_4$}] (b4) at (4,1) {};
 

### 2021-02-16 Chapter-1/Chapter-1.tex
update

@@
 
-\begin{itemize}
+\begin{enumerate}
     \item It is hard to identify side-channel vulnerabilities in real-world software.
@@
 Recent work can identify thousands of leaked points, but most of them are not patched by developers because those leakages are either false positives or leaked very little information.
+\end{enumerate}
+
+\section{Contribution}
+To address Problem 1, we make the following contributions on detecting side-channel leakages:
+
+\begin{itemize}
+    \item We designs a symbolic analysis method that can detect secret-dependent control-flow transfers and secret-dependent data access.
+The key idea is to only symbolically execute those machine instructions that are relevant to vulnerabilities while executing other instructions natively.
+    \item We implement the above method in a tool called ~\detect{}.
+The evaluation results shows that ~\detect{}  is 3 to 100 times faster than existing tools while identifying all vulnerabilities when we run it on the same library.
+Additional, we do not need to apply domain knowledge to only part of the original program, which simplify the analysis.
 \end{itemize}
 
-\section{Contribution}
-To address the above problems, we make the following contributions in this dissertations:
+To address Problem 2, we make the following contributions on quantifying side-channel leakages:
 
 \begin{itemize}
-    \item We propose a novel method that can quantify fine-grained leaked
+    \item We propose a method that can quantify fine-grained leaked
     information from side-channel vulnerabilities that result from actual attack

### 2021-02-16 Chapter-1/Chapter-1.tex
update

@@
 The evaluation results shows that ~\detect{}  is 3 to 100 times faster than existing tools while identifying all vulnerabilities when we run it on the same library.
-Additional, we do not need to apply domain knowledge to only part of the original program, which simplify the analysis.
+We do not need to apply domain knowledge to only part of the original program, which simplify the analysis.
+In addition, ~\detect{} yields new leakages which are not identified by previous tools.
+We confirm those findings with developers.
 \end{itemize}

### 2021-02-16 Chapter-1/Chapter-1.tex
update

@@
 
-To address Problem 2, we make the following contributions on quantifying side-channel leakages:
+To address Problem 2, we make the following contributions on quantifying side-channel leakages in a single trace attack:
 
@@
     help developers to triage and fix the vulnerabilities.
+\end{itemize}
+
+To address Problem 2, we make the following contributions on quantifying side-channel leakages on chosen plaintext side-channel attacks: 
+\begin{itemize}
     \item We propose a novel method that can detect and analyze the effect of each side-channel leakage sites automatically.

### 2021-02-18 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 \section{Contribution}
+We address the above problems from two aspects.
+First, we propose a novel method that can detect side-channel vulnerabilities in real-world applications automatically fast and precisely.
+Second, we propose methods that can quantify each side-channel leakages precisely.
+In additional, we study two kinds of threat models, a single trace attack, and chosen message attacks
+
+In summary, we make the following contributions:
+
 To address Problem 1, we make the following contributions on detecting side-channel leakages:
@@
 \section{Dissertation Organization}
-The rest of the dissertation is organized as follows. We first present relevant backgrounds and related works in Chapter~\ref{chapter1}. We then propose our works in
-Chapter~\ref{chapter2}. Chapter~\ref{chapter3} and Chapter~\ref{chapter4} introduce
-our recent progress about the proposed work.
+The rest of the dissertation is organized as follows.
+We present relevant backgrounds and related works in Chapter~\ref{chapter2}.
+Chapter~\ref{chapter3} presents a novel method to detect side-channel vulnerabilities in binary executables.
+Chapter~\ref{chapter4} present a method that can quantify each side-channel leakage in a single trace attack.
+Chapter~\ref{chapter5} extend the approach and quantifies the side-channel leakage in chosen message attacks.
+Chapter~\ref{chapter6} conclude the thesis.

### 2021-02-24 SupplementaryMaterial/Acknowledgments.tex
update

@@
 % Place acknowledgments below.
-First of all, I would like to thank my advisor Prof.
+First of all, I would like to thank my advisor Dr.
 Dinghao Wu for the continuous support of my Ph.D.
@@
 Without his encouragement and support, I could not have finished the program.
-I also thank Dinghao for inviting me to Switzerland during his sabbatical leave.
+I also thank Dinghao for inviting me to Switzerland on his sabbatical.
 A large portion of the research presented in the dissertation was finished when I worked in Switzerland.
@@
 
-Beside my advisor, I would like to thank my committee members, Prof. Peng Liu, Prof. Sencun Zhu, Prof. Benjamin Hanrahan, and Prof. James R. Larus for their time, reviewing my dissertation.
+Beside my advisor, I would like to thank my committee members, Dr. Peng Liu, Dr. Sencun Zhu, Dr. Benjamin V. Hanrahan, and Prof. James R. Larus for their time, reviewing my dissertation.
 
@@
 Mingshen Sun, Dr.
-Greg Zaverucha and Dr.
+Greg Zaverucha, Dr.
+Kevin Kane, and Dr.
 Brian LaMacchia for their help during my internship at Baidu X-Lab and Microsoft Research Lab.

### 2021-02-24 Chapter-1/Chapter-1.tex

@@
 Chapter~\ref{chapter3} presents a novel method to detect side-channel vulnerabilities in binary executables.
-Chapter~\ref{chapter4} present a method that can quantify each side-channel leakage in a single trace attack.
-Chapter~\ref{chapter5} extend the approach and quantifies the side-channel leakage in chosen message attacks.
-Chapter~\ref{chapter6} conclude the thesis.
+Chapter~\ref{chapter4} presents a method that can quantify each side-channel leakage in a single trace attack.
+Chapter~\ref{chapter5} extends the approach and quantifies the side-channel leakage in chosen message attacks.
+Chapter~\ref{chapter6} concludes the thesis.

### 2021-03-14 Chapter-2/Chapter-2.tex
Updates from Overleaf

--- 2021-02-15 Chapter-2/Chapter-2.tex
@@
 
-\chapter{Background and Related Work}
+\chapter{Related Work}\label{chapter2}
+This chapter introduces the related work in this dissertation. We present the related work from the following aspects: side-channel attacks, detections, mitigation, and information quantification.
 
-\section{Address-based Side-channel Attacks}
+\section{Side-channel Attacks}
 Side channels can leak sensitive information
@@
 after restricting some code and data pages.
-
-\begin{figure}[]
-
-    \noindent\begin{minipage}{0.45\linewidth}
-        \noindent
-        \begin{lstlisting}[numbers = none]
-unsigned long long r;
-int secret[32];
-...
-while(i>0){
-    r = (r * r) % n;
-    if(secret[--i] == 1)
-        r = (r * x) % n;   
-}
-        \end{lstlisting}
-\vspace*{-9pt}
-        \caption{Secret-dependent control-flow transfers}
-        \label{fig:secret:cf}
-    \end{minipage}
-    \hfill
-    \begin{minipage}{0.45\linewidth}
-        \begin{lstlisting}[numbers = none]
-static char Fsb[256] = {...}
-... 
-uint32_t a = *RK++ ^ \ 
-(FSb[(secret)) ^
-(FSb[(secret >> 8)] << 8 ) ^
-(FSb[(secret >>16)] << 16 ) ^
-(FSb[(secret >>24)] << 24 );
-...
-        \end{lstlisting}
-\vspace*{-9pt}
-        \caption{Secret-dependent memory accesses}
-        \label{fig:secret:da}
-    \end{minipage}
-\vspace*{-12pt}
-\end{figure}
 
@@
 If the victim enclave program accesses the memory table, then the adversary can know which page is accessed by observing the page fault sequence.
-While the granularity of the controlled-channel attacks is very coarse grained, the controlled-channel attacks allow the attacker to have a noise-free observation.
-Examples of other attacks exploits page cache maintained by the OS, TLB also shares the same granularity.
+While the granularity of the controlled-channel attacks is coarse-grained, the controlled-channel attacks allow the attacker to have a noise-free observation.
+Other examples like the TLB side-channel attack, DDRAM attacks share the same page-level granularity.
 
@@
 
+\subsection{Target Applications}
+While there is a vast number of studies\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last} on side-channel attacks and detections, we find many of those work targets on the encryption key on cryptography libraries.
+In terms of the non-cryptography side-channel attacks.
+We find many of them can be classified into the below three categories.
+
+\subsubsection{Cryptography Libraries}
+
+\subsubsection{Machine Learning and Deep Learning Models}
+Previous side-channel attack mainly focus on recovering the input of the model and reversing the architecture of deep learning models.
+Hua et al.~\cite{hua2018reverse} were the first reverse engineer the architecture of neural networks.
+Wei et al.~\cite{wei2018know} perform the side-channel attacks on an FPG-based convolution neural network based on the power consumption to recover the real-world inputs.
+For the MNIST dataset, their attacks can achieve up 89\% accuracy.
+On the contrary, our attack based on the page access information can achieve accuracy.
+CSI NN~\cite{batina2019csi} reverse engineer the multi-layer perception and convolution neural network based on the Electromagnetic signal.
+Cache Telepathy~\cite{yan2020cache} introduce the cache based side-channel attack to extract DNN architecture.
+We mention that all existing approach need a lot of domain knowledge and expertise to launch the attack.
+\subsubsection{Media and Graphic Libraries}
+A few of recent work also studies the side-channel in media and graphic libraries.
+In the first controlled-channel attack~\cite{xu2015controlled}, they can recover the outline of the image by exploiting the vulnerability in the inverse DCT leakage site.
+Daimeng et al.~\cite{wang2019unveiling} present the cache attack in graphic libraries.
+Their approaches also combine a machine learning approach.
+However, they use the machine learning to infer the best exploitable cache line, while our approach use the machine learning to infer the total leaked information.
+\subsubsection{Others}
+Some other side-channel targets also include spell checking tools, and font libraries~\cite{xu2015controlled}.
+The attack to font libraries is essentially the same to the attack to the graphic library like GTK.
+By exploiting the differences of memory accesses when the program render each character, an attacker can recover part of the original sensitive information.
+We find most of those side-channel attacks target the trusted execution environments.
+We think part of the reason is that it is easy to argue that information in those libraries is also sensitive to users as well.
+
+\section{Detection and Mitifation}
+While there are several existing work on side-channel leakage detections, we find it very hard to apply existing methods to identify controlled-channel attacks.
+According to Table~\ref{table:related_work}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction.
+
+\textbf{Trace comparison.} If the victim program has two different execution traces with two different sensitive inputs, then we can distinguish the sensitive input by observing the execution trace.
+Therefore, we can conclude the program is vulnerable to side-channel attacks.
+The method is similar to UNIX tool \textsf{diff}.
+Moreover, the approach does not need to model or abstract the program's semantics.
+In general, the approach is quite salable.
+On the negative side, comparing the trace along can only find the leakage, but it cannot find the complex relationship between the leakage site and the original buffer.
+For example, if two leakage sites leak the same information in the original buffer, those approaches cannot find out the two leakage sites are the same.
+
+\textbf{Abstraction.} The second category of those tools belongs to the field of abstractions.
+Tools based on those approaches use the abstraction to generate approximations of the semantics of computer programs.
+After that, by analyzing the model, those tools can identify side-channel leakages.
+Comparing with the trace comparison approach, the method is more precise.
+
+Those methods usually follow the below steps.
+Suppose a program $P$ has $k$ as the input, we can run symbolic execution on the top the victim program.
+So temporary values can be represented as math formulas.
+After that, we need to build a cache or memory access model and model the side-channel leakage as a math constraint.
+Then we use SMT solvers to find if there are two different secret inputs that can lead to access different locations in the memory or the cache.
+If so, then the program is vulnerable to side-channel attacks.
+Contrary to the trace comparison, the method is quite precise.
+Moreover, it can model multiple leakages precisely as the conjunction of those formulas.
+However, after some initial investigations and experiments, we find such approach fails in practice due to the below reasons.
+
+\begin{itemize}
+    \item Existing tools cannot not handle many instructions such as AVX, and SIMD instructions.
+Most existing tools are research prototype or are implemented based on the research prototype.
+For many projects, the tool is only implemented to properly handle the benchmark in their papers.
+Second, many those tools rely on transferring those instructions into some intermediate languages.
+However, those intermediate languages do not support those architecture instructions.
+    \item Today's solvers can not handle many complicated constraints, especially the conjunction of those constraints.
+Recent studies show existing solver have bugs when it deals with floating pointer calculations.
+\end{itemize}
+
+According to Table~\ref{table:side_channel_detection_tool}, some methods may choose to analyze the source code or the intermediate languages.
+However, it still cannot solve the problem.
+First, many widely-used libraries (e.g., Intel MKL) do not open the source code.
+Second, some libraries use hand code assembly code to pursue the maximum performance.
+CacheAudit~\cite{182946} uses abstract domains to compute an
+over approximation of cache-based side-channel information leakage upper bound.
+However, it is difficult to judge the sensitive level of the side-channel leakage based on
+the leakage provided by CacheAudit. CacheS~\cite{236338} improves on
+CacheAudit with new abstract domains that only track
+secret-related code. Like CacheAudit, CacheS cannot
+indicate the sensitive level of side-channel vulnerabilities.
+CaSym~\cite{Brotzman19Casym} introduces a static cache-aware symbolic
+reasoning technique to cover multiple paths in a target program. Again, their
+approaches cannot evaluate the sensitive level for each side-channel
+vulnerability, and it only work on small code snippets.
+
+The dynamic approach, usually consists of taint analysis and symbolic execution,
+can perform a very precise analysis. CacheD~\cite{203878} takes a concrete execution trace and runs symbolic execution on the trace
+to get the formula of each memory address. CacheD is
+quite precise in avoiding false positives.
+However, CacheD is not able to detect secret-dependent control-flows.
+We adopted a similar approach to model the secret-dependent data accesses.
+\tool{} differs from CacheD in that we do not use traditional taint tracking or domain knowledge to cut the trace when identifying secret-dependent data access vulnerabilities.
+\tool{} works on machine instructions directly instead of intermediate representations.
+Moreover, \tool{} finds secret-dependent control-flows at the same time and gives a precise quantification of the leakage.
+DATA~\cite{217537} detects address-based side-channel vulnerabilities by comparing different execution traces under various test inputs.
+After collecting execution traces, DATA aligns them and finds the differences.
+It uses statistical hypothesis testing to find true leakages.
+However, both imperfect trace alignment and statistical testing result that DATA can produce false positives.
+MicroWalk~\cite{Wichelmann:2018:MFF:3274694.3274741} uses
+mutual information (MI) between sensitive input and execution state to detect side-channels.
+
 \begin{table}
@@
     \caption{Due to the page limit, we only shows some representations of the vast side-channel attacks: Attacks, the shared hardware resources with attackers, the granularity of the attacker can observe, is there any published attacks on non-cryptography library and if the type of attack can exploit multiple leakage sites.}
-    \label{table:side_channel_attack}
+    \label{table:side_channel_detection_tool}
     \resizebox{\columnwidth}{!}{%
@@
     \end{table}
-\section{Information Theory}
-This section presents a short introduction on information theory. For a detailed tutorial, we recommend users refer to the following literature.
 
-Given an event $e$ that occurs with the probability $p(e)$, we receive
-\begin{displaymath}
-    I = - \log_2p(e)
-\end{displaymath}
-bits of information by knowing the event $e$ happens according to information theory~\cite{shannon1948mathematical}. 
-Considering a char variable $a$
-with one byte storage size in a C program, its value ranges from 0 to 255.
-Assume $a$ has a uniform distribution. If we observe that
-$a$ equals $1$, the probability of this observation is $\frac{1}{256}$. So 
-we get $-\log(\frac{1}{256}) = 8$ bits information, which is exactly the size
-of a char variable in the C program.
+Both hardware~\cite{Page2005PartitionedCA,
+Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
+236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
+brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
+been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
+accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
+architecture~\cite{tiwari2011crafting}, require changes to complex processors and are complex to adopt. On the contrary, software approaches are
+usually easy to implement. Coppens et
+al.~\cite{Coppens:2009:PMT:1607723.1608124} uses a compiler
+to eliminate key-dependent control-flow transfers. Crane et
+al.~\cite{crane2015thwarting} mitigated side-channels by randomizing software.
+As for crypto libraries, the basic idea is to eliminate key-dependent
+control-flow transfers and data accesses. Common approaches include
+bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
+control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.
 
-Existing works on information leakage quantification typically use Shannon
-entropy~\cite{clark2007static,Wichelmann:2018:MFF:3274694.3274741},
-min-entropy~\cite{10.1007/978-3-642-00596-1_21}, and max-entropy~\cite{182946,
-Doychev:2017:RAS:3062341.3062388}. In these frameworks, the input sensitive
-information $K$ is considered as a random variable.
+\section{Quantification}
+Proposed by Denning~\cite{robling1982cryptography} and Gray~\cite{gray1992toward}, 
+Quantitative Information Flow (QIF) aims at providing an estimation of the amount of leaked information from the sensitive information given the public output. If zero bits
+of the information are leaked, the program is called non-interference. McCamant
+and Ernst~\cite{McCamantE2008} quantify the information leakage as the network
+flow capacity. Backes et al.~\cite{5207642} propose an automated method for QIF
+by computing an equivalence relation on the set of input keys. But the approach
+cannot handle real-world programs with bitwise operations. 
+Phan et al.~\cite{Phan:2012:SQI:2382756.2382791} propose symbolic QIF. The goal of their
+work is to ensure a program is non-interference. They adopt an over
+approximation method to estimate the total information leakage and their method
+does not work for secret-dependent memory access side-channels.
+Pasareanu et al.~\cite{pasareanu2016multi} combine symbolic analysis and Max-SMT solving to synthesize the concrete public input that can lead to the worst case leakage.
+They assume the target program has multiple different input secrets and calculate the average leakage for one-fixed public input.
+CHALICE~\cite{Chattopadhyay:2017:QIL:3127041.3127044} quantifies the leaked
+information for a given cache behavior. 
+It symbolically reasons about cache
+behavior and estimates the amount of leaked information based on cache miss/hit.
+Their approach only scale to small programs, which limits its usage in
+real-world applications. On the contrary, \tool{} assesses the sensitive level
+of side-channels with different granularities. It can also analyze side-channels
+in real-world crypto libraries.
 
-Let $k$ be one of the possible
-value of $K$. The Shannon entropy $H(K)$ is defined as
-\begin{displaymath}
-    H(K) = - \sum_{k {\in} K}p(k)\log_2(p(k))
-\end{displaymath}
-
-Shannon entropy can be used to quantify the initial uncertainty about the
-sensitive information. It measures the amount of information in a system.
-
-Min-entropy describes the information leaks for a program with the most likely input. 
-For example, min-entropy can be used to describe the
-best chance of success in guessing one's password using the
-most common password. %, which is defined as
-\begin{displaymath}
-    \mathit{min\text{-}entropy} = - \log_2(p_{\mathit{max}})
-\end{displaymath}
-
-Max-entropy is defined solely on the number of possible observations.
-%It is equal to $-\log_2{n}$.
-\begin{displaymath}
-    \mathit{max\text{-}entropy} = -\log_2{n}
-\end{displaymath}
-As it is easy to compute, most recent works~\cite{182946,Doychev:2017:RAS:3062341.3062388} use max-entropy as the definition of
-the amount of leaked information.
-
-To illustrate how these definitions work, we consider the code
-fragment in Figure~\ref{fig:side-channel}. It has two secret-dependent
-control-flows, A and B.
-
-\begin{figure}[h!]
-\centering
-\begin{lstlisting}[xleftmargin=.03\textwidth,xrightmargin=.01\textwidth]
-uint8_t key[2], t1, t2;
-get_key(key);              // 0 <= key[0], key[1] < 256
-t1 = key[0] + key[1];
-t2 = key[0] - key[1];
-if (t1 < 4){               // leakage site A
-    foo();    
-}                          
-if (t2 > 0){               // leakage site B     
-    doo();    
-}                          
-\end{lstlisting}
-\vspace*{-1pt}
-    \caption{Side-channel leakage}
-    \label{fig:side-channel}
-\end{figure}
-In this paper we assume an attacker can observe the secret-dependent control-flows in Figure~\ref{fig:side-channel}.
-Therefore, an attacker can have two different observations for each leak site
-depending on the value of the $\mathit{key}$: $A$ for function \textsf{foo} is executed, 
-$\neg A$ for function \textsf{foo} is not executed, $B$ for function \textsf{doo} is
-executed, and $\neg B$ for function \textsf{doo} is not executed. Now the
-question is how much information can be leaked from the above code if an
-attacker knows which branch is executed?
-
-\begin{table}[ht]
-    \centering\small\footnotesize
-    \caption{The distribution of observation}\label{shtable}
-    \vspace*{-0pt}
-%    \resizebox{\columnwidth}{!}{
-    \begin{tabular}{l|cc|cc}
-        \hline
-
-        Observation ($o$)   & $A$ & $\neg A$ & $B$ & $\neg B$ \\ \hline
-        Number of Solutions & 65526       & 10        & 32768     & 32768           \\ \hline
-        Possibility (p)     & 0.9998      & 0.0002    & 0.5    & 0.5       \\
-        \hline
-    \end{tabular}
-%        }
-\end{table}
-
-Assuming $\mathit{key}$ is uniformly distributed, we can calculate the corresponding
-possibility by counting the number of possible inputs. Table~\ref{shtable}
-describes the probability of each observation. We use the above three types of 
-leakage metrics to calculate the amount of leaked information for leak A and leak B.
-
-\vspace{3pt}
-\textbf{Min Entropy.}
-As $p_{A\mathit{max}} = 0.9998$ and $p_{B\mathit{max}} = 0.5$, 
-with the definition, min-entropy equals to
-\begin{align*}
-    \mathit{min\text{-}entropy_A} & = -\log_2{0.9998} = 0.000\ \mathrm{bits} \\
-    \mathit{min\text{-}entropy_B} & = -\log_2{0.5} = 1.000\ \mathrm{bits}
-\end{align*}
-
-\textbf{Max Entropy.}
-Depending on the value of key, the code can run two different branches for each leakage site. 
-Therefore, with the max entropy
-definition, both leakage sites leak
-
-\begin{displaymath}
-    \mathit{max\text{-}entropy} = -\log_2{2} = 1.000\ \mathrm{bits}
-\end{displaymath}
-
-\textbf{Shannon Entropy.}
-Based on Shannon entropy, the respective amount of information in A and B equals to
-{\footnotesize
-\begin{align*}
-    \mathit{Shannon\text{-}entropy_A} & = -(0.9998*\log_{2}0.9998      \\
-                                    & \qquad+ 0.0002*\log_{2}0.0002)  \\
-                                    & = 0.000\ \mathrm{bits}         \\
-    \mathit{Shannon\text{-}entropy_B} & = -(0.5*\log_{2}0.5      \\
-                                    & \qquad+ 0.5*\log_{2}0.5)        \\
-                                    & = 1.000\ \mathrm{bits}                             
-\end{align*}
-}
-In the next section, we will show that these measures work well only
-theoretically in a static analysis setting. 
-Generally, they do not apply to dynamic analysis or real
-settings. We will present that the static or theoretical results could be
-dramatically different from the real world, and we do need a better method to
-quantify the information leakage from a practical point of view.
-
-Let $k$ be one of the possible
-value of $K$. The Shannon entropy $H(K)$ is defined as
-\begin{equation}\label{eq1}
-    H(K) = - \sum_{k {\in} K}p(k)\log_2(k)
-\end{equation}
-
-Shannon entropy can be used to quantify the initial uncertainty about the sensitive information.
-It measures the amount of information in a system.
-For example, an AES encryption program takes a 128-bit key as the input.
-Suppose every key has the equal opportunity and $p_k = 1/ 2^{128}$, then the encryption system has $128 \, \mathit{bits}$ information according to Shannon entropy.
-
-In the paper, we use the channel capacity to describe the information leakages through a channel.
-In information theory, the channel capacity is used to quantify the rate of information can be reliably transmitted over a channel.
-If we use $K$ to represent the input secrets and $O$ to represent the output observation.
-The channel capacity ($C$) is defined as
-
-\begin{equation}\label{eq2}
-C(K;O) = \max_{p(x)} I(K;O)
-\end{equation}
-Here $I(K;O)$ is the mutual information between $K$ and $O$.  
-\begin{equation} \label{eq3}
-    I(K;O) = \sum_{k {\in} K}{\sum_{o {\in} O}{p(k, o)\log_2\frac{p(k, o)}{p(k)p(o)}}}
-\end{equation}
-
-While the general case of channel capacity is hard to execute, we consider the two special channels.
-
-\subsection{Noiseless Lossless Channel}
-The channel of the system is noiseless and lossless if
-
-\begin{equation} \label{eq:1}
-    C(K;O) = \max_{p(k)} I(K;O) = \max_{p(k)} H|O| =\max_{p(k)} H|K|
-\end{equation}
-$|K|$ represents the number of symbols in $K$.
-
-Figure~\ref{fig:channel}a shows the example of the type of the channel.
-Under the circumstance, we always have $P(o_i/k_i) = 1$ and $P(k_i/o_i) = 1$.
-As we can see, the channel have the unique output ($o \in O$) for every input ($k \in K$).
-
-\begin{figure}
-    \begin{minipage}{0.48\linewidth}
-    \resizebox{\linewidth}{!}{
-
-     \begin{tikzpicture}[ele/.style={fill=black,circle,minimum width=.8pt,inner sep=1pt},every fit/.style={ellipse,draw,inner sep=-2pt}]
-      \node[ele,label=left:{\LARGE $k_1$}] (a1) at (0,4) {};    
-      \node[ele,label=left:{\LARGE $k_2$}] (a2) at (0,3) {};    
-      \node[ele,label=left:{\LARGE $k_3$}] (a3) at (0,2) {};
-      \node[ele,label=left:{\LARGE $k_4$}] (a4) at (0,1) {};
-
-      \node[ele,,label=right:{\LARGE $o_1$}] (b1) at (4,4) {};
-      \node[ele,,label=right:{\LARGE $o_2$}] (b2) at (4,3) {};
-      \node[ele,,label=right:{\LARGE $o_3$}] (b3) at (4,2) {};
-      \node[ele,,label=right:{\LARGE $o_4$}] (b4) at (4,1) {};
-
-      \node[draw,fit= (a1) (a2) (a3) (a4),minimum width=2cm] {} ;
-      \node[draw,fit= (b1) (b2) (b3) (b4),minimum width=2cm] {} ;  
-      \draw[->,thick,shorten <=2pt,shorten >=2pt] (a1) -- (b1);
-      \draw[->,thick,shorten <=2pt,shorten >=2] (a2) -- (b2);
-      \draw[->,thick,shorten <=2pt,shorten >=2] (a3) -- (b3);
-      \draw[->,thick,shorten <=2pt,shorten >=2] (a4) -- (b4);
-     \end{tikzpicture}
-    }
-    \caption*{(a) Noiseless Lossless}
-    \end{minipage}
-    \hfill
-    \begin{minipage}{0.48\linewidth}
-    \resizebox{\linewidth}{!}{
-
-     \begin{tikzpicture}[ele/.style={fill=black,circle,minimum width=.8pt,inner sep=1pt},every fit/.style={ellipse,draw,inner sep=-2pt}]
-      \node[ele,label=left:{\LARGE $k_1$}] (a1) at (0,4) {};    
-      \node[ele,label=left:{\LARGE $k_2$}] (a2) at (0,3) {};    
-      \node[ele,label=left:{\LARGE $k_3$}] (a3) at (0,2) {};
-      \node[ele,label=left:{\LARGE $k_4$}] (a4) at (0,1) {};
-
-      \node[ele,,label=right:{\LARGE $o_1$}] (b1) at (4,4) {};
-      \node[ele,,label=right:{\LARGE $o_2$}] (b2) at (4,3) {};
-      \node[ele,,label=right:{\LARGE $o_3$}] (b3) at (4,2) {};
-      \node[ele,,label=right:{\LARGE $o_4$}] (b4) at (4,1) {};
-
-      \node[draw,fit= (a1) (a2) (a3) (a4),minimum width=2cm] {} ;
-      \node[draw,fit= (b1) (b2) (b3) (b4),minimum width=2cm] {} ;  
-      \draw[->,thick,shorten <=2pt,shorten >=2pt] (a1) -- (b1);
-      \draw[->,thick,shorten <=2pt,shorten >=2] (a2) -- (b2);
-      \draw[->,thick,shorten <=2pt,shorten >=2] (a3) -- (b2);
-      \draw[->,thick,shorten <=2pt,shorten >=2] (a4) -- (b2);
-     \end{tikzpicture}
-     }
-     \caption*{(b) Noiseless Loss}
-     \end{minipage}
-    \caption{Two Kinds of Channels}\label{fig:channel}
-    \end{figure}
-
-\subsection{Noiseless Loss Channel}
-In reality, noiseless loss channel is more common. We define the channel is noiseless loss if
-
-\begin{equation} \label{eq:2}
-    C(K;O) = \max_{p(x)} I(K;O) = \max_{p(x)} H |O| = \log_2 {|O|}
-\end{equation}
-
-Figure~\ref{fig:channel}b  shows the example of the type of the channel.
-Once the input symbol is determined, the output symbol is also determine.
-As we can see, the channel have the unique output ($o \in O$) for every input ($k \in K$).
+Model counting refers to the problem of computing the number of 
+models for a propositional formula (\#SAT). There are two approaches to
+solving the problem, exact model counting and approximate model 
+counting. We focus on approximate model counting since it is our approach. Wei and Selman~\cite{wei2005new} introduce
+ApproxCount, a local search based method using Markov Chain Monte 
+Carlo (MCMC). ApproxCount has the better scalability than 
+exact model counters. Other approximate model counter includes 
+SampleCount~\cite{gomes2007sampling},
+Mbound~\cite{gomes2006model}, and MiniCount~\cite{kroc2008leveraging}. 
+Unlike ApproxCount,
+these model counters can give lower or upper bounds with guarantees.
+Despite the rapid development of model counters for SAT and some 
+research~\cite{chistikov2017approximate,phan2015model} on Modulo Theories model counting (\#SMT),
+they cannot be directly applied to 
+side channel leakage quantification.
+ApproxFlow~\cite{biondi2018scalable} uses ApproxMC~\cite{chakraborty2016algorithmic} for information flow quantification,
+but it has only been tested with small programs.

### 2021-03-14 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 
-\chapter{Scalable Side-channel Vulnerability Detection}
+\chapter{Scalable Side-channel Vulnerability Detection}\label{chapter3}
 \section{Motivation}
-While there are several existing work on side-channel leakage detections, we find it very hard to apply existing methods to identify controlled-channel attacks.
-According to Table~\ref{table:related_work}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction.
-\begin{table*}
-    \centering
-    \caption{Existing leakage detection tool only evaluate them on cryptography library.
-1.
-Most recent work only evaluates their approaches on cryptography libraries.
-2.
-All of them can not reason about the total effect of multiple leakages.}
-    \label{table:related_work}
-
-    \begin{tabular}{lllcclc}
-    \toprule
-    Tool & S/D & Method  & AVX/SIMD  & Multiple & Evaluation & Available \\ \midrule
-    CacheAudit~\cite{doychev2015cacheaudit} & Static  & Abstraction  & \xmark & \xmark & Crypto Algorithm  & \cmark \\ 
-    CacheD~\cite{wang2017cached} & Dynamic  & Symbolic Execution + Taint Analysis  & \xmark & \xmark & Libgcrypt, OpenSSL & \xmark \\
-    CachSym~\cite{brotzman2019casym} & Static & Symbolic Execution  & \xmark & \xmark & Crypto Snippet & \xmark \\
-    CacheS~\cite{wang2019identifying} & Static & Abstract Interpretation & \xmark & \xmark & Libgcrypt, OpenSSL, mbedTLS & \xmark \\
-    DATA~\cite{weiser2018data} & Dynamic & Trace Alignment + Comparison & \cmark & \xmark & OpenSSL, PyCrypto & \cmark \\
-    ctgrind~\cite{langley2010ctgrind} & Dynamic & Taint Analysis & \cmark & \xmark & Crypto Library & \cmark \\
-    Satcco~\cite{xiao2017stacco} & Dynamic & Trace Comparison & \cmark & \xmark & OpenSSL, GnuTLS, mbedTLS, WolfTLS, LibreSSL & \xmark \\
-    ANABLEPS~\cite{wang2019time} & Dynamic & Trace Comparison & \cmark & \xmark & Deep Learning, gsl, Hunspell, PNG, Freetype, QRcodegen, Genometools & \xmark \\
-    MicroWalk~\cite{wichelmann2018microwalk} & Dynamic & Trace Comparison & \cmark & \xmark & Intel IPP, Microsoft CNG & \cmark \\ 
-    \bottomrule
-    \end{tabular}
-
-    \end{table*}
 
@@
 %can lead to different execution behaviors using constraint solver. 
-We implement
-the approach presented in \S\ref{sec:trace-qif} and model the side-channels as
-formulas. While the tool can finish analyzing some simple cases like AES, it can
+We implement the approach presented in \S\ref{sec:trace-qif} and model the side-channels as formulas. While the tool can finish analyzing some simple cases like AES, it can
 not handle complicated cases like RSA.

### 2021-03-14 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 
-\section{Detection and Mitifation}
+\section{Detection and Mitigation}
 While there are several existing work on side-channel leakage detections, we find it very hard to apply existing methods to identify controlled-channel attacks.

### 2021-03-14 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \section{Threat Model}
-
-\section{Examples}
+We assume that an attacker shares the same hardware platform with the target.
+Here are a few examples.
+1) A host machine has several Virtual Machines (VMs).
+The victim runs the application inside one VM.
+An attacker can start a new VM and probe the process running on the other VM.
+2) In a shielding system, a malicious operating system can extract sensitive information from the protected application.
+The attacker attempts to retrieve sensitive information through address-based
+side-channel attacks. The attacker has no direct access to the target's memory or cache,
+but it can probe its memory or cache at each program point. In reality, the
+attacker will face many possible obstacles such as the noisy observations 
+of the memory or cache. However, for this project, we assume
+the attacker has noise-free observations as in previous work~\cite{203878,182946,Brotzman19Casym}. 
+The threat model captures most cache-based and address-based side-channel attacks. 
+We only consider deterministic programs and assume an attacker 
+has access to the source code or binary executable of the target program.
 
 \section{Math Notations}
-e now discuss how to model observations ($O$), which are the direct information
+We now discuss how to model observations ($O$), which are the direct information
 that an adversary can get during the attack.

### 2021-03-18 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses.
-Most of the attack allows the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim.
+Most systems allows the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim.
 As a result, while the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.
@@
 \section{Contribution}
-We address the above problems from two aspects.
+We address above problems from two aspects.
 First, we propose a novel method that can detect side-channel vulnerabilities in real-world applications automatically fast and precisely.
 Second, we propose methods that can quantify each side-channel leakages precisely.
-In additional, we study two kinds of threat models, a single trace attack, and chosen message attacks
+In addition, we study two kinds of threat models, single-trace attacks, and chosen message attacks.
 

### 2021-03-19 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 
-Side channels are inevitable in modern computer systems as the sensitive
-information may be leaked through many kinds of inadvertent behaviors, such as power, electromagnetic radiation, and even
-sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}.
+Side-channels are ubiquitous in modern computer systems as sensitive information may be leaked through many kinds of negligent behaviors, such as power, electromagnetic radiation, or even sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}.
+It is typically hard to fix all side-channel vulnerabilities for real-world software systems.
+
 Among them, address-based side channel attacks, such as cache attacks, memory page attacks, and controlled-channel attacks, are especially common and have been studied for years~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}.

### 2021-03-22 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 
-Among them, address-based side channel attacks, such as cache attacks, memory page attacks, and controlled-channel attacks, are especially common and have been studied for years~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}.
-These
-attacks result from vulnerable software and shared hardware components.
-By observing program outputs or hardware behaviors, attackers can infer program
-execution flows that manipulate secrets and guess secrets such as encryption
-keys~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.
+Among them, address-based side-channel attacks, such as cache attacks, memory page attacks, and controlled-channel attacks, are especially common and have been studied for years~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}.
+These attacks result from vulnerable software and shared hardware components between the attacker and the victim.
+By observing program outputs or hardware behaviors, attackers can infer program execution flows that manipulate secrets and guess secrets such as encryption keys~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.
 

### 2021-03-22 Chapter-1/Chapter-1.tex
Updates from Overleaf

--- 2021-03-19 Chapter-1/Chapter-1.tex
@@
 \chapter{Introduction} \label{chapter1}
-
-Side-channels are ubiquitous in modern computer systems as sensitive information may be leaked through many kinds of negligent behaviors, such as power, electromagnetic radiation, or even sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}.
+Side channels are ubiquitous in modern computer systems as sensitive
+information can leak through many mechanisms such as power,
+electromagnetic radiation, and even sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}.
 It is typically hard to fix all side-channel vulnerabilities for real-world software systems.
 
-Among them, address-based side channel attacks, such as cache attacks, memory page attacks, and controlled-channel attacks, are especially common and have been studied for years~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}.
-These
-attacks result from vulnerable software and shared hardware components.
-By observing program outputs or hardware behaviors, attackers can infer program
-execution flows that manipulate secrets and guess secrets such as encryption
-keys~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.
+Among them, software side-channel attacks, such as cache attacks, memory page
+attacks, and controlled-channel attacks, are especially problematic as they do not require physical proximity~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}.
+These attacks arises from shared micro-architectural components in a computer processor.
+By observing inadvertent interactions between two programs, attackers can infer program execution flows that manipulate secrets and guess secrets such as encryption keys~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.
 
-In this chapter, we first introduce two code patterns that can be exploited to retrieve sensitive information.
-After that, we discuss some common attacks and corresponding defense strategies.
-The limitations of existing work motivate the research in the dissertation.
-Finally, we summarize the contributions of the dissertation.
+Many side-channel attacks originate in two code patterns: data flow from secrets to load addresses and data flow from secrets to branch conditions.
+We refer to them as secret-dependent data accesses and control flows, respectively.
+
+Recent work~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} can detect many side-channel vulnerabilities.
+For example, DATA~\cite{217537} reports 2,248 potential leakage sites for the RSA
+implementation in OpenSSL 1.1.0f\@. 
+Further analysis shows 1,510 leaks can be dismissed. But that
+leaves 460 data-access leaks and 278 control-flow leaks. 
+Many of these vulnerabilities have not been fixed by developers for a variety of reasons.
+
+First, some vulnerable implementations perform better. For example,
+RSA implementations usually adopt the CRT optimization,
+which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}.
+Second, fixing vulnerabilities can introduce new 
+weaknesses. Third, most vulnerabilities pose a negligible risk. 
+Although some vulnerabilities result in the key being 
+entirely compromised~\cite{184415, aumuller2002fault}, 
+many others are less severe in reality. Therefore, we need a proper quantification metric to  assess the sensitivity of side-channel vulnerabilities, so a developer can efficiently triage them.
+
+Previous work~\cite{182946,5207642} can identify numerous leakages or even provide an upper bound on the amount of leakage, which is useful to verify that an implementation is secure if it incurs zero leakage.
+However, these techniques cannot quantify the severity of a leak because they over approximate the leakage. For example, CacheAudit~\cite{182946} 
+reports that the upper-bound leakage of AES-128 exceeds the original key size.
+Besides, existing side-channel quantification work~\cite{182946,5207642} assumes an attacker runs the target program multiple times with different
+input secrets and calculates an ``average'' estimation, which is different from real attack scenarios when the secret that an attacker wants to retrieve is fixed.
+As a consequence, those results are less useful to assess the severity level of each leakage site.
 

### 2021-03-22 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 It is typically hard to fix all side-channel vulnerabilities for real-world software systems.
-
-Among them, software side-channel attacks, such as cache attacks, memory page
-attacks, and controlled-channel attacks, are especially problematic as they do not require physical proximity~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}.
+Among them, software side-channel attacks, such as cache attacks, memory page attacks, and controlled-channel attacks, are especially problematic as they do not require physical proximity~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}.
 These attacks arises from shared micro-architectural components in a computer processor.
@@
 
-Many side-channel attacks originate in two code patterns: data flow from secrets to load addresses and data flow from secrets to branch conditions.
-We refer to them as secret-dependent data accesses and control flows, respectively.
+Various countermeasures have been proposed to defend against
+side channel attacks. Hardware-level solutions, such as reducing shared
+resources, adopting oblivious RAM, and using transnational
+memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need new
+hardware features and changes in modern complex computer systems, which are
+hard to adopt in reality.
+Therefore, a promising and universal direction is software countermeasures, detecting and eliminating side channel vulnerabilities from code base.
+It is due to the following reason: many side-channel attacks originate in two code patterns: data flow from secrets to load addresses and data flow from secrets to branch conditions.
+We refer to them as secret-dependent data accesses and control flows respectively in the dissertation.
 
+However, eliminating side channel vulnerabilities from real-world software code base is not easy.
+First, some vulnerable implementations perform better.
+For example, RSA implementations usually adopt the CRT optimization,
+which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}. Fixing vulnerabilities can introduce new 
+weaknesses.
+Second, it is hard to detect side channels in reality.
+While recent work~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} can detect many side-channel vulnerabilities, they either suffer from expensive computation cost or high false positives and false negatives.
 Recent work~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} can detect many side-channel vulnerabilities.
-For example, DATA~\cite{217537} reports 2,248 potential leakage sites for the RSA
-implementation in OpenSSL 1.1.0f\@. 
-Further analysis shows 1,510 leaks can be dismissed. But that
-leaves 460 data-access leaks and 278 control-flow leaks. 
+For example, DATA~\cite{217537} reports 2,248 potential leakage sites for the RSA implementation in OpenSSL 1.1.0f\@.
+Further analysis shows 1,510 leaks can be dismissed.
+But that leaves 460 data-access leaks and 278 control-flow leaks.
 Many of these vulnerabilities have not been fixed by developers for a variety of reasons.
-
-First, some vulnerable implementations perform better. For example,
-RSA implementations usually adopt the CRT optimization,
-which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}.
-Second, fixing vulnerabilities can introduce new 
-weaknesses. Third, most vulnerabilities pose a negligible risk. 
+Third, most vulnerabilities pose a negligible risk.
 Although some vulnerabilities result in the key being 
@@
 As a consequence, those results are less useful to assess the severity level of each leakage site.
+
+We try to address the above problem from the following aspects.
+\begin{enumerate}
+\item 
+\item We propose a novel method to quantify information 
+leakage precisely from a single trace attack.
+We quantify the number of bits that can leak during a real execution and define the amount of leaked information as the cardinality of possible secrets based on an attacker's observation.
+Before an attack, an adversary has a large but finite input space.
+Whenever the adversary observes a leakage site, they can eliminate some impossible inputs and reduce the input space's size.
+In an extreme case, if the input space's size reduces to one, an adversary has determined the input, which means all secret information (e.g., the entire secret key) is
+leaked. By counting the number of inputs~\cite{10.1007/11499107_24}, we can quantify the information leakage precisely.
+We use symbolic execution to generate constraints to model the relation 
+between the original sensitive input and an attacker's observations. 
+Symbolic execution provides fine-grained information, but it is expensive
+to compute. Therefore, prior symbolic
+execution work~\cite{203878,236338,Brotzman19Casym} either analyzes only
+small programs or applies domain knowledge~\cite{203878} to simplify the analysis.
+We examine the bottleneck of the trace-oriented symbolic execution and optimize it to work for real-world crypto-systems.
+
+\end{enumerate}
 

### 2021-03-22 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 We refer to them as secret-dependent data accesses and control flows respectively in the dissertation.
+
+On the contrary, software approaches are
+usually easy to implement. The basic idea is to eliminate key-dependent
+control-flow transfers and data accesses. By removing the above two kinds of code patterns, developers protect their 
+code from a series of side-channel attacks.
 
@@
 \begin{enumerate}
-\item 
-\item We propose a novel method to quantify information 
+\item \textbf{Detection.} We propose a fast and precise side-channel detection method.
+Different from previous trace comparison based methods, our method has fewer false positives and false negatives.
+Compared with methods based on symbolic execution and abstract interpretation, our methods can work on real-world cryptography libraries.
+Symbolic execution provides fine-grained information, but it is expensive to compute.
+Therefore, prior symbolic
+execution work~\cite{203878,236338,Brotzman19Casym} either analyzes only
+small programs or applies domain knowledge~\cite{203878} to simplify the analysis.
+We examine the bottleneck of the trace-oriented symbolic execution and optimize it to work for real-world crypto-systems.
+\item \textbf{Quantification.} We propose methods to quantify information 
 leakage precisely from a single trace attack.
@@
 In an extreme case, if the input space's size reduces to one, an adversary has determined the input, which means all secret information (e.g., the entire secret key) is
-leaked. By counting the number of inputs~\cite{10.1007/11499107_24}, we can quantify the information leakage precisely.
-We use symbolic execution to generate constraints to model the relation 
+leaked. By counting the number of inputs~\cite{10.1007/11499107_24}, we can quantify the information leakage precisely. We use symbolic execution to generate constraints to model the relation 
 between the original sensitive input and an attacker's observations.
-Symbolic execution provides fine-grained information, but it is expensive
-to compute. Therefore, prior symbolic
-execution work~\cite{203878,236338,Brotzman19Casym} either analyzes only
-small programs or applies domain knowledge~\cite{203878} to simplify the analysis.
-We examine the bottleneck of the trace-oriented symbolic execution and optimize it to work for real-world crypto-systems.
 
 \end{enumerate}
-
-\section{Address-based Side-channel}
-\subsection{Attack}
-Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses.
-Most systems allows the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim.
-As a result, while the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.
-
-Cache channels rely on the time difference between cache misses and cache hits.
-A cache channel works when the victim program and the attacker's program shares some sized chunks like cache lines or cache sets.
-Recent studies shows that an attacker can even observe the address access at a finer granularity (e.g., CacheBleed).
-Page-level side-channels allow attackers observe the memory access at the granularity of memory pages.
-
-In this dissertation, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs).
-To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.
-
-When we examine those side-channel attacks, many of them stem from the two code patterns, \emph{secret-dependent control-flow transfers} and \emph{secret-dependent data accesses}.
-\begin{figure}[h]
-\begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
-int secret[32];
-...
-while(i>0){
-    r = (r * r) % n;
-    if(secret[--i] == 1)
-        r = (r * x) % n;   
-}
-\end{lstlisting}
-\caption{Secret-dependent control-flow transfers}
-\label{fig:secret:cf}
-\end{figure}
-
-Secret-dependent control-flow transfers happen when the value of secret can affect which branch the code executes.
-Figure~\ref{fig:secret:cf} shows an example.
-Depending on the value of \textsf{secret}, the code may or may not execute the code at line 6.
-As attackers, they can retrieve some information based on the execution control-flow.
-
-\begin{figure}[h]
-\begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
-static char FSb[256] = {...}
-... 
-uint32_t a = *RK++ ^ \ 
-(FSb[(secret)) ^
-(FSb[(secret >> 8)] << 8 ) ^
-(FSb[(secret >>16)] << 16 ) ^
-(FSb[(secret >>24)] << 24 );
-...
-\end{lstlisting}
-\caption{Secret-dependent data accesses}
-\label{fig:secret:da}
-\end{figure}
-
-Secret-dependent data accesses happen when the value of the secret can affect which memory cell the code reads or writes.
-Figure~\ref{fig:secret:da} shows an example.
-\textsf{FSb} is an array.
-Depending on the value of \textsf{secret}, the code may read or write different items in the array.
-
-\subsection{Defense}
-
-Both hardware~\cite{Page2005PartitionedCA,
-Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
-236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
-brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
-been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
-accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
-architecture~\cite{tiwari2011crafting}, require changes to complex processors and are complex to adopt.
-
-On the contrary, software approaches are
-usually easy to implement. The basic idea is to eliminate key-dependent
-control-flow transfers and data accesses. By removing the above two kinds of code patterns, developers protect their 
-code from a series of side-channel attacks.
 

### 2021-03-22 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 after restricting some code and data pages.
+
+Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses.
+Most systems allows the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim.
+As a result, while the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.
+
+Cache channels rely on the time difference between cache misses and cache hits.
+A cache channel works when the victim program and the attacker's program shares some sized chunks like cache lines or cache sets.
+Recent studies shows that an attacker can even observe the address access at a finer granularity (e.g., CacheBleed).
+Page-level side-channels allow attackers observe the memory access at the granularity of memory pages.
+
+In this dissertation, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs).
+To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.
+
+When we examine those side-channel attacks, many of them stem from the two code patterns, \emph{secret-dependent control-flow transfers} and \emph{secret-dependent data accesses}.
+\begin{figure}[h]
+\begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
+int secret[32];
+...
+while(i>0){
+    r = (r * r) % n;
+    if(secret[--i] == 1)
+        r = (r * x) % n;   
+}
+\end{lstlisting}
+\caption{Secret-dependent control-flow transfers}
+\label{fig:secret:cf}
+\end{figure}
+
+Secret-dependent control-flow transfers happen when the value of secret can affect which branch the code executes.
+Figure~\ref{fig:secret:cf} shows an example.
+Depending on the value of \textsf{secret}, the code may or may not execute the code at line 6.
+As attackers, they can retrieve some information based on the execution control-flow.
+
+\begin{figure}[h]
+\begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
+static char FSb[256] = {...}
+... 
+uint32_t a = *RK++ ^ \ 
+(FSb[(secret)) ^
+(FSb[(secret >> 8)] << 8 ) ^
+(FSb[(secret >>16)] << 16 ) ^
+(FSb[(secret >>24)] << 24 );
+...
+\end{lstlisting}
+\caption{Secret-dependent data accesses}
+\label{fig:secret:da}
+\end{figure}
+
+Secret-dependent data accesses happen when the value of the secret can affect which memory cell the code reads or writes.
+Figure~\ref{fig:secret:da} shows an example.
+\textsf{FSb} is an array.
+Depending on the value of \textsf{secret}, the code may read or write different items in the array.
 

### 2021-03-22 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 \chapter{Introduction} \label{chapter1}
+\section{Side-channel Analysis}
 Side channels are ubiquitous in modern computer systems as sensitive
@@
 
-We try to address the above problem from the following aspects.
+In summary, it is hard to apply software approaches in practice due to the following reasons.
+
+\begin{enumerate}
+    \item It is hard to identify side-channel vulnerabilities in real-world software.
+In general, many side-channel vulnerabilities are low-level problems.
+Control-flows or memory accesses may not be side-channel vulnerabilities if they are independent of original secret inputs.
+Recent work can identify side-channel leakages.
+But those tools can only work on small programs or need to apply some domain knowledge to simplify the analysis.
+    \item Side-channel vulnerabilities are ubiquitous.
+While some vulnerabilities can result in the key being entirely compromised, many other vulnerabilities are hard to exploit.
+Moreover, some vulnerable implementations perform better.
+Recent work can identify thousands of leaked points, but most of them are not patched by developers because those leakages are either false positives or leaked very little information.
+\end{enumerate}
+
+We try to address the above problem from the following two aspects.
 \begin{enumerate}
@@
 between the original sensitive input and an attacker's observations. 
-
-\end{enumerate}
-
-However, it is still hard to apply software approaches in practice due to the following reasons.
-
-\begin{enumerate}
-    \item It is hard to identify side-channel vulnerabilities in real-world software.
-In general, many side-channel vulnerabilities are low-level problems.
-Control-flows or memory accesses may not be side-channel vulnerabilities if they are independent of original secret inputs.
-Recent work can identify side-channel leakages.
-But those tools can only work on small programs or need to apply some domain knowledge to simplify the analysis.
-    \item Side-channel vulnerabilities are ubiquitous.
-While some vulnerabilities can result in the key being entirely compromised, many other vulnerabilities are hard to exploit.
-Moreover, some vulnerable implementations perform better.
-Recent work can identify thousands of leaked points, but most of them are not patched by developers because those leakages are either false positives or leaked very little information.
 \end{enumerate}
@@
 In addition, we study two kinds of threat models, single-trace attacks, and chosen message attacks.
-
 In summary, we make the following contributions:

### 2021-03-23 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 \section{Side-channel Attacks}
+Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses.
+Most systems allows the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim.
+As a result, while the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.
+
 Side channels can leak sensitive information
@@
 hardware components (e.g., CPU cache, TLB, and
-DRAM) in modern computer systems~\cite{ge2018survey,szefer2019survey}.
+DRAM) in modern computer system~\cite{ge2018survey,szefer2019survey}.
 
@@
 after restricting some code and data pages.
-
-Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses.
-Most systems allows the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim.
-As a result, while the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.
 

### 2021-03-23 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 \chapter{Introduction} \label{chapter1}
-\section{Side-channel Analysis}
+\section{Side-channels}
 Side channels are ubiquitous in modern computer systems as sensitive
@@
 By observing inadvertent interactions between two programs, attackers can infer program execution flows that manipulate secrets and guess secrets such as encryption keys~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.
+
+When we examine those side-channel attacks, many of them stem from the two code patterns, \emph{secret-dependent control-flow transfers} and \emph{secret-dependent data accesses}.
+\begin{figure}[h]
+\begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
+int secret[32];
+...
+while(i>0){
+    r = (r * r) % n;
+    if(secret[--i] == 1)
+        r = (r * x) % n;   
+}
+\end{lstlisting}
+\caption{Secret-dependent control-flow transfers}
+\label{fig:secret:cf}
+\end{figure}
+
+Secret-dependent control-flow transfers happen when the value of secret can affect which branch the code executes.
+Figure~\ref{fig:secret:cf} shows an example.
+Depending on the value of \textsf{secret}, the code may or may not execute the code at line 6.
+As attackers, they can retrieve some information based on the execution control-flow.
+
+\begin{figure}[h]
+\begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
+static char FSb[256] = {...}
+... 
+uint32_t a = *RK++ ^ \ 
+(FSb[(secret)) ^
+(FSb[(secret >> 8)] << 8 ) ^
+(FSb[(secret >>16)] << 16 ) ^
+(FSb[(secret >>24)] << 24 );
+...
+\end{lstlisting}
+\caption{Secret-dependent data accesses}
+\label{fig:secret:da}
+\end{figure}
+
+Secret-dependent data accesses happen when the value of the secret can affect which memory cell the code reads or writes.
+Figure~\ref{fig:secret:da} shows an example.
+\textsf{FSb} is an array.
+Depending on the value of \textsf{secret}, the code may read or write different items in the array.
 

### 2021-03-23 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.
-
-When we examine those side-channel attacks, many of them stem from the two code patterns, \emph{secret-dependent control-flow transfers} and \emph{secret-dependent data accesses}.
-\begin{figure}[h]
-\begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
-int secret[32];
-...
-while(i>0){
-    r = (r * r) % n;
-    if(secret[--i] == 1)
-        r = (r * x) % n;   
-}
-\end{lstlisting}
-\caption{Secret-dependent control-flow transfers}
-\label{fig:secret:cf}
-\end{figure}
-
-Secret-dependent control-flow transfers happen when the value of secret can affect which branch the code executes.
-Figure~\ref{fig:secret:cf} shows an example.
-Depending on the value of \textsf{secret}, the code may or may not execute the code at line 6.
-As attackers, they can retrieve some information based on the execution control-flow.
-
-\begin{figure}[h]
-\begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
-static char FSb[256] = {...}
-... 
-uint32_t a = *RK++ ^ \ 
-(FSb[(secret)) ^
-(FSb[(secret >> 8)] << 8 ) ^
-(FSb[(secret >>16)] << 16 ) ^
-(FSb[(secret >>24)] << 24 );
-...
-\end{lstlisting}
-\caption{Secret-dependent data accesses}
-\label{fig:secret:da}
-\end{figure}
-
-Secret-dependent data accesses happen when the value of the secret can affect which memory cell the code reads or writes.
-Figure~\ref{fig:secret:da} shows an example.
-\textsf{FSb} is an array.
-Depending on the value of \textsf{secret}, the code may read or write different items in the array.
 

### 2021-03-23 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 Depending on the value of \textsf{secret}, the code may read or write different items in the array.
+
+The key intuition is that above side-channel attacks happen when a
+program accesses different memory addresses if the program has different
+sensitive inputs. As shown in Figure~\ref{fig:secret:cf} and Figure~\ref{fig:secret:da}, 
+if a program shows different patterns in
+control transfers or data accesses when the program processes different
+sensitive inputs, the program could possibly have side channels vulnerabilities.
+Different kinds of side-channels can be exploited to retrieve information in
+various granularities. For example, cache channels can observe cache
+accesses at the level of cache sets~\cite{liu2015last}, cache lines~\cite{184415} or other granularities. 
+Other kinds of side-channels like controlled-channel attack~\cite{7163052},
+can observe the memory access at the level of memory pages.
 

### 2021-03-23 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses.
-Most systems allows the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim.
+Most systems allows the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim~\cite{ge2018survey,szefer2019survey}.
 As a result, while the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.
 
-Side channels can leak sensitive information
-unconsciously through different execution behaviors caused by shared 
-hardware components (e.g., CPU cache, TLB, and
-DRAM) in modern computer system~\cite{ge2018survey,szefer2019survey}.
+\begin{table}
+\centering
+\caption{Due to the page limit, we only shows some representations of the vast side-channel attacks: Attacks, the shared hardware resources with attackers, the granularity of the attacker can observe, is there any published attacks on non-cryptography library and if the type of attack can exploit multiple leakage sites.}
+\label{table:side_channel_attack}
+\resizebox{\columnwidth}{!}{%
+
+\begin{tabular}{lllcc}
+\toprule
+Attacks & Shared Resources & Granularity  & Non-Crpyto & Multiple   \\ \midrule
+CacheBleed~\cite{yarom2017cachebleed} & Cache & Sub Cache Line (<64 B)  & \xmark & \xmark \\ 
+CopyCat~\cite{moghimi2020copycat} & Page Tables   & Instruction   & \xmark &  \xmark \\
+Prime + Probe~\cite{liu2015last} & Cache & Cache Set (64-512 B)  & \cmark &   \xmark \\
+Prime + Abort~\cite{disselkoen2017prime+} & Cache  & Cache Set (64-512 B) & \cmark &  \xmark   \\
+Flush + Reload~\cite{yarom2014flush+} & Cache & Cache Line (64 B) & \cmark  &  \cmark \\
+Flush + Flush~\cite{gruss2016flush+} & Cache & Cache Line (64 B) & \cmark & \xmark  \\
+Controlled-channel Attack~\cite{xu2015controlled} & Page Tables & Page (4KB) & \cmark & \xmark \\
+TLBleed~\cite{gras_translation_2018} & MMUs & TLB Set (4KB) & \cmark  & \xmark \\
+Page Cache Attacks~\cite{gruss2019page} & Page Cache &  Page (4KB) & \xmark &  \cmark \\ 
+\bottomrule
+\end{tabular}
+}
+\end{table}
 
@@
 To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.
-
-The key intuition is that above side-channel attacks happen when a
-program accesses different memory addresses if the program has different
-sensitive inputs. As shown in Figure~\ref{fig:secret:cf} and Figure~\ref{fig:secret:da}, 
-if a program shows different patterns in
-control transfers or data accesses when the program processes different
-sensitive inputs, the program could possibly have side channels vulnerabilities.
-Different kinds of side-channels can be exploited to retrieve information in
-various granularities. For example, cache channels can observe cache
-accesses at the level of cache sets~\cite{liu2015last}, cache lines~\cite{184415} or other granularities. 
-Other kinds of side-channels like controlled-channel attack~\cite{7163052},
-can observe the memory access at the level of memory pages.
 

### 2021-03-23 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses.
-Most systems allows the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim~\cite{ge2018survey,szefer2019survey}.
-As a result, while the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.
+In many situations,  computer systems allow the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim~\cite{ge2018survey,szefer2019survey}.
+As a result, an attacker can probe the shared hardware resource to infer the sensitive information.
+While the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.
 
@@
 
-For example, cached-based
+For example, cached
 side-channels~\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last,184415}

### 2021-03-23 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 
-For example, cached
-side-channels~\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last,184415}
-rely on the time difference between cache misses and cache hits. We introduce two
-common attack strategies, namely Prime+Probe~\cite{liu2015last} and
-Flush+Reload~\cite{184415}. Prime+Probe targets a single cache set. An
-attacker preloads the cache set with its own data and waits until the victim
-executes the program. If the victim accesses the cache set and evicts part of
-the data, the attacker will experience a slow measurement. 
-While Flush+Reload targets a
-single cache line, it requires the attacker and victim share some memory. 
-During the ``flush'' stage, the attacker flushes the ``monitored
-memory'' from the cache and waits for the victim to access the memory,
-who will load the sensitive information to the cache line. In the next phase,
-the attacker reloads the ``monitored memory''. By measuring the time difference
-brought by cache hit and miss, the attacker can further infer the sensitive information.
-Some other types of side-channels target different hardware
-layers other than CPU cache. For example, the controlled-channel
-attack~\cite{7163052}, where an attacker works in the kernel space, can infer
-sensitive data in shielding systems by observing the page fault sequences
-after restricting some code and data pages.
-
-Cache channels rely on the time difference between cache misses and cache hits.
-A cache channel works when the victim program and the attacker's program shares some sized chunks like cache lines or cache sets.
-Recent studies shows that an attacker can even observe the address access at a finer granularity (e.g., CacheBleed).
-Page-level side-channels allow attackers observe the memory access at the granularity of memory pages.
-
-In this dissertation, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs).
-To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.
-
 \subsection{Cache-level Channel}
-Cache-based channels rely on the time difference between cache misses and cache hits. Cache channel attacks can observe cache accesses at the level of cache sets, cache lines or other granularities. 
+Cache channels~\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last,184415} rely on the time difference between cache misses and cache hits.
+Cache channel attacks can observe cache accesses at the level of cache sets, cache lines or other granularities.
 We introduce two common attack strategies, namely Prime+Probe and
@@
 layers other than CPU cache.
+
+Cache channels rely on the time difference between cache misses and cache hits.
+A cache channel works when the victim program and the attacker's program shares some sized chunks like cache lines or cache sets.
+Recent studies shows that an attacker can even observe the address access at a finer granularity (e.g., CacheBleed).
+Page-level side-channels allow attackers observe the memory access at the granularity of memory pages.
 

### 2021-03-23 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses.
-In many situations,  computer systems allow the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim~\cite{ge2018survey,szefer2019survey}.
+In many situations,  computer systems allow the attacker to shares some hardware resources (e.g., Cache, TLB, and DRAM) with the victim~\cite{ge2018survey,szefer2019survey}.
 As a result, an attacker can probe the shared hardware resource to infer the sensitive information.
@@
 \end{table}
+
+Table~\ref{table:side_channel_attack} shows some representations of the recent side-channel attacks.
 

### 2021-03-23 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 \section{Side-channel Attacks}
-Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses.
-In many situations,  computer systems allow the attacker to shares some hardware resources (e.g., Cache, TLB, and DRAM) with the victim~\cite{ge2018survey,szefer2019survey}.
-As a result, an attacker can probe the shared hardware resource to infer the sensitive information.
+Address-based side-channel attacks happen when a program accesses different memory addresses when it processes different secrets.
+In many situations, an attacker may shares some hardware resources (e.g., Cache, TLB, and DRAM) with the victim in today's computer system ~\cite{ge2018survey,szefer2019survey}.
+As a result, the attacker can probe the shared hardware resource to infer the sensitive information.
 While the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.
@@
 Table~\ref{table:side_channel_attack} shows some representations of the recent side-channel attacks.
+For a detailed overview of recent side-channel attacks, we refer to the following survey paper~\cite{ge2018survey}.
+We classified those side-channel attacks into two categories: cache channels and page channels.
 

### 2021-03-24 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 \section{Side-channel Attacks}
+While there are many kinds of side-channel attacks, we only study address-based side-channel attacks in this dissertation.
 Address-based side-channel attacks happen when a program accesses different memory addresses when it processes different secrets.
 In many situations, an attacker may shares some hardware resources (e.g., Cache, TLB, and DRAM) with the victim in today's computer system ~\cite{ge2018survey,szefer2019survey}.
-As a result, the attacker can probe the shared hardware resource to infer the sensitive information.
-While the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.
+As a result, the attacker can probe the shared hardware resource to infer the memory accesses of the victim.
+While the root cause of the attack is the same, there are various approaches and an attacker can exploit the attack to retrieve the information at different granularities.
 

### 2021-03-24 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 \subsection{Cache-level Channel}
+A CPU cache are an essential part in modern computer systems. It is a faster memory to reduce the average data accesses to the main memory.
 Cache channels~\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last,184415} rely on the time difference between cache misses and cache hits.

### 2021-03-24 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 \subsection{Cache-level Channel}
-A CPU cache are an essential part in modern computer systems. It is a faster memory to reduce the average data accesses to the main memory.
+A CPU cache are an essential part in modern computer systems.
+It is a faster memory to reduce the average data access costs to the main memory by storing copies of data from the main memory.
+When a CPU reads data from a memory location, it first check the memory location in the cache.
+If it finds the cache stores a copy of the memory location, a cache hit occurs.
+Otherwise, the CPU needs to read the data from the main memory and a cache miss happens.
 Cache channels~\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last,184415} rely on the time difference between cache misses and cache hits.

### 2021-03-24 Chapter-2/Chapter-2.tex
Updates from Overleaf

--- 2021-03-24 Chapter-2/Chapter-2.tex
@@
 \section{Side-channel Attacks}
-While there are many kinds of side-channel attacks, we only study address-based side-channel attacks in this dissertation.
-Address-based side-channel attacks happen when a program accesses different memory addresses when it processes different secrets.
+While there are many kinds of side-channel attacks, we focus on address-based side-channel attacks in this dissertation.
+Address-based side-channel attacks happen when a program accesses different memory locations when it processes different secrets.
 In many situations, an attacker may shares some hardware resources (e.g., Cache, TLB, and DRAM) with the victim in today's computer system ~\cite{ge2018survey,szefer2019survey}.
 As a result, the attacker can probe the shared hardware resource to infer the memory accesses of the victim.
-While the root cause of the attack is the same, there are various approaches and an attacker can exploit the attack to retrieve the information at different granularities.
+While the root cause of the attack is the same, there are various approaches and an attacker can exploit the vulnerability to retrieve the information at different granularities.
 
@@
 \subsection{Cache-level Channel}
-A CPU cache are an essential part in modern computer systems. It is a faster memory to reduce the average data accesses to the main memory.
+A CPU cache are an essential part in modern computer systems.
+It is a smaller and faster memory which is designed to reduce the average data access costs to the main memory by storing copies of data from the main memory.
+When a CPU reads data from a memory location, it first checks the memory location in the cache.
+If it finds that the cache stores a copy of the memory location, a cache hit occurs.
+Otherwise, the CPU needs to read the data from the main memory and a cache miss happens.
 Cache channels~\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last,184415} rely on the time difference between cache misses and cache hits.
 Cache channel attacks can observe cache accesses at the level of cache sets, cache lines or other granularities.
-We introduce two common attack strategies, namely Prime+Probe and
-Flush+Reload. Prime+Probe targets a single cache set. An
-attacker preloads the cache set with its own data and waits until the victim
-executes the program. If the victim accesses the cache set and evicts part of
-the data, the attacker will experience a slow measurement. 
-While Flush+Reload targets a single cache line, it requires the attacker and victim share some memory. During the ``flush'' stage, the attacker flushes the ``monitored
+We introduce two common attack strategies, namely Prime+Probe and Flush+Reload.
+
+\textbf{Prime+Probe.} Prime+Probe targets a single cache set. 
+An attacker primes the cache set with its own data and waits until the victim executes the program.
+After that, the attacker probes the cache by reading previously-loaded data.
+If the victim accesses the cache set and evicts some lines of the data, the attacker will experience a slow measurement.
+Under the circumstance, the attacker can know the victim must have touched some data that mapping to the same cache set.
+
+\textbf{Flush+Reload.} Flush+Reload allow an attacker to observe the memory at a fine granularity.
+It targets at a cache line instead of a cache set.
+While Flush+Reload targets a single cache line, it requires the attacker and victim share some memory.
+During the ``flush'' stage, the attacker flushes the ``monitored
 memory'' from the cache and waits for the victim to access the memory,
-who will load the sensitive information to the cache line. In the next phase,
+who may load the sensitive information to the cache line. On X86 machines, it can be achieved by using the \textsf{clflush} instruction. In the next phase,
 the attacker reloads the ``monitored memory''. By measuring the time difference

### 2021-03-24 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 
-\textbf{Flush+Reload.} Flush+Reload allow an attacker to observe the memory at a fine granularity.
-It targets at a cache line instead of a cache set.
+\textbf{Flush+Reload.} Flush+Reload allows an attacker to observe the memory at the granularity of cache line instead of a cache set.
 While Flush+Reload targets a single cache line, it requires the attacker and victim share some memory.
@@
 memory'' from the cache and waits for the victim to access the memory,
-who may load the sensitive information to the cache line. On X86 machines, it can be achieved by using the \textsf{clflush} instruction. In the next phase,
+who may load the sensitive information to the cache line. On X86-64 machines, it can be achieved by using the \textsf{clflush} instruction. In the next phase,
 the attacker reloads the ``monitored memory''. By measuring the time difference

### 2021-03-24 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 During the ``flush'' stage, the attacker flushes the ``monitored
-memory'' from the cache and waits for the victim to access the memory,
-who may load the sensitive information to the cache line. On X86-64 machines, it can be achieved by using the \textsf{clflush} instruction. In the next phase,
-the attacker reloads the ``monitored memory''. By measuring the time difference
-brought by cache hit and miss, the attacker can further infer the sensitive information. Some other types of side-channels target different hardware
-layers other than CPU cache.
+memory'' from the cache and waits for the victim to access the memory, who may load the sensitive information to the cache line.  In the next phase,
+the attacker reloads the ``monitored memory''. By measuring the time differences
+brought by cache hits and misses, the attacker can further infer the sensitive information.
+On X86-64 machines, the two steps can be combined by measuring the time differences of the \textsf{clflush} instruction.
+
+Some other types of side-channels target different hardware layers other than CPU cache.
 

### 2021-03-24 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 Flush + Flush~\cite{gruss2016flush+} & Cache & Cache Line (64 B) & \cmark & \xmark  \\
-Controlled-channel Attack~\cite{xu2015controlled} & Page Tables & Page (4KB) & \cmark & \xmark \\
-TLBleed~\cite{gras_translation_2018} & MMUs & TLB Set (4KB) & \cmark  & \xmark \\
-Page Cache Attacks~\cite{gruss2019page} & Page Cache &  Page (4KB) & \xmark &  \cmark \\ 
+Controlled-channel Attack~\cite{xu2015controlled} & Page Tables & Page (4 KB) & \cmark & \xmark \\
+TLBleed~\cite{gras_translation_2018} & MMUs & TLB Set (4 KB) & \cmark  & \xmark \\
+Page Cache Attacks~\cite{gruss2019page} & Page Cache &  Page (4 KB) & \xmark &  \cmark \\ 
 \bottomrule
@@
 
-Some other types of side-channels target different hardware layers other than CPU cache.
-
-Cache channels rely on the time difference between cache misses and cache hits.
-A cache channel works when the victim program and the attacker's program shares some sized chunks like cache lines or cache sets.
-Recent studies shows that an attacker can even observe the address access at a finer granularity (e.g., CacheBleed).
-Page-level side-channels allow attackers observe the memory access at the granularity of memory pages.
-
+Based on the above attacks, some work~\cite{brickell} suggests not having secret-dependent memory accesses at coarser than cache line granularity should be secure enough.
+However, recent studies shows that having memory accesses within a cache line is also dangerous.
+One example is the CacheBleed attack~\cite{yarom2017cachebleed}.
+It is a cache channel attack can exploits cache-back collisions.
 \subsection{Page-level Channel}

### 2021-03-24 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 
-Based on the above attacks, some work~\cite{brickell} suggests not having secret-dependent memory accesses at coarser than cache line granularity should be secure enough.
+Based on the above attacks, some work~\cite{brickell2011technologies} suggests not having secret-dependent memory accesses at coarser than cache line granularity should be secure enough.
 However, recent studies shows that having memory accesses within a cache line is also dangerous.

### 2021-03-24 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 \subsection{Page-level Channel}
-Recent studies also shows the attacks can observe the memory access at the granularity of memory pages.
+Page channel attacks can observe the memory access at the granularity of memory pages.
 One example is the controlled-channel attack~\cite{xu2015controlled}, where a privileged adversary try to infer the sensitive information by manipulating the enclave page access.
@@
 A malicious OS can proactively revoke a virtual enclave memory page from the memory.
-If the victim enclave program accesses the memory table, then the adversary can know which page is accessed by observing the page fault sequence.
+If the victim enclave program accesses the memory table, then the adversary can know which page is accessed by observing the page fault sequences.
 While the granularity of the controlled-channel attacks is coarse-grained, the controlled-channel attacks allow the attacker to have a noise-free observation.

### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 \subsection{Page-level Channel}
-Page channel attacks can observe the memory access at the granularity of memory pages.
+Page channel attacks allow an attacker can observe the memory access at the granularity of memory pages.
 One example is the controlled-channel attack~\cite{xu2015controlled}, where a privileged adversary try to infer the sensitive information by manipulating the enclave page access.
@@
 \subsection{Target Applications}
-While there is a vast number of studies\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last} on side-channel attacks and detections, we find many of those work targets on the encryption key on cryptography libraries.
-In terms of the non-cryptography side-channel attacks.
-We find many of them can be classified into the below three categories.
+While there is a vast number of studies\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last} on side-channel attacks, we find many of those work targets on the encryption key on cryptography libraries.
+We find current side-channel attacks can be classified into the below three categories.
 

### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 While there is a vast number of studies\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last} on side-channel attacks, we find many of those work targets on the encryption key on cryptography libraries.
-We find current side-channel attacks can be classified into the below three categories.
+In general, current side-channel attacks can be classified into the below three categories.
 
 \subsubsection{Cryptography Libraries}
+The first side-channel attack of cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996.
+Many algorithms (Diffie-Helloman, RSA) implementations at that time use the simple modular exponentiation algorithm, which does not run in fixed time.
+By measuring the time differences between the  modular exponentiation algorithm computes the exponent bits (0 or 1), an attacker can recover the whole secret key bit by bit.
+Many well-known cryptography algorithms are vulnerable to side-channels.
 

### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 By measuring the time differences between the  modular exponentiation algorithm computes the exponent bits (0 or 1), an attacker can recover the whole secret key bit by bit.
-Many well-known cryptography algorithms are vulnerable to side-channels.
-
+Recently, cryptography libraries usually have several implementations of one algorithm.
+Symmetric ciphers like AES can have more than five implementations (OpenSSL). The reference implementation
+usually adopt T-Tables and S-Tables to speed up the computations. However, such implementation are vulnerable to side-channels and can be exploited to retrieve the whole key.
 \subsubsection{Machine Learning and Deep Learning Models}

### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

--- 2021-03-25 Chapter-2/Chapter-2.tex
@@
 By measuring the time differences between the  modular exponentiation algorithm computes the exponent bits (0 or 1), an attacker can recover the whole secret key bit by bit.
-Many well-known cryptography algorithms are vulnerable to side-channels.
-
+Cryptography libraries usually have several implementations for symmetric ciphers.
+Symmetric ciphers like AES can have more than five implementations (OpenSSL).
+The reference implementation usually adopts T-Tables and S-Tables to speed up the computations.
+However, such implementations are vulnerable to side-channels and can be exploited to retrieve the whole key~\cite{bonneau2006cache}.
+In addition to the reference implementation, those libraries also have side channel silent versions.
+However, recent studies also shows those versions also have side-channel vulnerabilities caused by compiler optimizations and human mistakes.
 \subsubsection{Machine Learning and Deep Learning Models}

### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 Many algorithms (Diffie-Helloman, RSA) implementations at that time use the simple modular exponentiation algorithm, which does not run in fixed time.
-By measuring the time differences between the  modular exponentiation algorithm computes the exponent bits (0 or 1), an attacker can recover the whole secret key bit by bit.
+By measuring the time differences between the modular exponentiation algorithm computes the exponent bits (0 or 1), Kocher's attack can recover the whole secret key bit by bit.
 Cryptography libraries usually have several implementations for symmetric ciphers.
-Symmetric ciphers like AES can have more than five implementations (OpenSSL).
-The reference implementation usually adopts T-Tables and S-Tables to speed up the computations.
+For example, AES can have more than five different implementations (OpenSSL).
+Depending on the build configuration and the return value of CPUID, the code may execute any implementation of them.
+The reference implementation usually adopts T-Tables and S-Tables to speed up the computation.
 However, such implementations are vulnerable to side-channels and can be exploited to retrieve the whole key~\cite{bonneau2006cache}.
 In addition to the reference implementation, those libraries also have side channel silent versions.
-However, recent studies also shows those versions also have side-channel vulnerabilities caused by compiler optimizations and human mistakes.
+However, recent studies also shows those versions also have side-channel vulnerabilities caused by compiler optimizations and human mistakes~\cite{217537}.
+The situation is even worse for asymmetric ciphers (e.g., Diffie-Helloman, RSA, ECDSA) because those those ciphers have a lots of big number calculations.
 \subsubsection{Machine Learning and Deep Learning Models}

### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 For example, AES can have more than five different implementations (OpenSSL).
-Depending on the build configuration and the return value of CPUID, the code may execute any implementation of them.
+Depending on the build configuration and the return value of \textsf{CPUID}, the code may execute any implementation of them.
 The reference implementation usually adopts T-Tables and S-Tables to speed up the computation.
@@
 The situation is even worse for asymmetric ciphers (e.g., Diffie-Helloman, RSA, ECDSA) because those those ciphers have a lots of big number calculations.
-\subsubsection{Machine Learning and Deep Learning Models}
-Previous side-channel attack mainly focus on recovering the input of the model and reversing the architecture of deep learning models.
-Hua et al.~\cite{hua2018reverse} were the first reverse engineer the architecture of neural networks.
-Wei et al.~\cite{wei2018know} perform the side-channel attacks on an FPG-based convolution neural network based on the power consumption to recover the real-world inputs.
-For the MNIST dataset, their attacks can achieve up 89\% accuracy.
-On the contrary, our attack based on the page access information can achieve accuracy.
-CSI NN~\cite{batina2019csi} reverse engineer the multi-layer perception and convolution neural network based on the Electromagnetic signal.
-Cache Telepathy~\cite{yan2020cache} introduce the cache based side-channel attack to extract DNN architecture.
-We mention that all existing approach need a lot of domain knowledge and expertise to launch the attack.
+It is hard to implement those calculations completely side-channel resistant.
+Recent work~\cite{arnaud2013timing,yarom2017cachebleed,yarom2014flush+} has demonstrated several end-to-end attacks to recover the private keys of those ciphers.
+\subsubsection{Machine Learning Applications}
+Recent side-channel attack on machine learning applications mainly focus on recovering two types of the sensitive information: the input of the model, and the architecture of deep learning models.
+Hua et al.~\cite{hua2018reverse} were the first in the literature to reverse engineer the architecture of convolutional neural networks (CNNs) through the memory access patterns.
+Wei et al.~\cite{wei2018know} perform the side-channel attacks on an FPG-based convolution neural network based on the power consumption to recover inputs to the networks.
+For an image classification task trained by the MNIST dataset, their attacks can achieve up 89\% accuracy.
+CSI NN~\cite{batina2019csi} reverse engineer the multi-layer perception and convolution neural network based on the electromagnetic signals (EMs).
+Cache Telepathy~\cite{yan2020cache} introduces the cache based side-channel attack to extract DNNs' architectures.
+We find that all existing approaches need a lot of domain knowledge and expertise to launch the attacks.
 \subsubsection{Media and Graphic Libraries}
-A few of recent work also studies the side-channel in media and graphic libraries.
-In the first controlled-channel attack~\cite{xu2015controlled}, they can recover the outline of the image by exploiting the vulnerability in the inverse DCT leakage site.
+A few of recent work also studies the side-channel attacks in media and graphic libraries.
+In the controlled-channel attack~\cite{xu2015controlled}, they can recover the outline of the image by exploiting the vulnerability in the inverse DCT leakage site.
 Daimeng et al.~\cite{wang2019unveiling} present the cache attack in graphic libraries.

### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 A few of recent work also studies the side-channel attacks in media and graphic libraries.
-In the controlled-channel attack~\cite{xu2015controlled}, they can recover the outline of the image by exploiting the vulnerability in the inverse DCT leakage site.
+In the controlled-channel attack~\cite{xu2015controlled}, Yuanzhong et al.
+demonstrate an attack to recover the outline of the image by exploiting the vulnerability in the inverse DCT function in libjpeg.
 Daimeng et al.~\cite{wang2019unveiling} present the cache attack in graphic libraries.
-Their approaches also combine a machine learning approach.
-However, they use the machine learning to infer the best exploitable cache line, while our approach use the machine learning to infer the total leaked information.
+Their approaches combine a machine learning approach.
+They use the machine learning to pick cache lines that can be exploitable to leak most information.
 \subsubsection{Others}
@@
 The attack to font libraries is essentially the same to the attack to the graphic library like GTK.
-By exploiting the differences of memory accesses when the program render each character, an attacker can recover part of the original sensitive information.
-We find most of those side-channel attacks target the trusted execution environments.
-We think part of the reason is that it is easy to argue that information in those libraries is also sensitive to users as well.
-
+By exploiting the differences of memory accesses when the program renders different characters, an attacker can recover parts of the original sensitive information.
+Other side-channel attacks target on the kernel of the operating system.
+We list two examples here.
+One example is the to use the side-channel attacks to break the kernel address space randomization (KASLR).
 \section{Detection and Mitigation}
@@
     Flush + Flush~\cite{gruss2016flush+} & Cache & Cache Line (64 B) & \cmark & \xmark  \\
-    Controlled-channel Attack~\cite{xu2015controlled} & Page Tables & Page (4KB) & \cmark & \xmark \\
-    TLBleed~\cite{gras_translation_2018} & MMUs & TLB Set (4KB) & \cmark  & \xmark \\
-    Page Cache Attacks~\cite{gruss2019page} & Page Cache &  Page (4KB) & \xmark &  \cmark \\ 
+    Controlled-channel Attack~\cite{xu2015controlled} & Page Tables & Page (4 KB) & \cmark & \xmark \\
+    TLBleed~\cite{gras_translation_2018} & MMUs & TLB Set (4 KB) & \cmark  & \xmark \\
+    Page Cache Attacks~\cite{gruss2019page} & Page Cache &  Page (4 KB) & \xmark &  \cmark \\ 
     \bottomrule

### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 Some other side-channel targets also include spell checking tools, and font libraries~\cite{xu2015controlled}.
-The attack to font libraries is essentially the same to the attack to the graphic library like GTK.
+The attack to font libraries is essentially the same as the attack to the graphic library like GTK.
 By exploiting the differences of memory accesses when the program renders different characters, an attacker can recover parts of the original sensitive information.
@@
 One example is the to use the side-channel attacks to break the kernel address space randomization (KASLR).
+Many exploits rely on the knowledge of the memory location of a certain kernel function.
+Since Linux 4.12, the kernel loads core kernel image and device drivers at random positions during the boot time.
 \section{Detection and Mitigation}
@@
 According to Table~\ref{table:related_work}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction.
+Jang et al.~\cite{jang2016breaking} rely on side-channels to reveal mapping status of each page.
+After that, they detect kernel modules with unique size signatures to break KASLR.
 

### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 Since Linux 4.12, the kernel loads core kernel image and device drivers at random positions during the boot time.
+Jang et al.~\cite{jang2016breaking} rely on side-channels to reveal mapping status of each page.
+After that, they detect kernel modules with unique size signatures to break KASLR.
+
 \section{Detection and Mitigation}
@@
 According to Table~\ref{table:related_work}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction.
-Jang et al.~\cite{jang2016breaking} rely on side-channels to reveal mapping status of each page.
-After that, they detect kernel modules with unique size signatures to break KASLR.
 

### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 Other side-channel attacks target on the kernel of the operating system.
-We list two examples here.
 One example is the to use the side-channel attacks to break the kernel address space randomization (KASLR).
@@
 After that, they detect kernel modules with unique size signatures to break KASLR.
+The second example relies on the side-channel vulnerabilities~\cite{cao2019principled} inside kernels to infer the TCP sequence numbers, which can be used to hijack connections between the client and the server~\cite{cao2016off}.
 
@@
 While there are several existing work on side-channel leakage detections, we find it very hard to apply existing methods to identify controlled-channel attacks.
-According to Table~\ref{table:related_work}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction.
+According to Table~\ref{table:side_channel_detection_tool}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction.
 
-\textbf{Trace comparison.} If the victim program has two different execution traces with two different sensitive inputs, then we can distinguish the sensitive input by observing the execution trace.
+\textbf{Trace comparison.} If a program has two different execution traces under two different sensitive inputs, then attacker can distinguish the sensitive input by observing the execution trace.
 Therefore, we can conclude the program is vulnerable to side-channel attacks.
@@
 Moreover, the approach does not need to model or abstract the program's semantics.
-In general, the approach is quite salable.
-On the negative side, comparing the trace along can only find the leakage, but it cannot find the complex relationship between the leakage site and the original buffer.
+In general, the approach is quite fast.
+On the negative side, comparing the trace along can find the leakage, but it cannot find the complex relationship between the leakage site and the original buffer.
 For example, if two leakage sites leak the same information in the original buffer, those approaches cannot find out the two leakage sites are the same.
@@
 Moreover, it can model multiple leakages precisely as the conjunction of those formulas.
-However, after some initial investigations and experiments, we find such approach fails in practice due to the below reasons.
+However, such approach has the following limitations.
 
@@
 
-According to Table~\ref{table:side_channel_detection_tool}, some methods may choose to analyze the source code or the intermediate languages.
+According to Table~\ref{table:side_channel_detection_tool}, some methods may choose to analyze the source code or the intermediate representations of the vulnerable software.
 However, it still cannot solve the problem.
@@
 However, it is difficult to judge the sensitive level of the side-channel leakage based on
-the leakage provided by CacheAudit. CacheS~\cite{236338} improves on
-CacheAudit with new abstract domains that only track
+the leakage provided by CacheAudit. CacheS~\cite{236338} improves the approach from
+CacheAudit with a new abstract model that only track
 secret-related code. Like CacheAudit, CacheS cannot
@@
 However, both imperfect trace alignment and statistical testing result that DATA can produce false positives.
-MicroWalk~\cite{Wichelmann:2018:MFF:3274694.3274741} uses
-mutual information (MI) between sensitive input and execution state to detect side-channels.
+MicroWalk~\cite{Wichelmann:2018:MFF:3274694.3274741} uses mutual information (MI) between sensitive input and execution state to detect side-channels. 
+\begin{adjustbox}{angle=90}
 
-\begin{table}
-    \centering
-    \caption{Due to the page limit, we only shows some representations of the vast side-channel attacks: Attacks, the shared hardware resources with attackers, the granularity of the attacker can observe, is there any published attacks on non-cryptography library and if the type of attack can exploit multiple leakage sites.}
-    \label{table:side_channel_detection_tool}
-    \resizebox{\columnwidth}{!}{%
+\begin{table*}
+%\centering
+\caption{Existing leakage detection tool only evaluate them on cryptography library.
+1.
+Most recent work only evaluates their approaches on cryptography libraries.
+2.
+All of them can not reason about the total effect of multiple leakages.}
+\label{table:related_work}
+\resizebox{2\columnwidth}{!}{%
 
-    \begin{tabular}{lllcc}
+\begin{tabular}{lllcclc}
 \toprule
-    Attacks & Shared Resources & Granularity  & Non-Crpyto & Multiple   \\ \midrule
-    CacheBleed~\cite{yarom2017cachebleed} & Cache & Sub Cache Line (<64 B)  & \xmark & \xmark \\ 
-    CopyCat~\cite{moghimi2020copycat} & Page Tables   & Instruction   & \xmark &  \xmark \\
-    Prime + Probe~\cite{liu2015last} & Cache & Cache Set (64-512 B)  & \cmark &   \xmark \\
-    Prime + Abort~\cite{disselkoen2017prime+} & Cache  & Cache Set (64-512 B) & \cmark &  \xmark   \\
-    Flush + Reload~\cite{yarom2014flush+} & Cache & Cache Line (64 B) & \cmark  &  \cmark \\
-    Flush + Flush~\cite{gruss2016flush+} & Cache & Cache Line (64 B) & \cmark & \xmark  \\
-    Controlled-channel Attack~\cite{xu2015controlled} & Page Tables & Page (4 KB) & \cmark & \xmark \\
-    TLBleed~\cite{gras_translation_2018} & MMUs & TLB Set (4 KB) & \cmark  & \xmark \\
-    Page Cache Attacks~\cite{gruss2019page} & Page Cache &  Page (4 KB) & \xmark &  \cmark \\ 
+Tool & S/D & Method  & AVX/SIMD  & Multiple & Evaluation & Available \\ \midrule
+CacheAudit~\cite{doychev2015cacheaudit} & Static  & Abstraction  & \xmark & \xmark & Crypto Algorithm  & \cmark \\ 
+CacheD~\cite{wang2017cached} & Dynamic  & Symbolic Execution + Taint Analysis  & \xmark & \xmark & Libgcrypt, OpenSSL & \xmark \\
+CachSym~\cite{brotzman2019casym} & Static & Symbolic Execution  & \xmark & \xmark & Crypto Snippet & \xmark \\
+CacheS~\cite{wang2019identifying} & Static & Abstract Interpretation & \xmark & \xmark & Libgcrypt, OpenSSL, mbedTLS & \xmark \\
+DATA~\cite{weiser2018data} & Dynamic & Trace Alignment + Comparison & \cmark & \xmark & OpenSSL, PyCrypto & \cmark \\
+ctgrind~\cite{langley2010ctgrind} & Dynamic & Taint Analysis & \cmark & \xmark & Crypto Library & \cmark \\
+Satcco~\cite{xiao2017stacco} & Dynamic & Trace Comparison & \cmark & \xmark & OpenSSL, GnuTLS, mbedTLS, WolfTLS, LibreSSL & \xmark \\
+ANABLEPS~\cite{wang2019time} & Dynamic & Trace Comparison & \cmark & \xmark & Deep Learning, gsl, Hunspell, PNG, Freetype, QRcodegen, Genometools & \xmark \\
+MicroWalk~\cite{wichelmann2018microwalk} & Dynamic & Trace Comparison & \cmark & \xmark & Intel IPP, Microsoft CNG & \cmark \\ 
 \bottomrule
@@
 }
-    \end{table}
-
+\end{table*}
+\end{adjustbox}
 Both hardware~\cite{Page2005PartitionedCA,

### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 MicroWalk~\cite{Wichelmann:2018:MFF:3274694.3274741} uses mutual information (MI) between sensitive input and execution state to detect side-channels.
-\begin{adjustbox}{angle=90}
 
-\begin{table*}
+\begin{sidewaystable}
+
+%\begin{table*}
 %\centering
@@
 \label{table:related_work}
-\resizebox{2\columnwidth}{!}{%
+\resizebox{1\columnwidth}{!}{%
 
@@
 }
-\end{table*}
-\end{adjustbox}
+%\end{table*}
+\end{sidewaystable}
 Both hardware~\cite{Page2005PartitionedCA,

### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 All of them can not reason about the total effect of multiple leakages.}
-\label{table:related_work}
+\label{table:side_channel_detection_tool}
 \resizebox{1\columnwidth}{!}{%
@@
 Tool & S/D & Method  & AVX/SIMD  & Multiple & Evaluation & Available \\ \midrule
-CacheAudit~\cite{doychev2015cacheaudit} & Static  & Abstraction  & \xmark & \xmark & Crypto Algorithm  & \cmark \\ 
-CacheD~\cite{wang2017cached} & Dynamic  & Symbolic Execution + Taint Analysis  & \xmark & \xmark & Libgcrypt, OpenSSL & \xmark \\
-CachSym~\cite{brotzman2019casym} & Static & Symbolic Execution  & \xmark & \xmark & Crypto Snippet & \xmark \\
-CacheS~\cite{wang2019identifying} & Static & Abstract Interpretation & \xmark & \xmark & Libgcrypt, OpenSSL, mbedTLS & \xmark \\
-DATA~\cite{weiser2018data} & Dynamic & Trace Alignment + Comparison & \cmark & \xmark & OpenSSL, PyCrypto & \cmark \\
+CacheAudit~\cite{182946} & Static  & Abstraction  & \xmark & \xmark & Crypto Algorithm  & \cmark \\ 
+CacheD~\cite{203878} & Dynamic  & Symbolic Execution + Taint Analysis  & \xmark & \xmark & Libgcrypt, OpenSSL & \xmark \\
+CachSym~\cite{Brotzman19Casym} & Static & Symbolic Execution  & \xmark & \xmark & Crypto Snippet & \xmark \\
+CacheS~\cite{236338} & Static & Abstract Interpretation & \xmark & \xmark & Libgcrypt, OpenSSL, mbedTLS & \xmark \\
+DATA~\cite{217537} & Dynamic & Trace Alignment + Comparison & \cmark & \xmark & OpenSSL, PyCrypto & \cmark \\
 ctgrind~\cite{langley2010ctgrind} & Dynamic & Taint Analysis & \cmark & \xmark & Crypto Library & \cmark \\
 Satcco~\cite{xiao2017stacco} & Dynamic & Trace Comparison & \cmark & \xmark & OpenSSL, GnuTLS, mbedTLS, WolfTLS, LibreSSL & \xmark \\
-ANABLEPS~\cite{wang2019time} & Dynamic & Trace Comparison & \cmark & \xmark & Deep Learning, gsl, Hunspell, PNG, Freetype, QRcodegen, Genometools & \xmark \\
+ANABLEPS~\cite{wang2019time} & Dynamic & Trace Comparison & \cmark & \xmark & gsl, Hunspell, PNG, Freetype, QRcodegen, Genometools & \xmark \\
 MicroWalk~\cite{wichelmann2018microwalk} & Dynamic & Trace Comparison & \cmark & \xmark & Intel IPP, Microsoft CNG & \cmark \\ 

### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 \section{Detection and Mitigation}
-While there are several existing work on side-channel leakage detections, we find it very hard to apply existing methods to identify controlled-channel attacks.
+There are several existing work on side-channel leakage detections.
 According to Table~\ref{table:side_channel_detection_tool}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction.
@@
 ANABLEPS~\cite{wang2019time} & Dynamic & Trace Comparison & \cmark & \xmark & gsl, Hunspell, PNG, Freetype, QRcodegen, Genometools & \xmark \\
-MicroWalk~\cite{wichelmann2018microwalk} & Dynamic & Trace Comparison & \cmark & \xmark & Intel IPP, Microsoft CNG & \cmark \\ 
+MicroWalk~\cite{Wichelmann:2018:MFF:3274694.3274741} & Dynamic & Trace Comparison & \cmark & \xmark & Intel IPP, Microsoft CNG & \cmark \\ 
 \bottomrule

### 2021-03-26 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \chapter{Scalable Side-channel Vulnerability Detection}\label{chapter3}
-\section{Motivation}
+\section{Problem}
 
@@
 2) In a shielding system, a malicious operating system can extract sensitive information from the protected application.
+3) An user level application can probe some sensitive information inside the kernel.
 The attacker attempts to retrieve sensitive information through address-based
@@
 work well for our problem.
+
+\section{Design and Implementation}
+\subsection{Trace Logging}
+The trace information can be logged via some emulators (e.g., QEMU) or dynamic binary instrumentation tools (DBI). 
+We run a program with the concrete input under the DBI to record execution traces.
+The trace data has the following information:
+\begin{itemize}
+     \item Each instruction mnemonics and its memory address.
+     \item The operands of each instruction and their concrete values during the runtime.
+     \item The value of EFLAGS register. 
+     \item The memory address and the length of the sensitive information.
+      Most crypto libraries stores sensitive information in arrays,
+      variables or contiguous buffer.
+\end{itemize}
+
+\subsection{Instruction Level Symbolic Execution}
+\label{InstructionSE}
+The primary purpose of the step is to generate constraints of the input sensitive information from the execution trace.
+If we give the target program a new input which is different from the original input that was used to generate the execution trace but still satisfies those constraints, as an attacker, he will have the same observations on control-flow transfers and data-access patterns.
+
+The tool runs symbolic execution on top of execution traces.
+At the beginning of the symbolic execution, the tool creates new symbols for each byte in the raw buffer.
+For other data in the register or memory at the beginning, we use actual values from the runtime information collected during the runtime.
+During the symbolic execution for each instruction, the tool updates every variable in the memory and registers with a math formula.
+The formula is made up of concrete values and the input key as the symbols accumulated through the symbolic execution.
+For each formula, the tool will check weather it can be reduced into a concrete values (e.g., $k_1+12-k_1 = 12$ ).
+If so, the tool will only use the concrete values in the following symbolic execution.
+
+\subsubsection{Verification and Optimization}
+We run the symbolic execution (SE) on top of x86 instructions.
+In other words, we do not rely on any intermediate languages to simplify the implementation of symbolic execution.
+While the implementation itself has a lot of benefits (Better performance, accurate memory model), we need to implement the symbolic execution rules for each x86 instruction.
+However, due to the complexity of x86, it is inevitable to make mistakes. Therefore, we verify the correctness of the SE engine during the execution. 
+The tool will collect the runtime information (Register values, memory values) and compare them with the formula generated from the symbolic execution.
+Whenever the tool finishes the symbolic execution of each instruction, the tool will compare the formula for each symbol and its actual value.
+If the two values do not match, we check the code and fix the error.
+Also, if the formula does not contain any symbols, the tool will use the concrete value instead of symbolic execution.
+
+\subsubsection{Secret-dependent control-flows}
+An adversary can infer sensitive information from secret dependent control-flows.
+There are two kinds of control-transfer instructions: the unconditional control-transfer instructions and the conditional transfer instructions.
+The unconditional instructions, like CALL, JUMP, RET transfer control from one code segment location to another.
+Since the transfer is independent of the input sensitive information, an attacker was not able to infer any sensitive information from the control-flow.
+So the unconditional control-transfer does not leak any information based on our threat model.
+During the symbolic execution, we update the register information and memory cells with new formulas accordingly.
+
+The conditional control-flow transfer instructions, like conditional jumps, depending on CPU states, may or may not transfer control flows.
+For conditional jumps, the CPU will test if certain condition flag
+(e.g., CF = 0, ZF =1) is met and jump to certain branches, respectively.
+The symbolic engine will compute the flag and represent the flag in a symbol 
+formula. Because we are running on a symbolic execution on an execution trace, 
+we know which branch is executed.
+If a conditional jump uses the CPU status flag, we will generate the constraint accordingly.
+
 \section{Evaluation}

### 2021-03-26 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 The symbolic engine will compute the flag and represent the flag in a symbol 
-formula. Because we are running on a symbolic execution on an execution trace, 
-we know which branch is executed.
+formula. Because we are running on a symbolic execution on an execution trace, we know which branch is executed.
 If a conditional jump uses the CPU status flag, we will generate the constraint accordingly.
+
+For examples, considering the below x86 code snippet,
+
+\begin{lstlisting}
+ ...
+0x0000e781      add dword [local_14h], 1
+0x0000e785      cmp dword [local_14h], 4
+0x0000e789      jne 0xe7df
+0x0000e78b      mov dword [local_14h], 0
+ ...
+\end{lstlisting}
+
+At the beginning of the instruction segment, the value at the address of local\_14h can be written as $F(\vec{K})$.
+At the address $e785$, the value will be updated with $F(\vec{K})+1$.
+Then the code compares
+the value with 4 and use the result as a conditional jump. Based on the result, we can have the following formula:
+
+$$F(\vec{K}) + 1 = 4$$
+
+The formula, together with the memory address ($0xe789$) is store as a \textit{formula tuple (address, formula)}. Each formula tuple represents one leakage site.
+
+\subsubsection{Secret-dependent data access}
+Like input-dependent control-flow transfers, an adversary can also infer sensitive information from the data access pattern as well.
+We try to find this kind of leakages by checking every memory operand of the instruction.
+We generate the memory addressing
+formulas. As discussed before, every symbols in the formula is the input key. If the formula does not contain any symbols, the memory access is independent 
+from the input sensitive information and will not leak any sensitive information according to our threat model. Otherwise, we will generate the constraint for
+the memory addressing. We model the memory address with a symbolic formula $F(\vec{K})$. Because we also have the concrete value of the memory address $Addr1$. 
+Inspired by the work from~\cite{203878}, the formula can be written as:
+
+$$F(\vec{K}) >> L = Addr1 >> L$$
+
+$L$ represents the minimum memory address granularity that an attacker can observe. For example, Flush and Reload can distinguish between different cache lines, which means the value of L is 6.
+
+\subsubsection{Information Flow Check}
+\tool{} is designed to help software developers find and understand the side-channel vulnerabilities.
+To ease the procedure of fixing the bug, we also track the information flow for each byte of the input
+buffer. 
+The step can be seen as the multiple-tag taint analysis. With the help of the information from symbolic execution, we can implement a relatively simple but relatively precise information flow track.
+At the beginning of the analysis, \tool{} keep a track for each byte in 
+the original buffer.
+When \tool{} symbolically executes each instruction in the trace, it will check every value read from registers or memory.
+If the value is concrete, it means the instruction has nothing to do with the original buffer.
+If the value is a formula, it means the original information passes through the instruction.
+Since each byte in the sensitive buffer is represented as a symbol with a unique ID, \tool{} can know which byte in the origin buffer goes through the instruction.
 

### 2021-03-26 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 
-\chapter{Precise Analysis on Single-trace Attacks}
+\chapter{Precise Analysis on Single-trace Attacks}\label{chapter4}
 
-\section{Introduction}
+\section{Problem}
 Side channels are ubiquitous in modern computer systems as sensitive

### 2021-03-26 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 
-\chapter{Scalable Side-channel Vulnerability Detection}\label{chapter3}
+\chapter{Fast and Precise Side-channel Vulnerability Detection}\label{chapter3}
 \section{Problem}
+Side-channel attacks infer sensitive information such as cryptographic keys, personal data from software products unconsciously.
+As we discuss in \S\ref{chapter1} and \S\ref{chapter2}, patching software are usually easier than adopting new hardware to defend against side-channel attacks.
 
@@
 has access to the source code or binary executable of the target program.
+
+\section{An illustrative example}
 

### 2021-03-26 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 
-\section{Quantification}
+\section{Background}
+Given an event $e$ that occurs with the probability $p(e)$, we receive
+\begin{displaymath}
+    I = - \log_2p(e)
+\end{displaymath}
+bits of information by knowing the event $e$ happens according to information theory~\cite{shannon1948mathematical}. 
+Considering a char variable $a$
+with one byte storage size in a C program, its value ranges from 0 to 255.
+Assume $a$ has a uniform distribution. If we observe that
+$a$ equals $1$, the probability of this observation is $\frac{1}{256}$. So 
+we get $-\log(\frac{1}{256}) = 8$ bits information, which is exactly the size
+of a char variable in the C program.
+
+Existing works on information leakage quantification typically use Shannon
+entropy~\cite{clark2007static,Wichelmann:2018:MFF:3274694.3274741},
+min-entropy~\cite{10.1007/978-3-642-00596-1_21}, and max-entropy~\cite{182946,
+Doychev:2017:RAS:3062341.3062388}. In these frameworks, the input sensitive
+information $K$ is considered as a random variable.
+
+Let $k$ be one of the possible
+value of $K$. The Shannon entropy $H(K)$ is defined as
+\begin{displaymath}
+    H(K) = - \sum_{k {\in} K}p(k)\log_2(p(k))
+\end{displaymath}
+
+Shannon entropy can be used to quantify the initial uncertainty about the
+sensitive information. It measures the amount of information in a system.
+
+Min-entropy describes the information leaks for a program with the most likely input. 
+For example, min-entropy can be used to describe the
+best chance of success in guessing one's password using the
+most common password. %, which is defined as
+\begin{displaymath}
+    \mathit{min\text{-}entropy} = - \log_2(p_{\mathit{max}})
+\end{displaymath}
+
+Max-entropy is defined solely on the number of possible observations.
+%It is equal to $-\log_2{n}$.
+\begin{displaymath}
+    \mathit{max\text{-}entropy} = -\log_2{n}
+\end{displaymath}
+As it is easy to compute, most recent works~\cite{182946,Doychev:2017:RAS:3062341.3062388} use max-entropy as the definition of
+the amount of leaked information.
+
+To illustrate how these definitions work, we consider the code
+fragment in Figure~\ref{fig:side-channel}. It has two secret-dependent
+control-flows, A and B.
+
+\begin{figure}[h!]
+\centering
+\begin{lstlisting}[xleftmargin=.03\textwidth,xrightmargin=.01\textwidth]
+uint8_t key[2], t1, t2;
+get_key(key);              // 0 <= key[0], key[1] < 256
+t1 = key[0] + key[1];
+t2 = key[0] - key[1];
+if (t1 < 4){               // leakage site A
+    foo();    
+}                          
+if (t2 > 0){               // leakage site B     
+    doo();    
+}                          
+\end{lstlisting}
+\vspace*{-1pt}
+    \caption{Side-channel leakage}
+    \label{fig:side-channel}
+\end{figure}
+In this paper we assume an attacker can observe the secret-dependent control-flows in Figure~\ref{fig:side-channel}.
+Therefore, an attacker can have two different observations for each leak site
+depending on the value of the $\mathit{key}$: $A$ for function \textsf{foo} is executed, 
+$\neg A$ for function \textsf{foo} is not executed, $B$ for function \textsf{doo} is
+executed, and $\neg B$ for function \textsf{doo} is not executed. Now the
+question is how much information can be leaked from the above code if an
+attacker knows which branch is executed?
+
+\begin{table}[ht]
+    \centering\small\footnotesize
+    \caption{The distribution of observation}\label{shtable}
+    \vspace*{-0pt}
+%    \resizebox{\columnwidth}{!}{
+    \begin{tabular}{l|cc|cc}
+        \hline
+
+        Observation ($o$)   & $A$ & $\neg A$ & $B$ & $\neg B$ \\ \hline
+        Number of Solutions & 65526       & 10        & 32768     & 32768           \\ \hline
+        Possibility (p)     & 0.9998      & 0.0002    & 0.5    & 0.5       \\
+        \hline
+    \end{tabular}
+%        }
+\end{table}
+
+Assuming $\mathit{key}$ is uniformly distributed, we can calculate the corresponding
+possibility by counting the number of possible inputs. Table~\ref{shtable}
+describes the probability of each observation. We use the above three types of 
+leakage metrics to calculate the amount of leaked information for leak A and leak B.
+
+\vspace{3pt}
+\textbf{Min Entropy.}
+As $p_{A\mathit{max}} = 0.9998$ and $p_{B\mathit{max}} = 0.5$, 
+with the definition, min-entropy equals to
+\begin{align*}
+    \mathit{min\text{-}entropy_A} & = -\log_2{0.9998} = 0.000\ \mathrm{bits} \\
+    \mathit{min\text{-}entropy_B} & = -\log_2{0.5} = 1.000\ \mathrm{bits}
+\end{align*}
+
+\textbf{Max Entropy.}
+Depending on the value of key, the code can run two different branches for each leakage site. 
+Therefore, with the max entropy
+definition, both leakage sites leak
+
+\begin{displaymath}
+    \mathit{max\text{-}entropy} = -\log_2{2} = 1.000\ \mathrm{bits}
+\end{displaymath}
+
+\textbf{Shannon Entropy.}
+Based on Shannon entropy, the respective amount of information in A and B equals to
+{\footnotesize
+\begin{align*}
+    \mathit{Shannon\text{-}entropy_A} & = -(0.9998*\log_{2}0.9998      \\
+                                    & \qquad+ 0.0002*\log_{2}0.0002)  \\
+                                    & = 0.000\ \mathrm{bits}         \\
+    \mathit{Shannon\text{-}entropy_B} & = -(0.5*\log_{2}0.5      \\
+                                    & \qquad+ 0.5*\log_{2}0.5)        \\
+                                    & = 1.000\ \mathrm{bits}                             
+\end{align*}
+}
+In the next section, we will show that these measures work well only
+theoretically in a static analysis setting. 
+Generally, they do not apply to dynamic analysis or real
+settings. We will present that the static or theoretical results could be
+dramatically different from the real world, and we do need a better method to
+quantify the information leakage from a practical point of view.
+
+\section{Leakage Definition}
 
@@
 bit leakage.
+Both approaches fail to tell how much information is leaked during the execution
+precisely. The problem with existing methods is that they are static-based so
+input values and real runtime information are neglected by their approaches. 
+They assume an attacker runs
+the program multiple times with many different or random sensitive inputs. As
+shown in Figure~\ref{fig:gap}(a), previous models, both Shannon entropy and max
+entropy, give an ``average'' estimate of the information leakage. However, it is
+not the typical scenario for an adversary to launch a side-channel attack. When
+a side-channel attack happens, the adversary wants to retrieve the sensitive
+information, in which case the sensitive information is fixed (e.g., AES keys).
+The adversary will run the attack over and over again with fixed input and 
+guess the value bit by
+bit (e.g., Kocher's timing attacks~\cite{kocher1996timing}), as in Figure~\ref{fig:gap}(b). We want to have a
+theory for dynamic analysis that if the theory says an attack leaks $x$ bits of
+secret information from a side-channel vulnerability, then $x$ should be useful
+in estimating the sensitive level of the vulnerability. However, the above
+methods all fail in real attack models. This is the first challenge we face
+\textbf{(Challenge C1)}.
 
+\begin{figure}
+    \centering
+    \includegraphics[width=.65\columnwidth]{./figures/RA.pdf}
+\vspace*{-6pt}
+    \caption{The gap between the real attack and previous models}\label{fig:gap}
+\end{figure}
+
+\subsection{Theoretical Analysis \textbf{(Solution to Challege C1)}}
+Now we present our metric to quantify the amount of leaked information from
+dynamic analysis.
+
+In information theory, the mutual information (I) is a measure of the mutual
+dependence between two variables. Here we use I to describe the
+dependence between original sensitive keys ($K$) and attackers' observations ($O$), 
+which is defined as:
+
+\begin{equation} \label{eq:1}
+    I(K;O) = \sum_{k {\in} K}{\sum_{o {\in} O}{p(k, o)\log_2\frac{p(k, o)}{p(k)p(o)}}}
+\end{equation}
+
+where $P(k_i, o_i)$ is the joint discrete distribution of $K$ and $O$.
+Alternatively, the mutual information can also be equivalently expressed as:
+
+\begin{equation} \label{eq:2}
+    I(K;O) = H(K) - H(K|O)
+\end{equation}
+
+$H(K|O)$ is the entropy of $K$ with the condition $O$. It quantifies the
+uncertainty of $K$ given the value of $O$. In other word, the conditional
+entropy $H(K|O)$ marks the uncertainty about $K$ after an adversary has gained
+some observations ($O$).
+\begin{equation}
+    H(K|O) = - \sum_{o {\in} O} {p(o) \sum_{k {\in} K}{p(k|o)\log_2p(k|o)}}
+\end{equation}
+
+In this project, we hope to give a very precise definition of information
+leakages. Suppose an attacker runs the target program with one
+fixed input, we want to know how much information he can infer by observing the
+memory access patterns ($o$). We come to the simple slogan
+~\cite{10.1007/978-3-642-00596-1_21} %% where the information
+%% leakage equals:
+%% \textbf{Initial uncertainty - remaining uncertainty}
+that
+\begin{align*}
+     & \mathit{Information\ leakage} =                                         \\
+     & ~~~~ \mathit{Initial\ uncertainty} - \mathit{Remaining\ uncertainty}.
+\end{align*}
+
+Next we compare the Eq.~(\ref{eq:2}) with the above slogan, we find $H(K)$
+is the $\mathit{Initial\ uncertainty}$ and $H(K|O)$ is $\mathit{Remaining\
+uncertainty}$. During a real attack, the observation ($o$) is known.  Thus we
+have $H(K|O) = H(K|o)$.
+
+Therefore, we define the amount of leaked information as
+\begin{displaymath}
+    Leakage = H(K;o) = H(K) - H(K|o)
+\end{displaymath}
+
+For a program ($\beta$) without knowing any domain information, all possible sensitive
+inputs should appear equally. Therefore, for any $k \in K$, $p(k) =
+\frac{1}{|K|}$. So we have
+$$H(K) = \sum_{k {\in} K}\frac{1}{|K|}\log_2{|K|} = \log_2{|K|}$$
+For any $k' \in K \setminus K^o$, $p(k'|o) = 0$. We get
+\begin{align*}
+    H(K;o) & = - \sum_{k {\in} K^o}{p(k|o)\log_2p(k|o)}                         \\
+           & \qquad   - \sum_{k` {\in} (K \setminus K^o)}{p(k'|o)\log_2p(k'|o)} \\
+           & = \sum_{k {\in} K^o}\frac{1}{|K^o|}\log_2{|K^o|}                   \\
+           & = \log_2{|K^o|}
+\end{align*}
+
+\begin{mydef}
+    \label{def}
+    Given a program $\beta$ with the input set $K$,
+    an adversary has the observation $o$ when the input $k{\in}K^o$.
+    We denote it as
+    $$\beta(K^o, m) \rightarrow	o$$
+
+    The amount of leaked information $L_{\beta(k)\rightarrow o}$ based on the observation ($o$) is
+    $$L_{\beta(k)\rightarrow o} = \log_2{|K|} - \log_2{|K^o|}$$
+\end{mydef}
+
+The above definition~\cite{AskarovC12} can be understood in an intuitive way. Suppose an attacker
+wants to guess a 128-bit encryption key from a program. 
+Without any domain knowledge, 
+he can find the key by performing exhaustive search over $2^{128}$ possible keys. 
+However, the program has a side-channel leakage site. After the program finishes execution, the
+attacker get some leaked information and only need to find the key by performing 
+exhaustive search over $2^{120}$ possible keys. Then we can say that 8 bits of the information
+is leaked. In this example, $2^{128}$ is the size of $K$ and $2^{120}$ is the size of $K^o$.
+
+With the definition, if an attacker observes that the code in
+Figure~\ref{fig:password-checker} runs the branch 1, then the $K^{o^{1}} =
+\{\mathrm{``password"}\}$. Therefore, the information leakage $L_{P(k)=o^{1}} =
+\log_2{2^{64}} - \log_2{1} = 64$ bits, which means the key is totally leaked. If
+the attacker observes the code hits branch 2, the leaked information is
+$L_{P(k)=o^{2}} = \log_2{2^{64}} - \log_2{(2^{64}-1)} \approx 0$ bit.
+
+We can also calculate the leaked information from the sample code in
+Figure~\ref{fig:side-channel}. As the size of input sensitive information is
+usually public. The problem of quantifying the leaked information has been
+transferred into the problem of estimating the size of input key $|K^o|$ under
+the condition $o \in O$. The result is shown in Table~\ref{shtable2}. We can see
+that some branches (e.g., A) or traces leak much more information than some others. 
+Those kinds of branches can be vulnerable when an attacker's data is incorporate. 
+For example, the code will skip some of the calculation if the value is 0 in big 
+number multiplication.
+
+In
+contrast, an \emph{average} estimate based on random secret input information is around
+1 bit, as shown in \S\ref{sec:background_leak} and Table~\ref{shtable}, is
+not very useful in practice as an attacker is able to get much more leaked
+information in some attack scenarios.
+
+\begin{table}[ht]
+    \centering\small\footnotesize
+    \caption{New leakage modeling results}
+    \label{shtable2}
+    \vspace*{-9pt}
+%    \resizebox{\columnwidth}{!}{
+    \begin{tabular}{l|cc|cc}
+        \hline
+
+        Observation ($o$)   & $A$ & $\neg A$ & $B$ & $\neg B$ \\ \hline
+        Number of Solutions & 65526       & 10        & 32768     & 32768           \\ \hline
+        Leaked Information (bits) & 0.0         & 14.7      & 1.0       & 1.0         \\
+        \hline
+    \end{tabular}
+\end{table}
 \section{Approximate Model Counting}

### 2021-03-26 Chapter-5/Chapter-5.tex
init
update
Updates from Overleaf

--- 2021-02-14 Chapter-2/Chapter-2.tex
@@
 
-\chapter{Background}
+\chapter{Precise Analysis on Chosen-plaintext Attacks}\label{chapter5}
+\section{Introduction}
+Side-channel attacks allow attackers to infer sensitive information based on the non-functional behaviors of the computer system.
+Examples of those non-functional behaviors include acoustics, CPU usages, timing, EM signals, etc~\cite{agrawal2002side,hund2013practical,halevi2015keyboard}.
+In short, the program has different execution behaviors when it processes various keys.
+As an attacker, he can infer nontrivial information by observing those secret-dependent behaviors.
+While separate side-channel attacks may have different forms and patterns, we find a large portion of them share the same fundamental reasons.
+That is, the memory access pattern is dependent on the original sensitive input.
 
-\section{Address-based Side-channel Attacks}
+While removing those dependent memory-access patterns in existing software completely seems impossible, fixing some of the most dangerous leakages appears to be a feasible solution.
+Previous studies on side-channel detections have shown their effectiveness in finding such code patterns.
+As a developer, he can run the tool to analyze the side-channels leakages and fix those patterns.
+However, fixing all those leakages seem impossible.
+First, side-channels are inevitable.
+For example, tremendous efforts have been made to remove the side-channel vulnerabilities in cryptography libraries in the past decade.
+However, we still find that there are plenty of side-channel leakages in the latest version of OpenSSL.
+Second, many side-channel vulnerable versions usually have better performance, such as the T-table lookup in AES, CRT optimizations in RSA, and Fast Discrete Fourier Transform (FDFT) in many media processing libraries.
+Third, some developers are not interested in fixing side-channels vulnerabilities unless we can show them an attack demo, even for the cryptography developers.
+For many non-cryptography developers, side-channels are not in the threat model.
+However, recent studies have shown a series of attacks on the non-cryptography libraries.
 
-\section{Information Theory}
+The key to solve the problem is looking for a proper metric to assess the sensitive level of the side-channel leakages.
+Many side-channel analysis works focus on detecting leakages, which is fine because most side-channel attacks target cryptography libraries.
+For cryptography libraries, even a minor leakage can be severe because the leakage can reduce the strength of the encryption algorithm.
+However, many attacks also exploit non-cryptography libraries and applications like machine learning frameworks~\cite{yan2020cache,hong2018security}, graphic libraries~\cite{wang2019unveiling}, spell checking tools~\cite{xu2015controlled}, etc.
+Unlike side-channel attacks on cryptography libraries that exploit one vulnerability each time, attacks on non-cryptography rely on multiple side-channel leakage sites to retrieve more information.
+Suppose one program has two leakage sites, it is hard to estimate the total effect of those two leakages.
+Any two leakages have some underlying complex relationships.
+That is, the two leakages could be completely independent, which means they leak different information.
+Alternatively, the two leakages could leak the same information.
+A typical situation, that is, the two leakage sites, can leak some common knowledge.
+Apart from that, they have their unique leakages.
+However, no existing tools that can estimate the total effect of multiple leakage sites.
+For real-world applications with thousands of lines, it is hard to estimate the amount of leaked information.
+Attackers can guess the values of some temporary values.
+But those temporary values contain some knowledge of the original secret buffer.
 
-\section{Binary Analysis}
+Second, many precise side-channel analysis tools rely on some techniques like symbolic executions, taint analysis, and abstract interpretations~\cite{wang2017cached,doychev2015cacheaudit,brotzman2019casym,wang2019identifying}.
+Those methods need to consider the semantics of each ISA instruction, which is tedious.
+So they build the tool on the top of existing binary analysis frameworks.
+Due to the limitations of binary analysis frameworks, it is hard to apply existing methods to analyze side-channels in non-cryptography libraries.
+For many other applications like machine learning, media, and graphic libraries built on the top architecture-dependent libraries (e.g., Intel MKL~\cite{wang2014intel}), those tools can not handle it.
+Moreover, existing binary analysis frameworks (e.g., Angr~\cite{shoshitaishvili2016state}) are limited to analyze floating-point instructions.
+But the functionality of those applications heavily depends on floating-point calculations.
+
+Third, while many existing works can detect side-channel leakages, few of them can assess how severity level of those vulnerabilities~\cite{wang2017cached,doychev2015cacheaudit,brotzman2019casym,wang2019identifying,weiser2018data,wichelmann2018microwalk}.
+There are some tools~\cite{doychev2015cacheaudit,chattopadhyay2019quantifying} that can quantify the information leakage.
+Those tools usually rely on the abstraction to give an upper bound estimation of each leakage site, which is useful to justify the software is secure if the reported leakage is zero.
+But those tools can not tell software developers how serious each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage.
+The best way to estimate each leakage's severe level is to exploit the leakage and recover the information.
+However, the process itself is very tedious and needs a lot of domain knowledge.
+
+To solve the above problem, we propose a method to estimate the effect of each side-channel leakages automatically.
+We compare the side-channel attack to a communication system and use the channel capacity to quantify the amount of the information flow from the original secret to the observation of an attacker.
+The method also allows us to combine multiple leakages sites to retrieve the information.
+The  attack can be seem as a process that reduces the search space of the original sensitive inputs.
+We use the side-channel vulnerability to divide the input space.
+If the patterns can unique distinguish the input space, then we think the information is leaked totally.
+However, in the real cases, many of those side-channel leakage patterns are not enough for us to distinguish each leakage sites, but can still distinguish some of the sensitive inputs.
+In those cases, we call those leakages partial leaks.
+
+The method has three phases.
+In the first phase, we fuzz the target program with various inputs and collect the memory access information.
+In the second phase, we map the memory access information with the source code.
+With the debug information, we can precisely know the address access information of the source code.
+In the third phase, we exam the source code, if one function have two memory access patterns, then the function is vulnerable to side-channel attacks.
+Base on the distribution of memory access patterns under different inputs, we quantify the side-channel leakage of each functions.
+
+This paper makes the following contributions:
+
+\begin{itemize}
+
+\item We propose a novel method that can detect and analyze the effect of each side-channel leakage sites automatically.
+Our analysis combine information from both the source code and the run-time execution, which makes the method more effective in finding the leakages.
+The method can combine multiple leakage sites to retrieve more information as well.
+
+\item We analyze the amount of information leakage from side-channel vulnerabilities based on the channel capacity.
+We propose a method that can estimate the lower bound of information leakages.
+The theory can serve as the foundation of the future work on quantify the information leakage based on the fuzzing.
+
+\item We implement the above method in a tool called \tool{} and evaluate the tool with several benchmarks and several real-world applications such as OpenSSL, mbedTLS, TinyDNN, and GTK.
+The results show that our tool can detect and quantify the side-channel leakages effectively.
+Moreover, the leakage reports given by the \tool{} can help developers fix the reported vulnerabilities.
+\end{itemize}
+
+\section{Background and Threat Model}
+In the section, we first provide a brief introduction of the side-channel attacks that exploit the memory access patterns.
+After that, we give an overview of the background knowledge of information theory.
+Finally, we present the threat model of the paper.
+
+\subsection{Address-based Side-channel Attacks}
+Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses.
+Most of the attack allows the attacker to shares some hardware resources with the victim.
+As a result, while the fundamental reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.
+
+\begin{table}
+\centering
+\caption{Due to the page limit, we only shows some representations of the vast side-channel attacks: Attacks, the shared hardware resources with attackers, the granularity of the attacker can observe, is there any published attacks on non-cryptography library and if the type of attack can exploit multiple leakage sites.}
+\label{table:side_channel_attack}
+\resizebox{\columnwidth}{!}{%
+
+\begin{tabular}{lllcc}
+\toprule
+Attacks & Shared Resources & Granularity  & Non-Crpyto & Multiple   \\ \midrule
+CacheBleed~\cite{yarom2017cachebleed} & Cache & Sub Cache Line (<64 B)  & \xmark & \xmark \\ 
+CopyCat~\cite{moghimi2020copycat} & Page Tables   & Instruction   & \xmark &  \xmark \\
+Prime + Probe~\cite{liu2015last} & Cache & Cache Set (64-512 B)  & \cmark &   \xmark \\
+Prime + Abort~\cite{disselkoen2017prime+} & Cache  & Cache Set (64-512 B) & \cmark &  \xmark   \\
+Flush + Reload~\cite{yarom2014flush+} & Cache & Cache Line (64 B) & \cmark  &  \cmark \\
+Flush + Flush~\cite{gruss2016flush+} & Cache & Cache Line (64 B) & \cmark & \xmark  \\
+Controlled-channel Attack~\cite{xu2015controlled} & Page Tables & Page (4KB) & \cmark & \xmark \\
+TLBleed~\cite{gras_translation_2018} & MMUs & TLB Set (4KB) & \cmark  & \xmark \\
+Page Cache Attacks~\cite{gruss2019page} & Page Cache &  Page (4KB) & \xmark &  \cmark \\ 
+\bottomrule
+\end{tabular}
+}
+\end{table}
+
+\subsubsection{Cache-level Channel}
+Cache-based channels rely on the time difference between cache misses and cache hits. Cache channel attacks can observe cache accesses at the level of cache sets, cache lines or other granularities. 
+We introduce two common attack strategies, namely Prime+Probe and
+Flush+Reload. Prime+Probe targets a single cache set. An
+attacker preloads the cache set with its own data and waits until the victim
+executes the program. If the victim accesses the cache set and evicts part of
+the data, the attacker will experience a slow measurement. 
+While Flush+Reload targets a single cache line, it requires the attacker and victim share some memory. During the ``flush'' stage, the attacker flushes the ``monitored
+memory'' from the cache and waits for the victim to access the memory,
+who will load the sensitive information to the cache line. In the next phase,
+the attacker reloads the ``monitored memory''. By measuring the time difference
+brought by cache hit and miss, the attacker can further infer the sensitive information. Some other types of side-channels target different hardware
+layers other than CPU cache.
+
+\subsubsection{Page-level Channel}
+Recent studies also shows the attacks can observe the memory access at the granularity of memory pages.
+One example is the controlled-channel attack~\cite{xu2015controlled}, where a privileged adversary try to infer the sensitive information by manipulating the enclave page access.
+Those kinds of attacks usually happen on the shielding system.
+A malicious OS can proactively revoke a virtual enclave memory page from the memory.
+If the victim enclave program accesses the memory table, then the adversary can know which page is accessed by observing the page fault sequence.
+While the granularity of the controlled-channel attacks is very coarse grained, the controlled-channel attacks allow the attacker to have a noise-free observation.
+Examples of other attacks exploits page cache maintained by the OS, TLB also shares the same granularity.
+
+In this paper, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs).
+To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.
+
+\subsection{Channel Capacity}
+Let $k$ be one of the possible
+value of $K$. The Shannon entropy $H(K)$ is defined as
+\begin{equation}\label{eq1}
+    H(K) = - \sum_{k {\in} K}p(k)\log_2(k)
+\end{equation}
+
+Shannon entropy can be used to quantify the initial uncertainty about the sensitive information.
+It measures the amount of information in a system.
+For example, an AES encryption program takes a 128-bit key as the input.
+Suppose every key has the equal opportunity and $p_k = 1/ 2^{128}$, then the encryption system has $128 \, \mathit{bits}$ information according to Shannon entropy.
+
+In the paper, we use the channel capacity to describe the information leakages through a channel.
+In information theory, the channel capacity is used to quantify the rate of information can be reliably transmitted over a channel.
+If we use $K$ to represent the input secrets and $O$ to represent the output observation.
+The channel capacity ($C$) is defined as
+
+\begin{equation}\label{eq2}
+C(K;O) = \max_{p(x)} I(K;O)
+\end{equation}
+Here $I(K;O)$ is the mutual information between $K$ and $O$.  
+\begin{equation} \label{eq3}
+    I(K;O) = \sum_{k {\in} K}{\sum_{o {\in} O}{p(k, o)\log_2\frac{p(k, o)}{p(k)p(o)}}}
+\end{equation}
+
+While the general case of channel capacity is hard to execute, we consider the two special channels.
+
+\subsubsection{Noiseless Lossless Channel}
+The channel of the system is noiseless and lossless if
+
+\begin{equation} \label{eq:1}
+    C(K;O) = \max_{p(k)} I(K;O) = \max_{p(k)} H|O| =\max_{p(k)} H|K|
+\end{equation}
+$|K|$ represents the number of symbols in $K$.
+
+Figure~\ref{fig:channel}a shows the example of the type of the channel.
+Under the circumstance, we always have $P(o_i/k_i) = 1$ and $P(k_i/o_i) = 1$.
+As we can see, the channel have the unique output ($o \in O$) for every input ($k \in K$).
+
+\begin{figure}
+\begin{minipage}{0.48\linewidth}
+\resizebox{\linewidth}{!}{
+
+ \begin{tikzpicture}[ele/.style={fill=black,circle,minimum width=.8pt,inner sep=1pt},every fit/.style={ellipse,draw,inner sep=-2pt}]
+  \node[ele,label=left:{\LARGE $k_1$}] (a1) at (0,4) {};    
+  \node[ele,label=left:{\LARGE $k_2$}] (a2) at (0,3) {};    
+  \node[ele,label=left:{\LARGE $k_3$}] (a3) at (0,2) {};
+  \node[ele,label=left:{\LARGE $k_4$}] (a4) at (0,1) {};
+
+  \node[ele,,label=right:{\LARGE $o_1$}] (b1) at (4,4) {};
+  \node[ele,,label=right:{\LARGE $o_2$}] (b2) at (4,3) {};
+  \node[ele,,label=right:{\LARGE $o_3$}] (b3) at (4,2) {};
+  \node[ele,,label=right:{\LARGE $o_4$}] (b4) at (4,1) {};
+
+  \node[draw,fit= (a1) (a2) (a3) (a4),minimum width=2cm] {} ;
+  \node[draw,fit= (b1) (b2) (b3) (b4),minimum width=2cm] {} ;  
+  \draw[->,thick,shorten <=2pt,shorten >=2pt] (a1) -- (b1);
+  \draw[->,thick,shorten <=2pt,shorten >=2] (a2) -- (b2);
+  \draw[->,thick,shorten <=2pt,shorten >=2] (a3) -- (b3);
+  \draw[->,thick,shorten <=2pt,shorten >=2] (a4) -- (b4);
+ \end{tikzpicture}
+}
+\caption*{(a) Noiseless Lossless}
+\end{minipage}
+\hfill
+\begin{minipage}{0.48\linewidth}
+\resizebox{\linewidth}{!}{
+
+ \begin{tikzpicture}[ele/.style={fill=black,circle,minimum width=.8pt,inner sep=1pt},every fit/.style={ellipse,draw,inner sep=-2pt}]
+  \node[ele,label=left:{\LARGE $k_1$}] (a1) at (0,4) {};    
+  \node[ele,label=left:{\LARGE $k_2$}] (a2) at (0,3) {};    
+  \node[ele,label=left:{\LARGE $k_3$}] (a3) at (0,2) {};
+  \node[ele,label=left:{\LARGE $k_4$}] (a4) at (0,1) {};
+
+  \node[ele,,label=right:{\LARGE $o_1$}] (b1) at (4,4) {};
+  \node[ele,,label=right:{\LARGE $o_2$}] (b2) at (4,3) {};
+  \node[ele,,label=right:{\LARGE $o_3$}] (b3) at (4,2) {};
+  \node[ele,,label=right:{\LARGE $o_4$}] (b4) at (4,1) {};
+
+  \node[draw,fit= (a1) (a2) (a3) (a4),minimum width=2cm] {} ;
+  \node[draw,fit= (b1) (b2) (b3) (b4),minimum width=2cm] {} ;  
+  \draw[->,thick,shorten <=2pt,shorten >=2pt] (a1) -- (b1);
+  \draw[->,thick,shorten <=2pt,shorten >=2] (a2) -- (b2);
+  \draw[->,thick,shorten <=2pt,shorten >=2] (a3) -- (b2);
+  \draw[->,thick,shorten <=2pt,shorten >=2] (a4) -- (b2);
+ \end{tikzpicture}
+ }
+ \caption*{(b) Noiseless Loss}
+ \end{minipage}
+\caption{Two Kinds of Channels}\label{fig:channel}
+\end{figure}
+
+\subsubsection{Noiseless Loss Channel}
+In reality, noiseless loss channel is more common. We define the channel is noiseless loss if
+
+\begin{equation} \label{eq:2}
+    C(K;O) = \max_{p(x)} I(K;O) = \max_{p(x)} H |O| = \log_2 {|O|}
+\end{equation}
+
+Figure~\ref{fig:channel}b  shows the example of the type of the channel.
+Once the input symbol is determined, the output symbol is also determine.
+As we can see, the channel have the unique output ($o \in O$) for every input ($k \in K$).
+
+\subsection{Threat Model and Math Notation}
+
+We consider an attacker who shares the same hardware resource with the victim.
+The attacker may not know the memory access the victim program accesses directly, but he can infer whether some memory addresses are accessed or not at various granularities after \textit{each run} of the victim program.
+We call the memory access information as the observation ($O$) in the rest of the paper.
+This is a typical scenario for most side-channel attacks.
+We also assume the attacker can have access to the source code of the victim program ($\beta$).
+It is a valid assumption since most side-channel attacks target open source software.
+Also like recent works, we assume the attacker have a noise-free observation.
+For some side-channel channels like the controlled-channel attacks, it is already true.
+The program ($\beta$) has $K$ as the sensitive input.
+$K$ is a finite set that consists of every possible keys ($k \in K$).
+The program also takes known messages $M$ as the input.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=\columnwidth]{./figures/channel.pdf}
+    \caption{The relationship between the side-channel attack and the channel capacity.
+For a deterministic program, the side-channel attack can be seen as the communication between the observation ($o \in O$) and the secret ($k \in K$) via a discrete memoryless channel.}
+    \label{fig:side_channel}
+\end{figure}
+
+With the above definitions, we define the following mapping between $\beta$,
+$K$, $M$, and $O$:
+
+\begin{displaymath}
+    \beta(K, M) \rightarrow O
+\end{displaymath}
+
+Side-channel attacks can be seen as a process that refers the secret ($K$) based on the observations ($O$) shown in the figure~\ref{fig:side_channel}.
+As an attacker, he can observe the memory address of the victim program.
+He wants to infer the original secret ($k$) based on the observation.
+We also assume the attacker knows the known message $m \in M$.
+In the rest of paper, we use $\beta(K) \rightarrow O$ to denote a victim program with side-channel vulnerabilities.
+
+\section{Method}
+In this section, we first provide two examples shows how we rank the side-channel vulnerability. After that, we prove that our method is the conservative estimate of the amount of the each leakage.
+
+\subsection{An Example}
+Figure~\ref{fig:example1} show a function that is vulnerable to side-channel attacks.
+The function take a input secret from the caller.
+Depending on the value of the secret, it may access different values at line 7.
+Suppose an attacker can observe which item in the table \textsf{T} is accessed, he can infer the secret based on the observation.
+\begin{figure}[h]
+\begin{minipage}{0.6\linewidth}
+\begin{lstlisting}
+void bar(uint8_t secret)
+{
+  uint8_t T[128];
+  uint8_t index = 0, t;
+  int i;
+  index = (index+secret)%128;
+  t = T[index];
+  ...
+}
+\end{lstlisting}
+\end{minipage}
+\hspace{-4pt}
+\hfill
+\hspace{-4pt}
+\begin{minipage}{0.45\linewidth}
+\resizebox{\textwidth}{!}{%
+
+\begin{tabular}{cccccccccc}
+\toprule
+\diagbox{S}{T} & 0 & 1 & 2 & 3 & 4 & 5& 6& 7 &  ...\\ 
+\midrule
+0 & A &  &  &  &  &  \\
+1 &  & A &  &  &  &  \\
+2 &  &  & A &  &  &  \\
+3 &  &  &  & A &  &  \\
+4 &  &  &  &  & A &  \\
+5 &  &  &  &  &  & A & \\
+6 &  &  &  &  &  & &A \\
+7 &  &  &  &  &  &  && A\\ 
+\bottomrule
+\end{tabular}%
+}
+\end{minipage}
+\caption{A Serious Leakage}\label{fig:example1}
+\end{figure}
+
+To assess the sensitive level of the vulnerability, we use the sampling method to estimate the leakage.
+Suppose we give the function input from $0, 1, \dots, 7$ and observe the array $T$, we can find each different input have one unique observation.
+Therefore, the secret can be uniquely determined.
+
+\begin{figure}[h]
+\begin{minipage}{0.60\linewidth}
+\begin{lstlisting}
+void bar(uint8_t secret)
+{
+  uint8_t T[128];
+  uint8_t index = 0, t;
+  int i;
+  index = (index+secret)%128;
+  t = T[index % 4];
+  ...
+}
+\end{lstlisting}
+\end{minipage}
+\hspace{-4pt}
+\hfill
+\hspace{-4pt}
+\begin{minipage}{0.45\linewidth}
+\resizebox{\textwidth}{!}{%
+
+\begin{tabular}{cccccccccc}
+\toprule
+\diagbox{S}{T} & 0 & 1 & 2 & 3 & 4 & 5& 6& 7 &  ...\\ 
+\midrule
+0 & A &  &  &  &  &  \\
+1 &  & A &  &  &  &  \\
+2 &  &  & A &  &  &  \\
+3 & &  &  & A &  &  \\
+4 & A &  &  &  &  &  \\
+5 &  &  A& &  &  & & \\
+6 &  &  & A &  &  & & \\
+7 &  & &  &  A&  &  && \\ 
+\bottomrule
+\end{tabular}%
+}
+\end{minipage}
+\caption{A Minor Leakage. }\label{fig:example2}
+\end{figure}
+On the other hand, the second example also have a side-channel leakages at line 7.
+However, the leakage is slightly different.
+Still, we test the program with input from $0, 1, \dots, 7$.
+However, we find the attacker can not uniquely determine the secret based on the observation of table $T$.
+For example.
+both $0$ and $4$ read the first the item of the table.
+Therefore, we think the vulnerability is slightly minor than the previous one.
+Here comes with the definition of the amount of leaked information of the vulnerability.
+
+\begin{mydef}
+    \label{def}
+    Suppose we have a program $\beta$ with the input set $K$. We randomly select $k_1, k_2, \dots, k_n \in K' \subseteq K$ as the input. We denote it as
+    $$\beta(K') \rightarrow	O'$$
+
+    Here $O$ is a set that consists of various observations $o_1, o_2, \dots, o_m$. The amount of leaked information $L_{\beta(K')\rightarrow O'}$ based on the observation ($o$) is
+    $$L_{\beta(K')\rightarrow O'} = H(O') $$
+\end{mydef}
+
+With Definition~\ref{def}, we can calculate the information leakage in Figure~\ref{fig:example1} and Figure~\ref{fig:example2} respectively.
+In Figure~\ref{fig:example1}, we have $8$ kinds of observations and each observation is uniformly distributed.
+Therefore, the information leakage is $log_2{8} = 3$ bits.
+In Figure~\ref{fig:example2}, we have $4$ kinds of observations and each observation is also uniformly distributed.
+Therefore, the information leakage is $log_2{4} = 2$ bits.
+We test the program with $8$ inputs.
+Therefore, the Shannon entropy of the original K $H(K)$ is also $3\,\mathrm{bits}$, according to Equation~\ref{eq1}.
+Therefore, the leakage in Figure~\ref{fig:example1} show the leakage is leaked totally.
+
+\subsection{A Conservative Estimation}
+In this section, we prove Definition~\ref{def} is the conservative estimation of the amount of leaked information based on the channel capacity.
+
+\begin{theorem}\label{the1}
+If an attacker launches a side-channel attack on  deterministic programs, then the channel between the secret and the observation is a noiseless loss channel.
+\end{theorem}
+
+\begin{myprof}
+According to information theory,
+\begin{align*}
+     I(K;O) & = H(O) - H(O|K) \\
+            & = H(O) - \sum_{k {\in} K }{p(o|k)\log_2p(o|k)}
+\end{align*}
+For a deterministic program, $p(o|k)=1$. As a result, $H(O|K) = 0$.
+\begin{align*}
+     C(K;O) = \max_{p(k)} I(K;O) = \max_{p(k)} H |O| 
+\end{align*}
+\end{myprof}
+
+With THEOREM~\ref{the1}, we can have
+\begin{align*}
+     \max_{p(k)} H |O| >= \max_{p(k')} H |O'| >= H |O'|
+\end{align*}
+
+Accordingly, if Definition~\ref{def} says the vulnerability leakage has $m$ bits of leakages, then the vulnerability can have at least $m$ bits of leakages.
+We can use the definition to detect those severe leakages.
+In the examples of Figure~\ref{fig:example1} and Figure~\ref{fig:example2}, because the input secret range from $0$ to $255$, we can calculate the precise value of the amount of information leakage by iterating each input keys.
+In Figure~\ref{fig:example1}, each item in the array could be read.
+Therefore, the channel capacity in Figure~\ref{fig:example1} is $\log_2{128} = \,7\, \mathrm{bits}$.
+In Figure~\ref{fig:example2}, there could be $4$ kinds of information, so the information leakages defined by channel capacity is $\log_2{4} = \,2\, \mathrm{bits}$.
+Compared with the result from Definition~\ref{def}, we can see that the amount of leakages by Definition is a conservative estimation.
+
+\section{Align Non-deterministic Address Access Across Multiple Executions}
+We compare address accesses of different executions generated by different inputs to quantify the amount of leakage information.
+A meaningful comparison requires we align executions across multiple runs before we quantify the leakage.
+In this work, we combine the information from both the source code and the binary executable to align the memory access during the execution.
+
+\begin{figure}[h]
+\begin{minipage}{0.45\linewidth}
+\begin{lstlisting}[numbers=none]
+uint8_t *T = malloc(4);
+if (T==NULL) exit(1);
+...
+t = T[i];    
+\end{lstlisting}
+\end{minipage}
+\hfill
+\begin{minipage}{0.6\linewidth}
+\resizebox{\textwidth}{!}{
+
+\includegraphics[width=\columnwidth]{./figures/align.pdf}
+
+}
+\end{minipage}
+\caption{Without proper address alignment, there could be many false positives and false negatives.}\label{fig:align}
+\end{figure}
+
+Considering the example in figure~\ref{fig:align}, it read the data from the array \textsf{T} based on the index (i).
+If the index (i) is associated with a key, it could be a side-channel vulnerability.
+Unlike the example in the previous section, the array \textsf{T} is on the heap.
+Data on the heap are allocated in different addresses each time.
+Suppose during the first run, \textsf{T} is allocated at the address \textsf{0xff124800} and \textsf{T} is allocated at the address \textsf{0xff124801} at the second run.
+For the example in Figure~\ref{fig:align}(a), the index that used to access the array is always $1$, so it should not be a side-channel vulnerability here.
+However, because the based address is different.
+So we get two different memory accesses.
+Under the circumstance, it is a false positive.
+Besides, it can cause false negatives as the example shown in Figure~\ref{fig:align}(b).
+In the example, different keys lead to different index.
+However, as $T_0 + i_0$ equals to $T_1 + i_0$, \tool{} can not observe the difference here, which can cause a false positive.
+
+\textbf{Our Strategy: } We assign a value for each memory location~\cite{sumner2010memory}. The value should satisfy the following characteristics. 
+\begin{itemize}
+\item \textbf{Uniqueness.} At any point during the execution, different memory cells must have a different value.
+\item \textbf{Alignment.} The same memory cell across multiple executions should share the same value.
+\end{itemize}
+
+There are some possible solutions that can assign the value.
+\textbf{Run-time Information.} One example here is the concrete memory address during the runtime.
+Such a value satisfy the uniqueness characteristic.
+However, as the example shown in Figure~\ref{fig:align}, it does not have the alignment property.
+\textbf{Source Code Information.} Alternatively, we can use the information from the source code.
+Recent work~\cite{sumner2010memory} proposes using the execution point that allocate the memory cell as the index and tracking the pointer arithmetic to track the pointer that points to the memory.
+However, such a method may miss the alias symbol that points to the same memory cell.
+
+We propose to combine both the information from the source code and the runtime to align the memory access during the execution.
+At the point the memory is allocated, we use the tuple $(start\ address, length)$ to represent the buffer.
+In the following execution, we check if any memory access falls into the range of those tuples.
+If so, we add the memory access into the tuple.
+After the execution, the tuple can be mapped into the location of the source code and we only compare the memory access that belongs to the same lines in the source code.
+
+\section{Design}
+In this section, we explain the implementation of \tool{}.
+we first present the overview of \tool{}. After that, we discuss some design details to implement \tool{}.
+
+\subsection{Overview}
+Figure~\ref{fig:workflow} shows an overview of our side-channel leakages quantification tool.
+Given the source code of the victim program, \tool{} can find the address-based side-channel leakages by fuzzing the victim program.
+To assist the illustration, we divide the workflow of ~\tool{} into three steps.
+For the first step, we build the target program from the source code.
+After that, we give them random inputs to the victim program and run the target program and record each of the address in the binary file is hit or not and store the information in a bitmap.
+Next, we analyze the side-channel leakage from the address access bitmap.
+We split the address space into several segments to speed up the comparison according to Meta information.
+Finally, \tool{} Generate the final leakage report.
+For each leakage sites, \tool{} gives the conservative estimation of the information leakage.
+Every leakage site in the report is a true leakage and there is no false positives.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=\columnwidth]{./figures/workflow.pdf}
+    \caption{The workflow of \tool{}. We try to divide the \tool{} into three steps to assist the illustration. }\label{fig:workflow}
+\end{figure}
+
+\subsection{Step 1: Fuzzing}
+After we build the software into the binary executable, we give the binary code the random inputs.
+For cryptography libraries, the input is the encryption key.
+For non-cryptography libraries, the input could be images, text, and information in other format.
+Encryption algorithms like AES, DES take an array representing the secrets.
+We generate the random input by flipping the each bit of the keys.
+Some other programs also takes an buffer as the input.
+The buffer may contains the redundancy information and follow a specific format.
+So not any input that satisfies the input length is a valid input.
+Under the circumstance, we have a dictionary that contains the input.
+For example, Crypto libraries usually take PKCS \#1 as the input of RSA private key.
+We use some other tools to generate a list of valid keys and use the key to sample the program.
+Due to the enormous search space, we can not iterate every inputs.
+However, our method can give the conservative  estimate of each leakage site.
+\subsection{Step 2: Address Record}
+Next, we record the memory access information based on the input secret.
+We use the dynamic binary instrumentation (DBI) tool to record the whether a particular memory access information is accessed or not.
+Inspired by the AFL and valgrind, we use the bitmap to represent whether a particular memory is accessed or not.
+For example, the bitmap ${0101}$ of address $address_1, address_2, address_3, address_4$ means that $address_2, address_4$ are hit during the execution.
+During the execution, the direct information we get is the virtual memory address (VMA).
+However, we transfer the address into the offset (Load Memory Address (LMA)) in the original binary file.
+It has two benefits.
+First, modern computer systems employ the the Address Space Layout Randomization (ASLR).
+With ASLR, the operating system randomly put the enclave code and data at various memory offset.
+As a result, even for the same input, the code will get different execution traces because the enclave image is loaded at a different address each time Second, it helps us find the leakage site in the source code.
+
+We rely on the program header and symbol information to recover the offset in the binary.
+During the loading process, the operating system maps each segment into a continuous memory region.
+So the offset of the virtual memory address between the code within the same segment is the same as the offset within the binary file.
+We choose the start address of some common functions (e.g, $main$) ($b$) as the navigation function.
+We get the virtual memory address of the start of the function ($\mathit{VMA_b}$) from the DBI tool and the load memory address of the function ($\mathit{LMA_b}$) from the symbol information.
+For any virtual address, we use Equation~\ref{equ:eq6} to calculate the offset in the original address.
+\begin{equation}\label{equ:eq6}
+    \mathit{LMA_a} = \mathit{LMA_b} - VMA_b - VMA_a
+\end{equation}
+
+There are two kinds of memory access: the access to the code and the access to the data. 
+\begin{itemize}
+\item Code Access.
+The memory address of the code is the value of $rip$ register.
+However, the length of x86 instructions can be from 1 byte to 15 bytes.
+For instructions whose length is longer than one byte, we also update the address  after the value $rip$ until the address reach the boundary of the instruction.
+\item Data Access.
+For instructions with memory access, we identify all the operands of each instruction and.
+Same as the code address, the instruction can read or write multiple bytes one time.
+Instructions like \textsf{push} and \textsf{pop} have implicit memory access.
+We all update the bitmap of the address correspondingly.
+\end{itemize}
+
+\subsection{Step 3: Leakages Detection and Quantification}
+In this step, we detect and quantify the side-channel leakage.
+For each $k \in K$, we have a boolean number ($0$ or $1$) to describe whether the address $addr$ is accessed or not during the execution when the input is $k$.
+For the brevity of description, For the brevity of description, we use $B^{addr}_{k_i}$ to denote the boolean number.
+
+\subsubsection{Various Granularities Side-channel Detection}
+\tool{} can detect the side-channel vulnerabilities in different granularity.
+For each granularity, we calculate a new bitmap that represents access information of each unit.
+We have the bitmap of the memory access at the byte level.
+An attacker who has the coarse-grained observation at address space may not be able to distinguish the address difference.
+For example, modern X64 computer system uses 48-bit virtual memory addresses.
+The top 36 bit of the virtual address is called Virtual Page Number (VPN) and the bottom 12 bits of the virtual address is called offset.
+The memory management unit (MMU) transfer the virtual address into the physical address by mapping the Virtual Page Number (VPN) into the Physical Page Number (PPN) while keep the offset of the address.
+So two addresses with the Same VPN but different offset are not distinguishable by an attacker who only has the the page-level observation.
+
+Suppose a program reads one byte at memory $\mathsf{0x7ffff7ffd001}$ when the secret is $k_1$ and reads a different byte at memory $\mathsf{0x7ffff7ffda01}$ when the secret is $k_2$, an attacker who has the page-level observation can not launch the attack but an attacker who launches the cache attack can know the input is $k_1$ or $k_2$.
+We update the new bitmap of the large unit by merging the bitmaps of small units that fall into the large unit.
+That is, $\forall addr_1, addr_2, \dots, addr_n \in addr_N, B^{addr_N}_{k_i} = B^{addr_1}_{k_i} \lor,\dots,\lor B^{addr_N}_{k_n}$.
+
+\subsubsection{Leakage Detection} The access of the address is secret-dependent if $ \exists\, k_{i1}, k_{i2} \in K, \, B^{addr}_{k_i1} \oplus  B^{addr}_{k_i2} =1 $.
+In the paper, we perform the logical exclusive OR operation on every boolearn value in the same address.
+If the result is $1$, then the address is vulnerable to the side-channel attacks.
+
+\begin{myexample}
+Suppose we sample a program from $k1$ to $k8$ and record the memory access at the granularity of each byte from $\mathsf{7ffff7ffd000}$ to $\mathsf{7ffff7ffd03f}$ (One cache line), we perform the bit-wise or operation of each address with the address range.
+Because the cache line is always accessed.
+We think it is not a leak here.
+\begin{center}
+\begin{tabular}{c}
+{
+\begin{lstlisting}[frame=none]
+              k1  k2  k3  k4  k5  k6  k7  k8   Result  
+7ffff7ffd000   1   0   1   0   1   1   0   1 
+7ffff7ffd000   0   1   1   0   1   1   1   1 
+7ffff7ffd000   1   1   1   1   1   1   0   1 
+7ffff7ffd000   1   0   1   0   1   1   1   1 
+...
+7ffff7ffd03f   1   0   1   0   1   1   1   0  
+cache line     1   1   1   1   1   1   1   1    0 (No Leaks)
+\end{lstlisting}
+}
+\end{tabular}
+\end{center}
+\end{myexample}
+
+\subsubsection{Estimate The Leaked Information}
+According to Definition~\ref{def}, we quantify the information leakage based on the distribution of the observation.
+If we calculate the information leakage from an $4MB$ memory area, then the length of the byte-level bitmap is $4*1024*1024 = 4194304$.
+While it is possible to compute the distribution of the bitmap theoretically, it is hard to compare the bitmap of such length in practice.
+
+To solve the problem, we use the debug information to split the bitmap into several segments and map the leakage site into the location of the source code.
+Each segment maps the address access situation of the function in the source code.
+In our setting, the max length of the bitmap of each segment is $1024$, the length of \textsf{uint1024\_t}.
+So we can put the bitmap into a variable.
+The split operation ease the computation.
+But it also adds the limitation of max address range when we quantify the side-channel leakage shown in Table~\ref{tab:size_limitation}.
+We think the range of the memory is big enough for us to quantify the most of the cache side-channel attacks.
+
+\begin{table}[h]
+    \centering
+\resizebox{0.45\textwidth}{!}{%
+
+\begin{tabular}{llll}  
+\toprule
+Granularity  & Byte & Cache Line (64 Bytes) & Memory Page (4 KB) \\
+\midrule
+Range & 1024 Bytes & 64 KB  &  4 KB \\
+\bottomrule
+\end{tabular}
+}
+    \caption{The maximum range address range when we quantify the amount of the leakage with different granularity.}
+    \label{tab:size_limitation}
+\end{table}
+
+After that, we traverse the bitmap for each $k$ and count it to get the distribution of the bitmap. The counting process is like traversing a binary tree.
+
+\begin{myexample}
+Shown in Figure~\ref{fig:design:example2}, we have the following observation from $k_1$ to $k_8$, then we count the distribution of  the observation.
+The process is like traversing a binary tree and increase the counter of the child node.
+According to Definition~\ref{def}, the amount of the leakage is
+
+\begin{displaymath}
+  H(O') = - \frac{3}{8}*\log_2{\frac{3}{8}}- \frac{1}{2}*\log_2{\frac{1}{2}}
+  - \frac{1}{8}*\log_2{\frac{1}{8}} = 1.4 \,\mathrm{bits}
+\end{displaymath}
+
+\begin{figure}[h]
+\begin{minipage}{0.4\linewidth}
+\resizebox{\linewidth}{!}{
+  \begin{tikzpicture}
+  [level distance=1cm,
+  level 1/.style={sibling distance=2cm},
+  level 2/.style={sibling distance=1.5cm}]
+  \node {root}
+    child {node {0}
+      child {node {0:3}}
+      child {node {1:4}}
+    }
+    child {node {1}
+    child {node {0}}
+      child {node {1:1}}
+    };
+\end{tikzpicture}
+
+}\end{minipage}
+\hfill
+\begin{minipage}{0.18\linewidth}
+{
+\begin{lstlisting}[frame=none, numbers=none]
+k1  00
+k2  01
+k3  01
+k4  01
+k5  00
+k6  01
+k7  11
+k8  00
+\end{lstlisting}
+}
+\end{minipage}
+\hfill
+\begin{minipage}{0.30\linewidth}
+\resizebox{\linewidth}{!}{
+
+\begin{tabular}{ll}  
+\toprule
+Observation  & P  \\
+\midrule
+00 & $3/8$   \\
+01 & $1/2$   \\
+10 & 0 \\
+11 & $1/8$\\
+\bottomrule
+\end{tabular}
+}
+\end{minipage}
+\caption{Example 2}\label{fig:design:example2}
+\end{figure}
+\end{myexample}
+
+\section{Implementation}
+We have implemented a prototype of \tool{}.
+It takes an input of ELF binary as well as the source code of the corresponding problem.
+The front-end of \tool{} is implemented in Python.
+It can generate random inputs and test the program with those inputs many times.
+The address record part is implemented as an Intel Pin tool plugin in C++ to record the bitmap for each input.
+The main component uses libelfin, an open source library to parse ELF binaries and read DWARF debug information.
+The current implementation can support both 64-bits and 32-bits ELF binary in Linux.
+\tool{} will be open-sourced.
+
+\section{Discussion}
+
+This paper presents an approach that tries to give the conservative estimate of the amount of leaked information by address-based side-channel attacks.
+Those attacks exploit the data-flow from secrets to load address and the data-flow from the data-flow from secrets to branch conditions to retrieve secrets based on the observation on the memory accesses.
+Despite those kinds of side-channel leakages have been discovered for decades, the up-to-date software still has some side channel leakages.
+For some of those vulnerabilities, developers don't fix them because they think those side-channel vulnerabilities are not important.
+To show the importance of those side-channel leakages, one way is to demonstrate an end-to-end attack based on the vulnerability.
+However, demonstrating an end-to-end attack often need a lots of manual efforts and the domain knowledge of the victim program, which is not often the case in practices.
+It is good to have a tool that can assess the severity level of those side channel leakages automatically.
+So it would be better to have a proper metric to quantify the side-channel leakage.
+However, we find previous side-channel quantification tools are developed to  ensure the noninterference of the program.
+They use over approximation heuristics method to quantify the leakage.
+For example, CacheAudit estimate that a 128-bit AES encryption can leaks more than 128 bits.
+As a result, even those tool reports severe leakage, it does not mean the program has a truly severe leakage.
+
+Our tool can give the conservative estimation of the side-channel leakage based on Channel Capacity.
+The channel capacity measures  the information flow between the source and the destination.
+One useful characteristic of channel capacity is not affected by the distribution of the input, which is useful because in practice we can not have an assumption on the input secrets of the software.
+In the paper, we use the sampling result to over approximate the true value of the channel capacity.
+We prove the sampling method presented in the paper can only give the conservative estimation of the amount of the true leakage.
+
+\subsection{Limitation}
+\tool{} is a dynamic approach.
+So it bears the same limitations of dynamic approaches as well.
+\tool{} may have the coverage problem and can miss some side-channel vulnerabilities.
+It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control-flow with various inputs.
+For other libraries like graphic rendering, machine learning, \tool{} is very likely to miss some side-channel vulnerabilities.
+However, \tool{} is not designed to find side-channel vulnerabilities.
+The goal of \tool{} is to pick up those really serious side-channel vulnerabilities from the numerous vulnerabilities.
+So we do not think it is a main limitation of \tool{}.
+However, users of \tool{} should be aware the code coverage problem.
+
+Another limitation is that \tool{} can only find the position in the code that leaks the sensitive information, but it is not the root cause of the leaks.
+Consider the example in Figure~\ref{fig:limitation}, it takes the secret as the input.
+At line 3, it calculate an index based on the value of the secret.
+Depending on the value of index, it may or may not run the code at line 6.
+So line 5 is the reason that causes the vulnerability.
+But \tool{} can only tell the line 6 can leak the information, despite it is not the root cause of the vulnerability.
+
+\begin{figure}
+\centering
+\begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
+int foo(uint8_t secret){
+  uint8_t index = 0, t;
+  index = (index+secret)%128; // The index contains secrets
+  ...
+  if(index == 0){             // Secret-dependent flows
+    bar(r, x, n)              // The observation
+  }
+  ...
+}
+\end{lstlisting}
+    \caption{A code fragment}
+    \label{fig:limitation}
+\end{figure}

### 2021-03-26 Appendix-A/Appendix-A.tex
Updates from Overleaf

--- 2021-02-14 Chapter-2/Chapter-2.tex
@@
 % !TEX root = ../YourName-Dissertation.tex
+\Appendix{Abacus Usage Manual}
 
-\chapter{Background}
+\section{Introduction}
 
-\section{Address-based Side-channel Attacks}
+\tool{}~\cite{bao2021abacus} is an address-based side-channel vulnerability analysis tool.
+Different from previous tools~\cite{203878,236338,182946}, it can also give a precise estimation of the amount of the leaked information for each leakage site.
+\tool{} is open source under the MIT License.
 
-\section{Information Theory}
+%% We quantify the amount of leaked information for each leakage site
+%% based on the search space. For example, if the length of the key is
+%% 128 bits, an attacker needs to brute force $2^{128}$ possible keys
+%% without any domain knowledge. However, suppose the attacker observes
+%% some information and can reduce the size of the search space to
+%% $2^{120}$. Then we can conclude 8 bits of the information are leaked.
 
-\section{Binary Analysis}
+\tool{} takes a binary executable as the input.
+It uses dynamic binary instrumentation tools to collect execution traces.
+After that, \tool{} analyzes those traces and produces the vulnerability report.
+While \tool{} can work on the stripped binary executable, \tool{} can also read the symbol and debugging information to give a more fine-grained (e.g., line numbers) report.
+Table~\ref{tab:DESOpenSSL1.1.1} shows an example of the report.
+If you are interested in how \tool{} works, please refer to the technical paper~\cite{bao2021abacus}.
+
+\begin{table}[h!]
+\centering\tiny\scriptsize
+\caption{A sample leakage report}\label{tab:DESOpenSSL1.1.1}
+%\resizebox{\columnwidth}{!}{
+\begin{tabular}{lrlrr}
+\toprule
+\textbf{File} & \textbf{Line No.} & \textbf{Function} & \textbf{\# Leaked Bits} & \textbf{Type} \\\toprule
+set\_key.c& 350&DES\_set\_key\_unchecked&5.8 &DA\\
+set\_key.c& 350&DES\_set\_key\_unchecked&6.6 &DA\\
+set\_key.c& 350&DES\_set\_key\_unchecked&7.5 &DA\\
+set\_key.c& 350&DES\_set\_key\_unchecked&6.4 &DA\\
+set\_key.c& 355&DES\_set\_key\_unchecked&1.9 &DA\\
+set\_key.c& 355&DES\_set\_key\_unchecked&3.1 &DA\\
+\bottomrule
+\end{tabular}
+%}
+\end{table}
+
+\section{Requirements}
+We have tested \tool{} on both macOS and Ubuntu.
+You can refer to the continuous integration scripts to build \tool{} on your operating system.
+However, we strongly recommend you to build \tool{} inside a container to avoid any dependency problems.
+To simplify the illustration, we only include the instructions of installations within the docker in this paper.
+\begin{itemize}
+\item Supported OS: Ubuntu 18.04
+\item Memory: 32 GB (If you want to run experiments concurrently, update the size of RAM
+     accordingly. Otherwise the program may be terminated by the system.)
+\end{itemize}
+
+\section{Installation}
+
+\tool{} can be built within a docker, simply run the following command:
+
+\begin{lstlisting}[language=bash]
+$ git clone https://github.com/s3team/Abacus.git
+$ cd Abacus
+$ ./docker.sh
+\end{lstlisting}
+
+The ``docker.sh'' script creates a docker image automatically and enters the container that includes all dependencies. After that, run the following command to build \tool{}:
+
+\begin{lstlisting}[language=bash]
+$ ./build.sh
+\end{lstlisting}
+\section{Run the hello world example}
+In this section, we walk you through the steps to test a simple function with \tool{}.
+
+\begin{figure}[h]
+\begin{lstlisting}[xleftmargin=.07\textwidth, xrightmargin=.07\textwidth,numbers=left, frame=single, language=C]
+#include <stdio.h>
+
+void is_odd(uint16_t secret) {
+  int res = secret % 2;        
+  if (res) {             
+    printf("Odd Number\n");
+  } else {
+    printf("Even Number\n");
+  }
+}
+\end{lstlisting}
+\caption{A simple example}
+\label{fig:example0}
+\end{figure}
+
+As shown in Figure~\ref{fig:example0}, the function takes a 32-bit integer as the secret input and checks the last digit of the integer.
+An attacker can know the last bit of the input integer by observing which branch is actually executed.
+So in the above function, we think the code has one secret-dependent control-flow vulnerability, and it can leak one bit of the secret information.
+
+\subsection{Mark secret data as symbolic}
+In order to test this function with \tool{}, we need to mark the variable that representing the secret data as a symbolic variable.
+We use the function \textsf{abacus\_make\_symbolic}.
+The function takes three arguments: the type of the symbol, the address of the secret, and the length of the secret input.
+In the below example, the secret input is the variable \textsf{secret}, and its length is two bytes.
+We add the \textsf{main} function in Figure~\ref{fig:example1} and compile the source code into an executable.
+
+\begin{figure}[h]
+\begin{lstlisting}[firstnumber=12, xleftmargin=.07\textwidth, xrightmargin=.07\textwidth, numbers=left, frame=single, language=C]
+int main() {
+  uint16_t secret = 6;
+  char *type = "1";
+  abacus_make_symbolic(type, &secret, 2); 
+  is_odd(secret);
+  return 0;
+}
+\end{lstlisting}
+\caption{A simple function that marks a variable \textsf{secret} as symbolic}
+\label{fig:example1}
+\end{figure}
+
+\subsection{Build the example}
+
+Abacus analyzes vulnerabilities on the binary executable.
+Here we build it into  a 32-bit ELF executable.
+Note that while Abacus can work on stripped binaries without the source code, we use debug information to get a more detailed result (e.g., the line number in the source code) in this example.
+\begin{lstlisting}[language=bash]
+$ cd examples
+$ gcc -m32 -g example1.c
+\end{lstlisting}
+
+\subsection{Collect the trace}
+We use the pin tool to collect the execution trace. The tool can automatically collect the trace and other necessary runtime information.
+\begin{lstlisting}[language=bash]
+$ cd /abacus/Pintools
+$ make PIN_ROOT=/abacus/Intel-Pin-Archive/ TARGET=ia32
+$ cd /abacus
+$ /abacus/Intel-Pin-Archive/pin \ 
+  -t Pintools/obj-ia32/MyPinToolLinux.so \
+  -- ./examples/a.out 
+\end{lstlisting}
+
+You will get two files \textsf{Function.txt} and \textsf{Inst\_data.txt}. \textsf{Inst\_data.txt} is the mandatory input of \tool{}. \textsf{Function.txt} is optional.
+
+\subsection{Quantify the leakage}
+To analyze the execution trace and generate the report, run the below command:
+\begin{lstlisting}[language=bash]
+
+$ ./build/App/QIF/QIF ./Inst_data.txt -f Function.txt \ 
+  -d ./examples/a.out -o result.txt
+\end{lstlisting}
+
+You should get the following output:
+
+\begin{lstlisting}[language=bash]
+Start Computing Constraints
+Total Constraints: 1
+Control Transfer: 1
+Data Access: 0
+Information Leak for each address:
+Address: 5664259b Leaked:1.0 bits Type: CF  
+Source code: example1.c line number: 3
+Function Name:  is_odd Module Name:  a.out Offset: 30
+...
+\end{lstlisting}
+
+As expected, it shows that the function \textsf{is\_odd} has one secret-dependent control-flow vulnerability at line 5. Also, Abacus shows the vulnerability leaks 1 bit information.
+
+\section{Analyze Cryptography Function}
+We have applied \tool{} on the following libraries:
+\begin{itemize}
+\item OpenSSL: 0.9.7, 1.0.2f, 1.0.2k, 1.1.0f, 1.1.1, 1.1.1g
+\item MbedTLS: 2.5, 2.15
+\item Libgcrypt: 1.8.5
+\item Monocyper: 3.0
+\end{itemize}
+
+The results can be reproduced by running the simple command after you build \tool{} successfully inside the container. We have prepared scripts to analyze each cryptography algorithm automatically.
+For example, if you want to test AES in mbedTLS 2.5, you can simply run the 
+following command.
+
+\begin{lstlisting}[language=bash]
+$ cd /abacus/script/AES_MBEDTLS_2.5
+$ ./start.sh
+\end{lstlisting}
+
+\section{Command-line Options}
+\tool{} takes the trace file as the input (\textsf{Inst\_data.txt}). Besides the trace file, \tool{} has the following command-line options:
+\vspace{6pt}
+\\\textsf{-d {<executable file>}}
+\\ Read an elf \textit{executable file}.
+\tool{} can parse the debug information inside the file.
+With the optional input, \tool{} is able to output which line in the original source code actually leaks the sensitive information.
+\vspace{6pt}
+\\\textsf{-f {<function file>}}
+\\Read a function file that was generated by the Pin tool.
+The command is optional.
+With the optional input, \tool{} is able to output which function leaks the information and call sites from the sensitive buffer to the leaked site.
+\vspace{6pt}
+\\\textsf{-n {<Monte Carlo times>}}
+\\ Set the times of Monte Carlo Sampling when \tool{} estimates the amount of leakage information.
+If you do not specify the option, \tool{} can automatically terminate the sampling when the tool has 95\% confidence that the error of estimated leaked information is less than 1 bit.
+Please refer to the paper if you want to learn more about the details.
+\vspace{6pt}
+\\\textsf{-a {<the address of the secret buffer>} \\-s {<the size of the buffer>}}
+\\The two input options must be used together.
+In the previous example, we use \textsf{abacus\_make\_symbolic} to mark the secret buffer.
+For a raw binary, we use the above two options to tell \tool{} which buffer is the secret and its length.

### 2021-03-26 Appendix-A/Appendix-A.tex
Updates from Overleaf

@@
 
-\begin{lstlisting}[language=bash]
+\begin{lstlisting}[language=bash, frame=none, numbers=none]
 $ git clone https://github.com/s3team/Abacus.git
@@
 \begin{lstlisting}[language=bash]
-
 $ ./build/App/QIF/QIF ./Inst_data.txt -f Function.txt \ 

### 2021-03-26 figures/chapter4/form2figure.py
add figures

@@ -1,0 +1,88 @@
+#!/usr/bin/env python3
+# -*- coding: UTF-8 -*-
+import matplotlib
+import numpy as np
+
+matplotlib.use('pdf')
+basicPath = './'
+formPath = basicPath + 'form/'
+figurePath = basicPath + 'result/'
+
+
+def count(formName):
+    form = open(formName, 'r')
+    buf = form.readline()
+    buf = form.readline()
+    buf = form.readline()
+    while (buf):
+        if buf.split('|')[4] != 'Failed':
+            data[int(buf.split('|')[4])] += 1
+        else:
+            data[-1] += 1
+        buf = form.readline()
+
+    form.close()
+
+
+def plot(formName):
+    import matplotlib.pyplot as plt
+    plt.figure(figsize=(5, 5))
+    yax = plt.axes().yaxis
+    yax.set_ticks_position('none')
+    # yax.set_tick_params(pad=10)
+    xax = plt.axes().xaxis
+    # xax.set_ticks_position('none')
+    # xax.set_tick_params(pad=10)
+    dataLength = len(data) - 2
+    while data[dataLength] == 0:
+        dataLength -= 1
+    dataLength += 2
+
+    xtitles = list(range(dataLength))
+    if 'RSA' in formName:
+        if 'openssl' in formName:
+            plt.ylim(0, 80)
+            # plt.xlim(0.5, 15.5)
+            plt.xlim(-0.5, 15.5)
+
+            for i in range(len(xtitles)):
+                if (i % 2 == 0):
+                    xtitles[i] = ''
+
+            plt.yticks([10, 30, 50, 70])
+
+    xtitles[-1] = '*'
+    plt.xticks(range(dataLength), xtitles)
+
+    failedLable = plt.axes().get_xticklabels()
+    failedLable[-1].set_rotation(270)
+    data[dataLength-1] = data[-1]
+    plt.bar(range(dataLength),
+            data[:dataLength], align='center', color='grey', width=0.8)
+    # plt.bar(range(1, dataLength),
+    #         data[1:dataLength], align='center', color='grey', width=0.8)
+    plt.xticks(fontsize=18)
+    plt.yticks(fontsize=18)
+    plt.ylabel('Number of Leakages', fontsize=22)
+    plt.xlabel('Leakage Amount (bits)', fontsize=22)
+    # plt.title(formName.replace('.', ' ', 2), fontsize = 10)
+    plt.tight_layout()
[…]

### 2021-03-26 figures/chapter4/result2form.py

@@ -1,0 +1,53 @@
+#!/usr/bin/env python2
+# -*- coding: UTF-8 -*-
+
+import os
+import sys
+
+basicPath = './'
+resultPath = basicPath + 'form/'
+
+
+def data2form(finame, foname):
+    fi = open(finame, 'r')
+    buf = fi.readline()
+    fo = open(foname, 'w')
+    fo.write('| File | Line Num | Function | Leaked bits | Type | Location |\n' +
+             '| :--: | :------: | :------: | :---------: | :--: | :------: |\n')
+    while buf[:8] != 'DETAILS:':
+        while buf[:8] != 'Address:':
+            buf = fi.readline()
+
+        if buf[17:22] == 'Monte':
+            leakage = 'Failed'
+            ltype = ''
+        else:
+            leakage = buf[24:26]
+            ltype = buf[buf.find('Ty') + 6:buf.find('Ty') + 8]
+
+        buf = fi.readline()
+
+        lfile = buf[buf[13:].find(
+            ':') + 15: buf[buf[13:].find(':') + 15:].find(' ') + buf[13:].find(':') + 15]
+        lnumber = buf[-4:-1]
+        fo.write('|' + lfile + '|' + lnumber + '||' +
+                 leakage + '|' + ltype + '||\n')
+
+        buf = fi.readline()
+
+    fo.close()
+    fi.close()
+
+
+for enc in ['AES', 'DES', 'RSA']:
+    # mbedTLS
+    for version in ['2.5', '2.15.1']:
+        finame = 'result_' + enc + '-mbedTLS-' + version + 'Inst_data.txt'
+        foname = resultPath + enc + '.mbedTLS.' + version
+        data2form(finame, foname)
+
+    # openssl
+    for version in ['0.9.7', '1.0.2f', '1.0.2k', '1.1.0f', '1.1.1']:
+        finame = 'result_' + enc + '-openssl-' + version + 'Inst_data.txt'
+        foname = resultPath + enc + '.openssl.' + version
+        data2form(finame, foname)

### 2021-03-26 figures/chapter4/result2formLatex.py

@@ -1,0 +1,112 @@
+#!/usr/bin/env python3
+# -*- coding: UTF-8 -*-
+
+import os
+import sys
+
+basicPath = './'
+inputPath = basicPath  # + 'result_OCT17/'
+resultPath = basicPath + 'form/latex/'
+
+
+def data2form(finame, foname, enc, library, version):
+    sys.stdout.write(foname)
+    sys.stdout.flush()
+
+    with open(finame, 'r') as fi:
+        buf = fi.readline()
+        fo = open(foname, 'w')
+        fo.write('\\begin{table}[h!]\n' +
+                 '\\centering\\tiny\\scriptsize\n')
+        if enc == "AES" and library == "OpenSSL" and version == "1.1.0f":
+            fo.write('\\renewcommand{\\baselinestretch}{0.96}\\selectfont\n')
+        if enc == "AES" and library == "OpenSSL" and version == "1.1.1":
+            fo.write('\\renewcommand{\\baselinestretch}{0.96}\\selectfont\n')
+
+        fo.write('\\caption{Leakages in ' + enc +
+                 ' implemented by ' + library + ' ' + version + '}'
+                 '\\label{tab:' + enc + library + version + '}\n' +
+                 '%\\resizebox{\\columnwidth}{!}{\n')
+
+        if enc == "RSA" and library == "OpenSSL" and version in ["1.1.1", "1.1.0f"]:
+            fo.write('\\begin{tabular}{l@{~~}rlr@{~~}r}\n')
+        else:
+            fo.write('\\begin{tabular}{lrlrr}\n')
+
+        fo.write('\\hline\n' +
+                 '\\textbf{File} & ' +
+                 '\\textbf{Line No.} & ' +
+                 '\\textbf{Function} & ')
+
+        if enc == "RSA" and library == "OpenSSL" and version == "1.1.1":
+            fo.write('\\hspace*{-20em}')
+
+        fo.write('\\textbf{\# Leaked Bits} & ' +
+                 '\\textbf{Type} ' +
+                 '\\\\\\hline\n')
+        #  '\\textbf{Location} ' + '\\\\\\hline\n')
+
+        while buf and buf[:8] != '--------':
+            buf = fi.readline()
+
+        # buf = fi.readline()
+
+        while buf and buf[:8] != 'Address:':
+            buf = fi.readline()
+
+        while buf:
+            if buf[17:21] == 'Type':
+                leakage = '*'
[…]

### 2021-03-26 figures/chapter4/running_time_figure.py

@@ -1,0 +1,57 @@
+#!/usr/bin/env python3
+# -*- coding: UTF-8 -*-
+import matplotlib
+import numpy as np
+import csv
+
+matplotlib.use('pdf')
+basicPath = './'
+formPath = basicPath + 'form/'
+figurePath = basicPath + 'result/'
+
+
+def count(formName):
+    with open(formPath + formName + '.csv', 'r') as se_optimized:
+        f_csv = csv.reader(se_optimized)
+        time = next(f_csv)
+
+    time = time[:-1]
+
+    for i in range(len(time)):
+        # time[i] = int(time[i].replace('.', ''))
+        # # time[i] += time[i-1]
+        # time[i] = time[i]/10e5
+        time[i] = float(time[i])
+
+    print(time)
+    return time
+
+
+def plot(formName, line1, line2):
+    import matplotlib.pyplot as plt
+    plt.figure(figsize=(5, 5))
+
+    plt.plot(range(len(line1)), line1, color='grey')
+    plt.plot(range(len(line2)), line2, color='grey')
+
+    plt.xticks(fontsize=9)
+    plt.yticks(fontsize=9)
+    plt.ylabel('Time (s)', fontsize=11)
+    plt.xlabel('Number of Instructions (10e4)', fontsize=11)
+    # plt.title(formName.replace('.', ' ', 2), fontsize = 10)
+    plt.tight_layout()
+    plt.savefig(figurePath + formName.replace('.', '-') +
+                '.pdf', format='pdf')
+    plt.close('all')
+
+
+time1 = count('time_openssl1.1.1')
+time2 = []
+# for i in range(len(time1)-1):
+#     time2.append(time1[i + 1] - time1[i])
+
+# print(time2)
+# time2 = count('se_non_optimized')
+# time2 = []
+# time2[0] += 1
+plot('running_time', time1, time2)

### 2021-03-26 Chapter-3/Chapter-3.tex
update

@@
 in recent years, constraint solving remains one of the obstacles to achieve the
-scalability for real-world cryptosystems.
+scalability for real-world crypto systems.
 

### 2021-03-27 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 Side-channel attacks infer sensitive information such as cryptographic keys, personal data from software products unconsciously.
-As we discuss in \S\ref{chapter1} and \S\ref{chapter2}, patching software are usually easier than adopting new hardware to defend against side-channel attacks.
+As we discuss in \S\ref{chapter1} and \S\ref{chapter2}, patching leakage sites in software is usually easier than adopting new hardware to defend against side-channel attacks.
+In order to eliminate those leakage sites, the first step is finding those sites.
+
+Performance.
+
+Precision.
 

### 2021-03-28 Chapter-3/Chapter-3.tex
Updates from Overleaf

--- 2021-03-26 Chapter-3/Chapter-3.tex
@@
 Side-channel attacks infer sensitive information such as cryptographic keys, personal data from software products unconsciously.
-As we discuss in \S\ref{chapter1} and \S\ref{chapter2}, patching software are usually easier than adopting new hardware to defend against side-channel attacks.
+Based on the discussions in \S\ref{chapter1} and \S\ref{chapter2}, patching leakage sites in software is usually easier than adopting new hardware to defend against side-channel attacks.
+In order to eliminate those leakage sites, developers also need to identify potential leakage sites from the code base manually.
+However, the manual process is tedious and error-prone.
+Recent studies~\cite{203878} also suggests fixing old vulnerabilities can sometimes introduce new leakages.
+
+Recent work has made good progress in identifying side-channel leakages automatically.
+Some tools (e.g., DATA, CacheD) have successfully identified unknown leakage sites from software products automatically.
+However, existing tools have the following limitations.
 

### 2021-03-28 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 However, the manual process is tedious and error-prone.
-Recent studies~\cite{203878} also suggests fixing old vulnerabilities can sometimes introduce new leakages.
+Recent studies~\cite{203878} also suggest fixing old vulnerabilities can sometimes introduce new leakages.
 
 Recent work has made good progress in identifying side-channel leakages automatically.
-Some tools (e.g., DATA, CacheD) have successfully identified unknown leakage sites from software products automatically.
-However, existing tools have the following limitations.
+Some tools (e.g., CacheD, CaSym) can successfully identify unknown leakage sites from software products automatically.
+However, those tools have the following limitations.
+
+First, although some tools can find side-channel leakages in real-world software products, they can only analyze one code fragment at a time due to the expensive performance overhead.
+As a result, users sometimes need to manually cut off some irrelevant code based on the user's experience.
+The trimming process is tedious and needs domain knowledge from users (e.g., which part of the code is more likely to have side-channel leakage sites).
+More importantly, those tools miss leakages on the trimmed code.
+
+Second, many tools perform the analysis at the level of intermediate representations (IR) instead of machine code to facilitate the implementations.
+However, side-channel leakages are a pretty low-level issue and a low-level analysis can give the most accurate results.
+For example, the IR-level branches isn't necessarily a superset or a subset of machine-code level branches.
+Besides, compiler optimizations can eliminate the IR-level branches like conditional moves and the converse could also happen.
+
+To overcome the problem, we
 
@@
       \label{scala:ir}
-\vspace*{-1pt}
-      \resizebox{\columnwidth}{!}{%
+      \resizebox{.7\columnwidth}{!}{%
 

### 2021-03-28 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 However, side-channel leakages are a pretty low-level issue and a low-level analysis can give the most accurate results.
-For example, the IR-level branches isn't necessarily a superset or a subset of machine-code level branches.
+For example, the IR-level branches is not necessarily a superset or a subset of machine-code level branches.
 Besides, compiler optimizations can eliminate the IR-level branches like conditional moves and the converse could also happen.
 
-To overcome the problem, we
+To overcome the problem, we propose a fast and precise method to detect the side-channel leakages in real-world software products.
+Different from previous methods, our tool analyzes on the machine code, which can give more precision than traditional IR-based approaches.
+We examine the bottleneck of current symbolic execution approaches and optimize it to work on real-world cryptography systems.
+The evaluation results show that our tool can identify previous side-channel leakages, as well as find new leakages.
+Compared to recent tools, our tool is 3-100x faster while finding all the leakages when we evaluate on the same benchmarks.
 
-\section{Threat Model}
+\section{Background and Threat Model}
+\subsection{}
+
+\subsection{Threat Model}
 We assume that an attacker shares the same hardware platform with the target.
@@
 
-\section{An illustrative example}
+\section{Illustrative examples}
 

### 2021-03-29 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \section{Background and Threat Model}
-\subsection{}
+\subsection{Micro-architectures}
+Many side-channel attacks are architecture-dependent. To facilitate the illustration, we present some necessary backgrounds in this section.
 
@@
 We assume that an attacker shares the same hardware platform with the target.
+The attacker attempts to retrieve sensitive information through address-based
+side-channel attacks. The attacker has no direct access to the target's memory or cache,
+but it can probe its memory or cache at each program point. 
 Here are a few examples.
@@
 3) An user level application can probe some sensitive information inside the kernel.
-The attacker attempts to retrieve sensitive information through address-based
-side-channel attacks. The attacker has no direct access to the target's memory or cache,
-but it can probe its memory or cache at each program point. In reality, the
+
+In reality, the
 attacker will face many possible obstacles such as the noisy observations 
@@
 
-\section{Math Notations}
+\section{Our Theoretical Frameworks}
 We now discuss how to model observations ($O$), which are the direct information

### 2021-03-29 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 Many side-channel attacks are architecture-dependent. To facilitate the illustration, we present some necessary backgrounds in this section.
+
+CPUs can process data much faster than the main memory (DRAM) can supply it.
+To bridge the performance gap between the CPUs and the main memory, modern CPUs adopt a hierarchy memory.
+By storing extra copies of data and code in a smaller but faster memory, the software can get its most recently accessed code and data in a shorter time.
+
+Figure~\ref{fig:memory_hierarchy} shows the overview of the hierarchy memory.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.65\columnwidth]{./figures/chapter3/architecture.pdf}
+    \caption{Computer Memory Hierarchy}\label{fig:memory_hierarchy}
+\end{figure}
 

### 2021-03-29 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 Figure~\ref{fig:memory_hierarchy} shows the overview of the hierarchy memory.
-
+For a CPU with multiple Cores, each core has two private level-1 (L1) cache, an instruction cache (iCache) and a data cache (dCache).
+Because instructions and data have different access patterns, separating iCache and dCache make it possible CPUs to fetch the code and data simultaneously and improve the performance.
+Followed by the level-1 cache, each core also has the unified private level-2 cache.
+The level-3 cache is the last level cache (LLC).
+The LLC is shared among all the cores.
+The main memory is the bottom-most under the memory hierarchy.
 \begin{figure}
@@
     \caption{Computer Memory Hierarchy}\label{fig:memory_hierarchy}
+\end{figure}
+
+The current computer memory hierarchy opens the way for side-channel attacks from two aspects.
+First, the architecture relies on the system software to manage the addressing, which becomes a problem in a threat model where the operating system is not untrusted (e.g., Intel SGX).
+Second, the size of the cache is smaller than the main memory, which makes it possible that several program shares the same cache unit (e.g., cache line, cache set).
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.65\columnwidth]{./figures/chapter3/address.pdf}
+    \caption{Computer Memory Hierarchy}\label{fig:memory_address}
 \end{figure}

### 2021-03-29 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
     \includegraphics[width=.65\columnwidth]{./figures/chapter3/address.pdf}
-    \caption{Computer Memory Hierarchy}\label{fig:memory_address}
+    \caption{Memory Addressing}\label{fig:memory_address}
 \end{figure}
+
+In modern CPUs, L1 and L2 caches are traditional N-way set associate caches.
+That is, the cache is divided into several cache sets, and each set is associated with several cache lines.
+The cache line is the atomic unit.
+As shown in Figure~\ref{fig:memory_address}, when the cache is accessed, the CPU uses the \textsf{Index} field of the address to locate a cache set.
+After that, it tries to use the \textsf{Tag} field to match every cache line inside the set line.
+If the CPU can locate a cache line with the same tag, then a cache hit occurs.
+The CPUs use a similar process to manage the main memory.
+The main memory is divided into many pages.
+As shown in Figure~\ref{fig:memory_address},
+the translation process keeps the bottom bits while use the top bits to map the Physical Page Numbers to Virtual Page Numbers.
 

### 2021-03-29 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 
-\section{Illustrative examples}
+\section{Examples}
+\subsection{Secret-dependent Control-flow Transfers}
+
+\subsection{Secret-dependent Data Accesses}
 
 \section{Our Theoretical Frameworks}
+\begin{figure}
+    \centering
+    \includegraphics[width=.35\columnwidth]{./figures/chapter3/attack.pdf}
+    \caption{A side-channel attack}\label{fig:side-channel-attack}
+\end{figure}
+
 We now discuss how to model observations ($O$), which are the direct information

### 2021-03-30 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \section{Problem}
-Side-channel attacks infer sensitive information such as cryptographic keys, personal data from software products unconsciously.
+Side-channel attacks allow an attacker to infer sensitive information such as cryptographic keys, personal data from software products unconsciously.
 Based on the discussions in \S\ref{chapter1} and \S\ref{chapter2}, patching leakage sites in software is usually easier than adopting new hardware to defend against side-channel attacks.
-In order to eliminate those leakage sites, developers also need to identify potential leakage sites from the code base manually.
+In order to eliminate those leakage sites, developers often need to identify potential leakage sites from the code base manually.
 However, the manual process is tedious and error-prone.
@@
 Recent work has made good progress in identifying side-channel leakages automatically.
-Some tools (e.g., CacheD, CaSym) can successfully identify unknown leakage sites from software products automatically.
+Some tools (e.g., CacheD, CaSym) have successfully identified unknown leakage sites from software products automatically.
 However, those tools have the following limitations.
@@
 First, although some tools can find side-channel leakages in real-world software products, they can only analyze one code fragment at a time due to the expensive performance overhead.
-As a result, users sometimes need to manually cut off some irrelevant code based on the user's experience.
-The trimming process is tedious and needs domain knowledge from users (e.g., which part of the code is more likely to have side-channel leakage sites).
-More importantly, those tools miss leakages on the trimmed code.
+As a result, users of those tools sometimes need to manually cut off some irrelevant code based on their past experience.
+The trimming process is tedious and needs domain knowledge of the target software (e.g., which part of the code is more likely to have side-channel leakage sites).
+More importantly, if many leakages sites are on the trimmed code, those tools will miss those leakage sites as well.
 
-Second, many tools perform the analysis at the level of intermediate representations (IR) instead of machine code to facilitate the implementations.
-However, side-channel leakages are a pretty low-level issue and a low-level analysis can give the most accurate results.
+Second, many tools perform the analysis at the level of intermediate representations (IR) instead of machine code.
+It is a design decision to facilitate the implementations.
+While analyzing the IRs can simplify the implementation, it is not a suitable design choice for the side-channel analysis.
+In reality, side-channel leakages are a pretty low-level issue and only the low-level analysis can give the most accurate results.
 For example, the IR-level branches is not necessarily a superset or a subset of machine-code level branches.
 Besides, compiler optimizations can eliminate the IR-level branches like conditional moves and the converse could also happen.
+Moreover, translating the machine code into IRs can casue a significant overhead for the trace analysis, as we will discuss in the dissertation.
 
-To overcome the problem, we propose a fast and precise method to detect the side-channel leakages in real-world software products.
+To overcome the above problems, we propose a fast and precise method to detect the side-channel leakages in real-world software products.
 Different from previous methods, our tool analyzes on the machine code, which can give more precision than traditional IR-based approaches.

### 2021-03-30 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 
-CPUs can process data much faster than the main memory (DRAM) can supply it.
-To bridge the performance gap between the CPUs and the main memory, modern CPUs adopt a hierarchy memory.
+CPUs process data in a much faster speed than the main memory (DRAM) can supply.
+Modern CPUs adopt a hierarchy memory to bridge the performance gap between the CPUs and the main memory.
 By storing extra copies of data and code in a smaller but faster memory, the software can get its most recently accessed code and data in a shorter time.
@@
 Figure~\ref{fig:memory_hierarchy} shows the overview of the hierarchy memory.
-For a CPU with multiple Cores, each core has two private level-1 (L1) cache, an instruction cache (iCache) and a data cache (dCache).
-Because instructions and data have different access patterns, separating iCache and dCache make it possible CPUs to fetch the code and data simultaneously and improve the performance.
-Followed by the level-1 cache, each core also has the unified private level-2 cache.
+For a CPU with multiple cores, each core has two private level-1 (L1) cache, an instruction cache (iCache), and a data cache (dCache).
+Because instructions and data have different access patterns, separating iCache and dCache makes it possible for CPUs to fetch the code and data and improve performance simultaneously.
+Followed by the level-1 cache, each core also has the unified private level-2 cache for both the code and the data.
 The level-3 cache is the last level cache (LLC).
@@
 The current computer memory hierarchy opens the way for side-channel attacks from two aspects.
-First, the architecture relies on the system software to manage the addressing, which becomes a problem in a threat model where the operating system is not untrusted (e.g., Intel SGX).
-Second, the size of the cache is smaller than the main memory, which makes it possible that several program shares the same cache unit (e.g., cache line, cache set).
-
+First, the architecture relies on the system software for managing the memory, which becomes a problem in a threat model where the operating system is not untrusted (e.g., Intel SGX).
+Second, the size of the cache is smaller than the main memory.
+Is is possible that different units in the main memory share the same address in the cache.
 \begin{figure}
@@
 The cache line is the atomic unit.
-As shown in Figure~\ref{fig:memory_address}, when the cache is accessed, the CPU uses the \textsf{Index} field of the address to locate a cache set.
+As shown in Figure~\ref{fig:memory_address}, we can determine whether the data is in the cache with the folowing steps.
+Given an address, the CPU uses the \textsf{Set Index} field of the address to locate the cache set that the address should reside in.
 After that, it tries to use the \textsf{Tag} field to match every cache line inside the set line.
-If the CPU can locate a cache line with the same tag, then a cache hit occurs.
+If the CPU can locate a cache line with the same tag and the valid bit is set, then a cache hit occurs.
 The CPUs use a similar process to manage the main memory.
-The main memory is divided into many pages.
+The main memory is divided into many units called pages.
 As shown in Figure~\ref{fig:memory_address},
-the translation process keeps the bottom bits while use the top bits to map the Physical Page Numbers to Virtual Page Numbers.
+the translation process keeps the bottom bits same while using the top bits to map the Physical Page Numbers to Virtual Page Numbers.
 

### 2021-03-30 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 side-channel attacks. The attacker has no direct access to the target's memory or cache,
-but it can probe its memory or cache at each program point. 
-Here are a few examples.
-1) A host machine has several Virtual Machines (VMs).
-The victim runs the application inside one VM.
-An attacker can start a new VM and probe the process running on the other VM.
-2) In a shielding system, a malicious operating system can extract sensitive information from the protected application.
-3) An user level application can probe some sensitive information inside the kernel.
+but it can probe its memory or cache at each program point. Here are a few examples. 
+\begin{enumerate}
+\item A host machine has several Virtual Machines (VMs). The victim runs the application inside one VM. An attacker can control the VM and probe the process running on the other VM.
+\item  In a shielding system, a malicious operating system can extract sensitive information from the protected application.
+\item An user level application can probe some sensitive information inside the kernel.
+\end{enumerate}
 

### 2021-03-30 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 Second, the size of the cache is smaller than the main memory.
-Is is possible that different units in the main memory share the same address in the cache.
+It is possible that different units in the main memory share the same address in the cache.
 \begin{figure}
@@
 The cache line is the atomic unit.
-As shown in Figure~\ref{fig:memory_address}, we can determine whether the data is in the cache with the folowing steps.
+As shown in Figure~\ref{fig:memory_address}, we can determine whether the data is in the cache with the following steps.
 Given an address, the CPU uses the \textsf{Set Index} field of the address to locate the cache set that the address should reside in.
@@
 The threat model captures most cache-based and address-based side-channel attacks. 
-We only consider deterministic programs and assume an attacker 
-has access to the source code or binary executable of the target program.
+We only consider deterministic programs and assume an attacker has access to the source code or binary executable of the target program.
 
-\section{Examples}
-\subsection{Secret-dependent Control-flow Transfers}
+\section{Side-channel Leakages}
+\subsection{Secret-dependent Control Flow Transfers}
 

### 2021-03-31 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 In reality, the
-attacker will face many possible obstacles such as the noisy observations 
-of the memory or cache. However, for this project, we assume
+attacker will face many possible obstacles such as the noisy observations of the memory or cache. However, for this project, we assume
 the attacker has noise-free observations as in previous work~\cite{203878,182946,Brotzman19Casym}. 
@@
 \subsection{Secret-dependent Control Flow Transfers}
+\begin{figure}[h]
+\begin{minipage}{0.4\linewidth}
+\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
+void example1(uint8_t k, uint32_t m) {
+  uint32_t b = (k & m) >> 7;
+  if (b) {
+    printf("branch 1\n");
+  } else {
+    printf("branch 2\n");
+  }
+}
+\end{lstlisting}
+\end{minipage}
+\hfill
+\begin{minipage}{0.4\linewidth}
+\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
+push  ebp
+mov   ebp, esp
+movzx eax, [addr_key]    
+and   eax, [addr_message] 
+shr   eax, 0x7           
+test  eax, eax
+jne   branch 2
+...
+\end{lstlisting}
+\end{minipage}
+
+\begin{minipage}{0.4\linewidth}
+\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
+int example6(uint16_t k) {
+  int res;
+  if (k > 8) {
+    res = 0;
+  } else {
+    res = 1;
+  }
+  return res;
+}
+\end{lstlisting}
+\end{minipage}
+\hfill
+\begin{minipage}{0.4\linewidth}
+\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
+xor   eax, eax
+cmp   [addr_k], 8
+setbe  al
+xor    edx, edx
+ret
+\end{lstlisting}
+\end{minipage}
+\caption{A Serious Leakage}\label{fig:chapter3:cf}
+\end{figure}
 

### 2021-03-31 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \section{Side-channel Leakages}
-\subsection{Secret-dependent Control Flow Transfers}
+This section discusses two types of side-channel leakage code patterns.
+The key intuition is that the target application shows different control flows or data flows when it processes different sensitive input data.
+We refer them as secret-dependent control flow transfers and secret-dependent data accesses.
+Unlike previous work, our tool works on the machine code, which can provide us more prevision than the previous tools.
+\subsection{Control Flow}
 \begin{figure}[h]
-\begin{minipage}{0.4\linewidth}
+\begin{minipage}{0.45\linewidth}
 \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
-void example1(uint8_t k, uint32_t m) {
+int example1(uint8_t k, uint32_t m) {
   uint32_t b = (k & m) >> 7;
   if (b) {
-    printf("branch 1\n");
+    ...    // Branch 1
   } else {
-    printf("branch 2\n");
+    ...    // Branch 2
   }
+  ...
 }
@@
 \hfill
-\begin{minipage}{0.4\linewidth}
+\begin{minipage}{0.45\linewidth}
 \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
@@
 \end{lstlisting}
-\end{minipage}
+\end{minipage}\caption*{(a)}
 
-\begin{minipage}{0.4\linewidth}
+\begin{minipage}{0.45\linewidth}
 \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
-int example6(uint16_t k) {
+int example2(uint16_t k) {
   int res;
@@
 \end{lstlisting}
-\end{minipage}
-\caption{A Serious Leakage}\label{fig:chapter3:cf}
+\end{minipage}\caption*{(b)}
+\caption{Secret-dependent Control-flow Transfers}\label{fig:chapter3:cf}
 \end{figure}
 
-\subsection{Secret-dependent Data Accesses}
+\subsection{Data Flow}
+\begin{figure}[h]
+\begin{minipage}{0.4\linewidth}
+\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
+uint8_t T[128];
+...
+int example3(uint8_t secret){
+  uint32_t index = 0;
+  index = (index + secret) % 128;
+  uint8_t t = T[index];
+  ...
+}
+\end{lstlisting}
+\end{minipage}
+\hfill
+\begin{minipage}{0.4\linewidth}
+\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
+...
+lea    edx, [addr_T]
+mov    eax, [addr_secret]
+and    eax, 0x7f
+movzx  eax, [addr_T + eax*1]
+...
+\end{lstlisting}
+\end{minipage}\caption*{(a)}
+
+\begin{minipage}{0.4\linewidth}
+\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
+uint8_t T[128];
+...
+int example4(uint8_t secret){
+  uint32_t index = 0;
+  index = (index + secret) % 128;
+  uint8_t t = T[index % 4];
+  ...
+}
+\end{lstlisting}
+\end{minipage}
+\hfill
+\begin{minipage}{0.4\linewidth}
+\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
+...
+lea    edx, [addr_T]
+mov    eax, [addr_secret]
+and    eax, 0x3
+movzx  eax, [addr_T + eax*1]
+...
+\end{lstlisting}
+\end{minipage}\caption*{(b)}
+\caption{Secret-dependent Data Accesses}\label{fig:chapter3:da}
+\end{figure}
 

### 2021-03-31 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 mov   ebp, esp
-movzx eax, [addr_key]    
-and   eax, [addr_message] 
+movzx eax, [addr_k]    
+and   eax, [addr_me] 
 shr   eax, 0x7           
@@
 \end{figure}
+
+The first type of leakage sites is secret-dependent control-flow leakage sites. Shown in Figure~\ref{fig:chapter3:cf}(a), the
 

### 2021-04-01 Chapter-3/Chapter-3.tex
update

@@
 
-The first type of leakage sites is secret-dependent control-flow leakage sites. Shown in Figure~\ref{fig:chapter3:cf}(a), the
+If the input sensitive data can affect the control flow of the victim program, then an attacker can infer the sensitive data by observing the control flow during the execution.
+Figure~\ref{fig:chapter3:cf}(a) shows such an example.
+The function takes a public value \textsf{m} and a secret \textsf{k} as the input values.
+The code at line 2 ensures that the lower 7 bits of the value \textsf{k} does not affect the value \textsf{b}.
+However, depending on the value of \text{m}, the code snippet in Figure~\ref{fig:chapter3:cf}(a) may have a leakage site.
+If the eighth bit of \textsf{m} is 1, then can attacker can also infer the eighth bit of \textsf{k} by observing the branch at line 4 or line 6.
+The right figure shows the corresponding machine code.
+It has a conditional jump instruction \textsf{jne}.
+As a result, the sensitive input \textsf{k} can affects the program counter (the rip register), which is the root cause of the side-channel leakages.
+Figure~\ref{fig:chapter3:cf}(b) shows an opposite situation.
+While the sensitive input \textsf{k} can affect the if else branch, the compiler removes the branch with a conditional set instruction.
 

### 2021-04-01 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 It has a conditional jump instruction \textsf{jne}.
-As a result, the sensitive input \textsf{k} can affects the program counter (the rip register), which is the root cause of the side-channel leakages.
-Figure~\ref{fig:chapter3:cf}(b) shows an opposite situation.
+The sensitive input \textsf{k} can affects the program counter (the rip register), which is the root cause of the side-channel leakages.
+Figure~\ref{fig:chapter3:cf}(b) shows a different situation.
 While the sensitive input \textsf{k} can affect the if else branch, the compiler removes the branch with a conditional set instruction.
-
+The opposite situation is the same.
+For example, recent work tries to  use bit masking to rewrite the program with control flows.
+However, for some situations~\cite{Coppens:2009:PMT:1607723.1608124}, compilers (e.g., GCC) optimize the code too much (from a security view) and remove the unnecessary copy by reintroducing conditional moves.
 \subsection{Data Flow}

### 2021-04-01 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 
-If the input sensitive data can affect the control flow of the victim program, then an attacker can infer the sensitive data by observing the control flow during the execution.
+If the input-sensitive data can affect the victim program's control flow, then an attacker can infer the sensitive data by observing the control flow during the execution.
 Figure~\ref{fig:chapter3:cf}(a) shows such an example.
 The function takes a public value \textsf{m} and a secret \textsf{k} as the input values.
-The code at line 2 ensures that the lower 7 bits of the value \textsf{k} does not affect the value \textsf{b}.
+The code at line 2 ensures that the lower 7 bits of the value \textsf{k} do not affect the value \textsf{b}.
 However, depending on the value of \text{m}, the code snippet in Figure~\ref{fig:chapter3:cf}(a) may have a leakage site.
-If the eighth bit of \textsf{m} is 1, then can attacker can also infer the eighth bit of \textsf{k} by observing the branch at line 4 or line 6.
+If the eighth bit of \textsf{m} is 1, then an attacker can also infer the eighth bit of \textsf{k} by observing the branch at line 4 or line 6.
 The right figure shows the corresponding machine code.
 It has a conditional jump instruction \textsf{jne}.
-The sensitive input \textsf{k} can affects the program counter (the rip register), which is the root cause of the side-channel leakages.
+The sensitive input \textsf{k} can affect the program counter (the rip register), which is the root cause of the side-channel leakages.
 Figure~\ref{fig:chapter3:cf}(b) shows a different situation.
-While the sensitive input \textsf{k} can affect the if else branch, the compiler removes the branch with a conditional set instruction.
+While the sensitive input \textsf{k} can affect the if-else branch, the compiler removes the branch with a conditional set instruction.
 The opposite situation is the same.
@@
 \end{figure}
+
+Figure~\ref{fig:chapter3:da} shows an example of the secret dependent data access.
+\textsf{T} is an array with 128 elements.
+The size of each element is one byte.
+So the total size of the array is 128 Bytes.
+Suppose an attacker can observe the memory access at the granularity of one cache lines (64 Bytes), then it is not possible to hold all the data inside the one cache line.
+An attacker can get some information of the value \textsf{secret} in Figure~\ref{fig:chapter3:da}(a) by observing the cache line access.
 

### 2021-04-02 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
-uint8_t T[128];
+uint8_t T[4];
 ...
@@
 
-Figure~\ref{fig:chapter3:da} shows an example of the secret dependent data access.
+Figure~\ref{fig:chapter3:da} shows an example of the secret-dependent data access.
 \textsf{T} is an array with 128 elements.
@@
 An attacker can get some information of the value \textsf{secret} in Figure~\ref{fig:chapter3:da}(a) by observing the cache line access.
+Figure~\ref{fig:chapter3:da}(b) shows a different example.
+In this example, only four different elements can be accessed in the array and the size of the array is four bytes.
+However, such a code may still be vulnerable to side-channel vulnerabilities depending on the based address of the array.
 

### 2021-04-02 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
-uint8_t T[4];
+uint8_t T[32];
 ...
@@
   uint32_t index = 0;
-  index = (index + secret) % 128;
-  uint8_t t = T[index % 4];
+  index = (index + secret) % 32;
+  uint8_t t = T[index];
   ...
@@
 mov    eax, [addr_secret]
-and    eax, 0x3
+and    eax, 0x3f
 movzx  eax, [addr_T + eax*1]
@@
 Figure~\ref{fig:chapter3:da}(b) shows a different example.
-In this example, only four different elements can be accessed in the array and the size of the array is four bytes.
+In this example, only four different elements can be accessed in the array and the size of the array is 32 bytes.
 However, such a code may still be vulnerable to side-channel vulnerabilities depending on the based address of the array.

### 2021-04-02 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 
-\section{Side-channel Leakages}
-This section discusses two types of side-channel leakage code patterns.
+\section{Limitations of Current Side-channel Leakage Detection Tools}
+In this section, we introduces two limitations of current side-channel leakage detection method.
+The first limitation is that some tools may have some false positives or false negatives.
+The second limitation is the current tools are not fast enough to analyze real world side-channel leakages.
+
+\subsection{Imprecision}
+In this dissertation, we study two types of side-channel leakage code patterns.
 The key intuition is that the target application shows different control flows or data flows when it processes different sensitive input data.
@@
 Unlike previous work, our tool works on the machine code, which can provide us more prevision than the previous tools.
-\subsection{Control Flow}
+\subsubsection{Control Flow}
 \begin{figure}[h]
@@
 \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
-int example1(uint8_t k, uint32_t m) {
+int example1(uint8_t k, uint32_t m) {  // m = 0
   uint32_t b = (k & m) >> 7;
@@
 \end{lstlisting}
-\end{minipage}\caption*{(a)}
+\end{minipage}\caption*{(a) A False Negative}
 
@@
 \end{lstlisting}
-\end{minipage}\caption*{(b)}
+\end{minipage}\caption*{(b) A False Positive}
 \caption{Secret-dependent Control-flow Transfers}\label{fig:chapter3:cf}
@@
 The sensitive input \textsf{k} can affect the program counter (the rip register), which is the root cause of the side-channel leakages.
+
 Figure~\ref{fig:chapter3:cf}(b) shows a different situation.
@@
 However, for some situations~\cite{Coppens:2009:PMT:1607723.1608124}, compilers (e.g., GCC) optimize the code too much (from a security view) and remove the unnecessary copy by reintroducing conditional moves.
-\subsection{Data Flow}
+\subsubsection{Data Flow}
 \begin{figure}[h]
@@
 \end{lstlisting}
-\end{minipage}\caption*{(a)}
+\end{minipage}\caption*{(a) A True Leakage}
 
@@
 \end{lstlisting}
-\end{minipage}\caption*{(b)}
+\end{minipage}\caption*{(b) A False Positive}
 \caption{Secret-dependent Data Accesses}\label{fig:chapter3:da}
@@
 Figure~\ref{fig:chapter3:da}(b) shows a different example.
-In this example, only four different elements can be accessed in the array and the size of the array is 32 bytes.
-However, such a code may still be vulnerable to side-channel vulnerabilities depending on the based address of the array.
+In this example, only 32 different elements can be accessed in the array and the size of the array is 32 bytes, which is smaller than the size of one cache line.
+Depending on the base address of the array, the array can be stored in one cache line or two consecutive cache lines.
+Therefore, such a code may still be vulnerable to side-channel vulnerabilities.
+However, existing tools (e.g., CacheD) use a concrete base address.
+Under the circumstance, those tools may miss such vulnerabilities.
 
-\section{Our Theoretical Frameworks}
+\subsection{Performance}
+
+\section{Method}
 \begin{figure}

### 2021-04-02 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \subsection{Performance}
+The second limitation of the current side-channel detection tool is the performance bottleneck, especially for those tools based on the symbolic analysis.
+For example, CaSym can only analyze small programs.
+CacheD perfroms better.
+However, it still can not handle large programs like RSA directly.
+It uses some domain knowledge to analyze only part of the program.
+The expensive cost comes from the symbolic execution.
+Symbolic execution can be used to explore all the possible paths, which is useful for many tasks.
+But it is significantly less likely for cache side channels bugs in crypto primitives.
+Cryptography primitives are more likely to have an even coverage of different paths (based on pseudo-random cipher states), and a branch-based side channel is vulnerable from the very first branch on secret data, making complex path conditions less often relevant.
 

### 2021-04-02 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 Cryptography primitives are more likely to have an even coverage of different paths (based on pseudo-random cipher states), and a branch-based side channel is vulnerable from the very first branch on secret data, making complex path conditions less often relevant.
+Therefore, we choose to analyze a trace instead of the whole path.
+Another bottleneck is that the IR.
+While the IR can significantly decrease the difficulty of the implementation, it also gives introduce an average of 10x of the overall overhead.
+Third, using SMT solving can be convenient because of its generality, and it is commonly used for its precision when checking branch feasibility in symbolic execution.
+But the decision problems that an SMT solver handles are typically at least NP-hard.
+On the other hand, we can use some methods to avoid the solver and find side-channel leakages in a more efficient way.
 
@@
 \end{figure}
+
+In the section, we give necessary definitions and notation for dealing with
+programs and side-channels.
+
+Shown in Figure~\ref{fig:side-channel-attack}. We assume a program ($\beta$) has $K$ as its sensitive input. $K$ should be 
+a finite set of keys. The program also takes known messages $M$ as its input. 
+During an AES encryption, for example, 
+$\beta$ is the encryption function. $K$ is the set of all possible AES keys, 
+and $M$ represents the set consisting of all plaintext messages to be encrypted. In a real execution, an adversary may have 
+some observations ($O$) of the program. Examples of those observations include 
+timing, CPU usages, and electromagnetic signals (EM). This paper only
+uses secret-dependent control flows and secret-dependent data 
+accesses as observations.
+
+With the above definition, we have the following mapping between $\beta$,
+$K$, $M$, and $O$:
+%\vspace*{-0pt}
+\begin{displaymath}
+    \beta(K, M) \rightarrow O
+\end{displaymath}
+
+We model a side-channel in the following way. An adversary does not have
+access to $K$, but he knows $\beta$, $M$, and $O$. For one execution of a
+deterministic program, once $k \in K$ and $m \in M$ are fixed, the observation
+($o \in O$) should also be determined. An attacker knows $\beta$, $o$,
+and $m$. The attacker wants to infer the value of $k$. We use $K^o$ to denote
+the set of possible $k$ values that produce the same observation: $K^o = \{ k \in K \, |\, \beta(k, m) \rightarrow o\}$
 

### 2021-04-02 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 
-Shown in Figure~\ref{fig:side-channel-attack}. We assume a program ($\beta$) has $K$ as its sensitive input. $K$ should be 
-a finite set of keys. The program also takes known messages $M$ as its input. 
+Shown in Figure~\ref{fig:side-channel-attack}.
+We assume a program ($\beta$) has $K$ as its sensitive input.
+The program also takes public information $M$ as its input.
 During an AES encryption, for example,
@@
 
-We now discuss how to model observations ($O$), which are the direct information
-that an adversary can get during the attack.
+We now discuss how to model observations ($O$), which are the direct information that an adversary can get during the attack.
 
@@
 We define a branch is secret-dependent if:
-$$\exists k_{i1}, k_{i2} \in K, \,f_i(\beta, k_{i1}, m) \neq f_i(\beta, k_{i2}, m)$$
+$$\exists k_{i1}, k_{i2} \in K , \,f_i(\beta, k_{i1}, m) \neq f_i(\beta, k_{i2}, m)$$
 

### 2021-04-02 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 ...
-int example3(uint8_t secret){
-  uint32_t index = 0;
-  index = (index + secret) % 128;
+int example3(uint8_t k, uint32_t m){
+  uint32_t index = m;
+  index = (index + k) % 128;
   uint8_t t = T[index];
@@
 lea    edx, [addr_T]
-mov    eax, [addr_secret]
+mov    eax, [addr_k]
+add    eax, [addr_m]
 and    eax, 0x7f
@@
 ...
-int example4(uint8_t secret){
-  uint32_t index = 0;
-  index = (index + secret) % 32;
+int example4(uint8_t k, uint32_t m){
+  uint32_t index = m;
+  index = (index + k) % 32;
   uint8_t t = T[index];
@@
 lea    edx, [addr_T]
-mov    eax, [addr_secret]
+mov    eax, [addr_k]
+add    eax, [addr_m]
 and    eax, 0x3f

### 2021-04-02 Chapter-4/Chapter-4.tex
add figures
Updates from Overleaf

@@
 
-\vspace{3pt}
 \textbf{Min Entropy.}
@@
  \begin{figure}[h!]
-    \vspace*{-5pt}
     \centering
@@
     \label{fig:password-checker}
-\vspace*{-5pt}
 \end{figure}
@@
     \centering
-    \includegraphics[width=.65\columnwidth]{./figures/RA.pdf}
-\vspace*{-6pt}
+    \includegraphics[width=.65\columnwidth]{./figures/chapter4/RA.pdf}
     \caption{The gap between the real attack and previous models}\label{fig:gap}
@@
 
-\subsection{Theoretical Analysis \textbf{(Solution to Challege C1)}}
+\subsection{Theoretical Analysis}
 Now we present our metric to quantify the amount of leaked information from
@@
 
-            %For example, if the program has $2$ input whose size is 
-            %one byte, the whole search space is a $256^2$ cube. If we want
-            %the sampling distance between each point equals to $d$, we need
-            %$256^2d$ points. If the program has $10$ byte input, we need
-            %$256^{10}d$ points if we still we want the sampling distance equals
-            %to $d$.
+            For example, if the program has $2$ input whose size is 
+            one byte, the whole search space is a $256^2$ cube. If we want
+            the sampling distance between each point equals to $d$, we need
+            $256^2d$ points. If the program has $10$ byte input, we need
+            $256^{10}d$ points if we still we want the sampling distance equals
+            to $d$.
 
@@
             get a tight bound. 
-            %On an extreme situation, if the constraint only
-            %has one unique satisfying solution, the simple Monte Carlo method
-            %cannot find the satisfying assignment even after sampling many
-            %points.
+            On an extreme situation, if the constraint only
+            has one unique satisfying solution, the simple Monte Carlo method
+            cannot find the satisfying assignment even after sampling many
+            points.
 \end{enumerate}
@@
 
-%% We apply the following
-%% algorithm~\ref{algo:max-inde} to get the Maximum Independent Partition of the
-%% $c_t(\addr{1},\addr{2},\ldots,\addr{n})$.
+We apply the following
+algorithm~\ref{algo:max-inde} to get the Maximum Independent Partition of the
+$c_t(\addr{1},\addr{2},\ldots,\addr{n})$.
+
+\IncMargin{1em}
+\begin{algorithm}[h]\small
+    \DontPrintSemicolon
+    \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
+    \Input{$c_t(\addr{1},\addr{2},\ldots,\addr{n}) = c_{\addr{1}} \land c_{\addr{2}} \land \ldots \land c_{\addr{m}}$}
+    \Output{The Maximum Independent Partition of $G = \{g_{1}, g_{2}  , \ldots,  g_{m} \}$ }
+    Insert $c_{\addr{1}}$ to $G$ as a new entry \;
+    \For{$i\leftarrow 2$ \KwTo $n$}
+    {
+        $S_{c_{\addr{i}}}$ $\leftarrow$ $\pi(c_{\addr{i}})$ \;
+        \For{$g_{i} \in G$}
+        {
+            $S_{g_j}$ $\leftarrow$ $\pi(g_{j})$ \;
+            $S$ $\leftarrow$ $S_{c_{\addr{i}}} \cap S_{g_j}$  \;
+            \If{$S \neq \emptyset$}
+            {
+                $g_{j} \leftarrow g_{i} \land g_{\addr{i}}$ \;
+                \textbf{continue} \;
+            }
+            Insert $c_{\addr{i}}$ to $G$ as a new entry \;
+        }
+    }
+    \caption{The Maximum Independent Partition}
+    \label{algo:max-inde}
+\end{algorithm}
+\DecMargin{1em}
 
@@
 significantly reduced by the previous step, this is still a \#P problem. 
-%For our
-%project, we apply the approximate counting instead of exact counting for two
-%reasons. First, we do not need to have a very precise result of the exact number
-%of total solutions since the information is defined with a logarithmic function.
-%We do not need to distinguish between constraints having $10^{10}$ or $10^{10} +
-%10$ solutions; they are very close to after taking logarithmic. Second, the
-%precise model counting approaches, like Davis-Putnam-Logemann-Loveland (DPLL)
-%search, have difficulty scaling up to large problem sizes.
+For our
+project, we apply the approximate counting instead of exact counting for two
+reasons. First, we do not need to have a very precise result of the exact number of total solutions since the information is defined with a logarithmic function.
+We do not need to distinguish between constraints having $10^{10}$ or $10^{10} 
+10$ solutions; they are very close to after taking logarithmic. Second, the
+precise model counting approaches, like Davis-Putnam-Logemann-Loveland (DPLL)
+search, have difficulty scaling up to large problem sizes.
 
@@
 
+\IncMargin{1em}
+\begin{algorithm}\small
+    \SetAlgoLined
+    \DontPrintSemicolon
+
+    \KwIn{{The constraint $g_{i}= c_{i_1} \land c_{i_2}
+                    \land \ldots \land c_{i_m}$}}
+    \KwOut{{The number of assignments that satisfy $g_{i}$ $|K_{g_{i}}|$}}
+
+    $n$: the number of sampling times \;
+    $S_{c_i}$: the set contains input variables for $c_{i}$ \;
+    $n_{s}$: the number of satisfying assignments \;
+    $N_{c_t}$: the set contains all solution for $c_t$ \;
+    $r$: times of reducing $g$\;
+    $k$: the input variable \;
+    $R$: a function that produces a random point from $S_{c_i}$\;
+    %$\#k$: the satisfying number of k \fixme{this number is not used syntactically} \;
+    %Initialization: \;
+    $r$ $\leftarrow$ $1$,
+    $n$ $\leftarrow$ $0$ \;
+    \For{$t$ $\leftarrow$ $1$ \KwTo $m$} {
+        $S_{c_t}$ $\leftarrow$ $\pi(c_t)$ \;
+        \If{$|S_{c_t}| = 1$}
+        {
+            $N_{c_t}$ $\leftarrow$ Compute all solutions of $c_i$ \;
+            $N_{c_t} = \{n_1, \ldots, n_m\},\ S_{c_t} = \{k\}  $ \;
+            $g_{i} = $ $g_i(k=n_1) \land \ldots \land g_i(k=n_m)$ \;
+            $r \leftarrow r+1$ \;
+
+        }
+    }
+    \While{$n \leq \frac{8p}{1-p}$} {
+        $S_{g_i}$ $\leftarrow$ $\pi(g_i)$ \;
+        $v \leftarrow R(S_{g_i})$ 
+        \If{$v$ satisfies $g_i$}
+        {
+           $n_s \leftarrow n_s + 1$
+        }
+        $n \leftarrow n +1,\ p = \frac{n_s}{n}$
+    }
+
+    $|K_{g_{i}}|$ $\leftarrow$ $n_s|K| / (n * r * range(k))$
+    \caption{Multiple Step Monte Carlo Sampling}
+\end{algorithm}
+\DecMargin{1em}
 %% the algorithm

### 2021-04-02 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 \label{MCreasons}
-%According to
-%Definition~\ref{def} introduced in \S\ref{sec:trace-qif},
-%the problem of quantifying the amount of leaked information can be reduced to
-%the problem of computing the number of items in $K^o$. However, we find that while
-%there are various propositional model counters (e.g., \#SAT), they are not
-%sufficient scalable for production cryptosystem analysis.
-%there is no open source modulo theories counter (\#SMT) available.
+According to
+Definition~\ref{def} introduced in \S\ref{sec:trace-qif},
+the problem of quantifying the amount of leaked information can be reduced to
+the problem of computing the number of items in $K^o$. However, we find that while
+there are various propositional model counters (e.g., \#SAT), they are not
+sufficient scalable for production cryptosystem analysis.
+there is no open source modulo theories counter (\#SMT) available.
 
-%One straightforward method approximating the number of solutions is based on Monte Carlo
-%sampling. However, the number of satisfying values could be exponentially small.
-%Consider the formula $f_i\equiv{k_1} = 1\land{k_2} = 2\land{k_3} = 3\land{k_4} =
-%4$, where $k_1$, $k_2$, $k_3$, and $k_4$ each represents one byte in the
-%original sensitive input buffer, there is only one satisfying solution of total
-%$2^{32}$ possible values, which requires exponentially many samples to get a
-%tight bound. Monte Carlo method also suffers from the curse of dimensionality.
-%For example, the length of an RSA private key can be as long as 4096 bits. If we
-%take each byte (8 bits) in the original buffer as one symbol, the formula can
-%have as many as 512 symbols.
+One straightforward method approximating the number of solutions is based on Monte Carlo
+sampling. However, the number of satisfying values could be exponentially small.
+Consider the formula $f_i\equiv{k_1} = 1\land{k_2} = 2\land{k_3} = 3\land{k_4} =
+4$, where $k_1$, $k_2$, $k_3$, and $k_4$ each represents one byte in the
+original sensitive input buffer, there is only one satisfying solution of total
+$2^{32}$ possible values, which requires exponentially many samples to get a
+tight bound. Monte Carlo method also suffers from the curse of dimensionality.
+For example, the length of an RSA private key can be as long as 4096 bits. If we
+take each byte (8 bits) in the original buffer as one symbol, the formula can
+have as many as 512 symbols.
 
@@
 %\textbf{Our Solution to Challenge C3:}
-%We adopt multiple-step Monte Carlo sampling methods to count the number of
-%possible inputs that satisfy the logic formula groups. The key idea is to split
-%those constraints into several small formulas and sample them independently.
-%We will introduce the method in the following subsection.
+We adopt multiple-step Monte Carlo sampling methods to count the number of
+possible inputs that satisfy the logic formula groups. The key idea is to split
+those constraints into several small formulas and sample them independently.
+We will introduce the method in the following subsection.
 
-%\subsection{Information Leakage Estimation}
+\subsection{Information Leakage Estimation}
 
@@
 \land \ldots \land c_{\addr{n}}$. 
-%%The problem of estimating the total leaked
-%%information can be reduced to the problem of counting the number of different
-%%solutions that satisfies the constraint
-%%$c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}})$. 
+The problem of estimating the total leaked
+information can be reduced to the problem of counting the number of different
+solutions that satisfies the constraint
+$c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}})$. 
 A simple method is to pick elements $k$ from $K$ and check if an
@@
             a given constraint.
-            %\item For each constraint $F(C_{{addr}_i})$, the satisfying assignments
-            %are close to each other, which means if we find one satisfying assignment, we 
-            %are more likely to find other satisfying assignments nearby than randomly
-            %pick one point in the whole searching space.
 
@@
 simulation will terminate.
+
+\section{Implementation}
+
+\tool{} consists of 16,729 lines of code in C++17 and Python. It has three
+components: an Intel Pin tool that collects the execution trace, the
+instruction-level symbolic execution engine, and the back-end that estimates
+the information leakage.
+
+\begin{table}[h!]
+    \centering
+    %    \resizebox{.8\columnwidth}{!}{
+    \caption{\tool{}' main components and sizes}\label{tbl:implementation}
+    \begin{tabular}{lr@{~}@{}l}
+        \hline
+        Component            & \multicolumn{2}{c}{Lines of Code (LOC)}             \\ \hline
+        Trace Logging        & 501 lines                               & of C++    \\
+        Symbolic Execution   & 14,963 lines                            & of C++    \\
+        Data Flow            & 451 lines                               & of C++    \\
+        Monte Carlo Sampling & 603 lines                               & of C++    \\
+        Others               & 211 lines                               & of Python \\ \hline
+        Total                & 16,729 lines                            &           \\\hline
+    \end{tabular}
+    %    }
+\end{table}
+
+Our current implementation supports most Intel 32-bit instructions that are essential to find address-based side-channel
+vulnerabilities, including bitwise operations, control transfer, data movement, and logic
+instructions. The tool uses the real values to update the registers and memory for instructions that the implementation does not support. 
+Therefore, the tool may miss some leakages but will not raise false positives.
+
+\section{Evaluation}
+
+\section{Discussion}
+While recent work found many side-channel vulnerabilities, 
+we note that many of them have not been patched by developers.
+Side-channels are ubiquitous in software and it would be difficult to fix all of them. 
+We need a tool that estimates the sensitivity of each vulnerability
+so software engineers can focus on
+``severe'' leakages. For example, \tool{} reports that 
+the modular exponentiation using square and multiply algorithms can
+leak more information than a key validation function.
+
+Software developers can use \tool{} to find severe vulnerabilities
+and reason about countermeasures.
+\tool{} estimates the amount of leaked information for each side-channel leakage
+in one execution trace. \tool{} is useful for software
+engineers to test programs and fix vulnerabilities.
+The design, which is more precise in reporting true leakages as compared with other static
+methods~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, obviously misses
+leakages on unexplored traces. The amount of leaked information also depends on the secret key.
+However, as the tool is intended for debugging and testing,
+we think it is a software engineer's responsibility to select the input key and trigger 
+the path in which they are interested. It is not a problem for crypto software 
+since virtually all keys follow similar computational paths.
+
+We use the amount of leaked information to represent the sensitivity level of 
+each side-channel vulnerability. Although imperfect, \tool{} produces a reasonable 
+measurement for each leak. For example, the simple modular exponentiation is 
+notoriously famous for multiple side-channel attacks~\cite{kocher1996timing}. 
+During the execution, a single leak point may execute multiple times
+and each time leak a different bit. In this case, \tool{} reports that the 
+vulnerability can leak the whole key. However, not every leak point inside a 
+loop is severe. If a site in the loop leaks the same bit from the 
+original key, and these leaks are not independent. \tool{} captures most 
+fine-grained information by modeling each leak during the execution as a 
+formula and the conjunction of the formulas to describe its total effect. 
+Some leakage sites (e.g., square and multiply) 
+can leak one particular bit of the original key, but some leakage sites leak one bit 
+from several bytes in the original key. \tool{} can capture the dependency among the leaks and
+reports more precise leakage information.
+
+\tool{} reaches full precision if the number of estimated leaked bits 
+equals to Definition~\ref{def}. 
+\tool{} may lose precision from the 
+memory model it uses in theory. However, we did not find false positives 
+caused by the imprecise memory model during our evaluation. 
+Sampling introduces imprecision but with a probabilistic guarantee. 
+However, during the evaluation, we find that \tool{} cannot estimate 
+the amount of leakage for some leakage sites in a reasonable time, 
+which means the number of $K^o$ is very small. According to Definition~\ref{def}, 
+it means the leakage is very severe. The sampling method in \S\ref{sec:scala} seems
+simple and may miss some leakages (e.g., chosen ciphertext attacks) in theory. 
+However, the evaluation result 
+shows \tool{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.

### 2021-04-02 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 
-With the above definitions, we can model an attacker's observation by a series of math
-formulas. For example, in Figure~\ref{fig:side-channel}, if an attacker observes
+With the above definitions, we can model an attacker's observation by a series of math formulas. For example, in Figure~\ref{fig:side-channel}, if an attacker observes
 the code executes the branch 1, we have $c_5: k_1 + k_2 < 4$ to describe an
@@
 \section{Discussion}
+
+In the section, we discuss the limitations, usages, and some future work. 
+%
+\tool{} works on native x86 execution traces. The design, which is very
+precise in terms of true leakages compared to other static source code
+method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also has 
+the common limitations of dynamic approaches. \tool{} may only cover part of the code.
+  % Each time we only get one single execution trace. Therefore,
+We may 
+neglect some side-channel vulnerabilities not covered by the traces analyzed.
+However, this is not a crucial problem for analyzing crypto libraries because crypto
+libraries are designed to have the same code coverage for various inputs. Our
+evaluation also confirms the above point. For symmetric encryptions, during our
+evaluation there is no secret-dependent control-flow transfers. RSA
+implementations have several secret-dependent control-flow transfers. 
+  %But after we manually check those leakages cites. We find
+Most of them are  %used for
+bound checks, which do not leak much information and have negligible effects
+on the whole code coverage as well.

### 2021-04-02 Chapter-3/Chapter-3.tex
update

@@
     \centering
-    \includegraphics[width=.35\columnwidth]{./figures/chapter3/attack.pdf}
+    \includegraphics[width=.3\columnwidth]{./figures/chapter3/attack.pdf}
     \caption{A side-channel attack}\label{fig:side-channel-attack}
@@
 
-In the section, we give necessary definitions and notation for dealing with
+In the section, we give necessary definitions and notations for dealing with
 programs and side-channels.
 
-Shown in Figure~\ref{fig:side-channel-attack}.
-We assume a program ($\beta$) has $K$ as its sensitive input.
-The program also takes public information $M$ as its input.
-During an AES encryption, for example,
-$\beta$ is the encryption function. $K$ is the set of all possible AES keys, 
-and $M$ represents the set consisting of all plaintext messages to be encrypted. In a real execution, an adversary may have 
-some observations ($O$) of the program. Examples of those observations include 
-timing, CPU usages, and electromagnetic signals (EM). This paper only
-uses secret-dependent control flows and secret-dependent data 
+Shown in Figure~\ref{fig:side-channel-attack}, a side-channel attack can be formulated into the below steps.
+A program ($\beta$) has $K$ as its sensitive input (e.g., the encryption key) and $M$ as its the public input (e.g., the plaintext).
+In a real execution, an adversary may have
+some observations ($O$) of the program. Examples of those observations include the
+timing, CPU usages, and electromagnetic signals (EM). In this dissertation, we 
+use secret-dependent control flows and secret-dependent data 
 accesses as observations.
@@
 $K$, $M$, and $O$:
-%\vspace*{-0pt}
 \begin{displaymath}
@@
 ($o \in O$) should also be determined. An attacker knows $\beta$, $o$,
-and $m$. The attacker wants to infer the value of $k$. We use $K^o$ to denote
-the set of possible $k$ values that produce the same observation: $K^o = \{ k \in K \, |\, \beta(k, m) \rightarrow o\}$
+and $m$. The attacker wants to infer the value of $k$. Moreover, we assume
+an attacker can change the public input ($m \in M$) while keeping the secret input $k$. 
+The threat model is similar to a chosen-plaintext attack.
+We now discuss how to model observations ($O$), 
+which are the direct information that an adversary can get during the attack.
 
-We now discuss how to model observations ($O$), which are the direct information that an adversary can get during the attack.
-
-During the execution, a program ($\beta$) have many temporary values ($t_i \in
+For one execution, a program ($\beta$) has many temporary values ($t_i \in
 T$). Once $\beta$ (program), $k$ (secret), and $m$ (message, public) are
 determined, $t_i$ is also fixed. Therefore, $ t_i = f_i(\beta, k, m)$, where $f_
-i$ is a function that maps between $t_i$ and ($\beta$, $k$, $m$).
-
-In the paper, we consider two code patterns that can be exploited by an attacker,
+i$ is a function that maps between $t_i$ and ($\beta$, $k$, $m$). In the paper, 
+we consider two code patterns that can be exploited by an attacker,
 \emph{secret-dependent control transfers} and \emph{secret-dependent data
@@
 We define a branch is secret-dependent if:
-$$\exists k_{i1}, k_{i2} \in K , \,f_i(\beta, k_{i1}, m) \neq f_i(\beta, k_{i2}, m)$$
+$$\exists k_{i1}, k_{i2} \in K, m \in M, \,f_i(\beta, k_{i1}, m) \neq f_i(\beta, k_{i2}, m)$$
 

### 2021-04-02 Chapter-3/Chapter-3.tex
update

@@
 \subsection{Secret-dependent Control Transfers}
-We think a control-flow is secret-dependent if different input sensitive keys
-($K$) can lead to different branch conditions. Therefore,
-We define a branch is secret-dependent if:
+A control-flow path is secret-dependent if different input-sensitive keys
+($K$) can lead to different branch conditions. 
+We define a branch to be secret-dependent if:
 $$\exists k_{i1}, k_{i2} \in K, m \in M, \,f_i(\beta, k_{i1}, m) \neq f_i(\beta, k_{i2}, m)$$
 
-An adversary can observe which branch the code executes, if the branch condition
-equals to $t_b$. We use the constraint $c_i : f_i(\beta, k, m) = t_b$ to model
+An adversary can observe which branch the code executes if the branch condition
+equals $t_b$. We use the constraint $c_i : f_i(\beta, k, m) = t_b$ to model
 the observation ($o$) on secret-dependent control-transfers.
@@
 We consider a data access is secret-dependent if:
-$$\exists k_{i1}, k_{i2} \in K, \,f_i(\beta, k_{i1}, m) >> L \neq f_i(\beta, k_{i2}, m) >> L$$
+$$\exists k_{i1}, k_{i2} \in K, m \in M,\,f_i(\beta, k_{i1}, m) >> L \neq f_i(\beta, k_{i2}, m) >> L$$
 

### 2021-04-02 Chapter-3/Chapter-3.tex
update

@@
 Besides, compiler optimizations can eliminate the IR-level branches like conditional moves and the converse could also happen.
-Moreover, translating the machine code into IRs can casue a significant overhead for the trace analysis, as we will discuss in the dissertation.
+Moreover, translating the machine code into IRs can cause a significant overhead for the trace analysis, as we will discuss in the dissertation.
 
@@
 equals $t_b$. We use the constraint $c_i : f_i(\beta, k, m) = t_b$ to model
-the observation ($o$) on secret-dependent control-transfers.
+the observation ($o$) on secret-dependent control-transfers. Note that in the
+above definition, $m$ is also a variable.
 

### 2021-04-02 Chapter-3/Chapter-3.tex
update

@@
 the observation ($o$) on secret-dependent control-transfers. Note that in the
-above definition, $m$ is also a variable.
+above definition, $m$ is also a variable. So it is possible for some $m \in M$,
+we can not find a pair of two different $k_{i1}$ and $k_{i2}$ to satisfy the above
+inequation. For example, in the example from Figure~\ref{fig:chapter3:cf}, if $m = 0$,
+the code will always execute the branch 2. However, the function \textsf{example1} still
+has a secret-dependent control-flow for some $m$, so we think the code has
+some side-channel leakages.
 
@@
 Similar to secret-dependent control-flow transfers, a data access operation is
-secret-dependent if different input sensitive keys ($K$) can lead to different
+secret-dependent if different input sensitive keys ($K$) cause access to different
 memory addresses. We use the model from CacheD~\cite{203878}. The low $L$ bits
-of the address are irrelevant in side-channels.
+of the address are generally unimportant in side-channels.
 
-We consider a data access is secret-dependent if:
+A data access is secret-dependent if:
+
 $$\exists k_{i1}, k_{i2} \in K, m \in M,\,f_i(\beta, k_{i1}, m) >> L \neq f_i(\beta, k_{i2}, m) >> L$$
@@
 
-With the above definitions, we can model an attacker's observation by a series of math formulas. For example, in Figure~\ref{fig:side-channel}, if an attacker observes
-the code executes the branch 1, we have $c_5: k_1 + k_2 < 4$ to describe an
-attacker's knowledge and $K^{o5} = \{k_1,\, k_2\,|\, (k_1 + k_2) < 4\}$. If an
-attacker observes the code executes the branch 2, we have $c_8: k_1 - k_2 > 0$
-and $K^{o8} = \{k_1,\, k_2\,|\, (k_1 - k_2) > 0\}$.
 \section{Scalability}

### 2021-04-03 Chapter-3/Chapter-3.tex
update

@@
 f_i(\beta, k, m) >> L = t_b >> L$ to model the observation on secret-dependent
-data accesses.
+data accesses. Let's take a look the examples in Figure~\ref{fig:chapter3:da}(a). 
+Suppose the base address of the array \textsf{T}
+is 10. We symbolize both the $k$ and $m$. The formula that represents the memory access at line 6 
+is $(m + k) \mod 128$. Therefore, we have the formula: $(m + k_1) \mod 128 >> 6  \neq (m + k_2) \mod 128 >> 6$.
+Here is one possible solution: $m = 0, k_1 = 0, k_2 = 127$. In fact, for any $m$, we can always find
+possible $k_1$ and $k_2$ that satisfy the above inequation. It is a true leakage. The leakage can 
+also be identified by previous tools like CacheD. Similarly, we can model the memory access at line 6
+with the formula:  $(m + k_1) \mod 32 >> 6  \neq (m + k_2) \mod 32 >> 6$.
 

### 2021-04-03 Chapter-3/Chapter-3.tex
update
Updates from Overleaf

@@
   uint32_t index = m;
-  index = (index + k) % 128;
+  index = index + k % 128;
   uint8_t t = T[index];
@@
 mov    eax, [addr_k]
+and    eax, 0x7f
 add    eax, [addr_m]
-and    eax, 0x7f
 movzx  eax, [addr_T + eax*1]
@@
   uint32_t index = m;
-  index = (index + k) % 32;
+  index = index + k % 32;
   uint8_t t = T[index];
@@
 mov    eax, [addr_k]
+and    eax, 0x3f
 add    eax, [addr_m]
-and    eax, 0x3f
 movzx  eax, [addr_T + eax*1]
@@
 
-\section{Method}
+\section{Method}\label{chapter3:method}
 \begin{figure}
@@
 data accesses. Let's take a look the examples in Figure~\ref{fig:chapter3:da}(a). 
-Suppose the base address of the array \textsf{T}
-is 10. We symbolize both the $k$ and $m$. The formula that represents the memory access at line 6 
-is $(m + k) \mod 128$. Therefore, we have the formula: $(m + k_1) \mod 128 >> 6  \neq (m + k_2) \mod 128 >> 6$.
-Here is one possible solution: $m = 0, k_1 = 0, k_2 = 127$. In fact, for any $m$, we can always find
-possible $k_1$ and $k_2$ that satisfy the above inequation. It is a true leakage. The leakage can 
-also be identified by previous tools like CacheD. Similarly, we can model the memory access at line 6
-with the formula:  $(m + k_1) \mod 32 >> 6  \neq (m + k_2) \mod 32 >> 6$.
+Suppose the base address of the array \textsf{T} is 10.
+We symbolize both the $k$ and $m$.
+The formula that represents the memory access at line 6 is $10 + m + (k \mod 128)$.
+Therefore, we have the formula: $(10 + m + (k_1 \mod 128)) >> 6  \neq (10 + m + (k_2 \mod 128)) >> 6$.
+Here is one possible solution: $m = 0, k_1 = 0, k_2 = 127$.
+In fact, for any $m$, we can always find possible $k_1$ and $k_2$ that satisfy the above inequation.
+It is a true leakage.
+The leakage can also be identified by previous tools like CacheD.
+Similarly, we can model the memory access at line 6 with the formula:  $10 + m + (k_1 \mod 32) >> 6  \neq 10 + m + (k_2 \mod 32) >> 6$.
+If $m = 0$, we can not find satisfiable $k_1$ and $k_2$ for the above inequation, which indicates that it will always access the same cache line at line 6.
+It is the conclusion from Cache.
+However, it is possible that for some $m \in M$, we can find such a pair of $k_1$ and $k_2$ ($m = 53, k_1 = 1, k_2 = 0$).
+If the actual public input is $0$, existing tools (e.g., CacheD) can miss such a vulnerability.
+On the other hand, our tool can identify the leakages precisely.
 
@@
 \subsection{Trace-oriented Symbolic Execution}
-While symbolic execution can capture fine-grained semantics of programs, it
-is also notorious for its unbearable performance cost. Previous trace-oriented
-symbolic execution based
-works~\cite{203878,Chattopadhyay:2017:QIL:3127041.3127044} all have large
-performance bottlenecks. As a result, those approaches either only apply to
-small-size programs~\cite{Chattopadhyay:2017:QIL:3127041.3127044} or apply some
-domain knowledge to simplify the analysis. 
-%Those tools interpret each
-%instruction and update memory cells and registers with formulas that
-%captured the semantics of the execution and search different input values that
-%can lead to different execution behaviors using constraint solver. 
-We implement the approach presented in \S\ref{sec:trace-qif} and model the side-channels as formulas. While the tool can finish analyzing some simple cases like AES, it can
-not handle complicated cases like RSA.
-We observe that finding side-channels using symbolic execution is different from
-traditional general symbolic execution and can be optimized to be as efficient
-as other methods with approaches below.
+Symbolic execution is notorious for its high performance cost. 
+Previous trace-oriented symbolic execution
+work~\cite{203878,Chattopadhyay:2017:QIL:3127041.3127044} has serious
+performance bottlenecks. As a result, these approaches either apply only to
+small programs~\cite{Chattopadhyay:2017:QIL:3127041.3127044} or require
+domain knowledge~\cite{Wang:2007:NCD:1250662.1250723} to simplify the analysis. 
+Those tools interpret each
+instruction and update memory cells and registers with formulas that
+captured the semantics of the execution and search different input values that
+can lead to different execution behaviors using constraint solver. 
+We implement the approach presented in \S\ref{chapter3:method} and model the side-channels as formulas.
+While the tools can analyze some simple cases such as AES, it cannot handle complicated examples such as RSA.
+We observe that finding side-channels using symbolic execution differs from
+traditional symbolic execution, and it can be optimized to be as efficient
+as other methods.
 
 \subsection{Interpret Instructions Symbolically}
-Existing binary analysis tools~\cite{shoshitaishvili2016state,
-10.1007/978-3-642-22110-1_37} usually translate machine instructions into
-intermediate languages (IR) to simplify analysis. 
-The reason is that the number of machine instructions is
-enormous, and the semantics of each instruction is complex. Intel Developer
-Manual~\cite{intelsys} introduces more than 1000 different x86 instructions. 
-IR typically has fewer instructions compared to the original machine ISA\@.
-However, the IR layer, which predigest the implementation
-and reduce the workload of those tools, is not suitable for side-channels 
-analysis. Memory-based side-channels are very low issues. So, in general,
-IR-based or source code side-channels analyses are not accurate enough.
-In many cases, compilers can use conditional moves or bitwise operations to eliminate
+Existing binary analysis \cready{tools}{frameworks}~\cite{shoshitaishvili2016state,
+10.1007/978-3-642-22110-1_37, song2008bitblaze} translate machine instructions into
+intermediate languages (IR) to simplify analysis since
+the variety of machine instructions is
+enormous, and their semantics is complex. The Intel Developer
+Manual~\cite{intelsys} documents more than 1000 different x86 instructions. 
+Unfortunately, the IR layer, which
+reduces the workload of these tools, is not suitable for side-channels 
+analysis because
+IR-based or source code side-channels analyses do not represent the executed instructions accurate enough to analyze fully their control and memory accesses.
+For example, a compiler may use conditional moves or bitwise operations to eliminate
 branches. Also, as some IRs are not a superset or a subset of ISA, 
@@
 
-Moreover, the IR design introduces significant overhead~\cite{217563}.
-Transferring machine instructions into IR is time-consuming. For example,
+Moreover, the IR causes significant overhead~\cite{217563}.
+Translating machine instructions into IR is time-consuming. For example,
 REIL IR~\cite{dullien2009reil}, adopted in CacheS~\cite{236338}, has multiple
@@
 Also, IR increases the total number of instructions. For example, x86
-instruction \textit{test eax, eax} transfers into 18 REIL IR instructions. If we
-assume the time of symbolically executing grows as the number of instructions increase, the
-design of adopting IR layers can introduce large overhead.
+instruction \textit{test eax, eax} transfers into 18 REIL IR instructions.
 
-\vspace*{2pt}
-\textbf{Our Solution to Challenge C2:}
-We adopt the approach from QSYM~\cite{217563} and implement the symbolic execution
-directly on the top of x86 instructions. Table~\ref{scala:ir} shows that
-eliminating the IR layer can reduce the number of instructions executed during
-the analysis.
+\textbf{Our Solution:}
+We abandoned IR and expended the effort to implement 
+symbolic execution directly on x86 instructions. 
+Table~\ref{scala:ir} shows that eliminating the IR reduces the number 
+of instructions examined during analysis. Previous works~\cite{217563} also 
+adopted a similar approach to speed up fuzzing. Our implementation differs
+from that work in two aspects: 1) We use complete constraints. 2) We run the
+symbolic execution on one execution path each time. Our approach is approximately 30 times faster than using an IR (transferring ISA into IR and
+symbolically executing it).
 
@@
 
-Existing approach relies on satisfiability modulo theories (SMT) solvers (e.g,
-Z3~\cite{DeMoura:2008:ZES:1792734.1792766}) to find satisfying $k_1$ and $k_2$.
-We argue that while it is a universal approach to solving constraints with SMT
-solvers, for constraints with the above formats, using custom heuristics and
-testing is much more efficient in practice. Constraint solving is a decision
-problem expressed in logic formulas. SMT solvers transfer the inputted SMT
-formula into the boolean conjunctive normal form (CNF) and feed it into the
-internal boolean satisfiability problem (SAT) solver. The translation process,
-called ``bit blasting'', is time-consuming. Also, as the SAT problem is a
-well-known NP-complete problem, it is also hard to deal when it comes to
-realistic uses with huge formulas. Despite the rapid development of SMT solvers
-in recent years, constraint solving remains one of the obstacles to achieve the
-scalability for real-world crypto systems.
+Existing approaches rely on satisfiability modulo theories (SMT) solvers 
+(e.g., Z3~\cite{DeMoura:2008:ZES:1792734.1792766}) to find satisfying assignments to
+$k_1$ and $k_2$.
+While this is a universal approach to solving constraints, 
+for constraints of this form, using custom 
+heuristics and testing is much more efficient in practice. Constraint 
+solving is a decision problem expressed in logic formulas. SMT solvers 
+transfer the SMT formula into the boolean conjunctive normal 
+form (CNF) and feed it into the internal boolean satisfiability 
+problem (SAT) solver. The translation process, called ``bit blasting'', 
+is time-consuming. Also, as the SAT problem is a well-known NP-complete 
+problem, it is hard to deal when it comes to
+practical uses with huge formulas. Despite the rapid improvement 
+in SMT solvers in recent years, constraint solving remains one of 
+the obstacles to scaling the analysis of real-world crypto-systems.
 
-\vspace*{2pt}
-\textbf{Our Solution to Challenge C3:}
+\textbf{Our Solution:}
 Instead of feeding the formula $f_a(k_1) \neq f_a(k_2)$ into a SMT solver, we
-just randomly pick up $k_1, k_2 \in K$ and test them if they can satisfy the
+randomly pick $k_1, k_2 \in K$ and test them if they satisfy the
 formula. Our solution is based on the following intuition. For most combination
-of $(k_{1}, k_{2} )$, the formula $f_a(k_1) \neq f_a(k_2)$ holds. As long as
+of $(k_{1}, k_{2} )$, $f_a(k_1) \neq f_a(k_2)$. As long as
 $f_a$ is not a constant function, such $k_1, k_2$ must exist. For example,
@@
 test with different input combination with 100 times, we have $1 -
-(1-0.05)^{100} = 99.6\%$ chance find such $k_1, k_2$. Such random algorithms
-work well for our problem.
+(1-0.05)^{100} = 99.6\%$ chance find such $k_1, k_2$. This type of random algorithm
+works well for our problem.
 
@@
 libraries are designed to have the same code coverage for various inputs. Our
-evaluation also confirms the above point. For symmetric encryptions, during our
+evaluation also confirms the above point. For symmetric encryption, during our
 evaluation there is no secret-dependent control-flow transfers. RSA

### 2021-04-03 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \subsection{Interpret Instructions Symbolically}
-Existing binary analysis \cready{tools}{frameworks}~\cite{shoshitaishvili2016state,
+Existing binary analysis frameworks~\cite{shoshitaishvili2016state,
 10.1007/978-3-642-22110-1_37, song2008bitblaze} translate machine instructions into
@@
 \section{Evaluation}
+We evaluate our method on real-world crypto libraries, which include  OpenSSL, mbedTLS, Libgcrypt and Monocypher\@.
+OpenSSL is the most commonly used crypto libraries in today's software.
+mbedTLS\@ (previous known as PolarSSL) is designed to be easy to understand and fit on embedded devices.
+We also evaluate Monocypher, a new cryptographic library that resists to most side-channel attacks.
+Monocypher is designed to have no secret dependent indices and secret dependent branches. Therefore, Monocypher should be secure under our threat model.
+
+Moreover, for some crypto library, we evaluate more than one versions. After that, we compare the evaluation results with the version history to track developers' patches of those leakages.  
+\begin{itemize}
+\item OpenSSL: 0.9.7, 1.0.2f, 1.0.2k, 1.1.0f, 1.1.1, 1.1.1g
+\item MbedTLS: 2.5, 2.15
+\item Libgcrypt: 1.8.5
+\item Monocyper: 3.0
+\end{itemize}
+
+We mark variables and buffers that store a secret.
+For DES and AES, we mark symmetric keys as secrets. 
+For RSA, we mark private keys as secrets. For ECDSA, 
+we mark nonces and private keys as secrets.
+
+\subsection{Evaluation Result Overview}
 

### 2021-04-03 Chapter-3/Chapter-3.tex
update

@@
 \subsection{Evaluation Result Overview}
+\begin{table*}[]
+  \centering\small\footnotesize
+  \caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks), 
+      Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF),
+      The number of instructions\,(\# Instructions), Symbolic Execution\,(SE) and Monte Carlo\,(MC) time.
+  }\label{table:over_result}
+  \newlength{\x}
+  \newlength{\y}
+  \settowidth{\x}{~~}
+  \settowidth{\y}{m}
+  \addtolength{\x}{-1\y}
+  \newcommand{\foo}{\mbox{\hspace*{\the\x}}}
+%    \resizebox{1.9\columnwidth}{!}{
+  \begin{threeparttable}
+  \begin{tabular}{l@{}r@{~~}rrr@{~~}rr}
+      \hline
+      \textbf{Name}   & \textbf{\# Leaks} & \textbf{\# CF}         & \textbf{\# DF}
+                         & \textbf{\# Instructions}    & \textbf{SE} & \textbf{MC}                                                    \\\hline
+                                               &                        &                     &                      &              & ms                     \\
+      AES\tnote{1}               & 68                     & 0                   & 68                   & 39,855        & 512     & 1,052         \\
+      AES\tnote{2}                & 68                     & 0                   & 68                   & 39,855       & 520    & 1,057         \\
+      AES\tnote{4}                & 75                     & 0                   & 75                   & 1,704        & 231    & 9,199        \\
+      AES\tnote{5}                & 88                     & 0                   & 88                   & 1,350        & 36      & 1,924         \\
+      AES\tnote{6}                & 88                     & 0                   & 88                   & 1,350        & 35      & 1,961        \\
+      AES\tnote{7}                & 88                     & 0                   & 88                   & 1,420        & 36     & 2,161        \\
+      AES\tnote{8}                & 88                     & 0                   & 88                   & 1,586        & 43      & 1,631        \\
+      DES\tnote{1}                & 15                     & 0                   & 15                   & 4,596        & 58      & 162          \\
+      DES\tnote{2}                & 15                     & 0                   & 15                   & 4,596        & 57      & 162           \\
+      DES\tnote{4}                & 6                      & 0                   & 6                    & 2,976         & 163    & 4,677         \\
+      DES\tnote{5}                & 8                      & 0                   & 8                    & 2,593         & 166    & 6,509        \\
+      DES\tnote{6}                & 8                      & 0                   & 8                    & 2,593        & 165    & 5,975        \\
+      DES\tnote{7}                & 8                      & 0                   & 8                    & 4,260         & 182    & 5,292        \\
+      DES\tnote{8}                & 6                      & 0                   & 6                    & 8,272         & 229     & 5,152      \\
+                         &                        &                     &                      &                  & seconds                  \\
+      Chacha20\tnote{3}           & 0                      & 0                   & 0                    & 149,353        & 2     & 0             \\  
+      Poly1305\tnote{3}           & 0                      & 0                   & 0                    & 1,213,937      & 15    & 0             \\
+      Argon2i\tnote{3}            & 0                      & 0                   & 0                    & 4,595,142       & 37    & 0             \\
+      Ed25519\tnote{3}            & 0                      & 0                   & 0                    & 5,713,619       & 271   & 0            \\
+      ECDSA\tnote{1}              & 6                      &    6                & 0                    &  4,214,946     &  48   &   31       \\ 
+      ECDSA\tnote{2}              &   4                   &   4                 & 0                    &  4,192,558    & 102   & 1639          \\   
+      ECDSA\tnote{5}              &  5                    & 4                   & 1                    &  8,248,322       & 101     & 62           \\   
+      ECDSA\tnote{6}              &  5                    & 4                   & 1                    &  8,263,599      & 100     & 58            \\   
+      ECDSA\tnote{7}              &  5                    & 4                   & 1                    &  6,100,465       & 76      & 42                  \\  
+      ECDSA\tnote{8}              & 0                      &  0                   &    0               &  10,244,076       &  121     & 0                  \\  
+      ECDSA\tnote{9}              & 0                      &  0                   &  0                 &  9,266,191          & 102     & 59        \\
+
+                         &                        &                     &                      &                 & minutes            \\
+      RSA\tnote{1}                & 6                       & 6                   & 0                    & 22,109,246    & 39     & 41           \\
+      RSA\tnote{2}                & 12                      & 12                  & 0                    & 24,484,441    & 44     & 251           \\
+      RSA\tnote{4}                & 107                    & 105                 & 2                    & 17,002,523   & 23      & 428           \\
+      RSA\tnote{5}                & 38                     & 27                  & 11                   & 14,468,307   & 29     & 436          \\
+      RSA\tnote{6}                & 36                     & 27                  & 9                    & 15,285,210   & 40     & 714          \\
+      RSA\tnote{7}                & 31                     & 22                  & 9                    & 16,390,750   & 34      & 490         \\
+      RSA\tnote{8}                & 4                      &  4                  & 0                    & 18,207,016   & 8      & 53          \\
+      RSA\tnote{9}                & 8                      &  8                  & 0                    & 18,536,796    & 5      & 780         \\
+      RSA\tnote{10} & 11& 9& 2& 9,527,231& 2 &38\\
+      RSA\tnote{11} & 14& 14& 0& 10,513,606& 14 &503 \\
+      RSA\tnote{12}               & 8                      &  8                  & 0                    & 27,407,986    & 113    & 6560       \\
+
+      Total              & 904                    & 241                 & 663                & 167,141,947      & 341m  & 10,232m     \\\hline
+  \end{tabular}
+\end{threeparttable}
+\begin{tablenotes}
+  \scriptsize
+
+  \item[1] mbedTLS\,2.5  ~~~~\item[2] mbedTLS\,2.15 ~\item[3] Monocypher\,3.0 \\
+  \item[4] OpenSSL\,0.9.7  ~~\item[5] OpenSSL\,1.0.2f  \item[6] OpenSSL\,1.0.2k \\
+  \item[7] OpenSSL\,1.1.0f ~\item[8] OpenSSL\,1.1.1 ~\item[9] OpenSSL\,1.1.1g \\
+  \item[10] Libgcrypt\,1.6.1 \item[11] Libgcrypt\,1.7.3 \item[12] Libgcrypt\,1.8.5\\
+\end{tablenotes}
+\end{table*}
 

### 2021-04-03 Chapter-3/Chapter-3.tex
update

--- 2021-04-03 Chapter-3/Chapter-3.tex
@@
 \subsection{Evaluation Result Overview}
+\begin{table*}[]
+  \centering\small\footnotesize
+  \caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks), 
+      Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF),
+      The number of instructions\,(\# Instructions), Symbolic Execution\,(SE) and Monte Carlo\,(MC) time.
+  }\label{table:over_result}
+  \newlength{\x}
+  \newlength{\y}
+  \settowidth{\x}{~~}
+  \settowidth{\y}{m}
+  \addtolength{\x}{-1\y}
+  \newcommand{\foo}{\mbox{\hspace*{\the\x}}}
+  \begin{tabular}{lrrrrr}
+      \hline
+      \textbf{Name}   & \textbf{\# Leaks} & \textbf{\# CF}         & \textbf{\# DF}
+                         & \textbf{\# Instructions}    & \textbf{Time}     \\\hline
+                                               &                        &                     &                      &              & ms                     \\\cline{6-6}
+      AES\tnote{1}             & 68                     & 0                   & 68                   & 39,855        & 512     \\
+      AES\tnote{2}                & 68                     & 0                   & 68                   & 39,855       & 520         \\
+      AES\tnote{4}                & 75                     & 0                   & 75                   & 1,704        & 231       \\
+      AES\tnote{5}                & 88                     & 0                   & 88                   & 1,350        & 36     \\
+      AES\tnote{6}                & 88                     & 0                   & 88                   & 1,350        & 35   \\
+      AES\tnote{7}                & 88                     & 0                   & 88                   & 1,420        & 36    \\
+      AES\tnote{8}                & 88                     & 0                   & 88                   & 1,586        & 43      \\
+      DES\tnote{1}                & 15                     & 0                   & 15                   & 4,596        & 58     \\
+      DES\tnote{2}                & 15                     & 0                   & 15                   & 4,596        & 57      \\
+      DES\tnote{4}                & 6                      & 0                   & 6                    & 2,976         & 163    \\
+      DES\tnote{5}                & 8                      & 0                   & 8                    & 2,593         & 166     \\
+      DES\tnote{6}                & 8                      & 0                   & 8                    & 2,593        & 165     \\
+      DES\tnote{7}                & 8                      & 0                   & 8                    & 4,260         & 182     \\
+      DES\tnote{8}                & 6                      & 0                   & 6                    & 8,272         & 229     \\
+                         &                        &                     &                      &                  & seconds                  \\\cline{6-6}
+      Chacha20\tnote{3}           & 0                      & 0                   & 0                    & 149,353        & 2         \\  
+      Poly1305\tnote{3}           & 0                      & 0                   & 0                    & 1,213,937      & 15     \\
+      Argon2i\tnote{3}            & 0                      & 0                   & 0                    & 4,595,142       & 37    \\
+      Ed25519\tnote{3}            & 0                      & 0                   & 0                    & 5,713,619       & 271     \\
+      ECDSA\tnote{1}              & 6                      &    6                & 0                    &  4,214,946     &  48    \\ 
+      ECDSA\tnote{2}              &   4                   &   4                 & 0                    &  4,192,558    & 102        \\   
+      ECDSA\tnote{5}              &  5                    & 4                   & 1                    &  8,248,322       & 101     \\   
+      ECDSA\tnote{6}              &  5                    & 4                   & 1                    &  8,263,599      & 100      \\   
+      ECDSA\tnote{7}              &  5                    & 4                   & 1                    &  6,100,465       & 76     \\  
+      ECDSA\tnote{8}              & 0                      &  0                   &    0               &  10,244,076       &  121      \\  
+      ECDSA\tnote{9}              & 0                      &  0                   &  0                 &  9,266,191          & 102    \\
+
+                         &                        &                     &                      &                 & minutes            \\\cline{6-6}
+      RSA\tnote{1}                & 6                       & 6                   & 0                    & 22,109,246    & 39      \\
+      RSA\tnote{2}                & 12                      & 12                  & 0                    & 24,484,441    & 44        \\
+      RSA\tnote{4}                & 107                    & 105                 & 2                    & 17,002,523   & 23  \\
+      RSA\tnote{5}                & 38                     & 27                  & 11                   & 14,468,307   & 29    \\
+      RSA\tnote{6}                & 36                     & 27                  & 9                    & 15,285,210   & 40      \\
+      RSA\tnote{7}                & 31                     & 22                  & 9                    & 16,390,750   & 34      \\
+      RSA\tnote{8}                & 4                      &  4                  & 0                    & 18,207,016   & 8         \\
+      RSA\tnote{9}                & 8                      &  8                  & 0                    & 18,536,796    & 5       \\
+      RSA\tnote{10} & 11& 9& 2& 9,527,231& 2 \\
+      RSA\tnote{11} & 14& 14& 0& 10,513,606& 14  \\
+      RSA\tnote{12}               & 8                      &  8                  & 0                    & 27,407,986    & 113    \\
+
+      Total              & 904                    & 241                 & 663                & 167,141,947      & 341m  \\\hline
+  \end{tabular}
+\end{table*}
 

### 2021-04-03 Chapter-3/Chapter-3.tex
update

--- 2021-04-03 Chapter-3/Chapter-3.tex
@@
 \subsection{Evaluation Result Overview}
+\begin{table*}[]
+  \centering\small\footnotesize
+  \caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks), 
+      Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF),
+      The number of instructions\,(\# Instructions), Symbolic Execution\,(SE) and Monte Carlo\,(MC) time.
+  }\label{table:over_result}
+  \newlength{\x}
+  \newlength{\y}
+  \settowidth{\x}{~~}
+  \settowidth{\y}{m}
+  \addtolength{\x}{-1\y}
+  \newcommand{\foo}{\mbox{\hspace*{\the\x}}}
+  \begin{tabular}{lrrrrrr}
+      \hline
+      \textbf{Algorithm} & \textbf{Implementation}  & \textbf{\# Leaks} & \textbf{\# CF}         & \textbf{\# DF}
+                         & \textbf{\# Instructions}    & \textbf{Time}     \\\hline
+                                               &                        &                     &                      &              & ms                     \\\cline{6-6}
+      AES &             & 68                     & 0                   & 68                   & 39,855        & 512     \\
+      AES &                & 68                     & 0                   & 68                   & 39,855       & 520         \\
+      AES &                & 75                     & 0                   & 75                   & 1,704        & 231       \\
+      AES &                & 88                     & 0                   & 88                   & 1,350        & 36     \\
+      AES&           & 88                     & 0                   & 88                   & 1,350        & 35   \\
+      AES &         & 88                     & 0                   & 88                   & 1,420        & 36    \\
+      AES &        & 88                     & 0                   & 88                   & 1,586        & 43      \\
+      DES &         & 15                     & 0                   & 15                   & 4,596        & 58     \\
+      DES &             & 15                     & 0                   & 15                   & 4,596        & 57      \\
+      DES &         & 6                      & 0                   & 6                    & 2,976         & 163    \\
+      DES &         & 8                      & 0                   & 8                    & 2,593         & 166     \\
+      DES &           & 8                      & 0                   & 8                    & 2,593        & 165     \\
+      DES &            & 8                      & 0                   & 8                    & 4,260         & 182     \\
+      DES &       & 6                      & 0                   & 6                    & 8,272         & 229     \\
+                         &    &                    &                     &                      &                  & seconds                  \\\cline{6-6}
+      Chacha20 &           & 0                      & 0                   & 0                    & 149,353        & 2         \\  
+      Poly1305 &          & 0                      & 0                   & 0                    & 1,213,937      & 15     \\
+      Argon2i &          & 0                      & 0                   & 0                    & 4,595,142       & 37    \\
+      Ed25519 &           & 0                      & 0                   & 0                    & 5,713,619       & 271     \\
+      ECDSA &             & 6                      &    6                & 0                    &  4,214,946     &  48    \\ 
+      ECDSA &            &   4                   &   4                 & 0                    &  4,192,558    & 102        \\   
+      ECDSA &          &  5                    & 4                   & 1                    &  8,248,322       & 101     \\   
+      ECDSA &           &  5                    & 4                   & 1                    &  8,263,599      & 100      \\   
+      ECDSA &        &  5                    & 4                   & 1                    &  6,100,465       & 76     \\  
+      ECDSA &           & 0                      &  0                   &    0               &  10,244,076       &  121      \\  
+      ECDSA &          & 0           &  0                   &  0                 &  9,266,191          & 102    \\
+
+                         &                        &                     &                      &                 & minutes            \\\cline{6-6}
+      RSA &           & 6                       & 6                   & 0                    & 22,109,246    & 39      \\
+      RSA &            & 12                      & 12                  & 0                    & 24,484,441    & 44        \\
+      RSA &           & 107                    & 105                 & 2                    & 17,002,523   & 23  \\
+      RSA &           & 38                     & 27                  & 11                   & 14,468,307   & 29    \\
+      RSA &           & 36                     & 27                  & 9                    & 15,285,210   & 40      \\
+      RSA &          & 31                     & 22                  & 9                    & 16,390,750   & 34      \\
+      RSA &         & 4                      &  4                  & 0                    & 18,207,016   & 8         \\
+      RSA &            & 8                      &  8                  & 0                    & 18,536,796    & 5       \\
+      RSA & & 11& 9& 2& 9,527,231& 2 \\
+      RSA & & 14& 14& 0& 10,513,606& 14  \\
+      RSA &        & 8                      &  8                  & 0                    & 27,407,986    & 113    \\
+
+      Total              & 904                    & 241                 & 663                & 167,141,947      & 341m  \\\hline
+  \end{tabular}
+\end{table*}
 

### 2021-04-03 Chapter-3/Chapter-3.tex
update

@@
   \newcommand{\foo}{\mbox{\hspace*{\the\x}}}
-  \begin{tabular}{lrrrrrr}
+  \begin{tabular}{llrrrrr}
       \hline
@@
                          & \textbf{\# Instructions}    & \textbf{Time}     \\\hline
-                                               &                        &                     &                      &              & ms                     \\\cline{6-6}
-      AES &             & 68                     & 0                   & 68                   & 39,855        & 512     \\
-      AES &                & 68                     & 0                   & 68                   & 39,855       & 520         \\
-      AES &                & 75                     & 0                   & 75                   & 1,704        & 231       \\
-      AES &                & 88                     & 0                   & 88                   & 1,350        & 36     \\
-      AES&           & 88                     & 0                   & 88                   & 1,350        & 35   \\
-      AES &         & 88                     & 0                   & 88                   & 1,420        & 36    \\
-      AES &        & 88                     & 0                   & 88                   & 1,586        & 43      \\
+                                               &                        &                     &                      &              & ms                     \\\cline{7-7}
+      AES &  mbedTLS 2.5   & 68                     & 0                   & 68                   & 39,855        & 512     \\
+      AES &  mbedTLS 2.15   & 68                     & 0                   & 68                   & 39,855       & 520         \\
+      AES &  OpenSSL 0.9.7        & 75                     & 0                   & 75                   & 1,704        & 231       \\
+      AES &  OpenSSL 1.0.2f       & 88                     & 0                   & 88                   & 1,350        & 36     \\
+      AES&   OpenSSL 1.0.2k       & 88                     & 0                   & 88                   & 1,350        & 35   \\
+      AES &  OpenSSL 1.1.0f     & 88                     & 0                   & 88                   & 1,420        & 36    \\
+      AES & OpenSSL 1.1.1      & 88                     & 0                   & 88                   & 1,586        & 43      \\
       DES &         & 15                     & 0                   & 15                   & 4,596        & 58     \\
@@
       DES &       & 6                      & 0                   & 6                    & 8,272         & 229     \\
-                         &    &                    &                     &                      &                  & seconds                  \\\cline{6-6}
+                         &    &                    &                     &                      &                  & seconds                  \\\cline{7-7}
       Chacha20 &           & 0                      & 0                   & 0                    & 149,353        & 2         \\  
@@
 
-                         &                        &                     &                      &                 & minutes            \\\cline{6-6}
+                         &                        &                     &                      &                 & minutes            \\\cline{7-7}
       RSA &           & 6                       & 6                   & 0                    & 22,109,246    & 39      \\

### 2021-04-04 Chapter-3/Chapter-3.tex
update

@@
       AES & OpenSSL 1.1.1      & 88          & 0                   & 88                   & 1,586        & 43      \\
-      DES &         & 15                     & 0                   & 15                   & 4,596        & 58     \\
-      DES &             & 15                     & 0                   & 15                   & 4,596        & 57      \\
-      DES &         & 6                      & 0                   & 6                    & 2,976         & 163    \\
-      DES &         & 8                      & 0                   & 8                    & 2,593         & 166     \\
-      DES &           & 8                      & 0                   & 8                    & 2,593        & 165     \\
-      DES &            & 8                      & 0                   & 8                    & 4,260         & 182     \\
-      DES &       & 6                      & 0                   & 6                    & 8,272         & 229     \\
+      DES &  mbedTLS 2.5     & 15                     & 0                   & 15                   & 4,596        & 58     \\
+      DES &  mbedTLS 2.15           & 15                     & 0                   & 15                   & 4,596        & 57      \\
+      DES &  OpenSSL 0.9.7       & 6                      & 0                   & 6                    & 2,976         & 163    \\
+      DES &  OpenSSL 1.0.2f     & 8                      & 0                   & 8                    & 2,593         & 166     \\
+      DES &  OpenSSL 1.0.2k     & 8                      & 0                   & 8                    & 2,593        & 165     \\
+      DES &  OpenSSL 1.1.0f      & 8                      & 0                   & 8                    & 4,260         & 182     \\
+      DES &   OpenSSL 1.1.1    & 6                      & 0                   & 6                    & 8,272         & 229     \\
                          &    &                    &                     &                      &                  & seconds                  \\\cline{7-7}
-      Chacha20 &           & 0                      & 0                   & 0                    & 149,353        & 2         \\  
-      Poly1305 &          & 0                      & 0                   & 0                    & 1,213,937      & 15     \\
-      Argon2i &          & 0                      & 0                   & 0                    & 4,595,142       & 37    \\
-      Ed25519 &           & 0                      & 0                   & 0                    & 5,713,619       & 271     \\
-      ECDSA &             & 6                      &    6                & 0                    &  4,214,946     &  48    \\ 
-      ECDSA &            &   4                   &   4                 & 0                    &  4,192,558    & 102        \\   
-      ECDSA &          &  5                    & 4                   & 1                    &  8,248,322       & 101     \\   
-      ECDSA &           &  5                    & 4                   & 1                    &  8,263,599      & 100      \\   
-      ECDSA &        &  5                    & 4                   & 1                    &  6,100,465       & 76     \\  
-      ECDSA &           & 0                      &  0                   &    0               &  10,244,076       &  121      \\  
-      ECDSA &          & 0           &  0                   &  0                 &  9,266,191          & 102    \\
+      Chacha20 &  Monocypher 3.0    & 0          & 0                   & 0                    & 149,353        & 2         \\  
+      Poly1305 &  Monocypher 3.0    & 0          & 0                   & 0                    & 1,213,937      & 15     \\
+      Argon2i &   Monocypher 3.0    & 0         & 0                   & 0                    & 4,595,142       & 37    \\
+      Ed25519 &   Monocypher 3.0    & 0       & 0                   & 0                    & 5,713,619       & 271     \\
+      ECDSA &   mbedTLS 2.5   & 6       &    6                & 0                    &  4,214,946     &  48    \\ 
+      ECDSA &   mbedTLS 2.15   &   4                   &   4                 & 0                    &  4,192,558    & 102        \\   
+      ECDSA &    OpenSSL 1.0.2f   &  5                    & 4                   & 1                    &  8,248,322       & 101     \\   
+      ECDSA &   OpenSSL 1.0.2k     &  5                    & 4                   & 1                    &  8,263,599      & 100      \\   
+      ECDSA &   OpenSSL 1.1.0f  &  5                    & 4                   & 1                    &  6,100,465       & 76     \\  
+      ECDSA &   OpenSSL 1.1.1       & 0                      &  0                   &    0               &  10,244,076       &  121      \\  
+      ECDSA &   OpenSSL 1.1.1g    & 0         &  0       &  0           &  9,266,191          & 102    \\
 
                          &                        &                     &                      &                 & minutes            \\\cline{7-7}
-      RSA &           & 6                       & 6                   & 0                    & 22,109,246    & 39      \\
-      RSA &            & 12                      & 12                  & 0                    & 24,484,441    & 44        \\
-      RSA &           & 107                    & 105                 & 2                    & 17,002,523   & 23  \\
-      RSA &           & 38                     & 27                  & 11                   & 14,468,307   & 29    \\
-      RSA &           & 36                     & 27                  & 9                    & 15,285,210   & 40      \\
+      RSA &    mbedTLS 2.5   & 6            & 6          & 0                    & 22,109,246    & 39      \\
+      RSA &    mbedTLS 2.15    & 12          & 12     & 0                    & 24,484,441    & 44        \\
+      RSA &     OpenSSL 0.9.7      & 107     & 105           & 2                    & 17,002,523   & 23  \\
+      RSA &    OpenSSL 1.0.2f      & 38                     & 27                  & 11                   & 14,468,307   & 29    \\
+      RSA &   OpenSSL 1.0.2k      & 36              & 27                  & 9                    & 15,285,210   & 40      \\
       RSA &          & 31                     & 22                  & 9                    & 16,390,750   & 34      \\

### 2021-04-04 Chapter-3/Chapter-3.tex
update

@@
       RSA &   OpenSSL 1.0.2k      & 36              & 27                  & 9                    & 15,285,210   & 40      \\
-      RSA &          & 31                     & 22                  & 9                    & 16,390,750   & 34      \\
-      RSA &         & 4                      &  4                  & 0                    & 18,207,016   & 8         \\
-      RSA &            & 8                      &  8                  & 0                    & 18,536,796    & 5       \\
-      RSA & & 11& 9& 2& 9,527,231& 2 \\
-      RSA & & 14& 14& 0& 10,513,606& 14  \\
-      RSA &        & 8                      &  8                  & 0                    & 27,407,986    & 113    \\
+      RSA &   OpenSSL 1.1.0f       & 31           & 22                  & 9                    & 16,390,750   & 34      \\
+      RSA &  OpenSSL 1.1.1       & 4                      &  4                  & 0                    & 18,207,016   & 8         \\
+      RSA &  OpenSSL 1.1.1g      & 8                      &  8                  & 0                    & 18,536,796    & 5       \\
+      RSA & Libgcrypt 1.6.1 & 11& 9& 2& 9,527,231& 2 \\
+      RSA & Libgcrypt 1.7.3 & 14& 14& 0& 10,513,606& 14  \\
+      RSA & Libgcrypt 1.8.5 & 8                      &  8                  & 0                    & 27,407,986    & 113    \\
 

### 2021-04-04 Chapter-3/Chapter-3.tex
update

--- 2021-04-04 Chapter-3/Chapter-3.tex
@@
                        & \textbf{\# Instructions} & \textbf{Time}                                                               \\\hline
-                                               &                        &                     &                      &              & ms                     \\\cline{7-7}
+                       &                          &                   &                &                &             & ms      \\\cline{7-7}
     AES                & mbedTLS 2.5              & 68                & 0              & 68             & 39,855      & 512     \\
@@
     AES                & OpenSSL 1.0.2f           & 88                & 0              & 88             & 1,350       & 36      \\
-      AES&   OpenSSL 1.0.2k       & 88         & 0                   & 88                   & 1,350        & 35   \\
+    AES                & OpenSSL 1.0.2k           & 88                & 0              & 88             & 1,350       & 35      \\
     AES                & OpenSSL 1.1.0f           & 88                & 0              & 88             & 1,420       & 36      \\
@@
 
-                         &                        &                     &                      &                 & minutes            \\\cline{7-7}
+                       &                          &                   &                &                &             & minutes \\\cline{7-7}
     RSA                & mbedTLS 2.5              & 6                 & 6              & 0              & 22,109,246  & 39      \\
@@
     RSA                & OpenSSL 1.0.2k           & 36                & 27             & 9              & 15,285,210  & 40      \\
-      RSA &          & 31                     & 22                  & 9                    & 16,390,750   & 34      \\
-      RSA &         & 4                      &  4                  & 0                    & 18,207,016   & 8         \\
-      RSA &            & 8                      &  8                  & 0                    & 18,536,796    & 5       \\
-      RSA & & 11& 9& 2& 9,527,231& 2 \\
-      RSA & & 14& 14& 0& 10,513,606& 14  \\
-      RSA &        & 8                      &  8                  & 0                    & 27,407,986    & 113    \\
+    RSA                & OpenSSL 1.1.0f           & 31                & 22             & 9              & 16,390,750  & 34      \\
+    RSA                & OpenSSL 1.1.1            & 4                 & 4              & 0              & 18,207,016  & 8       \\
+    RSA                & OpenSSL 1.1.1g           & 8                 & 8              & 0              & 18,536,796  & 5       \\
+    RSA                & Libgcrypt 1.6.1          & 11                & 9              & 2              & 9,527,231   & 2       \\
+    RSA                & Libgcrypt 1.7.3          & 14                & 14             & 0              & 10,513,606  & 14      \\
+    RSA                & Libgcrypt 1.8.5          & 8                 & 8              & 0              & 27,407,986  & 113     \\
 
-      Total              & 904                    & 241                 & 663                & 167,141,947      & 341m  \\\hline
+    Total              &                          & 904               & 241            & 663            & 167,141,947 & 341m    \\\hline
   \end{tabular}

### 2021-04-04 Chapter-3/Chapter-3.tex
update

@@
 
+We build the source program into 32-bit x86 Linux executables with GCC 7.5
+running on Ubuntu 16.04.
+We run our experiments on a 2.90GHz Intel Xeon(R) E5-2690 CPU with 128GB
+RAM. The execution time is calculated on a single-core.
+
 \subsection{Evaluation Result Overview}
@@
   \newcommand{\foo}{\mbox{\hspace*{\the\x}}}
-  \begin{tabular}{llrrrrr}
+  \begin{tabular}{llrrrrrr}
     \hline
     \textbf{Algorithm} & \textbf{Implementation}  & \textbf{\# Leaks} & \textbf{\# CF}    & \textbf{\# DF}
-                       & \textbf{\# Instructions} & \textbf{Time}                                                               \\\hline
+                       & \textbf{\# Instructions} & \textbf{Time}     & \textbf{RAM (MB)}                                                  \\\hline
                        &                          &                   &                   &                &             & ms              \\\cline{7-7}
-    AES                & mbedTLS 2.5              & 68                & 0              & 68             & 39,855      & 512     \\
-    AES                & mbedTLS 2.15             & 68                & 0              & 68             & 39,855      & 520     \\
-    AES                & OpenSSL 0.9.7            & 75                & 0              & 75             & 1,704       & 231     \\
-    AES                & OpenSSL 1.0.2f           & 88                & 0              & 88             & 1,350       & 36      \\
-    AES                & OpenSSL 1.0.2k           & 88                & 0              & 88             & 1,350       & 35      \\
-    AES                & OpenSSL 1.1.0f           & 88                & 0              & 88             & 1,420       & 36      \\
-    AES                & OpenSSL 1.1.1            & 88                & 0              & 88             & 1,586       & 43      \\
-    DES                & mbedTLS 2.5              & 15                & 0              & 15             & 4,596       & 58      \\
-    DES                & mbedTLS 2.15             & 15                & 0              & 15             & 4,596       & 57      \\
-    DES                & OpenSSL 0.9.7            & 6                 & 0              & 6              & 2,976       & 163     \\
-    DES                & OpenSSL 1.0.2f           & 8                 & 0              & 8              & 2,593       & 166     \\
-    DES                & OpenSSL 1.0.2k           & 8                 & 0              & 8              & 2,593       & 165     \\
-    DES                & OpenSSL 1.1.0f           & 8                 & 0              & 8              & 4,260       & 182     \\
-    DES                & OpenSSL 1.1.1            & 6                 & 0              & 6              & 8,272       & 229     \\
+    AES                & mbedTLS 2.5              & 68                & 0                 & 68             & 39,855      & 512     & 47    \\
+    AES                & mbedTLS 2.15             & 68                & 0                 & 68             & 39,855      & 520     & 47    \\
+    AES                & OpenSSL 0.9.7            & 75                & 0                 & 75             & 1,704       & 231     & 15    \\
+    AES                & OpenSSL 1.0.2f           & 88                & 0                 & 88             & 1,350       & 36      & 15    \\
+    AES                & OpenSSL 1.0.2k           & 88                & 0                 & 88             & 1,350       & 35      & 16    \\
+    AES                & OpenSSL 1.1.0f           & 88                & 0                 & 88             & 1,420       & 36      & 16    \\
+    AES                & OpenSSL 1.1.1            & 88                & 0                 & 88             & 1,586       & 43      & 16    \\
+    DES                & mbedTLS 2.5              & 15                & 0                 & 15             & 4,596       & 58      & 8     \\
+    DES                & mbedTLS 2.15             & 15                & 0                 & 15             & 4,596       & 57      & 8     \\
+    DES                & OpenSSL 0.9.7            & 6                 & 0                 & 6              & 2,976       & 163     & 11    \\
+    DES                & OpenSSL 1.0.2f           & 8                 & 0                 & 8              & 2,593       & 166     & 11    \\
+    DES                & OpenSSL 1.0.2k           & 8                 & 0                 & 8              & 2,593       & 165     & 11    \\
+    DES                & OpenSSL 1.1.0f           & 8                 & 0                 & 8              & 4,260       & 182     & 21    \\
+    DES                & OpenSSL 1.1.1            & 6                 & 0                 & 6              & 8,272       & 229     & 43    \\
                        &                          &                   &                   &                &             & seconds         \\\cline{7-7}
-    Chacha20           & Monocypher 3.0           & 0                 & 0              & 0              & 149,353     & 2       \\
-    Poly1305           & Monocypher 3.0           & 0                 & 0              & 0              & 1,213,937   & 15      \\
-    Argon2i            & Monocypher 3.0           & 0                 & 0              & 0              & 4,595,142   & 37      \\
-    Ed25519            & Monocypher 3.0           & 0                 & 0              & 0              & 5,713,619   & 271     \\
-    ECDSA              & mbedTLS 2.5              & 6                 & 6              & 0              & 4,214,946   & 48      \\
-    ECDSA              & mbedTLS 2.15             & 4                 & 4              & 0              & 4,192,558   & 102     \\
-    ECDSA              & OpenSSL 1.0.2f           & 5                 & 4              & 1              & 8,248,322   & 101     \\
-    ECDSA              & OpenSSL 1.0.2k           & 5                 & 4              & 1              & 8,263,599   & 100     \\
-    ECDSA              & OpenSSL 1.1.0f           & 5                 & 4              & 1              & 6,100,465   & 76      \\
-    ECDSA              & OpenSSL 1.1.1            & 0                 & 0              & 0              & 10,244,076  & 121     \\
-    ECDSA              & OpenSSL 1.1.1g           & 0                 & 0              & 0              & 9,266,191   & 102     \\
+    Chacha20           & Monocypher 3.0           & 0                 & 0                 & 0              & 149,353     & 2       & 15    \\
+    Poly1305           & Monocypher 3.0           & 0                 & 0                 & 0              & 1,213,937   & 15      & 43    \\
+    Argon2i            & Monocypher 3.0           & 0                 & 0                 & 0              & 4,595,142   & 37      & 102   \\
+    Ed25519            & Monocypher 3.0           & 0                 & 0                 & 0              & 5,713,619   & 271     & 98    \\
+    ECDSA              & mbedTLS 2.5              & 6                 & 6                 & 0              & 4,214,946   & 48      & 689   \\
+    ECDSA              & mbedTLS 2.15             & 4                 & 4                 & 0              & 4,192,558   & 102     & 680   \\
+    ECDSA              & OpenSSL 1.0.2f           & 5                 & 4                 & 1              & 8,248,322   & 101     & 980   \\
+    ECDSA              & OpenSSL 1.0.2k           & 5                 & 4                 & 1              & 8,263,599   & 100     & 906   \\
+    ECDSA              & OpenSSL 1.1.0f           & 5                 & 4                 & 1              & 6,100,465   & 76      & 705   \\
+    ECDSA              & OpenSSL 1.1.1            & 0                 & 0                 & 0              & 10,244,076  & 121     & 1,048 \\
+    ECDSA              & OpenSSL 1.1.1g           & 0                 & 0                 & 0              & 9,266,191   & 102     & 1,001 \\
 
                        &                          &                   &                   &                &             & minutes         \\\cline{7-7}
-    RSA                & mbedTLS 2.5              & 6                 & 6              & 0              & 22,109,246  & 39      \\
-    RSA                & mbedTLS 2.15             & 12                & 12             & 0              & 24,484,441  & 44      \\
-    RSA                & OpenSSL 0.9.7            & 107               & 105            & 2              & 17,002,523  & 23      \\
-    RSA                & OpenSSL 1.0.2f           & 38                & 27             & 11             & 14,468,307  & 29      \\
-    RSA                & OpenSSL 1.0.2k           & 36                & 27             & 9              & 15,285,210  & 40      \\
-    RSA                & OpenSSL 1.1.0f           & 31                & 22             & 9              & 16,390,750  & 34      \\
-    RSA                & OpenSSL 1.1.1            & 4                 & 4              & 0              & 18,207,016  & 8       \\
-    RSA                & OpenSSL 1.1.1g           & 8                 & 8              & 0              & 18,536,796  & 5       \\
-    RSA                & Libgcrypt 1.6.1          & 11                & 9              & 2              & 9,527,231   & 2       \\
-    RSA                & Libgcrypt 1.7.3          & 14                & 14             & 0              & 10,513,606  & 14      \\
-    RSA                & Libgcrypt 1.8.5          & 8                 & 8              & 0              & 27,407,986  & 113     \\
+    RSA                & mbedTLS 2.5              & 6                 & 6                 & 0              & 22,109,246  & 39      & 3,708 \\
+    RSA                & mbedTLS 2.15             & 12                & 12                & 0              & 24,484,441  & 44      & 4,012 \\
+    RSA                & OpenSSL 0.9.7            & 107               & 105               & 2              & 17,002,523  & 23      & 3,601 \\
+    RSA                & OpenSSL 1.0.2f           & 38                & 27                & 11             & 14,468,307  & 29      & 3,301 \\
+    RSA                & OpenSSL 1.0.2k           & 36                & 27                & 9              & 15,285,210  & 40      & 3,402 \\
+    RSA                & OpenSSL 1.1.0f           & 31                & 22                & 9              & 16,390,750  & 34      & 3,701 \\
+    RSA                & OpenSSL 1.1.1            & 4                 & 4                 & 0              & 18,207,016  & 8       & 4,181 \\
+    RSA                & OpenSSL 1.1.1g           & 8                 & 8                 & 0              & 18,536,796  & 5       & 3,901 \\
+    RSA                & Libgcrypt 1.6.1          & 11                & 9                 & 2              & 9,527,231   & 2       & 2516  \\
+    RSA                & Libgcrypt 1.7.3          & 14                & 14                & 0              & 10,513,606  & 14      & 2,701 \\
+    RSA                & Libgcrypt 1.8.5          & 8                 & 8                 & 0              & 27,407,986  & 113     & 4,701 \\
 
@@
 \end{table*}
+Table~\ref{table:over_result} summarizes the results.
+\tool{} finds 904 leaks in the crypto libraries.
+Among these 904 leaks, 241 are due to secret-dependent
+control-flow transfers and 663 are due to secret-dependent data accesses.
 
+\tool{} also finds that most side-channel
+vulnerabilities leak very little information in practice, which confirms our
+initial assumption.
+However, \tool{} finds some vulnerabilities with severe
+leakages. Prior research has confirmed that some of these
+vulnerabilities can be exploited in real attacks.
+With our tool, developers can
+distinguish non-critical ``vulnerabilities'' from severe ones.
+
+Symmetric encryption implementations in OpenSSL and mbedTLS have significant leakage due to their lookup table implementations.
+\tool{} confirms that those leakage comes from table lookups.
+The new implementation of OpenSSL has adopted several methods (e.g., one single S-box instead of four lookup tables, smaller lookup tables) to mitigate the problem.
+Those changes are rather easy but significantly decrease the total amount of leaked information as the quantification result indicates.
+
+We also evaluate our tool on the RSA implementation. With the optimization
+introduced in \S\ref{sec:scala}, we need not apply domain knowledge to
+simplify the analysis. Our tool identifies all leakage sites
+reported by CacheD~\cite{203878} and find new leaks in less time.
+We also find newer
+versions of RSA in OpenSSL have fewer leaks. We
+will discuss the version changes and corresponding leakages in \S\ref{eval:asym}.
+
+\subsection{Comparison with the Existing Tools}
+\label{eval:scala}
+
+In this section, we compare \tool{} with the
+existing trace-based side-channel detection tools on vulnerability detections. For other tools, we use the data in the paper. As other tools do not quantify leakage sites,
+we only include the time of detecting vulnerabilities to perform a fair comparison.
+
+The comparison result with CacheD~\cite{203878} is shown in Table~\ref{eval:cacheD}.
+Note that one statement in the source code can be compiled into several machine instructions.
+So it is possible that one statement can have multiple leakage points.
+Under the circumstance, we think it is only a leakage.
+We have confirmed that \tool{} can identify all the secret-dependent data access vulnerabilities reported by CacheD. In addition, \tool{} finds many new ones.
+CacheD fails to detect some vulnerabilities for two
+reasons. First, CacheD can only detect secret-dependent data access
+vulnerabilities. \tool{} can detect secret-dependent control-flows as well.
+Second, according to the CacheD paper, CacheD times out after 20 hours to process
+asymmetric ciphers. CacheD applies some domain knowledge to simplify and speed up
+the analysis.
+While those optimizations do not introduce false positives, they may miss some
+vulnerabilities.
+We notice that the number of instructions in those traces are different due to the different analysis starting
+functions and building options during the evaluation.
+Table~\ref{eval:cacheD} shows that
+\tool{} is faster than CacheD. \tool{} is much faster than CacheD when analyzing the same
+number of instructions. For example, when we test~\tool{} on AES from OpenSSL
+0.9.7, \tool{} is over 100x faster than CacheD.
+\begin{table}[]
+  \caption{Comparison with CacheD: Time,
+    Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF), The Number of Instructions\,(\# Instructions).}
+  \label{eval:cacheD}
+  \begin{threeparttable}
+    \begin{tabular}{@{}c|r@{~~}r@{~~}r|r@{~~}r@{~}r@{}}
+      \hline
+      \multicolumn{1}{l|}{} & \multicolumn{3}{c|}{CacheD} & \multicolumn{3}{c}{Abacus}                                             \\
+      Name                  & Time (s)                    & \# Instructions            & DF & Time (s) & \# Instructions & CF+DF   \\ \hline
+      AES\tnote{1}          & 43.4                        & 791                        & 48 & 0.23     & 1,704           & 0+75    \\
+      AES\tnote{2}          & 48.5                        & 2,410                      & 32 & 0.04     & 1,350           & 0+88    \\
+      RSA\tnote{1}          & 199.3                       & 674,797                    & 1  & 1,351.6  & 17,002,523      & 105+2   \\
+      RSA\tnote{2}          & 165.6                       & 473,392                    & 1  & 1,753.3  & 14,468,307      & 27+11   \\
+      RSA\tnote{3}          & 11542.3                     & 26,848,103                 & 2  & 128.1    & 9,527,231       & 9+2     \\
+      RSA\tnote{4}          & 10788.9                     & 27,775,053                 & 0  & 891.7    & 10,513,606      & 14+0    \\ \hline
+      Total                 & 22,788.0                    & 55,738,546                 & 84 & 4,125.0  & 51,514,721      & 155+178 \\ \hline
+      \multicolumn{7}{l}{\# of Instructions per second \qquad  CacheD: 2,445 \qquad \tool: 12,489}                                 \\ \hline
+    \end{tabular}
+  \end{threeparttable}
+  \begin{tablenotes}
+    \scriptsize
+    \item[1] OpenSSL\,0.9.7  \item[2] OpenSSL\,1.0.2f   \item[3] Libgcrypt\,1.6.1 \item[4] Libgcrypt\,1.7.3 \\
+  \end{tablenotes}
+  \vspace*{-20pt}
+\end{table}
+Since DATA~\cite{217537} needs to compare several execution
+traces to identify side-channel leakages, \tool{} also outperforms
+DATA in terms of performance. For
+example, it takes 234 minutes for DATA to analyze the RSA of
+implementation in OpenSSL 1.1.0f. \tool{} only spends 34 minutes
+according to Table~\ref{table:over_result}.  Also, DATA reports
+report 278 control-flow and 460 memory-access leaks. Among those
+leakages, they find one new vulnerability in RSA after some manual
+analysis.  \tool{} finds the vulnerability and reports the
+vulnerability is severe (\textsf{int\_bn\_mod\_inverse} leaks more
+than 14.9 bits and \textsf{BN\_div} leaks more than 17.2 bits),
+which eases the pain to identify real sensitive leaks.}{DATA~\cite{217537} identifies
+side-channel leakages by finding differences in execution traces of
+the test program under \emph{various secret inputs}. According to
+the original DATA paper, it uses 443 different traces to analyze the
+side-channel vulnerabilities in symmetric cyphers and 450 different
+traces to analyze the side-channel vulnerabilities in asymmetric
+cyphers. On the other hand, \tool{} detects side-channel
+vulnerabilities from one execution trace. \tool{} uses symbolic
+analysis to extract formulas that model each side-channel
+leakage. After that, we sample the formula with \emph{various
+  secret inputs} to detect and quantify each leakage site. In
+theory, DATA might have better code coverage than \tool{} because it
+uses more execution traces,  but \tool{} has the following
+advantages. a) \tool{} is faster than DATA. For example, it takes
+116 minutes for DATA to detect vulnerabilities in the RSA implementation in OpenSSL 1.1.0f\@.
+\tool{} only spends 34 minutes, as shown in Table~\ref{table:over_result}.
+It takes 13 minutes and 20 minutes
+for DATA to analyze the side-channel leakages in AES and DES,
+respectively. On the other hand, \tool{} finishes its analysis in
+less than ten seconds while finding all the leakages reported by
+DATA. b) Because \tool{} does not run the test program again when we
+have a new \emph{secret input}, \tool{} can test more input secrets
+on those formulas within the same time to achieve better precision.
+c) DATA tries to use leakage models (domain knowledge) to classify each leakage.
+The strength of Abacus is that it does not need such domain knowledge.
+DATA reports 278 control-flow and 460 memory-access leaks for the RSA implementation in OpenSSL 1.1.0f. Among those leakages, they find one new vulnerability in RSA after some manual analysis.
+\tool{} finds the vulnerability and reports the vulnerability is
+severe (\textsf{int\_bn\_mod\_inverse} leaks more than 14.9 bits and
+\textsf{BN\_div} leaks more than 17.2 bits), which helps identify
+real sensitive leaks.  For each leakage site, \tool{} can provide
+concrete examples to trigger the issue and give an estimation to
+assess the severity level of the vulnerability.
 \section{Discussion}

### 2021-04-04 Chapter-4/Chapter-4.tex
update
Updates from Overleaf

@@
 
-\section{Implementation}
+\section{Design and Implementation}
+
+Figure~\ref{fig:workflow} shows the three steps of \tool{}.
+First, we run the target program with a
+concrete input (sensitive information) under the dynamic binary instrumentation
+(DBI) framework to collect an execution trace. After that, we run the symbolic
+execution to capture fine-grained semantic information for each
+secret-dependent control-flow transfer and data access. Finally, we run Monte
+Carlo (MC) simulation to estimate the amount of leaked information.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.45\textwidth]{./figures/chapter4/workflow.pdf}
+    \caption{The workflow of \tool{}.}
+    \label{fig:workflow}
+    \vspace*{-15pt}
+\end{figure}
+
+\subsection{Execution trace generation} The design goal of \tool{} is to estimate the information leakage as precisely as possible. 
+We run the target binary under a dynamic binary instrumentation (DBI) tool
+to record execution traces and runtime information.
+Once the sensitive information is loaded into memory, we start to collect the trace.
+In this step, we mark variables and buffers that hold the sensitive data by either annotating the source code (\textsf{make\_abacus\_symbolic}) or telling the DBI tool of the memory address and the length of secrets.
+
+\subsection{Instruction level symbolic execution} We model attackers'
+observations from side-channel vulnerabilities with logic formulas.
+Each formula captures the fine-grained information between input
+secrets and leakage sites. The engine only symbolically executes
+instruction that might be affected by the input sensitive data.
+\tool{} works on one path at a time.
+The memory model is conceptually similar to other offline executors (e.g., SAGE~\cite{godefroid2008automated} and the trace-based executor of BitBlaze~\cite{song2008bitblaze}).
+That is, we use symbolic execution to track secrets.
+When secrets are loaded into the memory, \tool{} starts to interpret instructions symbolically.
+We treat secrets as symbols ($S$).
+For other variables, we use concrete values ($C$)
+from the execution.
+We do not know which instruction may manipulate a secret until we execute it.
+For each instruction, if all its operands and implicit memory accesses are concrete values, we perform concrete calculation and update the destination with the concrete value according to the instruction semantics.
+Otherwise, we symbolically interpret the instruction and update the destination with a formula.
+
+\subsection{Leakage estimation} We change the information leakage 
+quantification problem into the counting problem. We propose a
+Monte Carlo method to estimate the number of satisfying solutions.
+With the help of the Central Limit Theorem (CLT), we also give an error 
+estimate with the probability, which provides us with the \emph{precision guarantee}.
 

### 2021-04-04 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \subsection{Constraint Solving}
-As discussed in \S\ref{side-channel:condition}, the problem of identifying
+As discussed in the previous section, the problem of identifying
 side-channels can be reduced to the question below.
@@
 We also evaluate Monocypher, a new cryptographic library that resists to most side-channel attacks.
-Monocypher is designed to have no secret dependent indices and secret dependent branches. Therefore, Monocypher should be secure under our threat model.
+According to the developers, Monocypher is designed to have no secret dependent indices and secret dependent branches.
+Therefore, Monocypher should be secure under our threat model.
+Libgcrypt is a crytpographic library from the GunPG.
+As some previous work (e.g., CacheD) choose to evaluate their tools on CacheD, we can compare the evaluation results by applying the tool on Libgcrypt.
 
-Moreover, for some crypto library, we evaluate more than one versions. After that, we compare the evaluation results with the version history to track developers' patches of those leakages.
+For some crypto libraries, we evaluate multiple versions.
+After that, we compare the evaluation results with the version history to track those leakages' patches.
+In summary, we evaluate our tool on the following libraries.
 \begin{itemize}
@@
   \item MbedTLS: 2.5, 2.15
-  \item Libgcrypt: 1.8.5
+  \item Libgcrypt: 1.6.1, 1.7.3, 1.8.5
   \item Monocyper: 3.0
@@
 
+We refer to the examples or test cases of those libraries and write simple
+programs that use the crypto libraries. For symmetric encryption, the length
+of the keys are 256 bit. For RSA, the length of the keys is 1024. For ECDSA, the
+length of the key is 384 bit. The input public message is ``Hello World!''.
 We mark variables and buffers that store a secret.
@@
 We build the source program into 32-bit x86 Linux executables with GCC 7.5
-running on Ubuntu 16.04.
+running on Ubuntu 16.04. While our tool can work on the stripped binaries, 
+in the evaluation, we keep the debug information to get the fine-grained infromation
+(e.g., line numbers).
 We run our experiments on a 2.90GHz Intel Xeon(R) E5-2690 CPU with 128GB
-RAM. The execution time is calculated on a single-core.
+RAM. We run the experiments simultaneously, but the execution time is calculated on a single-core.
 
@@
   \centering\small\footnotesize
-  \caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks),
+  \caption{Evaluation results overview: Algorithm, Implementation, Side-channel Leaks\,(Leaks),
     Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF),
-    The number of instructions\,(\# Instructions), Symbolic Execution\,(SE) and Monte Carlo\,(MC) time.
+    The number of instructions\,(\# Instructions), The Execution Time, and The Memory Usage.
   }\label{table:over_result}
-  \newlength{\x}
-  \newlength{\y}
-  \settowidth{\x}{~~}
-  \settowidth{\y}{m}
-  \addtolength{\x}{-1\y}
-  \newcommand{\foo}{\mbox{\hspace*{\the\x}}}
   \begin{tabular}{llrrrrrr}
@@
     DES                & OpenSSL 1.1.0f           & 8                 & 0                 & 8              & 4,260       & 182     & 21    \\
+    Triple DES         & OpenSSL 1.1.0f &  9 &0  &9   &13,105   & 369 & 56\\
     DES                & OpenSSL 1.1.1            & 6                 & 0                 & 6              & 8,272       & 229     & 43    \\
@@
 
-    Total              &                          & 904               & 241               & 663            & 167,141,947 & 341m            \\\hline
+    Total              &                          & 913               & 241               & 672            & 167,155,052 & 341m            \\\hline
   \end{tabular}
@@
 Table~\ref{table:over_result} summarizes the results.
-\tool{} finds 904 leaks in the crypto libraries.
-Among these 904 leaks, 241 are due to secret-dependent
-control-flow transfers and 663 are due to secret-dependent data accesses.
+\tool{} finds 913 leaks in the crypto libraries.
+Among these 913 leaks, 241 are due to secret-dependent
+control-flow transfers and 672 are due to secret-dependent data accesses.
 
@@
 We also evaluate our tool on the RSA implementation. With the optimization
-introduced in \S\ref{sec:scala}, we need not apply domain knowledge to
+introduced in the previous sections, we need not apply domain knowledge to
 simplify the analysis. Our tool identifies all leakage sites
@@
 We also find newer
-versions of RSA in OpenSSL have fewer leaks. We
-will discuss the version changes and corresponding leakages in \S\ref{eval:asym}.
+versions of RSA in OpenSSL have fewer leaks.
 
@@
 In this section, we compare \tool{} with the
-existing trace-based side-channel detection tools on vulnerability detections. For other tools, we use the data in the paper. As other tools do not quantify leakage sites,
-we only include the time of detecting vulnerabilities to perform a fair comparison.
+existing trace-based side-channel detection tools on vulnerability detections.
+For other tools, we use the data in the paper.
+As other tools do not quantify leakage sites, we only include the time of detecting vulnerabilities to perform a fair comparison.
 
@@
 0.9.7, \tool{} is over 100x faster than CacheD.
-\begin{table}[]
+\begin{table*}[]
+ \centering
   \caption{Comparison with CacheD: Time,
@@
   \label{eval:cacheD}
-  \begin{threeparttable}
+
     \begin{tabular}{@{}c|r@{~~}r@{~~}r|r@{~~}r@{~}r@{}}
@@
     \end{tabular}
-  \end{threeparttable}
-  \begin{tablenotes}
-    \scriptsize
-    \item[1] OpenSSL\,0.9.7  \item[2] OpenSSL\,1.0.2f   \item[3] Libgcrypt\,1.6.1 \item[4] Libgcrypt\,1.7.3 \\
-  \end{tablenotes}
-  \vspace*{-20pt}
-\end{table}
-Since DATA~\cite{217537} needs to compare several execution
-traces to identify side-channel leakages, \tool{} also outperforms
-DATA in terms of performance. For
-example, it takes 234 minutes for DATA to analyze the RSA of
-implementation in OpenSSL 1.1.0f. \tool{} only spends 34 minutes
-according to Table~\ref{table:over_result}.  Also, DATA reports
-report 278 control-flow and 460 memory-access leaks. Among those
-leakages, they find one new vulnerability in RSA after some manual
-analysis.  \tool{} finds the vulnerability and reports the
-vulnerability is severe (\textsf{int\_bn\_mod\_inverse} leaks more
-than 14.9 bits and \textsf{BN\_div} leaks more than 17.2 bits),
-which eases the pain to identify real sensitive leaks.}{DATA~\cite{217537} identifies
+
+\end{table*}
+DATA~\cite{217537} identifies
 side-channel leakages by finding differences in execution traces of
@@
 assess the severity level of the vulnerability.
-\section{Discussion}
+\section{Discussion and Limitation}
 

### 2021-04-04 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 
+During our evaluation process, we are interested in the following
+aspects:
+\begin{enumerate}
+    \item Is \tool{} effective to detect side-channels in real-world crypto systems? (Effectiveness)
+    \item How much performance overhead does the method introduce? (Performance)
+    \item How effective are the design choices made by the tool method? (Design Choices)
+\end{enumerate}
+
 \subsection{Evaluation Result Overview}
@@
 
-\tool{} also finds that most side-channel
-vulnerabilities leak very little information in practice, which confirms our
-initial assumption.
-However, \tool{} finds some vulnerabilities with severe
-leakages. Prior research has confirmed that some of these
-vulnerabilities can be exploited in real attacks.
-With our tool, developers can
-distinguish non-critical ``vulnerabilities'' from severe ones.
+The evaluated algorithms can be classified into two categories: symmetric
+encryption and asymmetric encryption.
 
@@
 reported by CacheD~\cite{203878} and find new leaks in less time.
-We also find newer
-versions of RSA in OpenSSL have fewer leaks.
+We also find newer versions of RSA in OpenSSL have fewer leaks.
 

### 2021-04-04 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 encryption and asymmetric encryption.
-
-Symmetric encryption implementations in OpenSSL and mbedTLS have significant leakage due to their lookup table implementations.
-\tool{} confirms that those leakage comes from table lookups.
+Most of the side-channel leakages in symmetric implementations are from the lookup tables.
 The new implementation of OpenSSL has adopted several methods (e.g., one single S-box instead of four lookup tables, smaller lookup tables) to mitigate the problem.
-Those changes are rather easy but significantly decrease the total amount of leaked information as the quantification result indicates.
 
@@
 reported by CacheD~\cite{203878} and find new leaks in less time.
-We also find newer versions of RSA in OpenSSL have fewer leaks.
+We also find newer versions of RSA in OpenSSL have fewer leaks. Our tool can
+finish all the analysis in less than 6 hours.
 
@@
 vulnerabilities.
-We notice that the number of instructions in those traces are different due to the different analysis starting
-functions and building options during the evaluation.
+Third, CacheD only symbolizes the encryption keys. Some side-channel leakages when the input messages equal to some certain values. It is possible that CacheD miss some
+leakages as we have discussion the previous sections.
+We notice that the number of instructions in those traces are different due to the different analysis starting functions and building options during the evaluation.
 Table~\ref{eval:cacheD} shows that
@@
 
-    \begin{tabular}{@{}c|r@{~~}r@{~~}r|r@{~~}r@{~}r@{}}
+    \begin{tabular}{@{}l|r@{~~}r@{~~}r|r@{~~}r@{~}r@{}}
       \hline
@@
       Name                  & Time (s)                    & \# Instructions            & DF & Time (s) & \# Instructions & CF+DF   \\ \hline
-      AES\tnote{1}          & 43.4                        & 791                        & 48 & 0.23     & 1,704           & 0+75    \\
-      AES\tnote{2}          & 48.5                        & 2,410                      & 32 & 0.04     & 1,350           & 0+88    \\
-      RSA\tnote{1}          & 199.3                       & 674,797                    & 1  & 1,351.6  & 17,002,523      & 105+2   \\
-      RSA\tnote{2}          & 165.6                       & 473,392                    & 1  & 1,753.3  & 14,468,307      & 27+11   \\
-      RSA\tnote{3}          & 11542.3                     & 26,848,103                 & 2  & 128.1    & 9,527,231       & 9+2     \\
-      RSA\tnote{4}          & 10788.9                     & 27,775,053                 & 0  & 891.7    & 10,513,606      & 14+0    \\ \hline
+      AES OpenSSL 0.9.7         & 43.4                        & 791                        & 48 & 0.23     & 1,704           & 0+75    \\
+      AES OpenSSL 1.0.2f       & 48.5                        & 2,410                      & 32 & 0.04     & 1,350           & 0+88    \\
+      RSA OpenSSL 0.9.7       & 199.3                       & 674,797                    & 1  & 1,351.6  & 17,002,523      & 105+2   \\
+      RSA OpenSSL 1.0.2f     & 165.6                       & 473,392                    & 1  & 1,753.3  & 14,468,307      & 27+11   \\
+      RSA Libgcrypt 1.6.1     & 11542.3                     & 26,848,103                 & 2  & 128.1    & 9,527,231       & 9+2     \\
+      RSA Libgcrypt 1.7.3         & 10788.9                     & 27,775,053                 & 0  & 891.7    & 10,513,606      & 14+0    \\ \hline
       Total                 & 22,788.0                    & 55,738,546                 & 84 & 4,125.0  & 51,514,721      & 155+178 \\ \hline
@@
 \end{table*}
+
 DATA~\cite{217537} identifies
@@
 less than ten seconds while finding all the leakages reported by
-DATA. b) Because \tool{} does not run the test program again when we
+DATA. b) Because \tool{} does not run the test program again when wedinghao w
 have a new \emph{secret input}, \tool{} can test more input secrets
@@
 DATA reports 278 control-flow and 460 memory-access leaks for the RSA implementation in OpenSSL 1.1.0f. Among those leakages, they find one new vulnerability in RSA after some manual analysis.
-\tool{} finds the vulnerability and reports the vulnerability is
-severe (\textsf{int\_bn\_mod\_inverse} leaks more than 14.9 bits and
-\textsf{BN\_div} leaks more than 17.2 bits), which helps identify
-real sensitive leaks.  For each leakage site, \tool{} can provide
+\tool{} finds the vulnerability.  For each leakage site, \tool{} can provide
 concrete examples to trigger the issue and give an estimation to
 assess the severity level of the vulnerability.
-\section{Discussion and Limitation}
 
-In the section, we discuss the limitations, usages, and some future work.
-%
+\section{Discussion}
+
 \tool{} works on native x86 execution traces. The design, which is very
@@
 the common limitations of dynamic approaches. \tool{} may only cover part of the code.
-% Each time we only get one single execution trace. Therefore,
-We may
-neglect some side-channel vulnerabilities not covered by the traces analyzed.
+Each time we only get one single execution trace. Therefore,
+we may neglect some side-channel vulnerabilities not covered by the traces analyzed.
 However, this is not a crucial problem for analyzing crypto libraries because crypto

### 2021-04-04 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 on the whole code coverage as well.
+
+While recent works have reported lots
+of potential side-channel vulnerabilities, most of them are not patched by
+developers. For RSA, the latest
+OpenSSL only has one leakage site that can leak more than 3 bits while there
+are 22 leakage sites according to \tool{}. DES implementation of OpenSSL has
+several sensitive leakages, but given the end life status of DES, it is still
+unpatched for the worth of engineering effort.

### 2021-04-04 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 keys~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.
-
-%% to deal with side channels, we can protect or detect them and detection is better
-%%arious countermeasures have been proposed to defend against software-based
-%%side-channel attacks. Hardware-level solutions, such as reducing shared
-%%resources, adopting oblivious RAM, and using transnational
-%%memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need new
-%%hardware features and changes in modern complex computer systems, which are
-%%impractical and hard to adopt in reality. Therefore, a promising and
-%%universal direction is software countermeasures, detecting and eliminating
-%%side-channel vulnerabilities from code base.
-
-Many side-channel attacks originate
-in two code patterns: data flow from secrets to load
-addresses and data flow from secrets to branch conditions. We refer to them as
-secret-dependent data accesses and control flows, respectively.
 
@@
 
-We assume that an attacker shares the same hardware platform with the target.
-The attacker attempts to retrieve sensitive information through address-based
-side-channel attacks. The attacker has no direct access to the target's memory or cache,
-but it can probe its memory or cache at each program point. In reality, the
-attacker will face many possible obstacles such as the noisy observations 
-of the memory or cache. However, for this project, we assume
-the attacker has noise-free observations as in previous work~\cite{203878,182946,Brotzman19Casym}. 
-The threat model captures most cache-based and address-based side-channel attacks. 
-We only consider deterministic programs and assume an attacker 
-has access to the source code or binary executable of the target program.
+The threat model is similar to our previous work. That is, we assume 
+an attacker can share some hardware resource with the victim. The attacker has
+the ability to probe the victim at any time of the execution. We also assume 
+an attacker has noise-free observations. The attacker has the access to the victim's
+binary executable. The threat mode is similar to 
+the previous work~\cite{203878,182946,Brotzman19Casym} and can catch most of 
+the address-based side-channel attacks in the literature.
 
@@
     \centering
-\begin{lstlisting}[xleftmargin=.03\textwidth,xrightmargin=.01\textwidth]
+    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
 uint8_t key[2], t1, t2;
@@
     \caption{The distribution of observation}\label{shtable}
-    \vspace*{-0pt}
     %    \resizebox{\columnwidth}{!}{
@@
     \centering
-    \begin{lstlisting}[xleftmargin=.03\textwidth,xrightmargin=.01\textwidth]
+    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
 char key[9] = input();
@@
 in estimating the sensitive level of the vulnerability. However, the above
-methods all fail in real attack models. This is the first challenge we face
-\textbf{(Challenge C1)}.
-
+methods all fail in real attack models. 
 \begin{figure}
@@
 dynamic analysis.
+
+\subsubsection{Math Notations}
+We assume a program ($\beta$) has $K$ as its sensitive input. $K$ should be 
+a finite set of keys. The program also takes known messages $M$ as its input. 
+During an AES encryption, for example, 
+$\beta$ is the encryption function. $K$ is the set of all possible AES keys, 
+and $M$ represents the set consisting of all plaintext messages to be encrypted. In a real execution, an adversary may have 
+some observations ($O$) of the program. This paper only
+uses secret-dependent control flows and secret-dependent data 
+accesses as observations.
+
+With the above definition, we have the following mapping between $\beta$,
+$K$, $M$, and $O$:
+%\vspace*{-0pt}
+\begin{displaymath}
+    \beta(K, M) \rightarrow O
+\end{displaymath}
+
+We model a side-channel in the following way. An adversary does not have
+access to $K$, but he knows $\beta$, $M$, and $O$. For one execution of a
+deterministic program, once $k \in K$ and $m \in M$ are fixed, the observation
+($o \in O$) should also be determined. An attacker knows $\beta$, $o$,
+and $m$. The attacker wants to infer the value of $k$. We use $K^o$ to denote
+the set of possible $k$ values that produce the same observation: $K^o = \{ k \in K \, |\, \beta(k, m) \rightarrow o\}$
+
+Then the problem of quantifying the amount of leaked information can be
+restated as the following question:
+
+\emph{How much uncertainty of $K$ is reduced if an attacker knows $\beta$, $m$, and $o$?}
 

### 2021-04-04 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 
-\subsection{Theoretical Analysis}
+\subsection{Precise Analysis}
 Now we present our metric to quantify the amount of leaked information from
@@
 \end{table}
+
+\subsection{Model Leakages}
 \section{Approximate Model Counting}
@@
 According to
-Definition~\ref{def} introduced in \S\ref{sec:trace-qif},
+Definition~\ref{def} introduced in the previous section,
 the problem of quantifying the amount of leaked information can be reduced to
@@
     \centering
-    \includegraphics[width=0.45\textwidth]{./figures/chapter4/workflow.pdf}
+    \includegraphics[width=0.85\textwidth]{./figures/chapter4/workflow.pdf}
     \caption{The workflow of \tool{}.}
     \label{fig:workflow}
-    \vspace*{-15pt}
 \end{figure}

### 2021-04-04 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 
-\subsubsection{Math Notations}
 We assume a program ($\beta$) has $K$ as its sensitive input. $K$ should be 
@@
 contrast, an \emph{average} estimate based on random secret input information is around
-1 bit, as shown in \S\ref{sec:background_leak} and Table~\ref{shtable}, is
+1 bit, as shown in the previous section and Table~\ref{shtable}, is
 not very useful in practice as an attacker is able to get much more leaked
@@
 \section{Evaluation}
+\begin{table}[]
+    \centering\small\footnotesize
+    \caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks), 
+        Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF),
+        The number of instructions\,(\# Instructions), Symbolic Execution\,(SE) and Monte Carlo\,(MC) time.
+    }\label{table:over_result}
+
+%    \resizebox{1.9\columnwidth}{!}{
+    \begin{threeparttable}
+    \begin{tabular}{l@{}r@{~~}rrr@{~~}rr}
+        \hline
+        \textbf{Name}   & \textbf{\# Leaks} & \textbf{\# CF}         & \textbf{\# DF}
+                           & \textbf{\# Instructions}    & \textbf{SE} & \textbf{MC}                                                    \\\hline
+                                                 &                        &                     &                      &              & ms        & ms              \\\cline{6-7}
+        AES\tnote{1}               & 68                     & 0                   & 68                   & 39,855        & 512     & 1,052         \\
+        AES\tnote{2}                & 68                     & 0                   & 68                   & 39,855       & 520    & 1,057         \\
+        AES\tnote{4}                & 75                     & 0                   & 75                   & 1,704        & 231    & 9,199        \\
+        AES\tnote{5}                & 88                     & 0                   & 88                   & 1,350        & 36      & 1,924         \\
+        AES\tnote{6}                & 88                     & 0                   & 88                   & 1,350        & 35      & 1,961        \\
+        AES\tnote{7}                & 88                     & 0                   & 88                   & 1,420        & 36     & 2,161        \\
+        AES\tnote{8}                & 88                     & 0                   & 88                   & 1,586        & 43      & 1,631        \\
+        DES\tnote{1}                & 15                     & 0                   & 15                   & 4,596        & 58      & 162          \\
+        DES\tnote{2}                & 15                     & 0                   & 15                   & 4,596        & 57      & 162           \\
+        DES\tnote{4}                & 6                      & 0                   & 6                    & 2,976         & 163    & 4,677         \\
+        DES\tnote{5}                & 8                      & 0                   & 8                    & 2,593         & 166    & 6,509        \\
+        DES\tnote{6}                & 8                      & 0                   & 8                    & 2,593        & 165    & 5,975        \\
+        DES\tnote{7}                & 8                      & 0                   & 8                    & 4,260         & 182    & 5,292        \\
+        DES\tnote{8}                & 6                      & 0                   & 6                    & 8,272         & 229     & 5,152      \\
+                           &                        &                     &                      &                  & seconds   & seconds               \\\cline{6-7}
+        Chacha20\tnote{3}           & 0                      & 0                   & 0                    & 149,353        & 2     & 0             \\  
+        Poly1305\tnote{3}           & 0                      & 0                   & 0                    & 1,213,937      & 15    & 0             \\
+        Argon2i\tnote{3}            & 0                      & 0                   & 0                    & 4,595,142       & 37    & 0             \\
+        Ed25519\tnote{3}            & 0                      & 0                   & 0                    & 5,713,619       & 271   & 0            \\
+        ECDSA\tnote{1}              & 6                      &    6                & 0                    &  4,214,946     &  48   &   31       \\ 
+        ECDSA\tnote{2}              &   4                   &   4                 & 0                    &  4,192,558    & 102   & 1639          \\   
+        ECDSA\tnote{5}              &  5                    & 4                   & 1                    &  8,248,322       & 101     & 62           \\   
+        ECDSA\tnote{6}              &  5                    & 4                   & 1                    &  8,263,599      & 100     & 58            \\   
+        ECDSA\tnote{7}              &  5                    & 4                   & 1                    &  6,100,465       & 76      & 42                  \\  
+        ECDSA\tnote{8}              & 0                      &  0                   &    0               &  10,244,076       &  121     & 0                  \\  
+        ECDSA\tnote{9}              & 0                      &  0                   &  0                 &  9,266,191          & 102     & 59        \\
+
+                           &                        &                     &                      &                 & minutes   & minutes         \\\cline{6-7}
+        RSA\tnote{1}                & 6                       & 6                   & 0                    & 22,109,246    & 39     & 41           \\
+        RSA\tnote{2}                & 12                      & 12                  & 0                    & 24,484,441    & 44     & 251           \\
+        RSA\tnote{4}                & 107                    & 105                 & 2                    & 17,002,523   & 23      & 428           \\
+        RSA\tnote{5}                & 38                     & 27                  & 11                   & 14,468,307   & 29     & 436          \\
+        RSA\tnote{6}                & 36                     & 27                  & 9                    & 15,285,210   & 40     & 714          \\
+        RSA\tnote{7}                & 31                     & 22                  & 9                    & 16,390,750   & 34      & 490         \\
+        RSA\tnote{8}                & 4                      &  4                  & 0                    & 18,207,016   & 8      & 53          \\
+        RSA\tnote{9}                & 8                      &  8                  & 0                    & 18,536,796    & 5      & 780         \\
+        RSA\tnote{10} & 11& 9& 2& 9,527,231& 2 &38\\
+        RSA\tnote{11} & 14& 14& 0& 10,513,606& 14 &503 \\
+        RSA\tnote{12}               & 8                      &  8                  & 0                    & 27,407,986    & 113    & 6560       \\
+
+        Total              & 904                    & 241                 & 663                & 167,141,947      & 341m  & 10,232m     \\\hline
+    \end{tabular}
+\end{threeparttable}
+\begin{tablenotes}
+    \scriptsize
+
+    \item[1] mbedTLS\,2.5  ~~~~\item[2] mbedTLS\,2.15 ~\item[3] Monocypher\,3.0 \\
+    \item[4] OpenSSL\,0.9.7  ~~\item[5] OpenSSL\,1.0.2f  \item[6] OpenSSL\,1.0.2k \\
+    \item[7] OpenSSL\,1.1.0f ~\item[8] OpenSSL\,1.1.1 ~\item[9] OpenSSL\,1.1.1g \\
+    \item[10] Libgcrypt\,1.6.1 \item[11] Libgcrypt\,1.7.3 \item[12] Libgcrypt\,1.8.5\\
+\end{tablenotes}
+\vspace*{-20pt}
+
+\end{table}
+
+\subsection{Case Studies}
+
+\subsubsection{Symmetric Ciphers: DES and AES}\label{eval:sym}
+We test both DES and AES ciphers from mbedTLS and OpenSSL\@. Both cipher
+implementations apply lookup tables, which improve performance but can also introduce side-channels as well.
+During our evaluation, we find mbedTLS 2.5 and 2.15.1 have the same implementation of AES and DES\@.
+Therefore, our tool reports the same leakages for both versions.
+
+We find that the DES implementations in both mbedTLS and OpenSSL have several
+severe information leakages in the key schedule function.
+We do not see any mitigation
+in the new version. We think it is not seen as worth the engineering
+efforts given the life cycles of DES\@.
+
+\tool{} shows that the AES in OpenSSL 1.1.1 has less leakage than other versions. 
+OpenSSL 1.1.1 uses 1KB lookup tables with 8-bit entries, unlike older versions that use a table with 32-bit entries.
+Our tool suggests a smaller lookup table might mitigate side-channel vulnerabilities.
+
+\subsubsection{Monocypher}\label{eval:mono}
+Monocypher is a small, easy to use cryptographic library with
+performance comparable to LibSodium~\cite{libsodium} and NaCl~\cite{bernstein2012security}. 
+We choose four ciphers that are 
+designed to be side-channel resistant from the library.
+Because those ciphers have no 
+data flow from secrets to branch conditions and load addresses.
+Monocypher should be safe under our threat models. 
+We analyze those ciphers with \tool{}, and it reports no leaks.
+This indicates that \tool{} is effective for validating countermeasures.
 

### 2021-04-05 Chapter-4/Chapter-4.tex
update

@@
 \begin{mydef}
-    \label{def}
+    \label{chatper4:def}
     Given a program $\beta$ with the input set $K$,
@@
 According to
-Definition~\ref{def} introduced in the previous section,
+Definition~\ref{chapter4:def} introduced in the previous section,
 the problem of quantifying the amount of leaked information can be reduced to

### 2021-04-05 Chapter-4/Chapter-4.tex
update

@@
 \label{MCreasons}
-According to
-Definition~\ref{chapter4:def} introduced in the previous section,
+In the previous section, we propose an information leakage definition for
+realistic attack scenarios to model two types of address-based side-channel
+leakages and showed how to quantify them by calculating the number of input
+keys ($K^o$) that satisfy the formulas. Intuitively, we can use
+symbolic execution to capture math formulas and model counting
+to obtain the number of satisfying input keys ($K^o$). However, preliminary
+experiments showed that this approach was far too expensive to use with real-world
+applications. In this section, we discuss the bottlenecks in
+this approach and propose a practical solution.
+
+According to Definition~\ref{chapter4:def} introduced in the previous section,
 the problem of quantifying the amount of leaked information can be reduced to
@@
 \end{theorem}
-\vspace{-3pt}
 With Theorem~\ref{IndependentConstraint}, we change the problem of
@@
 
-%% \IncMargin{1em}
-%% \begin{algorithm}[h]
-%%       \DontPrintSemicolon
-%%       \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
-%%       \Input{$c_t(\addr{1},\addr{2},\ldots,\addr{n}) = c_{\addr{1}} \land c_{\addr{2}} \land \ldots \land c_{\addr{m}}$}
-%%       \Output{The Maximum Independent Partition of $G = \{g_{1}, g_{2}  , \ldots,  g_{m} \}$ }
-%%       \For{$i\leftarrow 1$ \KwTo $n$}
-%%       {
-%%             $S_{c_i}$ $\leftarrow$ $\pi(c_{\addr{i}})$ \;
-%%             \For{$g_{i} \in G$}
-%%             {
-%%                   $S_{g_i}$ $\leftarrow$ $\pi(g_{i})$ \;
-%%                   $S$ $\leftarrow$ $S_{C_i} \cap S_{G_i}$  \;
-%%                   \If{$S \neq \emptyset$}
-%%                   {
-%%                         $g_{i} \leftarrow g_{i} \land g_{\addr{i}}$ \;
-%%                         \textbf{break} \;
-%%                   }
-%%                   Insert $c_{\addr{i}}$ to $G$
-%%             }
-%%       }
-%%       \caption{The Maximum Independent Partition}
-%%       \label{algo:max-inde}
-%% \end{algorithm}
-%% \DecMargin{1em}
-
 \subsection{Multiple-step Monte Carlo Sampling}
@@
 significantly reduced by the previous step, this is still a \#P problem.
-For our
-project, we apply the approximate counting instead of exact counting for two
+For our project, we apply the approximate counting instead of exact counting for two
 reasons. First, we do not need to have a very precise result of the exact number of total solutions since the information is defined with a logarithmic function.
@@
 \DecMargin{1em}
-%% the algorithm
-%\IncMargin{1em}
-%\begin{algorithm}
-%\SetAlgoLined
-%\DontPrintSemicolon
-
-%\KwIn{{The constraint $G_{i}= C_{i_1} \land C_{i_2}
-%\land \ldots \land C_{i_m}$}}    
-%\KwOut{{The number of assignments that satisfy $G_{i}$ $|K_{G_{i}}|$}}
-
-%\SetKwProg{RW}{RandomWalk}{}{}
-%\SetKwProg{MM}{MetropolisMove}{}{} 
-%$n$: the number of sampling times \;
-%$P$: a probability generator \;
-%$k$: the input assignment \;
-%$n_{s}$: the number of satisfying assignments \;
-%$\#k$: the satisfying number of k \fixme{this number is not used syntactically} \; 
-%Initialization: \;
-%$\#{k_0}$ $\leftarrow$ $\sum_{j=1}^{m}C_{i_j}(k_0)$ \;
-%\For{$t\leftarrow 1$ \KwTo $n$} {
-%      $p$ $\leftarrow$ $P$ \;
-%      \If{$p \geq 0.5$}
-%      {
-%        $v$ $\leftarrow$ \RW{$v$} {}
-%      }
-%      \Else{
-%            $v$ $\leftarrow$ \MM{$v$} {}
-%      }
-%      \If{$v$ satisfies $G_{i}$}
-%      {$n_{s}$ $\leftarrow$ $n_{s} + 1$}
-%}
-%$|K_{G_{i}}|$ $\leftarrow$ $n_s|K| / n$
-%\caption{Metropolis Sampling}
-%\end{algorithm}
-%\DecMargin{1em}
 
@@
             RSA\tnote{9}      & 8                        & 8              & 0              & 18,536,796  & 5       & 780     \\
-        RSA\tnote{10} & 11& 9& 2& 9,527,231& 2 &38\\
-        RSA\tnote{11} & 14& 14& 0& 10,513,606& 14 &503 \\
+            RSA\tnote{10}     & 11                       & 9              & 2              & 9,527,231   & 2       & 38      \\
+            RSA\tnote{11}     & 14                       & 14             & 0              & 10,513,606  & 14      & 503     \\
             RSA\tnote{12}     & 8                        & 8              & 0              & 27,407,986  & 113     & 6560    \\

### 2021-04-05 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 \begin{mydef}
-    \label{chatper4:def}
+    \label{chapter4:def}
     Given a program $\beta$ with the input set $K$,
@@
 
-In
-contrast, an \emph{average} estimate based on random secret input information is around
-1 bit, as shown in the previous section and Table~\ref{shtable}, is
-not very useful in practice as an attacker is able to get much more leaked
+In contrast, an \emph{average} estimate based on random secret input information is around 1 bit, as shown in the previous section and Table~\ref{shtable}, is not very useful in practice as an attacker is able to get much more leaked
 information in some attack scenarios.
@@
 \label{MCreasons}
-In the previous section, we propose an information leakage definition for
-realistic attack scenarios to model two types of address-based side-channel
-leakages and showed how to quantify them by calculating the number of input
-keys ($K^o$) that satisfy the formulas. Intuitively, we can use
-symbolic execution to capture math formulas and model counting
-to obtain the number of satisfying input keys ($K^o$). However, preliminary
-experiments showed that this approach was far too expensive to use with real-world
-applications. In this section, we discuss the bottlenecks in
-this approach and propose a practical solution.
+In the previous section, we propose an information leakage definition for realistic attack scenarios to model two types of address-based side-channel leakages and showed how to quantify them by calculating the number of input keys ($K^o$) that satisfy the formulas.
+Intuitively, we can use symbolic execution to capture math formulas and model counting to obtain the number of satisfying input keys ($K^o$).
+However, preliminary experiments showed that this approach was far too expensive to use with real-world applications.
+In this section, we discuss the bottlenecks in this approach and propose a practical solution.
 
@@
 
-%\vspace*{2pt}
-%\textbf{Our Solution to Challenge C3:}
 We adopt multiple-step Monte Carlo sampling methods to count the number of
@@
 
-\subsection{Information Leakage Estimation}
-
 \newcommand{\addr}[1]{{l}_{#1}}
@@
 
-In this section, we present the algorithm to calculate the information leakage
-based on Definition~\ref{def} (\S\ref{sec:trace-qif}), answering to
-\textbf{Challenge C3}.
+In this section, we present the algorithm to calculate the information leakage based on Definition~\ref{chapter4:def}.
 
@@
 For each leakage site, we model it with a constraint using the
-method presented in~\S\ref{side-channel:condition}. Suppose the address of the
-leakage site is $\addr{i}$, we use $c_{\addr{i}}$ to denote the constraint
-that models its side-channel leakage.
-%For
-%multiple leakage sites, we take the conjunction of those constraints to
-%represent those leakage sites.
+method presented in the previous section.
+Suppose the address of the leakage site is $\addr{i}$, we use $c_{\addr{i}}$ to denote the constraint that models its side-channel leakage.
+For multiple leakage sites, we take the conjunction of those constraints to represent those leakage sites.
 
@@
           as $n$ grows.
-
           For example, if the program has $2$ input whose size is
@@
 \end{theorem}
-With Theorem~\ref{IndependentConstraint}, we change the problem of
-counting the number of solutions to a complicated constraint in a high-dimension
-space into counting solutions to several small constraints. We compute the
-maximum independent partition by iterating each $\addr{i}$ and applying the function
-$\pi$ over the constraint $\addr{i}$.
+With Theorem~\ref{IndependentConstraint}, we change the problem of counting the number of solutions to a complicated constraint in a high-dimension
+space into counting solutions to several small constraints. We compute the maximum independent partition by iterating each $\addr{i}$ and applying the function $\pi$ over the constraint $\addr{i}$.
 
@@
 
-After we split those constraints into several small constraints, we count the
-number of solutions for each constraint. Even though the dimension has been
+After we split those constraints into several small constraints, we count the number of solutions for each constraint. Even though the dimension has been
 significantly reduced by the previous step, this is still a \#P problem.
-For our project, we apply the approximate counting instead of exact counting for two
-reasons. First, we do not need to have a very precise result of the exact number of total solutions since the information is defined with a logarithmic function.
-We do not need to distinguish between constraints having $10^{10}$ or $10^{10}
-    10$ solutions; they are very close to after taking logarithmic. Second, the
+For our project, we apply the approximate counting instead of exact counting for two reasons.
+First, we do not need to have a very precise result of the exact number of total solutions since the information is defined with a logarithmic function.
+We do not need to distinguish between constraints having $10^{10}$ or $10^{10} + 10$ solutions; they are very close to after taking logarithmic.
+Second, the
 precise model counting approaches, like Davis-Putnam-Logemann-Loveland (DPLL)
@@
 We apply the ``counting by sampling'' method. For
-the constraint $g_{i}= c_{i_1} \land c_{i_2} \land ,\ldots, \land c_{i_j} \land
-    ,\ldots, \land c_{i_m}$, if the solution satisfies $g_{i}$, it should also
+the constraint $g_{i}= c_{i_1} \land c_{i_2} \land ,\ldots, \land c_{i_j} \land ,\ldots, \land c_{i_m}$, if the solution satisfies $g_{i}$, it should also
 satisfy any constraint from $c_{i_1}$ to $c_{i_m}$. In other words, $K_{c_gi}$
@@
 we only generate random input numbers for the other input variables in
-constraint $g_{i}$. With this simple yet effective trick, we reduce the number of input
-while still ensuring accuracy.
+constraint $g_{i}$. With this simple yet effective trick, we reduce the number of input while still ensuring accuracy. The detailed of the algorithm is shown in Algorithm~\ref{chapter4:alg2}.
 
@@
     $|K_{g_{i}}|$ $\leftarrow$ $n_s|K| / (n * r * range(k))$
-    \caption{Multiple Step Monte Carlo Sampling}
+    \caption{Multiple Step Monte Carlo Sampling}\label{chapter4:alg2}
 \end{algorithm}
@@
 We treat secrets as symbols ($S$).
-For other variables, we use concrete values ($C$)
-from the execution.
+For other variables, we use concrete values ($C$) from the execution.
 We do not know which instruction may manipulate a secret until we execute it.
@@
 
-\subsection{Leakage estimation} We change the information leakage
-quantification problem into the counting problem. We propose a
-Monte Carlo method to estimate the number of satisfying solutions.
-With the help of the Central Limit Theorem (CLT), we also give an error
+\subsection{Leakage estimation} 
+We change the information leakage quantification problem into the counting problem. We propose a
+Monte Carlo method to estimate the number of satisfying solutions. With the help of the Central Limit Theorem (CLT), we also give an error
 estimate with the probability, which provides us with the \emph{precision guarantee}.
 
-\tool{} consists of 16,729 lines of code in C++17 and Python. It has three
-components: an Intel Pin tool that collects the execution trace, the
-instruction-level symbolic execution engine, and the back-end that estimates
-the information leakage.
+\tool{} consists of 16,729 lines of code in C++17 and Python. It has three components: an Intel Pin tool that collects the execution trace, the
+instruction-level symbolic execution engine, and the back-end that estimates the information leakage. Table~\ref{tbl:implementation} shows the breakdown of the implementation of \tool{}.
 
@@
 
-Our current implementation supports most Intel 32-bit instructions that are essential to find address-based side-channel
-vulnerabilities, including bitwise operations, control transfer, data movement, and logic
-instructions. The tool uses the real values to update the registers and memory for instructions that the implementation does not support.
+Our current implementation supports most Intel 32-bit instructions that are essential to find address-based side-channel vulnerabilities, including bitwise operations, control transfer, data movement, and logic instructions.
+The tool uses the real values to update the registers and memory for instructions that the implementation does not support.
 Therefore, the tool may miss some leakages but will not raise false positives.
@@
 \begin{table}[]
-    \centering\small\footnotesize
+    \centering
+    \small
     \caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks),
@@
     \begin{threeparttable}
-        \begin{tabular}{l@{}r@{~~}rrr@{~~}rr}
+    \renewcommand\TPTminimum{\linewidth}
+   % \captionsetup{font=small}
+    \makebox[\linewidth]{
+        \begin{tabular}{lrrrrrr}
             \hline
             \textbf{Name}     & \textbf{\# Leaks}        & \textbf{\# CF} & \textbf{\# DF}
-                              & \textbf{\# Instructions} & \textbf{SE}    & \textbf{MC}                                      \\\hline
+                              & \textbf{\# Instructions} & \textbf{Detection}    & \textbf{Quantification}                                      \\\hline
                               &                          &                &                &             & ms      & ms      \\\cline{6-7}
@@
             Total             & 904                      & 241            & 663            & 167,141,947 & 341m    & 10,232m \\\hline
-        \end{tabular}
+        \end{tabular}}
     \end{threeparttable}
@@
 
-        \item[1] mbedTLS\,2.5  ~~~~\item[2] mbedTLS\,2.15 ~\item[3] Monocypher\,3.0 \\
-        \item[4] OpenSSL\,0.9.7  ~~\item[5] OpenSSL\,1.0.2f  \item[6] OpenSSL\,1.0.2k \\
+        \item[1] mbedTLS\,2.5  \,~~~~~\item[2] mbedTLS\,2.15 ~\item[3] Monocypher\,3.0 \\
+        \item[4] OpenSSL\,0.9.7  ~~~\item[5] OpenSSL\,1.0.2f  \item[6] OpenSSL\,1.0.2k 
         \item[7] OpenSSL\,1.1.0f ~\item[8] OpenSSL\,1.1.1 ~\item[9] OpenSSL\,1.1.1g \\
-        \item[10] Libgcrypt\,1.6.1 \item[11] Libgcrypt\,1.7.3 \item[12] Libgcrypt\,1.8.5\\
+        \item[10] Libgcrypt\,1.6.1 ~\item[11] Libgcrypt\,1.7.3 \item[12] Libgcrypt\,1.8.5\\
     \end{tablenotes}
@@
 
+\subsection{Overview}
+
 \subsection{Case Studies}
@@
 \subsubsection{Symmetric Ciphers: DES and AES}\label{eval:sym}
-We test both DES and AES ciphers from mbedTLS and OpenSSL\@. Both cipher
-implementations apply lookup tables, which improve performance but can also introduce side-channels as well.
+We test both DES and AES ciphers from mbedTLS and OpenSSL\@.
+Both cipher implementations apply lookup tables, which improve performance but can also introduce side-channels as well.
 During our evaluation, we find mbedTLS 2.5 and 2.15.1 have the same implementation of AES and DES\@.
@@
 
-We find that the DES implementations in both mbedTLS and OpenSSL have several
-severe information leakages in the key schedule function.
-We do not see any mitigation
-in the new version. We think it is not seen as worth the engineering
-efforts given the life cycles of DES\@.
+We find that the DES implementations in both mbedTLS and OpenSSL have several severe information leakages in the key schedule function. We do not see any mitigation
+in the new version. We think it is not seen as worth the engineering efforts given the life cycles of DES\@.
 
@@
 Our tool suggests a smaller lookup table might mitigate side-channel vulnerabilities.
+
+\subsubsection{Asymmetric Ciphers: RSA}\label{eval:asym}
+
+\begin{figure*}
+    \centering
+    \vspace*{-9pt}
+    \hspace*{-15pt}
+    \subfloat[OpenSSL 0.9.7]{
+        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-0-9-7.pdf}
+        \label{fig:rsa-1}
+    }
+    \subfloat[OpenSSL 1.0.2f]{
+        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-0-2f.pdf}
+        \label{fig:rsa-2}
+    }
+    \subfloat[OpenSSL 1.0.2k]{
+        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-0-2k.pdf}
+        \label{fig:rsa-3}
+    }
+        \hfill
+
+    \subfloat[OpenSSL 1.1.0f]{
+        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-1-0f.pdf}
+        \label{fig:rsa-4}
+    }
+    \subfloat[OpenSSL 1.1.1]{
+        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-1-1.pdf}
+        \label{fig:rsa-5}
+    }
+    \subfloat[OpenSSL 1.1.1g]{
+        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-1-1g.pdf}
+        \label{fig:rsa-6}
+    }
+    \caption{Side-channel leakages in different implementations of RSA in OpenSSL\@. 
+        We round the number of leaked information into the nearest integer. 
+        The mark $*$ means timeout.}
+    \label{fig:rsa}
+\end{figure*}
+We also evaluate \tool{} on RSA. Due to the page limit,
+we do not present the detailed leakage report. %, which is available online at the tool release website.
+%% \jl{where?}. In general,
+%% developers are interested in fixing side-channel vulnerabilities for the RSA implementations.
+%% \jl{Then maybe find some space to present these results?}
+ As shown in Figure~\ref{fig:rsa}, the result indicates that the newer
+versions of OpenSSL leak less information than earlier
+versions. After version 0.9.7g, OpenSSL adopts a fixed-window \textsf{mod\_exp\_mont}
+implementation for RSA\@. With this design, the sequence of squares and
+multiples and the memory access patterns are independent of the secret key.
+\tool{}'s result confirms the new exponentiation implementation has mitigated 
+most leakages effectively because the four newer versions have fewer
+leakages than version 0.9.7, which introduced this change.
+OpenSSL version 1.0.2f, 1.0.2k, and 1.1.0f almost have the
+same amount of leakage. We check the ChangeLog and find only one change to
+patch vulnerability CVE-2016-0702. 
+\tool{} finds OpenSSL 1.1.1 and 1.1.1g have significantly less
+leaked information than other versions.
+We check the ChangeLog of these two versions and find a claim that
+the new RSA implementation adopts ``numerous side-channel attack mitigation'', 
+which proves the effectiveness of our quantifying method.
+%We also observe the latest version (1.1.1g) contains some new leakages. We have
+%contacted the developers and they have confirmed our findings.
+
+Our quantification result shows vulnerabilities
+that leak significant amounts of information
+are more likely to be fixed in the updated version.
+As presented in Figure~\ref{fig:rsa}, 
+OpenSSL 0.9.7 has several severe leaks from
+function \textsf{bn\_sqr\_comba8}, which is a main 
+component of the OpenSSL big number implementation.
+Shown in Figure~\ref{fig:old_sqr2}, it has a 
+secret-dependent control flow at line 8.
+The value of the function parameter \textbf{a} is derived from
+the secret key. 
+As function \textsf{bn\_sqr\_comba8}
+calls the macro (\textsf{sqr\_add\_c2}) multiple times, 
+and the code can leak some information each time.
+\tool{} indicates the vulnerability is quite serious. 
+It was patched in OpenSSL 1.1.1\@. In 
+Figure~\ref{fig:new_sqr2}, control-flows transfers are replaced
+so there are no leaks in the function
+\textsf{sqr\_add\_c2} in OpenSSL 1.1.1\@. We note
+that line 4 and 9 in Figure~\ref{fig:old_sqr2} both contain if branches.
+However, they are not leaks because
+most compilers use \emph{add with carry} instruction to eliminate the branch.
+In addition, branches can be compiled into non-branch machine instructions 
+with conditional moves. 
+We notice a bitwise operation in Libgcrypt 1.8.5 is compiled to a conditional 
+jump, which leads to a side-channel leakage.
+Therefore, source-level code reviews are not accurate
+enough to detect side-channels.
+
+For vulnerabilities that leak less amount of information,
+developers are more reluctant to fix them or fixing them unintentionally.
+For example, OpenSSL 0.9.7 adds a fixed windows version of function \textsf{BN\_mod\_exp\_mont\_consttime} to replace original function \textsf{BN\_mod\_exp\_mont}.
+\tool{} detects a minor vulnerability in the original function that can leak the last bit of the big number \textbf{m}.
+In the updated version, developers make the fixed windows the default option and rewrite most of the function.
+However, the leakage site still exists in OpenSSL 1.1.1.
+\begin{figure}
+    \centering
+    \begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
+# define mul_add_c2(a,b,c0,c1,c2)                    \
+    t=(BN_ULLONG)a*b;                                \
+    tt=(t+t)&BN_MASK;                                \
+    if (tt < t) c2++;                                \
+    t1=(BN_ULONG)Lw(tt);                             \
+    t2=(BN_ULONG)Hw(tt);                             \
+    c0=(c0+t1)&BN_MASK2;                             \
+    if ((c0 < t1) && (((++t2)&BN_MASK2) == 0)) c2++; \
+    c1=(c1+t2)&BN_MASK2; if ((c1) < t2) c2++;
+\end{lstlisting}
+    \vspace*{-6pt}
+    \caption{Macro \textsf{sqr\_add\_c2} in OpenSSL 0.9.7}
+    \label{fig:old_sqr2}
+    \vspace*{-8pt}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
+# define mul_add_c2(a,b,c0,c1,c2)      do { \
+    BN_ULONG ta = (a), tb = (b);            \
+    BN_ULONG lo, hi, tt;                    \
+    BN_UMULT_LOHI(lo,hi,ta,tb);             \
+    c0 += lo; tt = hi+((c0<lo)?1:0);        \
+    c1 += tt; c2 += (c1<tt)?1:0;            \
+    c0 += lo; hi += (c0<lo)?1:0;            \
+    c1 += hi; c2 += (c1<hi)?1:0;            \
+    } while(0)
+\end{lstlisting}
+    \vspace*{-6pt}
+    \caption{Macro \textsf{sqr\_add\_c2} in OpenSSL 1.1.1}
+    \label{fig:new_sqr2}
+    \vspace*{-10pt}
+\end{figure}
 
@@
 the amount of leakage for some leakage sites in a reasonable time,
-which means the number of $K^o$ is very small. According to Definition~\ref{def},
-it means the leakage is very severe. The sampling method in \S\ref{sec:scala} seems
-simple and may miss some leakages (e.g., chosen ciphertext attacks) in theory.
-However, the evaluation result
-shows \tool{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.
+which means the number of $K^o$ is very small. According to Definition~\ref{def}, it means the leakage is very severe.

### 2021-04-05 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 
+During our evaluation, we find mbed TLS 2.5 and 2.15.1 have the same
+implementation of AES\@. Our tool provides the same leakage report for both
+versions. \tool{} identifies that most leakages are in function
+\emph{mbedtls\_internal\_aes\_decrypt}. (Other leakage sites are in function
+\emph{mbedtls\_aes\_setkey\_enc}.) All leakages are caused by secret-dependent
+memory accesses. Shown in Figure~\ref{mbedtls_aes}, there are seven leakage
+sites in total. Leakage 1, 2, 3 are the same and leakage 4, 5, 6, 7 are the
+same. They both use a pre-computed lookup table to speed up computation.
+However, \tool{} reports leakage 1, 2, 3 typically leak more information
+compared to leakage 4, 5, 6, 7. We check the source code and find leakage 1, 2,
+3 use secret to access the lookup table \emph{RT0, RT1, RT2, RT3}, which is 8K
+each. On the contrary, leakage 4, 5, 6, 7 each accesses a smaller lookup table
+(2K). Therefore, leakage 4, 5, 6, 7 leak less information.
+
+\begin{figure}%[h!]
+    \centering
+    \begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
+int mbedtls_internal_aes_encrypt( mbedtls_aes_context *ctx,
+const unsigned char input[16],
+unsigned char output[16] )
+{
+uint32_t *RK, X0, X1, X2, X3, Y0, Y1, Y2, Y3;
+...
+for( i = ( ctx->nr >> 1 ) - 1; i > 0; i-- )
+{
+    AES_FROUND( Y0, Y1, Y2, Y3, X0, X1, X2, X3 ); // Leakage 1
+    AES_FROUND( X0, X1, X2, X3, Y0, Y1, Y2, Y3 ); // Leakage 2
+}
+AES_FROUND( Y0, Y1, Y2, Y3, X0, X1, X2, X3 );     // Leakage 3
+X0 = *RK++ ^ \                                    // Leakage 4
+    ( (uint32_t) FSb[ ( Y0       ) & 0xFF ]       ) ^
+    ( (uint32_t) FSb[ ( Y1 >>  8 ) & 0xFF ] <<  8 ) ^
+    ( (uint32_t) FSb[ ( Y2 >> 16 ) & 0xFF ] << 16 ) ^
+    ( (uint32_t) FSb[ ( Y3 >> 24 ) & 0xFF ] << 24 );
+// X1, X2, X3 do the same computation as X0
+...                                           // Leakage 5,6,7
+PUT_UINT32_LE( X0, output,  0 );
+...
+return( 0 );
+}
+\end{lstlisting}
+    \caption{Function \textit{mbedtls\_internal\_aes\_encrypt}}
+    \label{mbedtls_aes}
+\end{figure}
+
 \subsubsection{Asymmetric Ciphers: RSA}\label{eval:asym}
@@
 \end{lstlisting}
-    \vspace*{-6pt}
 \caption{Macro \textsf{sqr\_add\_c2} in OpenSSL 1.1.1}
 \label{fig:new_sqr2}
-    \vspace*{-10pt}
 \end{figure}
@@
 
+\subsection{Analysis of Software Countermeasures}\label{sec:eval_countermeasures}
+\subsubsection{Bit-slicing}
+Bit-slicing is an efficient method to construct constant-time implementation for side channel to mitigation.
+The basic concept is to implement a function in terms of single-bit logical gate operations, such as AND, XOR, OR, and NOT\@.
+
+Since the table look-ups and conditional jumps are replaced with single-bit logical gates, with no secret-dependent memory addresses or control flow, both the data access and control flow types of side-channel leakages are mitigated.
 \section{Discussion}

### 2021-04-05 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 Since the table look-ups and conditional jumps are replaced with single-bit logical gates, with no secret-dependent memory addresses or control flow, both the data access and control flow types of side-channel leakages are mitigated.
+\begin{figure}[h!]
+    \centering
+    \begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
+uint8_t password = input();
+
+uint8_t SBOX[] = {1, 0, 3, 1, 2, 2, 3, 0};
+
+if (password <= 0b111)      \\Leaks 5 bits of password
+    ret = SBOX[password];   \\Leaks 4 bits of password
+      \end{lstlisting}
+    \caption{SBOX without BitSlicing}
+    \label{fig:SBOX_da}
+\end{figure}
+
+\begin{figure}[h!]
+    \centering
+    \begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
+uint8_t password = input();
+
+a = *password & 0b001;
+b = (*password & 0b010) >> 1;
+c = (*password & 0b100) >> 2;
+
+na = ~a & 1;
+nb = ~b & 1;
+nc = ~c & 1;
+
+t0 = (b & nc);
+t1 = (b | nc);
+
+l = (a & nb) | t0;
+r = (na & t1) | t0;
+
+ret = l << 1 + r;
+\end{lstlisting}
+\caption{SBOX with BitSlicing}
+\label{fig:SBOX_bitslicing}
+\end{figure}
+We test \tool\ on bit-slicing. We adopt the SBOX
+implementations, commonly used in block ciphers such as DES and AES, with and
+without bit-slicing, and apply \tool{} to confirm the mitigation.
+The SBOX implementation with and without bit-slicing are shown in Figure~\ref{fig:SBOX_bitslicing} and Figure~\ref{fig:SBOX_da}, respectively.
+Considering an SBOX take some bits derived from a password as input and output 2-bit transform result, the plain implementation
+has a range check on the password input and a secret-dependent table lookup while bit-slicing does not.
+
+\tool\ reports that there are control-flow and data access types of leakages
+in the non-bit-slicing implementation (line 6 and line 7 in Figure~\ref{fig:SBOX_da}). The number of leaked bits is
+5.0 and 4.4, respectively. At line 6, according to Definition~\ref{def}, the
+input set $K$ is $[0,2^8-1]$, the observed input set $K^o$ is $[0,2^3-1]$. Thus,
+the leakage $L_{\beta(k)\rightarrow o}$ based on the observation ($o$) is
+$L_{\beta(k)\rightarrow o} = \log_2{|K|} - \log_2{|K^o|} = 8-3 = 5$ bit, which
+confirms the result from \tool. Similarly, we can verify the result of the other
+leakage site. \tool{} reports no leakage on the bit-slicing implementation.
+
+\subsubsection{Smaller Lookup Tables}
+\begin{figure}[h!]
+    \centering
+    \begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
+static const uint8_t T[16] = {
+      0x63U, 0x7cU, 0x77U, 0x7bU, 0xf2U, 0x6bU, 0x6fU, 0xc5U,
+      0x30U, 0x01U, 0x67U, 0x2bU, 0xfeU, 0xd7U, 0xabU, 0x76U};
+      \end{lstlisting}
+    \caption{One-byte Entry Lookup Table}
+    \label{fig:one_byte_table}
+\end{figure}
+
+\begin{figure}[h!]
+    \centering
+    \begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
+static const uint32_t T[16] = {
+    0xc66363a5U, 0xf87c7c84U, 0xee777799U, 0xf67b7b8dU,
+    0xfff2f20dU, 0xd66b6bbdU, 0xde6f6fb1U, 0x91c5c554U,
+    0x60303050U, 0x02010103U, 0xce6767a9U, 0x562b2b7dU,
+    0xe7fefe19U, 0xb5d7d762U, 0x4dababe6U, 0xec76769aU};
+    \end{lstlisting}
+
+    \caption{Four-byte Entry Lookup Table}
+    \label{fig:four_byte_table}
+\end{figure}
+\begin{figure}[h!]
+    \centering
+    \begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
+void encrypt_one(uint32_t *o, uint32_t *key, uint32_t l) {
+    for (int i = 0; i < l; i+=4)
+        output[i] = (T[(key[i]>>24)] << 24) ^
+                    (T[(key[i+1]>>16) & 0xff] << 16) ^
+                    (T[(key[i+2]>>8) & 0xff] << 8) ^
+                    (T[(key[i+3]) & 0xff]);
+}
+    \end{lstlisting}
+    \caption{Encrypt with One-byte Entry Lookup Table}
+    \label{fig:one_byte_table_lookup}
+\end{figure}
+
+\begin{figure}[h!]
+    \centering
+    \begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
+void encrypt_four(uint32_t *o, uint32_t *key, uint32_t l) {
+    for (int i = 0; i < l; i+=4)
+        output[i] = (T[(key[i]>>24)] & 0xff000000) ^
+                    (T[(key[i+1]>>16) & 0xff] & 0x00ff0000) ^
+                    (T[(key[i+2]>>8) & 0xff] & 0x0000ff00) ^
+                    (T[(key[i+3]) & 0xff] & 0x000000ff);
+}
+    \end{lstlisting}
+    \caption{Encrypt with One-byte Entry Lookup Table}
+    \label{fig:four_byte_table_lookup}
+\end{figure}
+
+Considering the cache-collision timing attack~\cite{Bonneau11894063_16}, the
+probability of leakage decreases when the lookup table entry or element size gets
+smaller. We take AES as an example, for the last round of encryption, the algorithm
+uses a specialized table with 4-byte size entries, of which only one
+byte from each element actually contributes to the result. Hence, a significant method to reduce
+the information leakage in AES is to reduce the size of the lookup table. We
+designed a demo to illustrate this countermeasure, a lookup table with one-byte
+size elements (see Figure~\ref{fig:one_byte_table}) will leak less information
+than a table with 4-byte element size (see Figure~\ref{fig:four_byte_table}). 
+The encrypt function for each table to process the same amount of information, 
+respectively, (see Figure~\ref{fig:one_byte_table_lookup} and
+Figure~\ref{fig:four_byte_table_lookup}).  \tool{} reports three leakage sites for
+each lookup table, with 4.0 bits for the table with smaller entries and 2.0
+bits for the table with bigger entries, confirming the theory.
+
 \section{Discussion}

### 2021-04-05 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
         The number of instructions\,(\# Instructions), Symbolic Execution\,(SE) and Monte Carlo\,(MC) time.
-    }\label{table:over_result}
+    }\label{chapter4:table:over_result}
 
@@
 \subsection{Overview}
+In this section, we evaluate \tool{} on a series of popular crypto libraries.
+In particular, we are interested in following aspects:
+\begin{itemize}
+\item Can \tool{} precisely report the number of leaked bits in crypto
+          libraries? 
+\item Are the numbers of leaked bits reported by \tool{} useful
+          to justify the severity levels of the side-channel vulnerabilities?
+\end{itemize}
+
+Our testbed is comprised of several popular cryptography libraries. We choose them based
+on the following aspects. First, they should be widely used in many popular software.
+In general, it is hard to implement a secure cryptography library from scratch. So most
+software only use a few number of different cryptography libraries. Second, we choose some
+libraries which are well studied in the previous work. We can refer to those conslusions to
+verify our results. Based on the two requirements, we evaluate \tool{} on the following libraries:
+OpenSSL, Libgcrypt, mbedTLS, Monocypher. OpenSSL, Libgcrypt, and mebdTLS are the most widely used
+cryptography libraries. OpenSSL and mbedTLS have been widely studied in the previous research.
+Monocyper is designed to be side-channel resistant. We use the library to test if our tool has any
+false positives. Besides, we also test \tool{} on some simple countermeasure implementations.
+
+We write simple encryption and decryption function with the above libraries. After that, we build
+the source code into 32-bit binary executions. The configuration of our experiment is shown as
+\begin{itemize}
+\end{itemize}
+follows.
+\begin{itemize}
+\item CPU: 2.90GHz Intel Xeon(R) E5-2690 CPU
+\item Memory: 128 GB
+\item OS: Ubuntu 18.04 LTS
+\item Compiler: GCC 7.5
+\end{itemize}
 

### 2021-04-05 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 We write simple encryption and decryption function with the above libraries. After that, we build
-the source code into 32-bit binary executions. The configuration of our experiment is shown as
-\begin{itemize}
-\end{itemize}
-follows.
+the source code into 32-bit binary executions. The configuration of our experiment is shown as follows.
 \begin{itemize}
@@
 \end{itemize}
+
+Table~\ref{chapter4:table:over_result} shows the overview of evaluation results. 
+\tool{} also finds that most side-channel
+vulnerabilities leak very little information in practice, which confirms our
+initial assumption.  
+However, \tool{} finds some vulnerabilities with severe
+leakages. Prior research has confirmed that some of these
+vulnerabilities can be exploited in real attacks.
+With our tool, developers can
+distinguish non-critical ``vulnerabilities'' from severe ones.
+
+Symmetric encryption implementations in OpenSSL and mbedTLS have significant leakage due to their lookup table implementations. 
+\tool{} confirms that those leakage comes from table lookups.
+The new implementation of OpenSSL has adopted several methods (e.g., one single S-box instead of four lookup tables, smaller lookup tables) to mitigate the problem.
+Those changes are rather easy but significantly decrease the total amount of leaked information as the quantification result indicates.
+
+\tool{} can estimate how
+much information is leaked from each vulnerability. During the evaluation,
+for each leakage site, \tool{} will stop once 1) it has 95\% confidence
+that the error of the estimated leaked information is less than 1 bit,
+which gives the leakage quantification a \emph{precision guarantee}, 
+or 2) it cannot reach the termination condition after 10 minutes.  In
+the latter case, it means \tool{} cannot estimate the amount of leakage with a
+probabilistic guarantee. We manually check these leakage sites and find most of them are quite severe.
+We will present the details in the subsequent sections.
 

### 2021-04-05 Chapter-1/Chapter-1.tex
update
Updates from Overleaf

@@
 \section{Side-channels}
-Side channels are ubiquitous in modern computer systems as sensitive
-information can leak through many mechanisms such as power,
-electromagnetic radiation, and even sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}.
-It is typically hard to fix all side-channel vulnerabilities for real-world software systems.
+Side channels are ubiquitous in modern computer systems as sensitive information can leak through many mechanisms such as power, electromagnetic radiation, and even sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}.
+It is typically hard to fix side-channel vulnerabilities for real-world software systems.
 Among them, software side-channel attacks, such as cache attacks, memory page attacks, and controlled-channel attacks, are especially problematic as they do not require physical proximity~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}.
@@
 
-The key intuition is that above side-channel attacks happen when a
-program accesses different memory addresses if the program has different
-sensitive inputs. As shown in Figure~\ref{fig:secret:cf} and Figure~\ref{fig:secret:da}, 
-if a program shows different patterns in
-control transfers or data accesses when the program processes different
-sensitive inputs, the program could possibly have side channels vulnerabilities.
-Different kinds of side-channels can be exploited to retrieve information in
-various granularities. For example, cache channels can observe cache
-accesses at the level of cache sets~\cite{liu2015last}, cache lines~\cite{184415} or other granularities. 
-Other kinds of side-channels like controlled-channel attack~\cite{7163052},
-can observe the memory access at the level of memory pages.
+The key intuition is that above side-channel attacks happen when a program accesses different memory addresses if the program has different sensitive inputs.
+As shown in Figure~\ref{fig:secret:cf} and Figure~\ref{fig:secret:da}, if a program shows different patterns in control transfers or data accesses when the program processes different sensitive inputs, the program could possibly have side channels vulnerabilities.
+Different kinds of side-channels can be exploited to retrieve information in various granularities.
+For example, cache channels can observe cache accesses at the level of cache sets~\cite{liu2015last}, cache lines~\cite{184415} or other granularities.
+Other kinds of side-channels like controlled-channel attack~\cite{7163052}, can observe the memory access at the level of memory pages.
 
-Various countermeasures have been proposed to defend against
-side channel attacks. Hardware-level solutions, such as reducing shared
-resources, adopting oblivious RAM, and using transnational
-memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need new
-hardware features and changes in modern complex computer systems, which are
-hard to adopt in reality.
-Therefore, a promising and universal direction is software countermeasures, detecting and eliminating side channel vulnerabilities from code base.
-It is due to the following reason: many side-channel attacks originate in two code patterns: data flow from secrets to load addresses and data flow from secrets to branch conditions.
-We refer to them as secret-dependent data accesses and control flows respectively in the dissertation.
-
-On the contrary, software approaches are
-usually easy to implement. The basic idea is to eliminate key-dependent
-control-flow transfers and data accesses. By removing the above two kinds of code patterns, developers protect their 
-code from a series of side-channel attacks.
+Various countermeasures have been proposed to defend against side channel attacks.
+Hardware-level solutions, such as reducing shared resources, adopting oblivious RAM, and using transnational memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need new hardware features and changes in modern complex computer systems, which are hard to adopt in reality.
+Therefore, a promising and universal direction is software countermeasures, detecting and eliminating side channel vulnerabilities (data flow from secrets to load addresses, and data flow from secrets to branch conditions) from code base.
 
@@
 First, some vulnerable implementations perform better.
-For example, RSA implementations usually adopt the CRT optimization,
-which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}. Fixing vulnerabilities can introduce new 
-weaknesses.
+For example, RSA implementations usually adopt the CRT optimization, which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}.
+Fixing vulnerabilities can introduce new weaknesses.
 Second, it is hard to detect side channels in reality.
 While recent work~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} can detect many side-channel vulnerabilities, they either suffer from expensive computation cost or high false positives and false negatives.
-Recent work~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} can detect many side-channel vulnerabilities.
 For example, DATA~\cite{217537} reports 2,248 potential leakage sites for the RSA implementation in OpenSSL 1.1.0f\@.
@@
 Third, most vulnerabilities pose a negligible risk.
-Although some vulnerabilities result in the key being 
-entirely compromised~\cite{184415, aumuller2002fault}, 
-many others are less severe in reality. Therefore, we need a proper quantification metric to assess the sensitivity of side-channel vulnerabilities, so a developer can efficiently triage them.
-
-Previous work~\cite{182946,5207642} can identify numerous leakages or even provide an upper bound on the amount of leakage, which is useful to verify that an implementation is secure if it incurs zero leakage.
-However, these techniques cannot quantify the severity of a leak because they over approximate the leakage. For example, CacheAudit~\cite{182946} 
-reports that the upper-bound leakage of AES-128 exceeds the original key size.
-Besides, existing side-channel quantification work~\cite{182946,5207642} assumes an attacker runs the target program multiple times with different
-input secrets and calculates an ``average'' estimation, which is different from real attack scenarios when the secret that an attacker wants to retrieve is fixed.
-As a consequence, those results are less useful to assess the severity level of each leakage site.
+Although some vulnerabilities result in the key being entirely compromised~\cite{184415, aumuller2002fault}, many others are less severe in reality.
+Therefore, we need a proper quantification metric to assess the sensitivity of side-channel vulnerabilities, so a developer can efficiently triage them.
 
@@
 Symbolic execution provides fine-grained information, but it is expensive to compute.
-Therefore, prior symbolic
-execution work~\cite{203878,236338,Brotzman19Casym} either analyzes only
-small programs or applies domain knowledge~\cite{203878} to simplify the analysis.
-We examine the bottleneck of the trace-oriented symbolic execution and optimize it to work for real-world crypto-systems.
-\item \textbf{Quantification.} We propose methods to quantify information 
-leakage precisely from a single trace attack.
+Therefore, prior symbolic execution work~\cite{203878,236338,Brotzman19Casym} either analyzes only small programs or applies domain knowledge~\cite{203878} to simplify the analysis.
+We examine the bottleneck of the trace-oriented symbolic execution and optimize it to work for real-world applications.
+    \item \textbf{Quantification.} We propose methods to quantify information leakage precisely from a single trace attack.
 We quantify the number of bits that can leak during a real execution and define the amount of leaked information as the cardinality of possible secrets based on an attacker's observation.
@@
 Whenever the adversary observes a leakage site, they can eliminate some impossible inputs and reduce the input space's size.
-In an extreme case, if the input space's size reduces to one, an adversary has determined the input, which means all secret information (e.g., the entire secret key) is
-leaked. By counting the number of inputs~\cite{10.1007/11499107_24}, we can quantify the information leakage precisely. We use symbolic execution to generate constraints to model the relation 
-between the original sensitive input and an attacker's observations. 
+In an extreme case, if the input space's size reduces to one, an adversary has determined the input, which means all secret information (e.g., the entire secret key) is leaked.
+By counting the number of inputs~\cite{10.1007/11499107_24}, we can quantify the information leakage precisely.
+We use symbolic execution to generate constraints to model the relation between the original sensitive input and an attacker's observations.
 \end{enumerate}
@@
 \section{Contribution}
-We address above problems from two aspects.
+This dissertation makes the following contributions.
 First, we propose a novel method that can detect side-channel vulnerabilities in real-world applications automatically fast and precisely.
 Second, we propose methods that can quantify each side-channel leakages precisely.
-In addition, we study two kinds of threat models, single-trace attacks, and chosen message attacks.
+In addition, we study two kinds of threat models, single-trace attacks, and multiple-trace attacks.
 In summary, we make the following contributions:
@@
 The key idea is to only symbolically execute those machine instructions that are relevant to vulnerabilities while executing other instructions natively.
-    \item We implement the above method in a tool called ~\detect{}.
-The evaluation results shows that ~\detect{}  is 3 to 100 times faster than existing tools while identifying all vulnerabilities when we run it on the same library.
+    \item We implement the above method in a tool called \detect{}.
+The evaluation results shows that \detect{}  is 3 to 100 times faster than existing tools while identifying all vulnerabilities when we run it on the same library.
 We do not need to apply domain knowledge to only part of the original program, which simplify the analysis.
-In addition, ~\detect{} yields new leakages which are not identified by previous tools.
+In addition, \detect{} yields new leakages which are not identified by previous tools.
 We confirm those findings with developers.
@@
 Chapter~\ref{chapter4} presents a method that can quantify each side-channel leakage in a single trace attack.
-Chapter~\ref{chapter5} extends the approach and quantifies the side-channel leakage in chosen message attacks.
-Chapter~\ref{chapter6} concludes the thesis.
+Chapter~\ref{chapter5} extends the approach and quantifies the side-channel leakage in multiple-trace attack.
+Chapter~\ref{chapter6} concludes the dissertation.

### 2021-04-05 Chapter-2/Chapter-2.tex
update
Updates from Overleaf

@@
 While there are many kinds of side-channel attacks, we focus on address-based side-channel attacks in this dissertation.
-Address-based side-channel attacks happen when a program accesses different memory locations when it processes different secrets.
-In many situations, an attacker may shares some hardware resources (e.g., Cache, TLB, and DRAM) with the victim in today's computer system ~\cite{ge2018survey,szefer2019survey}.
+Address-based side-channel attacks happen when a program accesses different memory locations when it processes various secrets.
+In modern computers, an attacker may shares some hardware resources (e.g., Cache, TLB, and DRAM) with the victim in today's computer system ~\cite{ge2018survey,szefer2019survey}.
 As a result, the attacker can probe the shared hardware resource to infer the memory accesses of the victim.
@@
 For a detailed overview of recent side-channel attacks, we refer to the following survey paper~\cite{ge2018survey}.
-We classified those side-channel attacks into two categories: cache channels and page channels.
+We classified those side-channel attacks into two categories: cache-level channels and page-level channels.
 
 \subsection{Cache-level Channel}
-A CPU cache are an essential part in modern computer systems.
-It is a smaller and faster memory which is designed to reduce the average data access costs to the main memory by storing copies of data from the main memory.
-When a CPU reads data from a memory location, it first checks the memory location in the cache.
+A CPU cache is an essential part of modern computer systems.
+It is a smaller and faster memory that is designed to reduce the average data access costs to the main memory by storing copies of data from the main memory.
+When a CPU reads data from a memory location, it first checks the cache.
 If it finds that the cache stores a copy of the memory location, a cache hit occurs.
-Otherwise, the CPU needs to read the data from the main memory and a cache miss happens.
+Otherwise, the CPU needs to read the main memory data, and a cache miss happens.
+
 Cache channels~\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last,184415} rely on the time difference between cache misses and cache hits.
+The core-private caches are traditionally set-associate cache.
+The cache is divided into different cache sets, and each cache set is made up of several cache lines.
 Cache channel attacks can observe cache accesses at the level of cache sets, cache lines or other granularities.

### 2021-04-05 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 One example is the CacheBleed attack~\cite{yarom2017cachebleed}.
-It is a cache channel attack can exploits cache-back collisions.
+It is a cache channel attack can exploits cache-bank collisions.
 \subsection{Page-level Channel}
 Page channel attacks allow an attacker can observe the memory access at the granularity of memory pages.
-One example is the controlled-channel attack~\cite{xu2015controlled}, where a privileged adversary try to infer the sensitive information by manipulating the enclave page access.
-Those kinds of attacks usually happen on the shielding system.
+One example is the controlled-channel attack~\cite{xu2015controlled}.
+It is a primary threats for the trusted execution environments (TEEs).
+A privileged adversary (e.g., Kernel) can infer the sensitive information by manipulating the enclave page access.
 A malicious OS can proactively revoke a virtual enclave memory page from the memory.
-If the victim enclave program accesses the memory table, then the adversary can know which page is accessed by observing the page fault sequences.
+If the victim enclave program accesses the memory table, then the OS can observe the page faults and  know which page is accessed.
 While the granularity of the controlled-channel attacks is coarse-grained, the controlled-channel attacks allow the attacker to have a noise-free observation.
@@
 
-In this paper, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs).
-To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.
+Based on the above discussion, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs) in the dissertation.
+To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in the literature.
 
 \subsection{Target Applications}
-While there is a vast number of studies\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last} on side-channel attacks, we find many of those work targets on the encryption key on cryptography libraries.
-In general, current side-channel attacks can be classified into the below three categories.
+There is a vast number of studies\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last} on side-channel attacks.
+Most early work targets on the encryption key on cryptography libraries.
+In recent years, researchers start to focus on more general target applications.
+In summary, current side-channel target applications can be classified into the below three categories.
 
@@
 The first side-channel attack of cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996.
-Many algorithms (Diffie-Helloman, RSA) implementations at that time use the simple modular exponentiation algorithm, which does not run in fixed time.
+It exploits the the simple modular exponentiation algorithm function in many algorithms (Diffie-Helloman, RSA) implementations.
+The function does not run in a fixed time.
 By measuring the time differences between the modular exponentiation algorithm computes the exponent bits (0 or 1), Kocher's attack can recover the whole secret key bit by bit.
+Since then, researchers start to break all kinds of cipher implementation through side-channel attacks.
 Cryptography libraries usually have several implementations for symmetric ciphers.

### 2021-04-05 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 \subsubsection{Cryptography Libraries}
+\begin{table}
+    \centering
+    \caption{This table shows some common vulnerable points in cryptography implementations and the corresponding protections.}
+    \label{chapter2:table:crypto}
+
+        \begin{tabular}{lll}
+            \toprule
+            Implementation & Common Vulnerable Point             & Mitigation \\ \midrule
+            AES &  T-table and S-table lookups   & AES instructions (AES-NI) \\&&Scalar bit-slicing \\&& Preloading tables     \\
+            DES & Table lookups & Scalar bit-slicing (No implmentation) \\
+            RSA & CRT optimization & Verifying the consistency with the public key\\
+            & Modular exponentiation& Montgomery modular multiplication\\
+            & & Base blinding and exponent blinding\\
+            (EC)DSA & Scalar multiplication& Constant time implementation\\
+            &Modular inversion &\\
+            &Modular reduction &\\
+            \bottomrule
+        \end{tabular}
+\end{table}
+
 The first side-channel attack of cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996.
@@
 Since then, researchers start to break all kinds of cipher implementation through side-channel attacks.
-Cryptography libraries usually have several implementations for symmetric ciphers.
-For example, AES can have more than five different implementations (OpenSSL).
+Table~\ref{chapter2:table:crypto} summarizes some common vulnerable points in cryptography library implementations.
+Note that Cryptography libraries usually have several implementations for some symmetric ciphers.
+For example, AES can have more than five different implementations  in OpenSSL.
 Depending on the build configuration and the return value of \textsf{CPUID}, the code may execute any implementation of them.

### 2021-04-05 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
             Implementation & Common Vulnerable Point             & Mitigation \\ \midrule
-            AES &  T-table and S-table lookups   & AES instructions (AES-NI) \\&&Scalar bit-slicing \\&& Preloading tables     \\
+            AES &  T-table and S-table lookups   & AES instructions (AES-NI) 
+            \\&&Scalar bit-slicing \\&& Preloading tables     \\
             DES & Table lookups & Scalar bit-slicing (No implmentation) \\

### 2021-04-05 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
     \label{chapter2:table:crypto}
+    \resizebox{\columnwidth}{!}{%
 
@@
             & & Base blinding and exponent blinding\\
-            (EC)DSA & Scalar multiplication& Constant time implementation\\
-            &Modular inversion &\\
+            (EC)DSA & Scalar multiplication& Constant time scalar implementation\\
+            &Modular inversion & Blinding\\
             &Modular reduction &\\
@@
         \end{tabular}
+        }
 \end{table}

### 2021-04-06 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 
-The first side-channel attack of cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996.
+The first side-channel attack to cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996.
 It exploits the the simple modular exponentiation algorithm function in many algorithms (Diffie-Helloman, RSA) implementations.
@@
 Table~\ref{chapter2:table:crypto} summarizes some common vulnerable points in cryptography library implementations.
-Note that Cryptography libraries usually have several implementations for some symmetric ciphers.
+Note that Cryptography libraries usually have several implementations for some ciphers.
 For example, AES can have more than five different implementations  in OpenSSL.
@@
 However, such implementations are vulnerable to side-channels and can be exploited to retrieve the whole key~\cite{bonneau2006cache}.
-In addition to the reference implementation, those libraries also have side channel silent versions.
-However, recent studies also shows those versions also have side-channel vulnerabilities caused by compiler optimizations and human mistakes~\cite{217537}.
-The situation is even worse for asymmetric ciphers (e.g., Diffie-Helloman, RSA, ECDSA) because those those ciphers have a lots of big number calculations.
+In addition to the reference implementation, those libraries also have side-channel mitigated versions.
+However, recent studies also shows those versions (e.g., AES-NI) also have side-channel vulnerabilities caused by compiler optimizations and human mistakes~\cite{217537}.
+The situation is even worse for asymmetric ciphers (e.g., Diffie-Helloman, RSA, ECDSA), because those those ciphers have a lots of big number calculations.
 It is hard to implement those calculations completely side-channel resistant.
 Recent work~\cite{arnaud2013timing,yarom2017cachebleed,yarom2014flush+} has demonstrated several end-to-end attacks to recover the private keys of those ciphers.
+There are two common countermeasures to mitigate the side-channel attacks in cryptography libraries.
+The first approach is to adopt constant time operation when computing the secret data.
+It is hard to migrate all the code into a constant time implementation.
+The second approach is to use blinding to reduce the information that can attacker can retrieve.
+However, the binding value can also be retrieved by an attacker through other attacks including side-channel attacks.
+
 \subsubsection{Machine Learning Applications}
-Recent side-channel attack on machine learning applications mainly focus on recovering two types of the sensitive information: the input of the model, and the architecture of deep learning models.
+Recent side-channel attacks on machine learning applications mainly focus on recovering two types of the sensitive information: the input of the model, and the architecture of deep learning models.
 Hua et al.~\cite{hua2018reverse} were the first in the literature to reverse engineer the architecture of convolutional neural networks (CNNs) through the memory access patterns.
@@
 A few of recent work also studies the side-channel attacks in media and graphic libraries.
+Gruss el at.
+shows an attack that can infer keystrokes by exploiting secret-dependent memory accesses in the GDK library.
 In the controlled-channel attack~\cite{xu2015controlled}, Yuanzhong et al.
@@
 By exploiting the differences of memory accesses when the program renders different characters, an attacker can recover parts of the original sensitive information.
-Other side-channel attacks target on the kernel of the operating system.
+Other side-channel attacks target on the OS's kernel.
 One example is the to use the side-channel attacks to break the kernel address space randomization (KASLR).
@@
 
-\textbf{Trace comparison.} If a program has two different execution traces under two different sensitive inputs, then attacker can distinguish the sensitive input by observing the execution trace.
+\textbf{Trace comparison.} If a program has two different execution traces under two different sensitive inputs, then attackers can distinguish the sensitive input by observing the execution trace.
 Therefore, we can conclude the program is vulnerable to side-channel attacks.
-The method is similar to UNIX tool \textsf{diff}.
-Moreover, the approach does not need to model or abstract the program's semantics.
+The method is similar to the UNIX tool \textsf{diff}.
+The approach does not need to model or abstract the program's semantics.
 In general, the approach is quite fast.
@@
 After that, by analyzing the model, those tools can identify side-channel leakages.
-Comparing with the trace comparison approach, the method is more precise.
+Compared with the trace comparison approach, the method is more precise.
 
 Those methods usually follow the below steps.
-Suppose a program $P$ has $k$ as the input, we can run symbolic execution on the top the victim program.
-So temporary values can be represented as math formulas.
-After that, we need to build a cache or memory access model and model the side-channel leakage as a math constraint.
-Then we use SMT solvers to find if there are two different secret inputs that can lead to access different locations in the memory or the cache.
-If so, then the program is vulnerable to side-channel attacks.
+Suppose a program $P$ has $k$ as the input.
+Those approaches first retrieve the relationship between the $k$ and temperate values during the execution.
+After that, they should have a cache or memory access model and model the side-channel leakage as a math constraint.
+By using SMT solvers to find if two different secret inputs can lead to access to different locations in the memory or the cache, those approaches can determine if the program is vulnerable to side-channel attacks.
 Contrary to the trace comparison, the method is quite precise.
 Moreover, it can model multiple leakages precisely as the conjunction of those formulas.
-However, such approach has the following limitations.
+However, such approaches have the following limitations.
 
 \begin{itemize}
-    \item Existing tools cannot not handle many instructions such as AVX, and SIMD instructions.
+    \item Many tools can only analyze the source code or the intermediate representation level.
+However, side-channel are low-level problems in general.
 Most existing tools are research prototype or are implemented based on the research prototype.
-For many projects, the tool is only implemented to properly handle the benchmark in their papers.
-Second, many those tools rely on transferring those instructions into some intermediate languages.
-However, those intermediate languages do not support those architecture instructions.
-    \item Today's solvers can not handle many complicated constraints, especially the conjunction of those constraints.
-Recent studies show existing solver have bugs when it deals with floating pointer calculations.
+For some projects, the tool is only implemented to handle the benchmark in their papers properly.
+    \item Today's solvers can not handle some complicated constraints, especially the conjunction of those constraints.
+Recent studies show existing solvers have bugs when it deals with floating pointer calculations.
 \end{itemize}

### 2021-04-06 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 For some projects, the tool is only implemented to handle the benchmark in their papers properly.
-    \item Today's solvers can not handle some complicated constraints, especially the conjunction of those constraints.
-Recent studies show existing solvers have bugs when it deals with floating pointer calculations.
+    \item Those tools heavily rely on SMT solvers.
+Despite SMT solvers have made incredible progress in terms of the performance, SMT solving is still the main bottlenecks of the many frameworks.
+SMT solvers are not good at non-linear arithmetic.
+However, such non-linear arithmetics are quite common in some cryptography algorithms.
+Recent studies show existing solvers still have plenty of bugs when it deals with real number calculations.
+Those calculations are also common in media libraries and machine learning applications.
 \end{itemize}

### 2021-04-07 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
   \centering
-  \includegraphics[width=.65\columnwidth]{./figures/chapter3/architecture.pdf}
+  \includegraphics[width=.5\columnwidth]{./figures/chapter3/architecture.pdf}
   \caption{Computer Memory Hierarchy}\label{fig:memory_hierarchy}
@@
 
-\begin{lstlisting}
+\begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
  ...
@@
 
+\subsection{Case Studies}
+\subsubsection{DES and AES}
+Our tool confirms that both implementations in OpenSSL and mbedTLS have side-channel leakages
+sites.
+Moreover, we find that all the leakages belong to the secret-dependent data accesses.
+The reference implementation of AES uses four lookup tables to speed up the computation.
+However, such implementation are vulnerable to side-channel attacks.
+Previous work has shown an end-to-end attack to fully recover the key.
+Our findings is similar to the previous work.
+We also notice that later version of OpenSSL (after 1.0.1) uses a modified version with smaller S-table.
+However, \tool{} also find the leakage sites in the version.
+Recent work also finds the sites through theoretical analysis.
+
+\subsection{RSA}
+
 \section{Discussion}
@@
 we may neglect some side-channel vulnerabilities not covered by the traces analyzed.
-However, this is not a crucial problem for analyzing crypto libraries because crypto
+However, this is not a crucial problem for analyzing crypto libraries, because crypto
 libraries are designed to have the same code coverage for various inputs. Our
@@
 
-While recent works have reported lots
-of potential side-channel vulnerabilities, most of them are not patched by
-developers. For RSA, the latest
-OpenSSL only has one leakage site that can leak more than 3 bits while there
-are 22 leakage sites according to \tool{}. DES implementation of OpenSSL has
-several sensitive leakages, but given the end life status of DES, it is still
-unpatched for the worth of engineering effort.
+While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers.
+For RSA, the latest OpenSSL only has one leakage site that can leak more than 3 bits while there are 22 leakage sites according to \tool{}.
+DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort.
+The sampling method  seems simple and may miss some leakages in theory.
+However, the evaluation result shows \tool{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.

### 2021-04-07 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \subsection{RSA}
+We also evaluates our tool on the RSA implementations. With the optimizations
+introduced in the previous section, we do not apply any domain knowledge to
+simplify the analysis. Therefore, our tools can identify all the leakage sites
+reported by CacheD~\cite{203878} in a shorter time. Our tool finds that most
+leakages in RSA occur in the big number implementation. We also find the newer
+versions of RSA in OpenSSL tend to have fewer leakages detected by \tool{}.
+
+Even for the up-to-date version of OpenSSL, \tool{} still find several
+side-channel leakages. It is a secret-dependent control flow transfers. 
+However, as the branch is inside a loop and a bit shift function causes the branch leak different bits from the sensitive buffer.
+
+\begin{figure}[h]
+\centering
+\begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
+while (!BN_is_bit_set(B, shift)) { /* note that 0 < B */
+    shift++;
+    if (BN_is_odd(X)) {
+        if (!BN_uadd(X, X, n))
+            goto err;
+    }
+    ...
+    if (!BN_rshift1(X, X))  // It causes the leak severe!
+        goto err;
+    ...
+}
+\end{lstlisting}
+    \vspace*{-6pt}
+    \caption{Unknown sensitive secret-dependent branch leaks from function 
+             \textsf{int\_bn\_mod\_inverse} in OpenSSL 1.1.1. Same as the example
+             in \S\ref{appendix:minor:vul}, the code can leak the last digit from
+             big number \textbf{X}. However, the leak is more severe because of the 
+             function \textsf{BN\_rshift1}. Each time function \textsf{BN\_rshift1}
+             will shift \textbf{X} right by one and places the result in \textbf{X}. Therefore,
+             an attacker can infer multiple bits of \textbf{X} by observing the branch at line 3.}
+    \label{fig:unknown}
+    \vspace*{-6pt}
+\end{figure}
 

### 2021-04-07 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 
-\subsection{RSA}
+\subsubsection{RSA}
 We also evaluates our tool on the RSA implementations. With the optimizations
@@
 Even for the up-to-date version of OpenSSL, \tool{} still find several
-side-channel leakages. It is a secret-dependent control flow transfers. 
+side-channel leakages. Shown in Figure~\ref{fig:unknown_leakage}.
+It is a secret-dependent control flow transfers. 
 However, as the branch is inside a loop and a bit shift function causes the branch leak different bits from the sensitive buffer.
@@
 \end{lstlisting}
-    \vspace*{-6pt}
     \caption{Unknown sensitive secret-dependent branch leaks from function 
-             \textsf{int\_bn\_mod\_inverse} in OpenSSL 1.1.1. Same as the example
-             in \S\ref{appendix:minor:vul}, the code can leak the last digit from
-             big number \textbf{X}. However, the leak is more severe because of the 
+             \textsf{int\_bn\_mod\_inverse} in OpenSSL 1.1.1. The function can leak the last digit from big number \textbf{X}. However, the leak is more severe because of the 
              function \textsf{BN\_rshift1}. Each time function \textsf{BN\_rshift1}
@@
              an attacker can infer multiple bits of \textbf{X} by observing the branch at line 3.}
-    \label{fig:unknown}
-    \vspace*{-6pt}
+    \label{fig:unknown_leakage}
 \end{figure}
+
+\subsubsection{Monocypher}\label{eval:mono}
+Monocypher is a small, easy to use cryptographic library with
+performance comparable to LibSodium~\cite{libsodium} and NaCl~\cite{bernstein2012security}.
+We choose four ciphers that are
+designed to be side-channel resistant from the library.
+Because those ciphers have no
+data flow from secrets to branch conditions and load addresses.
+Monocypher should be safe under our threat models.
+We analyze those ciphers with \tool{}, and it reports no leaks.
+This indicates that \tool{} is effective for validating countermeasures.
 

### 2021-04-07 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 
-\subsubsection{Monocypher}\label{eval:mono}
-Monocypher is a small, easy to use cryptographic library with
-performance comparable to LibSodium~\cite{libsodium} and NaCl~\cite{bernstein2012security}.
-We choose four ciphers that are
-designed to be side-channel resistant from the library.
-Because those ciphers have no
-data flow from secrets to branch conditions and load addresses.
-Monocypher should be safe under our threat models.
-We analyze those ciphers with \tool{}, and it reports no leaks.
-This indicates that \tool{} is effective for validating countermeasures.
-
 \subsection{Analysis of Software Countermeasures}\label{sec:eval_countermeasures}

### 2021-04-07 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 Quantitative Information Flow (QIF) aims at providing an estimation of the amount of leaked information from the sensitive information given the public output. If zero bits
-of the information are leaked, the program is called non-interference. McCamant
-and Ernst~\cite{McCamantE2008} quantify the information leakage as the network
-flow capacity. Backes et al.~\cite{5207642} propose an automated method for QIF
-by computing an equivalence relation on the set of input keys. But the approach
-cannot handle real-world programs with bitwise operations.
+of the information are leaked, the program is called non-interference. 
+McCamant and Ernst~\cite{McCamantE2008} quantify the information leakage as the network
+flow capacity. They model the possible information leakage as a network of limited-capacity
+channel. After that, they use the maximum rate of the channel to represent the amount of 
+secret information that the execution can reveal.
+Backes et al.~\cite{5207642} propose an automated method for QIF
+by computing an equivalence relation on the set of input keys. However,
+the evaluation shows the approach only works on small programs.
+Besides, their approach cannot handle programs with bitwise operations.
+However, such bitwise operations are quite common in cryptographic libraries.
 Phan et al.~\cite{Phan:2012:SQI:2382756.2382791} propose symbolic QIF. The goal of their
@@
 of side-channels with different granularities. It can also analyze side-channels
-in real-world crypto libraries.
+in real-world cryptographic libraries.
 
 Model counting refers to the problem of computing the number of
-models for a propositional formula (\#SAT). There are two approaches to
+solutions for a propositional formula (\#SAT). There are two approaches to
 solving the problem, exact model counting and approximate model
@@
 Mbound~\cite{gomes2006model}, and MiniCount~\cite{kroc2008leveraging}.
-Unlike ApproxCount,
-these model counters can give lower or upper bounds with guarantees.
+Unlike ApproxCount, these model counters can give lower or upper bounds with guarantees.
 Despite the rapid development of model counters for SAT and some
-research~\cite{chistikov2017approximate,phan2015model} on Modulo Theories model counting (\#SMT),
-they cannot be directly applied to
-side channel leakage quantification.
-ApproxFlow~\cite{biondi2018scalable} uses ApproxMC~\cite{chakraborty2016algorithmic} for information flow quantification,
-but it has only been tested with small programs.
+research~\cite{chistikov2017approximate,phan2015model} on Modulo Theories model counting (\#SMT), they cannot be directly applied to side channel leakage quantification.
+ApproxFlow~\cite{biondi2018scalable} uses ApproxMC~\cite{chakraborty2016algorithmic} for information flow quantification, but it has only been tested with small programs.

### 2021-04-07 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 
-Model counting refers to the problem of computing the number of
+Model counting refers to the problem of computing the number of satisfying
 solutions for a propositional formula (\#SAT). There are two approaches to
 solving the problem, exact model counting and approximate model
-counting. We focus on approximate model counting since it is our approach. Wei and Selman~\cite{wei2005new} introduce
+counting. Exact model counting for propositional formulas (\#SAT) should determine
+the number of solutions. Intuitively, such model counter should traverse the whole
+search space to find all the satisfying solutions. Consequently, exact model counter is 
+ very slow. Those model counters have difficulty scaling up to real-world programs.
+We focus on approximate model counting since it is our approach. Wei and Selman~\cite{wei2005new} introduce
 ApproxCount, a local search based method using Markov Chain Monte
@@
 Despite the rapid development of model counters for SAT and some
-research~\cite{chistikov2017approximate,phan2015model} on Modulo Theories model counting (\#SMT), they cannot be directly applied to side channel leakage quantification.
+research~\cite{chistikov2017approximate,phan2015model} on Modulo Theories model counting (\#SMT), existing tools cannot be directly applied to side channel leakage quantification.
 ApproxFlow~\cite{biondi2018scalable} uses ApproxMC~\cite{chakraborty2016algorithmic} for information flow quantification, but it has only been tested with small programs.

### 2021-04-07 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 very slow. Those model counters have difficulty scaling up to real-world programs.
-We focus on approximate model counting since it is our approach. Wei and Selman~\cite{wei2005new} introduce
+On the other hand, approximate model counter is much faster compared with the exact 
+model counter. The related work focus on approximate model counting since it is close to our approach. Wei and Selman~\cite{wei2005new} introduce
 ApproxCount, a local search based method using Markov Chain Monte
@@
 Despite the rapid development of model counters for SAT and some
-research~\cite{chistikov2017approximate,phan2015model} on Modulo Theories model counting (\#SMT), existing tools cannot be directly applied to side channel leakage quantification.
+research~\cite{chistikov2017approximate,phan2015model}, existing tools cannot be directly applied to side channel leakage quantification for the following two reasons.
 ApproxFlow~\cite{biondi2018scalable} uses ApproxMC~\cite{chakraborty2016algorithmic} for information flow quantification, but it has only been tested with small programs.

### 2021-04-07 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 Even for the up-to-date version of OpenSSL, \tool{} still find several
-side-channel leakages. Shown in Figure~\ref{fig:unknown_leakage}.
-It is a secret-dependent control flow transfers. 
+side-channel leakages. Figure~\ref{chapter3:fig:unknown_leakage} shows an unknown leakage site in OpenSSL 1.1.1. It is a secret-dependent control flow transfers. 
 However, as the branch is inside a loop and a bit shift function causes the branch leak different bits from the sensitive buffer.
@@
              an attacker can infer multiple bits of \textbf{X} by observing the branch at line 3.}
-    \label{fig:unknown_leakage}
+    \label{chapter3:fig:unknown_leakage}
 \end{figure}
@@
 
-\tool{} works on native x86 execution traces. The design, which is very
-precise in terms of true leakages compared to other static source code
-method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also has
-the common limitations of dynamic approaches. \tool{} may only cover part of the code.
-Each time we only get one single execution trace. Therefore,
-we may neglect some side-channel vulnerabilities not covered by the traces analyzed.
-However, this is not a crucial problem for analyzing crypto libraries, because crypto
-libraries are designed to have the same code coverage for various inputs. Our
-evaluation also confirms the above point. For symmetric encryption, during our
-evaluation there is no secret-dependent control-flow transfers. RSA
-implementations have several secret-dependent control-flow transfers.
-%But after we manually check those leakages cites. We find
-Most of them are  %used for
-bound checks, which do not leak much information and have negligible effects
-on the whole code coverage as well.
+\tool{} works on native x86 execution traces.
+The design, which is very precise in terms of true leakages compared to other static source code method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also has the common limitations of dynamic approaches.
+\tool{} may only cover part of the code.
+Each time we only get one single execution trace.
+Therefore, we may neglect some side-channel vulnerabilities not covered by the traces analyzed.However, this is not a crucial problem for analyzing cryptographic libraries, because cryptographic libraries are designed to have the same code coverage for various inputs.
+Our evaluation also confirms the above point.
+For symmetric encryption, during our evaluation there is no secret-dependent control-flow transfers.
+RSA implementations have several secret-dependent control-flow transfers.
+Most of them are bound checks, which do not leak much information and have negligible effects on the whole code coverage as well.
 

### 2021-04-08 Chapter-5/Chapter-5.tex
Updates from Overleaf
add figures
update

@@
 
-\chapter{Precise Analysis on Chosen-plaintext Attacks}\label{chapter5}
+\chapter{Precise Analysis on Multiple-trace Attacks}\label{chapter5}
 \section{Introduction}
 Side-channel attacks allow attackers to infer sensitive information based on the non-functional behaviors of the computer system.
-Examples of those non-functional behaviors include acoustics, CPU usages, timing, EM signals, etc~\cite{agrawal2002side,hund2013practical,halevi2015keyboard}.
-In short, the program has different execution behaviors when it processes various keys.
-As an attacker, he can infer nontrivial information by observing those secret-dependent behaviors.
+Examples of those non-functional behaviors include acoustics, CPU usages, timing, EM signals, etc~\cite{agrawal2002side,hund2013practical,halevi2015keyboard,batina2019csi}.
+In summary, if the program has different execution behaviors when it processes various keys, an attacker can infer nontrivial information by observing those secret-dependent behaviors.
 While separate side-channel attacks may have different forms and patterns, we find a large portion of them share the same fundamental reasons.
@@
 
-While removing those dependent memory-access patterns in existing software completely seems impossible, fixing some of the most dangerous leakages appears to be a feasible solution.
+While removing those dependent memory-access patterns in existing software completely is hard and tedious, fixing some of the most dangerous leakages appears to be a feasible solution.
 Previous studies on side-channel detections have shown their effectiveness in finding such code patterns.
-As a developer, he can run the tool to analyze the side-channels leakages and fix those patterns.
-However, fixing all those leakages seem impossible.
+Developers can run the tool to analyze the side-channels leakages and fix those patterns.
+However, fixing all those leakages seem impossible for the following reasons.
 First, side-channels are inevitable.
@@
 However, we still find that there are plenty of side-channel leakages in the latest version of OpenSSL.
-Second, many side-channel vulnerable versions usually have better performance, such as the T-table lookup in AES, CRT optimizations in RSA, and Fast Discrete Fourier Transform (FDFT) in many media processing libraries.
-Third, some developers are not interested in fixing side-channels vulnerabilities unless we can show them an attack demo, even for the cryptography developers.
+Second, many side-channel vulnerable versions usually have better performance, such as the T-table lookups in AES, CRT optimizations in RSA, and Fast Discrete Fourier Transform (FDFT) in many media processing libraries.
+Third, some developers are not interested in fixing side-channels vulnerabilities unless people can show them an attack demo, even for the cryptography developers.
 For many non-cryptography developers, side-channels are not in the threat model.
@@
 
-The key to solve the problem is looking for a proper metric to assess the sensitive level of the side-channel leakages.
-Many side-channel analysis works focus on detecting leakages, which is fine because most side-channel attacks target cryptography libraries.
-For cryptography libraries, even a minor leakage can be severe because the leakage can reduce the strength of the encryption algorithm.
-However, many attacks also exploit non-cryptography libraries and applications like machine learning frameworks~\cite{yan2020cache,hong2018security}, graphic libraries~\cite{wang2019unveiling}, spell checking tools~\cite{xu2015controlled}, etc.
-Unlike side-channel attacks on cryptography libraries that exploit one vulnerability each time, attacks on non-cryptography rely on multiple side-channel leakage sites to retrieve more information.
-Suppose one program has two leakage sites, it is hard to estimate the total effect of those two leakages.
+The key to solving the problem is looking for a proper metric to assess the side-channel leakages' sensitive level.
+Many side-channel analysis tools focus on detecting leakages, which is fine because most side-channel attacks target cryptography libraries.
+For cryptography libraries, even a minor leakage can be severe because the leakage can reduce the encryption algorithm's strength.
+However, many attacks also exploit non-cryptography libraries and applications like machine learning applications~\cite{yan2020cache,hong2018security}, graphic libraries~\cite{wang2019unveiling}, spell checking tools~\cite{xu2015controlled}, etc.
+Unlike side-channel attacks on cryptography libraries that exploit one vulnerability at a time, attacks on non-cryptography rely on multiple side-channel leakage sites to retrieve more information.
+Suppose one program has two leakage sites.
+It is hard to estimate the total effect of those two leakages.
 Any two leakages have some underlying complex relationships.
@@
   \centering
-    \includegraphics[width=\columnwidth]{./figures/channel.pdf}
+  \includegraphics[width=\columnwidth]{./figures/chapter5/channel.pdf}
   \caption{The relationship between the side-channel attack and the channel capacity.
@@
         \toprule
-\diagbox{S}{T} & 0 & 1 & 2 & 3 & 4 & 5& 6& 7 &  ...\\ 
+        \diagbox{S}{T} & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & ... \\
         \midrule
@@
         5              &   &   &   &   &   & A &             \\
-6 &  &  &  &  &  & &A \\
-7 &  &  &  &  &  &  && A\\ 
+        6              &   &   &   &   &   &   & A           \\
+        7              &   &   &   &   &   &   &   & A       \\
         \bottomrule
@@
         4              & A &   &   &   &   &                 \\
-5 &  &  A& &  &  & & \\
+        5              &   & A &   &   &   &   &             \\
         6              &   &   & A &   &   &   &             \\
-7 &  & &  &  A&  &  && \\ 
+        7              &   &   &   & A &   &   &   &         \\
         \bottomrule
@@
 
-\includegraphics[width=\columnwidth]{./figures/align.pdf}
+      \includegraphics[width=\columnwidth]{./figures/chapter5/align.pdf}
 
@@
   \centering
-    \includegraphics[width=\columnwidth]{./figures/workflow.pdf}
+  \includegraphics[width=\columnwidth]{./figures/chapter5/workflow.pdf}
   \caption{The workflow of \tool{}. We try to divide the \tool{} into three steps to assist the illustration. }\label{fig:workflow}
@@
         10          & 0     \\
-11 & $1/8$\\
+        11          & $1/8$ \\
         \bottomrule
@@
 
-\subsection{Limitation}
 \tool{} is a dynamic approach.

### 2021-04-08 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-Second, many precise side-channel analysis tools rely on some techniques like symbolic executions, taint analysis, and abstract interpretations~\cite{wang2017cached,doychev2015cacheaudit,brotzman2019casym,wang2019identifying}.
+Second, many side-channel leakage detection tools rely on some techniques like symbolic executions, taint analysis, and abstract interpretations~\cite{203878,182946,Brotzman19Casym,236338}.
 Those methods need to consider the semantics of each ISA instruction, which is tedious.
@@
 
-Third, while many existing works can detect side-channel leakages, few of them can assess how severity level of those vulnerabilities~\cite{wang2017cached,doychev2015cacheaudit,brotzman2019casym,wang2019identifying,weiser2018data,wichelmann2018microwalk}.
-There are some tools~\cite{doychev2015cacheaudit,chattopadhyay2019quantifying} that can quantify the information leakage.
+Third, while many existing works can detect side-channel leakages, few of them can assess how severity level of those vulnerabilities~\cite{203878,182946,Brotzman19Casym,236338,217537,Wichelmann:2018:MFF:3274694.3274741}.
+There are some tools~\cite{182946,Chattopadhyay:2017:QIL:3127041.3127044} that can quantify the information leakage.
 Those tools usually rely on the abstraction to give an upper bound estimation of each leakage site, which is useful to justify the software is secure if the reported leakage is zero.

### 2021-04-08 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 Second, many side-channel leakage detection tools rely on some techniques like symbolic executions, taint analysis, and abstract interpretations~\cite{203878,182946,Brotzman19Casym,236338}.
-Those methods need to consider the semantics of each ISA instruction, which is tedious.
-So they build the tool on the top of existing binary analysis frameworks.
-Due to the limitations of binary analysis frameworks, it is hard to apply existing methods to analyze side-channels in non-cryptography libraries.
+It is hard to implement those techniques from scratch.
+So they build the tool on top of existing binary analysis frameworks.
+Due to the limitations of existing binary analysis frameworks, it is hard to apply existing methods to analyze side-channels in non-cryptography libraries.
 For many other applications like machine learning, media, and graphic libraries built on the top architecture-dependent libraries (e.g., Intel MKL~\cite{wang2014intel}), those tools can not handle it.
-Moreover, existing binary analysis frameworks (e.g., Angr~\cite{shoshitaishvili2016state}) are limited to analyze floating-point instructions.
+Moreover, some binary analysis frameworks (e.g., Angr~\cite{shoshitaishvili2016state}) are limited in analyzing floating-point instructions.
 But the functionality of those applications heavily depends on floating-point calculations.
 
-Third, while many existing works can detect side-channel leakages, few of them can assess how severity level of those vulnerabilities~\cite{203878,182946,Brotzman19Casym,236338,217537,Wichelmann:2018:MFF:3274694.3274741}.
+Third, while many existing tools can detect side-channel leakages, few of them can assess how severity level of those vulnerabilities~\cite{203878,182946,Brotzman19Casym,236338,217537,Wichelmann:2018:MFF:3274694.3274741}.
 There are some tools~\cite{182946,Chattopadhyay:2017:QIL:3127041.3127044} that can quantify the information leakage.
-Those tools usually rely on the abstraction to give an upper bound estimation of each leakage site, which is useful to justify the software is secure if the reported leakage is zero.
+Those tools can give an upper bound estimation of each leakage site, which is useful to justify the software is secure if the reported leakage is zero.
 But those tools can not tell software developers how serious each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage.
@@
 
-To solve the above problem, we propose a method to estimate the effect of each side-channel leakages automatically.
-We compare the side-channel attack to a communication system and use the channel capacity to quantify the amount of the information flow from the original secret to the observation of an attacker.
+To solve the above problem, we propose a method to estimate the effect of side-channel leakages automatically.
+We compare the side-channel attack to a communication system and use the channel capacity to quantify the amount of the information flow from the original secret to an attacker's observation.
 The method also allows us to combine multiple leakages sites to retrieve the information.
-The  attack can be seem as a process that reduces the search space of the original sensitive inputs.
+The attack can be seen as a process that reduces the search space of the original sensitive inputs.
 We use the side-channel vulnerability to divide the input space.
-If the patterns can unique distinguish the input space, then we think the information is leaked totally.
-However, in the real cases, many of those side-channel leakage patterns are not enough for us to distinguish each leakage sites, but can still distinguish some of the sensitive inputs.
-In those cases, we call those leakages partial leaks.
+If the patterns can uniquely distinguish the input space, then we think the information is leaked totally.
+However, in real cases, many of those side-channel leakage patterns are not enough to distinguish each leakage site but can still discern some secret inputs.
+In those cases, we call those partial leakages leaks.
 

### 2021-04-08 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-The method has three phases.
+The method consists of three phases.
 In the first phase, we fuzz the target program with various inputs and collect the memory access information.
@@
 With the debug information, we can precisely know the address access information of the source code.
-In the third phase, we exam the source code, if one function have two memory access patterns, then the function is vulnerable to side-channel attacks.
-Base on the distribution of memory access patterns under different inputs, we quantify the side-channel leakage of each functions.
+In the third phase, we exam the source code.
+If one function has two memory access patterns, then the function is vulnerable to side-channel attacks.
+Based on the distribution of memory access patterns under different inputs, we quantify each function's side-channel leakage.
 

### 2021-04-08 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-\subsection{Address-based Side-channel Attacks}
-Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses.
-Most of the attack allows the attacker to shares some hardware resources with the victim.
-As a result, while the fundamental reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.
-
-\begin{table}
-  \centering
-  \caption{Due to the page limit, we only shows some representations of the vast side-channel attacks: Attacks, the shared hardware resources with attackers, the granularity of the attacker can observe, is there any published attacks on non-cryptography library and if the type of attack can exploit multiple leakage sites.}
-  \label{table:side_channel_attack}
-  \resizebox{\columnwidth}{!}{%
-
-    \begin{tabular}{lllcc}
-      \toprule
-      Attacks                                           & Shared Resources & Granularity            & Non-Crpyto & Multiple \\ \midrule
-      CacheBleed~\cite{yarom2017cachebleed}             & Cache            & Sub Cache Line (<64 B) & \xmark     & \xmark   \\
-      CopyCat~\cite{moghimi2020copycat}                 & Page Tables      & Instruction            & \xmark     & \xmark   \\
-      Prime + Probe~\cite{liu2015last}                  & Cache            & Cache Set (64-512 B)   & \cmark     & \xmark   \\
-      Prime + Abort~\cite{disselkoen2017prime+}         & Cache            & Cache Set (64-512 B)   & \cmark     & \xmark   \\
-      Flush + Reload~\cite{yarom2014flush+}             & Cache            & Cache Line (64 B)      & \cmark     & \cmark   \\
-      Flush + Flush~\cite{gruss2016flush+}              & Cache            & Cache Line (64 B)      & \cmark     & \xmark   \\
-      Controlled-channel Attack~\cite{xu2015controlled} & Page Tables      & Page (4KB)             & \cmark     & \xmark   \\
-      TLBleed~\cite{gras_translation_2018}              & MMUs             & TLB Set (4KB)          & \cmark     & \xmark   \\
-      Page Cache Attacks~\cite{gruss2019page}           & Page Cache       & Page (4KB)             & \xmark     & \cmark   \\
-      \bottomrule
-    \end{tabular}
-  }
-\end{table}
-
-\subsubsection{Cache-level Channel}
-Cache-based channels rely on the time difference between cache misses and cache hits. Cache channel attacks can observe cache accesses at the level of cache sets, cache lines or other granularities.
-We introduce two common attack strategies, namely Prime+Probe and
-Flush+Reload. Prime+Probe targets a single cache set. An
-attacker preloads the cache set with its own data and waits until the victim
-executes the program. If the victim accesses the cache set and evicts part of
-the data, the attacker will experience a slow measurement.
-While Flush+Reload targets a single cache line, it requires the attacker and victim share some memory. During the ``flush'' stage, the attacker flushes the ``monitored
-memory'' from the cache and waits for the victim to access the memory,
-who will load the sensitive information to the cache line. In the next phase,
-the attacker reloads the ``monitored memory''. By measuring the time difference
-brought by cache hit and miss, the attacker can further infer the sensitive information. Some other types of side-channels target different hardware
-layers other than CPU cache.
-
-\subsubsection{Page-level Channel}
-Recent studies also shows the attacks can observe the memory access at the granularity of memory pages.
-One example is the controlled-channel attack~\cite{xu2015controlled}, where a privileged adversary try to infer the sensitive information by manipulating the enclave page access.
-Those kinds of attacks usually happen on the shielding system.
-A malicious OS can proactively revoke a virtual enclave memory page from the memory.
-If the victim enclave program accesses the memory table, then the adversary can know which page is accessed by observing the page fault sequence.
-While the granularity of the controlled-channel attacks is very coarse grained, the controlled-channel attacks allow the attacker to have a noise-free observation.
-Examples of other attacks exploits page cache maintained by the OS, TLB also shares the same granularity.
-
 In this paper, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs).
@@
       \begin{tikzpicture}[ele/.style={fill=black,circle,minimum width=.8pt,inner sep=1pt},every fit/.style={ellipse,draw,inner sep=-2pt}]
-        \node[ele,label=left:{\LARGE $k_1$}] (a1) at (0,4) {};
-        \node[ele,label=left:{\LARGE $k_2$}] (a2) at (0,3) {};
-        \node[ele,label=left:{\LARGE $k_3$}] (a3) at (0,2) {};
-        \node[ele,label=left:{\LARGE $k_4$}] (a4) at (0,1) {};
+        \node[ele,label=left:{\normalsize	 $k_1$}] (a1) at (0,4) {};
+        \node[ele,label=left:{\normalsize	 $k_2$}] (a2) at (0,3) {};
+        \node[ele,label=left:{\normalsize	 $k_3$}] (a3) at (0,2) {};
+        \node[ele,label=left:{\normalsize	 $k_4$}] (a4) at (0,1) {};
 
-        \node[ele,,label=right:{\LARGE $o_1$}] (b1) at (4,4) {};
-        \node[ele,,label=right:{\LARGE $o_2$}] (b2) at (4,3) {};
-        \node[ele,,label=right:{\LARGE $o_3$}] (b3) at (4,2) {};
-        \node[ele,,label=right:{\LARGE $o_4$}] (b4) at (4,1) {};
+        \node[ele,,label=right:{\normalsize	 $o_1$}] (b1) at (4,4) {};
+        \node[ele,,label=right:{\normalsize	 $o_2$}] (b2) at (4,3) {};
+        \node[ele,,label=right:{\normalsize	 $o_3$}] (b3) at (4,2) {};
+        \node[ele,,label=right:{\normalsize	 $o_4$}] (b4) at (4,1) {};
 
@@
       \begin{tikzpicture}[ele/.style={fill=black,circle,minimum width=.8pt,inner sep=1pt},every fit/.style={ellipse,draw,inner sep=-2pt}]
-        \node[ele,label=left:{\LARGE $k_1$}] (a1) at (0,4) {};
-        \node[ele,label=left:{\LARGE $k_2$}] (a2) at (0,3) {};
-        \node[ele,label=left:{\LARGE $k_3$}] (a3) at (0,2) {};
-        \node[ele,label=left:{\LARGE $k_4$}] (a4) at (0,1) {};
+        \node[ele,label=left:{\normalsize $k_1$}] (a1) at (0,4) {};
+        \node[ele,label=left:{\normalsize $k_2$}] (a2) at (0,3) {};
+        \node[ele,label=left:{\normalsize $k_3$}] (a3) at (0,2) {};
+        \node[ele,label=left:{\normalsize $k_4$}] (a4) at (0,1) {};
 
-        \node[ele,,label=right:{\LARGE $o_1$}] (b1) at (4,4) {};
-        \node[ele,,label=right:{\LARGE $o_2$}] (b2) at (4,3) {};
-        \node[ele,,label=right:{\LARGE $o_3$}] (b3) at (4,2) {};
-        \node[ele,,label=right:{\LARGE $o_4$}] (b4) at (4,1) {};
+        \node[ele,,label=right:{\normalsize $o_1$}] (b1) at (4,4) {};
+        \node[ele,,label=right:{\normalsize $o_2$}] (b2) at (4,3) {};
+        \node[ele,,label=right:{\normalsize $o_3$}] (b3) at (4,2) {};
+        \node[ele,,label=right:{\normalsize $o_4$}] (b4) at (4,1) {};
 

### 2021-04-08 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
   \begin{minipage}{0.6\linewidth}
-    \begin{lstlisting}
+    \begin{lstlisting}[xleftmargin=.15\textwidth,xrightmargin=.30\textwidth]
 void bar(uint8_t secret)
@@
   \end{minipage}
-  \hspace{-4pt}
   \hfill
-  \hspace{-4pt}
-  \begin{minipage}{0.45\linewidth}
-    \resizebox{\textwidth}{!}{%
+  \begin{minipage}{0.4\linewidth}
+    \resizebox{0.8\textwidth}{!}{%
 
@@
   \begin{minipage}{0.60\linewidth}
-    \begin{lstlisting}
+    \begin{lstlisting}[xleftmargin=.15\textwidth,xrightmargin=.30\textwidth]
 void bar(uint8_t secret)
@@
 
-\section{Align Non-deterministic Address Access Across Multiple Executions}
+\section{Align Address Access Across Multiple Executions}
 We compare address accesses of different executions generated by different inputs to quantify the amount of leakage information.
@@
   \begin{minipage}{0.45\linewidth}
-    \begin{lstlisting}[numbers=none]
+    \begin{lstlisting}[numbers=none,xleftmargin=.1\textwidth,xrightmargin=.2\textwidth]
 uint8_t *T = malloc(4);

### 2021-04-08 Chapter-6/Chapter-6.tex
Updates from Overleaf

\chapter{Future Work and Conclusion}\label{chapter6}

### 2021-04-08 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
-\chapter{Future Work and Conclusion}\label{chapter6}
+\chapter{Conclusion and Future Work}\label{chapter6}
+This dissertation research studies the address-based side-channel leakages in two aspects: detection and quantification.
+In the side-channel vulnerability detection research, we explore and solve the two bottlenecks in today's automated side-channel vulnerability detection tool, performance and precision.
+In the side-channel vulnerability quantification research, we propose two different side-channel leakage quantification tools based on information theory.
+
+In Chapter~\ref{chapter3}, we present the first technique \detect{}.

### 2021-04-08 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \subsubsection{Information Flow Check}
-\tool{} is designed to help software developers find and understand the side-channel vulnerabilities.
+\detect{} is designed to help software developers find and understand the side-channel vulnerabilities.
 To ease the procedure of fixing the bug, we also track the information flow for each byte of the input
@@
 The step can be seen as the multiple-tag taint analysis. With the help of the information from symbolic execution, we can implement a relatively simple but relatively precise information flow track.
-At the beginning of the analysis, \tool{} keep a track for each byte in
+At the beginning of the analysis, \detect{} keep a track for each byte in
 the original buffer.
-When \tool{} symbolically executes each instruction in the trace, it will check every value read from registers or memory.
+When \detect{} symbolically executes each instruction in the trace, it will check every value read from registers or memory.
 If the value is concrete, it means the instruction has nothing to do with the original buffer.
 If the value is a formula, it means the original information passes through the instruction.
-Since each byte in the sensitive buffer is represented as a symbol with a unique ID, \tool{} can know which byte in the origin buffer goes through the instruction.
+Since each byte in the sensitive buffer is represented as a symbol with a unique ID, \detect{} can know which byte in the origin buffer goes through the instruction.
 
@@
 \begin{enumerate}
-    \item Is \tool{} effective to detect side-channels in real-world crypto systems? (Effectiveness)
+    \item Is \detect{} effective to detect side-channels in real-world crypto systems? (Effectiveness)
     \item How much performance overhead does the method introduce? (Performance)
@@
 Table~\ref{table:over_result} summarizes the results.
-\tool{} finds 913 leaks in the crypto libraries.
+\detect{} finds 913 leaks in the crypto libraries.
 Among these 913 leaks, 241 are due to secret-dependent
@@
 
-In this section, we compare \tool{} with the
+In this section, we compare \detect{} with the
 existing trace-based side-channel detection tools on vulnerability detections.
@@
 Under the circumstance, we think it is only a leakage.
-We have confirmed that \tool{} can identify all the secret-dependent data access vulnerabilities reported by CacheD. In addition, \tool{} finds many new ones.
+We have confirmed that \detect{} can identify all the secret-dependent data access vulnerabilities reported by CacheD. In addition, \detect{} finds many new ones.
 CacheD fails to detect some vulnerabilities for two
 reasons. First, CacheD can only detect secret-dependent data access
-vulnerabilities. \tool{} can detect secret-dependent control-flows as well.
+vulnerabilities. \detect{} can detect secret-dependent control-flows as well.
 Second, according to the CacheD paper, CacheD times out after 20 hours to process
@@
 Table~\ref{eval:cacheD} shows that
-\tool{} is faster than CacheD. \tool{} is much faster than CacheD when analyzing the same
-number of instructions. For example, when we test~\tool{} on AES from OpenSSL
-0.9.7, \tool{} is over 100x faster than CacheD.
+\detect{} is faster than CacheD. \detect{} is much faster than CacheD when analyzing the same
+number of instructions. For example, when we test~\detect{} on AES from OpenSSL
+0.9.7, \detect{} is over 100x faster than CacheD.
 \begin{table*}[]
@@
 traces to analyze the side-channel vulnerabilities in asymmetric
-cyphers. On the other hand, \tool{} detects side-channel
-vulnerabilities from one execution trace. \tool{} uses symbolic
+cyphers. On the other hand, \detect{} detects side-channel
+vulnerabilities from one execution trace. \detect{} uses symbolic
 analysis to extract formulas that model each side-channel
@@
   secret inputs} to detect and quantify each leakage site. In
-theory, DATA might have better code coverage than \tool{} because it
-uses more execution traces,  but \tool{} has the following
-advantages. a) \tool{} is faster than DATA. For example, it takes
+theory, DATA might have better code coverage than \detect{} because it
+uses more execution traces,  but \detect{} has the following
+advantages. a) \detect{} is faster than DATA. For example, it takes
 116 minutes for DATA to detect vulnerabilities in the RSA implementation in OpenSSL 1.1.0f\@.
-\tool{} only spends 34 minutes, as shown in Table~\ref{table:over_result}.
+\detect{} only spends 34 minutes, as shown in Table~\ref{table:over_result}.
 It takes 13 minutes and 20 minutes
 for DATA to analyze the side-channel leakages in AES and DES,
-respectively. On the other hand, \tool{} finishes its analysis in
+respectively. On the other hand, \detect{} finishes its analysis in
 less than ten seconds while finding all the leakages reported by
-DATA. b) Because \tool{} does not run the test program again when wedinghao w
-have a new \emph{secret input}, \tool{} can test more input secrets
+DATA. b) Because \detect{} does not run the test program again when wedinghao w
+have a new \emph{secret input}, \detect{} can test more input secrets
 on those formulas within the same time to achieve better precision.
@@
 DATA reports 278 control-flow and 460 memory-access leaks for the RSA implementation in OpenSSL 1.1.0f. Among those leakages, they find one new vulnerability in RSA after some manual analysis.
-\tool{} finds the vulnerability.  For each leakage site, \tool{} can provide
+\detect{} finds the vulnerability.  For each leakage site, \detect{} can provide
 concrete examples to trigger the issue and give an estimation to
@@
 We also notice that later version of OpenSSL (after 1.0.1) uses a modified version with smaller S-table.
-However, \tool{} also find the leakage sites in the version.
+However, \detect{} also find the leakage sites in the version.
 Recent work also finds the sites through theoretical analysis.
@@
 leakages in RSA occur in the big number implementation. We also find the newer
-versions of RSA in OpenSSL tend to have fewer leakages detected by \tool{}.
+versions of RSA in OpenSSL tend to have fewer leakages detected by \detect{}.
 
-Even for the up-to-date version of OpenSSL, \tool{} still find several
+Even for the up-to-date version of OpenSSL, \detect{} still find several
 side-channel leakages. Figure~\ref{chapter3:fig:unknown_leakage} shows an unknown leakage site in OpenSSL 1.1.1. It is a secret-dependent control flow transfers. 
@@
 Monocypher should be safe under our threat models.
-We analyze those ciphers with \tool{}, and it reports no leaks.
-This indicates that \tool{} is effective for validating countermeasures.
+We analyze those ciphers with \detect{}, and it reports no leaks.
+This indicates that \detect{} is effective for validating countermeasures.
 
@@
 
-\tool{} works on native x86 execution traces.
+\detect{} works on native x86 execution traces.
 The design, which is very precise in terms of true leakages compared to other static source code method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also has the common limitations of dynamic approaches.
-\tool{} may only cover part of the code.
+\detect{} may only cover part of the code.
 Each time we only get one single execution trace.
@@
 While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers.
-For RSA, the latest OpenSSL only has one leakage site that can leak more than 3 bits while there are 22 leakage sites according to \tool{}.
+For RSA, the latest OpenSSL only has one leakage site that can leak more than 3 bits while there are 22 leakage sites according to \detect{}.
 DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort.
 The sampling method  seems simple and may miss some leakages in theory.
-However, the evaluation result shows \tool{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.
+However, the evaluation result shows \detect{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.

### 2021-04-08 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-  \item We implement the above method in a tool called \tool{} and evaluate the tool with several benchmarks and several real-world applications such as OpenSSL, mbedTLS, TinyDNN, and GTK.
+  \item We implement the above method in a tool called \ctool{} and evaluate the tool with several benchmarks and several real-world applications such as OpenSSL, mbedTLS, TinyDNN, and GTK.
 The results show that our tool can detect and quantify the side-channel leakages effectively.
-Moreover, the leakage reports given by the \tool{} can help developers fix the reported vulnerabilities.
+Moreover, the leakage reports given by the \ctool{} can help developers fix the reported vulnerabilities.
 \end{itemize}
@@
 As we can see, the channel have the unique output ($o \in O$) for every input ($k \in K$).
+
+\subsection{Chi-squared Test}
 
@@
 In the example, different keys lead to different index.
-However, as $T_0 + i_0$ equals to $T_1 + i_0$, \tool{} can not observe the difference here, which can cause a false positive.
+However, as $T_0 + i_0$ equals to $T_1 + i_0$, \ can not observe the difference here, which can cause a false positive.
 
@@
 
+\section{Multiple Leakages Sites}
+
 \section{Design}
-In this section, we explain the implementation of \tool{}.
-we first present the overview of \tool{}. After that, we discuss some design details to implement \tool{}.
+In this section, we explain the implementation of \ctool{}.
+we first present the overview of \ctool{}. After that, we discuss some design details to implement \ctool{}.
 
@@
 Figure~\ref{fig:workflow} shows an overview of our side-channel leakages quantification tool.
-Given the source code of the victim program, \tool{} can find the address-based side-channel leakages by fuzzing the victim program.
-To assist the illustration, we divide the workflow of ~\tool{} into three steps.
+Given the source code of the victim program, \ctool{} can find the address-based side-channel leakages by fuzzing the victim program.
+To assist the illustration, we divide the workflow of ~\ctool{} into three steps.
 For the first step, we build the target program from the source code.
@@
 We split the address space into several segments to speed up the comparison according to Meta information.
-Finally, \tool{} Generate the final leakage report.
-For each leakage sites, \tool{} gives the conservative estimation of the information leakage.
+Finally, \ctool{} Generate the final leakage report.
+For each leakage sites, \ctool{} gives the conservative estimation of the information leakage.
 Every leakage site in the report is a true leakage and there is no false positives.
@@
   \includegraphics[width=\columnwidth]{./figures/chapter5/workflow.pdf}
-  \caption{The workflow of \tool{}. We try to divide the \tool{} into three steps to assist the illustration. }\label{fig:workflow}
+  \caption{The workflow of \ctool{}. We try to divide the \ctool{} into three steps to assist the illustration. }\label{fig:workflow}
 \end{figure}
@@
 \subsubsection{Various Granularities Side-channel Detection}
-\tool{} can detect the side-channel vulnerabilities in different granularity.
+\ctool{} can detect the side-channel vulnerabilities in different granularity.
 For each granularity, we calculate a new bitmap that represents access information of each unit.
@@
 \section{Implementation}
-We have implemented a prototype of \tool{}.
+We have implemented a prototype of \ctool{}.
 It takes an input of ELF binary as well as the source code of the corresponding problem.
-The front-end of \tool{} is implemented in Python.
+The front-end of \ctool{} is implemented in Python.
 It can generate random inputs and test the program with those inputs many times.
@@
 The current implementation can support both 64-bits and 32-bits ELF binary in Linux.
-\tool{} will be open-sourced.
+\ctool{} will be open-sourced.
+
+\section{Evaluation}
 
@@
 They use over approximation heuristics method to quantify the leakage.
-For example, CacheAudit estimate that a 128-bit AES encryption can leaks more than 128 bits.
+For example, CacheAudit estimates that a 128-bit AES encryption can leaks more than 128 bits.
 As a result, even those tool reports severe leakage, it does not mean the program has a truly severe leakage.
@@
 
-\tool{} is a dynamic approach.
+\ctool{} is a dynamic approach.
 So it bears the same limitations of dynamic approaches as well.
-\tool{} may have the coverage problem and can miss some side-channel vulnerabilities.
+\ctool{} may have the coverage problem and can miss some side-channel vulnerabilities.
 It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control-flow with various inputs.
-For other libraries like graphic rendering, machine learning, \tool{} is very likely to miss some side-channel vulnerabilities.
-However, \tool{} is not designed to find side-channel vulnerabilities.
-The goal of \tool{} is to pick up those really serious side-channel vulnerabilities from the numerous vulnerabilities.
-So we do not think it is a main limitation of \tool{}.
-However, users of \tool{} should be aware the code coverage problem.
+For other libraries like graphic rendering, machine learning, \ctool{} is very likely to miss some side-channel vulnerabilities.
+However, \ctool{} is not designed to find side-channel vulnerabilities.
+The goal of \ctool{} is to pick up those really serious side-channel vulnerabilities from the numerous vulnerabilities.
+So we do not think it is a main limitation of \ctool{}.
+However, users of \ctool{} should be aware the code coverage problem.
 
-Another limitation is that \tool{} can only find the position in the code that leaks the sensitive information, but it is not the root cause of the leaks.
+Another limitation is that \ctool{} can only find the position in the code that leaks the sensitive information, but it is not the root cause of the leaks.
 Consider the example in Figure~\ref{fig:limitation}, it takes the secret as the input.
@@
 So line 5 is the reason that causes the vulnerability.
-But \tool{} can only tell the line 6 can leak the information, despite it is not the root cause of the vulnerability.
+But \ctool{} can only tell the line 6 can leak the information, despite it is not the root cause of the vulnerability.
 

### 2021-04-08 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 
-In Chapter~\ref{chapter3}, we present the first technique \detect{}.
+In Chapter~\ref{chapter3}, we present a practical address-based side-channel detection tool, \detect{}, that is capable of detecting
+
+In Chapter~\ref{chapter4}, we present a novel method to quantify address-based side-channel leakage.
+We implement the method in a prototype called \tool{} and show its effectiveness in finding and quantifying side-channel leakage.
+With the new definition of information leakage that models actual side-channel attackers, quantifying the number of leaked bits helps understand the severity level of side-channel vulnerabilities.
+The evaluation confirms that \tool{} is useful in estimating the amount of leaked information in real-world applications.
+
+In Chapter~\ref{chapter5}, we propose a fuzzing method to automatically detect and quantify the address-based side-channel leakages automatically.
+The proposed method can produce the conservative estimation of the side-channel leakage of the deterministic program.
+As a result, any severe leakage reported by \ctool{} is the true severe leakage.
+Our evaluation result on both several libraries and benchmarks show that \ctool{} is effective and accurate in detecting the side-channel leakage.

### 2021-04-08 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 
-In Chapter~\ref{chapter3}, we present a practical address-based side-channel detection tool, \detect{}, that is capable of detecting
+In Chapter~\ref{chapter3}, we present a practical address-based side-channel detection tool, \detect{}, that is capable of detecting secret-dependent control-flows and data accesses at the same time.
+We model side-channel leakage sites as math constraints and use dynamic symbolic execution to generate constraints for possible leakages.
+Using statistical testing, \detect{} can identify the true leakages from those constraints.
+Besides, \detect{} analyze the side-channel leakages directly from X86 execution traces.
+Existing binary analysis tools usually transfer the x86 instruction to intermediate languages (IR) simplify the implementation.
+However, such designs have expensive overheads and imprecise analysis results.
+To tackle the problem, we take the engineering efforts and implement the analysis based on Intel developer's manual from scratch.
+We evaluate \detect{} on popular cryptographic libraries including OpenSSL, mbedTLS, Libgcrypt, and Monocyper.
+The evaluation results show that \detect{} is three times to one hundred times faster than the state of art tools while finding all the leakages reported by the previous tools.
+In addition, \detect{} identity new leakages.
+The new leakages was later confirmed by other researchers and software developers.
 
 In Chapter~\ref{chapter4}, we present a novel method to quantify address-based side-channel leakage.
-We implement the method in a prototype called \tool{} and show its effectiveness in finding and quantifying side-channel leakage.
+We quantify the amount of leakage information for a single trace attack.
+The amount of the leaked information is based on the search space reduced by side-channel attacks.
+We rely on \detect{} to detect side-channel leakages.
+After that, we use approximate model counting to quantify the leakage site.
+The method is implemented in a prototype tool called \tool{}.
+We show its effectiveness in quantifying side-channel leakage.
 With the new definition of information leakage that models actual side-channel attackers, quantifying the number of leaked bits helps understand the severity level of side-channel vulnerabilities.
@@
 As a result, any severe leakage reported by \ctool{} is the true severe leakage.
+We also study the total effect of two leakages.
 Our evaluation result on both several libraries and benchmarks show that \ctool{} is effective and accurate in detecting the side-channel leakage.

### 2021-04-08 SupplementaryMaterial/Vita.tex
Updates from Overleaf

% Place your vita below.

Qinkun Bao is a fifth year Ph.D. student at the College of information Sciences
and Technology, The Pennsylvania State University. He is a member of the Software 
System Security Research Lab where he works under the supervision of Dr. Dinghao Wu.
His research interests span reverse engineering, binary analysis, and trusted computations. Before he went to Penn State, he received his bachelor degree in Electronic Engineering and Information Science from University of Science and Technology of China.

### 2021-04-08 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 We also study the total effect of two leakages.
+Using statistical hypothesis testing, we are able to determine if the two leakages are independent.
+If so, we can calculate the sum of the amount of leakage by adding two leakages.
 Our evaluation result on both several libraries and benchmarks show that \ctool{} is effective and accurate in detecting the side-channel leakage.
+
+In conclusion, this dissertation research develops practical techniques for side-channels in software systems.
+For each proposed method, we implement and evaluate it on real-world software.
+The evaluation results show the effeteness and generality of our proposed method.
+We also open source the tool in the dissertation to facilitate the future research in the area.
+
+In the future, we plan to explore the following directions based on the dissertation research.
+
+\textbf{Kernel Space Side-channel Vulnerability Detection.}

### 2021-04-09 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 
-In conclusion, this dissertation research develops practical techniques for side-channels in software systems.
+In conclusion, this dissertation research develops practical techniques for practical and precise side-channel analysis in software systems.
 For each proposed method, we implement and evaluate it on real-world software.
 The evaluation results show the effeteness and generality of our proposed method.
-We also open source the tool in the dissertation to facilitate the future research in the area.
+We also open source the tool in the dissertation to facilitate future research in the area.
 
@@
 \textbf{Kernel Space Side-channel Vulnerability Detection.}
+
+\textbf{Compiler-assisted Side-channel Vulnerability Analysis And Mitigation.}
+
+\textbf{Static Side-channel Quantification.}

### 2021-04-09 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 
-\textbf{Kernel Space Side-channel Vulnerability Detection.}
+\textbf{Kernel Space Side-channel Vulnerability Detection.} There are several side-channel vulnerability detection tools together with the dissertation tool.
+Most of the tools are designed to analyze the side-channel leakages in user-level applications like cryptographic libraries.
+It is reasonable since many side-channel attacks are used to break cryptographic applications.
+Recently, researchers also started to focus on side-channel attacks~\cite{cao2016off} inside the kernel space.
+However, it is non-trivial to apply existing side-channel detection tools in the Linux kernel.
+Take the method in the dissertation, for example.
+We may have the following challenges.
+First, our proposed tools in the dissertation rely on the dynamic binary instrumentation frameworks to collect the runtime information.
+As for kernel programs, a similar task can be achieved by some whole system emulators like BitBlaze~\cite{song2008bitblaze} and S2E~\cite{chipounov2012s2e}.
+S2E uses a modified Linux kernel and QEMU to trace the kernel components.
+S2E uses QEMU 1.0, which does not support the latest Linux kernel.
+The engineering efforts of extending S2E to work on the latest kernel are significant.
+Second, the kernel has very complicated control-flow graphs compared to cryptography libraries.
+Some vulnerabilities need to be triggered by specific input from the user space applications or devices.
+Our tool can not handle interruptions and exceptions.
+But they are common inside the kernel.
+On the positive side, we expect there are plenty of leakage sites inside the kernel.
+The dissertation provide the approaches to pick up ``severe'' leakages automatically.
 
-\textbf{Compiler-assisted Side-channel Vulnerability Analysis And Mitigation.}
-
-\textbf{Static Side-channel Quantification.}
+\textbf{Compiler-assisted Side-channel Vulnerability Analysis and Mitigation.}
+We propose to mitigate the side-channel leakages in a compiler backend.
+For example, the conditional execution can be eliminated by using the masks.
+Eliminating side-channel leakages from compilers is not a brand new idea.
+Coppens et al.~\cite{Coppens:2009:PMT:1607723.1608124} propose several methods to remove several approaches to eliminate all potential leakages that are related to data flow and control flow.
+GNU toolchain adds new options (\textsf{-mlfence-after-load}, \textsf{-mlfence-before-indirect-branch}) to mitigate the Load Value Injection (LVI) attack during the compilation.
+Coppens et al.'s approach has a slowdown with a factor from 2 to 24.
+The LVI harden binaries generated from GNU toolchains takes 6-10x longer to run.
+The performance impact from the aggressive mitigation.
+For example, GNU toolchains inset LFENCE before any possible vulnerable instructions, which include all load instructions, all indirect branches, and return instructions.
+We plan only to change those points that are more likely to leak sensitive information.
+Even more, with the tool presented in the dissertation, we can only modify part of the ''severe`` leakage sites.

### 2021-04-09 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 ApproxFlow~\cite{biondi2018scalable} uses ApproxMC~\cite{chakraborty2016algorithmic} for information flow quantification, but it has only been tested with small programs.
+
+\section{Trace-based Binary Analysis}
+Trace-based binary analysis can be seen as a type of dynamic analysis. It 
+analyzes one concrete program path one time rather than trying to cover
+as many paths as possible. Compared to static analysis, trace-based analysis
+is usually more precise as it can use runtime information. It usually has
+two steps. The first step is collecting trace information. Existing
+approaches usually often rely on binary instrumentation frameworks or emulators (e.g, Intel Pin~\cite{luk2005pin},
+Valgrind~\cite{nethercote2007valgrind}, QEMU). The second step is analyzing the trace using techniques, such
+as symbolic execution, taint analysis. Depending on when the analysis is launched,
+there are two kinds of trace-based analysis, online analysis and offline analysis.
+As the name suggests, online analysis is performed at runtime. The target program's
+data can be modified directly in memory, which is useful in fuzzing because the analysis
+can force the program to go through into a specific branch. Contrary to online analysis,
+offline analysis or post analysis happens when the program finish executions. 
+Trace-based binary analysis has been adopted in several tasks like algorithm
+detection, vulnerability detection and malware analysis. We only mention a few of
+most related works here. Xu et al.~\cite{xu2017cryptographic} introduce bit-wise symbolic execution, which can
+identify crypto algorithms in obfuscated binaries. Ming et al.~\cite{ming2017binsim} use 
+system call sliced segment equivalence checking to do binary diffing. Jia et al.~\cite{jia2017towards}
+perform an offline analysis on execution traces to identify heap overflows.
+
+There are several known binary analysis frameworks that can ease users 
+to launch analysis on binary executable. BitBlaze~\cite{brumley2011bap} is a binary analysis platform
+that provides both the static and dynamic analysis. It uses tracecap plugin to 
+collect execution trace and convert the trace into Vine IR. Binary Analysis Platform (BAP)
+is an another binary analysis platform. Similar to BitBlaze, it use a Pintrace tool to
+collect execution trace and convert the trace into BAP IR. Angr~\cite{shoshitaishvili2016state}, the most popular
+binary analysis platform recently, also support trace-based analysis. It first convert
+each instruction into VEX IR and interpret each IR in Python.
+
+Above existing well-known binary analysis frameworks all adopt the IR layer, which make
+it easy to implement the framework and support multiple architectures. However, it can have
+a very low efficiency and long traces. All IR must be interpreted no matter if symbolic variables
+are involved or not. Besides, as side-channels are low level problems in general, the IR
+design will also lose some information. For example, IR-level branches are not necessarily 
+a super-set or a sub-set of machine-code level branches. Some IR-level branches can be compiled into
+non-branch instructions like conditional moves. Those above limitations motivate us to
+implement a new trace-based binary analysis framework.

### 2021-04-09 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \section{Background and Threat Model}
-In the section, we first provide a brief introduction of the side-channel attacks that exploit the memory access patterns.
-After that, we give an overview of the background knowledge of information theory.
-Finally, we present the threat model of the paper.
-
-In this paper, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs).
-To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.
+In the section, we give an overview of the background knowledge of information theory. Finally, we present the threat model of the paper.
 
@@
 In the rest of paper, we use $\beta(K) \rightarrow O$ to denote a victim program with side-channel vulnerabilities.
+
+In this paper, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs).
+To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.
 
@@
 \section{Evaluation}
+In this section, we evaluate \tool{} on several small benchmarks and real-world software trying to answer the following questions:
+
+\begin{itemize}
+\item \textbf{Effectiveness:} Can \tool{} quantify the information leakage with an conservative estimation? If so, what is loss compared it with the real leakage?
+\item \textbf{Performance:} How much overhead can \tool{} produce?
+\item \textbf{Usage:} What is the real usage of \tool{}? Can \tool{} handle both Cryptography and Non-cryptography libraries? Can \tool{} help developers find and fix side-channel leakages?
+\end{itemize}
+
+\textbf{Evaluation setup.} We run all the following experiment in a server machine with Ubuntu 18.04 LTS.
+The server machine equips with 2.90GHz Intel Xeon(R) E5-2690 CPU with 128GB RAM memory.
+We use the default compilation settings to build the source code of the software into ELF 64-bit executables with GCC 7.5.
+The server has many cores, but we do not use all cores during the evaluation.
+We sometimes run several experiments concurrently.
+The evaluation time presented in the following section is based on a single-core.
+
+\begin{table*}[h]
+\footnotesize
+\caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks), Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DA),The number of instructions\,(Program Size), Symbolic Execution\,(SE), and Monte Carlo\,(MC).}\label{table:over_result}
+\begin{tabular}{lrrrrrrrrrrrr}\toprule
+
+\textbf{Name}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{3}{c}{\textbf{Output Leakage (bits)}} & \multicolumn{3}{c}{\textbf{Maximum Leakage (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{2}{c}{\textbf{Performance}}    \\
+\cmidrule(lr){2-3}\cmidrule(lr){4-6}\cmidrule(lr){7-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}& \# & bits & Byte & Cache Line& Page & Byte & Cache Line& Page & LoC & Size & Fuzzing & Comparison
+\\\midrule
+AES       \\
+AES       \\
+AES \\
+RC4 \\
+RC4 \\
+RC4 \\
+RSA \\
+RSA \\
+Tiny DNN \\
+GDK \\
+Total             \\
+\bottomrule
+\end{tabular}
+
+\end{table*}
+
+\subsection{Overview}
+
+\subsection{Benchmarks}
+\subsubsection{Password Checker}
+
+\subsubsection{Electronic Purse}
+
+\subsubsection{Lookup Table}
+
+\subsection{Cryptography Library}
+
+\subsection{Case Study: Attacks on Multi-class Classification Inference Engine}
+In the section, we demonstrate an attack that can recover the deep learning model inference output by the controlled-channel attack.
+Running the machine learning inference engine inside the enclave is a typical scenario for machine learning as service.
+The machine learning service provider upload the the trained model into an enclave running on the cloud platform and provide machine learning service to a third party user.
+With the help of the enclave, both the model and the user's inferred result is protected from the outside.
+However, we will show that the above information can be easily retrieved from the untrusted world through the side-channel attack.
+
+We use MNIST as the dataset and LeNet-5 for MNIST digits recognition task.
+LeNet-5 is known to work well on handwritten digit recognition.
+We first train the network.
+The batch size in our experiment is 10 and the numbers of epochs is 30.
+After the training, the accuracy of the neural networks on test set images is 99.5\%.
+
+Then we use the model to infer the images. During the inference, we also record the page access information.
+
+\subsection{Case Study: Graphic Libraries}
 

### 2021-04-09 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \section{Background and Threat Model}
-In the section, we give an overview of the background knowledge of information theory. Finally, we present the threat model of the paper.
+In the section, we give an overview of the background knowledge of information theory, and present the threat model of the paper.
 
@@
 value of $K$. The Shannon entropy $H(K)$ is defined as
-\begin{equation}\label{eq1}
+\begin{equation}\label{chapter5:eq1}
   H(K) = - \sum_{k {\in} K}p(k)\log_2(k)
@@
 For example, an AES encryption program takes a 128-bit key as the input.
-Suppose every key has the equal opportunity and $p_k = 1/ 2^{128}$, then the encryption system has $128 \, \mathit{bits}$ information according to Shannon entropy.
+Suppose each key has the equal opportunity and $p_k = 1/ 2^{128}$, then the encryption system has $128 \, \mathit{bits}$ information according to Shannon entropy.
 
-In the paper, we use the channel capacity to describe the information leakages through a channel.
+In the paper, we use the channel capacity to describe the amount of information leakages through a channel.
 In information theory, the channel capacity is used to quantify the rate of information can be reliably transmitted over a channel.
@@
 
-\begin{equation}\label{eq2}
+\begin{equation}\label{chapter5:eq2}
   C(K;O) = \max_{p(x)} I(K;O)
@@
 Here $I(K;O)$ is the mutual information between $K$ and $O$.
-\begin{equation} \label{eq3}
+\begin{equation} \label{chapter5:eq3}
   I(K;O) = \sum_{k {\in} K}{\sum_{o {\in} O}{p(k, o)\log_2\frac{p(k, o)}{p(k)p(o)}}}
@@
 
-While the general case of channel capacity is hard to execute, we consider the two special channels.
+While the channel capacity in general situations is hard to compute, we consider two special channels.
 
@@
 
-\begin{table*}[h]
+\begin{sidewaystable}
 \footnotesize
@@
 
-\end{table*}
+\end{sidewaystable}
 

### 2021-04-09 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \subsubsection{Noiseless Lossless Channel}
-The channel of the system is noiseless and lossless if
+An information channel is noiseless and lossless if
 
-\begin{equation} \label{eq:1}
+\begin{equation} \label{chapter5:eq4}
   C(K;O) = \max_{p(k)} I(K;O) = \max_{p(k)} H|O| =\max_{p(k)} H|K|
@@
 
-Figure~\ref{fig:channel}a shows the example of the type of the channel.
+Figure~\ref{fig:channel}(a) shows an example of the type of the channel.
 Under the circumstance, we always have $P(o_i/k_i) = 1$ and $P(k_i/o_i) = 1$.
@@
 
-Figure~\ref{fig:channel}b  shows the example of the type of the channel.
+Figure~\ref{fig:channel}(b) shows the example of the type of the channel.
 Once the input symbol is determined, the output symbol is also determine.

### 2021-04-09 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \begin{figure}
-  \begin{minipage}{0.48\linewidth}
+  \begin{minipage}{0.45\linewidth}
     \resizebox{\linewidth}{!}{
@@
   \hfill
-  \begin{minipage}{0.48\linewidth}
+  \begin{minipage}{0.45\linewidth}
     \resizebox{\linewidth}{!}{
@@
 \begin{mydef}
-  \label{def}
+  \label{chapter5:def}
   Suppose we have a program $\beta$ with the input set $K$. We randomly select $k_1, k_2, \dots, k_n \in K' \subseteq K$ as the input. We denote it as
@@
 
-With Definition~\ref{def}, we can calculate the information leakage in Figure~\ref{fig:example1} and Figure~\ref{fig:example2} respectively.
+With Definition~\ref{chapter5:def}, we can calculate the information leakage in Figure~\ref{fig:example1} and Figure~\ref{fig:example2} respectively.
 In Figure~\ref{fig:example1}, we have $8$ kinds of observations and each observation is uniformly distributed.
@@
 We test the program with $8$ inputs.
-Therefore, the Shannon entropy of the original K $H(K)$ is also $3\,\mathrm{bits}$, according to Equation~\ref{eq1}.
-Therefore, the leakage in Figure~\ref{fig:example1} show the leakage is leaked totally.
+Therefore, the Shannon entropy of the original K $H(K)$ is also $3\,\mathrm{bits}$.
+According to Equation~\ref{chapter5:eq1}.
+the secret-dependent data accesses in Figure~\ref{fig:example1} can leak the sensitive information totally.
 
 \subsection{A Conservative Estimation}
-In this section, we prove Definition~\ref{def} is the conservative estimation of the amount of leaked information based on the channel capacity.
+In this section, we prove Definition~\ref{chapter5:def} is the conservative estimation of the amount of leaked information based on the channel capacity.
 

### 2021-04-09 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 In Figure~\ref{fig:example2}, there could be $4$ kinds of information, so the information leakages defined by channel capacity is $\log_2{4} = \,2\, \mathrm{bits}$.
-Compared with the result from Definition~\ref{def}, we can see that the amount of leakages by Definition is a conservative estimation.
+Compared with the result from Definition~\ref{chapter5:def}, we can see that the amount of leakages by Definition is a conservative estimation.
 
@@
 The process is like traversing a binary tree and increase the counter of the child node.
-According to Definition~\ref{def}, the amount of the leakage is
+According to Definition~\ref{chapter5:def}, the amount of the leakage is
 

### 2021-04-09 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-Accordingly, if Definition~\ref{def} says the vulnerability leakage has $m$ bits of leakages, then the vulnerability can have at least $m$ bits of leakages.
+Accordingly, if Definition~\ref{chapter5:def} says the vulnerability leakage has $m$ bits of leakages, then the vulnerability can have at least $m$ bits of leakages.
 We can use the definition to detect those severe leakages.

### 2021-04-09 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 
-\subsection{Model Leakages}
 \section{Approximate Model Counting}
@@
 
-According to the Definition~\ref{def}, to calculate the amount of leaked
+According to the Definition~\ref{chapter4:def}, to calculate the amount of leaked
 information, the key is to calculate the cardinality
@@
 can have the following error propagation formula $\Delta L = \frac{\Delta
-        p}{p\ln2}$ by taking the derivative from Definition~\ref{def}. For \tool, we want the error of estimated leaked
+        p}{p\ln2}$ by taking the derivative from Definition~\ref{chapter4:def}. For \tool, we want the error of estimated leaked
 information ($\Delta L$) to be less than 1 bit. So we get $\frac{\Delta
@@
 in the non-bit-slicing implementation (line 6 and line 7 in Figure~\ref{fig:SBOX_da}). The number of leaked bits is
-5.0 and 4.4, respectively. At line 6, according to Definition~\ref{def}, the
+5.0 and 4.4, respectively. At line 6, according to Definition~\ref{chapter4:def}, the
 input set $K$ is $[0,2^8-1]$, the observed input set $K^o$ is $[0,2^3-1]$. Thus,
@@
 \tool{} reaches full precision if the number of estimated leaked bits
-equals to Definition~\ref{def}.
+equals to Definition~\ref{chapter4:def}.
 \tool{} may lose precision from the
@@
 the amount of leakage for some leakage sites in a reasonable time,
-which means the number of $K^o$ is very small. According to Definition~\ref{def}, it means the leakage is very severe.
+which means the number of $K^o$ is very small. According to Definition~\ref{chapter4:def}, it means the leakage is very severe.

### 2021-04-09 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-\begin{equation} \label{eq:2}
+\begin{equation} \label{chapter:eq:5}
   C(K;O) = \max_{p(x)} I(K;O) = \max_{p(x)} H |O| = \log_2 {|O|}
@@
   \end{minipage}
-  \caption{A Serious Leakage}\label{fig:example1}
+  \caption{A Serious Leakage}\label{chapter5:fig:example1}
 \end{figure}
@@
   \end{minipage}
-  \caption{A Minor Leakage. }\label{fig:example2}
+  \caption{A Minor Leakage. }\label{chapter5:fig:example2}
 \end{figure}
@@
 
-With Definition~\ref{chapter5:def}, we can calculate the information leakage in Figure~\ref{fig:example1} and Figure~\ref{fig:example2} respectively.
-In Figure~\ref{fig:example1}, we have $8$ kinds of observations and each observation is uniformly distributed.
+With Definition~\ref{chapter5:def}, we can calculate the information leakage in Figure~\ref{chapter5:fig:example1} and Figure~\ref{chapter5:fig:example2} respectively.
+In Figure~\ref{chapter5:fig:example1}, we have $8$ kinds of observations and each observation is uniformly distributed.
 Therefore, the information leakage is $log_2{8} = 3$ bits.
-In Figure~\ref{fig:example2}, we have $4$ kinds of observations and each observation is also uniformly distributed.
+In Figure~\ref{chapter5:fig:example2}, we have $4$ kinds of observations and each observation is also uniformly distributed.
 Therefore, the information leakage is $log_2{4} = 2$ bits.
@@
 According to Equation~\ref{chapter5:eq1}.
-the secret-dependent data accesses in Figure~\ref{fig:example1} can leak the sensitive information totally.
+the secret-dependent data accesses in Figure~\ref{chapter5:fig:example1} can leak the sensitive information totally.
 
@@
 We can use the definition to detect those severe leakages.
-In the examples of Figure~\ref{fig:example1} and Figure~\ref{fig:example2}, because the input secret range from $0$ to $255$, we can calculate the precise value of the amount of information leakage by iterating each input keys.
-In Figure~\ref{fig:example1}, each item in the array could be read.
-Therefore, the channel capacity in Figure~\ref{fig:example1} is $\log_2{128} = \,7\, \mathrm{bits}$.
-In Figure~\ref{fig:example2}, there could be $4$ kinds of information, so the information leakages defined by channel capacity is $\log_2{4} = \,2\, \mathrm{bits}$.
+In the examples of Figure~\ref{chapter5:fig:example1} and Figure~\ref{chapter5:fig:example2}, because the input secret range from $0$ to $255$, we can calculate the precise value of the amount of information leakage by iterating each input keys.
+In Figure~\ref{chapter5:fig:example1}, each item in the array could be read.
+Therefore, the channel capacity in Figure~\ref{chapter5:fig:example1} is $\log_2{128} = \,7\, \mathrm{bits}$.
+In Figure~\ref{chapter5:fig:example2}, there could be $4$ kinds of information, so the information leakages defined by channel capacity is $\log_2{4} = \,2\, \mathrm{bits}$.
 Compared with the result from Definition~\ref{chapter5:def}, we can see that the amount of leakages by Definition is a conservative estimation.
@@
 \subsection{Overview}
-Figure~\ref{fig:workflow} shows an overview of our side-channel leakages quantification tool.
+Figure~\ref{chapter5:fig:workflow} shows an overview of our side-channel leakages quantification tool.
 Given the source code of the victim program, \ctool{} can find the address-based side-channel leakages by fuzzing the victim program.
@@
   \includegraphics[width=\columnwidth]{./figures/chapter5/workflow.pdf}
-  \caption{The workflow of \ctool{}. We try to divide the \ctool{} into three steps to assist the illustration. }\label{fig:workflow}
+  \caption{The workflow of \ctool{}. We try to divide the \ctool{} into three steps to assist the illustration. }\label{chapter5:fig:workflow}
 \end{figure}
@@
 \subsubsection{Estimate The Leaked Information}
-According to Definition~\ref{def}, we quantify the information leakage based on the distribution of the observation.
+According to Definition~\ref{chapter5:def}, we quantify the information leakage based on the distribution of the observation.
 If we calculate the information leakage from an $4MB$ memory area, then the length of the byte-level bitmap is $4*1024*1024 = 4194304$.
@@
 \footnotesize
-\caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks), Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DA),The number of instructions\,(Program Size), Symbolic Execution\,(SE), and Monte Carlo\,(MC).}\label{table:over_result}
+\caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks), Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DA),The number of instructions\,(Program Size), Symbolic Execution\,(SE), and Monte Carlo\,(MC).}\label{chapter5:table:over_result}
 \begin{tabular}{lrrrrrrrrrrrr}\toprule

### 2021-04-09 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \section{Evaluation}
-In this section, we evaluate \tool{} on several small benchmarks and real-world software trying to answer the following questions:
+In this section, we evaluate \ctool{} on several small benchmarks and real-world software trying to answer the following questions:
 
 \begin{itemize}
-\item \textbf{Effectiveness:} Can \tool{} quantify the information leakage with an conservative estimation? If so, what is loss compared it with the real leakage?
-\item \textbf{Performance:} How much overhead can \tool{} produce?
-\item \textbf{Usage:} What is the real usage of \tool{}? Can \tool{} handle both Cryptography and Non-cryptography libraries? Can \tool{} help developers find and fix side-channel leakages?
+\item \textbf{Effectiveness:} Can \ctool{} quantify the information leakage with an conservative estimation? If so, what is the loss compared it with the real leakage?
+\item \textbf{Performance:} How much overhead can \ctool{} produce?
+\item \textbf{Usage:} What is the real usage of \ctool{}? Can \ctool{} handle both Cryptography and Non-cryptography libraries? Can \ctool{} help developers find and fix side-channel leakages?
 \end{itemize}
@@
 \caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks), Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DA),The number of instructions\,(Program Size), Symbolic Execution\,(SE), and Monte Carlo\,(MC).}\label{chapter5:table:over_result}
+\centering
 \begin{tabular}{lrrrrrrrrrrrr}\toprule

### 2021-04-10 Appendix-A/Appendix-A.tex
Updates from Overleaf

@@
 
-\section{Introduction}
+\section*{Introduction}
 
@@
 
-\section{Requirements}
+\section*{Requirements}
 We have tested \tool{} on both macOS and Ubuntu.
@@
 
-\section{Installation}
+\section*{Installation}
 
@@
 \end{lstlisting}
-\section{Run the hello world example}
+\section*{Run the hello world example}
 In this section, we walk you through the steps to test a simple function with \tool{}.
@@
 
-\subsection{Mark secret data as symbolic}
+\subsection*{Mark secret data as symbolic}
 In order to test this function with \tool{}, we need to mark the variable that representing the secret data as a symbolic variable.
@@
 
-\subsection{Build the example}
+\subsection*{Build the example}
 
@@
 
-\subsection{Collect the trace}
+\subsection*{Collect the trace}
 We use the pin tool to collect the execution trace. The tool can automatically collect the trace and other necessary runtime information.
@@
 
-\subsection{Quantify the leakage}
+\subsection*{Quantify the leakage}
 To analyze the execution trace and generate the report, run the below command:
@@
 
-\section{Analyze Cryptography Function}
+\section*{Analyze Cryptography Function}
 We have applied \tool{} on the following libraries:
@@
 
-\section{Command-line Options}
+\section*{Command-line Options}
 \tool{} takes the trace file as the input (\textsf{Inst\_data.txt}). Besides the trace file, \tool{} has the following command-line options:

### 2021-04-10 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers.
-For RSA, the latest OpenSSL only has one leakage site that can leak more than 3 bits while there are 22 leakage sites according to \detect{}.
-DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort.
+The DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort.
+After we manually analyze those leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which partially explain why developers are not interested in fix all the leakages.
+
+We use a sampling method to detect side-channel leakages.
 The sampling method seems simple and may miss some leakages in theory.

### 2021-04-10 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \section{Multiple Leakages Sites}
+Real-world software can have various side-channel vulnerabilities.
+Those vulnerabilities may spread in the whole program.
+An adversary may exploit more than one side-channel vulnerabilities to gain more information~\cite{7163052, 191010}.
+In order to precisely quantify the
+total information leakage, we need to know the relation of those leakage sites.
+
+Suppose one program has two side-channel vulnerabilities A and B, which can leak $L_A$ and $L_B$ bits respectively according to the definition~\ref{chapter5:def}. 
+Depending on the relation between A and B, the total leaked information $L_{\mathit{total}}$ will be:
+
+\subsection{Independent Leakages}
+If A and B are independent leakages, the total information leakage will be:
+$$L_{\mathit{total}} = L_A + L_B $$
+
+\subsection{Dependent Leakages}
+If A and B are dependent leakages, the total information leakage will be:
+$$\max{\{L_A, L_B\}}  \leq L_{\mathit{total}} < L_A + L_B$$
 
@@
 \item \textbf{Effectiveness:} Can \ctool{} quantify the information leakage with an conservative estimation? If so, what is the loss compared it with the real leakage?
-\item \textbf{Performance:} How much overhead can \ctool{} produce?
+\item \textbf{Performance:} What are overhead costs of \ctool{}?
 \item \textbf{Usage:} What is the real usage of \ctool{}? Can \ctool{} handle both Cryptography and Non-cryptography libraries? Can \ctool{} help developers find and fix side-channel leakages?
@@
 
-\subsection{Overview}
+\subsection{Result Overview}
 

### 2021-04-10 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 
+\subsection{Attack Models}
+Previous work~\cite{182946} classifies the address-based side-channel attacks into three type based on the type of information that an attacker can learn during the attack.
+\subsubsection*{Time-based Attacks}
+In time-based attacks, an attacker can monitor the execution time of a victim.
+It could be the overall execution time or the execution time of some interesting points (e.g.
+a function).
+The execution time is correlated to some events (e.g., cache hits, cache misses, page faults) during the execution.
+Example of those attacks include remote timing attacks, Bernstein attack on AES, and Kocher’s original attack from CRYPTO 96.
+\subsubsection*{Access-based Attacks}
+\subsubsection*{Trace-based Attacks}
+
 \subsection{Target Applications}
@@
 
-\subsubsection{Cryptography Libraries}
+\subsubsection*{Cryptography Libraries}
 \begin{table}
@@
 
-\subsubsection{Machine Learning Applications}
+\subsubsection*{Machine Learning Applications}
 Recent side-channel attacks on machine learning applications mainly focus on recovering two types of the sensitive information: the input of the model, and the architecture of deep learning models.
@@
 We find that all existing approaches need a lot of domain knowledge and expertise to launch the attacks.
-\subsubsection{Media and Graphic Libraries}
+\subsubsection*{Media and Graphic Libraries}
 A few of recent work also studies the side-channel attacks in media and graphic libraries.
@@
 They use the machine learning to pick cache lines that can be exploitable to leak most information.
-\subsubsection{Others}
+\subsubsection*{Others}
 Some other side-channel targets also include spell checking tools, and font libraries~\cite{xu2015controlled}.

### 2021-04-10 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 
-\subsubsection{Secret-dependent control-flows}
+\subsubsection{Secret-dependent Control-flows}
 An adversary can infer sensitive information from secret dependent control-flows.
@@
 
-\subsubsection{Secret-dependent data access}
+\subsubsection{Secret-dependent Data Accesses}
 Like input-dependent control-flow transfers, an adversary can also infer sensitive information from the data access pattern as well.

### 2021-04-10 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 
-\subsection{Execution trace generation} The design goal of \tool{} is to estimate the information leakage as precisely as possible.
+\subsection{Execution Trace Generation} The design goal of \tool{} is to estimate the information leakage as precisely as possible.
 We run the target binary under a dynamic binary instrumentation (DBI) tool
@@
 
-\subsection{Instruction level symbolic execution} We model attackers'
+\subsection{Instruction Level Symbolic Execution} We model attackers'
 observations from side-channel vulnerabilities with logic formulas.
@@
 
-\subsection{Leakage estimation} 
+\subsection{Leakage Estimation} 
 We change the information leakage quantification problem into the counting problem. We propose a

### 2021-04-10 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
-\chapter{Conclusion and Future Work}\label{chapter6}
+\chapter{Conclusion}\label{chapter6}
 This dissertation research studies the address-based side-channel leakages in two aspects: detection and quantification.
@@
 In the side-channel vulnerability quantification research, we propose two different side-channel leakage quantification tools based on information theory.
+
+\section{Summary}
 
@@
 We also open source the tool in the dissertation to facilitate future research in the area.
-
+\section{Future Directions}
 In the future, we plan to explore the following directions based on the dissertation research.

### 2021-04-10 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 \subsubsection*{Time-based Attacks}
-In time-based attacks, an attacker can monitor the execution time of a victim.
+In time-based attacks, an adversary can monitor the execution time of a victim.
 It could be the overall execution time or the execution time of some interesting points (e.g.
@@
 \subsubsection*{Access-based Attacks}
+In access-based attacks, an adversary can 
 \subsubsection*{Trace-based Attacks}

### 2021-04-11 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 If the victim enclave program accesses the memory table, then the OS can observe the page faults and  know which page is accessed.
-While the granularity of the controlled-channel attacks is coarse-grained, the controlled-channel attacks allow the attacker to have a noise-free observation.
+While the granularity of the controlled-channel attacks is coarse-grained,  controlled-channel attacks allow the attacker to have a noise-free observation.
 Other examples like the TLB side-channel attack, DDRAM attacks share the same page-level granularity.
@@
 The execution time is correlated to some events (e.g., cache hits, cache misses, page faults) during the execution.
-Example of those attacks include remote timing attacks, Bernstein attack on AES, and Kocher’s original attack from CRYPTO 96.
+Examples of those attacks include remote timing attacks~\cite{brumley2005remote}, Bernstein attack on AES~\cite{bernstein2005cache}, and Kocher’s original attack~\cite{kocher1996timing} from CRYPTO 96.
 \subsubsection*{Access-based Attacks}
-In access-based attacks, an adversary can 
+In access-based attacks, an adversary can probe one time only after the termination of the victim program.
+The attacker can learn the outcome of each memory access.
+For example, a cache-based channel attack can know which memory access incurs a cache hit and which memory access incurs a cache miss.
+Because an attacker can probe the victim program after the execution, the attacker do not know the order of accesses.
+Access-based attacks often happen in the cloud computing environment when the attacker and victim share the same hardware (e.g., L3 Cache).
+Examples of those attacks include cache template attacks~\cite{191010}, Prime and Probe attacks~\cite{liu2015last}, and Flush and Reload attacks~\cite{yarom2014flush+}.
 \subsubsection*{Trace-based Attacks}
+In trace-based attacks, an adversary can probe the victim program at any point.
+The attacker can learn the order of memory accesses.
+Suppose the victim program has two functions \textsf{a} and \textsf{b}.
+In an access-based attacks, the attacker can learn both \textsf{a} and \textsf{b} are executed.
+In a trace-based attacks, the attacker can know the execution sequence of two functions (e.g., $aabbb$).
+Controlled-channel attacks~\cite{moghimi2020copycat, xu2015controlled} belong to the category, where a malicious operating system can interrupt the victim applications and probe the program at any time.
 
@@
 real-world applications. On the contrary, \tool{} assesses the sensitive level
-of side-channels with different granularities. It can also analyze side-channels
-in real-world cryptographic libraries.
+of side-channels with different granularities. It can also analyze side-channels in real-world cryptographic libraries.
 

### 2021-04-11 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \section{Multiple Leakages Sites}
-Real-world software can have various side-channel vulnerabilities.
+Real-world software can have many side-channel vulnerabilities.
 Those vulnerabilities may spread in the whole program.
@@
 total information leakage, we need to know the relation of those leakage sites.
+
+\begin{figure}[h]
+\begin{minipage}{0.4\linewidth}
+\begin{lstlisting}
+void function1(uint8_t* secret)
+{
+  uint8_t k1, k2;
+  k1 = secret[1];
+  k2 = secret[2];
+  if (k1 > k2)
+    a();
+  if (k1 + k2 < 256)
+    b();
+  ...
+}
+\end{lstlisting}
+\end{minipage}
+\hfill
+\begin{minipage}{0.4\linewidth}
+\begin{lstlisting}
+void function2(uint8_t* secret)
+{
+  uint8_t k1, k2;
+  k1 = secret[1];
+  k2 = secret[2];
+  if (k1 + k2 > 128)
+    a();
+  if (k1 > 64)
+    b();
+  ...
+}
+\end{lstlisting}
+\end{minipage}
+\caption{Mutiple Leakages}\label{chapter5:fig:mutiple}
+\end{figure}
 

### 2021-04-11 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 }
-\end{lstlisting}
+\end{lstlisting}\caption*{(a) Independent Leakages}
 \end{minipage}
@@
   if (k1 + k2 > 128)
-    a();
+    c();
   if (k1 > 64)
-    b();
+    d();
   ...
 }
-\end{lstlisting}
+\end{lstlisting} \caption*{(b) Dependent Leakages}
 \end{minipage}
-\caption{Mutiple Leakages}\label{chapter5:fig:mutiple}
+\caption{Multiple Leakages}\label{chapter5:fig:multiple}
 \end{figure}
+
+Considering the examples in Figure~\ref{chapter5:fig:multiple}, Figure~\ref{chapter5:fig:multiple}(a) show a code snippet with two leakage sites at line 6 and line 8 respectively.
+For example, if an adversary observes that function \textsf{a} executes, then the attacker can infer the first byte in buffer \textsf{secret} is larger than the second byte.
+Similarly, if an adversary observes that function \textsf{b} executes, then the attacker can infer that the sum of first two bytes in buffer \textsf{secret} is smaller than $256$.
 

### 2021-04-11 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-\subsection{Chi-squared Test}
-
+\subsection{Chi-Squared Test}
+A chi-squared test can determine if there is a relationship between two categorical variables.
+Suppose we can summarize the data in a $rxc$  two-way contingency table.
+The chi-square test statistic is calculated with the below formula:
+\[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k}\]
+$O$ is the observe value and $E$ is the expected value. A low value means that there is a high correlation between the two variables. 
 \subsection{Threat Model and Math Notation}
@@
     c();
-  if (k1 > 64)
+  if (k1 > 32)
     d();
@@
 For example, if an adversary observes that function \textsf{a} executes, then the attacker can infer the first byte in buffer \textsf{secret} is larger than the second byte.
-Similarly, if an adversary observes that function \textsf{b} executes, then the attacker can infer that the sum of first two bytes in buffer \textsf{secret} is smaller than $256$.
+Similarly, if an adversary observes that function \textsf{b} executes, then the attacker can infer that the sum of the first two bytes in buffer \textsf{secret} is smaller than $256$.
+The interesting part here is that if the attacker observes that function \textsf{a} executes, then he still has zero knowledge about the function \textsf{b}.
+The two leakage sites in Figure~\ref{chapter5:fig:multiple}(b) are different.
+If an attacker observes function \textsf{c} executes, then it is likely the attacker can observe that function \textsf{d} also executes.
 
@@
 $$\max{\{L_A, L_B\}}  \leq L_{\mathit{total}} < L_A + L_B$$
+
+We use the chi-square test to check if two leakage sites are independent.
+Here we run the example in Figure~\ref{chapter5:fig:multiple} many times.
+We record the times of the observation of the execution.
+Because each time, the execution is independent of the previous execution.
+The times of the observation for each event should satisfy the normal distribution.
+After that, we can use the chi-squared test to test whether the two leakage sites are independent.
+
+\begin{figure}[h]
+  \begin{minipage}{0.4\linewidth}
+      \begin{tabular}{rrrr}
+        \toprule
+        & $c$ & $c$  & total\\
+        \midrule
+        $d$   & 255 & 253 &     \\
+        $d$   & 260  & 256 &       \\
+        total &   &        \\
+        \bottomrule
+      \end{tabular}%
+  \end{minipage}
+  \hfill
+  \begin{minipage}{0.4\linewidth}
+      \begin{tabular}{rrrr}
+        \toprule
+        & $c$ & $c$  & total\\
+        \midrule
+        $d$   & 809 & 82 &     \\
+        $d$   & 70  & 63&       \\
+        total &   &        \\
+        \bottomrule
+      \end{tabular}%
+  \end{minipage}
+  \caption{}\label{chapter5:fig:con_table}
+\end{figure}
 
@@
   \centering
-  \resizebox{0.45\textwidth}{!}{%
+  \resizebox{0.8\textwidth}{!}{%
 

### 2021-04-11 Chapter-5/Chapter-5.tex
Updates from Overleaf
update

@@
 
-\subsection{Chi-Squared Test}
-A chi-squared test can determine if there is a relationship between two categorical variables.
-Suppose we can summarize the data in a $rxc$  two-way contingency table.
-The chi-square test statistic is calculated with the below formula:
-\[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k}\]
-$O$ is the observe value and $E$ is the expected value. A low value means that there is a high correlation between the two variables. 
 \subsection{Threat Model and Math Notation}
@@
 If A and B are dependent leakages, the total information leakage will be:
-$$\max{\{L_A, L_B\}}  \leq L_{\mathit{total}} < L_A + L_B$$
+\[\max{\{L_A, L_B\}}  \leq L_{\mathit{total}} < L_A + L_B\]
 
 We use the chi-square test to check if two leakage sites are independent.
+A chi-squared test can determine if there is a relationship between two categorical variables.
+Suppose we can summarize the data in a $rxc$  two-way contingency table.
+The chi-square test statistic is calculated with the below formula:
+\[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k}\]
+$O$ is the observe value and $E$ is the expected value. A low value means that there is a high correlation between the two variables.
+
 Here we run the example in Figure~\ref{chapter5:fig:multiple} many times.
@@
         \midrule
-        $d$   & 255 & 253 &     \\
-        $d$   & 260  & 256 &       \\
-        total &   &        \\
+        $d$   & 255 & 253 &   508  \\
+        $d$   & 260  & 256 &    516   \\
+        total &   515 &  509   & 1,024   \\
         \bottomrule
@@
         \midrule
-        $d$   & 809 & 82 &     \\
-        $d$   & 70  & 63&       \\
-        total &   &        \\
+        $d$   & 809 & 82 & 891    \\
+        $d$   & 70  & 63&  133     \\
+        total &  879 &  145  & 1,024    \\
         \bottomrule

### 2021-04-11 Chapter-5/Chapter-5.tex
update

@@
 A chi-squared test can determine if there is a relationship between two categorical variables.
-Suppose we can summarize the data in a $rxc$  two-way contingency table.
+Suppose we can summarize the data in a $r*c$  two-way contingency table.
 The chi-square test statistic is calculated with the below formula:
 \[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k}\]
-$O$ is the observe value and $E$ is the expected value. A low value means that there is a high correlation between the two variables.
+Here $O$ is the observe value and $E$ is the expected value. A low value means that there is a high correlation between the two variables.
 
-Here we run the example in Figure~\ref{chapter5:fig:multiple} many times.
-We record the times of the observation of the execution.
-Because each time, the execution is independent of the previous execution.
-The times of the observation for each event should satisfy the normal distribution.
+Take the example in Figure~\ref{chapter5:fig:multiple}, suppose we test them with various random inputs $1024$ times.
+We record the total times that we get the same observation.
+For each time, the execution is independent of the previous execution.
+The times of the same observation for each event should satisfy the normal distribution.
 After that, we can use the chi-squared test to test whether the two leakage sites are independent.
@@
 \begin{figure}[h]
-  \begin{minipage}{0.4\linewidth}
+  \begin{minipage}{0.45\linewidth}
       \begin{tabular}{rrrr}
         \toprule
-        & $c$ & $c$  & total\\
+        & $c$ & $\lnot c$  & total\\
         \midrule
-        $d$   & 255 & 253 &   508  \\
-        $d$   & 260  & 256 &    516   \\
+        $d$   & 255 (255.5) & 253 (252.5) &   508  \\
+        $\lnot d$   & 260 (259.5)  & 256 (256.5) &    516   \\
         total &   515 &  509   & 1,024   \\
@@
   \hfill
-  \begin{minipage}{0.4\linewidth}
+  \begin{minipage}{0.45\linewidth}
       \begin{tabular}{rrrr}
         \toprule
-        & $c$ & $c$  & total\\
+        & $c$ & $\lnot c$  & total\\
         \midrule
-        $d$   & 809 & 82 & 891    \\
-        $d$   & 70  & 63&  133     \\
+        $d$   & 809 (764.8) & 82 (126.2) & 891    \\
+        $\lnot d$   & 70 (114.2)  & 63 (18.8)&  133     \\
         total &  879 &  145  & 1,024    \\
@@
   \end{minipage}
-  \caption{}\label{chapter5:fig:con_table}
+  \caption{The Contingency Table for the experiments. The numbers in the bracket are expected values. }\label{chapter5:fig:con_table}
 \end{figure}

### 2021-04-11 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 Suppose we can summarize the data in a $r*c$  two-way contingency table.
-The chi-square test statistic is calculated with the below formula:
+The chi-square test statistic and the degrees of freedom $v$ is calculated with the below formula:
 \[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k}\] 
+\[v = (r - 1)(c - 1)\]
 Here $O$ is the observe value and $E$ is the expected value. A low value means that there is a high correlation between the two variables.
 
-Take the example in Figure~\ref{chapter5:fig:multiple}, suppose we test them with various random inputs $1024$ times.
-We record the total times that we get the same observation.
+The null hypothesis is that the two leakages are independent.
+We generate random inputs as the secret and record the memory access for each execution.
 For each time, the execution is independent of the previous execution.
@@
         \toprule
-        & $c$ & $\lnot c$  & total\\
+        & $a$ & $\lnot a$  & total\\
         \midrule
-        $d$   & 255 (255.5) & 253 (252.5) &   508  \\
-        $\lnot d$   & 260 (259.5)  & 256 (256.5) &    516   \\
+        $b$   & 255 (255.5) & 253 (252.5) &   508  \\
+        $\lnot b$   & 260 (259.5)  & 256 (256.5) &    516   \\
         total &   515 &  509   & 1,024   \\

### 2021-04-11 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 If A and B are independent leakages, the total information leakage will be:
-$$L_{\mathit{total}} = L_A + L_B $$
+\[L_{\mathit{total}} = L_A + L_B \]
 
@@
 \begin{figure}[h]
-  \begin{minipage}{0.45\linewidth}
+  \begin{minipage}{0.40\linewidth}
       \begin{tabular}{rrrr}
@@
         \bottomrule
-      \end{tabular}%
+      \end{tabular}\caption*{(a)}
   \end{minipage}
+\hspace{-15pt}
 \hfill
-  \begin{minipage}{0.45\linewidth}
+\hspace{-15pt}
+  \begin{minipage}{0.40\linewidth}
       \begin{tabular}{rrrr}
@@
         \bottomrule
-      \end{tabular}%
+      \end{tabular}\caption*{(b)}
   \end{minipage}
-  \caption{The Contingency Table for the experiments. The numbers in the bracket are expected values. }\label{chapter5:fig:con_table}
+  \caption{The contingency table for the experiments. The numbers in the bracket are expected values. }\label{chapter5:fig:con_table}
 \end{figure}
 
+Assume we generate $1024$ random inputs and record the memory access each time.
+For the example in Figure~\ref{chapter5:fig:multiple}, we use $a$ to denote the function \textsf{a} executes and $\lnot a$ to denote the function \textsf{a} does not execute during the execution.
+After we calculate the number of the same observation, we get the contingency table shown in Figure~\ref{chapter5:fig:con_table}.
 \section{Design}

### 2021-04-11 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 For the example in Figure~\ref{chapter5:fig:multiple}, we use $a$ to denote the function \textsf{a} executes and $\lnot a$ to denote the function \textsf{a} does not execute during the execution.
-After we calculate the number of the same observation, we get the contingency table shown in Figure~\ref{chapter5:fig:con_table}.
+After calculating the number of the same observation, we get the contingency table shown in Figure~\ref{chapter5:fig:con_table}.
+Suppose the observations of function \textsf{a} and function \textsf{b} are independent.
+We calculate the expected value for the observation $ab$ based on the frequency.
+\[ E_{ab} = \frac{(255+256)*(255+253)}{1024} = 255.5\]
+Similarly, we calculate the rest expected values with the hypothesis that the leakages are independent and fill in them in Figure~\ref{chapter5:fig:con_table}.
+The degree of freedom $v$ is $(2-1)*(2-1) = 1$.
+
 \section{Design}

### 2021-04-12 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
   \end{minipage}
-  \caption{A Serious Leakage}\label{chapter5:fig:example1}
+  \caption{A Serious Leakage.}\label{chapter5:fig:example1}
 \end{figure}
@@
   \hfill
-  \begin{minipage}{0.6\linewidth}
+  \begin{minipage}{0.5\linewidth}
     \resizebox{\textwidth}{!}{
@@
 
+Based on the equation, we calculate the chi-square test statistic for two leakage sites in Figure~\ref{chapter5:fig:multiple} (a) and (b).
+
+\[\tilde{\chi}^2_{a}= \frac{(255.5-255)^2}{255.5} + \frac{(252.5-253)^2}{252.5} + \frac{(259.5-260)^2}{259.5} + \frac{(256.5-256)^2}{256.5} = 0.004\] 
+\[\tilde{\chi}^2_{b}= \frac{(764.8-809)^2}{764.8} + \frac{(126.2-82)^2}{126.2} + \frac{(114.2-70)^2}{114.2} + \frac{(18.8-63)^2}{18.8} = 139.1\]
+
+According to Chi Square Distribution Table, we have the probability $p=0.95$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (a).
+We have the probability $p=0.00$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (b).
 \section{Design}

### 2021-04-12 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-According to Chi Square Distribution Table, we have the probability $p=0.95$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (a).
-We have the probability $p=0.00$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (b).
+According to Chi Square Distribution Table, we have the probability $p\approx0.95$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (a).
+We have the probability $p\approx0.00$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (b).
 \section{Design}

### 2021-04-12 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
   \centering
-  \includegraphics[width=\columnwidth]{./figures/chapter5/channel.pdf}
+  \includegraphics[width=.8\columnwidth]{./figures/chapter5/channel.pdf}
   \caption{The relationship between the side-channel attack and the channel capacity.
@@
 We have the probability $p\approx0.00$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (b).
+Therefore, we infer that the two leakages in Figure~\ref{chapter5:fig:multiple} (a) are independent.
+And the two leakages Figure~\ref{chapter5:fig:multiple} (b) are dependent.
+For each leakage points, we use the above method to test if any two leakage sites are independent.
+We combine them into a leakage are calculate the total amount of the leakage.
 \section{Design}

### 2021-04-14 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 And the two leakages Figure~\ref{chapter5:fig:multiple} (b) are dependent.
+In this paper, for any two leakage, if $p < 0.03$, we think the two leakage sites are independent.
 For each leakage points, we use the above method to test if any two leakage sites are independent.
@@
 We use the default compilation settings to build the source code of the software into ELF 64-bit executables with GCC 7.5.
-The server has many cores, but we do not use all cores during the evaluation.
-We sometimes run several experiments concurrently.
-The evaluation time presented in the following section is based on a single-core.
 
@@
 \footnotesize
-\caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks), Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DA),The number of instructions\,(Program Size), Symbolic Execution\,(SE), and Monte Carlo\,(MC).}\label{chapter5:table:over_result}
+\caption{Evaluation results overview: Name of the benchmark, The Size of the Input Data, The number of leaked functions, The Maximum Leakage, The size of the benchmark, and The Performance.}\label{chapter5:table:over_result}
 \centering
-\begin{tabular}{lrrrrrrrrrrrr}\toprule
+\begin{tabular}{lrrrrrrrrrrrrr}\toprule
 
-\textbf{Name}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{3}{c}{\textbf{Output Leakage (bits)}} & \multicolumn{3}{c}{\textbf{Maximum Leakage (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{2}{c}{\textbf{Performance}}    \\
-\cmidrule(lr){2-3}\cmidrule(lr){4-6}\cmidrule(lr){7-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}& \# & bits & Byte & Cache Line& Page & Byte & Cache Line& Page & LoC & Size & Fuzzing & Comparison
+\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{3}{c}{\textbf{\# Leakage Functions}} & \multicolumn{3}{c}{\textbf{Maximum Leakage (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\
+\cmidrule(lr){2-3}\cmidrule(lr){4-6}\cmidrule(lr){7-9}\cmidrule(lr){10-11}\cmidrule(lr){12-14}& \# & bits & Byte & Cache Line& Page & Byte & Cache Line& Page & LoC & Size & Fuzzing & Comparison & Chi-squared
 \\\midrule
-AES       \\
-AES       \\
-AES \\
-RC4 \\
-RC4 \\
-RC4 \\
-RSA \\
-RSA \\
-Tiny DNN \\
-GDK \\
-Total             \\
+Safe Password Checker& 65536& 16.0\\
+Unsafe Password Checker & 65536 & 16.0\\
+One-byte Lookup Table & 65536 & 16.0\\
+Four-byte Lookup Table & 65536 & 16.0\\
+AES mbedTLS 2.15 & 65536 & 16.0   \\
+AES OpenSSL 1.1.0  & 65536 & 16.0    \\
+AES OpenSSL 1.1.1& 65536 & 16.0 \\
+AES wolfSSL 4.5.0& 65536 & 16.0\\
+AES Libgcrypt 1.8.7& 65536 & 16.0\\
+RC4 mbedTLS 2.15& 65536 & 16.0\\
+RC4 OpenSSL 1.1.0& 65536 & 16.0\\
+RC4 OpenSSL 1.1.1& 65536 & 16.0\\
+RC4 wolfSSL 4.5.0& 65536 & 16.0\\
+RSA mbedTLS 2.15& 4096 & 12.0\\
+RSA OpenSSL 1.1.0& 4096 & 12.0\\
+RSA OpenSSL 1.1.1& 4096 & 12.0\\
+RSA wolfSSL 4.5.0& 4096 & 12.0\\
+RSA Libgcrypt 1.8.7& 4096 & 12.0 \\
+Tiny DNN & 12000 & 13.6 &\\
+GDK 3.24.23 & 65535 & 16.0 &\\
 \bottomrule
@@
 \subsubsection{Password Checker}
-
-\subsubsection{Electronic Purse}
 
@@
 Then we use the model to infer the images. During the inference, we also record the page access information.
-
-\subsection{Case Study: Graphic Libraries}
 
@@
   \centering
-  \begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
+  \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
 int foo(uint8_t secret){

### 2021-04-14 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 The server machine equips with 2.90GHz Intel Xeon(R) E5-2690 CPU with 128GB RAM memory.
-We use the default compilation settings to build the source code of the software into ELF 64-bit executables with GCC 7.5.
+We use the default release settings to build the source code of the software into ELF 64-bit executables with GCC 7.5.
 
@@
 \textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{3}{c}{\textbf{\# Leakage Functions}} & \multicolumn{3}{c}{\textbf{Maximum Leakage (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\
-\cmidrule(lr){2-3}\cmidrule(lr){4-6}\cmidrule(lr){7-9}\cmidrule(lr){10-11}\cmidrule(lr){12-14}& \# & bits & Byte & Cache Line& Page & Byte & Cache Line& Page & LoC & Size & Fuzzing & Comparison & Chi-squared
+\cmidrule(lr){2-3}\cmidrule(lr){4-6}\cmidrule(lr){7-9}\cmidrule(lr){10-11}\cmidrule(lr){12-14}& \# & bits &  1 Byte & 64 Bytes & 4 KBs & 1 Byte & 64 Bytes & 4 KBs & LoC & Size & Fuzzing & Comparison & Chi-squared
 \\\midrule
-Safe Password Checker& 65536& 16.0\\
-Unsafe Password Checker & 65536 & 16.0\\
+Unsafe Password Checker& 65536& 16.0& 1&0&0& & & & 18 & 104 KB & 21 min & 0.4 min & 0 min\\
+Safe Password Checker & 65536 & 16.0& 0&0&0&0 &0 &0 & 20 & 106 KB & 20 min & 0.4 min & 0 min\\
 One-byte Lookup Table & 65536 & 16.0\\
@@
 \subsubsection{Password Checker}
+\begin{figure}
+  \begin{minipage}{0.45\linewidth}
+    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
+bool pwcheck(uint8_t *key, uint8_t *pub) {
+  for (int i = 0; i < 2; ++i) {
+    if (key[i] != pub[i]) {
+      return false;
+    }
+  }
+  return true;
+}
+\end{lstlisting}
+  \end{minipage}
+  \hfill
+  \begin{minipage}{0.45\linewidth}
+    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none]
+bool pwcheck(uint8_t *key, uint8_t *pub) {
+  bool matched = true;
+  for (int i = 0; i < 2; ++i) {
+    if (pub[i] != key[i]) 
+      matched = false;
+  }
+  return matched;
+}
+\end{lstlisting}
+  \end{minipage}
+  \caption{A password checker. The right version is vulnerable to side-channel attacks. The left version is the fixed version.}\label{fig:chapter5:pwcheck}
+\end{figure}
 
 \subsubsection{Lookup Table}
+\begin{figure}
+\centering
+    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
+static const uint8_t T[16] = {
+      0x63U, 0x7cU, 0x77U, 0x7bU, 0xf2U, 0x6bU, 0x6fU, 0xc5U,
+      0x30U, 0x01U, 0x67U, 0x2bU, 0xfeU, 0xd7U, 0xabU, 0x76U};
+...
+output = (T[(key[i]>>24)] << 24) ^
+         (T[(key[i+1]>>16) & 0xff] << 16) ^
+         (T[(key[i+2]>>8) & 0xff] << 8) ^
+         (T[(key[i+3]) & 0xff]);
+\end{lstlisting}
+  \caption{Lookup Tables with Small Entries.}\label{fig:chapter5:small_lookup}
+\end{figure}
 
+\begin{figure}
+\centering
+    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
+static const uint32_t T[16] = {
+    0xc66363a5U, 0xf87c7c84U, 0xee777799U, 0xf67b7b8dU,
+    0xfff2f20dU, 0xd66b6bbdU, 0xde6f6fb1U, 0x91c5c554U,
+    0x60303050U, 0x02010103U, 0xce6767a9U, 0x562b2b7dU,
+    0xe7fefe19U, 0xb5d7d762U, 0x4dababe6U, 0xec76769aU};
+...
+output = (T[(key[i+0]>>24)] << 24) ^
+         (T[(key[i+1]>>16) & 0xff] << 16) ^
+         (T[(key[i+2]>>8) & 0xff] << 8) ^
+         (T[(key[i+3]) & 0xff]);
+\end{lstlisting}
+  \caption{Lookup Tables with Big Entries.}\label{fig:chapter5:big_lookup}
+\end{figure}
 \subsection{Cryptography Library}

### 2021-04-14 Chapter-5/Chapter-5.tex
update

@@
 \item \textbf{Performance:} What are overhead costs of \ctool{}?
-\item \textbf{Usage:} What is the real usage of \ctool{}? Can \ctool{} handle both Cryptography and Non-cryptography libraries? Can \ctool{} help developers find and fix side-channel leakages?
+\item \textbf{Usage:}  Can \ctool{} help developers find and fix side-channel leakages?
 \end{itemize}
@@
 
+\textbf{Benchmarks.} 
+We collect benchmarks from real-world applications and libraries.
+Our test programs cover applications from diverse functionalities, including small programs, cryptography, machine learning applications, and graphic libraries.
+
+\textit{Small Programs:} We use two benchmarks that are well studied in the previous work. The amount of actual leakage of those samples are known. We use them to evaluate the precision of the tool.
+
+\textit{Cryptography Applications:} Our benchmarks include the most popular cryptography libraries, such as mebdTLS, OpenSSL, Libgcropt, and wolfSSL.
+We divide ciphers into three categories: stream ciphers, symmetric ciphers, and asymmetric ciphers.
+For stream ciphers, we use RC4.
+For symmetric ciphers, we choose AES.
+We also evaluate the tool on RSA, a widely used algorithm in the public-key cryptosystem.
+
+\textit{Machine Learning Applications:} We evaluate the tool on TinyDNN, a dependency-free deep learning framework in C++.
+
+\textit{Graphic Libraries:} We evaluate the tool on GTK, a popular graphic library. Previous research has demonstrated attacks to infer the keystroke.
+
 \begin{sidewaystable}
@@
 \centering
-\begin{tabular}{lrrrrrrrrrrrrr}\toprule
+\begin{tabular}{lrrrrrrrrrrr}\toprule
 
-\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{3}{c}{\textbf{\# Leakage Functions}} & \multicolumn{3}{c}{\textbf{Maximum Leakage (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\
-\cmidrule(lr){2-3}\cmidrule(lr){4-6}\cmidrule(lr){7-9}\cmidrule(lr){10-11}\cmidrule(lr){12-14}& \# & bits &  1 Byte & 64 Bytes & 4 KBs & 1 Byte & 64 Bytes & 4 KBs & LoC & Size & Fuzzing & Comparison & Chi-squared
+\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Functions}} & \multicolumn{2}{c}{\textbf{Maximum Leakage (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\
+\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-12}& \# & bits &  1 Byte &  4 KBs & 1 Byte  & 4 KBs & LoC & Size & Fuzzing & Comparison & Chi-squared
 \\\midrule
-Unsafe Password Checker& 65536& 16.0& 1&0&0& & & & 18 & 104 KB & 21 min & 0.4 min & 0 min\\
-Safe Password Checker & 65536 & 16.0& 0&0&0&0 &0 &0 & 20 & 106 KB & 20 min & 0.4 min & 0 min\\
-One-byte Lookup Table & 65536 & 16.0\\
-Four-byte Lookup Table & 65536 & 16.0\\
-AES mbedTLS 2.15 & 65536 & 16.0   \\
-AES OpenSSL 1.1.0  & 65536 & 16.0    \\
+Unsafe Password Checker& 65536& 16.0& 1&0&0&  & 18 & 104 KB & 21 min & 0.4 min & 0 min\\
+Safe Password Checker & 65536 & 16.0& 0&0 &0 &0 & 20 & 106 KB & 20 min & 0.4 min & 0 min\\
+One-byte Lookup Table & 65536 & 16.0& 1&1&0&  & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
+Four-byte Lookup Table & 65536 & 16.0& 1&1&0&  & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
+AES T-Table mbedTLS 2.15 & 65536 & 16.0&2&2&0 &&&&& 1.1 MB &  \\
+AES NI mbedTLS 2.15 & 65536 & 16.0&0&0&0 &&&&& 1.1 MB &  \\
+AES bitsliced OpenSSL 1.1.0  & 65536 & 16.0 & 2& &0&&&    \\
 AES OpenSSL 1.1.1& 65536 & 16.0 \\
@@
 \subsection{Result Overview}
+Table~\ref{chapter5:table:over_result} presents the overview result.
 
@@
 \end{figure}
-\subsection{Cryptography Library}
 

### 2021-04-14 Chapter-5/Chapter-5.tex
update

@@
 
-\begin{sidewaystable}
+\begin{table}
 \footnotesize
@@
 AES bitsliced OpenSSL 1.1.0  & 65536 & 16.0 & 2& &0&&&    \\
-AES OpenSSL 1.1.1& 65536 & 16.0 \\
+AES bitsliced OpenSSL 1.1.1& 65536 & 16.0 \\
 AES wolfSSL 4.5.0& 65536 & 16.0\\
@@
 
-\end{sidewaystable}
+\end{table}
 

### 2021-04-14 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \centering
+\resizebox{\columnwidth}{!}{
 \begin{tabular}{lrrrrrrrrrrr}\toprule
 
-\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Functions}} & \multicolumn{2}{c}{\textbf{Maximum Leakage (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\
+\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Functions}} & \multicolumn{2}{c}{\textbf{Max.
+Leak (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\
 \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-12}& \# & bits &  1 Byte &  4 KBs & 1 Byte  & 4 KBs & LoC & Size & Fuzzing & Comparison & Chi-squared
 \\\midrule
-Unsafe Password Checker& 65536& 16.0& 1&0&0&  & 18 & 104 KB & 21 min & 0.4 min & 0 min\\
+Unsafe Password Checker& 65536& 16.0& 1&0&0&  0& 18 & 104 KB & 21 min & 0.4 min & 0 min\\
 Safe Password Checker & 65536 & 16.0& 0&0 &0 &0 & 20 & 106 KB & 20 min & 0.4 min & 0 min\\
@@
 Four-byte Lookup Table & 65536 & 16.0& 1&1&0&  & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
-AES T-Table mbedTLS 2.15 & 65536 & 16.0&2&2&0 &&&&& 1.1 MB &  \\
-AES NI mbedTLS 2.15 & 65536 & 16.0&0&0&0 &&&&& 1.1 MB &  \\
-AES bitsliced OpenSSL 1.1.0  & 65536 & 16.0 & 2& &0&&&    \\
-AES bitsliced OpenSSL 1.1.1& 65536 & 16.0 \\
-AES wolfSSL 4.5.0& 65536 & 16.0\\
-AES Libgcrypt 1.8.7& 65536 & 16.0\\
-RC4 mbedTLS 2.15& 65536 & 16.0\\
-RC4 OpenSSL 1.1.0& 65536 & 16.0\\
-RC4 OpenSSL 1.1.1& 65536 & 16.0\\
-RC4 wolfSSL 4.5.0& 65536 & 16.0\\
-RSA mbedTLS 2.15& 4096 & 12.0\\
-RSA OpenSSL 1.1.0& 4096 & 12.0\\
-RSA OpenSSL 1.1.1& 4096 & 12.0\\
-RSA wolfSSL 4.5.0& 4096 & 12.0\\
-RSA Libgcrypt 1.8.7& 4096 & 12.0 \\
-Tiny DNN & 12000 & 13.6 &\\
-GDK 3.24.23 & 65535 & 16.0 &\\
+AES T-Table mbedTLS 2.15 & 65536 & 16.0&2&2&0 &&& 1.1 MB &  \\
+AES NI mbedTLS 2.15 & 65536 & 16.0&0&0&0 &&& 1.1 MB &  \\
+AES OpenSSL 1.1.0  & 65536 & 16.0 & 2&0 &0&&& 1.0 MB   \\
+AES  OpenSSL 1.1.1& 65536 & 16.0 & 2&0 &0&&& 909 KB\\
+AES  wolfSSL 4.5.0& 65536 & 16.0 &2&0&0&  &&1.1 MB \\
+AES Libgcrypt 1.8.7& 65536 & 16.0 &0 &0 &0& &&4.4 MB\\
+RC4 mbedTLS 2.15& 65536 & 16.0 &2 &2 & & & & 1.1 MB\\
+RC4 OpenSSL 1.1.0& 65536 & 16.0&2 &2 & & & & 1.0 MB\\
+RC4 OpenSSL 1.1.1& 65536 & 16.0&2 &2 & & & & 896 KB\\
+RC4 wolfSSL 4.5.0& 65536 & 16.0&2 &2 & & & &886 KB\\
+RSA mbedTLS 2.15& 4096 & 12.0 &&&& &&1.8 MB\\
+RSA OpenSSL 1.1.0& 4096 & 12.0 &&&& && 11 MB\\
+RSA OpenSSL 1.1.1& 4096 & 12.0 &&&& &&13 MB\\
+RSA wolfSSL 4.5.0& 4096 & 12.0 &&&& &&4.2 MB\\
+RSA Libgcrypt 1.8.7& 4096 & 12.0 &&&& &&4.4 MB\\
+Tiny DNN & 12000 & 13.6 & &&&&& 4.4 MB \\
+GDK 3.24.23 & 65535 & 16.0 & &&&&& 48 MB\\
 \bottomrule
 \end{tabular}
+}
 

### 2021-04-14 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \begin{figure}[h]
-  \begin{minipage}{0.4\linewidth}
+  \begin{minipage}{0.3\linewidth}
     \resizebox{\linewidth}{!}{
@@
   \hfill
-  \begin{minipage}{0.18\linewidth}
+  \begin{minipage}{0.2\linewidth}
     {
@@
   \hfill
-  \begin{minipage}{0.30\linewidth}
+  \begin{minipage}{0.25\linewidth}
     \resizebox{\linewidth}{!}{
@@
 The address record part is implemented as an Intel Pin tool plugin in C++ to record the bitmap for each input.
-The main component uses libelfin, an open source library to parse ELF binaries and read DWARF debug information.
+The main component uses \textsf{libelfin}, an open source library to parse ELF binaries and read DWARF debug information.
 The current implementation can support both 64-bits and 32-bits ELF binary in Linux.
@@
 Leak (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\
-\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-12}& \# & bits &  1 Byte &  4 KBs & 1 Byte  & 4 KBs & LoC & Size & Fuzzing & Comparison & Chi-squared
+\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-12}& \# & bits &  1 Byte &  64 Bytes & 1 Byte  & 64 Bytes & LoC & Size & Fuzzing & Comparison & Chi-squared
 \\\midrule
-Unsafe Password Checker& 65536& 16.0& 1&0&0&  0& 18 & 104 KB & 21 min & 0.4 min & 0 min\\
+Unsafe Password Checker& 65536& 16.0& 1&0&0.04&  0& 18 & 104 KB & 21 min & 0.4 min & 0 min\\
 Safe Password Checker & 65536 & 16.0& 0&0 &0 &0 & 20 & 106 KB & 20 min & 0.4 min & 0 min\\

### 2021-04-14 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Functions}} & \multicolumn{2}{c}{\textbf{Max.
+\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Leaked Functions}} & \multicolumn{2}{c}{\textbf{Max.
 Leak (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\
@@
 Safe Password Checker & 65536 & 16.0& 0&0 &0 &0 & 20 & 106 KB & 20 min & 0.4 min & 0 min\\
-One-byte Lookup Table & 65536 & 16.0& 1&1&0&  & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
-Four-byte Lookup Table & 65536 & 16.0& 1&1&0&  & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
-AES T-Table mbedTLS 2.15 & 65536 & 16.0&2&2&0 &&& 1.1 MB &  \\
-AES NI mbedTLS 2.15 & 65536 & 16.0&0&0&0 &&& 1.1 MB &  \\
-AES OpenSSL 1.1.0  & 65536 & 16.0 & 2&0 &0&&& 1.0 MB   \\
+One-byte Lookup Table & 65536 & 16.0& 1&1&9.8& 3.6 & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
+Four-byte Lookup Table & 65536 & 16.0& 1&1&9.6& 8.5 & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
+AES T-Table mbedTLS 2.15 & 65536 & 16.0&2&2&11.6 &6.7& -& 1.1 MB &65 min & 0.8 min & 0.1 min  \\
+AES NI mbedTLS 2.15 & 65536 & 16.0&0&0&0 &0&-& 1.1 MB & 45 min & 0 min & 0 min  \\
+AES OpenSSL 1.1.0  & 65536 & 16.0 & 2&0 &0.11 & 0&-& 1.0 MB  & 49 min & 0.2 min & 0 min \\
 AES  OpenSSL 1.1.1& 65536 & 16.0 & 2&0 &0&&& 909 KB\\
@@
     \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
-static const uint8_t T[16] = {
+static const uint8_t T[1024] = {
       0x63U, 0x7cU, 0x77U, 0x7bU, 0xf2U, 0x6bU, 0x6fU, 0xc5U,
-      0x30U, 0x01U, 0x67U, 0x2bU, 0xfeU, 0xd7U, 0xabU, 0x76U};
+      0x30U, 0x01U, 0x67U, 0x2bU, 0xfeU, 0xd7U, 0xabU, 0x76U,
 ...
@@
     \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
-static const uint32_t T[16] = {
+static const uint32_t T[256] = {
     0xc66363a5U, 0xf87c7c84U, 0xee777799U, 0xf67b7b8dU,

### 2021-04-14 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 AES NI mbedTLS 2.15 & 65536 & 16.0&0&0&0 &0&-& 1.1 MB & 45 min & 0 min & 0 min  \\
-AES OpenSSL 1.1.0  & 65536 & 16.0 & 2&0 &0.11 & 0&-& 1.0 MB  & 49 min & 0.2 min & 0 min \\
-AES  OpenSSL 1.1.1& 65536 & 16.0 & 2&0 &0&&& 909 KB\\
-AES  wolfSSL 4.5.0& 65536 & 16.0 &2&0&0&  &&1.1 MB \\
-AES Libgcrypt 1.8.7& 65536 & 16.0 &0 &0 &0& &&4.4 MB\\
-RC4 mbedTLS 2.15& 65536 & 16.0 &2 &2 & & & & 1.1 MB\\
-RC4 OpenSSL 1.1.0& 65536 & 16.0&2 &2 & & & & 1.0 MB\\
-RC4 OpenSSL 1.1.1& 65536 & 16.0&2 &2 & & & & 896 KB\\
-RC4 wolfSSL 4.5.0& 65536 & 16.0&2 &2 & & & &886 KB\\
-RSA mbedTLS 2.15& 4096 & 12.0 &&&& &&1.8 MB\\
-RSA OpenSSL 1.1.0& 4096 & 12.0 &&&& && 11 MB\\
-RSA OpenSSL 1.1.1& 4096 & 12.0 &&&& &&13 MB\\
-RSA wolfSSL 4.5.0& 4096 & 12.0 &&&& &&4.2 MB\\
-RSA Libgcrypt 1.8.7& 4096 & 12.0 &&&& &&4.4 MB\\
-Tiny DNN & 12000 & 13.6 & &&&&& 4.4 MB \\
-GDK 3.24.23 & 65535 & 16.0 & &&&&& 48 MB\\
+AES OpenSSL 1.1.0  & 65536 & 16.0 & 2&0 &1.4 & 0&-& 1.0 MB  & 49 min & 0.2 min & 0 min \\
+AES  OpenSSL 1.1.1& 65536 & 16.0 & 2&0 &1.3&0&-& 909 KB & 46 min & 0.2 min & 0 min\\
+AES  wolfSSL 4.5.0& 65536 & 16.0 &2&0& 0.11& 0 & - &1.1 MB & 53 min & 0.1 min & 0 min \\
+AES Libgcrypt 1.8.7& 65536 & 16.0 &0 &0 &0&0 &-&4.4 MB & 164 min& 0 min & 0 min\\
+RSA mbedTLS 2.15& 4096 & 12.0 &10&8&13.3& 6.0 &-&1.8 MB\\
+RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&6.7& 4.1 &-& 11 MB\\
+RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&&13 MB\\
+RSA wolfSSL 4.5.0& 4096 & 12.0 &5&2&3.4& 2.5&&4.2 MB\\
+RSA Libgcrypt 1.8.7& 4096 & 12.0 &8&6&8.6& 6.6&&4.4 MB\\
+Tiny DNN & 12000 & - & 17&14&17.1&16.1&-& 4.4 MB \\
+GDK 3.24.23 & 65535 & 16.0 & 33&31& 12.1& 6.0&-& 48 MB\\
 \bottomrule

### 2021-04-14 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&6.7& 4.1 &-& 11 MB\\
-RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&&13 MB\\
-RSA wolfSSL 4.5.0& 4096 & 12.0 &5&2&3.4& 2.5&&4.2 MB\\
-RSA Libgcrypt 1.8.7& 4096 & 12.0 &8&6&8.6& 6.6&&4.4 MB\\
+RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&-&13 MB\\
+RSA wolfSSL 4.5.0& 4096 & 12.0 &5&2&3.4& 2.5&-&4.2 MB\\
+RSA Libgcrypt 1.8.7& 4096 & 12.0 &8&6&8.6& 6.6&-&4.4 MB\\
 Tiny DNN & 12000 & - & 17&14&17.1&16.1&-& 4.4 MB \\

### 2021-04-14 Chapter-5/Chapter-5.tex
Updates from Overleaf

--- 2021-04-14 Chapter-5/Chapter-5.tex
@@
 AES Libgcrypt 1.8.7& 65536 & 16.0 &0 &0 &0&0 &-&4.4 MB & 164 min& 0 min & 0 min\\
-RSA mbedTLS 2.15& 4096 & 12.0 &10&8&13.3& 6.0 &-&1.8 MB\\
-RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&6.7& 4.1 &-& 11 MB\\
-RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&&13 MB\\
-RSA wolfSSL 4.5.0& 4096 & 12.0 &5&2&3.4& 2.5&&4.2 MB\\
-RSA Libgcrypt 1.8.7& 4096 & 12.0 &8&6&8.6& 6.6&&4.4 MB\\
-Tiny DNN & 12000 & - & 17&14&17.1&16.1&-& 4.4 MB \\
-GDK 3.24.23 & 65535 & 16.0 & 33&31& 12.1& 6.0&-& 48 MB\\
+RSA mbedTLS 2.15& 4096 & 12.0 &10&8&13.3& 6.0 &-&1.8 MB& 1321.1 min & 5.1 min & 63.5 min \\
+RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&6.7& 4.1 &-& 11 MB & 981.1 min & 4.5 min & 75.4 min\\
+RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&-&13 MB & 1021.1 min & 5.5 min & 45.1 min\\
+RSA wolfSSL 4.5.0& 4096 & 12.0 &5&2&3.4& 2.5&-&4.2 MB & 1613.6 min & 7.9 min & 51.6 min\\
+RSA Libgcrypt 1.8.7& 4096 & 12.0 &8&6&8.6& 6.6&-&4.4 MB & 1412.6 min & 4.3 min & 23.9 min\\
+Tiny DNN & 12000 & - & 17&14&17.1&16.1&-& 4.4 MB & 183.5 min & 24.6 min & 5.2 min\\
+GDK 3.24.23 & 4096 & 16.0 & 33&31& 12.1& 6.0&-& 48.5 MB & 60.8 min & 4.1 min & 1.5 min\\
 \bottomrule

### 2021-04-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

--- 2021-04-14 Chapter-5/Chapter-5.tex
@@
 \\\midrule
-Unsafe Password Checker& 65536& 16.0& 1&0&0.04&  0& 18 & 104 KB & 21 min & 0.4 min & 0 min\\
-Safe Password Checker & 65536 & 16.0& 0&0 &0 &0 & 20 & 106 KB & 20 min & 0.4 min & 0 min\\
-One-byte Lookup Table & 65536 & 16.0& 1&1&9.8& 3.6 & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
-Four-byte Lookup Table & 65536 & 16.0& 1&1&9.6& 8.5 & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
-AES T-Table mbedTLS 2.15 & 65536 & 16.0&2&2&11.6 &6.7& -& 1.1 MB &65 min & 0.8 min & 0.1 min  \\
-AES NI mbedTLS 2.15 & 65536 & 16.0&0&0&0 &0&-& 1.1 MB & 45 min & 0 min & 0 min  \\
-AES OpenSSL 1.1.0  & 65536 & 16.0 & 2&0 &1.4 & 0&-& 1.0 MB  & 49 min & 0.2 min & 0 min \\
-AES  OpenSSL 1.1.1& 65536 & 16.0 & 2&0 &1.3&0&-& 909 KB & 46 min & 0.2 min & 0 min\\
-AES  wolfSSL 4.5.0& 65536 & 16.0 &2&0& 0.11& 0 & - &1.1 MB & 53 min & 0.1 min & 0 min \\
-AES Libgcrypt 1.8.7& 65536 & 16.0 &0 &0 &0&0 &-&4.4 MB & 164 min& 0 min & 0 min\\
-RSA mbedTLS 2.15& 4096 & 12.0 &10&8&13.3& 6.0 &-&1.8 MB\\
-RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&6.7& 4.1 &-& 11 MB\\
-RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&&13 MB\\
-RSA wolfSSL 4.5.0& 4096 & 12.0 &5&2&3.4& 2.5&&4.2 MB\\
-RSA Libgcrypt 1.8.7& 4096 & 12.0 &8&6&8.6& 6.6&&4.4 MB\\
-Tiny DNN & 12000 & - & 17&14&17.1&16.1&-& 4.4 MB \\
-GDK 3.24.23 & 65535 & 16.0 & 33&31& 12.1& 6.0&-& 48 MB\\
+Unsafe Password Checker& 65536& 16.0& 1&0&0.04&  0& 18 & 104 KB & 21.6 min & 0.4 min & 0 min\\
+Safe Password Checker & 65536 & 16.0& 0&0 &0 &0 & 20 & 106 KB & 20.1 min & 0.4 min & 0 min\\
+One-byte Lookup Table & 65536 & 16.0& 1&1&9.8& 3.6 & 18 & 104 KB & 11.9 min & 0.1 min & 0 min\\
+Four-byte Lookup Table & 65536 & 16.0& 1&1&9.6& 8.5 & 18 & 104 KB & 11.4 min & 0.1 min & 0 min\\
+AES T-Table mbedTLS 2.15 & 65536 & 16.0&2&2&11.6 &6.7& -& 1.1 MB &65.9 min & 0.8 min & 0.1 min  \\
+AES NI mbedTLS 2.15 & 65536 & 16.0&0&0&0 &0&-& 1.1 MB & 45.0 min & 0 min & 0 min  \\
+AES OpenSSL 1.1.0  & 65536 & 16.0 & 2&0 &1.4 & 0&-& 1.0 MB  & 49.0 min & 0.2 min & 0 min \\
+AES  OpenSSL 1.1.1& 65536 & 16.0 & 2&0 &1.3&0&-& 909 KB & 46.1 min & 0.2 min & 0 min\\
+AES  wolfSSL 4.5.0& 65536 & 16.0 &2&0& 0.11& 0 & - &1.1 MB & 53.3 min & 0.1 min & 0 min \\
+AES Libgcrypt 1.8.7& 65536 & 16.0 &0 &0 &0&0 &-&4.4 MB & 164.6 min& 0 min & 0 min\\
+RSA mbedTLS 2.15& 4096 & 12.0 &10&8&13.3& 6.0 &-&1.8 MB& 1321.1 min & 63.5 min & 5.1 min \\
+RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&6.7& 4.1 &-& 11 MB & 981.1 min & 75.4 min & 4.5 min\\
+RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&-&13 MB & 1021.1 min & 45.1 min & 5.5 min\\
+RSA wolfSSL 4.5.0& 4096 & 12.0 &5&2&3.4& 2.5&-&4.2 MB & 1613.6 min & 51.6 min & 7.9 min\\
+RSA Libgcrypt 1.8.7& 4096 & 12.0 &8&6&8.6& 6.6&-&4.4 MB & 1412.6 min & 23.9 min & 4.3 min\\
+Tiny DNN & 12000 & - & 17&14&17.1&16.1&-& 4.4 MB & 183.5 min & 24.6 min & 5.2 min\\
+GDK 3.24.23 & 4096 & 16.0 & 33&31& 12.1& 6.0&-& 48.5 MB & 60.8 min & 4.1 min & 1.5 min\\
 \bottomrule

### 2021-04-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

--- 2021-04-14 Chapter-5/Chapter-5.tex
@@
 \textit{Cryptography Applications:} Our benchmarks include the most popular cryptography libraries, such as mebdTLS, OpenSSL, Libgcropt, and wolfSSL.
-We divide ciphers into three categories: stream ciphers, symmetric ciphers, and asymmetric ciphers.
+Encryption ciphers can be divided into three categories:  symmetric ciphers, and asymmetric ciphers.
 For stream ciphers, we use RC4.
@@
 \\\midrule
-Unsafe Password Checker& 65536& 16.0& 1&0&0.04&  0& 18 & 104 KB & 21 min & 0.4 min & 0 min\\
-Safe Password Checker & 65536 & 16.0& 0&0 &0 &0 & 20 & 106 KB & 20 min & 0.4 min & 0 min\\
-One-byte Lookup Table & 65536 & 16.0& 1&1&9.8& 3.6 & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
-Four-byte Lookup Table & 65536 & 16.0& 1&1&9.6& 8.5 & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
-AES T-Table mbedTLS 2.15 & 65536 & 16.0&2&2&11.6 &6.7& -& 1.1 MB &65 min & 0.8 min & 0.1 min  \\
-AES NI mbedTLS 2.15 & 65536 & 16.0&0&0&0 &0&-& 1.1 MB & 45 min & 0 min & 0 min  \\
-AES OpenSSL 1.1.0  & 65536 & 16.0 & 2&0 &1.4 & 0&-& 1.0 MB  & 49 min & 0.2 min & 0 min \\
-AES  OpenSSL 1.1.1& 65536 & 16.0 & 2&0 &1.3&0&-& 909 KB & 46 min & 0.2 min & 0 min\\
-AES  wolfSSL 4.5.0& 65536 & 16.0 &2&0& 0.11& 0 & - &1.1 MB & 53 min & 0.1 min & 0 min \\
-AES Libgcrypt 1.8.7& 65536 & 16.0 &0 &0 &0&0 &-&4.4 MB & 164 min& 0 min & 0 min\\
-RSA mbedTLS 2.15& 4096 & 12.0 &10&8&13.3& 6.0 &-&1.8 MB\\
-RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&6.7& 4.1 &-& 11 MB\\
-RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&-&13 MB\\
-RSA wolfSSL 4.5.0& 4096 & 12.0 &5&2&3.4& 2.5&-&4.2 MB\\
-RSA Libgcrypt 1.8.7& 4096 & 12.0 &8&6&8.6& 6.6&-&4.4 MB\\
-Tiny DNN & 12000 & - & 17&14&17.1&16.1&-& 4.4 MB \\
-GDK 3.24.23 & 65535 & 16.0 & 33&31& 12.1& 6.0&-& 48 MB\\
+Unsafe Password Checker& 4096& 12.0& 1&0&0.04&  0& 18 & 104 KB & 2.4 min & 0.4 min & 0 min\\
+Safe Password Checker & 4096 & 12.0& 0&0 &0 &0 & 20 & 106 KB & 2.3 min & 0.4 min & 0 min\\
+One-byte Lookup Table & 4096 & 12.0& 1&1&9.8& 3.6 & 18 & 104 KB & 0.8 min & 0.1 min & 0 min\\
+Four-byte Lookup Table & 4096 & 12.0& 1&1&9.6& 8.5 & 18 & 104 KB & 0.7 min & 0.1 min & 0 min\\
+AES T-Table mbedTLS 2.15 & 4096 & 12.0&2&2&11.6 &6.7& -& 1.1 MB &4.1 min & 0.8 min & 0.1 min  \\
+AES NI mbedTLS 2.15 & 4096 & 12.0&0&0&0 &0&-& 1.1 MB & 2.8 min & 0 min & 0 min  \\
+AES OpenSSL 1.1.0  & 4096 & 12.0 & 2&0 &1.4 & 0&-& 1.0 MB  & 3.1 min & 0.2 min & 0 min \\
+AES  OpenSSL 1.1.1& 4096 & 12.0 & 2&0 &1.3&0&-& 909 KB & 2.9 min & 0.2 min & 0 min\\
+AES  wolfSSL 4.5.0& 4096 & 12.0 &2&0& 0.11& 0 & - &1.1 MB & 3.3 min & 0.1 min & 0 min \\
+AES Libgcrypt 1.8.7& 4096 & 12.0 &0 &0 &0&0 &-&4.4 MB & 10.2 min& 0 min & 0 min\\
+RSA mbedTLS 2.15& 4096 & 12.0 &10&8&13.3& 6.0 &-&1.8 MB& 1321.1 min & 63.5 min & 5.1 min \\
+RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&6.7& 4.1 &-& 11 MB & 981.1 min & 75.4 min & 4.5 min\\
+RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&-&13 MB & 1021.1 min & 45.1 min & 5.5 min\\
+RSA wolfSSL 4.5.0& 4096 & 12.0 &5&2&3.4& 2.5&-&4.2 MB & 1613.6 min & 51.6 min & 7.9 min\\
+RSA Libgcrypt 1.8.7& 4096 & 12.0 &8&6&8.6& 6.6&-&4.4 MB & 1412.6 min & 23.9 min & 4.3 min\\
+Tiny DNN & 12000 & - & 17&14&17.1&16.1&-& 4.4 MB & 183.5 min & 24.6 min & 5.2 min\\
+GDK 3.24.23 & 4096 & 16.0 & 33&31& 12.1& 6.0&-& 48.5 MB & 60.8 min & 4.1 min & 1.5 min\\
 \bottomrule
@@
 Table~\ref{chapter5:table:over_result} presents the overview result.
+The minimum unit of the program during the experiment is the function.
+Suppose the function has more than one access map, then the function that is vulnerable to side-channel attacks.
+We measure the side-channel leakages at two different granularities: the byte level and the cache line level.
+The result shows that the program has more leaked vulnerabilities and tends to leak more information at the byte level compare with the cache line level.
+Each time we run the target program under random inputs and record memory accesses.
 

### 2021-04-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 The main component uses \textsf{libelfin}, an open source library to parse ELF binaries and read DWARF debug information.
-The current implementation can support both 64-bits and 32-bits ELF binary in Linux.
-\ctool{} will be open-sourced.
+The current implementation can support  64-bits ELF binary in Linux.
 
@@
 Safe Password Checker & 4096 & 12.0& 0&0 &0 &0 & 20 & 106 KB & 2.3 min & 0.4 min & 0 min\\
-One-byte Lookup Table & 4096 & 12.0& 1&1&9.8& 3.6 & 18 & 104 KB & 0.8 min & 0.1 min & 0 min\\
+One-byte Lookup Table & 4096 & 12.0& 1&1&7.5& 3.6 & 18 & 104 KB & 0.8 min & 0.1 min & 0 min\\
 Four-byte Lookup Table & 4096 & 12.0& 1&1&9.6& 8.5 & 18 & 104 KB & 0.7 min & 0.1 min & 0 min\\
@@
 AES NI mbedTLS 2.15 & 4096 & 12.0&0&0&0 &0&-& 1.1 MB & 2.8 min & 0 min & 0 min  \\
-AES OpenSSL 1.1.0  & 4096 & 12.0 & 2&0 &1.4 & 0&-& 1.0 MB  & 3.1 min & 0.2 min & 0 min \\
-AES  OpenSSL 1.1.1& 4096 & 12.0 & 2&0 &1.3&0&-& 909 KB & 2.9 min & 0.2 min & 0 min\\
-AES  wolfSSL 4.5.0& 4096 & 12.0 &2&0& 0.11& 0 & - &1.1 MB & 3.3 min & 0.1 min & 0 min \\
+AES OpenSSL 1.1.0  & 4096 & 12.0 & 1&0 &1.4 & 0&-& 1.0 MB  & 3.1 min & 0.2 min & 0 min \\
+AES  OpenSSL 1.1.1& 4096 & 12.0 & 1&0 &1.3&0&-& 909 KB & 2.9 min & 0.2 min & 0 min\\
+AES  wolfSSL 4.5.0& 4096 & 12.0 &1&0& 0.11& 0 & - &1.1 MB & 3.3 min & 0.1 min & 0 min \\
 AES Libgcrypt 1.8.7& 4096 & 12.0 &0 &0 &0&0 &-&4.4 MB & 10.2 min& 0 min & 0 min\\
@@
 
-\subsection{Result Overview}
 Table~\ref{chapter5:table:over_result} presents the overview result.
@@
 Each time we run the target program under random inputs and record memory accesses.
+For cryptography programs, we run the target program with $4096$ different inputs.
+During the fuzzing process, if the program does not have new memory access bitmap after several rounds.
+We call the fuzzing step is fixed.
+From the side-channel detection aspect, it is not necessary to continue running the experiments since more rounds do not reveal new leakages.
+During the experiment, we find AES ciphers reach the fixed point after about 300 rounds and RSA can reach the fixed point after around 500 rounds.
+Previous work~\cite{217537} also reported similar result.
+During our experiment, we continue running the experiment until the observe value for the same observation is at least 5 to satisfy the Chi-square test requirement.
+Therefore, we choose to run all the cipher with different inputs for $4096$ times.
+If one program has more than two leaked functions, we run the chi-squared test and calculate the total amount of leakages.
 
@@
   \end{minipage}
-  \caption{A password checker. The right version is vulnerable to side-channel attacks. The left version is the fixed version.}\label{fig:chapter5:pwcheck}
+  \caption{A password checker. The left version is vulnerable to side-channel attacks. The right version is the fixed version.}\label{fig:chapter5:pwcheck}
 \end{figure}
+
+We illustrate the quantification method on a password checking example.
+As shown in Figure~\label{fig:chapter5:pwcheck}, the left version is vulnerable to side-channel attacks because of the early return at line 4.
+If the first bytes of \textsf{key} and \textsf{pub} are the same, the function will continue running and access the second byte.
+The right version fixes the vulnerability because the function will continue comparing the second byte even if the first byte is different.
+\ctool{} identifies the leakage site in the left figure successfully and estimates the amount of leakage site is $0.04$ bits.
 
@@
 \centering
-    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
+    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth, frame=none]
 static const uint8_t T[1024] = {
@@
 ...
-output = (T[(key[i]>>24)] << 24) ^
-         (T[(key[i+1]>>16) & 0xff] << 16) ^
-         (T[(key[i+2]>>8) & 0xff] << 8) ^
-         (T[(key[i+3]) & 0xff]);
+output = (T[(key[0]>>24)] << 24) ^
+         (T[(key[1]>>16) & 0xff] << 16) ^
+         (T[(key[2]>>8) & 0xff] << 8) ^
+         (T[(key[3]) & 0xff]);
 \end{lstlisting}
@@
 \centering
-    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
+    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth, frame=none]
 static const uint32_t T[256] = {
@@
 ...
-output = (T[(key[i+0]>>24)] << 24) ^
-         (T[(key[i+1]>>16) & 0xff] << 16) ^
-         (T[(key[i+2]>>8) & 0xff] << 8) ^
-         (T[(key[i+3]) & 0xff]);
+output = (T[(key[0]>>24)] << 24) ^
+         (T[(key[1]>>16) & 0xff] << 16) ^
+         (T[(key[2]>>8) & 0xff] << 8) ^
+         (T[(key[3]) & 0xff]);
 \end{lstlisting}
@@
 
-\subsection{Case Study: Attacks on Multi-class Classification Inference Engine}
+We analyze the table lookup with \ctool{}.
+It is a common operation used by symmetric ciphers like AES.
+Figure~\ref{fig:chapter5:big_lookup} is from the original AES reference implementation.
+It uses a lookup table and each entry is 4 bytes, which is vulnerable to side-channel attacks.
+Most cryptography libraries adopted the mitigated version, shown in Figure~\ref{fig:chapter5:small_lookup}.
+The evaluation result shows the version with smaller lookup tables leaks less information, which confirm the effectiveness of the mitigation technique.
+
+\subsection{Cryptography Libraries}
+For symmetric ciphers, we evaluate \ctool{} on three types implementation of AES.
+For mebedTLS, we evaluate AES-NI and the reference implementation.
+We do not find any leakage sites in the AES-NI version.
+On the other hand, the reference implementation has several leakage sites.
+The bitsliced version from OpenSSL and wolfSSL should be resistant to side-channel attacks.
+However, we find they only adopt the protection in the encryption function but leave the key
+expansion function unprotected.
+
+\subsection{Machine Learning Applications}
 In the section, we demonstrate an attack that can recover the deep learning model inference output by the controlled-channel attack.
@@
 After the training, the accuracy of the neural networks on test set images is 99.5\%.
-
-Then we use the model to infer the images. During the inference, we also record the page access information.
+Then we use the model to infer the images.
+During the inference, we also record the page access information.
 

### 2021-04-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \subsection{Cryptography Libraries}
-For symmetric ciphers, we evaluate \ctool{} on three types implementation of AES.
+For symmetric ciphers, we evaluate \ctool{} on three types of AES implementations.
 For mebedTLS, we evaluate AES-NI and the reference implementation.
@@
 The bitsliced version from OpenSSL and wolfSSL should be resistant to side-channel attacks.
-However, we find they only adopt the protection in the encryption function but leave the key
-expansion function unprotected.
+However, we find they only adopt the protection in the encryption function but leave the key expansion function unprotected.
+The T-Table implementation has side-channel leakage sites in both the key expanding function and the actually encryption function.
+The result is similarly to the previous work.
+
+We use a fixed RSA blinding value during the evaluation to avoid non-deterministic behaviors.
+We compare the result with previous work and find \ctool{} can identify all the leaked functions reported in the previous work.
 

### 2021-04-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-\textbf{Evaluation setup.} We run all the following experiment in a server machine with Ubuntu 18.04 LTS.
-The server machine equips with 2.90GHz Intel Xeon(R) E5-2690 CPU with 128GB RAM memory.
+\textbf{Evaluation setup.} We run all the following experiment in a machine with Ubuntu 18.04 LTS.
+The server machine equips with 2.30GHz Intel Core i9-9880 CPU with 16GB RAM memory.
 We use the default release settings to build the source code of the software into ELF 64-bit executables with GCC 7.5.
@@
 
+\begin{table}[!ht]
+\centering\tiny\scriptsize
+\caption{Leakages in RSA implemented by OpenSSL 1.1.0f}\label{tab:RSAOpenSSL1.1.0f}
+%\resizebox{\columnwidth}{!}{
+\begin{tabular}{lrlrr}
+\hline
+\textbf{File} & \textbf{Line No.} & \textbf{Function} & \textbf{\# Leaked Bits} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
+bn\_lib.c& 143&BN\_num\_bits\_word&*&CF\\
+bn\_lib.c& 144&BN\_num\_bits\_word&*&CF\\
+bn\_lib.c& 145&BN\_num\_bits\_word&17.2 &DA\\
+bn\_lib.c& 1029&bn\_correct\_top&*&CF\\
+bn\_lib.c& 639&BN\_ucmp&*&CF\\
+ct\_b64.c& 164&\_\_udivdi3&5.9 &CF\\
+bn\_div.c& 330&BN\_div&*&CF\\
+bn\_gcd.c& 192&int\_bn\_mod\_inverse&1.0 &CF\\
+bn\_gcd.c& 215&int\_bn\_mod\_inverse&7.9 &CF\\
+bn\_gcd.c& 237&int\_bn\_mod\_inverse&8.2 &CF\\
+bn\_gcd.c& 218&int\_bn\_mod\_inverse&14.9 &CF\\
+bn\_gcd.c& 240&int\_bn\_mod\_inverse&9.2 &CF\\
+bn\_lib.c& 147&BN\_num\_bits\_word&*&DA\\
+bn\_lib.c& 152&BN\_num\_bits\_word&12.6 &CF\\
+bn\_lib.c& 153&BN\_num\_bits\_word&*&DA\\
+bn\_lib.c& 156&BN\_num\_bits\_word&*&DA\\
+bn\_div.c& 384&BN\_div&17.2 &CF\\
+bn\_div.c& 330&BN\_div&11.9 &CF\\
+bn\_div.c& 334&BN\_div&3.8 &CF\\
+bn\_exp.c& 622&BN\_mod\_exp\_mont\_consttime&1.0 &CF\\
+bn\_exp.c& 741&BN\_mod\_exp\_mont\_consttime&1.0 &CF\\
+bn\_mont.c& 138&BN\_from\_montgomery\_word&*&DA\\
+bn\_mont.c& 139&BN\_from\_montgomery\_word&*&DA\\
+bn\_mont.c& 140&BN\_from\_montgomery\_word&*&DA\\
+bn\_mont.c& 142&BN\_from\_montgomery\_word&*&DA\\
+bn\_mont.c& 152&BN\_from\_montgomery\_word&*&DA\\
+bn\_asm.c& 733&bn\_sqr\_comba8&*&CF\\
+bn\_asm.c& 592&bn\_mul\_comba8&*&CF\\
+bn\_mont.c& 98&BN\_from\_montgomery\_word&0.0 &CF\\
+bn\_div.c& 330&BN\_div&0.3 &CF\\
+bn\_div.c& 330&BN\_div&0.3 &CF\\
+\hline
+\end{tabular}
+%}
+\renewcommand{\baselinestretch}{1.0}\selectfont
+\end{table}
 \subsection{Machine Learning Applications}

### 2021-04-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

--- 2021-04-15 Chapter-5/Chapter-5.tex
@@
 
+\begin{table}[!ht]
+\centering\tiny\scriptsize
+\caption{Leakages in RSA implemented by OpenSSL 1.1.0f}\label{tab:RSAOpenSSL1.1.0f}
+%\resizebox{\columnwidth}{!}{
+\begin{tabular}{llrr}
+\hline
+\textbf{File}  & \textbf{Function} & \textbf{\# Leaked Bits} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
+bn\_lib.c& BN\_num\_bits\_word&*&CF\\
+bn\_lib.c& BN\_num\_bits\_word&*&CF\\
+bn\_lib.c& BN\_num\_bits\_word&17.2 &DA\\
+bn\_lib.c& bn\_correct\_top&*&CF\\
+bn\_lib.c& BN\_ucmp&*&CF\\
+ct\_b64.c& \_\_udivdi3&5.9 &CF\\
+bn\_div.c& BN\_div&*&CF\\
+bn\_gcd.c& int\_bn\_mod\_inverse&1.0 &CF\\
+bn\_gcd.c& int\_bn\_mod\_inverse&7.9 &CF\\
+bn\_gcd.c& int\_bn\_mod\_inverse&8.2 &CF\\
+bn\_gcd.c& int\_bn\_mod\_inverse&14.9 &CF\\
+bn\_gcd.c& int\_bn\_mod\_inverse&9.2 &CF\\
+bn\_lib.c& BN\_num\_bits\_word&*&DA\\
+bn\_lib.c& BN\_num\_bits\_word&12.6 &CF\\
+bn\_lib.c& BN\_num\_bits\_word&*&DA\\
+bn\_lib.c& BN\_num\_bits\_word&*&DA\\
+bn\_div.c& BN\_div&17.2 &CF\\
+bn\_div.c& BN\_div&11.9 &CF\\
+bn\_div.c& BN\_div&3.8 &CF\\
+bn\_exp.c& BN\_mod\_exp\_mont\_consttime&1.0 &CF\\
+bn\_exp.c& BN\_mod\_exp\_mont\_consttime&1.0 &CF\\
+bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
+bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
+bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
+bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
+bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
+bn\_asm.c& bn\_sqr\_comba8&*&CF\\
+bn\_asm.c& bn\_mul\_comba8&*&CF\\
+bn\_mont.c& BN\_from\_montgomery\_word&0.0 &CF\\
+bn\_div.c& BN\_div&0.3 &CF\\
+bn\_div.c& BN\_div&0.3 &CF\\
+\hline
+\end{tabular}
+%}
+\renewcommand{\baselinestretch}{1.0}\selectfont
+\end{table}
 \subsection{Machine Learning Applications}

### 2021-04-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \subsection{Cryptography Libraries}
-For symmetric ciphers, we evaluate \ctool{} on three types of AES implementations.
+AES encryption can be divided into three steps.
+In the first step, the round keys are derived from the encryption keys called the AES key schedule, and the state array is initialized with the plain-text and the initial round step.
+In the second step, the AES performs eleven rounds of state manipulation.
+In the final stage, the state array is copied out as the encrypted data.
+The reference implementation uses lookup tables in the first two steps.
+Intuitively, the implementation is vulnerable to side-channel attacks.
+There are some mitigated versions of AES.
+We evaluate \ctool{} on three variants of AES implementations: the reference implementation, the bit-sliced version, and the AES-NI implementation.
 For mebedTLS, we evaluate AES-NI and the reference implementation.
@@
 On the other hand, the reference implementation has several leakage sites.
-The bitsliced version from OpenSSL and wolfSSL should be resistant to side-channel attacks.
+The bit-sliced version from OpenSSL and wolfSSL should be resistant to side-channel attacks.
 However, we find they only adopt the protection in the encryption function but leave the key expansion function unprotected.
 The T-Table implementation has side-channel leakage sites in both the key expanding function and the actually encryption function.
-The result is similarly to the previous work.
-
-We use a fixed RSA blinding value during the evaluation to avoid non-deterministic behaviors.
-We compare the result with previous work and find \ctool{} can identify all the leaked functions reported in the previous work.
+
+We use a fixed RSA blinding value during the evaluation to avoid non-deterministic behaviors during the execution.
+After that, we compare the result with the previous work~\cite{bao2021abacus,203878}.
+The result shows that \ctool{} can identify all the leakage sites reported in the previous work.
+In addition, \ctool{} identify new leakages in the private key decoded functions (\textsf{EVP\_DecodeUpdate}, \textsf{EVP\_DecodeBlock}) in OpenSSL 1.1.0f and OpenSSL 1.1.1.
 
@@
 \centering\tiny\scriptsize
-\caption{Leakages in RSA implemented by OpenSSL 1.1.0f}\label{tab:RSAOpenSSL1.1.0f}
+\caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0f}\label{chapter5:tab:RSAOpenSSL1.1.0f}
 %\resizebox{\columnwidth}{!}{
@@
 
-Another limitation is that \ctool{} can only find the position in the code that leaks the sensitive information, but it is not the root cause of the leaks.
-Consider the example in Figure~\ref{fig:limitation}, it takes the secret as the input.
-At line 3, it calculate an index based on the value of the secret.
-Depending on the value of index, it may or may not run the code at line 6.
-So line 5 is the reason that causes the vulnerability.
-But \ctool{} can only tell the line 6 can leak the information, despite it is not the root cause of the vulnerability.
-
 \begin{figure}
@@
 \end{figure}
+
+Another limitation is that \ctool{} can only find the position in the code that leaks the sensitive information, but it is not the root cause of the leaks.
+Consider the example in Figure~\ref{fig:limitation}, it takes the secret as the input.
+At line 3, it calculate an index based on the value of the secret.
+Depending on the value of index, it may or may not run the code at line 6.
+So line 5 is the reason that causes the vulnerability.
+But \ctool{} can only tell the line 6 can leak the information, despite it is not the root cause of the vulnerability.

### 2021-04-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 RSA mbedTLS 2.15& 4096 & 12.0 &10&8&13.3& 6.0 &-&1.8 MB& 1321.1 min & 63.5 min & 5.1 min \\
-RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&6.7& 4.1 &-& 11 MB & 981.1 min & 75.4 min & 4.5 min\\
+RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&8.7& 6.1 &-& 11 MB & 981.1 min & 75.4 min & 4.5 min\\
 RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&-&13 MB & 1021.1 min & 45.1 min & 5.5 min\\
@@
 
-We use a fixed RSA blinding value during the evaluation to avoid non-deterministic behaviors during the execution.
+We use a fixed RSA blinding value to avoid non-deterministic behaviors during the execution.
 After that, we compare the result with the previous work~\cite{bao2021abacus,203878}.
 The result shows that \ctool{} can identify all the leakage sites reported in the previous work.
-In addition, \ctool{} identify new leakages in the private key decoded functions (\textsf{EVP\_DecodeUpdate}, \textsf{EVP\_DecodeBlock}) in OpenSSL 1.1.0f and OpenSSL 1.1.1.
+In addition, \ctool{} identify new leakages in the private key decoded functions (\textsf{EVP\_DecodeUpdate}, \textsf{EVP\_DecodeBlock}) in OpenSSL 1.1.0f.
+To evaluate the effectiveness of the quantification result, we compare the RSA implementation between OpenSSL 1.1.0 and OpenSSL 1.1.1.
+Table~\ref{chapter5:tab:RSAOpenSSL1.1.0} shows the summary.
+Note that \ctool{} can analyze the side-channel leakages at both the byte granularity and the cache line granularity.
+However, we only show the result in cache line granularity.
+We compare the result with \tool{}, a symbolic analysis based side-channel quantification tool.
+\tool{} can tell which line actually leaks the information.
+So it is possible that one function has several two leakage sites.
 
@@
 \centering\tiny\scriptsize
-\caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0f}\label{chapter5:tab:RSAOpenSSL1.1.0f}
+\caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0}\label{chapter5:tab:RSAOpenSSL1.1.0}
 %\resizebox{\columnwidth}{!}{
-\begin{tabular}{llrr}
+\begin{tabular}{llrrc}
 \hline
-\textbf{File}  & \textbf{Function} & \textbf{\# Leaked Bits} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
-bn\_lib.c& BN\_num\_bits\_word&*&CF\\
-bn\_lib.c& BN\_num\_bits\_word&*&CF\\
-bn\_lib.c& BN\_num\_bits\_word&17.2 &DA\\
+\textbf{File}  & \textbf{Function} & \textbf{\tool{} Result} & \textbf{\ctool{} Result} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
+bn\_lib.c& BN\_num\_bits\_word&*&CF & \cmark\\
 bn\_lib.c& bn\_correct\_top&*&CF\\
@@
 bn\_gcd.c& int\_bn\_mod\_inverse&1.0 &CF\\
-bn\_gcd.c& int\_bn\_mod\_inverse&7.9 &CF\\
-bn\_gcd.c& int\_bn\_mod\_inverse&8.2 &CF\\
-bn\_gcd.c& int\_bn\_mod\_inverse&14.9 &CF\\
-bn\_gcd.c& int\_bn\_mod\_inverse&9.2 &CF\\
-bn\_lib.c& BN\_num\_bits\_word&*&DA\\
-bn\_lib.c& BN\_num\_bits\_word&12.6 &CF\\
-bn\_lib.c& BN\_num\_bits\_word&*&DA\\
 bn\_lib.c& BN\_num\_bits\_word&*&DA\\
 bn\_div.c& BN\_div&17.2 &CF\\
-bn\_div.c& BN\_div&11.9 &CF\\
-bn\_div.c& BN\_div&3.8 &CF\\
-bn\_exp.c& BN\_mod\_exp\_mont\_consttime&1.0 &CF\\
 bn\_exp.c& BN\_mod\_exp\_mont\_consttime&1.0 &CF\\
 bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
-bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
-bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
-bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
-bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
 bn\_asm.c& bn\_sqr\_comba8&*&CF\\
-bn\_asm.c& bn\_mul\_comba8&*&CF\\
 bn\_mont.c& BN\_from\_montgomery\_word&0.0 &CF\\
-bn\_div.c& BN\_div&0.3 &CF\\
 bn\_div.c& BN\_div&0.3 &CF\\

### 2021-04-16 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 
-\subsection{Analysis of Software Countermeasures}\label{sec:eval_countermeasures}
+\subsection{Benchmarks}\label{sec:eval_countermeasures}
 \subsubsection{Bit-slicing}
@@
 
-\subsubsection{Smaller Lookup Tables}
-\begin{figure}[h!]
+\subsubsection{Lookup Table}
+\begin{figure}
 \centering
-    \begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
-static const uint8_t T[16] = {
+    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth, frame=none]
+static const uint8_t T[1024] = {
       0x63U, 0x7cU, 0x77U, 0x7bU, 0xf2U, 0x6bU, 0x6fU, 0xc5U,
-      0x30U, 0x01U, 0x67U, 0x2bU, 0xfeU, 0xd7U, 0xabU, 0x76U};
+      0x30U, 0x01U, 0x67U, 0x2bU, 0xfeU, 0xd7U, 0xabU, 0x76U,
+...
+output = (T[(key[0]>>24)] << 24) ^
+         (T[(key[1]>>16) & 0xff] << 16) ^
+         (T[(key[2]>>8) & 0xff] << 8) ^
+         (T[(key[3]) & 0xff]);
 \end{lstlisting}
-    \caption{One-byte Entry Lookup Table}
-    \label{fig:one_byte_table}
+  \caption{Lookup Tables with Small Entries.}\label{fig:chapter4:small_lookup}
 \end{figure}
 
-\begin{figure}[h!]
+\begin{figure}
 \centering
-    \begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
-static const uint32_t T[16] = {
+    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth, frame=none]
+static const uint32_t T[256] = {
     0xc66363a5U, 0xf87c7c84U, 0xee777799U, 0xf67b7b8dU,
@@
     0xe7fefe19U, 0xb5d7d762U, 0x4dababe6U, 0xec76769aU};
+...
+output = (T[(key[0]>>24)] << 24) ^
+         (T[(key[1]>>16) & 0xff] << 16) ^
+         (T[(key[2]>>8) & 0xff] << 8) ^
+         (T[(key[3]) & 0xff]);
 \end{lstlisting}
-
-    \caption{Four-byte Entry Lookup Table}
-    \label{fig:four_byte_table}
-\end{figure}
-\begin{figure}[h!]
-    \centering
-    \begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
-void encrypt_one(uint32_t *o, uint32_t *key, uint32_t l) {
-    for (int i = 0; i < l; i+=4)
-        output[i] = (T[(key[i]>>24)] << 24) ^
-                    (T[(key[i+1]>>16) & 0xff] << 16) ^
-                    (T[(key[i+2]>>8) & 0xff] << 8) ^
-                    (T[(key[i+3]) & 0xff]);
-}
-    \end{lstlisting}
-    \caption{Encrypt with One-byte Entry Lookup Table}
-    \label{fig:one_byte_table_lookup}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
-void encrypt_four(uint32_t *o, uint32_t *key, uint32_t l) {
-    for (int i = 0; i < l; i+=4)
-        output[i] = (T[(key[i]>>24)] & 0xff000000) ^
-                    (T[(key[i+1]>>16) & 0xff] & 0x00ff0000) ^
-                    (T[(key[i+2]>>8) & 0xff] & 0x0000ff00) ^
-                    (T[(key[i+3]) & 0xff] & 0x000000ff);
-}
-    \end{lstlisting}
-    \caption{Encrypt with One-byte Entry Lookup Table}
-    \label{fig:four_byte_table_lookup}
+  \caption{Lookup Tables with Big Entries.}\label{fig:chapter4:big_lookup}
 \end{figure}
@@
 probability of leakage decreases when the lookup table entry or element size gets
-smaller. We take AES as an example, for the last round of encryption, the algorithm
-uses a specialized table with 4-byte size entries, of which only one
-byte from each element actually contributes to the result. Hence, a significant method to reduce
-the information leakage in AES is to reduce the size of the lookup table. We
-designed a demo to illustrate this countermeasure, a lookup table with one-byte
-size elements (see Figure~\ref{fig:one_byte_table}) will leak less information
-than a table with 4-byte element size (see Figure~\ref{fig:four_byte_table}). 
-The encrypt function for each table to process the same amount of information, 
-respectively, (see Figure~\ref{fig:one_byte_table_lookup} and
-Figure~\ref{fig:four_byte_table_lookup}).  \tool{} reports three leakage sites for
+smaller.
+We analyze the table lookup with \tool{}.
+It is a common operation used by symmetric ciphers like AES.
+Figure~\ref{fig:chapter4:big_lookup} is from the original AES reference implementation.
+It uses a lookup table and each entry is 4 bytes, which is vulnerable to side-channel attacks.
+Most cryptography libraries adopted the mitigated version, shown in Figure~\ref{fig:chapter4:small_lookup}.
+\tool{} reports three leakage sites for
 each lookup table, with 4.0 bits for the table with smaller entries and 2.0
 bits for the table with bigger entries, confirming the theory.
+The evaluation result shows the version with smaller lookup tables leaks less information, which confirm the effectiveness of the mitigation technique.
+
+\subsubsection{Password Checker}
+\begin{figure}
+  \begin{minipage}{0.45\linewidth}
+    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
+bool pwcheck(uint8_t *key, uint8_t *pub) {
+  for (int i = 0; i < 2; ++i) {
+    if (key[i] != pub[i]) {
+      return false;
+    }
+  }
+  return true;
+}
+\end{lstlisting}
+  \end{minipage}
+  \hfill
+  \begin{minipage}{0.45\linewidth}
+    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none]
+bool pwcheck(uint8_t *key, uint8_t *pub) {
+  bool matched = true;
+  for (int i = 0; i < 2; ++i) {
+    if (pub[i] != key[i]) 
+      matched = false;
+  }
+  return matched;
+}
+\end{lstlisting}
+  \end{minipage}
+  \caption{A password checker. The left version is vulnerable to side-channel attacks. The right version is the fixed version.}\label{fig:chapter4:pwcheck}
+\end{figure}
+
+We illustrate the quantification method on a password checking example.
+As shown in Figure~\label{fig:chapter4:pwcheck}, the left version is vulnerable to side-channel attacks because of the early return at line 4.
+If the first bytes of \textsf{key} and \textsf{pub} are the same, the function will continue running and access the second byte.
+The right version fixes the vulnerability because the function will continue comparing the second byte even if the first byte is different.
+\tool{} identifies the leakage site in the left figure successfully and estimates the amount of leakage site is $16$ bits.
 

### 2021-04-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \\\midrule
-Unsafe Password Checker& 4096& 12.0& 1&0&0.04&  0& 18 & 104 KB & 2.4 min & 0.4 min & 0 min\\
-Safe Password Checker & 4096 & 12.0& 0&0 &0 &0 & 20 & 106 KB & 2.3 min & 0.4 min & 0 min\\
 One-byte Lookup Table & 4096 & 12.0& 1&1&7.5& 3.6 & 18 & 104 KB & 0.8 min & 0.1 min & 0 min\\
@@
 RSA mbedTLS 2.15& 4096 & 12.0 &10&8&13.3& 6.0 &-&1.8 MB& 1321.1 min & 63.5 min & 5.1 min \\
-RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&8.7& 6.1 &-& 11 MB & 981.1 min & 75.4 min & 4.5 min\\
+RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&9.7& 8.1 &-& 11 MB & 981.1 min & 75.4 min & 4.5 min\\
 RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&-&13 MB & 1021.1 min & 45.1 min & 5.5 min\\
@@
 
-\subsection{Benchmarks}
-\subsubsection{Password Checker}
-\begin{figure}
-  \begin{minipage}{0.45\linewidth}
-    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
-bool pwcheck(uint8_t *key, uint8_t *pub) {
-  for (int i = 0; i < 2; ++i) {
-    if (key[i] != pub[i]) {
-      return false;
-    }
-  }
-  return true;
-}
-\end{lstlisting}
-  \end{minipage}
-  \hfill
-  \begin{minipage}{0.45\linewidth}
-    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none]
-bool pwcheck(uint8_t *key, uint8_t *pub) {
-  bool matched = true;
-  for (int i = 0; i < 2; ++i) {
-    if (pub[i] != key[i]) 
-      matched = false;
-  }
-  return matched;
-}
-\end{lstlisting}
-  \end{minipage}
-  \caption{A password checker. The left version is vulnerable to side-channel attacks. The right version is the fixed version.}\label{fig:chapter5:pwcheck}
-\end{figure}
-
-We illustrate the quantification method on a password checking example.
-As shown in Figure~\label{fig:chapter5:pwcheck}, the left version is vulnerable to side-channel attacks because of the early return at line 4.
-If the first bytes of \textsf{key} and \textsf{pub} are the same, the function will continue running and access the second byte.
-The right version fixes the vulnerability because the function will continue comparing the second byte even if the first byte is different.
-\ctool{} identifies the leakage site in the left figure successfully and estimates the amount of leakage site is $0.04$ bits.
-
-\subsubsection{Lookup Table}
-\begin{figure}
-\centering
-    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth, frame=none]
-static const uint8_t T[1024] = {
-      0x63U, 0x7cU, 0x77U, 0x7bU, 0xf2U, 0x6bU, 0x6fU, 0xc5U,
-      0x30U, 0x01U, 0x67U, 0x2bU, 0xfeU, 0xd7U, 0xabU, 0x76U,
-...
-output = (T[(key[0]>>24)] << 24) ^
-         (T[(key[1]>>16) & 0xff] << 16) ^
-         (T[(key[2]>>8) & 0xff] << 8) ^
-         (T[(key[3]) & 0xff]);
-\end{lstlisting}
-  \caption{Lookup Tables with Small Entries.}\label{fig:chapter5:small_lookup}
-\end{figure}
-
-\begin{figure}
-\centering
-    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth, frame=none]
-static const uint32_t T[256] = {
-    0xc66363a5U, 0xf87c7c84U, 0xee777799U, 0xf67b7b8dU,
-    0xfff2f20dU, 0xd66b6bbdU, 0xde6f6fb1U, 0x91c5c554U,
-    0x60303050U, 0x02010103U, 0xce6767a9U, 0x562b2b7dU,
-    0xe7fefe19U, 0xb5d7d762U, 0x4dababe6U, 0xec76769aU};
-...
-output = (T[(key[0]>>24)] << 24) ^
-         (T[(key[1]>>16) & 0xff] << 16) ^
-         (T[(key[2]>>8) & 0xff] << 8) ^
-         (T[(key[3]) & 0xff]);
-\end{lstlisting}
-  \caption{Lookup Tables with Big Entries.}\label{fig:chapter5:big_lookup}
-\end{figure}
-
-We analyze the table lookup with \ctool{}.
-It is a common operation used by symmetric ciphers like AES.
-Figure~\ref{fig:chapter5:big_lookup} is from the original AES reference implementation.
-It uses a lookup table and each entry is 4 bytes, which is vulnerable to side-channel attacks.
-Most cryptography libraries adopted the mitigated version, shown in Figure~\ref{fig:chapter5:small_lookup}.
-The evaluation result shows the version with smaller lookup tables leaks less information, which confirm the effectiveness of the mitigation technique.
-
 \subsection{Cryptography Libraries}
@@
 
+RSA implementations blinding the data on a random value before operating on it.
 We use a fixed RSA blinding value to avoid non-deterministic behaviors during the execution.
 After that, we compare the result with the previous work~\cite{bao2021abacus,203878}.
-The result shows that \ctool{} can identify all the leakage sites reported in the previous work.
-In addition, \ctool{} identify new leakages in the private key decoded functions (\textsf{EVP\_DecodeUpdate}, \textsf{EVP\_DecodeBlock}) in OpenSSL 1.1.0f.
-To evaluate the effectiveness of the quantification result, we compare the RSA implementation between OpenSSL 1.1.0 and OpenSSL 1.1.1.
-Table~\ref{chapter5:tab:RSAOpenSSL1.1.0} shows the summary.
+The result shows that \ctool{} can identify all leakage sites reported in the previous work.
+In addition, \ctool{} identify new leakages in the private key decoded function (\textsf{conv\_ascii2bin}) in OpenSSL 1.1.1.
+To evaluate the effectiveness of the quantification result, we compare the two RSA implementations between OpenSSL 1.1.0 and OpenSSL 1.1.1.
+\ctool{} identify several functions that are vulnerable to side-channel attacks.
+We are interested if those leaked functions are fixed in the updated version.
 Note that \ctool{} can analyze the side-channel leakages at both the byte granularity and the cache line granularity.
-However, we only show the result in cache line granularity.
+We show the result analyzed with cache line granularity.
 We compare the result with \tool{}, a symbolic analysis based side-channel quantification tool.
-\tool{} can tell which line actually leaks the information.
-So it is possible that one function has several two leakage sites.
+\tool{} can tell which line in the source code actually leaks the information.
+So it is possible that one function has several leakage sites.
+Suppose the function has two leakages sites and they leak $a$ and $b$ bits respectively.
+We use the set $(a, b)$ to represent the result of \tool{}.
 
@@
 \centering\tiny\scriptsize
-\caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0}\label{chapter5:tab:RSAOpenSSL1.1.0}
+\caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0.}\label{chapter5:tab:RSAOpenSSL1.1.0}
 %\resizebox{\columnwidth}{!}{
@@
 \hline
-\textbf{File}  & \textbf{Function} & \textbf{\tool{} Result} & \textbf{\ctool{} Result} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
-bn\_lib.c& BN\_num\_bits\_word&*&CF & \cmark\\
-bn\_lib.c& bn\_correct\_top&*&CF\\
-bn\_lib.c& BN\_ucmp&*&CF\\
-ct\_b64.c& \_\_udivdi3&5.9 &CF\\
-bn\_div.c& BN\_div&*&CF\\
-bn\_gcd.c& int\_bn\_mod\_inverse&1.0 &CF\\
-bn\_lib.c& BN\_num\_bits\_word&*&DA\\
-bn\_div.c& BN\_div&17.2 &CF\\
-bn\_exp.c& BN\_mod\_exp\_mont\_consttime&1.0 &CF\\
-bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
-bn\_asm.c& bn\_sqr\_comba8&*&CF\\
-bn\_mont.c& BN\_from\_montgomery\_word&0.0 &CF\\
-bn\_div.c& BN\_div&0.3 &CF\\
+\textbf{File}  & \textbf{Vulnerable Function} & \textbf{\tool{} Result (bits)} & \textbf{\ctool{} Result (bits)} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
+bn\_lib.c& BN\_num\_bits\_word&(*, *, 17.2)& 5.7 & \cmark\\
+bn\_lib.c& bn\_correct\_top&*& 3.6 & \cmark\\
+bn\_lib.c& BN\_ucmp&*& 6.7 & \cmark\\
+ct\_b64.c& \_\_udivdi3&5.9 &4.3 & \cmark\\
+bn\_gcd.c& int\_bn\_mod\_inverse&(14.9, 9.2, 8.2, 7.9, 1.0) & 7.7 & \cmark\\
+bn\_lib.c& BN\_num\_bits\_word&(*, *, *, 12.6)& 8.5 & \cmark\\
+bn\_exp.c& BN\_mod\_exp\_mont\_consttime& (1.0, 1.0) & 1.0 & \xmark\\
+bn\_mont.c& BN\_from\_montgomery\_word& (*, *, *, *, *, *, 0.0)& 9.7 &\cmark\\
+bn\_asm.c& bn\_sqr\_comba8&0.3&5.0& \cmark\\
+bn\_div.c& BN\_div&(17.2, 11.9, 3,8, 0.3, 0.3) & 7.3  & \cmark\\
+rsa\_ossl.c& rsa\_ossl\_mod\_exp& 1.0 & 0.8 & \xmark\\
+encode.c & conv\_bin2ascii & Not Found & 1.0 & \xmark\\
 \hline
@@
 \end{table}
+
 \subsection{Machine Learning Applications}

### 2021-04-16 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 
-In conclusion, this dissertation research develops practical techniques for practical and precise side-channel analysis in software systems.
+In conclusion, this dissertation research develops practical techniques for precise side-channel analysis in software systems.
 For each proposed method, we implement and evaluate it on real-world software.
 The evaluation results show the effeteness and generality of our proposed method.
-We also open source the tool in the dissertation to facilitate future research in the area.
+We open source the tools in the dissertation to facilitate future research in the area.
 \section{Future Directions}

### 2021-04-16 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 This dissertation research studies the address-based side-channel leakages in two aspects: detection and quantification.
-In the side-channel vulnerability detection research, we explore and solve the two bottlenecks in today's automated side-channel vulnerability detection tool, performance and precision.
+In the side-channel vulnerability detection research, we explore and solve the two bottlenecks in today's automated side-channel vulnerability detection tool, performance, and precision.
 In the side-channel vulnerability quantification research, we propose two different side-channel leakage quantification tools based on information theory.
@@
 We plan only to change those points that are more likely to leak sensitive information.
-Even more, with the tool presented in the dissertation, we can only modify part of the ''severe`` leakage sites.
+Even more, with the tool presented in the dissertation, we can only modify part of the ``severe'' leakage sites.

### 2021-04-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 AES NI mbedTLS 2.15 & 4096 & 12.0&0&0&0 &0&-& 1.1 MB & 2.8 min & 0 min & 0 min  \\
-AES OpenSSL 1.1.0  & 4096 & 12.0 & 1&0 &1.4 & 0&-& 1.0 MB  & 3.1 min & 0.2 min & 0 min \\
+AES OpenSSL 1.1.0f  & 4096 & 12.0 & 1&0 &1.4 & 0&-& 1.0 MB  & 3.1 min & 0.2 min & 0 min \\
 AES  OpenSSL 1.1.1& 4096 & 12.0 & 1&0 &1.3&0&-& 909 KB & 2.9 min & 0.2 min & 0 min\\
@@
 RSA mbedTLS 2.15& 4096 & 12.0 &10&8&13.3& 6.0 &-&1.8 MB& 1321.1 min & 63.5 min & 5.1 min \\
-RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&9.7& 8.1 &-& 11 MB & 981.1 min & 75.4 min & 4.5 min\\
+RSA OpenSSL 1.1.0f& 4096 & 12.0 &12&6&9.7& 8.1 &-& 11 MB & 981.1 min & 75.4 min & 4.5 min\\
 RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&-&13 MB & 1021.1 min & 45.1 min & 5.5 min\\
@@
 \centering\tiny\scriptsize
-\caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0.}\label{chapter5:tab:RSAOpenSSL1.1.0}
+\caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0.
+According to \tool{}\cite{bao2021abacus}, the mark ``$*$'' means timeout, which indicates more severe leakages.
+}\label{chapter5:tab:RSAOpenSSL1.1.0}
 %\resizebox{\columnwidth}{!}{
+\begin{threeparttable}
 \begin{tabular}{llrrc}
@@
 \textbf{File}  & \textbf{Vulnerable Function} & \textbf{\tool{} Result (bits)} & \textbf{\ctool{} Result (bits)} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
-bn\_lib.c& BN\_num\_bits\_word&(*, *, 17.2)& 5.7 & \cmark\\
-bn\_lib.c& bn\_correct\_top&*& 3.6 & \cmark\\
+bn\_lib.c& BN\_num\_bits\_word&(*, *, *, *, *, 17.2, 12.6)& 5.7 & \cmark\\
+bn\_lib.c& bn\_correct\_top& 1.0 & 7.6 & \cmark\\
 bn\_lib.c& BN\_ucmp&*& 6.7 & \cmark\\
 ct\_b64.c& \_\_udivdi3&5.9 &4.3 & \cmark\\
-bn\_gcd.c& int\_bn\_mod\_inverse&(14.9, 9.2, 8.2, 7.9, 1.0) & 7.7 & \cmark\\
-bn\_lib.c& BN\_num\_bits\_word&(*, *, *, 12.6)& 8.5 & \cmark\\
+bn\_gcd.c& int\_bn\_mod\_inverse&(14.9, 9.2, 8.2, 7.9, 1.0) & 7.7 & \cmark\tnote{1} \\
 bn\_exp.c& BN\_mod\_exp\_mont\_consttime& (1.0, 1.0) & 1.0 & \xmark\\
 bn\_mont.c& BN\_from\_montgomery\_word& (*, *, *, *, *, *, 0.0)& 9.7 &\cmark\\
-bn\_asm.c& bn\_sqr\_comba8&0.3&5.0& \cmark\\
+bn\_asm.c& bn\_sqr\_comba8&9.3&5.0& \cmark\\
 bn\_div.c& BN\_div&(17.2, 11.9, 3,8, 0.3, 0.3) & 7.3  & \cmark\\
-rsa\_ossl.c& rsa\_ossl\_mod\_exp& 1.0 & 0.8 & \xmark\\
-encode.c & conv\_bin2ascii & Not Found & 1.0 & \xmark\\
+rsa\_ossl.c& rsa\_ossl\_mod\_exp& 1.0 & 4.8 & \cmark\\
+encode.c & conv\_bin2ascii & Not Found & 1.2 & \xmark\\
 \hline
 \end{tabular}
-%}
-\renewcommand{\baselinestretch}{1.0}\selectfont
+\end{threeparttable}
+\begin{tablenotes}
+    \scriptsize
+    \item[1] The leakage site at line 144 (OpenSSL 1.1.1) are not fixed.
+\end{tablenotes}
+
 \end{table}
+
+Table~\ref{chapter5:tab:RSAOpenSSL1.1.0} shows the leaked function and the amount of leakage reported by \tool{} and \ctool{}.
+First, as the result indicates, the leakage sites that leak more information (> 5.0 bits) are all fixed in OpenSSL 1.1.1.
+The result indicates that \ctool{} can help developers identify side-channel leakages and pick the severe from them automatically.
+As expected, we find most of the leakages are from the big number calculations.
+OpenSSL has a side-channel mitigated big number implementation.
+As long as big numbers are derived from secret data, the big number should be enabled with the flag \textsf{BN\_FLG\_CONSTTIME}.
+However, the flag is off by default.
+We find developers forget to propagate the flag in the caller, which results in the vulnerabilities in \textsf{BN\_div} and \textsf{int\_bn\_mod\_inverse}.
+Second, for those leakage sites that are not fixed by the developers, both \tool{} and \ctool{} report that they leak less amount of information.
+For example, function \textsf{BN\_mod\_exp\_mont\_consttime} check if the modulus is odd.
+However, it is not a side-channel leakage vulnerability.
+Both tools report the leakage site can leak one bit of information.
+Third, even \tool{} reports some leakage sites leak little information, \ctool{} can report the vulnerability is severe.
+\tool{} quantifies the amount of leaked information for one execution.
+So it is possible that some leakage site leak little information for one input but leaks more information for another input.
 

### 2021-04-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 bn\_lib.c& BN\_num\_bits\_word&(*, *, *, *, *, 17.2, 12.6)& 5.7 & \cmark\\
-bn\_lib.c& bn\_correct\_top& 1.0 & 7.6 & \cmark\\
+bn\_lib.c& bn\_correct\_top& 1.7 & 7.6 & \cmark\\
 bn\_lib.c& BN\_ucmp&*& 6.7 & \cmark\\
@@
 \tool{} quantifies the amount of leaked information for one execution.
-So it is possible that some leakage site leak little information for one input but leaks more information for another input.
+So it is possible that some leakage site leak little information for one input but leaks more information for a different input.
 
@@
 In the section, we demonstrate an attack that can recover the deep learning model inference output by the controlled-channel attack.
-Running the machine learning inference engine inside the enclave is a typical scenario for machine learning as service.
-The machine learning service provider upload the the trained model into an enclave running on the cloud platform and provide machine learning service to a third party user.
+Running the machine learning inference engine inside the enclave is a typical scenario for machine learning as a service.
+The machine learning service provider uploads the trained model into an enclave running on the cloud platform and provides a machine learning service to a third-party user.
 With the help of the enclave, both the model and the user's inferred result is protected from the outside.

### 2021-04-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \footnotesize
-\caption{Evaluation results overview: Name of the benchmark, The Size of the Input Data, The number of leaked functions, The Maximum Leakage, The size of the benchmark, and The Performance.}\label{chapter5:table:over_result}
+\caption{Evaluation results overview: Name of the benchmark, The Size of the Input Data, The number of leaked functions, The Maximum Leakage, The size of the benchmark, and Performance.}\label{chapter5:table:over_result}
 \centering
@@
 AES Libgcrypt 1.8.7& 4096 & 12.0 &0 &0 &0&0 &-&4.4 MB & 10.2 min& 0 min & 0 min\\
-RSA mbedTLS 2.15& 4096 & 12.0 &10&8&13.3& 6.0 &-&1.8 MB& 1321.1 min & 63.5 min & 5.1 min \\
+RSA mbedTLS 2.15& 4096 & 12.0 &10&8&10.3& 6.0 &-&1.8 MB& 1321.1 min & 63.5 min & 5.1 min \\
 RSA OpenSSL 1.1.0f& 4096 & 12.0 &12&6&9.7& 8.1 &-& 11 MB & 981.1 min & 75.4 min & 4.5 min\\
@@
 Tiny DNN & 12000 & - & 17&14&17.1&16.1&-& 4.4 MB & 183.5 min & 24.6 min & 5.2 min\\
-GDK 3.24.23 & 4096 & 16.0 & 33&31& 12.1& 6.0&-& 48.5 MB & 60.8 min & 4.1 min & 1.5 min\\
+GDK 3.24.23 & 4096 & 16.0 & 33&31& 12.1& 6.0&-& 48.5 MB & 1060.8 min & 24.1 min & 1.5 min\\
 \bottomrule
@@
 \tool{} quantifies the amount of leaked information for one execution.
-So it is possible that some leakage site leak little information for one input but leaks more information for a different input.
-
-\subsection{Machine Learning Applications}
+So it is possible that some leakage sites leak little information for one input but leak more information for a different input.
+
+\subsection{Non-cryptography Applications}
+
+%% TODO
 In the section, we demonstrate an attack that can recover the deep learning model inference output by the controlled-channel attack.

### 2021-04-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 AES Libgcrypt 1.8.7& 4096 & 12.0 &0 &0 &0&0 &-&4.4 MB & 10.2 min& 0 min & 0 min\\
-RSA mbedTLS 2.15& 4096 & 12.0 &10&8&10.3& 6.0 &-&1.8 MB& 1321.1 min & 63.5 min & 5.1 min \\
+RSA mbedTLS 2.15& 4096 & 12.0 &7&6&10.3& 6.0 &-&1.8 MB& 1321.1 min & 63.5 min & 5.1 min \\
 RSA OpenSSL 1.1.0f& 4096 & 12.0 &12&6&9.7& 8.1 &-& 11 MB & 981.1 min & 75.4 min & 4.5 min\\
@@
 So it is possible that some leakage sites leak little information for one input but leak more information for a different input.
+We run the chi-squared test to determine if any two leaked functions have independent leakages.
 
@@
 
-%% TODO
+%% TODO Analyze the result of the GTK
 In the section, we demonstrate an attack that can recover the deep learning model inference output by the controlled-channel attack.

### 2021-04-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 The process is like traversing a binary tree and increase the counter of the child node.
-According to Definition~\ref{chapter5:def}, the amount of the leakage is
+According to Definition~\ref{chapter5:def}, the amount of the leakage is $1.4$ $\mathit{bits}$.
 
@@
 We run the chi-squared test to determine if any two leaked functions have independent leakages.
+However, we can not conclude any two leakages are independent under the chi-squared test.
+We think it is due to the avalanche effect in cryptography.
 
@@
 \end{lstlisting}
-  \caption{A code fragment}
+  \caption{The reported leaked functions are not the root cause of the vulernability}
   \label{fig:limitation}

### 2021-04-16 SupplementaryMaterial/Acknowledgments.tex
Updates from Overleaf

@@
 % Place acknowledgments below.
-First of all, I would like to thank my advisor Dr.
-Dinghao Wu for the continuous support of my Ph.D.
+I am tremendously fortunate to have been advised by Dr.
+Dinghao Wu.
+I thank Dinghao for inviting me to EPFL on his sabbatical.
+A large portion of the research presented in the dissertation was finished when I worked in Switzerland.
+The knowledge and skills I learned from him will also help me make progress in my future career.
+I also think him for treating me as an independent researcher since the forth year of my Ph.D.
 study.
@@
 Without his encouragement and support, I could not have finished the program.
-I also thank Dinghao for inviting me to Switzerland on his sabbatical.
-A large portion of the research presented in the dissertation was finished when I worked in Switzerland.
-The knowledge and skills I learned from him will also help me make progress in my future career.
 
-Beside my advisor, I would like to thank my committee members, Dr. Peng Liu, Dr. Sencun Zhu, Dr. Benjamin V. Hanrahan, and Prof. James R. Larus for their time, reviewing my dissertation.
+Beside my advisor, I also thank my committee members, Dr.
+Peng Liu, Dr.
+Sencun Zhu, Dr.
+Benjamin Hanrahan, and Dr.
+James Larus for their time, reviewing my dissertation.
+Without the strong encouragement from Dr.
+Peng Liu's former students in 2015, I would not have applied for Penn State.
 
+Pursuing a Ph.D.
+can be extremely stressful, but summer internships are always the relaxing and productive moments during my study.
 I would also like to thank Dr.
@@
 Kevin Kane, and Dr.
-Brian LaMacchia for their help during my internship at Baidu X-Lab and Microsoft Research Lab.
+Brian LaMacchia for their help during my internship at Baidu X-Lab and Microsoft Research.
 I also thank my friends and collaborators at Penn State University and EPFL.

### 2021-04-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 RSA Libgcrypt 1.8.7& 4096 & 12.0 &8&6&8.6& 6.6&-&4.4 MB & 1412.6 min & 23.9 min & 4.3 min\\
-Tiny DNN & 12000 & - & 17&14&17.1&16.1&-& 4.4 MB & 183.5 min & 24.6 min & 5.2 min\\
+Tiny DNN & 10000 & - & 17&14&17.1&16.1&-& 4.4 MB & 183.5 min & 24.6 min & 5.2 min\\
 GDK 3.24.23 & 4096 & 16.0 & 33&31& 12.1& 6.0&-& 48.5 MB & 1060.8 min & 24.1 min & 1.5 min\\
@@
 %% TODO Analyze the result of the GTK
-In the section, we demonstrate an attack that can recover the deep learning model inference output by the controlled-channel attack.
-Running the machine learning inference engine inside the enclave is a typical scenario for machine learning as a service.
-The machine learning service provider uploads the trained model into an enclave running on the cloud platform and provides a machine learning service to a third-party user.
-With the help of the enclave, both the model and the user's inferred result is protected from the outside.
-However, we will show that the above information can be easily retrieved from the untrusted world through the side-channel attack.
-
-We use MNIST as the dataset and LeNet-5 for MNIST digits recognition task.
-LeNet-5 is known to work well on handwritten digit recognition.
-We first train the network.
+
+We evaluate \ctool{} on TinyDNN, a deep learning framework in C++.
+We construct a LeNet-5 like model~\cite{lecun1998gradient} and trained it with the MINIST dataset.
 The batch size in our experiment is 10 and the numbers of epochs is 30.
@@
 Then we use the model to infer the images.
+The inference dataset consists of $10000$ images.
 During the inference, we also record the page access information.
+The evaluation shows that  leakage primarily comes from the activation function and the image convert function.
 

### 2021-04-16 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
   \includegraphics[width=.5\columnwidth]{./figures/chapter3/architecture.pdf}
-  \caption{Computer Memory Hierarchy}\label{fig:memory_hierarchy}
+  \caption{Computer memory hierarchy.
+The hierarchy is designed to minimise the access time with the relatively low cost.
+It is the root cause of many side-channel attacks.}\label{fig:memory_hierarchy}
 \end{figure}
@@
   \includegraphics[width=.65\columnwidth]{./figures/chapter3/address.pdf}
-  \caption{Memory Addressing}\label{fig:memory_address}
+  \caption{Memory addressing}\label{fig:memory_address}
 \end{figure}
@@
 the attacker has noise-free observations as in previous work~\cite{203878,182946,Brotzman19Casym}.
-The threat model captures most cache-based and address-based side-channel attacks.
+The threat model captures most address-based side-channel attacks and apply to the three attack models: 1) time-based attacks, 2) access-based attacks, 3) trace-based attacks.
 We only consider deterministic programs and assume an attacker has access to the source code or binary executable of the target program.

### 2021-04-16 SupplementaryMaterial/Acknowledgments.tex
Updates from Overleaf

@@
 The knowledge and skills I learned from him will also help me make progress in my future career.
-I also think him for treating me as an independent researcher since the forth year of my Ph.D.
+I also thank him for treating me as an independent researcher since the fourth year of my Ph.D.
 study.
@@
 
-Beside my advisor, I also thank my committee members, Dr.
+Besides my advisor, I also thank my committee members, Dr.
 Peng Liu, Dr.
@@
 Benjamin Hanrahan, and Dr.
-James Larus for their time, reviewing my dissertation.
+James Larus, for their time, reviewing my dissertation.
 Without the strong encouragement from Dr.
@@
 Pursuing a Ph.D.
-can be extremely stressful, but summer internships are always the relaxing and productive moments during my study.
+can be extremely stressful, and summer internships are always the relaxing and productive moments during my study.
 I would also like to thank Dr.
@@
 Kevin Kane, and Dr.
-Brian LaMacchia for their help during my internship at Baidu X-Lab and Microsoft Research.
+Brian LaMacchia for their help during my internships at Baidu X-Lab and Microsoft Research.
 I also thank my friends and collaborators at Penn State University and EPFL.

### 2021-04-17 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 \section{Side-channels}
-Side channels are ubiquitous in modern computer systems as sensitive information can leak through many mechanisms such as power, electromagnetic radiation, and even sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}.
-It is typically hard to fix side-channel vulnerabilities for real-world software systems.
-Among them, software side-channel attacks, such as cache attacks, memory page attacks, and controlled-channel attacks, are especially problematic as they do not require physical proximity~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}.
-These attacks arises from shared micro-architectural components in a computer processor.
-By observing inadvertent interactions between two programs, attackers can infer program execution flows that manipulate secrets and guess secrets such as encryption keys~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.
+Side-channel attacks allow an attacker to infer sensitive information based on ``side-channel'' information.
+Examples of the ``side-channel'' information include execution timing, CPU usages, power consumption, and even sound.
+For example, in 1996, Kocher demonstrated that an attacker could break cryptosystems like RSA and Diffie-Hellman by measuring the execution time of a simple modular exponentiation operation.
+The simple modular exponentiation calculates the remainder of an exponent divided by an integer.
+The simple modular exponentiation operation executes faster when the exponent bit is 0 and slower when the exponent bit is 1.
+An attacker can infer the whole secret key by measuring the execution time of the operation bit by bit.
 

### 2021-04-17 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \section{Problem}
-Side-channel attacks allow an attacker to infer sensitive information such as cryptographic keys, personal data from software products unconsciously.
-Based on the discussions in \S\ref{chapter1} and \S\ref{chapter2}, patching leakage sites in software is usually easier than adopting new hardware to defend against side-channel attacks.
+Side channels are ubiquitous in modern computer systems as sensitive information can leak through many mechanisms such as power, electromagnetic radiation, and even sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}.
+It is typically hard to fix side-channel vulnerabilities for real-world software systems.
+Among them, software side-channel attacks, such as cache attacks, memory page attacks, and controlled-channel attacks, are especially problematic as they do not require physical proximity~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}.
+These attacks arise from shared micro-architectural components in a computer processor.
+By observing inadvertent interactions between two programs, attackers can infer program execution flows that manipulate secrets and guess secrets such as encryption keys~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.
+
+The root cause of most side-channel attacks can been as a result of the combination of the hardware design and the vulnerable software.
+Existing countermeasures can be classified into two categories: fixing the software and adopting new hardware.
+Based on the discussion in \S\ref{chapter1} and \S\ref{chapter2}, patching bugs in software is usually easier than adopting new hardware to defend against side-channel attacks.
 In order to eliminate those leakage sites, developers often need to identify potential leakage sites from the code base manually.

### 2021-04-17 SupplementaryMaterial/Abstract.tex
Updates from Overleaf

@@
 
-\vspace{-0.3in}
+%\vspace{-0.3in}
 Side-channel attacks can leak secret information unconsciously from non-functional characteristics, e.g., time, power, and memory usage.
-Similar to many other vulnerabilities in software, attackers exploit the flaws in designs of hardware and implementations of software.
-Contrary to the the hardware countermeasures, which usually need changes to the complex underlying hardware, software solutions are more easier to adopt in many scenarios.
-This dissertation study various aspects of the side-channel vulnerabilities.
+Like many other software vulnerabilities, attackers exploit flaws in designs of hardware and implementations of software.
+Hardware countermeasures, which usually need changes to the complex underlying hardware, are hard to adopt in practice.
+On the contrary, software approaches are usually easy to implement.
+This dissertation studies various aspects of side-channel vulnerabilities.
 
-The dissertation first introduces a new method to detect address-based side-channel in the binary code.
-While existing approaches can identify side-channel leakages in real-world programs.
-We notice that while some existing work can detect side-channel leakages.
-Many of them are computationally expensive and apply some domain knowledge to simplify the analysis.
-We examine the bottleneck of current symbolic approaches and scaling it production-system crypto analysis.
-The evaluation results confirm that the approach is much faster than the state of art tools while identifying all the known leakages reported by previous tools.
+The dissertation first introduces a new method to detect address-based side-channel vulnerabilities in the binary code.
+While existing approaches can identify side-channel leakages in real-world programs, many of them are computationally expensive and need to apply domain knowledge to simplify the analysis.
+We examine the bottleneck of current symbolic approaches and propose methods to identify side-channel vulnerabilities in real-world cryptography applications.
+We implement the approach in a tool and apply it on popular cryptography libraries.
+The evaluation results confirm that the tool is much faster than the state of art tools while identifying all the known leakages reported by previous tools.
+In addition, our tool catches new vulnerabilities that are missed by previous tools.
+We confirm those vulnerabilities with manual checks and by contacting the developers.
 
@@
 By applying the Central Limit Theorem, we provide an error bound for these estimations.
+We have implemented the technique in a tool called \tool{} and apply \tool{} on OpenSSL, mbedTLS, Libgcrypt, and Monocypher.
+Our results demonstrate that most reported vulnerabilities are difficult to exploit in practice and should be de-prioritized by developers.
 The evaluation results shows that our method can successfully distinguish severe leakages from many negligible leakages.
@@
 Third, we extend our approach to quantify side-channel leakages from multiple trace attacks.
-In this work, we present MME, an address-based side-channel detection and quantification tool that can quantify the side-channel leakages in a conservation but precise way.
-Contrary to previous side-channel detection tools, our approach can identify those really severe side-channel leakages without false positives.
-Moreover, our tools can estimate the total effect of multiple leakage sites as well.
-MME consists of three steps.
+In this work, we present \ctool{}, an address-based side-channel detection and quantification tool that can quantify the side-channel leakages in a conservation but precise way.
+Contrary to previous side-channel detection tools, our approach can identify those severe side-channel leakages without false positives.
+Moreover, by applying the chi-squared test, our tools can estimate the total effect of multiple leakage sites as well.
+\ctool{} consists of three steps.
 First, the target program is running with a number of the sensitive inputs to record the memory access under different inputs.

### 2021-04-17 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 \section{Side-channels}
-Side-channel attacks allow an attacker to infer sensitive information based on ``side-channel'' information.
-Examples of the ``side-channel'' information include execution timing, CPU usages, power consumption, and even sound.
-For example, in 1996, Kocher demonstrated that an attacker could break cryptosystems like RSA and Diffie-Hellman by measuring the execution time of a simple modular exponentiation operation.
+A side-channel attack is any attack that allows adversaries to infer sensitive information based on ``side-channel'' information.
+In 1996, Kocher published the first side-channel attack in the literature.
+He demonstrated that an attacker could break cryptosystems like RSA or Diffie-Hellman by measuring the execution time of a simple modular exponentiation operation.
 The simple modular exponentiation calculates the remainder of an exponent divided by an integer.
@@
 An attacker can infer the whole secret key by measuring the execution time of the operation bit by bit.
+Since then, researchers have proposed numerous side-channel attacks which exploit numerous kinds of ``side-channel'' information, including execution timing, CPU usages, power consumption,  electromagnetic radiation, and even sound.
 
-When we examine those side-channel attacks, many of them stem from the two code patterns, \emph{secret-dependent control-flow transfers} and \emph{secret-dependent data accesses}.
+Various countermeasures have been proposed to defend against side channel attacks.
+Hardware-level solutions, such as reducing shared resources, adopting oblivious RAM, and using transnational memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need new hardware features and changes in modern complex computer systems, which are hard to adopt in reality.
+Therefore, a promising and universal direction is software countermeasures, detecting and eliminating side channel vulnerabilities (data flow from secrets to load addresses, and data flow from secrets to branch conditions) from code base.
+For example, when we examine those side-channel attacks, many of them stem from the two code patterns: \emph{secret-dependent control-flow transfers} and \emph{secret-dependent data accesses}.
 \begin{figure}[h]
@@
 Other kinds of side-channels like controlled-channel attack~\cite{7163052}, can observe the memory access at the level of memory pages.
-
-Various countermeasures have been proposed to defend against side channel attacks.
-Hardware-level solutions, such as reducing shared resources, adopting oblivious RAM, and using transnational memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need new hardware features and changes in modern complex computer systems, which are hard to adopt in reality.
-Therefore, a promising and universal direction is software countermeasures, detecting and eliminating side channel vulnerabilities (data flow from secrets to load addresses, and data flow from secrets to branch conditions) from code base.
 
@@
 Chapter~\ref{chapter5} extends the approach and quantifies the side-channel leakage in multiple-trace attack.
-Chapter~\ref{chapter6} concludes the dissertation.
+Chapter~\ref{chapter6} concludes the dissertation and proposes the future work.

### 2021-04-17 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 The simple modular exponentiation operation executes faster when the exponent bit is 0 and slower when the exponent bit is 1.
-An attacker can infer the whole secret key by measuring the execution time of the operation bit by bit.
+An attacker can infer the whole secret key by measuring the execution time of the operation.
 Since then, researchers have proposed numerous side-channel attacks which exploit numerous kinds of ``side-channel'' information, including execution timing, CPU usages, power consumption,  electromagnetic radiation, and even sound.
 
-Various countermeasures have been proposed to defend against side channel attacks.
-Hardware-level solutions, such as reducing shared resources, adopting oblivious RAM, and using transnational memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need new hardware features and changes in modern complex computer systems, which are hard to adopt in reality.
-Therefore, a promising and universal direction is software countermeasures, detecting and eliminating side channel vulnerabilities (data flow from secrets to load addresses, and data flow from secrets to branch conditions) from code base.
-For example, when we examine those side-channel attacks, many of them stem from the two code patterns: \emph{secret-dependent control-flow transfers} and \emph{secret-dependent data accesses}.
+A large portion of side-channel attacks is the joint result of the underlying computer architecture design and the above software stack.
+One example is cache channel attacks.
+The cache is a smaller but faster memory designed to bridge the gap of the access time between the main memory and CPU registers by storing the copy of recently accessed data.
+Some software accesses different memory addresses when it processes different input data.
+Because the size of the cache is significantly smaller than the size of the main memory, the CPU can only find part of the data in the cache.
+Such differences can be reflected in the differences between the program execution time.
+Hence we have cache side-channel attacks.
+
+Various countermeasures have been proposed to defend against side-channel attacks.
+Based on the above discussion, existing countermeasures can be further divided into two categories, the hardware-based method and the software-based method.
+Hardware-level solutions, such as reducing shared resources, adopting oblivious RAM, and using transnational memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need to adopt new hardware features and apply changes to today's modern complex computer systems, which are hard to adopt in reality.
+Therefore, a promising and universal direction is software countermeasures, detecting and eliminating side channel vulnerabilities (data flow from secrets to load addresses, and data flow from secrets to branch conditions) from existing code base.
+For example, when we examine those side-channel attacks, many of them exploit two kinds of code patterns: \emph{secret-dependent control-flow transfers} and \emph{secret-dependent data accesses}.
 \begin{figure}[h]
@@
 
-The key intuition is that above side-channel attacks happen when a program accesses different memory addresses if the program has different sensitive inputs.
-As shown in Figure~\ref{fig:secret:cf} and Figure~\ref{fig:secret:da}, if a program shows different patterns in control transfers or data accesses when the program processes different sensitive inputs, the program could possibly have side channels vulnerabilities.
-Different kinds of side-channels can be exploited to retrieve information in various granularities.
+The key intuition is that the above side-channel attacks happen when a program accesses different memory addresses if the program has different sensitive inputs.
+As shown in Figure~\ref{fig:secret:cf} and Figure~\ref{fig:secret:da}, if a program shows different patterns in control transfers or data accesses when the program processes different sensitive inputs, the program could have side channels vulnerabilities.
+Various techniques can be used to exploit the above leakage site at different granularities.
 For example, cache channels can observe cache accesses at the level of cache sets~\cite{liu2015last}, cache lines~\cite{184415} or other granularities.
 Other kinds of side-channels like controlled-channel attack~\cite{7163052}, can observe the memory access at the level of memory pages.
+So a natural defense approach is to remove the above code patterns in the software.
 
-However, eliminating side channel vulnerabilities from real-world software code base is not easy.
-First, some vulnerable implementations perform better.
+However, eliminating side-channel vulnerabilities from real-world software code base is not easy.
+First, some vulnerable implementations actually perform better.
 For example, RSA implementations usually adopt the CRT optimization, which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}.
 Fixing vulnerabilities can introduce new weaknesses.
-Second, it is hard to detect side channels in reality.
-While recent work~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} can detect many side-channel vulnerabilities, they either suffer from expensive computation cost or high false positives and false negatives.
-For example, DATA~\cite{217537} reports 2,248 potential leakage sites for the RSA implementation in OpenSSL 1.1.0f\@.
+We are in a dilemma between the performance and the security.
+Second, it is hard to detect side-channel leakages in reality.
+While recent work~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} can detect many side-channel vulnerabilities, they either suffer from expensive computation costs or high false positives and false negatives.
+For example, recent tools like DATA~\cite{217537} reports 2,248 potential leakage sites for the RSA implementation in OpenSSL 1.1.0f\@.
 Further analysis shows 1,510 leaks can be dismissed.
@@
 Third, most vulnerabilities pose a negligible risk.
-Although some vulnerabilities result in the key being entirely compromised~\cite{184415, aumuller2002fault}, many others are less severe in reality.
+Although some vulnerabilities result in the key being compromised~\cite{184415, aumuller2002fault} entirely, many others are less severe in reality.
 Therefore, we need a proper quantification metric to assess the sensitivity of side-channel vulnerabilities, so a developer can efficiently triage them.
@@
 Recent work can identify side-channel leakages.
-But those tools can only work on small programs or need to apply some domain knowledge to simplify the analysis.
+But those tools can only work on small programs or need to apply some domain knowledge of the target program to simplify the analysis.
     \item Side-channel vulnerabilities are ubiquitous.
@@
 
-We try to address the above problem from the following two aspects.
+In this dissertation, we try to address the above problem from the following two aspects.
 \begin{enumerate}
@@
 Therefore, prior symbolic execution work~\cite{203878,236338,Brotzman19Casym} either analyzes only small programs or applies domain knowledge~\cite{203878} to simplify the analysis.
-We examine the bottleneck of the trace-oriented symbolic execution and optimize it to work for real-world applications.
-    \item \textbf{Quantification.} We propose methods to quantify information leakage precisely from a single trace attack.
-We quantify the number of bits that can leak during a real execution and define the amount of leaked information as the cardinality of possible secrets based on an attacker's observation.
+We examine the bottleneck of the trace-oriented symbolic execution and optimize it to work on real-world applications.
+    \item \textbf{Quantification.} We propose methods to quantify the amount of information leakage precisely that an attacker can retrieve during the side-channel attacks.
+We define the amount of leaked information as the cardinality of possible secrets based on an attacker's observation.
 Before an attack, an adversary has a large but finite input space.
@@
 By counting the number of inputs~\cite{10.1007/11499107_24}, we can quantify the information leakage precisely.
-We use symbolic execution to generate constraints to model the relation between the original sensitive input and an attacker's observations.
 \end{enumerate}
@@
 This dissertation makes the following contributions.
-First, we propose a novel method that can detect side-channel vulnerabilities in real-world applications automatically fast and precisely.
+First, we propose a novel method that can detect side-channel vulnerabilities in real-world applications fast and precisely.
 Second, we propose methods that can quantify each side-channel leakages precisely.
@@
 The key idea is to only symbolically execute those machine instructions that are relevant to vulnerabilities while executing other instructions natively.
-    \item We implement the above method in a tool called \detect{}.
+We implement the above method in a tool called \detect{}.
 The evaluation results shows that \detect{} is 3 to 100 times faster than existing tools while identifying all vulnerabilities when we run it on the same library.
@@
 \begin{itemize}
-    \item We propose a method that can quantify fine-grained leaked
-          information from side-channel vulnerabilities that result from actual attack
-          scenarios in a single trace attack. Our approach differs from previous ones in that we
-          model real attack scenarios for one execution.
-          We model the information quantification problem as a counting problem
-          and use a Monte Carlo sampling method to estimate the information leakage.
-    \item We implement the method into a tool and apply it
-          to several pieces of real software. \tool{} successfully identifies
-          previous unknown and known side-channel vulnerabilities and calculates the corresponding information leakage.
+    \item We propose a method that can quantify fine-grained leaked information from side-channel vulnerabilities that result from actual attack scenarios in a single trace attack.
+Our approach differs from previous ones in that we precisely calculate the amount of leakages.
+We model the information quantification problem as a counting problem and use a Monte Carlo sampling method to estimate the information leakage.
+    \item We implement the method into a tool and apply it to several pieces of real software.
+\tool{} successfully identifies previous unknown and known side-channel vulnerabilities and calculates the corresponding information leakage.
 Our results are useful in practice.
-          The leakage estimates and the corresponding trigger inputs can
-          help developers to triage and fix the vulnerabilities.
+The leakage estimates and the corresponding inputs that triggers the vulnerability can help developers to triage and fix the vulnerabilities.
 \end{itemize}
 
-To address Problem 2, we make the following contributions on quantifying side-channel leakages on chosen plaintext side-channel attacks:
+To address Problem 2, we make the following contributions on quantifying side-channel leakages on a multiple trace attack:
 \begin{itemize}
     \item We propose a novel method that can detect and analyze the effect of each side-channel leakage sites automatically.
-Our analysis combine information from both the source code and the run-time execution, which makes the method more effective in finding the leakages.
-The method can combine multiple leakage sites to retrieve more information as well.
+Our analysis combine the information from both the source code and the run-time execution, which makes the method more effective in finding the leakages.
+By running the chi-squared test, the method can find independent leakages.
+Attacker can combine multiple leakage sites to retrieve more information as well.
     \item We analyze the amount of information leakage from side-channel vulnerabilities based on the channel capacity.
@@
 The theory can serve as the foundation of the future work on quantify the information leakage based on the fuzzing.
-    \item We implement the above method in a tool called \ctool{} and evaluate the tool with several benchmarks and several real-world applications such as OpenSSL, mbedTLS, TinyDNN, and GTK.
+    \item We implement the above method in a tool called \ctool{} and evaluate the tool with several benchmarks and several real-world applications such as OpenSSL, mbedTLS, Libgcrpyt, TinyDNN, and GTK.
 The results show that our tool can detect and quantify the side-channel leakages effectively.
@@
 The rest of the dissertation is organized as follows.
-We present relevant backgrounds and related works in Chapter~\ref{chapter2}.
+We present background and related work of the dissertation in Chapter~\ref{chapter2}.
 Chapter~\ref{chapter3} presents a novel method to detect side-channel vulnerabilities in binary executables.
 Chapter~\ref{chapter4} presents a method that can quantify each side-channel leakage in a single trace attack.
-Chapter~\ref{chapter5} extends the approach and quantifies the side-channel leakage in multiple-trace attack.
+Chapter~\ref{chapter5} extends the approach and quantifies the side-channel leakage in a multiple-trace attack.
 Chapter~\ref{chapter6} concludes the dissertation and proposes the future work.

### 2021-04-17 SupplementaryMaterial/Acknowledgments.tex
Updates from Overleaf

@@
 can be extremely stressful, and summer internships are always the relaxing and productive moments during my study.
-I would also like to thank Dr.
+I would like to thank Dr.
 Kang Li, Mr.
@@
 
-This research was supported in part by by the National Science Foundation (NSF) under grant CNS-1652790, and the Office of Naval Research (ONR) under grants N00014-16-1-2912, N00014-16-1-2265, and N00014-17-1-2894.
+This research was supported in part by the National Science Foundation (NSF) under grant CNS-1652790, and the Office of Naval Research (ONR) under grants N00014-16-1-2912, N00014-16-1-2265, and N00014-17-1-2894.
 Any opinions, conclusions in the paper do not reflect the views of funding agencies.

### 2021-04-17 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 An attacker can infer the whole secret key by measuring the execution time of the operation.
-Since then, researchers have proposed numerous side-channel attacks which exploit numerous kinds of ``side-channel'' information, including execution timing, CPU usages, power consumption,  electromagnetic radiation, and even sound.
+Since then, researchers have proposed numerous side-channel attacks which exploit numerous kinds of ``side-channel'' information, including execution timing~\cite{184415,disselkoen2017prime+}, power consumption~\cite{kar20178}, electromagnetic radiation~\cite{agrawal2002side,217605}, and even sound~\cite{chari1999towards}.
 

### 2021-04-17 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 \chapter{Related Work}\label{chapter2}
-This chapter introduces the related work in this dissertation. We present the related work from the following aspects: side-channel attacks, detections, mitigation, and information quantification.
+This dissertation studies the address-based side-channel attacks.
+We review the related work in this chapter.
+The related work covers the following aspects: side-channel attacks, detections, mitigation, and information quantification.
 
@@
 While there are many kinds of side-channel attacks, we focus on address-based side-channel attacks in this dissertation.
-Address-based side-channel attacks happen when a program accesses different memory locations when it processes various secrets.
-In modern computers, an attacker may shares some hardware resources (e.g., Cache, TLB, and DRAM) with the victim in today's computer system ~\cite{ge2018survey,szefer2019survey}.
+Address-based side-channel attacks happen when a program accesses different memory locations when it processes different secrets.
+In modern computer ssytems, an attacker may shares some hardware resources (e.g., Cache, TLB, and DRAM) with the victim~\cite{ge2018survey,szefer2019survey}.
 As a result, the attacker can probe the shared hardware resource to infer the memory accesses of the victim.
@@
     \centering
-    \caption{Due to the page limit, we only shows some representations of the vast side-channel attacks: Attacks, the shared hardware resources with attackers, the granularity of the attacker can observe, is there any published attacks on non-cryptography library and if the type of attack can exploit multiple leakage sites.}
+    \caption{Due to the page limit, we only shows some representations of the vast side-channel attacks: Attacks, the shared resources with attackers, the granularity of the attacker can observe, is there any published attacks on non-cryptography library and if the type of attack have been used to exploit multiple leakage sites.}
     \label{table:side_channel_attack}
@@
 When a CPU reads data from a memory location, it first checks the cache.
-If it finds that the cache stores a copy of the memory location, a cache hit occurs.
-Otherwise, the CPU needs to read the main memory data, and a cache miss happens.
+If it finds that the cache has a copy of data from the main memory, a cache hit occurs.
+Otherwise, the CPU needs to read from the main memory, and a cache miss happens.
 
 Cache channels~\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last,184415} rely on the time difference between cache misses and cache hits.
-The core-private caches are traditionally set-associate cache.
+The core-private caches (e.g., L1 and L2) are traditionally set-associate cache.
 The cache is divided into different cache sets, and each cache set is made up of several cache lines.
@@
 memory'' from the cache and waits for the victim to access the memory, who may load the sensitive information to the cache line.  In the next phase,
-the attacker reloads the ``monitored memory''. By measuring the time differences
-brought by cache hits and misses, the attacker can further infer the sensitive information.
+the attacker reloads the ``monitored memory''.
+By measuring the time differences brought by cache hits and misses, the attacker can infer the sensitive information.
 On X86-64 machines, the two steps can be combined by measuring the time differences of the \textsf{clflush} instruction.
 
-Based on the above attacks, some work~\cite{brickell2011technologies} suggests not having secret-dependent memory accesses at coarser than cache line granularity should be secure enough.
-However, recent studies shows that having memory accesses within a cache line is also dangerous.
+Based on the above attacks, some work~\cite{brickell2011technologies} suggests having secret-dependent memory accesses at finer than the size of one cache line should be secure enough.
+However, recent studies shows that having different memory accesses within a cache line is also dangerous.
 One example is the CacheBleed attack~\cite{yarom2017cachebleed}.
@@
 One example is the controlled-channel attack~\cite{xu2015controlled}.
-It is a primary threats for the trusted execution environments (TEEs).
+It is a primary threat for the trusted execution environments (TEEs).
 A privileged adversary (e.g., Kernel) can infer the sensitive information by manipulating the enclave page access.
@@
 If the victim enclave program accesses the memory table, then the OS can observe the page faults and  know which page is accessed.
-While the granularity of the controlled-channel attacks is coarse-grained,  controlled-channel attacks allow the attacker to have a noise-free observation.
-Other examples like the TLB side-channel attack, DDRAM attacks share the same page-level granularity.
+While the granularity of the controlled-channel attacks is more coarse-grained compared with cache channel attacks, controlled-channel attacks allow the attacker to have a noise-free observation.
+Other examples like the TLB side-channel attack and DDRAM attacks share the same page-level granularity.
 
-Based on the above discussion, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs) in the dissertation.
+Based on the above discussion, we consider three types of granularities in the dissertation: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs).
 To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in the literature.

### 2021-04-17 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 Previous work~\cite{182946} classifies the address-based side-channel attacks into three type based on the type of information that an attacker can learn during the attack.
-\subsubsection*{Time-based Attacks}
-In time-based attacks, an adversary can monitor the execution time of a victim.
+\subsubsection*{Timing-based Attacks}
+In timing-based attacks, an adversary can monitor the execution time of a victim.
 It could be the overall execution time or the execution time of some interesting points (e.g.
 a function).
-The execution time is correlated to some events (e.g., cache hits, cache misses, page faults) during the execution.
-Examples of those attacks include remote timing attacks~\cite{brumley2005remote}, Bernstein attack on AES~\cite{bernstein2005cache}, and Kocher’s original attack~\cite{kocher1996timing} from CRYPTO 96.
+The execution time is correlated to some events (e.g., cache hits, cache misses, page faults, the number of instructions) during the execution.
+Examples of those attacks include remote timing attacks~\cite{brumley2005remote}, Bernstein's attack on AES~\cite{bernstein2005cache}, and Kocher’s original attack~\cite{kocher1996timing} from CRYPTO 96.
 \subsubsection*{Access-based Attacks}
 In access-based attacks, an adversary can probe one time only after the termination of the victim program.
-The attacker can learn the outcome of each memory access.
+The attacker can learn the memory addresses are that accessed during the execution.
 For example, a cache-based channel attack can know which memory access incurs a cache hit and which memory access incurs a cache miss.
-Because an attacker can probe the victim program after the execution, the attacker do not know the order of accesses.
-Access-based attacks often happen in the cloud computing environment when the attacker and victim share the same hardware (e.g., L3 Cache).
+Since the attacker can probe the victim program after the execution, the attacker do not know the order of accesses.
+Access-based attacks often happen in the cloud computing environment when the attacker and victim share the same hardware (e.g., LLC Cache).
 Examples of those attacks include cache template attacks~\cite{191010}, Prime and Probe attacks~\cite{liu2015last}, and Flush and Reload attacks~\cite{yarom2014flush+}.

### 2021-04-18 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 \section{Problem}
-Side channels are ubiquitous in modern computer systems as sensitive
-information can leak through many mechanisms such as power,
-electromagnetic radiation, and even
-sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}.
-Among them, software side-channel attacks, such as cache attacks, memory page
-attacks, and controlled-channel attacks, are especially problematic as they do not require physical proximity~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}. These
-attacks arises from shared micro-architectural components in a computer processor.
-By observing inadvertent interactions between two programs, attackers can infer program
-execution flows that manipulate secrets and guess secrets such as encryption
-keys~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.
-
-Recent work~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946}
-can detect many side-channel vulnerabilities. For example,
-DATA~\cite{217537} reports 2,248 potential leakage sites for the RSA
-implementation in OpenSSL 1.1.0f\@.
-Further analysis shows 1,510 leaks can be dismissed. But that
-leaves 460 data-access leaks and 278 control-flow leaks.
+In Chapter~\ref{chapter3}, we present a method to identify address-based side-channel leakage sites in cryptography libraries ~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.
+However, many reported leakage sites are not patched by developers.
+Recent work on side-channel vulnerabilities identification~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} also faces the same situation.
+For example, DATA~\cite{217537} reports 2,248 potential leakage sites for the RSA implementation in OpenSSL 1.1.0f\@.
+Further analysis shows 1,510 leaks can be dismissed.
+But that leaves 460 data-access leaks and 278 control-flow leaks.
 Many of these vulnerabilities have not been fixed by developers for a variety of reasons.
+
 First, some vulnerable implementations perform better. For example,
-RSA implementations usually adopt the CRT optimization,
-which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}.
-Second, fixing vulnerabilities can introduce new
+RSA implementations usually adopt the CRT optimization, which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}. Second, fixing vulnerabilities can introduce new
 weaknesses.
 Third, most vulnerabilities pose a negligible risk.
-Although some vulnerabilities result in the key being
-entirely compromised~\cite{184415, aumuller2002fault},
-many others are less
-severe in reality. Therefore, we need a proper quantification metric to
-assess the sensitivity of side-channel vulnerabilities,
-so a developer can efficiently triage them.
-
-Previous work~\cite{182946,5207642} can identify numerous leakages or even provide an upper bound on the amount of leakage, which is useful to verify that an implementation is secure if it incurs zero leakage.
+Although some vulnerabilities result in the key being entirely compromised~\cite{184415, aumuller2002fault}, many others are less severe in reality.
+Therefore, we need a proper quantification metric to assess the sensitivity of side-channel vulnerabilities, so a developer can efficiently triage them.
+
+Previous work on side-channel quantification~\cite{182946,5207642} can identify numerous leakages or even provide an upper bound on the amount of leakage, which is useful to verify that an implementation is secure if it incurs zero leakage.
 However, these techniques cannot quantify the severity of a leak because they over approximate the leakage. For example, CacheAudit~\cite{182946}

### 2021-04-18 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 Side channels are ubiquitous in modern computer systems as sensitive information can leak through many mechanisms such as power, electromagnetic radiation, and even sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}.
-It is typically hard to fix side-channel vulnerabilities for real-world software systems.
 Among them, software side-channel attacks, such as cache attacks, memory page attacks, and controlled-channel attacks, are especially problematic as they do not require physical proximity~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}.
@@
 less than ten seconds while finding all the leakages reported by
-DATA. b) Because \detect{} does not run the test program again when wedinghao w
+DATA. b) Because \detect{} does not exexute the test program again when we
 have a new \emph{secret input}, \detect{} can test more input secrets

### 2021-04-18 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
     \centering
-    \begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
+    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
 int mbedtls_internal_aes_encrypt( mbedtls_aes_context *ctx,
@@
     \centering
-    \begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
+    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
 # define mul_add_c2(a,b,c0,c1,c2)                    \
@@
     \centering
-    \begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
+    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
 # define mul_add_c2(a,b,c0,c1,c2)      do { \
@@
     \centering
-    \begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
+    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
 uint8_t password = input();
@@
 We illustrate the quantification method on a password checking example.
-As shown in Figure~\label{fig:chapter4:pwcheck}, the left version is vulnerable to side-channel attacks because of the early return at line 4.
+As shown in Figure~\ref{fig:chapter4:pwcheck}, the left version is vulnerable to side-channel attacks because of the early return at line 4.
 If the first bytes of \textsf{key} and \textsf{pub} are the same, the function will continue running and access the second byte.
 The right version fixes the vulnerability because the function will continue comparing the second byte even if the first byte is different.
-\tool{} identifies the leakage site in the left figure successfully and estimates the amount of leakage site is $16$ bits.
+\tool{} identifies the leakage site in the left figure successfully and estimates the amount of leakage is $16$ bits.
 

### 2021-04-18 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 
-The root cause of most side-channel attacks can been as a result of the combination of the hardware design and the vulnerable software.
+The cause of most side-channel attacks can been as the combination of the hardware design and the vulnerable software.
 Existing countermeasures can be classified into two categories: fixing the software and adopting new hardware.
-Based on the discussion in \S\ref{chapter1} and \S\ref{chapter2}, patching bugs in software is usually easier than adopting new hardware to defend against side-channel attacks.
-In order to eliminate those leakage sites, developers often need to identify potential leakage sites from the code base manually.
+Based on the discussion in \S\ref{chapter1} and \S\ref{chapter2}, fixing side-channel leakage sites in software is usually easier than adopting new hardware to defend against side-channel attacks.
+In order to eliminate those leakage sites, developers need to find potential leakage sites from the large code base manually.
 However, the manual process is tedious and error-prone.
-Recent studies~\cite{203878} also suggest fixing old vulnerabilities can sometimes introduce new leakages.
+Recent work~\cite{203878} also suggests fixing old vulnerabilities can sometimes introduce new leakages.
 
-Recent work has made good progress in identifying side-channel leakages automatically.
+Recent work has made good progress in detecting side-channel leakages automatically.
 Some tools (e.g., CacheD, CaSym) have successfully identified unknown leakage sites from software products automatically.
@@
 First, although some tools can find side-channel leakages in real-world software products, they can only analyze one code fragment at a time due to the expensive performance overhead.
-As a result, users of those tools sometimes need to manually cut off some irrelevant code based on their past experience.
+As a result, users of those tools sometimes need to cut off some irrelevant code based on their experience manually.
 The trimming process is tedious and needs domain knowledge of the target software (e.g., which part of the code is more likely to have side-channel leakage sites).
-More importantly, if many leakages sites are on the trimmed code, those tools will miss those leakage sites as well.
+More importantly, if many leakage sites are on the trimmed code, those tools will miss those leakage sites as well.
 
-Second, many tools perform the analysis at the level of intermediate representations (IR) instead of machine code.
+Second, many tools perform the analysis at the level of intermediate representations (IR) instead of the machine code.
 It is a design decision to facilitate the implementations.
@@
 Compared to recent tools, our tool is 3-100x faster while finding all the leakages when we evaluate on the same benchmarks.
+In addition, our tool finds new side-channel vulnerabilities that are missed by the previous work.
 
@@
 
-CPUs process data in a much faster speed than the main memory (DRAM) can supply.
-Modern CPUs adopt a hierarchy memory to bridge the performance gap between the CPUs and the main memory.
-By storing extra copies of data and code in a smaller but faster memory, the software can get its most recently accessed code and data in a shorter time.
+During the evolution of the modern computer architecture, researchers find that CPUs process data in a much faster speed than the main memory (DRAM) can supply.
+As a result, modern CPUs adopt a hierarchy memory architecture to bridge the performance gap between the CPUs and the main memory.
+By storing extra copies of recently accessed data and code in a smaller but faster memory, the software can get its most recently accessed code and data in a shorter time.
 
-Figure~\ref{fig:memory_hierarchy} shows the overview of the hierarchy memory.
+Figure~\ref{fig:memory_hierarchy} shows the overview of one example of the hierarchy memory architecture.
 For a CPU with multiple cores, each core has two private level-1 (L1) cache, an instruction cache (iCache), and a data cache (dCache).
@@
 The LLC is shared among all the cores.
-The main memory is the bottom-most under the memory hierarchy.
+The main memory is in the bottom-most under the memory hierarchy.
 \begin{figure}

### 2021-04-18 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 The attacker attempts to retrieve sensitive information through address-based
-side-channel attacks. The attacker has no direct access to the target's memory or cache,
-but it can probe its memory or cache at each program point. Here are a few examples.
+side-channel attacks. The attacker has no direct access to the target's memory or cache, but he can probe the memory or cache at each program point. Here are a few examples.
 \begin{enumerate}
   \item A host machine has several Virtual Machines (VMs). The victim runs the application inside one VM. An attacker can control the VM and probe the process running on the other VM.
-  \item  In a shielding system, a malicious operating system can extract sensitive information from the protected application.
-  \item An user level application can probe some sensitive information inside the kernel.
+  \item  In a shielding system, a malicious operating system can extract sensitive information from protected user-level applications.
+  \item A ring-3 application can probe some sensitive information inside the kernel.
 \end{enumerate}
 
-In reality, the
-attacker will face many possible obstacles such as the noisy observations of the memory or cache. However, for this project, we assume
+In reality, attackers will face many possible obstacles, such as the noisy observations of the memory or cache. However, for this project, we assume
 the attacker has noise-free observations as in previous work~\cite{203878,182946,Brotzman19Casym}.
@@
 \section{Limitations of Current Side-channel Leakage Detection Tools}
-In this section, we introduces two limitations of current side-channel leakage detection method.
-The first limitation is that some tools may have some false positives or false negatives.
-The second limitation is the current tools are not fast enough to analyze real world side-channel leakages.
+In this section, we introduces two limitations of current side-channel leakage detection tools.
+The first limitation is that some tools have some false positives or false negatives.
+The second limitation is current tools are not fast enough to analyze real world side-channel leakages.
 
@@
 In this dissertation, we study two types of side-channel leakage code patterns.
-The key intuition is that the target application shows different control flows or data flows when it processes different sensitive input data.
+The intuition is that the target application shows different control flows or data flows when it processes different sensitive input data.
 We refer them as secret-dependent control flow transfers and secret-dependent data accesses.
-Unlike previous work, our tool works on the machine code, which can provide us more prevision than the previous tools.
+Unlike previous work, our tool works on the machine code, which is more precise
+than previous tools.
 \subsubsection{Control Flow}
@@
   \begin{minipage}{0.45\linewidth}
-    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
+    \begin{lstlisting}[xleftmargin=.15\textwidth, xrightmargin=.0\textwidth, frame=none]
 int example1(uint8_t k, uint32_t m) { // m = 0
@@
   \begin{minipage}{0.45\linewidth}
-    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
+    \begin{lstlisting}[xleftmargin=.15\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
 push  ebp
@@
   \begin{minipage}{0.45\linewidth}
-    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
+    \begin{lstlisting}[xleftmargin=.15\textwidth, xrightmargin=.0\textwidth, frame=none]
 int example2(uint16_t k) {
@@
   \begin{minipage}{0.45\linewidth}
-    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
+    \begin{lstlisting}[xleftmargin=.15\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
 xor   eax, eax
@@
   \begin{minipage}{0.4\linewidth}
-    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
+    \begin{lstlisting}[xleftmargin=.15\textwidth, xrightmargin=.0\textwidth, frame=none]
 uint8_t T[128];
@@
   \begin{minipage}{0.4\linewidth}
-    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
+    \begin{lstlisting}[xleftmargin=.15\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
 ...
@@
   \begin{minipage}{0.4\linewidth}
-    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
+    \begin{lstlisting}[xleftmargin=.15\textwidth, xrightmargin=.0\textwidth, frame=none]
 uint8_t T[32];

### 2021-04-18 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \section{Limitations of Current Side-channel Leakage Detection Tools}
-In this section, we introduces two limitations of current side-channel leakage detection tools.
+In this section, we introduce two limitations of current side-channel leakage detection tools.
 The first limitation is that some tools have some false positives or false negatives.
-The second limitation is current tools are not fast enough to analyze real world side-channel leakages.
+The second limitation is current tools are not fast enough to analyze side-channel leakages in real-world software.
 
@@
 The intuition is that the target application shows different control flows or data flows when it processes different sensitive input data.
-We refer them as secret-dependent control flow transfers and secret-dependent data accesses.
-Unlike previous work, our tool works on the machine code, which is more precise
-than previous tools.
+We refer them as \textit{secret-dependent control flow transfers} and \textit{secret-dependent data accesses}.
+Unlike previous work, our tool works on the machine code, which is more precise than previous tools.
 \subsubsection{Control Flow}

### 2021-04-19 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 However, eliminating side-channel vulnerabilities from real-world software code base is not easy.
-First, some vulnerable implementations actually perform better.
-For example, RSA implementations usually adopt the CRT optimization, which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}.
-Fixing vulnerabilities can introduce new weaknesses.
-We are in a dilemma between the performance and the security.
-Second, it is hard to detect side-channel leakages in reality.
+First, side-channels are a low-level problem in computer systems.
+As a non-functional property, it can be difficult for programmers to reason about or test.
 While recent work~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} can detect many side-channel vulnerabilities, they either suffer from expensive computation costs or high false positives and false negatives.
-For example, recent tools like DATA~\cite{217537} reports 2,248 potential leakage sites for the RSA implementation in OpenSSL 1.1.0f\@.
-Further analysis shows 1,510 leaks can be dismissed.
-But that leaves 460 data-access leaks and 278 control-flow leaks.
 Many of these vulnerabilities have not been fixed by developers for a variety of reasons.
-Third, most vulnerabilities pose a negligible risk.
+Second, most vulnerabilities pose a negligible risk.
 Although some vulnerabilities result in the key being compromised~\cite{184415, aumuller2002fault} entirely, many others are less severe in reality.
 Therefore, we need a proper quantification metric to assess the sensitivity of side-channel vulnerabilities, so a developer can efficiently triage them.
+Third, many side-channel vulnerable implementations (e.g., the CRT optimization and lookup tables) have better performance.
+It is a dilemma between the performance and the security.
 

### 2021-04-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 The main memory is in the bottom-most under the memory hierarchy.
-\begin{figure}
+\begin{figure}[ht]
   \centering
@@
 It is possible that different units in the main memory share the same address in the cache.
-\begin{figure}
+\begin{figure}[ht]
   \centering
@@
 We refer them as \textit{secret-dependent control flow transfers} and \textit{secret-dependent data accesses}.
-Unlike previous work, our tool works on the machine code, which is more precise than previous tools.
+Unlike previous work, our tool works on the machine code, which is more precise than previous tools that work on the source code or the intermediate representation.
 \subsubsection{Control Flow}
-\begin{figure}[h]
+\begin{figure}[ht]
   \begin{minipage}{0.45\linewidth}
@@
   \end{minipage}\caption*{(b) A False Positive}
-  \caption{Secret-dependent Control-flow Transfers}\label{fig:chapter3:cf}
+  \caption{Secret-dependent control-flow transfers}\label{fig:chapter3:cf}
 \end{figure}
@@
 Figure~\ref{fig:chapter3:cf}(a) shows such an example.
-The function takes a public value \textsf{m} and a secret \textsf{k} as the input values.
+The function takes a public value \textsf{m} and a secret \textsf{k} as the inputs.
 The code at line 2 ensures that the lower 7 bits of the value \textsf{k} do not affect the value \textsf{b}.
 However, depending on the value of \text{m}, the code snippet in Figure~\ref{fig:chapter3:cf}(a) may have a leakage site.
-If the eighth bit of \textsf{m} is 1, then an attacker can also infer the eighth bit of \textsf{k} by observing the branch at line 4 or line 6.
+If the eighth bit of \textsf{m} is 1, then an attacker can infer the eighth bit of \textsf{k} by observing the branch at line 4 or line 6.
 The right figure shows the corresponding machine code.
@@
 
+However, the if-else branch does not always indicate there is a potential leakage site.
 Figure~\ref{fig:chapter3:cf}(b) shows a different situation.
@@
 \subsubsection{Data Flow}
-\begin{figure}[h]
+\begin{figure}[ht]
   \begin{minipage}{0.4\linewidth}
@@
   \end{minipage}\caption*{(b) A False Positive}
-  \caption{Secret-dependent Data Accesses}\label{fig:chapter3:da}
+  \caption{Secret-dependent data accesses}\label{fig:chapter3:da}
 \end{figure}
@@
 \subsection{Performance}
-The second limitation of the current side-channel detection tool is the performance bottleneck, especially for those tools based on the symbolic analysis.
+The second limitation of current side-channel detection tools is the performance bottleneck, especially for those tools based on the symbolic analysis.
 For example, CaSym can only analyze small programs.
-CacheD perfroms better.
+CacheD performs better than CaSym.
 However, it still can not handle large programs like RSA directly.
@@
 Symbolic execution can be used to explore all the possible paths, which is useful for many tasks.
-But it is significantly less likely for cache side channels bugs in crypto primitives.
+Nevertheless, it is significantly less likely for cache side channel bugs in crypto primitives.
 Cryptography primitives are more likely to have an even coverage of different paths (based on pseudo-random cipher states), and a branch-based side channel is vulnerable from the very first branch on secret data, making complex path conditions less often relevant.
@@
 But the decision problems that an SMT solver handles are typically at least NP-hard.
-On the other hand, we can use some methods to avoid the solver and find side-channel leakages in a more efficient way.
+On the other hand, we can use some methods to avoid the solver and find side-channel leakages more efficiently.
 
 \section{Method}\label{chapter3:method}
-\begin{figure}
+\begin{figure}[ht]
   \centering
@@
 In a real execution, an adversary may have
-some observations ($O$) of the program. Examples of those observations include the
-timing, CPU usages, and electromagnetic signals (EM). In this dissertation, we
-use secret-dependent control flows and secret-dependent data
+some observations ($O$) of the program.
+Examples of those observations include the timing, CPU usages, and electromagnetic signals (EM).
+In this dissertation, we use secret-dependent control flows and secret-dependent data
 accesses as observations.
@@
 and $m$. The attacker wants to infer the value of $k$. Moreover, we assume
-an attacker can change the public input ($m \in M$) while keeping the secret input $k$.
-The threat model is similar to a chosen-plaintext attack.
+an attacker can change the public input ($m \in M$) while keeping the secret input $k$. The threat model is similar to a chosen-plaintext attack.
 We now discuss how to model observations ($O$),
@@
 \emph{secret-dependent control transfers} and \emph{secret-dependent data
-  accesses}. In other words, an adversary has observations based on control-flows
-and data accesses.
+  accesses}.
 
@@
 We define a branch to be secret-dependent if:
-$$\exists k_{i1}, k_{i2} \in K, m \in M, \,f_i(\beta, k_{i1}, m) \neq f_i(\beta, k_{i2}, m)$$
+$$\exists k_{i1}, k_{i2} \in K, m \in M, \,f_i(\beta, k_{i1}, m) \neq f_i(\beta, k_{i2}, m) \land PC$$
 
-An adversary can observe which branch the code executes if the branch condition
+$PC$ represents the path condition. An adversary can observe which branch the code executes if the branch condition
 equals $t_b$. We use the constraint $c_i : f_i(\beta, k, m) = t_b$ to model
@@
 above definition, $m$ is also a variable. So it is possible for some $m \in M$,
-we can not find a pair of two different $k_{i1}$ and $k_{i2}$ to satisfy the above
-inequation. For example, in the example from Figure~\ref{fig:chapter3:cf}, if $m = 0$,
-the code will always execute the branch 2. However, the function \textsf{example1} still
-has a secret-dependent control-flow for some $m$, so we think the code has
-some side-channel leakages.
+we can not find a pair of two different $k_{i1}$ and $k_{i2}$ to satisfy the above inequation.
+For example, in Figure~\ref{fig:chapter3:cf}, if $m = 0$, the function \textsf{example1} will always execute the branch 2.
+However, if $m = \mathtt{0xffffffff}$ and $k = 0$, the function \textsf{example1} executes the branch 1 and the function \textsf{example1} executes the branch 2 when $k = \mathtt{0xf000000}$.
 
@@
 Similar to secret-dependent control-flow transfers, a data access operation is
-secret-dependent if different input sensitive keys ($K$) cause access to different
-memory addresses. We use the model from CacheD~\cite{203878}. The low $L$ bits
-of the address are generally unimportant in side-channels.
+secret-dependent if different input sensitive keys ($K$) cause access to different memory addresses.
+We use the model from CacheD~\cite{203878}.
+The low $L$ bits of the address are generally unimportant in side-channels.
 
@@
 
-$$\exists k_{i1}, k_{i2} \in K, m \in M,\,f_i(\beta, k_{i1}, m) >> L \neq f_i(\beta, k_{i2}, m) >> L$$
+$$\exists k_{i1}, k_{i2} \in K, m \in M,\,f_i(\beta, k_{i1}, m) >> L \neq f_i(\beta, k_{i2}, m) >> L \land PC$$
 
@@
 
-\begin{table}%[ht]
+\begin{table}[ht]
   \centering\small\footnotesize
@@
 test with different input combination with 100 times, we have $1 -
-  (1-0.05)^{100} = 99.6\%$ chance find such $k_1, k_2$. This type of random algorithm
-works well for our problem.
+  (1-0.05)^{100} = 99.6\%$ chance find such $k_1, k_2$. This type of random algorithm works well for our problem.
 
@@
 The formula is made up of concrete values and the input key as the symbols accumulated through the symbolic execution.
+We implement several rules to simplify the formulas.
 For each formula, the tool will check weather it can be reduced into a concrete values (e.g., $k_1+12-k_1 = 12$ ).
@@
 
-\begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
+\begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth, frame=none][ht]
 ...
@@
 
-At the beginning of the instruction segment, the value at the address of local\_14h can be written as $F(\vec{K})$.
-At the address $e785$, the value will be updated with $F(\vec{K})+1$.
-Then the code compares
-the value with 4 and use the result as a conditional jump. Based on the result, we can have the following formula:
+At the address $\mathtt{0x0000e781}$, the value at the address of $\mathtt{local\_14h}$ can be written as $F(\vec{K})$.
+At the address $\mathtt{0x0000e785}$, the value will be updated with $F(\vec{K})+1$.
+Then the code compares the value with $4$ and use the result as a conditional jump.
+Based on the result, we can have the following formula:
 
@@
 
-The formula, together with the memory address ($0xe789$) is store as a \textit{formula tuple (address, formula)}. Each formula tuple represents one leakage site.
+The formula, together with the memory address ($\mathtt{0x0000e789}$) is stored as a \textit{formula tuple (address, formula)}. Each formula tuple represents one potential leakage site.
 
@@
 from the input sensitive information and will not leak any sensitive information according to our threat model. Otherwise, we will generate the constraint for
-the memory addressing. We model the memory address with a symbolic formula $F(\vec{K})$. Because we also have the concrete value of the memory address $Addr1$.
+the memory addressing.
+We model the memory address with a symbolic formula $F(\vec{K})$.
+Because we also have the concrete value of the memory address $\mathtt{Addr1}$.
 Inspired by the work from~\cite{203878}, the formula can be written as:
 
-$$F(\vec{K}) >> L = Addr1 >> L$$
+$$F(\vec{K}) >> L = \mathtt{Addr1} >> L$$
 
@@
 The step can be seen as the multiple-tag taint analysis. With the help of the information from symbolic execution, we can implement a relatively simple but relatively precise information flow track.
-At the beginning of the analysis, \detect{} keep a track for each byte in
+At the beginning of the analysis, \detect{} keep track for each byte in
 the original buffer.
@@
 \subsection{Evaluation Result Overview}
-\begin{table*}[]
+\begin{table*}
   \centering\small\footnotesize
@@
 0.9.7, \detect{} is over 100x faster than CacheD.
-\begin{table*}[]
+\begin{table*}[ht]
  \centering
@@
       \multicolumn{1}{l|}{} & \multicolumn{3}{c|}{CacheD} & \multicolumn{3}{c}{Abacus}                                             \\
-      Name                  & Time (s)                    & \# Instructions            & DF & Time (s) & \# Instructions & CF+DF   \\ \hline
+      Benchmark                  & Time (s)                    & \# Instructions            & DF & Time (s) & \# Instructions & CF+DF   \\ \hline
       AES OpenSSL 0.9.7         & 43.4                        & 791                        & 48 & 0.23     & 1,704           & 0+75    \\
@@
 c) DATA tries to use leakage models (domain knowledge) to classify each leakage.
-The strength of Abacus is that it does not need such domain knowledge.
+The strength of \ctool{} is that it does not need such domain knowledge.
 DATA reports 278 control-flow and 460 memory-access leaks for the RSA implementation in OpenSSL 1.1.0f. Among those leakages, they find one new vulnerability in RSA after some manual analysis.
 \detect{} finds the vulnerability.  For each leakage site, \detect{} can provide
-concrete examples to trigger the issue and give an estimation to
-assess the severity level of the vulnerability.
-
+concrete examples to trigger the issue.
 \subsection{Case Studies}
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \centering

### 2021-04-19 SupplementaryMaterial/Vita.tex
Updates from Overleaf

@@
 
-Qinkun Bao is a fifth year Ph.D. student at the College of information Sciences
+Qinkun Bao is a fifth-year Ph.D. student at the College of Information Sciences
 and Technology, The Pennsylvania State University. He is a member of the Software 
-System Security Research Lab where he works under the supervision of Dr. Dinghao Wu.
-His research interests span reverse engineering, binary analysis, and trusted computations.
-Before he went to Penn State, he received his bachelor degree in Electronic Engineering and Information Science from University of Science and Technology of China.
+System Security Research Lab, where he works under the supervision of Dr. Dinghao Wu.
+His research interests span reverse engineering, binary analysis, and trusted computing.
+Before he went to Penn State, he received his bachelor's degree in Electronic Engineering and Information Science from University of Science and Technology of China.

### 2021-04-19 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 We evaluate \ctool{} on TinyDNN, a deep learning framework in C++.
-We construct a LeNet-5 like model~\cite{lecun1998gradient} and trained it with the MINIST dataset.
+We construct a LeNet-5 model~\cite{lecun1998gradient} and trained it with the MINIST dataset.
+LeNet-5 network has six layers, including three convolutional layers, one fully connected layers and two pooling layers.
 The batch size in our experiment is 10 and the numbers of epochs is 30.
@@
 The inference dataset consists of $10000$ images.
-During the inference, we also record the page access information.
+During the inference, we record the memory access information.
 The evaluation shows that  leakage primarily comes from the activation function and the image convert function.

### 2021-04-19 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 According to \tool{}\cite{bao2021abacus}, the mark ``$*$'' means timeout, which indicates more severe leakages.
-}\label{chapter5:tab:RSAOpenSSL1.1.0}
+$0.0$ means very small amount of leakage, but not exactly zero.}\label{chapter5:tab:RSAOpenSSL1.1.0}
 %\resizebox{\columnwidth}{!}{
@@
 bn\_exp.c& BN\_mod\_exp\_mont\_consttime& (1.0, 1.0) & 1.0 & \xmark\\
-bn\_mont.c& BN\_from\_montgomery\_word& (*, *, *, *, *, *, 0.0)& 9.7 &\cmark\\
+bn\_mont.c& BN\_from\_montgomery\_word\tnote{2}& (*, *, *, *, *, *, 0.0)& 9.7 &\cmark\\
+bn\_mont.c& BN\_from\_montgomery\_word& 0.0& 0.1 &\xmark\\
+
 bn\_asm.c& bn\_sqr\_comba8&9.3&5.0& \cmark\\
@@
     \scriptsize
-    \item[1] The leakage site at line 144 (OpenSSL 1.1.1) are not fixed.
+    \item[1] The leakage site at line 144 (OpenSSL 1.1.1) are not fixed.\\
+    \item[2] We break the function into two parts during the analysis.
+
 \end{tablenotes}
@@
 During the inference, we record the memory access information.
-The evaluation shows that  leakage primarily comes from the activation function and the image convert function.
+The evaluation shows all three types of layers have different memory accesses under different inputs.
+In addition, we find that the leakages primarily comes from the activation function and the image convert function.
 
@@
 
-This paper presents an approach that tries to give the conservative estimate of the amount of leaked information by address-based side-channel attacks.
+This chapter presents an approach that can give the conservative estimate of the amount of leaked information by address-based side-channel attacks.
 Those attacks exploit the data-flow from secrets to load address and the data-flow from the data-flow from secrets to branch conditions to retrieve secrets based on the observation on the memory accesses.
 Despite those kinds of side-channel leakages have been discovered for decades, the up-to-date software still has some side channel leakages.
-For some of those vulnerabilities, developers don't fix them because they think those side-channel vulnerabilities are not important.
+For some of those vulnerabilities, developers do not fix them because they think those side-channel vulnerabilities are not important.
 To show the importance of those side-channel leakages, one way is to demonstrate an end-to-end attack based on the vulnerability.

### 2021-04-19 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-RSA implementations blinding the data on a random value before operating on it.
+RSA implementations are blinding the data on a random value before operating on it.
 We use a fixed RSA blinding value to avoid non-deterministic behaviors during the execution.
@@
 So it is possible that one function has several leakage sites.
-Suppose the function has two leakages sites and they leak $a$ and $b$ bits respectively.
+Suppose the function has two leakages sites, and they leak $a$ and $b$ bits, respectively.
 We use the set $(a, b)$ to represent the result of \tool{}.

### 2021-04-19 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 On the positive side, we expect there are plenty of leakage sites inside the kernel.
-The dissertation provide the approaches to pick up ``severe'' leakages automatically.
+The dissertation provides the approaches to pick up ``severe'' leakages automatically.
 
 \textbf{Compiler-assisted Side-channel Vulnerability Analysis and Mitigation.}
-We propose to mitigate the side-channel leakages in a compiler backend.
+We propose to mitigate the side-channel leakages from a compiler backend.
 For example, the conditional execution can be eliminated by using the masks.
@@
 The performance impact from the aggressive mitigation.
-For example, GNU toolchains inset LFENCE before any possible vulnerable instructions, which include all load instructions, all indirect branches, and return instructions.
+For example, GNU toolchains inset LFENCE before any possible vulnerable instructions, including all load instructions, all indirect branches, and return instructions.
 We plan only to change those points that are more likely to leak sensitive information.

### 2021-04-19 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 \IncMargin{1em}
-\begin{algorithm}[h]\small
+\begin{algorithm}[th]\small
     \DontPrintSemicolon
@@
 
-\begin{figure}[t]
+\begin{figure}[ht]
     \centering
@@
 
-\begin{table}[h!]
+\begin{table}[ht]
     \centering
@@
 \subsection{Benchmarks}\label{sec:eval_countermeasures}
-\subsubsection{Bit-slicing}
+\subsubsection*{Bit-slicing}
 Bit-slicing is an efficient method to construct constant-time implementation for side channel to mitigation.
@@
       \end{lstlisting}
-    \caption{SBOX without BitSlicing}
+    \caption{SBOX without bitslicing}
     \label{fig:SBOX_da}
@@
 \end{lstlisting}
-\caption{SBOX with BitSlicing}
+\caption{SBOX with bitslicing}
 \label{fig:SBOX_bitslicing}
@@
 
-\subsubsection{Lookup Table}
+\subsubsection*{Lookup Table}
 \begin{figure}
@@
 \end{lstlisting}
-  \caption{Lookup Tables with Small Entries.}\label{fig:chapter4:small_lookup}
+  \caption{Lookup tables with small entries.}\label{fig:chapter4:small_lookup}
 \end{figure}
@@
 \end{lstlisting}
-  \caption{Lookup Tables with Big Entries.}\label{fig:chapter4:big_lookup}
+  \caption{Lookup tables with big entries.}\label{fig:chapter4:big_lookup}
 \end{figure}
@@
 
-\subsubsection{Password Checker}
+\subsubsection*{Password Checker}
 \begin{figure}

### 2021-04-19 SupplementaryMaterial/Abstract.tex
Updates from Overleaf

@@
 %\vspace{-0.3in}
-Side-channel attacks can leak secret information unconsciously from non-functional characteristics, e.g., time, power, and memory usage.
+Side-channel vulnerabilities can leak secret information unconsciously through non-functional characteristics, e.g., time, power, and memory usage.
 Like many other software vulnerabilities, attackers exploit flaws in designs of hardware and implementations of software.
 Hardware countermeasures, which usually need changes to the complex underlying hardware, are hard to adopt in practice.
-On the contrary, software approaches are usually easy to implement.
+On the contrary, software approaches are generally easy to implement.
 This dissertation studies various aspects of side-channel vulnerabilities.
@@
 We examine the bottleneck of current symbolic approaches and propose methods to identify side-channel vulnerabilities in real-world cryptography applications.
-We implement the approach in a tool and apply it on popular cryptography libraries.
+We implement the approach in a tool and apply it to popular cryptography libraries.
 The evaluation results confirm that the tool is much faster than the state of art tools while identifying all the known leakages reported by previous tools.
@@
 
-Second, while current side-channel detection work is able to identify numerous potential vulnerabilities.
+Second, while current side-channel detection tools are able to identify numerous potential vulnerabilities.
 However, in practice, many such vulnerabilities leak a negligible amount of sensitive information, and thus developers are often reluctant to address them.
@@
 Contrary to previous side-channel detection tools, our approach can identify those severe side-channel leakages without false positives.
-Moreover, by applying the chi-squared test, our tools can estimate the total effect of multiple leakage sites as well.
+Moreover, by applying the chi-squared test, our tool can estimate the total effect of multiple leakage sites as well.
 \ctool{} consists of three steps.
-First, the target program is running with a number of the sensitive inputs to record the memory access under different inputs.
+First, the target program is executed with a number of different sensitive inputs to record memory accesses.
 Second, the long address traces are split into several segments based on the location in the source code.
@@
 Based on the channel capacity between the original secrets and the observation of the attacker, we quantify the information leakages for each leakage site.
-We evaluate MME with OpenSSL, mbedTLS, TinyDNN and GTK.
-Our evaluation results show MME is effective in identifying and quantifying side-channel leakages.
+We evaluate \ctool{} with OpenSSL, mbedTLS, TinyDNN and GTK.
+Our evaluation results show \ctool{} is effective in identifying and quantifying side-channel leakages.

### 2021-04-19 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 A side-channel attack is any attack that allows adversaries to infer sensitive information based on ``side-channel'' information.
-In 1996, Kocher published the first side-channel attack in the literature.
+In 1996, Kocher published the first side-channel attack in the literature~\cite{kocher1996timing}.
 He demonstrated that an attacker could break cryptosystems like RSA or Diffie-Hellman by measuring the execution time of a simple modular exponentiation operation.
@@
 One example is cache channel attacks.
-The cache is a smaller but faster memory designed to bridge the gap of the access time between the main memory and CPU registers by storing the copy of recently accessed data.
-Some software accesses different memory addresses when it processes different input data.
-Because the size of the cache is significantly smaller than the size of the main memory, the CPU can only find part of the data in the cache.
+The CPU cache is a smaller but faster memory designed to bridge the gap of the access time between the main memory and CPU registers by storing copies of recently accessed data.
+Because software may access different memory addresses when it processes different input data, and the size of the cache is significantly smaller than the size of the main memory, the CPU can only find part of the data in the cache.
 Such differences can be reflected in the differences between the program execution time.
@@
 Based on the above discussion, existing countermeasures can be further divided into two categories, the hardware-based method and the software-based method.
-Hardware-level solutions, such as reducing shared resources, adopting oblivious RAM, and using transnational memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need to adopt new hardware features and apply changes to today's modern complex computer systems, which are hard to adopt in reality.
+Hardware-level solutions, such as reducing shared resources, adopting oblivious RAM, and using transnational memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need to adopt new hardware features and make changes to today's modern complex computer systems, which are hard to adopt in reality.
 Therefore, a promising and universal direction is software countermeasures, detecting and eliminating side channel vulnerabilities (data flow from secrets to load addresses, and data flow from secrets to branch conditions) from existing code base.
-For example, when we examine those side-channel attacks, many of them exploit two kinds of code patterns: \emph{secret-dependent control-flow transfers} and \emph{secret-dependent data accesses}.
+For example, when we examine recent side-channel attacks, many of them exploit two kinds of code patterns: \emph{secret-dependent control-flow transfers} and \emph{secret-dependent data accesses}.
 \begin{figure}[h]
@@
 The key intuition is that the above side-channel attacks happen when a program accesses different memory addresses if the program has different sensitive inputs.
-As shown in Figure~\ref{fig:secret:cf} and Figure~\ref{fig:secret:da}, if a program shows different patterns in control transfers or data accesses when the program processes different sensitive inputs, the program could have side channels vulnerabilities.
+As shown in Figure~\ref{fig:secret:cf} and Figure~\ref{fig:secret:da}, if a program shows different patterns in control transfers or data accesses when the program processes different sensitive inputs, the program could have side-channel vulnerabilities.
 Various techniques can be used to exploit the above leakage site at different granularities.
-For example, cache channels can observe cache accesses at the level of cache sets~\cite{liu2015last}, cache lines~\cite{184415} or other granularities.
-Other kinds of side-channels like controlled-channel attack~\cite{7163052}, can observe the memory access at the level of memory pages.
+For example, cache channels can observe cache accesses at the level of cache sets~\cite{liu2015last}, cache lines~\cite{184415} or other granularities~\cite{yarom2017cachebleed}.
+Other types of side-channel attacks like controlled-channel attack~\cite{7163052}, can observe the memory access at the level of memory pages.
 So a natural defense approach is to remove the above code patterns in the software.
@@
 While recent work~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} can detect many side-channel vulnerabilities, they either suffer from expensive computation costs or high false positives and false negatives.
-Many of these vulnerabilities have not been fixed by developers for a variety of reasons.
+Many of those reported vulnerabilities have not been fixed by developers for a variety of reasons.
 Second, most vulnerabilities pose a negligible risk.
@@
 Different from previous trace comparison based methods, our method has fewer false positives and false negatives.
-Compared with methods based on symbolic execution and abstract interpretation, our methods can work on real-world cryptography libraries.
+Compared with methods based on symbolic execution and abstract interpretation, our methods can apply on real-world cryptography libraries directly.
 Symbolic execution provides fine-grained information, but it is expensive to compute.
@@
 We examine the bottleneck of the trace-oriented symbolic execution and optimize it to work on real-world applications.
-    \item \textbf{Quantification.} We propose methods to quantify the amount of information leakage precisely that an attacker can retrieve during the side-channel attacks.
-We define the amount of leaked information as the cardinality of possible secrets based on an attacker's observation.
+    \item \textbf{Quantification.} We propose methods to quantify the amount of information leakage precisely that an attacker can retrieve during side-channel attacks.
+For the first project, we define the amount of leaked information as the cardinality of possible secrets based on an attacker's observation.
+For the second project, we we quantify the amount of leaked information based on channel capacity.
 Before an attack, an adversary has a large but finite input space.
@@
 \begin{itemize}
-    \item We designs a symbolic analysis method that can detect secret-dependent control-flow transfers and secret-dependent data access.
+    \item We designs a symbolic analysis method that can detect secret-dependent control-flow transfers and secret-dependent data accesses.
 The key idea is to only symbolically execute those machine instructions that are relevant to vulnerabilities while executing other instructions natively.
@@
 The evaluation results shows that \detect{} is 3 to 100 times faster than existing tools while identifying all vulnerabilities when we run it on the same library.
-We do not need to apply domain knowledge to only part of the original program, which simplify the analysis.
+We do not need to apply domain knowledge to analyze part of the original program, which simplify the analysis.
 In addition, \detect{} yields new leakages which are not identified by previous tools.
@@
 By running the chi-squared test, the method can find independent leakages.
-Attacker can combine multiple leakage sites to retrieve more information as well.
+Attackers can combine multiple leakage sites to retrieve more information as well.
     \item We analyze the amount of information leakage from side-channel vulnerabilities based on the channel capacity.
@@
 The theory can serve as the foundation of the future work on quantify the information leakage based on the fuzzing.
-    \item We implement the above method in a tool called \ctool{} and evaluate the tool with several benchmarks and several real-world applications such as OpenSSL, mbedTLS, Libgcrpyt, TinyDNN, and GTK.
+    \item We implement the above method in a tool called \ctool{} and evaluate the tool with several benchmarks and real-world applications such as OpenSSL, mbedTLS, Libgcrpyt, TinyDNN, and GTK.
 The results show that our tool can detect and quantify the side-channel leakages effectively.
@@
 The rest of the dissertation is organized as follows.
-We present background and related work of the dissertation in Chapter~\ref{chapter2}.
+We present the related work of the dissertation in Chapter~\ref{chapter2}.
 Chapter~\ref{chapter3} presents a novel method to detect side-channel vulnerabilities in binary executables.

### 2021-04-19 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 \chapter{Related Work}\label{chapter2}
-This dissertation studies the address-based side-channel attacks.
+This dissertation studies address-based side-channel attacks.
 We review the related work in this chapter.
-The related work covers the following aspects: side-channel attacks, detections, mitigation, and information quantification.
+The related work covers the following aspects: side-channel attacks, detections, mitigation, information quantification, and current binary analysis tools.
 
@@
 In modern computer ssytems, an attacker may shares some hardware resources (e.g., Cache, TLB, and DRAM) with the victim~\cite{ge2018survey,szefer2019survey}.
-As a result, the attacker can probe the shared hardware resource to infer the memory accesses of the victim.
-While the root cause of the attack is the same, there are various approaches and an attacker can exploit the vulnerability to retrieve the information at different granularities.
+An attacker can probe the shared hardware resource to infer the memory accesses of the victim.
+While the root cause of the attack is the same, there are many approaches, and an attacker can exploit the vulnerability in different methods to retrieve the information at different granularities.
 
@@
 
-Table~\ref{table:side_channel_attack} shows some representations of the recent side-channel attacks.
+Table~\ref{table:side_channel_attack} shows some representations of recent side-channel attacks.
 For a detailed overview of recent side-channel attacks, we refer to the following survey paper~\cite{ge2018survey}.
@@
 Controlled-channel attacks~\cite{moghimi2020copycat, xu2015controlled} belong to the category, where a malicious operating system can interrupt the victim applications and probe the program at any time.
-
+In general, the trace-based attack has the strongest assumption  but it can retrieve the most information among the three types of attacks.
 \subsection{Target Applications}
@@
 \subsubsection*{Media and Graphic Libraries}
-A few of recent work also studies the side-channel attacks in media and graphic libraries.
-Gruss el at.
-shows an attack that can infer keystrokes by exploiting secret-dependent memory accesses in the GDK library.
+Recent work also studies the side-channel attacks in media and graphic libraries.
+Gruss el at.~\cite{191010} shows an attack that can infer keystrokes by exploiting secret-dependent memory accesses in the GDK library.
 In the controlled-channel attack~\cite{xu2015controlled}, Yuanzhong et al.

### 2021-04-19 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 It is a primary threat for the trusted execution environments (TEEs).
-A privileged adversary (e.g., Kernel) can infer the sensitive information by manipulating the enclave page access.
-A malicious OS can proactively revoke a virtual enclave memory page from the memory.
+A privileged adversary (e.g., kernel) can infer the sensitive information by manipulating the enclave page accesses.
+A malicious OS can proactively revoke a virtual enclave memory page from the virtual memory.
 If the victim enclave program accesses the memory table, then the OS can observe the page faults and  know which page is accessed.

### 2021-04-19 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 \subsection{Attack Models}
-Previous work~\cite{182946} classifies the address-based side-channel attacks into three type based on the type of information that an attacker can learn during the attack.
+Previous work~\cite{182946} classifies side-channel attacks into three type based on the type of information that an attacker can learn during the attack.
 \subsubsection*{Timing-based Attacks}
-In timing-based attacks, an adversary can monitor the execution time of a victim.
+In timing-based attacks, an adversary can monitor the execution time of a victim program.
 It could be the overall execution time or the execution time of some interesting points (e.g.
 a function).
-The execution time is correlated to some events (e.g., cache hits, cache misses, page faults, the number of instructions) during the execution.
+The execution time is correlated to some events (e.g., cache hits and misses, page faults, the number of instructions).
 Examples of those attacks include remote timing attacks~\cite{brumley2005remote}, Bernstein's attack on AES~\cite{bernstein2005cache}, and Kocher’s original attack~\cite{kocher1996timing} from CRYPTO 96.
@@
 For example, a cache-based channel attack can know which memory access incurs a cache hit and which memory access incurs a cache miss.
-Since the attacker can probe the victim program after the execution, the attacker do not know the order of accesses.
+Since the attacker can probe the victim program after the execution, the attacker do not know the order of memory accesses.
 Access-based attacks often happen in the cloud computing environment when the attacker and victim share the same hardware (e.g., LLC Cache).
@@
 Suppose the victim program has two functions \textsf{a} and \textsf{b}.
-In an access-based attacks, the attacker can learn both \textsf{a} and \textsf{b} are executed.
+In an access-based attacks, the attacker can only learn both \textsf{a} and \textsf{b} are executed.
 In a trace-based attacks, the attacker can know the execution sequence of two functions (e.g., $aabbb$).
 Controlled-channel attacks~\cite{moghimi2020copycat, xu2015controlled} belong to the category, where a malicious operating system can interrupt the victim applications and probe the program at any time.
-In general, the trace-based attack has the strongest assumption  but it can retrieve the most information among the three types of attacks.
+In general, the trace-based attack has the strongest assumption about the threat model,  but it can retrieve the more information compared to other two types of attacks.
 \subsection{Target Applications}

### 2021-04-19 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 There is a vast number of studies\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last} on side-channel attacks.
-Most early work targets on the encryption key on cryptography libraries.
-In recent years, researchers start to focus on more general target applications.
-In summary, current side-channel target applications can be classified into the below three categories.
+Most early work targets on retrieving encryption key from cryptography libraries.
+In recent years, researchers start to focus on more general and diverse applications.
+In summary,  the target applications of  current side-channel attacks can be classified into the below three categories.
 

### 2021-04-19 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
     \centering
-    \caption{This table shows some common vulnerable points in cryptography implementations and the corresponding protections.}
+    \caption{This table shows some common vulnerable points in cryptography implementations and corresponding software mitigation methods.}
     \label{chapter2:table:crypto}
@@
 Table~\ref{chapter2:table:crypto} summarizes some common vulnerable points in cryptography library implementations.
-Note that Cryptography libraries usually have several implementations for some ciphers.
+Note that cryptography libraries usually have several implementations for some ciphers.
 For example, AES can have more than five different implementations  in OpenSSL.
@@
 In addition to the reference implementation, those libraries also have side-channel mitigated versions.
-However, recent studies also shows those versions (e.g., AES-NI) also have side-channel vulnerabilities caused by compiler optimizations and human mistakes~\cite{217537}.
-The situation is even worse for asymmetric ciphers (e.g., Diffie-Helloman, RSA, ECDSA), because those those ciphers have a lots of big number calculations.
+However, recent studies also show those versions (e.g., AES-NI) also have side-channel vulnerabilities caused by compiler optimizations and human mistakes~\cite{217537}.
+The situation is even worse for asymmetric ciphers (e.g., Diffie-Helloman, RSA, ECDSA).
+Those ciphers have a lots of big number calculations.
 It is hard to implement those calculations completely side-channel resistant.
-Recent work~\cite{arnaud2013timing,yarom2017cachebleed,yarom2014flush+} has demonstrated several end-to-end attacks to recover the private keys of those ciphers.
-There are two common countermeasures to mitigate the side-channel attacks in cryptography libraries.
+Recent work~\cite{arnaud2013timing,yarom2017cachebleed,yarom2014flush+} has demonstrated several end-to-end attacks to recover the private key of those ciphers.
+There are two common countermeasures to mitigate side-channel attacks in cryptography libraries.
 The first approach is to adopt constant time operation when computing the secret data.
@@
 The second approach is to use blinding to reduce the information that can attacker can retrieve.
-However, the binding value can also be retrieved by an attacker through other attacks including side-channel attacks.
+However, the binding value can also be retrieved by an attacker through other methods including side-channel attacks.
 

### 2021-04-19 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 Recent work also studies the side-channel attacks in media and graphic libraries.
-Gruss el at.~\cite{191010} shows an attack that can infer keystrokes by exploiting secret-dependent memory accesses in the GDK library.
+Gruss el at.~\cite{191010} show an attack that can infer keystrokes by exploiting secret-dependent memory accesses in the GDK library.
 In the controlled-channel attack~\cite{xu2015controlled}, Yuanzhong et al.
@@
 Daimeng et al.~\cite{wang2019unveiling} present the cache attack in graphic libraries.
-Their approaches combine a machine learning approach.
-They use the machine learning to pick cache lines that can be exploitable to leak most information.
+Their approaches combine a machine learning approach to pick cache lines that can be exploitable to leak the most information.
 \subsubsection*{Others}
 Some other side-channel targets also include spell checking tools, and font libraries~\cite{xu2015controlled}.
-The attack to font libraries is essentially the same as the attack to the graphic library like GTK.
+The attack to font libraries is essentially the same as the attack to the graphic library like GDK.
 By exploiting the differences of memory accesses when the program renders different characters, an attacker can recover parts of the original sensitive information.
 Other side-channel attacks target on the OS's kernel.
-One example is the to use the side-channel attacks to break the kernel address space randomization (KASLR).
+One example is  using the side-channel attack to break the kernel address space randomization (KASLR).
 Many exploits rely on the knowledge of the memory location of a certain kernel function.
@@
 After that, they detect kernel modules with unique size signatures to break KASLR.
-The second example relies on the side-channel vulnerabilities~\cite{cao2019principled} inside kernels to infer the TCP sequence numbers, which can be used to hijack connections between the client and the server~\cite{cao2016off}.
+The second example relies on the side-channel vulnerabilities~\cite{cao2019principled} inside kernels to infer the TCP sequence numbers, which can be used by a third party to hijack connections between the client and the server~\cite{cao2016off}.
 
@@
 In general, the approach is quite fast.
-On the negative side, comparing the trace along can find the leakage, but it cannot find the complex relationship between the leakage site and the original buffer.
-For example, if two leakage sites leak the same information in the original buffer, those approaches cannot find out the two leakage sites are the same.
+On the negative side, comparing the trace along can find the leakage, but it cannot find the complex relationship between the leakage site and the original secret input.
+For example, if two leakage sites leak the same information, those approaches cannot find out the two leakage sites are the same.
 
 \textbf{Abstraction.} The second category of those tools belongs to the field of abstractions.
-Tools based on those approaches use the abstraction to generate approximations of the semantics of computer programs.
+Tools based on those approaches use the abstraction to generate approximations to model the semantics of computer programs.
 After that, by analyzing the model, those tools can identify side-channel leakages.
@@
 After that, they should have a cache or memory access model and model the side-channel leakage as a math constraint.
-By using SMT solvers to find if two different secret inputs can lead to access to different locations in the memory or the cache, those approaches can determine if the program is vulnerable to side-channel attacks.
+By using SMT solvers to find different secret inputs that lead accesses to different locations in the memory or the cache, those approaches can determine if the program is vulnerable to side-channel attacks.
 Contrary to the trace comparison, the method is quite precise.
@@
 However, side-channel are low-level problems in general.
-Most existing tools are research prototype or are implemented based on the research prototype.
-For some projects, the tool is only implemented to handle the benchmark in their papers properly.
+Most existing tools are research prototypes.
+For some projects, the tools can only handle the benchmarks in their papers properly.
     \item Those tools heavily rely on SMT solvers.
-Despite SMT solvers have made incredible progress in terms of the performance, SMT solving is still the main bottlenecks of the many frameworks.
+Despite SMT solvers have made incredible progress in terms of the performance, SMT solving is still the main bottlenecks of those tools.
 SMT solvers are not good at non-linear arithmetic.
-However, such non-linear arithmetics are quite common in some cryptography algorithms.
+However, such non-linear arithmetics are quite common in cryptography algorithms.
 Recent studies show existing solvers still have plenty of bugs when it deals with real number calculations.
@@
 First, many widely-used libraries (e.g., Intel MKL) do not open the source code.
-Second, some libraries use hand code assembly code to pursue the maximum performance.
-CacheAudit~\cite{182946} uses abstract domains to compute an
+Second, some libraries use hard-coded assembly code to pursue maximum performance.
+Here, we introduce several tools. CacheAudit~\cite{182946} uses abstract domains to compute an
 over approximation of cache-based side-channel information leakage upper bound.
-However, it is difficult to judge the sensitive level of the side-channel leakage based on
-the leakage provided by CacheAudit. CacheS~\cite{236338} improves the approach from
+However, it is difficult to judge the sensitive level of the side-channel leakage based on the leakage provided by CacheAudit.
+Besides, CacheAudit is not scalable enough to analyze ciphers like RSA implementations.
+CacheS~\cite{236338} improves the approach from
 CacheAudit with a new abstract model that only track
@@
 indicate the sensitive level of side-channel vulnerabilities.
-CaSym~\cite{Brotzman19Casym} introduces a static cache-aware symbolic
-reasoning technique to cover multiple paths in a target program. Again, their
-approaches cannot evaluate the sensitive level for each side-channel
-vulnerability, and it only work on small code snippets.
+CaSym~\cite{Brotzman19Casym} introduces a static cache-aware symbolic reasoning technique to cover multiple paths in a target program.
+CaSym can work on two threat models: trace-based attacks and access-based attacks.
+Again, their
+approaches cannot evaluate the sensitive level for each side-channel vulnerability, and it only work on small code snippets.
 
@@
 However, CacheD is not able to detect secret-dependent control-flows.
-We adopted a similar approach to model the secret-dependent data accesses.
+We adopted a similar approach to model the secret-dependent data accesses in the dissertation.
 \tool{} differs from CacheD in that we do not use traditional taint tracking or domain knowledge to cut the trace when identifying secret-dependent data access vulnerabilities.
@@
 Moreover, \tool{} finds secret-dependent control-flows at the same time and gives a precise quantification of the leakage.
-DATA~\cite{217537} detects address-based side-channel vulnerabilities by comparing different execution traces under various test inputs.
+DATA~\cite{217537} detects address-based side-channel vulnerabilities by comparing and aligning different execution traces under various test inputs.
 After collecting execution traces, DATA aligns them and finds the differences.

### 2021-04-20 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 However, both imperfect trace alignment and statistical testing result that DATA can produce false positives.
-MicroWalk~\cite{Wichelmann:2018:MFF:3274694.3274741} uses mutual information (MI) between sensitive input and execution state to detect side-channels.
+MicroWalk~\cite{Wichelmann:2018:MFF:3274694.3274741} adopts a similar approach from DATA by comparing all accessed addresses.
+It uses mutual information (MI) between sensitive input and execution state to quantify the information.
 
@@
 as many paths as possible. Compared to static analysis, trace-based analysis
-is usually more precise as it can use runtime information. It usually has
+is usually more precise as it can incorporate the runtime information. It usually has
 two steps. The first step is collecting trace information. Existing
@@
 there are two kinds of trace-based analysis, online analysis and offline analysis.
-As the name suggests, online analysis is performed at runtime. The target program's
-data can be modified directly in memory, which is useful in fuzzing because the analysis
-can force the program to go through into a specific branch. Contrary to online analysis,
+As the name suggests, online analysis is performed during the program execution.
+The target program's data can be modified directly in memory, which is useful to tasks like fuzzing because the analysis
+can force the program to execute a specific branch. Contrary to online analysis,
 offline analysis or post analysis happens when the program finish executions. 
@@
 
-There are several known binary analysis frameworks that can ease users 
-to launch analysis on binary executable. BitBlaze~\cite{brumley2011bap} is a binary analysis platform
-that provides both the static and dynamic analysis. It uses tracecap plugin to 
-collect execution trace and convert the trace into Vine IR. Binary Analysis Platform (BAP)
+There are several known binary analysis frameworks that can ease users to launch analysis on binary executable.
+BitBlaze~\cite{brumley2011bap} is a binary analysis platform that provides both the static and dynamic analysis.
+It uses the tracecap plugin to  collect execution trace and convert the trace into Vine IR.
+Binary Analysis Platform (BAP)
 is an another binary analysis platform. Similar to BitBlaze, it use a Pintrace tool to
 collect execution trace and convert the trace into BAP IR. Angr~\cite{shoshitaishvili2016state}, the most popular
-binary analysis platform recently, also support trace-based analysis. It first convert
-each instruction into VEX IR and interpret each IR in Python.
+binary analysis platform recently, also support trace-based analysis. It converts each instruction into VEX IR and interprets each IR in Python.
 
-Above existing well-known binary analysis frameworks all adopt the IR layer, which make
-it easy to implement the framework and support multiple architectures. However, it can have
-a very low efficiency and long traces. All IR must be interpreted no matter if symbolic variables
-are involved or not. Besides, as side-channels are low level problems in general, the IR
-design will also lose some information. For example, IR-level branches are not necessarily 
-a super-set or a sub-set of machine-code level branches. Some IR-level branches can be compiled into
-non-branch instructions like conditional moves. Those above limitations motivate us to
-implement a new trace-based binary analysis framework.
+Above existing well-known binary analysis frameworks all adopt the IR layer, which make it easy to implement the analysis and support multiple architectures.
+However, it can have a very low efficiency and long traces.
+All IR must be interpreted no matter if symbolic variables are involved or not.
+Besides, as side-channels are low level problems in general, the IR design will also lose some information.
+For example, IR-level branches are not necessarily  a super-set or a sub-set of machine-code level branches.
+Some IR-level branches can be compiled into non-branch instructions like conditional moves.
+Those above limitations motivate us to implement a new trace-based binary analysis framework.

### 2021-04-20 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 Recent work has made good progress in detecting side-channel leakages automatically.
-Some tools (e.g., CacheD, CaSym) have successfully identified unknown leakage sites from software products automatically.
+Some tools (e.g., CacheD~\cite{203878}, CaSym~\cite{Brotzman19Casym}) have successfully identified unknown leakage sites from software products automatically.
 However, those tools have the following limitations.
 
-First, although some tools can find side-channel leakages in real-world software products, they can only analyze one code fragment at a time due to the expensive performance overhead.
+First, although some tools~\cite{Brotzman19Casym} can find side-channel leakages in real-world software products, they can only analyze one code fragment at a time due to the expensive performance overhead.
 As a result, users of those tools sometimes need to cut off some irrelevant code based on their experience manually.
 The trimming process is tedious and needs domain knowledge of the target software (e.g., which part of the code is more likely to have side-channel leakage sites).
-More importantly, if many leakage sites are on the trimmed code, those tools will miss those leakage sites as well.
+More importantly, if serious leakage sites are on the trimmed code, those tools will miss those leakage sites as well.
 
@@
 In reality, side-channel leakages are a pretty low-level issue and only the low-level analysis can give the most accurate results.
-For example, the IR-level branches is not necessarily a superset or a subset of machine-code level branches.
+For example, the IR-level branches are not necessarily a superset or a subset of machine-code level branches.
 Besides, compiler optimizations can eliminate the IR-level branches like conditional moves and the converse could also happen.
@@
 To overcome the above problems, we propose a fast and precise method to detect the side-channel leakages in real-world software products.
-Different from previous methods, our tool analyzes on the machine code, which can give more precision than traditional IR-based approaches.
 We examine the bottleneck of current symbolic execution approaches and optimize it to work on real-world cryptography systems.
+Different from previous methods, our tool analyzes the machine instructions, which can give more precision than traditional IR-based approaches.
+We evaluate our tool on popular cryptography libraries including OpenSSL, mbedTLS, Libgcrypt, and Monocypher.
 The evaluation results show that our tool can identify previous side-channel leakages, as well as find new leakages.
-Compared to recent tools, our tool is 3-100x faster while finding all the leakages when we evaluate on the same benchmarks.
+Compared with recent tools, our tool is 3-100x faster while finding all the leakages when we evaluate on the same benchmarks.
 In addition, our tool finds new side-channel vulnerabilities that are missed by the previous work.
@@
 
-During the evolution of the modern computer architecture, researchers find that CPUs process data in a much faster speed than the main memory (DRAM) can supply.
-As a result, modern CPUs adopt a hierarchy memory architecture to bridge the performance gap between the CPUs and the main memory.
+During the evolution of the computer architecture, researchers find that CPUs process data in a much faster speed than the main memory (DRAM) can supply.
+As a result, CPUs adopt a hierarchy memory architecture to bridge the performance gap between the CPUs and the main memory.
 By storing extra copies of recently accessed data and code in a smaller but faster memory, the software can get its most recently accessed code and data in a shorter time.
@@
 \subsection{Threat Model}
-We assume that an attacker shares the same hardware platform with the target.
-The attacker attempts to retrieve sensitive information through address-based
-side-channel attacks. The attacker has no direct access to the target's memory or cache, but he can probe the memory or cache at each program point. Here are a few examples.
+We assume that an attacker shares the same hardware platform with the victim.
+The attacker attempts to retrieve sensitive information through address-based side-channel attacks.
+The attacker has no direct access to the victim's data, but he can probe the memory or cache at each program point.
+Here are a few examples.
 \begin{enumerate}
-  \item A host machine has several Virtual Machines (VMs). The victim runs the application inside one VM. An attacker can control the VM and probe the process running on the other VM.
-  \item  In a shielding system, a malicious operating system can extract sensitive information from protected user-level applications.
+  \item A host machine has several virtual machines (VMs). The victim runs the application inside one VM. An attacker can control one VM and probe the process running on the other VM.
+  \item  In a shielding system~\cite{arnautov2016scone,schuster2015vc3}, a malicious operating system can extract sensitive information from protected user-level applications.
   \item A ring-3 application can probe some sensitive information inside the kernel.
@@
 
-In reality, attackers will face many possible obstacles, such as the noisy observations of the memory or cache. However, for this project, we assume
-the attacker has noise-free observations as in previous work~\cite{203878,182946,Brotzman19Casym}.
+In reality, attackers may face many possible obstacles, such as the noisy observations of the memory or cache.
+However, for this project, we assume the attacker has noise-free observations as in previous work~\cite{203878,182946,Brotzman19Casym}.
 The threat model captures most address-based side-channel attacks and apply to the three attack models: 1) time-based attacks, 2) access-based attacks, 3) trace-based attacks.
@@
 
-With the above definition, we have the following mapping between $\beta$,
-$K$, $M$, and $O$:
+With the above definition, we have the following mapping between $\beta$, $K$, $M$, and $O$:
 \begin{displaymath}
@@
 we can not find a pair of two different $k_{i1}$ and $k_{i2}$ to satisfy the above inequation.
-For example, in Figure~\ref{fig:chapter3:cf}, if $m = 0$, the function \textsf{example1} will always execute the branch 2.
-However, if $m = \mathtt{0xffffffff}$ and $k = 0$, the function \textsf{example1} executes the branch 1 and the function \textsf{example1} executes the branch 2 when $k = \mathtt{0xf000000}$.
+For example, in Figure~\ref{fig:chapter3:cf}, if $m = \mathtt{0}$, the function \textsf{example1} will always execute the branch 2.
+However, if $m = \mathtt{0xffffffff}$ and $k = \mathtt{0}$, the function \textsf{example1} executes the branch 1 and the function \textsf{example1} executes the branch 2 when $k = \mathtt{0xf000000}$.
 
@@
 \subsection{Trace-oriented Symbolic Execution}
-Symbolic execution is notorious for its high performance cost.
+Symbolic execution is notorious for its expensive performance cost.
 Previous trace-oriented symbolic execution
@@
   \label{scala:ir}
-  \resizebox{.7\columnwidth}{!}{%
+  \resizebox{.8\columnwidth}{!}{%
 
@@
 The trace information can be logged via some emulators (e.g., QEMU) or dynamic binary instrumentation tools (DBI).
-We run a program with the concrete input under the DBI to record execution traces.
+In this work, we run a program with the concrete input under the DBI to record execution traces.
 The trace data has the following information:
@@
 
-\begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth, frame=none][ht]
+\begin{lstlisting}[xleftmargin=.3\textwidth, xrightmargin=.2\textwidth, frame=none][ht]
 ...
@@
 \detect{} is designed to help software developers find and understand the side-channel vulnerabilities.
-To ease the procedure of fixing the bug, we also track the information flow for each byte of the input
+To ease the procedure of fixing bugs, we also track the information flow for each byte of the input
 buffer.
 The step can be seen as the multiple-tag taint analysis. With the help of the information from symbolic execution, we can implement a relatively simple but relatively precise information flow track.
-At the beginning of the analysis, \detect{} keep track for each byte in
+At the beginning of the analysis, \detect{} keep track of each byte in
 the original buffer.
@@
 Therefore, Monocypher should be secure under our threat model.
-Libgcrypt is a crytpographic library from the GunPG.
+Libgcrypt is a cryptographic library from the GunPG.
 As some previous work (e.g., CacheD) choose to evaluate their tools on CacheD, we can compare the evaluation results by applying the tool on Libgcrypt.
@@
 running on Ubuntu 16.04. While our tool can work on the stripped binaries, 
-in the evaluation, we keep the debug information to get the fine-grained infromation
+in the evaluation, we keep the debug information to get the fine-grained information
 (e.g., line numbers).
@@
     \item How much performance overhead does the method introduce? (Performance)
-    \item How effective are the design choices made by the tool method? (Design Choices)
 \end{enumerate}
@@
 
-\detect{} works on native x86 execution traces.
-The design, which is very precise in terms of true leakages compared to other static source code method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also has the common limitations of dynamic approaches.
+\textbf{Coverage.} \detect{} works on native x86 execution traces.
+The design, which is very precise in terms of true leakages compared to other static source code method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also share the common limitations of dynamic approaches.
 \detect{} may only cover part of the code.
 Each time we only get one single execution trace.
-Therefore, we may neglect some side-channel vulnerabilities not covered by the traces analyzed.However, this is not a crucial problem for analyzing cryptographic libraries, because cryptographic libraries are designed to have the same code coverage for various inputs.
-Our evaluation also confirms the above point.
-For symmetric encryption, during our evaluation there is no secret-dependent control-flow transfers.
+Therefore, we may neglect some side-channel vulnerabilities not covered by the traces analyzed.
+However, this is not a crucial problem for analyzing cryptographic libraries, because cryptographic libraries are designed to have the same code coverage for various inputs.
+Our evaluation also confirms the above intuition.
+For symmetric encryption, there is no secret-dependent control-flow transfers during our evaluation.
 RSA implementations have several secret-dependent control-flow transfers.
-Most of them are bound checks, which do not leak much information and have negligible effects on the whole code coverage as well.
+Many of them are bound checks, which do not leak much information and have negligible effects on the whole code coverage as well.
 
-While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers.
+\textbf{Design Choices.} At the early stage of the project, we use SMT solvers to get the solutions of constraints.
+However, we find for some ciphers (RSA), \detect{} times out after several days.
+The profiling result shows that it is spending most its time in Z3.
+Later, we use a sampling method to detect side-channel leakages.
+The sampling method seems simple and may miss some leakages in theory.
+However, the evaluation result shows \detect{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.
+
+\textbf{Cache Model.} We use a simple cache model in this work.
+Recent work~\cite{Brotzman19Casym,182946} uses an LRU cache.
+First, there is no fundamental difficulties for us to adopt a more realistic cache models.
+Second, the LRU model is still a substantial simplification of a real cache.
+However, the choice of a logical model of cache can bring expensive overheads.
+
+\textbf{Leakages.} While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers.
 The DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort.
 After we manually analyze those leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which partially explain why developers are not interested in fix all the leakages.
-
-We use a sampling method to detect side-channel leakages.
-The sampling method seems simple and may miss some leakages in theory.
-However, the evaluation result shows \detect{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.

### 2021-04-20 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
   \end{minipage}
-  \caption{A Serious Leakage.}\label{chapter5:fig:example1}
+  \caption{A serious leakage.}\label{chapter5:fig:example1}
 \end{figure}
@@
   \end{minipage}
-  \caption{A Minor Leakage. }\label{chapter5:fig:example2}
+  \caption{A minor leakage. }\label{chapter5:fig:example2}
 \end{figure}
@@
 \end{minipage}
-\caption{Multiple Leakages}\label{chapter5:fig:multiple}
+\caption{Multiple leakage sites. The two leakage sites in Figure (a) leak different information. But the leaked information in Figure (b) has some overlaps. }\label{chapter5:fig:multiple}
 \end{figure}
@@
 
-According to Chi Square Distribution Table, we have the probability $p\approx0.95$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (a).
+According to Chi-squared distribution table, we have the probability $p\approx0.95$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (a).
 We have the probability $p\approx0.00$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (b).
@@
 \textbf{Evaluation setup.} We run all the following experiment in a machine with Ubuntu 18.04 LTS.
-The server machine equips with 2.30GHz Intel Core i9-9880 CPU with 16GB RAM memory.
+The machine equips with 2.30GHz Intel Core i9-9880 CPU with 16GB RAM memory.
 We use the default release settings to build the source code of the software into ELF 64-bit executables with GCC 7.5.

### 2021-04-20 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
     \item We implement the method into a tool and apply it to several pieces of real software.
-\tool{} successfully identifies previous unknown and known side-channel vulnerabilities and calculates the corresponding information leakage.
+\tool{}\footnote{Abacus is open source under the MIT license.
+\url{https://github.com/s3team/Abacus}} successfully identifies previous unknown and known side-channel vulnerabilities and calculates the corresponding information leakage.
 Our results are useful in practice.

### 2021-04-21 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \section{Evaluation}
-In this section, we evaluate \ctool{} on several small benchmarks and real-world software trying to answer the following questions:
+In this section, we evaluate \ctool{} on real-world software trying to answer the following questions:
 
@@
 
-\textit{Small Programs:} We use two benchmarks that are well studied in the previous work. The amount of actual leakage of those samples are known. We use them to evaluate the precision of the tool.
-
 \textit{Cryptography Applications:} Our benchmarks include the most popular cryptography libraries, such as mebdTLS, OpenSSL, Libgcropt, and wolfSSL.
@@
 
-\begin{table}
+\begin{sidewaystable}
 \footnotesize
@@
 
-\end{table}
+\end{sidewaystable}
 

### 2021-04-21 SupplementaryMaterial/Vita.tex
Updates from Overleaf

@@
 Before he went to Penn State, he received his bachelor's degree in Electronic Engineering and Information Science from University of Science and Technology of China.
+
+  \section*{Publications}
+  \begin{enumerate}
+    \item \textbf{Qinkun Bao}, Zihao Wang, Xiaoting Li, James Larus, and Dinghao Wu, ``Abacus: Precise Side-Channel Analysis'', In \emph{Proceedings of the 43rd International Conference on Software Engineering (ICSE 2021)}.
+(Technical Track)
+    \item \textbf{Qinkun Bao}, Zihao Wang, James Larus, and Dinghao Wu, ``Abacus: A Tool for Precise Side-Channel Analysis", In \emph{Proceedings of the 43rd International Conference on Software Engineering: Companion (ICSE-Companion 2021)}.
+(Artifact)
+
+    \item \textbf{Qinkun Bao}, Zihao Wang, James Larus, and Dinghao Wu, ``Quincunx: Measuring Side-channel Vulnerabilities
+    By Fuzzing and Memory Auditing'', under review.
+
+    \item \textbf{Qinkun Bao}, Zihao Wang, Quan Li, and Dinghao Wu, ``Fast Semantic-aware Function Recognition in Obfuscated Binaries'', under review.
+
+    \item Shixiong Jing, \textbf{Qinkun Bao}, Pei Wang, Xulong Tang, and Dinghao Wu, ``Characterizing AI Model Inference Applications Running in SGX Environment'', under review.
+
+    \item Yufei Jiang, \textbf{Qinkun Bao}, Xiao Liu, and Dinghao Wu, ``RedDroid: Android Application Redundacy Customization based on Static Analysis'', in \emph{Proceedings of the 29th IEEE International Symposium on Software Reliability Engineering (ISSRE 2018)}, Memphis, TN, October 15-18, 2018
+
+\item Pei Wang, \textbf{Qinkun Bao}, Li Wang, Shuai Wang, Zhaofeng Chen, Tao Wei, and Dinghao Wu, ``Software Protection On-The-Go: An Empirical Study on Mobile App Obfuscation'', in \emph{Proceedings of 40th International Conference on Software Engineering (ICSE 2018)}, Gothenburg, Sweden, May 27-June 3, 2018
+
+\item Shengru Li, Kai Han, Nirwan Ansari, \textbf{Qinkun Bao}, Daoyun Hu, Junjie Liu, Shui Yu, and Zuqing Zhu, ``Improving SDN Scalability with Protocol-Oblivious Source Routing: A System-Level Study'', \emph{IEEE Transactions on Network and Service Management}, vol.
+15, no.
+1, pp.
+275-288, March 2018
+
+\item Shuai Wang, Wenhao Wang, \textbf{Qinkun Bao}, Pei Wang, Xiaofeng Wang, and Dinghao Wu, ``Binary Code Retrofitting and Hardening Using SGX'', in \emph{Proceedings of the 2017 workshop on Forming an Ecosystem Around Software Transformation (FEAST17)}, co-located with CCS 2017, Dallas, USA, November 3, 2017
+\end{enumerate}

### 2021-04-21 SupplementaryMaterial/Vita.tex
Updates from Overleaf

@@
 (Technical Track)
-    \item \textbf{Qinkun Bao}, Zihao Wang, James Larus, and Dinghao Wu, ``Abacus: A Tool for Precise Side-Channel Analysis", In \emph{Proceedings of the 43rd International Conference on Software Engineering: Companion (ICSE-Companion 2021)}.
+    \item \textbf{Qinkun Bao}, Zihao Wang, James Larus, and Dinghao Wu, ``Abacus: A Tool for Precise Side-Channel Analysis'', In \emph{Proceedings of the 43rd International Conference on Software Engineering: Companion (ICSE-Companion 2021)}.
 (Artifact)

### 2021-04-21 SupplementaryMaterial/Vita.tex
Updates from Overleaf

@@
 \item Shuai Wang, Wenhao Wang, \textbf{Qinkun Bao}, Pei Wang, Xiaofeng Wang, and Dinghao Wu, ``Binary Code Retrofitting and Hardening Using SGX'', in \emph{Proceedings of the 2017 workshop on Forming an Ecosystem Around Software Transformation (FEAST17)}, co-located with CCS 2017, Dallas, USA, November 3, 2017
+
+\item Shilin Zhu, Siyao Meng, \textbf{Qinkun Bao}, Xiaoliang Chen, and Zuqing Zhu, ``Availability-Aware Service Provisioning in EONs: How Efficient will FIPP-p-Cycles be?",  in \emph{Proceedings of IEEE/OSA Optical Fiber Communication Conference (OFC)}, paper W2A.51, March 2016
+
+\item Xiaoliang Chen, Fan Ji, Shilin Zhu, \textbf{Qinkun Bao}, and Zuqing Zhu, ``Availability-Aware Service Provisioning in SD-EON based Inter-Datacenter Networks",  \emph{Photonic Network Communications (Springer)}, vol.
+31, no.
+3, pp.
+543-549, June 2016
 \end{enumerate}

### 2021-04-22 Chapter-2/Chapter-2.tex
Update Chapter-2.tex

@@
 \subsection{Attack Models}
-Previous work~\cite{182946} classifies side-channel attacks into three type based on the type of information that an attacker can learn during the attack.
+Previous work~\cite{182946} classifies side-channel attacks into three types based on the type of information that an attacker can learn during the attack.
 \subsubsection*{Timing-based Attacks}
 In timing-based attacks, an adversary can monitor the execution time of a victim program.
-It could be the overall execution time or the execution time of some interesting points (e.g.
-a function).
+It could be the overall execution time or the execution time of some interesting points (e.g., a function).
 The execution time is correlated to some events (e.g., cache hits and misses, page faults, the number of instructions).
@@
 In access-based attacks, an adversary can probe one time only after the termination of the victim program.
-The attacker can learn the memory addresses are that accessed during the execution.
+The attacker can learn the memory addresses that are accessed during the execution.
 For example, a cache-based channel attack can know which memory access incurs a cache hit and which memory access incurs a cache miss.
-Since the attacker can probe the victim program after the execution, the attacker do not know the order of memory accesses.
+Since the attacker can probe the victim program after the execution, the attacker does not know the order of memory accesses.
 Access-based attacks often happen in the cloud computing environment when the attacker and victim share the same hardware (e.g., LLC Cache).
@@
 In an access-based attacks, the attacker can only learn both \textsf{a} and \textsf{b} are executed.
-In a trace-based attacks, the attacker can know the execution sequence of two functions (e.g., $aabbb$).
-Controlled-channel attacks~\cite{moghimi2020copycat, xu2015controlled} belong to the category, where a malicious operating system can interrupt the victim applications and probe the program at any time.
-In general, the trace-based attack has the strongest assumption about the threat model,  but it can retrieve the more information compared to other two types of attacks.
+In a trace-based attack, the attacker can know the execution sequence of two functions (e.g., $aabbb$).
+Controlled-channel attacks~\cite{moghimi2020copycat, xu2015controlled} belong to the category where a malicious operating system can interrupt the victim applications and probe the program at any time.
+In general, the trace-based attack has the strongest assumption about the threat model,  but it can retrieve more information compared to the other two types of attacks.
 \subsection{Target Applications}

### 2021-04-22 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 We consider an attacker who shares the same hardware resource with the victim.
-The attacker may not know the memory access the victim program accesses directly, but he can infer whether some memory addresses are accessed or not at various granularities after \textit{each run} of the victim program.
+The attacker may not know the memory access the victim program accesses directly.
+Still, he can infer whether some memory addresses are accessed or not at various granularities after \textit{each run} of the victim program.
 We call the memory access information as the observation ($O$) in the rest of the paper.
@@
 We also assume the attacker can have access to the source code of the victim program ($\beta$).
-It is a valid assumption since most side-channel attacks target open source software.
-Also like recent works, we assume the attacker have a noise-free observation.
+It is a valid assumption since most side-channel attacks target open-source software.
+Also, like recent works, we assume the attacker has a noise-free observation.
 For some side-channel channels like the controlled-channel attacks, it is already true.
 The program ($\beta$) has $K$ as the sensitive input.
-$K$ is a finite set that consists of every possible keys ($k \in K$).
+$K$ is a finite set that consists of every possible key ($k \in K$).
 The program also takes known messages $M$ as the input.

### 2021-04-22 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-  \item We propose a novel method that can detect and analyze the effect of each side-channel leakage sites automatically.
-Our analysis combine information from both the source code and the run-time execution, which makes the method more effective in finding the leakages.
+  \item We propose a novel method that automatically detects and analyzes the effect of each side-channel leakage site.
+Our analysis combines information from both the source code and the run-time execution, which makes the method more effective in finding the leakages.
 The method can combine multiple leakage sites to retrieve more information as well.
@@
 We propose a method that can estimate the lower bound of information leakages.
-The theory can serve as the foundation of the future work on quantify the information leakage based on the fuzzing.
+The theory can serve as the foundation of future work on quantifying the information leakage based on the fuzzing.
 

### 2021-04-22 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \subsection{An Example}
-Figure~\ref{fig:example1} show a function that is vulnerable to side-channel attacks.
-The function take a input secret from the caller.
+Figure~\ref{fig:example1} shows a function that is vulnerable to side-channel attacks.
+The function takes an input secret from the caller.
 Depending on the value of the secret, it may access different values at line 7.
-Suppose an attacker can observe which item in the table \textsf{T} is accessed, he can infer the secret based on the observation.
+Suppose an attacker can observe which item in the table \textsf{T} is accessed.
+He can infer the secret based on the observation.
+
 \begin{figure}[h]
@@
 \end{figure}
-On the other hand, the second example also have a side-channel leakages at line 7.
+On the other hand, the second example also has side-channel leakages at line 7.
 However, the leakage is slightly different.
 Still, we test the program with input from $0, 1, \dots, 7$.
-However, we find the attacker can not uniquely determine the secret based on the observation of table $T$.
-For example.
-both $0$ and $4$ read the first the item of the table.
-Therefore, we think the vulnerability is slightly minor than the previous one.
-Here comes with the definition of the amount of leaked information of the vulnerability.
+However, we find the attacker can not uniquely determine the secret based on the observation of table $T$, for example.
+Both $0$ and $4$ read the first item of the table.
+Therefore, we think the vulnerability is minor than the previous one.
+Here comes the definition of the amount of leaked information of the vulnerability.
 
@@
 We can use the definition to detect those severe leakages.
-In the examples of Figure~\ref{chapter5:fig:example1} and Figure~\ref{chapter5:fig:example2}, because the input secret range from $0$ to $255$, we can calculate the precise value of the amount of information leakage by iterating each input keys.
+In the examples of Figure~\ref{chapter5:fig:example1} and Figure~\ref{chapter5:fig:example2}, because the secret input range from $0$ to $255$, we can calculate the precise value of the amount of information leakage by iterating each input keys.
 In Figure~\ref{chapter5:fig:example1}, each item in the array could be read.
@@
 In Figure~\ref{chapter5:fig:example2}, there could be $4$ kinds of information, so the information leakages defined by channel capacity is $\log_2{4} = \,2\, \mathrm{bits}$.
-Compared with the result from Definition~\ref{chapter5:def}, we can see that the amount of leakages by Definition is a conservative estimation.
+Compared with the result from Definition~\ref{chapter5:def}, we can see that the amount of leakages by Definition~\ref{chapter5:def} is a conservative estimation.
 
@@
 Considering the example in figure~\ref{fig:align}, it read the data from the array \textsf{T} based on the index (i).
-If the index (i) is associated with a key, it could be a side-channel vulnerability.
+If index (i) is associated with a key, it could be a side-channel vulnerability.
 Unlike the example in the previous section, the array \textsf{T} is on the heap.
@@
 Suppose during the first run, \textsf{T} is allocated at the address \textsf{0xff124800} and \textsf{T} is allocated at the address \textsf{0xff124801} at the second run.
-For the example in Figure~\ref{fig:align}(a), the index that used to access the array is always $1$, so it should not be a side-channel vulnerability here.
+For the example in Figure~\ref{fig:align}(a), the index that is used to access the array is always $1$, so it should not be a side-channel vulnerability here.
 However, because the based address is different.
@@
 Under the circumstance, it is a false positive.
-Besides, it can cause false negatives as the example shown in Figure~\ref{fig:align}(b).
-In the example, different keys lead to different index.
-However, as $T_0 + i_0$ equals to $T_1 + i_0$, \ can not observe the difference here, which can cause a false positive.
+Besides, it can cause false negatives, as the example shown in Figure~\ref{fig:align}(b).
+In the example, different keys lead to different indexes.
+However, as $T_0 + i_0$ equals to $T_1 + i_0$, \ctool{} can not observe the difference here, which can cause a false positive.
 
@@
 \textbf{Run-time Information.} One example here is the concrete memory address during the runtime.
-Such a value satisfy the uniqueness characteristic.
+Such a value satisfies the uniqueness characteristic.
 However, as the example shown in Figure~\ref{fig:align}, it does not have the alignment property.
 \textbf{Source Code Information.} Alternatively, we can use the information from the source code.
-Recent work~\cite{sumner2010memory} proposes using the execution point that allocate the memory cell as the index and tracking the pointer arithmetic to track the pointer that points to the memory.
+Recent work~\cite{sumner2010memory} proposes using the execution point that allocates the memory cell as the index and tracking the pointer arithmetic to track the pointer that points to the memory.
 However, such a method may miss the alias symbol that points to the same memory cell.
@@
 If so, we add the memory access into the tuple.
-After the execution, the tuple can be mapped into the location of the source code and we only compare the memory access that belongs to the same lines in the source code.
+After the execution, the tuple can be mapped into the location of the source code, and we only compare the memory access that belongs to the same lines in the source code.
 
@@
 Real-world software can have many side-channel vulnerabilities.
-Those vulnerabilities may spread in the whole program.
+Those vulnerabilities may spread throughout the whole program.
 An adversary may exploit more than one side-channel vulnerabilities to gain more information~\cite{7163052, 191010}.
@@
 Suppose we can summarize the data in a $r*c$  two-way contingency table.
-The chi-square test statistic and the degrees of freedom $v$ is calculated with the below formula:
-\[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k}\] 
-\[v = (r - 1)(c - 1)\]
-Here $O$ is the observe value and $E$ is the expected value. A low value means that there is a high correlation between the two variables.
+The chi-square test statistic and the degrees of freedom $v$ are calculated with the below formula:
+\[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k} \qquad	 v = (r - 1)(c - 1)\]
+Here $O$ is the observed value, and $E$ is the expected value. A low value means that there is a high correlation between the two variables.
 

### 2021-04-22 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 Address-based side-channel attacks happen when a program accesses different memory locations when it processes different secrets.
-In modern computer ssytems, an attacker may shares some hardware resources (e.g., Cache, TLB, and DRAM) with the victim~\cite{ge2018survey,szefer2019survey}.
+In modern computer systems, an attacker may shares some hardware resources (e.g., Cache, TLB, and DRAM) with the victim~\cite{ge2018survey,szefer2019survey}.
 An attacker can probe the shared hardware resource to infer the memory accesses of the victim.
@@
     \centering
-    \caption{Due to the page limit, we only shows some representations of the vast side-channel attacks: Attacks, the shared resources with attackers, the granularity of the attacker can observe, is there any published attacks on non-cryptography library and if the type of attack have been used to exploit multiple leakage sites.}
+    \caption{Due to the page limit, we only show some representations of the vast side-channel attacks: Attacks, the shared resources with attackers, the granularity of the attacker can observe, is there any published attacks on the non-cryptography library, and if the type of attack has been used to exploit multiple leakage sites.}
     \label{table:side_channel_attack}
@@
 An attacker primes the cache set with its own data and waits until the victim executes the program.
-After that, the attacker probes the cache by reading previously-loaded data.
+After that, the attacker probes the cache by reading previously loaded data.
 If the victim accesses the cache set and evicts some lines of the data, the attacker will experience a slow measurement.
-Under the circumstance, the attacker can know the victim must have touched some data that mapping to the same cache set.
+Under the circumstance, the attacker can know the victim must have touched some data that map to the same cache set.
 
-\textbf{Flush+Reload.} Flush+Reload allows an attacker to observe the memory at the granularity of cache line instead of a cache set.
-While Flush+Reload targets a single cache line, it requires the attacker and victim share some memory.
+\textbf{Flush+Reload.} Flush+Reload allows an attacker to observe the memory at the granularity of the cache line instead of a cache set.
+While Flush+Reload targets a single cache line, it requires the attacker and victim to share some memory.
 During the ``flush'' stage, the attacker flushes the ``monitored
@@
 Based on the above attacks, some work~\cite{brickell2011technologies} suggests having secret-dependent memory accesses at finer than the size of one cache line should be secure enough.
-However, recent studies shows that having different memory accesses within a cache line is also dangerous.
+However, recent studies show that having different memory accesses within a cache line is also dangerous.
 One example is the CacheBleed attack~\cite{yarom2017cachebleed}.
-It is a cache channel attack can exploits cache-bank collisions.
+It is a cache channel attack that can exploit cache-bank collisions.
 \subsection{Page-level Channel}
@@
 One example is the controlled-channel attack~\cite{xu2015controlled}.
-It is a primary threat for the trusted execution environments (TEEs).
-A privileged adversary (e.g., kernel) can infer the sensitive information by manipulating the enclave page accesses.
+It is a primary threat to the trusted execution environments (TEEs).
+A privileged adversary (e.g., kernel) can infer sensitive information by manipulating the enclave page accesses.
 A malicious OS can proactively revoke a virtual enclave memory page from the virtual memory.
@@
 There is a vast number of studies\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last} on side-channel attacks.
-Most early work targets on retrieving encryption key from cryptography libraries.
+Most early work targets retrieving encryption keys from cryptography libraries.
 In recent years, researchers start to focus on more general and diverse applications.
@@
 
-The first side-channel attack to cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996.
-It exploits the the simple modular exponentiation algorithm function in many algorithms (Diffie-Helloman, RSA) implementations.
+The first side-channel attack on cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996.
+It exploits the simple modular exponentiation algorithm function in many algorithms (Diffie-Hellman, RSA) implementations.
 The function does not run in a fixed time.
@@
 However, recent studies also show those versions (e.g., AES-NI) also have side-channel vulnerabilities caused by compiler optimizations and human mistakes~\cite{217537}.
-The situation is even worse for asymmetric ciphers (e.g., Diffie-Helloman, RSA, ECDSA).
-Those ciphers have a lots of big number calculations.
+The situation is even worse for asymmetric ciphers (e.g., Diffie-Hellman, RSA, ECDSA).
+Those ciphers have a lot of big number calculations.
 It is hard to implement those calculations completely side-channel resistant.
@@
 The first approach is to adopt constant time operation when computing the secret data.
-It is hard to migrate all the code into a constant time implementation.
-The second approach is to use blinding to reduce the information that can attacker can retrieve.
-However, the binding value can also be retrieved by an attacker through other methods including side-channel attacks.
+It is hard to migrate all the code into a constant-time implementation.
+The second approach is to use blinding to reduce the information that an attacker can retrieve.
+However, the binding value can also be retrieved by an attacker through other methods, including side-channel attacks.
 
 \subsubsection*{Machine Learning Applications}
-Recent side-channel attacks on machine learning applications mainly focus on recovering two types of the sensitive information: the input of the model, and the architecture of deep learning models.
+Recent side-channel attacks on machine learning applications mainly focus on recovering two types of sensitive information: the input of the model and the architecture of deep learning models.
 Hua et al.~\cite{hua2018reverse} were the first in the literature to reverse engineer the architecture of convolutional neural networks (CNNs) through the memory access patterns.
@@
 CSI NN~\cite{batina2019csi} reverse engineer the multi-layer perception and convolution neural network based on the electromagnetic signals (EMs).
-Cache Telepathy~\cite{yan2020cache} introduces the cache based side-channel attack to extract DNNs' architectures.
+Cache Telepathy~\cite{yan2020cache} introduces the cache-based side-channel attack to extract DNNs' architectures.
 We find that all existing approaches need a lot of domain knowledge and expertise to launch the attacks.
@@
 Recent work also studies the side-channel attacks in media and graphic libraries.
-Gruss el at.~\cite{191010} show an attack that can infer keystrokes by exploiting secret-dependent memory accesses in the GDK library.
+Gruss et at.~\cite{191010} show an attack that can infer keystrokes by exploiting secret-dependent memory accesses in the GDK library.
 In the controlled-channel attack~\cite{xu2015controlled}, Yuanzhong et al.
@@
 \subsubsection*{Others}
-Some other side-channel targets also include spell checking tools, and font libraries~\cite{xu2015controlled}.
-The attack to font libraries is essentially the same as the attack to the graphic library like GDK.
+Some other side-channel targets also include spelling checking tools and font libraries~\cite{xu2015controlled}.
+The attack on font libraries is essentially the same as the attack on the graphic library like GDK.
 By exploiting the differences of memory accesses when the program renders different characters, an attacker can recover parts of the original sensitive information.
-Other side-channel attacks target on the OS's kernel.
+Other side-channel attacks target the OS's kernel.
 One example is using the side-channel attack to break the kernel address space randomization (KASLR).
@@
 Since Linux 4.12, the kernel loads core kernel image and device drivers at random positions during the boot time.
-Jang et al.~\cite{jang2016breaking} rely on side-channels to reveal mapping status of each page.
+Jang et al.~\cite{jang2016breaking} rely on side-channels to reveal the mapping status of each page.
 After that, they detect kernel modules with unique size signatures to break KASLR.
@@
 \section{Detection and Mitigation}
-There are several existing work on side-channel leakage detections.
+There are several existing works on side-channel leakage detections.
 According to Table~\ref{table:side_channel_detection_tool}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction.
@@
 \textbf{Abstraction.} The second category of those tools belongs to the field of abstractions.
-Tools based on those approaches use the abstraction to generate approximations to model the semantics of computer programs.
+Tools based on those approaches use abstraction to generate approximations to model the semantics of computer programs.
 After that, by analyzing the model, those tools can identify side-channel leakages.
@@
     \item Those tools heavily rely on SMT solvers.
-Despite SMT solvers have made incredible progress in terms of the performance, SMT solving is still the main bottlenecks of those tools.
+Despite SMT solvers having made incredible progress in performance, SMT solving is still the main bottleneck of those tools.
 SMT solvers are not good at non-linear arithmetic.
@@
 Here, we introduce several tools. CacheAudit~\cite{182946} uses abstract domains to compute an
-over approximation of cache-based side-channel information leakage upper bound.
+over-approximation of cache-based side-channel information leakage upper bound.
 However, it is difficult to judge the sensitive level of the side-channel leakage based on the leakage provided by CacheAudit.
@@
 CacheS~\cite{236338} improves the approach from
-CacheAudit with a new abstract model that only track
+CacheAudit with a new abstract model that only tracks
 secret-related code. Like CacheAudit, CacheS cannot
@@
 Again, their
-approaches cannot evaluate the sensitive level for each side-channel vulnerability, and it only work on small code snippets.
+approaches cannot evaluate the sensitive level for each side-channel vulnerability, and it only works on small code snippets.
 
@@
 It uses statistical hypothesis testing to find true leakages.
-However, both imperfect trace alignment and statistical testing result that DATA can produce false positives.
+However, both imperfect trace alignment and a statistical testing result that DATA can produce false positives.
 MicroWalk~\cite{Wichelmann:2018:MFF:3274694.3274741} adopts a similar approach from DATA by comparing all accessed addresses.
@@
 flow capacity. They model the possible information leakage as a network of limited-capacity
-channel. After that, they use the maximum rate of the channel to represent the amount of 
-secret information that the execution can reveal.
+channel. After that, they use the maximum rate of the channel to represent the amount of secret information that the execution can reveal.
 Backes et al.~\cite{5207642} propose an automated method for QIF
@@
 Phan et al.~\cite{Phan:2012:SQI:2382756.2382791} propose symbolic QIF. The goal of their
-work is to ensure a program is non-interference. They adopt an over
-approximation method to estimate the total information leakage and their method
+work is to ensure a program is non-interference. They adopt an over-approximation method to estimate the total information leakage, and their method
 does not work for secret-dependent memory access side-channels.
-Pasareanu et al.~\cite{pasareanu2016multi} combine symbolic analysis and Max-SMT solving to synthesize the concrete public input that can lead to the worst case leakage.
+Pasareanu et al.~\cite{pasareanu2016multi} combine symbolic analysis and Max-SMT solving to synthesize the concrete public input that can lead to the worst-case leakage.
 They assume the target program has multiple different input secrets and calculate the average leakage for one-fixed public input.
@@
 behavior and estimates the amount of leaked information based on cache miss/hit.
-Their approach only scale to small programs, which limits its usage in
+Their approach only scales to small programs, which limits its usage in
 real-world applications. On the contrary, \tool{} assesses the sensitive level
-of side-channels with different granularities. It can also analyze side-channels in real-world cryptographic libraries.
+of side channels with different granularities. It can also analyze side channels in real-world cryptographic libraries.
 
@@
 solutions for a propositional formula (\#SAT). There are two approaches to
-solving the problem, exact model counting and approximate model
+solving the problem, exact model counting, and approximate model
 counting. Exact model counting for propositional formulas (\#SAT) should determine
-the number of solutions. Intuitively, such model counter should traverse the whole
-search space to find all the satisfying solutions. Consequently, exact model counter is 
-very slow. Those model counters have difficulty scaling up to real-world programs.
-On the other hand, approximate model counter is much faster compared with the exact 
-model counter. The related work focus on approximate model counting since it is close to our approach. Wei and Selman~\cite{wei2005new} introduce
-ApproxCount, a local search based method using Markov Chain Monte
-Carlo (MCMC). ApproxCount has the better scalability than
+the number of solutions. Intuitively, such a model counter should traverse the whole
+search space to find all the satisfying solutions. Consequently, the exact model counter is very slow. Those model counters have difficulty scaling up to real-world programs.
+On the other hand, the approximate model counter is much faster compared with the exact model counter.
+The related work focuses on approximate model counting since it is close to our approach.
+Wei and Selman~\cite{wei2005new} introduce
+ApproxCount, a local search-based method using Markov Chain Monte
+Carlo (MCMC). ApproxCount has better scalability than
 exact model counters. Other approximate model counter includes
@@
 Despite the rapid development of model counters for SAT and some
-research~\cite{chistikov2017approximate,phan2015model}, existing tools cannot be directly applied to side channel leakage quantification for the following two reasons.
+research~\cite{chistikov2017approximate,phan2015model}, existing tools cannot be directly applied to side-channel leakage quantification for the following two reasons.
 ApproxFlow~\cite{biondi2018scalable} uses ApproxMC~\cite{chakraborty2016algorithmic} for information flow quantification, but it has only been tested with small programs.
@@
 \section{Trace-based Binary Analysis}
-Trace-based binary analysis can be seen as a type of dynamic analysis. It 
-analyzes one concrete program path one time rather than trying to cover
+Trace-based binary analysis can be seen as a type of dynamic analysis. It analyzes one concrete program path one time rather than trying to cover
 as many paths as possible. Compared to static analysis, trace-based analysis
@@
 two steps. The first step is collecting trace information. Existing
-approaches usually often rely on binary instrumentation frameworks or emulators (e.g, Intel Pin~\cite{luk2005pin},
+approaches usually often rely on binary instrumentation frameworks or emulators (e.g., Intel Pin~\cite{luk2005pin},
 Valgrind~\cite{nethercote2007valgrind}, QEMU). The second step is analyzing the trace using techniques, such
 as symbolic execution, taint analysis. Depending on when the analysis is launched,
-there are two kinds of trace-based analysis, online analysis and offline analysis.
+there are two kinds of trace-based analysis, online analysis, and offline analysis.
 As the name suggests, online analysis is performed during the program execution.
@@
 can force the program to execute a specific branch. Contrary to online analysis,
-offline analysis or post analysis happens when the program finish executions. 
+offline analysis or post-analysis happens when the program finishes executions. 
 Trace-based binary analysis has been adopted in several tasks like algorithm
-detection, vulnerability detection and malware analysis. We only mention a few of
-most related works here. Xu et al.~\cite{xu2017cryptographic} introduce bit-wise symbolic execution, which can
-identify crypto algorithms in obfuscated binaries. Ming et al.~\cite{ming2017binsim} use 
-system call sliced segment equivalence checking to do binary diffing. Jia et al.~\cite{jia2017towards}
+detection, vulnerability detection, and malware analysis. We only mention a few of
+the most related works here. Xu et al.~\cite{xu2017cryptographic} introduce bitwise symbolic execution, which can
+identify crypto algorithms in obfuscated binaries. Ming et al.~\cite{ming2017binsim} use system call sliced segment equivalence checking to do binary diffing. Jia et al.~\cite{jia2017towards}
 perform an offline analysis on execution traces to identify heap overflows.
 
-There are several known binary analysis frameworks that can ease users to launch analysis on binary executable.
-BitBlaze~\cite{brumley2011bap} is a binary analysis platform that provides both the static and dynamic analysis.
-It uses the tracecap plugin to  collect execution trace and convert the trace into Vine IR.
+There are several known binary analysis frameworks that can ease users to launch analysis on binary executables.
+BitBlaze~\cite{brumley2011bap} is a binary analysis platform that provides both static and dynamic analysis.
+It uses the tracecap plugin to collect execution traces and convert the trace into Vine IR.
 Binary Analysis Platform (BAP)
-is an another binary analysis platform. Similar to BitBlaze, it use a Pintrace tool to
-collect execution trace and convert the trace into BAP IR. Angr~\cite{shoshitaishvili2016state}, the most popular
-binary analysis platform recently, also support trace-based analysis. It converts each instruction into VEX IR and interprets each IR in Python.
+is another binary analysis platform. Similar to BitBlaze, it uses a Pintrace tool to
+collect execution traces and convert the trace into BAP IR. Angr~\cite{shoshitaishvili2016state}, the most popular
+binary analysis platform recently, also supports trace-based analysis. It converts each instruction into VEX IR and interprets each IR in Python.
 
-Above existing well-known binary analysis frameworks all adopt the IR layer, which make it easy to implement the analysis and support multiple architectures.
-However, it can have a very low efficiency and long traces.
+The above existing well-known binary analysis frameworks all adopt the IR layer, which makes it easy to implement the analysis and support multiple architectures.
+However, it can have very low efficiency and long traces.
 All IR must be interpreted no matter if symbolic variables are involved or not.
-Besides, as side-channels are low level problems in general, the IR design will also lose some information.
+Besides, as side-channels are low-level problems in general, the IR design will also lose some information.
 For example, IR-level branches are not necessarily a super-set or a sub-set of machine-code level branches.

### 2021-04-22 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
   \item We propose a novel method that automatically detects and analyzes the effect of each side-channel leakage site.
-Our analysis combines information from both the source code and the run-time execution, which makes the method more effective in finding the leakages.
+Our analysis combines information from both the source code and the runtime execution, which makes the method more effective in finding the leakages.
 The method can combine multiple leakage sites to retrieve more information as well.
@@
 \section{Background and Threat Model}
-In the section, we give an overview of the background knowledge of information theory, and present the threat model of the paper.
+In the section, we give an overview of the background knowledge of information theory and present the threat model of the paper.
 
@@
 Figure~\ref{fig:channel}(b) shows the example of the type of the channel.
-Once the input symbol is determined, the output symbol is also determine.
-As we can see, the channel have the unique output ($o \in O$) for every input ($k \in K$).
+Once the input symbol is determined, the output symbol is also determined.
+As we can see, the channel has a unique output ($o \in O$) for every input ($k \in K$).
 
@@
 \section{Method}
-In this section, we first provide two examples shows how we rank the side-channel vulnerability. After that, we prove that our method is the conservative estimate of the amount of the each leakage.
+In this section, we first provide two examples that show how we rank the side-channel vulnerability. After that, we prove that our method is the conservative estimate of the amount of each leakage.
 
@@
 To assess the sensitive level of the vulnerability, we use the sampling method to estimate the leakage.
-Suppose we give the function input from $0, 1, \dots, 7$ and observe the array $T$, we can find each different input have one unique observation.
+Suppose we give the function input from $0, 1, \dots, 7$ and observe the array $T$, we can find each different input has one unique observation.
 Therefore, the secret can be uniquely determined.
@@
 We compare address accesses of different executions generated by different inputs to quantify the amount of leakage information.
-A meaningful comparison requires we align executions across multiple runs before we quantify the leakage.
+A meaningful comparison requires that we align executions across multiple runs before we quantify the leakage.
 In this work, we combine the information from both the source code and the binary executable to align the memory access during the execution.
@@
 Suppose during the first run, \textsf{T} is allocated at the address \textsf{0xff124800} and \textsf{T} is allocated at the address \textsf{0xff124801} at the second run.
-For the example in Figure~\ref{fig:align}(a), the index that is used to access the array is always $1$, so it should not be a side-channel vulnerability here.
-However, because the based address is different.
+For the example in Figure~\ref{fig:align}(a), the index that is used to access the array is always $1$, so it should not be a side-channel vulnerability here, however, because the based address is different.
 So we get two different memory accesses.
@@
 
-Suppose one program has two side-channel vulnerabilities A and B, which can leak $L_A$ and $L_B$ bits respectively according to the definition~\ref{chapter5:def}. 
+Suppose one program has two side-channel vulnerabilities A and B, which can leak $L_A$ and $L_B$ bits respectively, according to the definition~\ref{chapter5:def}. 
 Depending on the relation between A and B, the total leaked information $L_{\mathit{total}}$ will be:
@@
 And the two leakages Figure~\ref{chapter5:fig:multiple} (b) are dependent.
-In this paper, for any two leakage, if $p < 0.03$, we think the two leakage sites are independent.
-For each leakage points, we use the above method to test if any two leakage sites are independent.
+In this paper, for any two leakages, if $p < 0.03$, we think the two leakage sites are independent.
+We use the above method to test if any two leakage sites are independent for each leakage point.
 We combine them into a leakage are calculate the total amount of the leakage.
@@
 In this section, we explain the implementation of \ctool{}.
-we first present the overview of \ctool{}. After that, we discuss some design details to implement \ctool{}.
+We first present the overview of \ctool{}. After that, we discuss some design details to implement \ctool{}.
 
@@
 For the first step, we build the target program from the source code.
-After that, we give them random inputs to the victim program and run the target program and record each of the address in the binary file is hit or not and store the information in a bitmap.
+After that, we give them random inputs to the victim program and run the target program and record each of the addresses in the binary file is hit or not, and store the information in a bitmap.
 Next, we analyze the side-channel leakage from the address access bitmap.
@@
 Finally, \ctool{} Generate the final leakage report.
-For each leakage sites, \ctool{} gives the conservative estimation of the information leakage.
-Every leakage site in the report is a true leakage and there is no false positives.
+For each leakage site, \ctool{} gives the conservative estimation of the information leakage.
+Every leakage site in the report is a true leakage, and there are no false positives.
 
@@
 For cryptography libraries, the input is the encryption key.
-For non-cryptography libraries, the input could be images, text, and information in other format.
+For non-cryptography libraries, the input could be images, text, and information in other formats.
 Encryption algorithms like AES, DES take an array representing the secrets.
-We generate the random input by flipping the each bit of the keys.
-Some other programs also takes an buffer as the input.
-The buffer may contains the redundancy information and follow a specific format.
+We generate the random input by flipping each bit of the keys.
+Some other programs also take a buffer as the input.
+The buffer may contain the redundancy information and follow a specific format.
 So not any input that satisfies the input length is a valid input.
@@
 We use some other tools to generate a list of valid keys and use the key to sample the program.
-Due to the enormous search space, we can not iterate every inputs.
-However, our method can give the conservative  estimate of each leakage site.
+Due to the enormous search space, we can not iterate every input.
+However, our method can give a conservative estimate of each leakage site.
 \subsection{Step 2: Address Record}
 Next, we record the memory access information based on the input secret.
-We use the dynamic binary instrumentation (DBI) tool to record the whether a particular memory access information is accessed or not.
-Inspired by the AFL and valgrind, we use the bitmap to represent whether a particular memory is accessed or not.
+We use the dynamic binary instrumentation (DBI) tool to record whether a particular memory access information is accessed or not.
+Inspired by the AFL and Valgrind, we use the bitmap to represent whether a particular memory is accessed or not.
 For example, the bitmap ${0101}$ of address $address_1, address_2, address_3, address_4$ means that $address_2, address_4$ are hit during the execution.
@@
 It has two benefits.
-First, modern computer systems employ the the Address Space Layout Randomization (ASLR).
-With ASLR, the operating system randomly put the enclave code and data at various memory offset.
-As a result, even for the same input, the code will get different execution traces because the enclave image is loaded at a different address each time Second, it helps us find the leakage site in the source code.
+First, modern computer systems employ the Address Space Layout Randomization (ASLR).
+With ASLR, the operating system randomly puts the enclave code and data at various memory offset.
+As a result, the code will get different execution traces even for the same input because the enclave image is loaded at a different address each time.
+Second, it helps us find the leakage site in the source code.
 
 We rely on the program header and symbol information to recover the offset in the binary.
-During the loading process, the operating system maps each segment into a continuous memory region.
+During the loading process, the operating system maps each segment into a contiguous memory region.
 So the offset of the virtual memory address between the code within the same segment is the same as the offset within the binary file.
@@
 
-There are two kinds of memory access: the access to the code and the access to the data.
+There are two kinds of memory accesses: accesses to the code and accesses to the data.
 \begin{itemize}
@@
 However, the length of x86 instructions can be from 1 byte to 15 bytes.
-For instructions whose length is longer than one byte, we also update the address  after the value $rip$ until the address reach the boundary of the instruction.
+For instructions whose length is longer than one byte, we also update the address after the value $rip$ until the address reaches the instruction's boundary.
   \item Data Access.
@@
 \subsubsection{Various Granularities Side-channel Detection}
-\ctool{} can detect the side-channel vulnerabilities in different granularity.
+\ctool{} can detect the side-channel vulnerabilities in different granularities.
 For each granularity, we calculate a new bitmap that represents access information of each unit.
 We have the bitmap of the memory access at the byte level.
-An attacker who has the coarse-grained observation at address space may not be able to distinguish the address difference.
-For example, modern X64 computer system uses 48-bit virtual memory addresses.
-The top 36 bit of the virtual address is called Virtual Page Number (VPN) and the bottom 12 bits of the virtual address is called offset.
-The memory management unit (MMU) transfer the virtual address into the physical address by mapping the Virtual Page Number (VPN) into the Physical Page Number (PPN) while keep the offset of the address.
-So two addresses with the Same VPN but different offset are not distinguishable by an attacker who only has the the page-level observation.
+An attacker who has the coarse-grained observation at address space may not distinguish the address difference.
+For example, modern X64 computer systems use 48-bit virtual memory addresses.
+The top 36 bit of the virtual address is called Virtual Page Number (VPN), and the bottom 12 bits of the virtual address is called offset.
+The memory management unit (MMU) transfers the virtual address into the physical address by mapping the Virtual Page Number (VPN) into the Physical Page Number (PPN) while keeping the offset of the address.
+So two addresses with the Same VPN but different offset are not distinguishable by an attacker who only has the page-level observation.
 
@@
 \begin{myexample}
-Suppose we sample a program from $k1$ to $k8$ and record the memory access at the granularity of each byte from $\mathsf{7ffff7ffd000}$ to $\mathsf{7ffff7ffd03f}$ (One cache line), we perform the bit-wise or operation of each address with the address range.
+Suppose we sample a program from $k1$ to $k8$ and record the memory access at the granularity of each byte from $\mathsf{7ffff7ffd000}$ to $\mathsf{7ffff7ffd03f}$ (One cache line).
+We perform the bit-wise or operation of each address with the address range.
 Because the cache line is always accessed.
@@
 According to Definition~\ref{chapter5:def}, we quantify the information leakage based on the distribution of the observation.
-If we calculate the information leakage from an $4MB$ memory area, then the length of the byte-level bitmap is $4*1024*1024 = 4194304$.
+If we calculate the information leakage from a $4MB$ memory area, then the length of the byte-level bitmap is $4*1024*1024 = 4194304$.
 While it is possible to compute the distribution of the bitmap theoretically, it is hard to compare the bitmap of such length in practice.
 
-To solve the problem, we use the debug information to split the bitmap into several segments and map the leakage site into the location of the source code.
+To solve the problem, we use the debug information to split the bitmap into several segments and map the leakage site into the source code location.
 Each segment maps the address access situation of the function in the source code.
@@
 So we can put the bitmap into a variable.
-The split operation ease the computation.
-But it also adds the limitation of max address range when we quantify the side-channel leakage shown in Table~\ref{tab:size_limitation}.
-We think the range of the memory is big enough for us to quantify the most of the cache side-channel attacks.
+The split operation eases the computation.
+However, it also adds the limitation of the max address range when we quantify the side-channel leakage shown in Table~\ref{tab:size_limitation}.
+We think the range of the memory is big enough for us to quantify most of the cache side-channel attacks.
 
@@
 The address record part is implemented as an Intel Pin tool plugin in C++ to record the bitmap for each input.
-The main component uses \textsf{libelfin}, an open source library to parse ELF binaries and read DWARF debug information.
+The main component uses \textsf{libelfin}, an open-source library to parse ELF binaries and read DWARF debug information.
 The current implementation can support  64-bits ELF binary in Linux.
@@
 \begin{itemize}
-\item \textbf{Effectiveness:} Can \ctool{} quantify the information leakage with an conservative estimation? If so, what is the loss compared it with the real leakage?
+\item \textbf{Effectiveness:} Can \ctool{} quantify the information leakage with an conservative estimation? If so, what is the loss compared with the real leakage?
 \item \textbf{Performance:} What are overhead costs of \ctool{}?
@@
 
-\textbf{Evaluation setup.} We run all the following experiment in a machine with Ubuntu 18.04 LTS.
-The machine equips with 2.30GHz Intel Core i9-9880 CPU with 16GB RAM memory.
-We use the default release settings to build the source code of the software into ELF 64-bit executables with GCC 7.5.
+\textbf{Evaluation setup.} We run all the following experiments in a machine with Ubuntu 18.04 LTS.
+The machine equips with a 2.30GHz Intel Core i9-9880 CPU with 16GB RAM memory.
+We use the default release settings to build the software's source code into ELF 64-bit executables with GCC 7.5.
 
@@
 \textit{Cryptography Applications:} Our benchmarks include the most popular cryptography libraries, such as mebdTLS, OpenSSL, Libgcropt, and wolfSSL.
-Encryption ciphers can be divided into three categories:  symmetric ciphers, and asymmetric ciphers.
+Encryption ciphers can be divided into three categories:  symmetric ciphers and asymmetric ciphers.
 For stream ciphers, we use RC4.
@@
 For cryptography programs, we run the target program with $4096$ different inputs.
-During the fuzzing process, if the program does not have new memory access bitmap after several rounds.
+During the fuzzing process, if the program does not have a new memory access bitmap after several rounds.
 We call the fuzzing step is fixed.
 From the side-channel detection aspect, it is not necessary to continue running the experiments since more rounds do not reveal new leakages.
-During the experiment, we find AES ciphers reach the fixed point after about 300 rounds and RSA can reach the fixed point after around 500 rounds.
-Previous work~\cite{217537} also reported similar result.
-During our experiment, we continue running the experiment until the observe value for the same observation is at least 5 to satisfy the Chi-square test requirement.
+During the experiment, we find AES ciphers reach the fixed point after about 300 rounds, and RSA can reach the fixed point after around 500 rounds.
+Previous work~\cite{217537} also reported a similar result.
+During our experiment, we continue running the experiment until the observed value for the same observation is at least 5 to satisfy the Chi-square test requirement.
 Therefore, we choose to run all the cipher with different inputs for $4096$ times.
@@
 However, we find they only adopt the protection in the encryption function but leave the key expansion function unprotected.
-The T-Table implementation has side-channel leakage sites in both the key expanding function and the actually encryption function.
+The T-Table implementation has side-channel leakage sites in both the key expanding function and the actual encryption function.
 
@@
 We show the result analyzed with cache line granularity.
-We compare the result with \tool{}, a symbolic analysis based side-channel quantification tool.
+We compare the result with \tool{}, a symbolic analysis-based side-channel quantification tool.
 \tool{} can tell which line in the source code actually leaks the information.
@@
 However, it is not a side-channel leakage vulnerability.
-Both tools report the leakage site can leak one bit of information.
-Third, even \tool{} reports some leakage sites leak little information, \ctool{} can report the vulnerability is severe.
+Both tools report that the leakage site can leak one bit of information.
+Third, even \tool{} reports some leakage sites to leak little information, \ctool{} can report the vulnerability is severe.
 \tool{} quantifies the amount of leaked information for one execution.
@@
 We run the chi-squared test to determine if any two leaked functions have independent leakages.
-However, we can not conclude any two leakages are independent under the chi-squared test.
+However, we can not conclude that any two leakages are independent under the chi-squared test.
 We think it is due to the avalanche effect in cryptography.
@@
 We construct a LeNet-5 model~\cite{lecun1998gradient} and trained it with the MINIST dataset.
-LeNet-5 network has six layers, including three convolutional layers, one fully connected layers and two pooling layers.
-The batch size in our experiment is 10 and the numbers of epochs is 30.
+LeNet-5 network has six layers, including three convolutional layers, one fully connected layer and two pooling layers.
+The batch size in our experiment is 10, and the number of epochs is 30.
 After the training, the accuracy of the neural networks on test set images is 99.5\%.
@@
 During the inference, we record the memory access information.
-The evaluation shows all three types of layers have different memory accesses under different inputs.
-In addition, we find that the leakages primarily comes from the activation function and the image convert function.
+The evaluation shows that all three types of layers have different memory accesses under different inputs.
+In addition, we find that the leakages primarily come from the activation function and the image convert function.
 
@@
 
-This chapter presents an approach that can give the conservative estimate of the amount of leaked information by address-based side-channel attacks.
+This chapter presents an approach that can give a conservative estimate of the amount of leaked information by address-based side-channel attacks.
 Those attacks exploit the data-flow from secrets to load address and the data-flow from the data-flow from secrets to branch conditions to retrieve secrets based on the observation on the memory accesses.
-Despite those kinds of side-channel leakages have been discovered for decades, the up-to-date software still has some side channel leakages.
+Despite those kinds of side-channel leakages that have been discovered for decades, the up-to-date software still has some side channel leakages.
 For some of those vulnerabilities, developers do not fix them because they think those side-channel vulnerabilities are not important.
 To show the importance of those side-channel leakages, one way is to demonstrate an end-to-end attack based on the vulnerability.
-However, demonstrating an end-to-end attack often need a lots of manual efforts and the domain knowledge of the victim program, which is not often the case in practices.
+However, demonstrating an end-to-end attack often need a lot of manual effort and the domain knowledge of the victim program, which is not often the case in practices.
 It is good to have a tool that can assess the severity level of those side channel leakages automatically.
@@
 They use over approximation heuristics method to quantify the leakage.
-For example, CacheAudit estimates that a 128-bit AES encryption can leaks more than 128 bits.
+For example, CacheAudit estimates that a 128-bit AES encryption can leak more than 128 bits.
 As a result, even those tool reports severe leakage, it does not mean the program has a truly severe leakage.
@@
 The channel capacity measures the information flow between the source and the destination.
-One useful characteristic of channel capacity is not affected by the distribution of the input, which is useful because in practice we can not have an assumption on the input secrets of the software.
+One useful characteristic of channel capacity is not affected by the input of the input, which is useful because we cannot assume the input secrets of the software in practice.
 In the paper, we use the sampling result to over approximate the true value of the channel capacity.
@@
 The goal of \ctool{} is to pick up those really serious side-channel vulnerabilities from the numerous vulnerabilities.
-So we do not think it is a main limitation of \ctool{}.
-However, users of \ctool{} should be aware the code coverage problem.
+So we do not think it is the main limitation of \ctool{}.
+However, users of \ctool{} should be aware of the code coverage problem.
 
@@
 Consider the example in Figure~\ref{fig:limitation}, it takes the secret as the input.
-At line 3, it calculate an index based on the value of the secret.
-Depending on the value of index, it may or may not run the code at line 6.
+At line 3, it calculates an index based on the value of the secret.
+Depending on the value of the index, it may or may not run the code at line 6.
 So line 5 is the reason that causes the vulnerability.
-But \ctool{} can only tell the line 6 can leak the information, despite it is not the root cause of the vulnerability.
+But \ctool{} can only tell that line 6 can leak the information, despite it is not the root cause of the vulnerability.

### 2021-04-22 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 \begin{itemize}
-    \item We propose a novel method that can detect and analyze the effect of each side-channel leakage sites automatically.
+    \item We propose a novel method that can detect and analyze the effect of each side-channel leakage site automatically.
 Our analysis combine the information from both the source code and the run-time execution, which makes the method more effective in finding the leakages.
@@
 We propose a method that can estimate the lower bound of information leakages.
-The theory can serve as the foundation of the future work on quantify the information leakage based on the fuzzing.
+The theory can serve as the foundation of the future work on quantifying the information leakage based on the fuzzing.
     \item We implement the above method in a tool called \ctool{} and evaluate the tool with several benchmarks and real-world applications such as OpenSSL, mbedTLS, Libgcrpyt, TinyDNN, and GTK.

### 2021-04-22 Chapter-5/Chapter-5.tex
Update Chapter-5.tex

@@
 
-Side-channel attacks can be seen as a process that refers the secret ($K$) based on the observations ($O$) shown in the figure~\ref{fig:side_channel}.
+Side-channel attacks can be seen as a process that infers the secret ($K$) based on the observations ($O$) shown in the figure~\ref{fig:side_channel}.
 As an attacker, he can observe the memory address of the victim program.

### 2021-04-25 SupplementaryMaterial/Abstract.tex
(Abstract) jim's edits

@@
 %\vspace{-0.3in}
-Side-channel vulnerabilities can leak secret information unconsciously through non-functional characteristics, e.g., time, power, and memory usage.
+Side-channel vulnerabilities can leak secret information through non-functional characteristics, e.g., time, power, and memory usage.
 Like many other software vulnerabilities, attackers exploit flaws in designs of hardware and implementations of software.
-Hardware countermeasures, which usually need changes to the complex underlying hardware, are hard to adopt in practice.
+Hardware countermeasures, which usually require changes to the complex underlying hardware, are hard to adopt in practice.
 On the contrary, software approaches are generally easy to implement.
@@
 The dissertation first introduces a new method to detect address-based side-channel vulnerabilities in the binary code.
-While existing approaches can identify side-channel leakages in real-world programs, many of them are computationally expensive and need to apply domain knowledge to simplify the analysis.
-We examine the bottleneck of current symbolic approaches and propose methods to identify side-channel vulnerabilities in real-world cryptography applications.
+While existing approaches can identify side-channel leakages in real-world programs, many these approaches are computationally expensive and need to apply domain knowledge to simplify the analysis.
+We examine the bottleneck in the symbolic approaches and propose methods to identify side-channel vulnerabilities in real-world cryptography applications.
 We implement the approach in a tool and apply it to popular cryptography libraries.
-The evaluation results confirm that the tool is much faster than the state of art tools while identifying all the known leakages reported by previous tools.
+The evaluation results confirm that the tool is much faster than state-of-art tools while identifying all the known leakages reported by previous tools.
 In addition, our tool catches new vulnerabilities that are missed by previous tools.
-We confirm those vulnerabilities with manual checks and by contacting the developers.
+We confirm those vulnerabilities with manual checking and by contacting the developers.
 
-Second, while current side-channel detection tools are able to identify numerous potential vulnerabilities.
+Second, current side-channel detection tools are able to identify numerous potential vulnerabilities.
 However, in practice, many such vulnerabilities leak a negligible amount of sensitive information, and thus developers are often reluctant to address them.
@@
 In this work, we present \ctool{}, an address-based side-channel detection and quantification tool that can quantify the side-channel leakages in a conservation but precise way.
-Contrary to previous side-channel detection tools, our approach can identify those severe side-channel leakages without false positives.
+Unlike previous side-channel detection tools, our approach can identify those severe side-channel leakages without false positives.
 Moreover, by applying the chi-squared test, our tool can estimate the total effect of multiple leakage sites as well.

### 2021-04-25 Chapter-1/Chapter-1.tex
(Introduction) Jim's edits

@@
 An attacker can infer the whole secret key by measuring the execution time of the operation.
-Since then, researchers have proposed numerous side-channel attacks which exploit numerous kinds of ``side-channel'' information, including execution timing~\cite{184415,disselkoen2017prime+}, power consumption~\cite{kar20178}, electromagnetic radiation~\cite{agrawal2002side,217605}, and even sound~\cite{chari1999towards}.
+Since then, researchers have proposed numerous side-channel attacks which exploit different kinds of ``side-channel'' information, including execution timing~\cite{184415,disselkoen2017prime+}, power consumption~\cite{kar20178}, electromagnetic radiation~\cite{agrawal2002side,217605}, and even sound~\cite{chari1999towards}.
 
-A large portion of side-channel attacks is the joint result of the underlying computer architecture design and the above software stack.
+A large portion of side-channel attacks is the joint result of the underlying computer architecture and the software stack.
 One example is cache channel attacks.
 The CPU cache is a smaller but faster memory designed to bridge the gap of the access time between the main memory and CPU registers by storing copies of recently accessed data.
-Because software may access different memory addresses when it processes different input data, and the size of the cache is significantly smaller than the size of the main memory, the CPU can only find part of the data in the cache.
-Such differences can be reflected in the differences between the program execution time.
+Because software may access different memory addresses when it processes different input data, and the size of the cache is significantly smaller than the size of the main memory, the CPU only finds part of the data in the cache.
+Such differences can be reflected in the variance in the program execution time.
 Hence we have cache side-channel attacks.
@@
 Based on the above discussion, existing countermeasures can be further divided into two categories, the hardware-based method and the software-based method.
-Hardware-level solutions, such as reducing shared resources, adopting oblivious RAM, and using transnational memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need to adopt new hardware features and make changes to today's modern complex computer systems, which are hard to adopt in reality.
-Therefore, a promising and universal direction is software countermeasures, detecting and eliminating side channel vulnerabilities (data flow from secrets to load addresses, and data flow from secrets to branch conditions) from existing code base.
+Hardware-level solutions, such as reducing shared resources, oblivious RAM, and transnational memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need to adopt new hardware features and changes in today's modern complex computer systems, which are hard to adopt in reality.
+Therefore, a promising and universal direction is software countermeasures, detecting and eliminating side-channel vulnerabilities (data flow from secrets to load addresses, and data flow from secrets to branch conditions) in existing code base.
 For example, when we examine recent side-channel attacks, many of them exploit two kinds of code patterns: \emph{secret-dependent control-flow transfers} and \emph{secret-dependent data accesses}.
@@
 \end{lstlisting}
-    \caption{Secret-dependent control-flow transfers}
+    \caption{Secret-dependent control-flow transfer}
     \label{fig:secret:cf}
@@
 Figure~\ref{fig:secret:cf} shows an example.
-Depending on the value of \textsf{secret}, the code may or may not execute the code at line 6.
-As attackers, they can retrieve some information based on the execution control-flow.
+Depending on the value of \textsf{secret}, the code may or may not execute line 6.
+An attacker can retrieve some information based on the execution control-flow.
 
@@
 
-Secret-dependent data accesses happen when the value of the secret can affect which memory cell the code reads or writes.
+Secret-dependent data accesses happen when the value of the secret can affect which memory location the code reads or writes.
 Figure~\ref{fig:secret:da} shows an example.
@@
 
-The key intuition is that the above side-channel attacks happen when a program accesses different memory addresses if the program has different sensitive inputs.
+The key intuition is that the above side-channel attacks happen when a program accesses different memory addresses with different sensitive inputs.
 As shown in Figure~\ref{fig:secret:cf} and Figure~\ref{fig:secret:da}, if a program shows different patterns in control transfers or data accesses when the program processes different sensitive inputs, the program could have side-channel vulnerabilities.
@@
 For example, cache channels can observe cache accesses at the level of cache sets~\cite{liu2015last}, cache lines~\cite{184415} or other granularities~\cite{yarom2017cachebleed}.
-Other types of side-channel attacks like controlled-channel attack~\cite{7163052}, can observe the memory access at the level of memory pages.
+Other types of side-channel attacks such as controlled-channel attack~\cite{7163052}, can observe a memory access at the level of memory pages.
 So a natural defense approach is to remove the above code patterns in the software.
@@
 As a non-functional property, it can be difficult for programmers to reason about or test.
-While recent work~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} can detect many side-channel vulnerabilities, they either suffer from expensive computation costs or high false positives and false negatives.
-Many of those reported vulnerabilities have not been fixed by developers for a variety of reasons.
+While recent work~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} can detect many side-channel vulnerabilities, it either suffers from expensive computation costs or high false positives and false negatives.
 Second, most vulnerabilities pose a negligible risk.
-Although some vulnerabilities result in the key being compromised~\cite{184415, aumuller2002fault} entirely, many others are less severe in reality.
+Although some vulnerabilities result in the key being entirely compromised~\cite{184415, aumuller2002fault}, many others are less severe in reality.
 Therefore, we need a proper quantification metric to assess the sensitivity of side-channel vulnerabilities, so a developer can efficiently triage them.
 Third, many side-channel vulnerable implementations (e.g., the CRT optimization and lookup tables) have better performance.
-It is a dilemma between the performance and the security.
+This is a dilemma between the performance and the security.
 
@@
 In general, many side-channel vulnerabilities are low-level problems.
-Control-flows or memory accesses may not be side-channel vulnerabilities if they are independent of original secret inputs.
+Control-flows or memory accesses may not be side-channel vulnerabilities if they are independent of the secret inputs.
 Recent work can identify side-channel leakages.
-But those tools can only work on small programs or need to apply some domain knowledge of the target program to simplify the analysis.
+But those tools can only work on small programs or need to apply domain knowledge of the target program to simplify the analysis.
     \item Side-channel vulnerabilities are ubiquitous.

### 2021-04-26 Chapter-1/Chapter-1.tex
(Jim's edits) Introduction

@@
     \item \textbf{Detection.} We propose a fast and precise side-channel detection method.
-Different from previous trace comparison based methods, our method has fewer false positives and false negatives.
-Compared with methods based on symbolic execution and abstract interpretation, our methods can apply on real-world cryptography libraries directly.
+Unlike previous trace-comparison methods, our method has fewer false positives and false negatives.
+Compared with methods based on symbolic execution and abstract interpretation, our methods can be applied to real-world cryptography libraries directly.
 Symbolic execution provides fine-grained information, but it is expensive to compute.
@@
 We examine the bottleneck of the trace-oriented symbolic execution and optimize it to work on real-world applications.
-    \item \textbf{Quantification.} We propose methods to quantify the amount of information leakage precisely that an attacker can retrieve during side-channel attacks.
+    \item \textbf{Quantification.} We propose methods to quantify precisely the amount of information leakage that an attacker can retrieve during side-channel attacks.
 For the first project, we define the amount of leaked information as the cardinality of possible secrets based on an attacker's observation.
@@
 First, we propose a novel method that can detect side-channel vulnerabilities in real-world applications fast and precisely.
-Second, we propose methods that can quantify each side-channel leakages precisely.
-In addition, we study two kinds of threat models, single-trace attacks, and multiple-trace attacks.
+Second, we propose methods that can quantify precisely each side-channel leakages.
+In addition, we study two kinds of threat models: single-trace attacks, and multiple-trace attacks.
 In summary, we make the following contributions:
@@
 \begin{itemize}
-    \item We designs a symbolic analysis method that can detect secret-dependent control-flow transfers and secret-dependent data accesses.
+    \item We design a symbolic analysis method that can detect secret-dependent control-flow transfers and secret-dependent data accesses.
 The key idea is to only symbolically execute those machine instructions that are relevant to vulnerabilities while executing other instructions natively.
@@
 We do not need to apply domain knowledge to analyze part of the original program, which simplify the analysis.
-In addition, \detect{} yields new leakages which are not identified by previous tools.
-We confirm those findings with developers.
+In addition, \detect{} finds new leakages which are not identified by previous tools.
+We confirmed those findings with developers.
 \end{itemize}
@@
     \item We propose a method that can quantify fine-grained leaked information from side-channel vulnerabilities that result from actual attack scenarios in a single trace attack.
-Our approach differs from previous ones in that we precisely calculate the amount of leakages.
+Our approach differs from previous ones in that we precisely calculate the amount of leakage.
 We model the information quantification problem as a counting problem and use a Monte Carlo sampling method to estimate the information leakage.
@@
 Our results are useful in practice.
-The leakage estimates and the corresponding inputs that triggers the vulnerability can help developers to triage and fix the vulnerabilities.
+The leakage estimates and the corresponding inputs that triggers the vulnerability can help developers triage and fix the vulnerabilities.
 \end{itemize}
@@
     \item We propose a novel method that can detect and analyze the effect of each side-channel leakage site automatically.
-Our analysis combine the information from both the source code and the run-time execution, which makes the method more effective in finding the leakages.
-By running the chi-squared test, the method can find independent leakages.
+Our analysis combines the information from both the source code and the run-time execution, which makes the method more effective in finding the leakages.
+By applying a chi-squared test, the method can find independent leakages.
 Attackers can combine multiple leakage sites to retrieve more information as well.

### 2021-04-26 Chapter-2/Chapter-2.tex
(Related work) Jim's edits

@@
 While there are many kinds of side-channel attacks, we focus on address-based side-channel attacks in this dissertation.
-Address-based side-channel attacks happen when a program accesses different memory locations when it processes different secrets.
-In modern computer systems, an attacker may shares some hardware resources (e.g., Cache, TLB, and DRAM) with the victim~\cite{ge2018survey,szefer2019survey}.
+Address-based side-channel attacks happen when a program accesses different memory locations as it processes different secrets.
+In modern computer systems, an attacker may share hardware resources (e.g., Cache, TLB, and DRAM) with the victim~\cite{ge2018survey,szefer2019survey}.
 An attacker can probe the shared hardware resource to infer the memory accesses of the victim.
@@
     \centering
-    \caption{Due to the page limit, we only show some representations of the vast side-channel attacks: Attacks, the shared resources with attackers, the granularity of the attacker can observe, is there any published attacks on the non-cryptography library, and if the type of attack has been used to exploit multiple leakage sites.}
+    \caption{Due to the page limit, we only show some representations of the vast side-channel attacks: the shared resources with attackers, the granularity of the attacker can observe, is there any published attacks on non-cryptography libraries, and if the type of attack has been used to exploit multiple leakage sites.}
     \label{table:side_channel_attack}
@@
 
-Cache channels~\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last,184415} rely on the time difference between cache misses and cache hits.
+Cache channels~\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last,184415} rely on the time difference between a cache miss and cache hit.
 The core-private caches (e.g., L1 and L2) are traditionally set-associate cache.
@@
 An attacker primes the cache set with its own data and waits until the victim executes the program.
-After that, the attacker probes the cache by reading previously loaded data.
+Then the attacker probes the cache by reading previously loaded data.
 If the victim accesses the cache set and evicts some lines of the data, the attacker will experience a slow measurement.
-Under the circumstance, the attacker can know the victim must have touched some data that map to the same cache set.
+Under the circumstance, the attacker can know that the victim must have touched some data that map to the same cache set.
 
@@
 During the ``flush'' stage, the attacker flushes the ``monitored
-memory'' from the cache and waits for the victim to access the memory, who may load the sensitive information to the cache line.  In the next phase,
+memory'' from the cache and waits for the victim to access the memory, which may be a load of the sensitive information to the cache line.  In the next phase,
 the attacker reloads the ``monitored memory''.
@@
 A malicious OS can proactively revoke a virtual enclave memory page from the virtual memory.
-If the victim enclave program accesses the memory table, then the OS can observe the page faults and know which page is accessed.
+If the victim enclave program accesses the memory in the  page, then the OS can observe the page faults and know which page is accessed.
 While the granularity of the controlled-channel attacks is more coarse-grained compared with cache channel attacks, controlled-channel attacks allow the attacker to have a noise-free observation.
-Other examples like the TLB side-channel attack and DDRAM attacks share the same page-level granularity.
+Other examples include the TLB side-channel attack and DDRAM attacks share the same page-level granularity.
 
 Based on the above discussion, we consider three types of granularities in the dissertation: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs).
-To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in the literature.
+To the best of our knowledge, these three types of granularities can cover most of the side-channel attacks in the literature.
 
@@
 Since the attacker can probe the victim program after the execution, the attacker does not know the order of memory accesses.
-Access-based attacks often happen in the cloud computing environment when the attacker and victim share the same hardware (e.g., LLC Cache).
+Access-based attacks often happen in the cloud computing environment when the attacker and victim share the same hardware (e.g., LLC cache).
 Examples of those attacks include cache template attacks~\cite{191010}, Prime and Probe attacks~\cite{liu2015last}, and Flush and Reload attacks~\cite{yarom2014flush+}.
@@
 In a trace-based attack, the attacker can know the execution sequence of two functions (e.g., $aabbb$).
-Controlled-channel attacks~\cite{moghimi2020copycat, xu2015controlled} belong to the category where a malicious operating system can interrupt the victim applications and probe the program at any time.
+Controlled-channel attacks~\cite{moghimi2020copycat, xu2015controlled} belong to the category where a malicious operating system can interrupt the victim application and probe the program at any time.
 In general, the trace-based attack has the strongest assumption about the threat model,  but it can retrieve more information compared to the other two types of attacks.
@@
 There is a vast number of studies\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last} on side-channel attacks.
-Most early work targets retrieving encryption keys from cryptography libraries.
+Most early work targeted retrieving encryption keys from cryptography libraries.
 In recent years, researchers start to focus on more general and diverse applications.
-In summary,  the target applications of current side-channel attacks can be classified into the below three categories.
+In summary,  the target applications of current side-channel attacks can be classified into three categories.
 
@@
 Those ciphers have a lot of big number calculations.
-It is hard to implement those calculations completely side-channel resistant.
+It is hard to implement those calculations to be completely side-channel resistant.
 Recent work~\cite{arnaud2013timing,yarom2017cachebleed,yarom2014flush+} has demonstrated several end-to-end attacks to recover the private key of those ciphers.
@@
 Hua et al.~\cite{hua2018reverse} were the first in the literature to reverse engineer the architecture of convolutional neural networks (CNNs) through the memory access patterns.
-Wei et al.~\cite{wei2018know} perform the side-channel attacks on an FPG-based convolution neural network based on the power consumption to recover inputs to the networks.
+Wei et al.~\cite{wei2018know} perform the side-channel attacks on an FPG-based convolution neural network by using the power consumption to recover inputs to the networks.
 For an image classification task trained by the MNIST dataset, their attacks can achieve up 89\% accuracy.
-CSI NN~\cite{batina2019csi} reverse engineer the multi-layer perception and convolution neural network based on the electromagnetic signals (EMs).
+CSI NN~\cite{batina2019csi} reverse engineered the multi-layer perception and convolution neural network based on the electromagnetic signals (EMs).
 Cache Telepathy~\cite{yan2020cache} introduces the cache-based side-channel attack to extract DNNs' architectures.
@@
 In the controlled-channel attack~\cite{xu2015controlled}, Yuanzhong et al.
-demonstrate an attack to recover the outline of the image by exploiting the vulnerability in the inverse DCT function in libjpeg.
-Daimeng et al.~\cite{wang2019unveiling} present the cache attack in graphic libraries.
-Their approaches combine a machine learning approach to pick cache lines that can be exploitable to leak the most information.
+demonstrate an attack to recover the outline of an image by exploiting the vulnerability in the inverse DCT function in libjpeg.
+Daimeng et al.~\cite{wang2019unveiling} present a cache attack on graphic libraries.
+Their approaches uses a machine learning approach to pick cache lines that can be exploitable to leak the most information.
 \subsubsection*{Others}
 Some other side-channel targets also include spelling checking tools and font libraries~\cite{xu2015controlled}.
-The attack on font libraries is essentially the same as the attack on the graphic library like GDK.
+The attack on font libraries is essentially the same as the attack on the graphic library GDK.
 By exploiting the differences of memory accesses when the program renders different characters, an attacker can recover parts of the original sensitive information.
@@
 In general, the approach is quite fast.
-On the negative side, comparing the trace along can find the leakage, but it cannot find the complex relationship between the leakage site and the original secret input.
-For example, if two leakage sites leak the same information, those approaches cannot find out the two leakage sites are the same.
+On the negative side, comparing the trace can find the leakage, but it cannot find the complex relationship between the leakage site and the original secret input.
+For example, if two leakage sites leak the same information, these approaches cannot find out the two leakage sites are the same.
 
 \textbf{Abstraction.} The second category of those tools belongs to the field of abstractions.
-Tools based on those approaches use abstraction to generate approximations to model the semantics of computer programs.
-After that, by analyzing the model, those tools can identify side-channel leakages.
+Tools based on these approaches use abstraction to generate approximations to model the semantics of computer programs.
+After that, by analyzing the model, these tools can identify side-channel leakages.
 Compared with the trace comparison approach, the method is more precise.
 
-Those methods usually follow the below steps.
+Those methods usually follow the steps below.
 Suppose a program $P$ has $k$ as the input.
-Those approaches first retrieve the relationship between the $k$ and temperate values during the execution.
+Those approaches first retrieve the relationship between the $k$ and temporary values during the execution.
 After that, they should have a cache or memory access model and model the side-channel leakage as a math constraint.
 By using SMT solvers to find different secret inputs that lead accesses to different locations in the memory or the cache, those approaches can determine if the program is vulnerable to side-channel attacks.
-Contrary to the trace comparison, the method is quite precise.
+Unlike to the trace comparison, the method is quite precise.
 Moreover, it can model multiple leakages precisely as the conjunction of those formulas.
-However, such approaches have the following limitations.
+However, these approaches have the following limitations.
 
@@
 However, such non-linear arithmetics are quite common in cryptography algorithms.
-Recent studies show existing solvers still have plenty of bugs when it deals with real number calculations.
+Recent studies show existing solvers still have bugs when dealing with real number calculations.
 Those calculations are also common in media libraries and machine learning applications.
@@
 
-The dynamic approach, usually consists of taint analysis and symbolic execution,
+The dynamic approach, usually consisting of taint analysis and symbolic execution,
 can perform a very precise analysis. CacheD~\cite{203878} takes a concrete execution trace and runs symbolic execution on the trace
-to get the formula of each memory address. CacheD is
+to get a formula for each memory address. CacheD is
 quite precise in avoiding false positives.
@@
     %\centering
-    \caption{Existing leakage detection tool only evaluate them on cryptography library.
-1.
-Most recent work only evaluates their approaches on cryptography libraries.
-2.
-All of them can not reason about the total effect of multiple leakages.}
+    \caption{Many leakage detection tools are only evaluated on cryptography libraries.  All of them can not reason about the total effect of multiple leakages.}
     \label{table:side_channel_detection_tool}
@@
 accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
-architecture~\cite{tiwari2011crafting}, require changes to complex processors and are complex to adopt. On the contrary, software approaches are
+architecture~\cite{tiwari2011crafting}, require changes to complex processors and are difficult to adopt. On the contrary, software approaches are
 usually easy to implement. Coppens et
@@
 to eliminate key-dependent control-flow transfers. Crane et
-al.~\cite{crane2015thwarting} mitigated side-channels by randomizing software.
+al.~\cite{crane2015thwarting} mitigates side-channels by randomizing software.
 As for crypto libraries, the basic idea is to eliminate key-dependent
@@
 Proposed by Denning~\cite{robling1982cryptography} and Gray~\cite{gray1992toward},
-Quantitative Information Flow (QIF) aims at providing an estimation of the amount of leaked information from the sensitive information given the public output. If zero bits
+Quantitative Information Flow (QIF) aims to provide an estimation of the amount of leaked information from the sensitive information given the public output. If zero bits
 of the information are leaked, the program is called non-interference. 
@@
 Despite the rapid development of model counters for SAT and some
-research~\cite{chistikov2017approximate,phan2015model}, existing tools cannot be directly applied to side-channel leakage quantification for the following two reasons.
+research~\cite{chistikov2017approximate,phan2015model}, existing tools cannot be directly applied to side-channel leakage quantification.
 ApproxFlow~\cite{biondi2018scalable} uses ApproxMC~\cite{chakraborty2016algorithmic} for information flow quantification, but it has only been tested with small programs.
@@
 as many paths as possible. Compared to static analysis, trace-based analysis
-is usually more precise as it can incorporate the runtime information. It usually has
+is usually more precise as it can incorporate runtime information. It usually has
 two steps. The first step is collecting trace information. Existing
@@
 The target program's data can be modified directly in memory, which is useful to tasks like fuzzing because the analysis
-can force the program to execute a specific branch. Contrary to online analysis,
-offline analysis or post-analysis happens when the program finishes executions. 
+can force the program to execute a specific branch. 
+Offline analysis or post-analysis happens after the program finishes executions. 
 Trace-based binary analysis has been adopted in several tasks like algorithm
@@
 
-There are several known binary analysis frameworks that can ease users to launch analysis on binary executables.
+There are several known binary analysis frameworks that can help users to launch analysis on binary executables.
 BitBlaze~\cite{brumley2011bap} is a binary analysis platform that provides both static and dynamic analysis.
@@
 All IR must be interpreted no matter if symbolic variables are involved or not.
-Besides, as side-channels are low-level problems in general, the IR design will also lose some information.
+As side-channels are low-level problems in general, the IR will lose some information.
 For example, IR-level branches are not necessarily a super-set or a sub-set of machine-code level branches.

### 2021-04-26 Chapter-3/Chapter-3.tex
(Chapter 3) Jim's edits

@@
 
-The cause of most side-channel attacks can been as the combination of the hardware design and the vulnerable software.
+The cause of most side-channel attacks is the combination of the hardware design and the vulnerable software.
 Existing countermeasures can be classified into two categories: fixing the software and adopting new hardware.
 Based on the discussion in \S\ref{chapter1} and \S\ref{chapter2}, fixing side-channel leakage sites in software is usually easier than adopting new hardware to defend against side-channel attacks.
-In order to eliminate those leakage sites, developers need to find potential leakage sites from the large code base manually.
+In order to eliminate those leakage sites, developers need to find potential leakage sites in a large code base.
 However, the manual process is tedious and error-prone.
@@
 Recent work has made good progress in detecting side-channel leakages automatically.
-Some tools (e.g., CacheD~\cite{203878}, CaSym~\cite{Brotzman19Casym}) have successfully identified unknown leakage sites from software products automatically.
-However, those tools have the following limitations.
+Some tools (e.g., CacheD~\cite{203878}, CaSym~\cite{Brotzman19Casym}) have successfully identified unknown leakage sites in software products automatically.
+However, those tools have limitations.
 
 First, although some tools~\cite{Brotzman19Casym} can find side-channel leakages in real-world software products, they can only analyze one code fragment at a time due to the expensive performance overhead.
-As a result, users of those tools sometimes need to cut off some irrelevant code based on their experience manually.
+As a result, users of those tools sometimes need to cut off manually irrelevant code based on their experience.
 The trimming process is tedious and needs domain knowledge of the target software (e.g., which part of the code is more likely to have side-channel leakage sites).
@@
 It is a design decision to facilitate the implementations.
-While analyzing the IRs can simplify the implementation, it is not a suitable design choice for the side-channel analysis.
-In reality, side-channel leakages are a pretty low-level issue and only the low-level analysis can give the most accurate results.
+While analyzing the IRs can simplify the implementation, it is not suitable for side-channel analysis.
+Side-channel leakages are a pretty low-level issue and only the low-level analysis can give the most accurate results.
 For example, the IR-level branches are not necessarily a superset or a subset of machine-code level branches.
-Besides, compiler optimizations can eliminate the IR-level branches like conditional moves and the converse could also happen.
+Besides, compiler optimizations can eliminate the IR-level branches with conditional moves, and the converse could also happen.
 Moreover, translating the machine code into IRs can cause a significant overhead for the trace analysis, as we will discuss in the dissertation.
@@
 We examine the bottleneck of current symbolic execution approaches and optimize it to work on real-world cryptography systems.
-Different from previous methods, our tool analyzes the machine instructions, which can give more precision than traditional IR-based approaches.
+Unlike previous methods, our tool analyzes the machine instructions, which can give more precision than traditional IR-based approaches.
 We evaluate our tool on popular cryptography libraries including OpenSSL, mbedTLS, Libgcrypt, and Monocypher.
-The evaluation results show that our tool can identify previous side-channel leakages, as well as find new leakages.
+The evaluation results show that our tool can identify previous side-channel leakages as well as find new leakages.
 Compared with recent tools, our tool is 3-100x faster while finding all the leakages when we evaluate on the same benchmarks.
-In addition, our tool finds new side-channel vulnerabilities that are missed by the previous work.
+In addition, our tool finds new side-channel vulnerabilities missed by the previous work.
 
@@
 
-During the evolution of the computer architecture, researchers find that CPUs process data in a much faster speed than the main memory (DRAM) can supply.
-As a result, CPUs adopt a hierarchy memory architecture to bridge the performance gap between the CPUs and the main memory.
+During the evolution of the computer architecture, researchers found that CPUs process data much faster than the main memory (DRAM) can supply.
+As a result, CPUs adopted a hierarchy memory architecture to bridge the performance gap between the CPUs and the main memory.
 By storing extra copies of recently accessed data and code in a smaller but faster memory, the software can get its most recently accessed code and data in a shorter time.
@@
 For a CPU with multiple cores, each core has two private level-1 (L1) cache, an instruction cache (iCache), and a data cache (dCache).
-Because instructions and data have different access patterns, separating iCache and dCache makes it possible for CPUs to fetch the code and data and improve performance simultaneously.
+Because instructions and data have different access patterns, separating iCache and dCache makes it possible for CPUs to fetch the code and data simultaneously and improve performance.
 Followed by the level-1 cache, each core also has the unified private level-2 cache for both the code and the data.
@@
 The LLC is shared among all the cores.
-The main memory is in the bottom-most under the memory hierarchy.
+The main memory is at the bottom of the memory hierarchy.
 \begin{figure}[ht]
@@
 The current computer memory hierarchy opens the way for side-channel attacks from two aspects.
-First, the architecture relies on the system software for managing the memory, which becomes a problem in a threat model where the operating system is not untrusted (e.g., Intel SGX).
+First, the architecture relies on the system software to manage the memory, which becomes a problem in a threat model when the operating system is not untrusted (e.g., Intel SGX).
 Second, the size of the cache is smaller than the main memory.

### 2021-04-26 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 Libgcrypt is a cryptographic library from the GunPG.
-As some previous work (e.g., CacheD) choose to evaluate their tools on CacheD, we can compare the evaluation results by applying the tool on Libgcrypt.
+As some previous work (e.g., CacheD) choose to evaluate their tools on Libgcrypt, we can compare the evaluation results by applying the tool on Libgcrypt.
 

### 2021-04-26 Chapter-5/Chapter-5.tex
Update Chapter-5.tex
Updates from Overleaf

@@
 Side-channel attacks allow attackers to infer sensitive information based on the non-functional behaviors of the computer system.
-Examples of those non-functional behaviors include acoustics, CPU usages, timing, EM signals, etc~\cite{agrawal2002side,hund2013practical,halevi2015keyboard,batina2019csi}.
+Examples of these non-functional behaviors include acoustics, CPU usages, timing, EM signals, etc~\cite{agrawal2002side,hund2013practical,halevi2015keyboard,batina2019csi}.
 In summary, if the program has different execution behaviors when it processes various keys, an attacker can infer nontrivial information by observing those secret-dependent behaviors.
-While separate side-channel attacks may have different forms and patterns, we find a large portion of them share the same fundamental reasons.
+While separate side-channel attacks may have different forms and patterns, we find that a large portion of them share the same fundamental reasons.
 That is, the memory access pattern is dependent on the original sensitive input.
@@
 
-\textit{Cryptography Applications:} Our benchmarks include the most popular cryptography libraries, such as mebdTLS, OpenSSL, Libgcropt, and wolfSSL.
+\textit{Cryptography Applications:} Our benchmarks include the most popular cryptography libraries, such as mebdTLS, OpenSSL, Libgcrypt, and wolfSSL.
 Encryption ciphers can be divided into three categories:  symmetric ciphers and asymmetric ciphers.

### 2021-04-26 SupplementaryMaterial/Vita.tex
Updates from Overleaf

@@
 
-    \item \textbf{Qinkun Bao}, Zihao Wang, James Larus, and Dinghao Wu, ``Quincunx: Measuring Side-channel Vulnerabilities
+    \item \textbf{Qinkun Bao}, Zihao Wang, James Larus, and Dinghao Wu, ``Measuring Side-channel Vulnerabilities
     By Fuzzing and Memory Auditing'', under review.
@@
     \item \textbf{Qinkun Bao}, Zihao Wang, Quan Li, and Dinghao Wu, ``Fast Semantic-aware Function Recognition in Obfuscated Binaries'', under review.
+
+    \item Zihao Wang, Pei Wang, \textbf{Qinkun Bao}, and Dinghao Wu, ``Inferring Complex Grammars with Static Program Analysis'', under review.
 

### 2021-04-28 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 Those tools can give an upper bound estimation of each leakage site, which is useful to justify the software is secure if the reported leakage is zero.
-But those tools can not tell software developers how serious each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage.
+But those tools can not tell software developers how severe each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage.
 The best way to estimate each leakage's severe level is to exploit the leakage and recover the information.
@@
 
-\subsection{Threat Model and Math Notation}
+\subsection{Threat Model and Notation}
 
@@
   \end{minipage}
-  \caption{A serious leakage.}\label{chapter5:fig:example1}
+  \caption{A severe leakage.}\label{chapter5:fig:example1}
 \end{figure}
@@
 However, \ctool{} is not designed to find side-channel vulnerabilities.
-The goal of \ctool{} is to pick up those really serious side-channel vulnerabilities from the numerous vulnerabilities.
+The goal of \ctool{} is to pick up those really severe side-channel vulnerabilities from the numerous vulnerabilities.
 So we do not think it is the main limitation of \ctool{}.

### 2021-04-29 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-Accordingly, if Definition~\ref{chapter5:def} says the vulnerability leakage has $m$ bits of leakages, then the vulnerability can have at least $m$ bits of leakages.
+Accordingly, if Definition~\ref{chapter5:def} says the vulnerability leakage has $m$ bits of leakages, then the vulnerability leaks at least $m$ bits of leakages.
 We can use the definition to detect those severe leakages.

### 2021-05-11 SupplementaryMaterial/Abstract.tex
Updates from Overleaf

@@
 Our results demonstrate that most reported vulnerabilities are difficult to exploit in practice and should be de-prioritized by developers.
-The evaluation results shows that our method can successfully distinguish severe leakages from many negligible leakages.
+The evaluation results show that our method can successfully distinguish severe leakages from many negligible leakages.
 
@@
 Our evaluation results show \ctool{} is effective in identifying and quantifying side-channel leakages.
+
+This dissertation research develops fundamental and practical techniques for precise side-channel 
+analysis in software systems. We have also open sourced our research software prototypes.
+As a result, developers can use our tools to develop more secure systems and the academic and industry
+communities can further advance side channel analysis on top of our research.

### 2021-05-14 SupplementaryMaterial/Vita.tex
Updates from Overleaf

--- 2021-04-21 SupplementaryMaterial/Vita.tex
@@
 
-Qinkun Bao is a fifth-year Ph.D. student at the College of Information Sciences
-and Technology, The Pennsylvania State University. He is a member of the Software 
-System Security Research Lab, where he works under the supervision of Dr. Dinghao Wu.
+Qinkun Bao earned his Ph.D. at the College of Information Sciences
+and Technology, The Pennsylvania State University. He was a member of the Software 
+System Security Research Lab, where he worked under the supervision of Dr. Dinghao Wu.
 His research interests span reverse engineering, binary analysis, and trusted computing.
 Before he went to Penn State, he received his bachelor's degree in Electronic Engineering and Information Science from University of Science and Technology of China.
-
-  \section*{Publications}
-  \begin{enumerate}
-    \item \textbf{Qinkun Bao}, Zihao Wang, Xiaoting Li, James Larus, and Dinghao Wu, ``Abacus: Precise Side-Channel Analysis'', In \emph{Proceedings of the 43rd International Conference on Software Engineering (ICSE 2021)}.
-(Technical Track)
-    \item \textbf{Qinkun Bao}, Zihao Wang, James Larus, and Dinghao Wu, ``Abacus: A Tool for Precise Side-Channel Analysis'', In \emph{Proceedings of the 43rd International Conference on Software Engineering: Companion (ICSE-Companion 2021)}.
-(Artifact)
-
-    \item \textbf{Qinkun Bao}, Zihao Wang, James Larus, and Dinghao Wu, ``Quincunx: Measuring Side-channel Vulnerabilities
-    By Fuzzing and Memory Auditing'', under review.
-
-    \item \textbf{Qinkun Bao}, Zihao Wang, Quan Li, and Dinghao Wu, ``Fast Semantic-aware Function Recognition in Obfuscated Binaries'', under review.
-
-    \item Shixiong Jing, \textbf{Qinkun Bao}, Pei Wang, Xulong Tang, and Dinghao Wu, ``Characterizing AI Model Inference Applications Running in SGX Environment'', under review.
-
-    \item Yufei Jiang, \textbf{Qinkun Bao}, Xiao Liu, and Dinghao Wu, ``RedDroid: Android Application Redundacy Customization based on Static Analysis'', in \emph{Proceedings of the 29th IEEE International Symposium on Software Reliability Engineering (ISSRE 2018)}, Memphis, TN, October 15-18, 2018
-
-\item Pei Wang, \textbf{Qinkun Bao}, Li Wang, Shuai Wang, Zhaofeng Chen, Tao Wei, and Dinghao Wu, ``Software Protection On-The-Go: An Empirical Study on Mobile App Obfuscation'', in \emph{Proceedings of 40th International Conference on Software Engineering (ICSE 2018)}, Gothenburg, Sweden, May 27-June 3, 2018
-
-\item Shengru Li, Kai Han, Nirwan Ansari, \textbf{Qinkun Bao}, Daoyun Hu, Junjie Liu, Shui Yu, and Zuqing Zhu, ``Improving SDN Scalability with Protocol-Oblivious Source Routing: A System-Level Study'', \emph{IEEE Transactions on Network and Service Management}, vol.
-15, no.
-1, pp.
-275-288, March 2018
-
-\item Shuai Wang, Wenhao Wang, \textbf{Qinkun Bao}, Pei Wang, Xiaofeng Wang, and Dinghao Wu, ``Binary Code Retrofitting and Hardening Using SGX'', in \emph{Proceedings of the 2017 workshop on Forming an Ecosystem Around Software Transformation (FEAST17)}, co-located with CCS 2017, Dallas, USA, November 3, 2017
-\end{enumerate}

### 2021-05-18 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 The CPU cache is a smaller but faster memory designed to bridge the gap of the access time between the main memory and CPU registers by storing copies of recently accessed data.
-Because software may access different memory addresses when it processes different input data, and the size of the cache is significantly smaller than the size of the main memory, the CPU only finds part of the data in the cache.
+Because software may access different memory addresses when it processes different input data, and the size of the cache is significantly smaller than the size of the main memory, the CPU may only find part of the data in the cache.
 Such differences can be reflected in the variance in the program execution time.
@@
 Based on the above discussion, existing countermeasures can be further divided into two categories, the hardware-based method and the software-based method.
-Hardware-level solutions, such as reducing shared resources, oblivious RAM, and transnational memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need to adopt new hardware features and changes in today's modern complex computer systems, which are hard to adopt in reality.
+Hardware-level solutions, such as reducing shared resources, oblivious RAM, and transnational memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need to adopt new hardware features and change  today's modern complex computer systems, which are hard to adopt in reality.
 Therefore, a promising and universal direction is software countermeasures, detecting and eliminating side-channel vulnerabilities (data flow from secrets to load addresses, and data flow from secrets to branch conditions) in existing code base.

### 2021-05-18 Chapter-3/Chapter-3.tex
reorganizing the repo

@@
 This indicates that \detect{} is effective for validating countermeasures.
-
-\section{Discussion}
-
-\textbf{Coverage.} \detect{} works on native x86 execution traces.
-The design, which is very precise in terms of true leakages compared to other static source code method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also share the common limitations of dynamic approaches.
-\detect{} may only cover part of the code.
-Each time we only get one single execution trace.
-Therefore, we may neglect some side-channel vulnerabilities not covered by the traces analyzed.
-However, this is not a crucial problem for analyzing cryptographic libraries, because cryptographic libraries are designed to have the same code coverage for various inputs.
-Our evaluation also confirms the above intuition.
-For symmetric encryption, there is no secret-dependent control-flow transfers during our evaluation.
-RSA implementations have several secret-dependent control-flow transfers.
-Many of them are bound checks, which do not leak much information and have negligible effects on the whole code coverage as well.
-
-\textbf{Design Choices.} At the early stage of the project, we use SMT solvers to get the solutions of constraints.
-However, we find for some ciphers (RSA), \detect{} times out after several days.
-The profiling result shows that it is spending most its time in Z3.
-Later, we use a sampling method to detect side-channel leakages.
-The sampling method seems simple and may miss some leakages in theory.
-However, the evaluation result shows \detect{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.
-
-\textbf{Cache Model.} We use a simple cache model in this work.
-Recent work~\cite{Brotzman19Casym,182946} uses an LRU cache.
-First, there is no fundamental difficulties for us to adopt a more realistic cache models.
-Second, the LRU model is still a substantial simplification of a real cache.
-However, the choice of a logical model of cache can bring expensive overheads.
-
-\textbf{Leakages.} While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers.
-The DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort.
-After we manually analyze those leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which partially explain why developers are not interested in fix all the leakages.

### 2021-05-18 Chapter-4/Chapter-4.tex
Updates from Overleaf
reorganizing the repo

@@
 \subsubsection*{Lookup Table}
-\begin{figure}
+\begin{figure}[h]
 \centering
@@
 \tool{} identifies the leakage site in the left figure successfully and estimates the amount of leakage is $16$ bits.
-
-\section{Discussion}
-While recent work found many side-channel vulnerabilities,
-we note that many of them have not been patched by developers.
-Side-channels are ubiquitous in software and it would be difficult to fix all of them.
-We need a tool that estimates the sensitivity of each vulnerability
-so software engineers can focus on
-``severe'' leakages. For example, \tool{} reports that
-the modular exponentiation using square and multiply algorithms can
-leak more information than a key validation function.
-
-Software developers can use \tool{} to find severe vulnerabilities
-and reason about countermeasures.
-\tool{} estimates the amount of leaked information for each side-channel leakage
-in one execution trace. \tool{} is useful for software
-engineers to test programs and fix vulnerabilities.
-The design, which is more precise in reporting true leakages as compared with other static
-methods~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, obviously misses
-leakages on unexplored traces. The amount of leaked information also depends on the secret key.
-However, as the tool is intended for debugging and testing,
-we think it is a software engineer's responsibility to select the input key and trigger
-the path in which they are interested. It is not a problem for crypto software
-since virtually all keys follow similar computational paths.
-
-We use the amount of leaked information to represent the sensitivity level of
-each side-channel vulnerability. Although imperfect, \tool{} produces a reasonable
-measurement for each leak. For example, the simple modular exponentiation is
-notoriously famous for multiple side-channel attacks~\cite{kocher1996timing}.
-During the execution, a single leak point may execute multiple times
-and each time leak a different bit. In this case, \tool{} reports that the
-vulnerability can leak the whole key. However, not every leak point inside a
-loop is severe. If a site in the loop leaks the same bit from the
-original key, and these leaks are not independent. \tool{} captures most
-fine-grained information by modeling each leak during the execution as a
-formula and the conjunction of the formulas to describe its total effect.
-Some leakage sites (e.g., square and multiply)
-can leak one particular bit of the original key, but some leakage sites leak one bit
-from several bytes in the original key. \tool{} can capture the dependency among the leaks and
-reports more precise leakage information.
-
-\tool{} reaches full precision if the number of estimated leaked bits
-equals to Definition~\ref{chapter4:def}.
-\tool{} may lose precision from the
-memory model it uses in theory. However, we did not find false positives
-caused by the imprecise memory model during our evaluation.
-Sampling introduces imprecision but with a probabilistic guarantee.
-However, during the evaluation, we find that \tool{} cannot estimate
-the amount of leakage for some leakage sites in a reasonable time,
-which means the number of $K^o$ is very small. According to Definition~\ref{chapter4:def}, it means the leakage is very severe.

### 2021-05-18 Chapter-5/Chapter-5.tex
reorganizing the repo

@@
 In addition, we find that the leakages primarily come from the activation function and the image convert function.
-
-\section{Discussion}
-
-This chapter presents an approach that can give a conservative estimate of the amount of leaked information by address-based side-channel attacks.
-Those attacks exploit the data-flow from secrets to load address and the data-flow from the data-flow from secrets to branch conditions to retrieve secrets based on the observation on the memory accesses.
-Despite those kinds of side-channel leakages that have been discovered for decades, the up-to-date software still has some side channel leakages.
-For some of those vulnerabilities, developers do not fix them because they think those side-channel vulnerabilities are not important.
-To show the importance of those side-channel leakages, one way is to demonstrate an end-to-end attack based on the vulnerability.
-However, demonstrating an end-to-end attack often need a lot of manual effort and the domain knowledge of the victim program, which is not often the case in practices.
-It is good to have a tool that can assess the severity level of those side channel leakages automatically.
-So it would be better to have a proper metric to quantify the side-channel leakage.
-However, we find previous side-channel quantification tools are developed to ensure the noninterference of the program.
-They use over approximation heuristics method to quantify the leakage.
-For example, CacheAudit estimates that a 128-bit AES encryption can leak more than 128 bits.
-As a result, even those tool reports severe leakage, it does not mean the program has a truly severe leakage.
-
-Our tool can give the conservative estimation of the side-channel leakage based on Channel Capacity.
-The channel capacity measures the information flow between the source and the destination.
-One useful characteristic of channel capacity is not affected by the input of the input, which is useful because we cannot assume the input secrets of the software in practice.
-In the paper, we use the sampling result to over approximate the true value of the channel capacity.
-We prove the sampling method presented in the paper can only give the conservative estimation of the amount of the true leakage.
-
-\ctool{} is a dynamic approach.
-So it bears the same limitations of dynamic approaches as well.
-\ctool{} may have the coverage problem and can miss some side-channel vulnerabilities.
-It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control-flow with various inputs.
-For other libraries like graphic rendering, machine learning, \ctool{} is very likely to miss some side-channel vulnerabilities.
-However, \ctool{} is not designed to find side-channel vulnerabilities.
-The goal of \ctool{} is to pick up those really severe side-channel vulnerabilities from the numerous vulnerabilities.
-So we do not think it is the main limitation of \ctool{}.
-However, users of \ctool{} should be aware of the code coverage problem.
-
-\begin{figure}
-  \centering
-  \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
-int foo(uint8_t secret){
-  uint8_t index = 0, t;
-  index = (index+secret)%128; // The index contains secrets
-  ...
-  if(index == 0){             // Secret-dependent flows
-    bar(r, x, n)              // The observation
-  }
-  ...
-}
-\end{lstlisting}
-  \caption{The reported leaked functions are not the root cause of the vulernability}
-  \label{fig:limitation}
-\end{figure}
-
-Another limitation is that \ctool{} can only find the position in the code that leaks the sensitive information, but it is not the root cause of the leaks.
-Consider the example in Figure~\ref{fig:limitation}, it takes the secret as the input.
-At line 3, it calculates an index based on the value of the secret.
-Depending on the value of the index, it may or may not run the code at line 6.
-So line 5 is the reason that causes the vulnerability.
-But \ctool{} can only tell that line 6 can leak the information, despite it is not the root cause of the vulnerability.

### 2021-05-18 Chapter-6/Chapter-6.tex
reorganizing the repo

@@
-\chapter{Conclusion}\label{chapter6}
-This dissertation research studies the address-based side-channel leakages in two aspects: detection and quantification.
-In the side-channel vulnerability detection research, we explore and solve the two bottlenecks in today's automated side-channel vulnerability detection tool, performance, and precision.
-In the side-channel vulnerability quantification research, we propose two different side-channel leakage quantification tools based on information theory.
+\chapter{Discussion and Limitations}
+\section{Fast and Precise Side-channel Vulnerability Detection}
+\textbf{Coverage.} \detect{} works on native x86 execution traces.
+The design, which is very precise in terms of true leakages compared to other static source code method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also share the common limitations of dynamic approaches.
+\detect{} may only cover part of the code.
+Each time we only get one single execution trace.
+Therefore, we may neglect some side-channel vulnerabilities not covered by the traces analyzed.
+However, this is not a crucial problem for analyzing cryptographic libraries, because cryptographic libraries are designed to have the same code coverage for various inputs.
+Our evaluation also confirms the above intuition.
+For symmetric encryption, there is no secret-dependent control-flow transfers during our evaluation.
+RSA implementations have several secret-dependent control-flow transfers.
+Many of them are bound checks, which do not leak much information and have negligible effects on the whole code coverage as well.
 
-\section{Summary}
+\textbf{Design Choices.} At the early stage of the project, we use SMT solvers to get the solutions of constraints.
+However, we find for some ciphers (RSA), \detect{} times out after several days.
+The profiling result shows that it is spending most its time in Z3.
+Later, we use a sampling method to detect side-channel leakages.
+The sampling method seems simple and may miss some leakages in theory.
+However, the evaluation result shows \detect{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.
 
-In Chapter~\ref{chapter3}, we present a practical address-based side-channel detection tool, \detect{}, that is capable of detecting secret-dependent control-flows and data accesses at the same time.
-We model side-channel leakage sites as math constraints and use dynamic symbolic execution to generate constraints for possible leakages.
-Using statistical testing, \detect{} can identify the true leakages from those constraints.
-Besides, \detect{} analyze the side-channel leakages directly from X86 execution traces.
-Existing binary analysis tools usually transfer the x86 instruction to intermediate languages (IR) simplify the implementation.
-However, such designs have expensive overheads and imprecise analysis results.
-To tackle the problem, we take the engineering efforts and implement the analysis based on Intel developer's manual from scratch.
-We evaluate \detect{} on popular cryptographic libraries including OpenSSL, mbedTLS, Libgcrypt, and Monocyper.
-The evaluation results show that \detect{} is three times to one hundred times faster than the state of art tools while finding all the leakages reported by the previous tools.
-In addition, \detect{} identity new leakages.
-The new leakages was later confirmed by other researchers and software developers.
+\textbf{Cache Model.} We use a simple cache model in this work.
+Recent work~\cite{Brotzman19Casym,182946} uses an LRU cache.
+First, there is no fundamental difficulties for us to adopt a more realistic cache models.
+Second, the LRU model is still a substantial simplification of a real cache.
+However, the choice of a logical model of cache can bring expensive overheads.
 
-In Chapter~\ref{chapter4}, we present a novel method to quantify address-based side-channel leakage.
-We quantify the amount of leakage information for a single trace attack.
-The amount of the leaked information is based on the search space reduced by side-channel attacks.
-We rely on \detect{} to detect side-channel leakages.
-After that, we use approximate model counting to quantify the leakage site.
-The method is implemented in a prototype tool called \tool{}.
-We show its effectiveness in quantifying side-channel leakage.
-With the new definition of information leakage that models actual side-channel attackers, quantifying the number of leaked bits helps understand the severity level of side-channel vulnerabilities.
-The evaluation confirms that \tool{} is useful in estimating the amount of leaked information in real-world applications.
+\textbf{Leakages.} While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers.
+The DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort.
+After we manually analyze those leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which partially explain why developers are not interested in fix all the leakages.
+\section{Precise Analysis on Single-trace Attacks}
+While recent work found many side-channel vulnerabilities,
+we note that many of them have not been patched by developers.
+Side-channels are ubiquitous in software and it would be difficult to fix all of them.
+We need a tool that estimates the sensitivity of each vulnerability
+so software engineers can focus on
+``severe'' leakages. For example, \tool{} reports that
+the modular exponentiation using square and multiply algorithms can
+leak more information than a key validation function.
 
-In Chapter~\ref{chapter5}, we propose a fuzzing method to automatically detect and quantify the address-based side-channel leakages automatically.
-The proposed method can produce the conservative estimation of the side-channel leakage of the deterministic program.
-As a result, any severe leakage reported by \ctool{} is the true severe leakage.
-We also study the total effect of two leakages.
-Using statistical hypothesis testing, we are able to determine if the two leakages are independent.
-If so, we can calculate the sum of the amount of leakage by adding two leakages.
-Our evaluation result on both several libraries and benchmarks show that \ctool{} is effective and accurate in detecting the side-channel leakage.
+Software developers can use \tool{} to find severe vulnerabilities
+and reason about countermeasures.
+\tool{} estimates the amount of leaked information for each side-channel leakage
+in one execution trace. \tool{} is useful for software
+engineers to test programs and fix vulnerabilities.
+The design, which is more precise in reporting true leakages as compared with other static
+methods~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, obviously misses
+leakages on unexplored traces. The amount of leaked information also depends on the secret key.
+However, as the tool is intended for debugging and testing,
+we think it is a software engineer's responsibility to select the input key and trigger
+the path in which they are interested. It is not a problem for crypto software
+since virtually all keys follow similar computational paths.
 
-In conclusion, this dissertation research develops practical techniques for precise side-channel analysis in software systems.
-For each proposed method, we implement and evaluate it on real-world software.
-The evaluation results show the effeteness and generality of our proposed method.
-We open source the tools in the dissertation to facilitate future research in the area.
-\section{Future Directions}
-In the future, we plan to explore the following directions based on the dissertation research.
+We use the amount of leaked information to represent the sensitivity level of
+each side-channel vulnerability. Although imperfect, \tool{} produces a reasonable
+measurement for each leak. For example, the simple modular exponentiation is
+notoriously famous for multiple side-channel attacks~\cite{kocher1996timing}.
+During the execution, a single leak point may execute multiple times
+and each time leak a different bit. In this case, \tool{} reports that the
+vulnerability can leak the whole key. However, not every leak point inside a
+loop is severe. If a site in the loop leaks the same bit from the
+original key, and these leaks are not independent. \tool{} captures most
+fine-grained information by modeling each leak during the execution as a
+formula and the conjunction of the formulas to describe its total effect.
+Some leakage sites (e.g., square and multiply)
+can leak one particular bit of the original key, but some leakage sites leak one bit
+from several bytes in the original key. \tool{} can capture the dependency among the leaks and
+reports more precise leakage information.
 
-\textbf{Kernel Space Side-channel Vulnerability Detection.} There are several side-channel vulnerability detection tools together with the dissertation tool.
-Most of the tools are designed to analyze the side-channel leakages in user-level applications like cryptographic libraries.
-It is reasonable since many side-channel attacks are used to break cryptographic applications.
-Recently, researchers also started to focus on side-channel attacks~\cite{cao2016off} inside the kernel space.
-However, it is non-trivial to apply existing side-channel detection tools in the Linux kernel.
-Take the method in the dissertation, for example.
-We may have the following challenges.
-First, our proposed tools in the dissertation rely on the dynamic binary instrumentation frameworks to collect the runtime information.
-As for kernel programs, a similar task can be achieved by some whole system emulators like BitBlaze~\cite{song2008bitblaze} and S2E~\cite{chipounov2012s2e}.
-S2E uses a modified Linux kernel and QEMU to trace the kernel components.
-S2E uses QEMU 1.0, which does not support the latest Linux kernel.
-The engineering efforts of extending S2E to work on the latest kernel are significant.
-Second, the kernel has very complicated control-flow graphs compared to cryptography libraries.
-Some vulnerabilities need to be triggered by specific input from the user space applications or devices.
-Our tool can not handle interruptions and exceptions.
-But they are common inside the kernel.
-On the positive side, we expect there are plenty of leakage sites inside the kernel.
-The dissertation provides the approaches to pick up ``severe'' leakages automatically.
+\tool{} reaches full precision if the number of estimated leaked bits
+equals to Definition~\ref{chapter4:def}.
+\tool{} may lose precision from the
+memory model it uses in theory. However, we did not find false positives
+caused by the imprecise memory model during our evaluation.
+Sampling introduces imprecision but with a probabilistic guarantee.
+However, during the evaluation, we find that \tool{} cannot estimate
+the amount of leakage for some leakage sites in a reasonable time,
+which means the number of $K^o$ is very small. According to Definition~\ref{chapter4:def}, it means the leakage is very severe. 
+\section{Precise Analysis on Multiple-trace Attacks}
+This chapter presents an approach that can give a conservative estimate of the amount of leaked information by address-based side-channel attacks.
+Those attacks exploit the data-flow from secrets to load address and the data-flow from the data-flow from secrets to branch conditions to retrieve secrets based on the observation on the memory accesses.
+Despite those kinds of side-channel leakages that have been discovered for decades, the up-to-date software still has some side channel leakages.
+For some of those vulnerabilities, developers do not fix them because they think those side-channel vulnerabilities are not important.
+To show the importance of those side-channel leakages, one way is to demonstrate an end-to-end attack based on the vulnerability.
+However, demonstrating an end-to-end attack often need a lot of manual effort and the domain knowledge of the victim program, which is not often the case in practices.
+It is good to have a tool that can assess the severity level of those side channel leakages automatically.
+So it would be better to have a proper metric to quantify the side-channel leakage.
+However, we find previous side-channel quantification tools are developed to ensure the noninterference of the program.
+They use over approximation heuristics method to quantify the leakage.
+For example, CacheAudit estimates that a 128-bit AES encryption can leak more than 128 bits.
+As a result, even those tool reports severe leakage, it does not mean the program has a truly severe leakage.
 
-\textbf{Compiler-assisted Side-channel Vulnerability Analysis and Mitigation.}
-We propose to mitigate the side-channel leakages from a compiler backend.
-For example, the conditional execution can be eliminated by using the masks.
-Eliminating side-channel leakages from compilers is not a brand new idea.
-Coppens et al.~\cite{Coppens:2009:PMT:1607723.1608124} propose several methods to remove several approaches to eliminate all potential leakages that are related to data flow and control flow.
-GNU toolchain adds new options (\textsf{-mlfence-after-load}, \textsf{-mlfence-before-indirect-branch}) to mitigate the Load Value Injection (LVI) attack during the compilation.
-Coppens et al.'s approach has a slowdown with a factor from 2 to 24.
-The LVI harden binaries generated from GNU toolchains takes 6-10x longer to run.
-The performance impact from the aggressive mitigation.
-For example, GNU toolchains inset LFENCE before any possible vulnerable instructions, including all load instructions, all indirect branches, and return instructions.
-We plan only to change those points that are more likely to leak sensitive information.
-Even more, with the tool presented in the dissertation, we can only modify part of the ``severe'' leakage sites.
+Our tool can give the conservative estimation of the side-channel leakage based on Channel Capacity.
+The channel capacity measures the information flow between the source and the destination.
+One useful characteristic of channel capacity is not affected by the input of the input, which is useful because we cannot assume the input secrets of the software in practice.
+In the paper, we use the sampling result to over approximate the true value of the channel capacity.
+We prove the sampling method presented in the paper can only give the conservative estimation of the amount of the true leakage.
+
+\ctool{} is a dynamic approach.
+So it bears the same limitations of dynamic approaches as well.
+\ctool{} may have the coverage problem and can miss some side-channel vulnerabilities.
+It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control-flow with various inputs.
+For other libraries like graphic rendering, machine learning, \ctool{} is very likely to miss some side-channel vulnerabilities.
+However, \ctool{} is not designed to find side-channel vulnerabilities.
+The goal of \ctool{} is to pick up those really severe side-channel vulnerabilities from the numerous vulnerabilities.
+So we do not think it is the main limitation of \ctool{}.
+However, users of \ctool{} should be aware of the code coverage problem.
+
+\begin{figure}
+  \centering
+  \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
+int foo(uint8_t secret){
+  uint8_t index = 0, t;
+  index = (index+secret)%128; // The index contains secrets
+  ...
+  if(index == 0){             // Secret-dependent flows
+    bar(r, x, n)              // The observation
+  }
+  ...
+}
+\end{lstlisting}
+  \caption{The reported leaked functions are not the root cause of the vulernability}
+  \label{fig:limitation}
+\end{figure}
+
+Another limitation is that \ctool{} can only find the position in the code that leaks the sensitive information, but it is not the root cause of the leaks.
+Consider the example in Figure~\ref{fig:limitation}, it takes the secret as the input.
+At line 3, it calculates an index based on the value of the secret.
+Depending on the value of the index, it may or may not run the code at line 6.
+So line 5 is the reason that causes the vulnerability.
+But \ctool{} can only tell that line 6 can leak the information, despite it is not the root cause of the vulnerability.
+
+\section{Limitations}

### 2021-05-18 Chapter-7/Chapter-7.tex
reorganizing the repo

\chapter{Conclusion}\label{chapter6}
This dissertation research studies the address-based side-channel leakages in two aspects: detection and quantification. In the side-channel vulnerability detection research, we explore and solve the two bottlenecks in today's automated side-channel vulnerability detection tool, performance and precision. In the side-channel vulnerability quantification research, we propose two different side-channel leakage quantification tools based on information theory.

\section{Summary}

In Chapter~\ref{chapter3}, we present a practical address-based side-channel detection tool, \detect{}, that is capable of detecting secret-dependent control-flows and data accesses at the same time. We model side-channel leakage sites as math constraints and use dynamic symbolic execution to generate constraints for possible leakages. Using statistical testing, \detect{} can identify the true leakages from those constraints. \detect{} analyzes the side-channel leakages directly from X86 execution traces. Existing binary analysis tools usually transfer the x86 instruction to intermediate languages (IR) simplify the implementation. However, such designs have expensive overheads and imprecise analysis results. To tackle these problem, we take the engineering efforts and implement the analysis from scratch  based on Intel developer's manual. We evaluate \detect{} on popular cryptographic libraries including OpenSSL, mbedTLS, Libgcrypt, and Monocyper. The evaluation results show that \detect{} is three times to one hundred times faster than the state of art tools while finding all the leakages reported by the previous tools. In addition, \detect{} identity new leakages. The new leakages were later confirmed by other researchers and software developers.

In Chapter~\ref{chapter4}, we present a novel method to quantify address-based side-channel leakage. We quantify the amount of leakage information for a single trace attack. The amount of the leaked information is based on the search space reduced by side-channel attacks. We rely on \detect{} to detect side-channel leakages. After that, we use approximate model counting to quantify the leakage site. The method is implemented in a prototype tool called \tool{}. We show its effectiveness in quantifying side-channel leakage. With the new definition of information leakage that models actual side-channel attackers, quantifying the number of leaked bits helps understand the severity level of side-channel vulnerabilities. The evaluation confirms that \tool{} is useful in estimating the amount of leaked information in real-world applications.

In Chapter~\ref{chapter5}, we propose a fuzzing method to automatically detect and quantify the address-based side-channel leakages automatically. The proposed method can produce a conservative estimation of the side-channel leakage of the deterministic program. As a result, any severe leakage reported by \ctool{} is the true severe leakage. We also study the total effect of two leakages. Using statistical hypothesis testing, we are able to determine if the two leakages are independent. If so, we can calculate the sum of the amount of leakage by adding two leakages. Our evaluation result on both several libraries and benchmarks show that \ctool{} is effective and accurate in detecting the side-channel leakage.

In conclusion, this dissertation research develops practical techniques for precise side-channel analysis in software systems. For each proposed method, we implement and evaluate it on real-world software. The evaluation results show the effeteness and generality of our proposed method.  We open source the tools in the dissertation to facilitate future research in the area.
\section{Future Directions}
In the future, we plan to explore the following directions based on the dissertation research.

\textbf{Kernel Space Side-channel Vulnerability Detection.} There are several side-channel vulnerability detection tools together with the dissertation tool. Most of the tools are designed to analyze the side-channel leakages in user-level applications like cryptographic libraries. It is reasonable since many side-channel attacks are used to break cryptographic applications. Recently, researchers also started to focus on side-channel attacks~\cite{cao2016off} inside the kernel space. However, it is non-trivial to apply existing side-channel detection tools in the Linux kernel. Take the method in the dissertation, for example. We may have the following challenges. First, our proposed tools in the dissertation rely on the dynamic binary instrumentation frameworks to collect the runtime information. As for kernel programs, a similar task can be achieved by some whole system emulators like BitBlaze~\cite{song2008bitblaze} and S2E~\cite{chipounov2012s2e}. S2E uses a modified Linux kernel and QEMU to trace the kernel components. S2E uses QEMU 1.0, which does not support the latest Linux kernel. The engineering efforts of extending S2E to work on the latest kernel are significant. Second, the kernel has very complicated control-flow graphs compared to cryptography libraries. Some vulnerabilities need to be triggered by specific input from the user space applications or devices. Our tool can not handle interruptions and exceptions. But they are common inside the kernel. On the positive side, we expect there are plenty of leakage sites inside the kernel. The dissertation provides the approaches to pick up ``severe'' leakages automatically.

\textbf{Compiler-assisted Side-channel Vulnerability Analysis and Mitigation.}
We propose to mitigate the side-channel leakages on a compiler backend. For example, the conditional execution can be eliminated by using the masks. Eliminating side-channel leakages from compilers is not a brand new idea. Coppens et al.~\cite{Coppens:2009:PMT:1607723.1608124} propose several methods to remove all potential leakages that are related to data flow and control flow.  GNU toolchain adds new options (\textsf{-mlfence-after-load}, \textsf{-mlfence-before-indirect-branch}) to mitigate the Load Value Injection (LVI) attack during the compilation. Coppens et al.'s approach has a slowdown with a factor from 2 to 24. The LVI harden binaries generated from GNU toolchains takes 6-10x longer to run.  For example, GNU toolchains inset LFENCE before any possible vulnerable instructions, including all load instructions, all indirect branches, and return instructions. We plan only to change those points that are likely to leak sensitive information. Finally, with the tool presented in the dissertation, we can modify only part of the ``severe'' leakage sites.

### 2021-05-18 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \subsection{Case Studies}
-\subsubsection{DES and AES}
+\subsubsection*{DES and AES}
 Our tool confirms that both implementations in OpenSSL and mbedTLS have side-channel leakages
@@
 
-\subsubsection{RSA}
+\subsubsection*{RSA}
 We also evaluates our tool on the RSA implementations. With the optimizations
@@
 
-\subsubsection{Monocypher}\label{eval:mono}
+\subsubsection*{Monocypher}\label{eval:mono}
 Monocypher is a small, easy to use cryptographic library with

### 2021-05-18 changelog.tex
update change log

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Changelog}
\author{Qinkun Bao}
\date{May 2021}

\begin{document}

\maketitle

\section{Introduction}

\end{document}

### 2021-05-18 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 An attacker can probe the shared hardware resource to infer the memory accesses of the victim.
-While the root cause of the attack is the same, there are many approaches, and an attacker can exploit the vulnerability in different methods to retrieve the information at different granularities.
+While the root cause of the attack is the same, there are many approaches, and an attacker can exploit side-channel leakage sites in different methods to retrieve the information at different granularities.
 
@@
 
-\textbf{Flush+Reload.} Flush+Reload allows an attacker to observe the memory at the granularity of the cache line instead of a cache set.
+\textbf{Flush+Reload.} Flush+Reload allows an attacker to observe the memory at the granularity of a cache line instead of a cache set.
 While Flush+Reload targets a single cache line, it requires the attacker and victim to share some memory.
@@
 memory'' from the cache and waits for the victim to access the memory, which may be a load of the sensitive information to the cache line.  In the next phase,
-the attacker reloads the ``monitored memory''.
-By measuring the time differences brought by cache hits and misses, the attacker can infer the sensitive information.
+the attacker reloads the ``monitored memory''. The attacker's process read all data in the `monitored
+memory''. If the time is relatively fast, it indicate that the data has been accessed by the victim program and the cache has loaded the data. 
 On X86-64 machines, the two steps can be combined by measuring the time differences of the \textsf{clflush} instruction.

### 2021-05-19 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 
-\textbf{Flush+Reload.} Flush+Reload allows an attacker to observe the memory at the granularity of a cache line instead of a cache set.
-While Flush+Reload targets a single cache line, it requires the attacker and victim to share some memory.
+\textbf{Flush+Reload.} Flush+Reload allows an attacker to observe memory accesses at the granularity of a cache line instead of a cache set.
+While Flush+Reload has a fine-grained granularity compared with Prime+Probe, it requires the attacker and victim to share some memory.
+It also has two stages.
 During the ``flush'' stage, the attacker flushes the ``monitored

### 2021-05-19 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 While the granularity of the controlled-channel attacks is more coarse-grained compared with cache channel attacks, controlled-channel attacks allow the attacker to have a noise-free observation.
-Other examples include the TLB side-channel attack and DDRAM attacks share the same page-level granularity.
+Other examples such as TLB side-channel attacks and DDRAM attacks share the same page-level granularity.
 
@@
 Access-based attacks often happen in the cloud computing environment when the attacker and victim share the same hardware (e.g., LLC cache).
-Examples of those attacks include cache template attacks~\cite{191010}, Prime and Probe attacks~\cite{liu2015last}, and Flush and Reload attacks~\cite{yarom2014flush+}.
+Examples of those attacks include cache template attacks~\cite{191010}, Prime+Probe attacks~\cite{liu2015last}, and Flush+Reload attacks~\cite{yarom2014flush+}.
 \subsubsection*{Trace-based Attacks}
@@
 approaches usually often rely on binary instrumentation frameworks or emulators (e.g., Intel Pin~\cite{luk2005pin},
-Valgrind~\cite{nethercote2007valgrind}, QEMU). The second step is analyzing the trace using techniques, such
+Valgrind~\cite{nethercote2007valgrind}, and QEMU). The second step is analyzing the trace using techniques, such
 as symbolic execution, taint analysis. Depending on when the analysis is launched,

### 2021-05-20 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 \subsubsection*{Timing-based Attacks}
-In timing-based attacks, an adversary can monitor the execution time of a victim program.
+In timing-based attacks, an adversary can measure and compare the execution time of victim programs.
 It could be the overall execution time or the execution time of some interesting points (e.g., a function).
 The execution time is correlated to some events (e.g., cache hits and misses, page faults, the number of instructions).
-Examples of those attacks include remote timing attacks~\cite{brumley2005remote}, Bernstein's attack on AES~\cite{bernstein2005cache}, and Kocher’s original attack~\cite{kocher1996timing} from CRYPTO 96.
+Timing-based attacks are perilous because these attacks are able to be carried out remotely over the networks remotely~\cite{brumley2005remote}.
+Examples of these attacks include remote timing attacks~\cite{brumley2005remote}, Bernstein's attack on AES~\cite{bernstein2005cache}, and Kocher’s original attack~\cite{kocher1996timing} from CRYPTO 96.
 \subsubsection*{Access-based Attacks}
-In access-based attacks, an adversary can probe one time only after the termination of the victim program.
-The attacker can learn the memory addresses that are accessed during the execution.
-For example, a cache-based channel attack can know which memory access incurs a cache hit and which memory access incurs a cache miss.
+In access-based attacks, an adversary can learn the memory addresses that are accessed during the execution after the termination of the victim program. 
+For example, a cache-based channel attack can know which memory access incurs a cache hit and which memory access incurs a cache miss to infer addresses that the victim program accesses.
 Since the attacker can probe the victim program after the execution, the attacker does not know the order of memory accesses.
@@
 \subsubsection*{Trace-based Attacks}
-In trace-based attacks, an adversary can probe the victim program at any point.
+In trace-based attacks, an adversary can interrupt and  probe the victim program at any point.
 The attacker can learn the order of memory accesses.
@@
 In an access-based attacks, the attacker can only learn both \textsf{a} and \textsf{b} are executed.
-In a trace-based attack, the attacker can know the execution sequence of two functions (e.g., $aabbb$).
-Controlled-channel attacks~\cite{moghimi2020copycat, xu2015controlled} belong to the category where a malicious operating system can interrupt the victim application and probe the program at any time.
+In a trace-based attack, the attacker can know the execution sequence of two functions (e.g., $\mathtt{aabbb}$).
+Controlled-channel attacks~\cite{moghimi2020copycat, xu2015controlled} belong to this category where a malicious operating system can interrupt the victim application and probe the program at any time.
 In general, the trace-based attack has the strongest assumption about the threat model,  but it can retrieve more information compared to the other two types of attacks.
@@
 There is a vast number of studies\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last} on side-channel attacks.
-Most early work targeted retrieving encryption keys from cryptography libraries.
+Most early works targeted retrieving encryption keys from cryptography libraries.
 In recent years, researchers start to focus on more general and diverse applications.
@@
 The situation is even worse for asymmetric ciphers (e.g., Diffie-Hellman, RSA, ECDSA).
-Those ciphers have a lot of big number calculations.
+These ciphers have a lot of big number calculations.
 It is hard to implement those calculations to be completely side-channel resistant.
@@
 It is hard to migrate all the code into a constant-time implementation.
-The second approach is to use blinding to reduce the information that an attacker can retrieve.
+The second approach is to use blinding to obfuscate the information that an attacker can retrieve.
+Side-channel attacks allow an adversary to retrieve information by measuring something other than the program's output itself.
+Binding values can alter the input to some unpredictable data and introduce the randomization to the execution.
 However, the binding value can also be retrieved by an attacker through other methods, including side-channel attacks.
+An attacker can launch an attack to retrieve the binding value to recover the secret input.
 

### 2021-05-20 changelog.tex
Updates from Overleaf

@@
 \section{Introduction}
+(1). Fuzzing – need stronger motivation
 
+(2). Discuss the limitations of your research
+e.g., can only handle address based …
+you might want to include some discussion on the points (3), (4), and (5) below.
+
+(3). Can you extend your research (especially the quantification part) to include other side channel signals?
+
+(4). A bits vs. Q bits. Lower bounds?
+Improve the presentation
+Make the comparison more meaningful
+
+(5). iid assumption – does it fit your research on side-channel?
+
+(6). Some feedback I gave before your defense.
 \end{document}

### 2021-05-20 changelog.tex
Updates from Overleaf

--- 2021-05-18 changelog.tex
@@
 \maketitle
+Thank you for reviewing my dissertation.
+I have gone through the details of each comment and revised my dissertation multiple rounds to eliminate any logic flow and fix all the typos and grammar errors.
+In summary, the revisions cover the following aspects.
 
-\section{Introduction}
+\section{Requested Changes}
+
+\begin{enumerate}
+\item Fuzzing – need stronger motivation.
+\item Discuss the limitations of your research
+e.g., can only handle address based …
+you might want to include some discussion on the points (3), (4), and (5) below.
+\item Can you extend your research (especially the quantification part) to include other side channel signals?
+\item A bits vs. Q bits. Lower bounds?
+       Improve the presentation
+       Make the comparison more meaningful
+       Etc.
+\item iid assumption – does it fit your research on side-channel?
+\item Some feedback I gave before your defense.
+
+Before the defense, Dr. Wu gave me the following feedback.
+\end{enumerate}
+\section{Other Changes}
 

### 2021-05-21 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 While analyzing the IRs can simplify the implementation, it is not suitable for side-channel analysis.
-Side-channel leakages are a pretty low-level issue and only the low-level analysis can give the most accurate results.
+Side-channel leakages are a low-level issue and only the low-level analysis can produce the most accurate results.
 For example, the IR-level branches are not necessarily a superset or a subset of machine-code level branches.
@@
 The evaluation results show that our tool can identify previous side-channel leakages as well as find new leakages.
-Compared with recent tools, our tool is 3-100x faster while finding all the leakages when we evaluate on the same benchmarks.
+Compared with recent tools~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741}, our tool is 3-100x faster while finding all the leakages when we evaluate on the same benchmarks.
 In addition, our tool finds new side-channel vulnerabilities missed by the previous work.

### 2021-05-21 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 In modern CPUs, L1 and L2 caches are traditional N-way set associate caches.
-That is, the cache is divided into several cache sets, and each set is associated with several cache lines.
+That is, the cache is divided into several cache sets, and each set contains several cache lines.
 The cache line is the atomic unit.
 As shown in Figure~\ref{fig:memory_address}, we can determine whether the data is in the cache with the following steps.
-Given an address, the CPU uses the \textsf{Set Index} field of the address to locate the cache set that the address should reside in.
+Given an address, the CPU uses the \textsf{Index} field of the address to locate the cache set that the address should reside in.
 After that, it tries to use the \textsf{Tag} field to match every cache line inside the set line.
@@
 In this section, we introduce two limitations of current side-channel leakage detection tools.
-The first limitation is that some tools have some false positives or false negatives.
-The second limitation is current tools are not fast enough to analyze side-channel leakages in real-world software.
+The first is that some tools have some false positives or false negatives.
+The second is that current tools are not fast enough to analyze side-channel leakages in real-world software.
 
@@
 The size of each element is one byte.
-So the total size of the array is 128 Bytes.
+So the total size of the array is 128 bytes.
 Suppose an attacker can observe the memory access at the granularity of one cache lines (64 Bytes), then it is not possible to hold all the data inside the one cache line.
@@
 Figure~\ref{fig:chapter3:da}(b) shows a different example.
-In this example, only 32 different elements can be accessed in the array and the size of the array is 32 bytes, which is smaller than the size of one cache line.
+In this example, only 32 different elements can be accessed in the array and the size of the array is 32 bytes, which is smaller than the size of a cache line.
 Depending on the base address of the array, the array can be stored in one cache line or two consecutive cache lines.
@@
 \subsection{Performance}
-The second limitation of current side-channel detection tools is the performance bottleneck, especially for those tools based on the symbolic analysis.
+The second limitation of current side-channel detection tools is the performance bottleneck, especially for those tools based on symbolic analysis.
 For example, CaSym can only analyze small programs.
@@
 
-Shown in Figure~\ref{fig:side-channel-attack}, a side-channel attack can be formulated into the below steps.
+Shown in Figure~\ref{fig:side-channel-attack}, a side-channel attack can be formulated into the following steps.
 A program ($\beta$) has $K$ as its sensitive input (e.g., the encryption key) and $M$ as its the public input (e.g., the plaintext).
@@
 We now discuss how to model observations ($O$),
-which are the direct information that an adversary can get during the attack.
+which are the direct information that an adversary gets during the attack.
 
@@
 If $m = 0$, we can not find satisfiable $k_1$ and $k_2$ for the above inequation, which indicates that it will always access the same cache line at line 6.
-It is the conclusion from Cache.
 However, it is possible that for some $m \in M$, we can find such a pair of $k_1$ and $k_2$ ($m = 53, k_1 = 1, k_2 = 0$).
@@
 captured the semantics of the execution and search different input values that
-can lead to different execution behaviors using constraint solver.
+can lead to different execution behaviors using a constraint solver.
 We implement the approach presented in \S\ref{chapter3:method} and model the side-channels as formulas.

### 2021-05-22 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 The cache is divided into different cache sets, and each cache set is made up of several cache lines.
+Typically, the smallest storage unit in a CPU cache is a cache line.
 Cache channel attacks can observe cache accesses at the level of cache sets, cache lines or other granularities.
@@
 
-\section{Detection and Mitigation}
+\section{Defenses and Mitigation}
+
+Both hardware~\cite{Page2005PartitionedCA,
+    Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
+    236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
+    brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
+been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
+accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
+architecture~\cite{tiwari2011crafting}, require changes to complex processors and are difficult to adopt. On the contrary, software approaches are
+usually easy to implement. Coppens et
+al.~\cite{Coppens:2009:PMT:1607723.1608124} uses a compiler
+to eliminate key-dependent control-flow transfers. Crane et
+al.~\cite{crane2015thwarting} mitigates side-channels by randomizing software.
+As for crypto libraries, the basic idea is to eliminate key-dependent
+control-flow transfers and data accesses. Common approaches include
+bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
+control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.
+
+\subsection{Software Countermeasures}
+\subsubsection*{Software Vulnerability Identification}
 There are several existing works on side-channel leakage detections.
@@
 \end{sidewaystable}
-Both hardware~\cite{Page2005PartitionedCA,
-    Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
-    236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
-    brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
-been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
-accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
-architecture~\cite{tiwari2011crafting}, require changes to complex processors and are difficult to adopt. On the contrary, software approaches are
-usually easy to implement. Coppens et
-al.~\cite{Coppens:2009:PMT:1607723.1608124} uses a compiler
-to eliminate key-dependent control-flow transfers. Crane et
-al.~\cite{crane2015thwarting} mitigates side-channels by randomizing software.
-As for crypto libraries, the basic idea is to eliminate key-dependent
-control-flow transfers and data accesses. Common approaches include
-bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
-control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.
+
+\subsubsection*{Runtime Behavior Randomization}
+
+\subsection{Hardware Countermeasures}
+\subsubsection*{Resource Partitioning}
+\subsubsection*{Randomization}
 

### 2021-05-22 Chapter-2/Chapter-2.tex

@@
 Recent work~\cite{arnaud2013timing,yarom2017cachebleed,yarom2014flush+} has demonstrated several end-to-end attacks to recover the private key of those ciphers.
-There are two common countermeasures to mitigate side-channel attacks in cryptography libraries.
-The first approach is to adopt constant time operation when computing the secret data.
-It is hard to migrate all the code into a constant-time implementation.
-The second approach is to use blinding to obfuscate the information that an attacker can retrieve.
-Side-channel attacks allow an adversary to retrieve information by measuring something other than the program's output itself.
-Binding values can alter the input to some unpredictable data and introduce the randomization to the execution.
-However, the binding value can also be retrieved by an attacker through other methods, including side-channel attacks.
-An attacker can launch an attack to retrieve the binding value to recover the secret input.
 
@@
 \subsubsection*{Software Vulnerability Identification}
+For many software countermeasures, the first step is identifying side-channel leakages in software manually. It can be done manually or by some program analysis tools.
 There are several existing works on side-channel leakage detections.
@@
 
-\subsubsection*{Runtime Behavior Randomization}
-
+\subsubsection*{Software Patching}
+There are two common countermeasures to mitigate side-channel attacks in cryptography libraries.
+The first approach is to adopt constant time operation when computing the secret data.
+It is hard to migrate all the code into a constant-time implementation.
+The second approach is to use blinding to obfuscate the information that an attacker can retrieve.
+Side-channel attacks allow an adversary to retrieve information by measuring something other than the program's output itself.
+Binding values can alter the input to some unpredictable data and introduce the randomization to the execution.
+However, the binding value can also be retrieved by an attacker through other methods, including side-channel attacks.
+An attacker can launch an attack to retrieve the binding value to recover the secret input.
 \subsection{Hardware Countermeasures}
@@
 
-\section{Quantification}
+\subsection{Discussion on Existing Countermeasures}
+\section{Information Quantification}
 Proposed by Denning~\cite{robling1982cryptography} and Gray~\cite{gray1992toward},

### 2021-05-22 changelog.tex
Updates from Overleaf

@@
 In summary, the revisions cover the following aspects.
-
-\section{Requested Changes}
 
@@
 Before the defense, Dr. Wu gave me the following feedback.
+\begin{itemize}
+\item Add a chapter on Discussion and Limitations
+\item Discuss potential ways and related work to mitigated reported side channels
+
+I extended the related work on current side-channel defenses in Chapter.
+I cited and discussed the related work on side-channel defenses from two aspects: software countermeasures and hardware countermeasures.
+\end{itemize}
+
+\item Improve Grammar.
 \end{enumerate}
-\section{Other Changes}
 

### 2021-05-22 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 \subsubsection*{Software Patching}
-There are two common countermeasures to mitigate side-channel attacks in cryptography libraries.
-The first approach is to adopt constant time operation when computing the secret data.
-It is hard to migrate all the code into a constant-time implementation.
-The second approach is to use blinding to obfuscate the information that an attacker can retrieve.
+Once we have identified side-channel leakages, there are two common approaches to mitigate side-channel attacks in libraries.
+The first approach is to adopt unified behavior code when computing the secret data.
+For example, a control flow leakage happens when different secret inputs lead to different paths.
+Software can mitigate the leakage by executing both branches and select the result with the bit-wise operations.
+However, for exiting code base, it is hard to migrate all the code into a constant-time implementation.
+The second approach is to introduce randomized behaviors during the execution to obfuscate the information that an attacker can retrieve.
+One example is cryptographic blinding.
 Side-channel attacks allow an adversary to retrieve information by measuring something other than the program's output itself.

### 2021-05-23 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 
-\subsubsection*{Software Patching}
-Once we have identified side-channel leakages, there are two common approaches to mitigate side-channel attacks in libraries.
+\subsubsection*{Software Patch}
+Once we have identified side-channel leakages, there are two common approaches to mitigate side-channel attacks.
 The first approach is to adopt unified behavior code when computing the secret data.
 For example, a control flow leakage happens when different secret inputs lead to different paths.
-Software can mitigate the leakage by executing both branches and select the result with the bit-wise operations.
-However, for exiting code base, it is hard to migrate all the code into a constant-time implementation.
+Software developers can mitigate the leakage by executing both branches and select the result with bit-wise operations.
+However, for exiting code base, it is hard to migrate all the code into a side-channel free implementation.
 The second approach is to introduce randomized behaviors during the execution to obfuscate the information that an attacker can retrieve.
 One example is cryptographic blinding.
-Side-channel attacks allow an adversary to retrieve information by measuring something other than the program's output itself.
-Binding values can alter the input to some unpredictable data and introduce the randomization to the execution.
+Developers can use a random value to blend the secret key but still generate the same encrypted data with a carefully designed algorithm.
+Binding values can alter the program execution to some unpredictable states and introduce the randomization to the execution.
 However, the binding value can also be retrieved by an attacker through other methods, including side-channel attacks.

### 2021-05-23 SupplementaryMaterial/Abstract.tex
Updates from Overleaf

@@
 
-%\vspace{-0.3in}
-Side-channel vulnerabilities can leak secret information through non-functional characteristics, e.g., time, power, and memory usage.
-Like many other software vulnerabilities, attackers exploit flaws in designs of hardware and implementations of software.
-Hardware countermeasures, which usually require changes to the complex underlying hardware, are hard to adopt in practice.
-On the contrary, software approaches are generally easy to implement.
-This dissertation studies various aspects of side-channel vulnerabilities.
+\vspace{-0.3in}
+Side channels are ubiquitous in modern computer systems as sensitive
+information can leak through many mechanisms such as power consumption, 
+execution timing, and even electromagnetic radiation. Among them, 
+address-based side-channel attacks, such as cache-based attacks, 
+memory page attacks, and controlled-channel attacks, are especially
+problematic as they do not require physical proximity. Hardware 
+countermeasures, which usually require changes to the complex 
+underlying hardware, are hard to adopt in practice.  On the contrary, 
+software approaches are generally easy to implement. While some existing 
+tools can detect side-channel leakages, many of these approaches are 
+computationally expensive or imprecise. Besides, many such vulnerabilities 
+leak a negligible amount of sensitive information, and thus developers 
+are often reluctant to address them. Existing tools do not provide sufficient 
+information, such as the amount of information leakage through side channels, 
+to evaluate the severity of a vulnerability.
 
-The dissertation first introduces a new method to detect address-based side-channel vulnerabilities in the binary code.
-While existing approaches can identify side-channel leakages in real-world programs, many these approaches are computationally expensive and need to apply domain knowledge to simplify the analysis.
-We examine the bottleneck in the symbolic approaches and propose methods to identify side-channel vulnerabilities in real-world cryptography applications.
-We implement the approach in a tool and apply it to popular cryptography libraries.
-The evaluation results confirm that the tool is much faster than state-of-art tools while identifying all the known leakages reported by previous tools.
-In addition, our tool catches new vulnerabilities that are missed by previous tools.
-We confirm those vulnerabilities with manual checking and by contacting the developers.
+In this dissertation, we present methods to detect and quantify 
+address-based side-channel vulnerabilities in real-world applications. 
+First, a new method to detect address-based side-channel vulnerabilities 
+for the binary code is proposed. We examine the bottleneck in the symbolic 
+approaches and improve the analysis precision and performance.
+Second, we propose a new program analysis method to precisely quantify
+the leaked information in a single-trace attack. We model an
+attacker’s observation of each leakage site as a constraint and run
+Monte Carlo sampling to estimate the number of leaked bits for each
+leakage site. Finally, we extend our approach to quantify side-channel 
+leakages from multiple trace attacks. We present a method to quantify
+the lower bound of side-channel leakages. Unlike the previous side-channel 
+detection tools, our approach can identify severe side-channel
+leakages without false positives.
 
-Second, current side-channel detection tools are able to identify numerous potential vulnerabilities.
-However, in practice, many such vulnerabilities leak a negligible amount of sensitive information, and thus developers are often reluctant to address them.
-Existing tools do not provide information to evaluate a leak’s severity, such as the number of leaked bits.
-To address this issue, we propose a new program analysis method to precisely quantify the leaked information in a single-trace attack through side-channels.
-It can identify covert information flows in programs that expose confidential information and can reason about security flaws that would otherwise be difficult, if not impossible, for a developer to find.
-We model an attacker’s observation of each leakage site as a constraint.
-We use symbolic execution to generate these constraints and then run Monte Carlo sampling to estimate the number of leaked bits for each leakage site.
-By applying the Central Limit Theorem, we provide an error bound for these estimations.
-We have implemented the technique in a tool called \tool{} and apply \tool{} on OpenSSL, mbedTLS, Libgcrypt, and Monocypher.
-Our results demonstrate that most reported vulnerabilities are difficult to exploit in practice and should be de-prioritized by developers.
-The evaluation results show that our method can successfully distinguish severe leakages from many negligible leakages.
-
-Third, we extend our approach to quantify side-channel leakages from multiple trace attacks.
-In this work, we present \ctool{}, an address-based side-channel detection and quantification tool that can quantify the side-channel leakages in a conservation but precise way.
-Unlike previous side-channel detection tools, our approach can identify those severe side-channel leakages without false positives.
-Moreover, by applying the chi-squared test, our tool can estimate the total effect of multiple leakage sites as well.
-\ctool{} consists of three steps.
-First, the target program is executed with a number of different sensitive inputs to record memory accesses.
-Second, the long address traces are split into several segments based on the location in the source code.
-Finally, we analyze the memory-access information from those segments and compare the address access information with the original source code.
-Based on the channel capacity between the original secrets and the observation of the attacker, we quantify the information leakages for each leakage site.
-We evaluate \ctool{} with OpenSSL, mbedTLS, TinyDNN and GTK.
-Our evaluation results show \ctool{} is effective in identifying and quantifying side-channel leakages.
-
+We implement the approaches and apply them to popular cryptography libraries.  
+The evaluation results confirm that our side-channel detection method 
+is much faster than state-of-art tools while identifying all the known leakages 
+reported by previous tools.
+The experiments also show that 
+our side channel analysis reports quite precise leakage information
+that can help developers better triage the reported vulnerabilities.
 This dissertation research develops fundamental and practical techniques for precise side-channel 

### 2021-05-23 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 The second approach is to introduce randomized behaviors during the execution to obfuscate the information that an attacker can retrieve.
-One example is cryptographic blinding.
+One example is cryptographic blinding~\cite{coron1999resistance}.
 Developers can use a random value to blend the secret key but still generate the same encrypted data with a carefully designed algorithm.
@@
 \subsubsection*{Resource Partitioning}
+Side-channel attacks usually require attackers and victims to share some hardware resources (e.g., CPU cache, MMU).
+A straightforward way to defend those attacks is to partition the resources and ensure the attacker and the victim never share the same hardware resource.
 \subsubsection*{Randomization}

### 2021-05-23 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 A straightforward way to defend those attacks is to partition the resources and ensure the attacker and the victim never share the same hardware resource.
+For example, in a cloud computing environment, several virtual machines (VMs) can be hosted on the same physical machine and those VMs share the same last-level cache (LLC).
+Researchers proposed different methods to partition the LLC such as cache coloring~\cite{shi2011limiting}, using Intel Cache Allocation Technology~\cite{liu2016catalyst}.
 \subsubsection*{Randomization}
+This type of defense randomizes the behaviors of hardware resources to make it harder for attackers to infer secrets based on side-channel information.
+For example, Random Permutation Cache (PRcache)~\cite{wang2007new} uses a dynamically randomized memory to cache mapping table for each different process.
+Vattikonda et al.~\cite{vattikonda2011eliminating} add noises to the result of the system timer to mitigate timing-based channels.
 

### 2021-05-23 changelog.tex
Updates from Overleaf

@@
 
-I extended the related work on current side-channel defenses in Chapter.
-I cited and discussed the related work on side-channel defenses from two aspects: software countermeasures and hardware countermeasures.
+I extended the related work on current side-channel defenses in Chapter 2.
+I discussed the current work on side-channel defenses from two aspects: software countermeasures and hardware countermeasures.
 \end{itemize}

### 2021-05-23 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 Side-channel attacks usually require attackers and victims to share some hardware resources (e.g., CPU cache, MMU).
-A straightforward way to defend those attacks is to partition the resources and ensure the attacker and the victim never share the same hardware resource.
+A straightforward way to defend those attacks is to partition the resources and ensure the attacker and the victim never share the same hardware resource~\cite{Page2005PartitionedCA,shi2011limiting,liu2016catalyst}.
 For example, in a cloud computing environment, several virtual machines (VMs) can be hosted on the same physical machine and those VMs share the same last-level cache (LLC).
@@
 \subsection{Discussion on Existing Countermeasures}
+Despite a lot of hardware countermeasures that have been proposed in academia, few of them have been adopted in real-world production systems.
+In general, hardware countermeasures usually require new hardware designs and are harder to adopt in practice.
+In addition, some hardware methods (e.g., Oblivious RAM) may introduce expensive computation overhead.
+Therefore, many practical solutions are still software countermeasures.
+However, software methods are not very general, and it is hard to find many side-channel leakages in large code bases manually.
+In this dissertation, we propose side-channel analysis methods to address the problem.
 \section{Information Quantification}
@@
 
-The above existing well-known binary analysis frameworks all adopt the IR layer, which makes it easy to implement the analysis and support multiple architectures.
+The above existing well-known binary analysis frameworks adopt the IR layer, which makes it easy to implement the analysis and support multiple architectures.
 However, it can have very low efficiency and long traces.

### 2021-05-23 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 
+To evaluate the effectiveness of the leaked bits reported by \tool{}, we conduct a case study of all the leaked sites identidied by \tool{} in OpenSSL 1.1.0f.
+Table~\ref{chapter4:tab:RSAOpenSSL1.1.0} shows the result.
+First, all leakage sites that leak more than 5 bits information are fixed by developers.
+Second, for all leakages that are not patched by developers, the quantification result shows that they leak less than 1.0 bits information.
+The evaluation results show that \tool{} can help developers find severe leakages automatically.
+
+\begin{table}[!ht]
+\centering\tiny\scriptsize
+\caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0f.
+According to \tool{}\cite{bao2021abacus}, the mark ``$*$'' means timeout, which indicates more severe leakages.
+$0.0$ means very small amount of leakage, but not exactly zero.}\label{chapter4:tab:RSAOpenSSL1.1.0}
+%\resizebox{\columnwidth}{!}{
+\begin{tabular}{rrrrc}
+\hline
+\textbf{File}  & \textbf{Line Number} & \textbf{Vulnerable Function} & \textbf{Leaked Information (bits)} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
+bn\_lib.c& 143&BN\_num\_bits\_word&*& \cmark\\
+bn\_lib.c& 144&BN\_num\_bits\_word&*& \cmark\\
+bn\_lib.c& 145&BN\_num\_bits\_word&17.2 & \cmark\\
+bn\_lib.c& 1029&bn\_correct\_top&*&\cmark\\
+bn\_lib.c& 639&BN\_ucmp&*&\cmark\\
+ct\_b64.c& 164&\_\_udivdi3&5.9 &\cmark\\
+bn\_div.c& 330&BN\_div&*&\cmark\\
+bn\_gcd.c& 192&int\_bn\_mod\_inverse&1.0 &\xmark\\
+bn\_gcd.c& 215&int\_bn\_mod\_inverse&7.9 &\cmark\\
+bn\_gcd.c& 237&int\_bn\_mod\_inverse&8.2 &\cmark\\
+bn\_gcd.c& 218&int\_bn\_mod\_inverse&14.9 &\cmark\\
+bn\_gcd.c& 240&int\_bn\_mod\_inverse&9.2 &\cmark\\
+bn\_lib.c& 147&BN\_num\_bits\_word&*&\cmark\\
+bn\_lib.c& 152&BN\_num\_bits\_word&12.6 &\cmark\\
+bn\_lib.c& 153&BN\_num\_bits\_word&*&\cmark\\
+bn\_lib.c& 156&BN\_num\_bits\_word&*&\cmark\\
+bn\_div.c& 384&BN\_div&17.2 &\cmark\\
+bn\_div.c& 330&BN\_div&11.9 &\cmark\\
+bn\_div.c& 334&BN\_div&3.8 &\cmark\\
+bn\_exp.c& 622&BN\_mod\_exp\_mont\_consttime&1.0 &\xmark\\
+bn\_exp.c& 741&BN\_mod\_exp\_mont\_consttime&1.0 &\xmark\\
+bn\_mont.c& 138&BN\_from\_montgomery\_word&*&\cmark\\
+bn\_mont.c& 139&BN\_from\_montgomery\_word&*&\cmark\\
+bn\_mont.c& 140&BN\_from\_montgomery\_word&*&\cmark\\
+bn\_mont.c& 142&BN\_from\_montgomery\_word&*&\cmark\\
+bn\_mont.c& 152&BN\_from\_montgomery\_word&*&\cmark\\
+bn\_asm.c& 733&bn\_sqr\_comba8&*&\cmark\\
+bn\_asm.c& 592&bn\_mul\_comba8&*&\cmark\\
+bn\_mont.c& 98&BN\_from\_montgomery\_word&0.0 &\xmark\\
+bn\_div.c& 330&BN\_div&0.3 &\xmark\\
+bn\_div.c& 330&BN\_div&0.3 &\cmark\\
+\hline
+\end{tabular}
+\end{table}
+
 \subsection{Benchmarks}\label{sec:eval_countermeasures}

### 2021-05-23 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 We are interested if those leaked functions are fixed in the updated version.
-Note that \ctool{} can analyze the side-channel leakages at both the byte granularity and the cache line granularity.
-We show the result analyzed with cache line granularity.
-We compare the result with \tool{}, a symbolic analysis-based side-channel quantification tool.
-\tool{} can tell which line in the source code actually leaks the information.
-So it is possible that one function has several leakage sites.
-Suppose the function has two leakages sites, and they leak $a$ and $b$ bits, respectively.
-We use the set $(a, b)$ to represent the result of \tool{}.
+Note that \ctool{} can analyze the side-channel leakages at both the byte granularity and the cache line granularity. We show the result analyzed with cache line granularity.
 
 \begin{table}[!ht]
-\centering\tiny\scriptsize
+\centering
 \caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0.
@@
 \begin{threeparttable}
-\begin{tabular}{llrrc}
+\begin{tabular}{llrc}
 \hline
-\textbf{File}  & \textbf{Vulnerable Function} & \textbf{\tool{} Result (bits)} & \textbf{\ctool{} Result (bits)} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
-bn\_lib.c& BN\_num\_bits\_word&(*, *, *, *, *, 17.2, 12.6)& 5.7 & \cmark\\
-bn\_lib.c& bn\_correct\_top& 1.7 & 7.6 & \cmark\\
-bn\_lib.c& BN\_ucmp&*& 6.7 & \cmark\\
-ct\_b64.c& \_\_udivdi3&5.9 &4.3 & \cmark\\
-bn\_gcd.c& int\_bn\_mod\_inverse&(14.9, 9.2, 8.2, 7.9, 1.0) & 7.7 & \cmark\tnote{1} \\
-bn\_exp.c& BN\_mod\_exp\_mont\_consttime& (1.0, 1.0) & 1.0 & \xmark\\
-bn\_mont.c& BN\_from\_montgomery\_word\tnote{2}& (*, *, *, *, *, *, 0.0)& 9.7 &\cmark\\
-bn\_mont.c& BN\_from\_montgomery\_word& 0.0& 0.1 &\xmark\\
+\textbf{File}  & \textbf{Vulnerable Function} & \textbf{Result (bits)} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
+bn\_lib.c& BN\_num\_bits\_word& 5.7 & \cmark\\
+bn\_lib.c& bn\_correct\_top&  7.6 & \cmark\\
+bn\_lib.c& BN\_ucmp& 6.7 & \cmark\\
+ct\_b64.c& \_\_udivdi3&4.3 & \cmark\\
+bn\_gcd.c& int\_bn\_mod\_inverse & 7.7 & \cmark\tnote{1} \\
+bn\_exp.c& BN\_mod\_exp\_mont\_consttime&  1.0 & \xmark\\
+bn\_mont.c& BN\_from\_montgomery\_word\tnote{2}& 9.7 &\cmark\\
+bn\_mont.c& BN\_from\_montgomery\_word&  0.1 &\xmark\\
 
-bn\_asm.c& bn\_sqr\_comba8&9.3&5.0& \cmark\\
-bn\_div.c& BN\_div&(17.2, 11.9, 3,8, 0.3, 0.3) & 7.3  & \cmark\\
-rsa\_ossl.c& rsa\_ossl\_mod\_exp& 1.0 & 4.8 & \cmark\\
-encode.c & conv\_bin2ascii & Not Found & 1.2 & \xmark\\
+bn\_asm.c& bn\_sqr\_comba8&5.0& \cmark\\
+bn\_div.c& BN\_div & 7.3  & \cmark\\
+rsa\_ossl.c& rsa\_ossl\_mod\_exp& 4.8 & \cmark\\
+encode.c & conv\_bin2ascii & 1.2 & \xmark\\
 \hline
@@
 \begin{tablenotes}
-    \scriptsize
     \item[1] The leakage site at line 144 (OpenSSL 1.1.1) are not fixed.\\

### 2021-05-23 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 \section{Precise Analysis on Multiple-trace Attacks}
-This chapter presents an approach that can give a conservative estimate of the amount of leaked information by address-based side-channel attacks.
-Those attacks exploit the data-flow from secrets to load address and the data-flow from the data-flow from secrets to branch conditions to retrieve secrets based on the observation on the memory accesses.
-Despite those kinds of side-channel leakages that have been discovered for decades, the up-to-date software still has some side channel leakages.
-For some of those vulnerabilities, developers do not fix them because they think those side-channel vulnerabilities are not important.
-To show the importance of those side-channel leakages, one way is to demonstrate an end-to-end attack based on the vulnerability.
-However, demonstrating an end-to-end attack often need a lot of manual effort and the domain knowledge of the victim program, which is not often the case in practices.
-It is good to have a tool that can assess the severity level of those side channel leakages automatically.
-So it would be better to have a proper metric to quantify the side-channel leakage.
-However, we find previous side-channel quantification tools are developed to ensure the noninterference of the program.
-They use over approximation heuristics method to quantify the leakage.
-For example, CacheAudit estimates that a 128-bit AES encryption can leak more than 128 bits.
-As a result, even those tool reports severe leakage, it does not mean the program has a truly severe leakage.
+This paper presents an approach that tries to give a conservative
+estimate of the amount of leaked information by address-based
+side-channel attacks. Those attacks exploit the data-flow from secrets
+to load address and the data-flow from the data-flow from secrets to
+branch conditions to retrieve secrets based on the observation on the
+memory accesses. Although those kinds of side-channel leakages have
+been discovered for decades, the up-to-date software still has some
+side-channel leakages. For some of those vulnerabilities, developers
+do not fix them because they think those side-channel vulnerabilities
+are not important. To show the importance of those side-channel
+leakages, one way is to demonstrate an end-to-end attack based on the
+vulnerability. However, demonstrating an end-to-end attack often need
+a lot of manual effort and the domain knowledge of the victim program,
+which is not often the case in practice. It is good to have a tool
+that automatically assesses the severity level of those side-channel
+leakages. So it would be better to have a proper metric to quantify
+the side-channel leakage. However, we find previous side-channel
+quantification tools are developed to ensure the noninterference of
+the program. They use the over-approximation heuristics method to
+quantify the leakage. For example, CacheAudit estimates that a 128-bit
+AES encryption can leak more than 128 bits. As a result, even those
+tools report severe leakage, it does not mean the program has a truly
+severe leakage.
 
-Our tool can give the conservative estimation of the side-channel leakage based on Channel Capacity.
-The channel capacity measures the information flow between the source and the destination.
-One useful characteristic of channel capacity is not affected by the input of the input, which is useful because we cannot assume the input secrets of the software in practice.
-In the paper, we use the sampling result to over approximate the true value of the channel capacity.
-We prove the sampling method presented in the paper can only give the conservative estimation of the amount of the true leakage.
+Our tool can give a conservative estimation of the
+side-channel leakage based on Channel Capacity. The channel capacity
+measures the information flow between the source and the
+destination. One useful characteristic of channel capacity is not
+affected by the input, which is useful because we cannot
+assume the input secrets of the software in practice. In the paper, we
+use the sampling result to approximate the true value of the
+channel capacity. We prove the sampling method presented in the paper can only give the conservative estimation of the amount of the true leakage.
 
@@
 \ctool{} may have the coverage problem and can miss some side-channel vulnerabilities.
-It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control-flow with various inputs.
+It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control flow under various inputs.
 For other libraries like graphic rendering, machine learning, \ctool{} is very likely to miss some side-channel vulnerabilities.
 However, \ctool{} is not designed to find side-channel vulnerabilities.
-The goal of \ctool{} is to pick up those really severe side-channel vulnerabilities from the numerous vulnerabilities.
+The goal of \ctool{} is to pick up those really serious side-channel vulnerabilities from the numerous vulnerabilities.
 So we do not think it is the main limitation of \ctool{}.
@@
 
-\begin{figure}
-  \centering
-  \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
-int foo(uint8_t secret){
-  uint8_t index = 0, t;
-  index = (index+secret)%128; // The index contains secrets
-  ...
-  if(index == 0){             // Secret-dependent flows
-    bar(r, x, n)              // The observation
-  }
-  ...
-}
-\end{lstlisting}
-  \caption{The reported leaked functions are not the root cause of the vulernability}
-  \label{fig:limitation}
-\end{figure}
-
-Another limitation is that \ctool{} can only find the position in the code that leaks the sensitive information, but it is not the root cause of the leaks.
-Consider the example in Figure~\ref{fig:limitation}, it takes the secret as the input.
-At line 3, it calculates an index based on the value of the secret.
-Depending on the value of the index, it may or may not run the code at line 6.
-So line 5 is the reason that causes the vulnerability.
-But \ctool{} can only tell that line 6 can leak the information, despite it is not the root cause of the vulnerability.
-
 \section{Limitations}

### 2021-05-23 changelog.tex
Updates from Overleaf

--- 2021-05-20 changelog.tex
@@
 
-\section{Requested Changes}
+\begin{enumerate}
+\item \textbf{Fuzzing – need stronger motivation.}
+\item \textbf{Discuss the limitations of your research
+e.g., can only handle address based …
+you might want to include some discussion on the points (3), (4), and (5) below.}
+\item \textbf{Can you extend your research (especially the quantification part) to include other side channel signals?}
 
-\begin{enumerate}
-\item Fuzzing – need stronger motivation.
-\item Discuss the limitations of your research
-e.g., can only handle address based …
-you might want to include some discussion on the points (3), (4), and (5) below.
-\item Can you extend your research (especially the quantification part) to include other side channel signals?
-\item A bits vs. Q bits. Lower bounds?
+It is possible to extend the quantification part to include other side channel signals.
+The key here is to model the noise in reality.
+In my dissertation, I assume an attacker can have a noise-free observation.
+\item \textbf{A bits vs. Q bits. Lower bounds?
        Improve the presentation
        Make the comparison more meaningful
-       Etc.
-\item iid assumption – does it fit your research on side-channel?
-\item Some feedback I gave before your defense.
+       Etc.}
+\item \textbf{iid assumption – does it fit your research on side-channel?}
 
-Before the defense, Dr. Wu gave me the following feedback.
+\item \textbf{Some feedback I gave before your defense.}
+
+As suggested by Dr. Wu, I added a new chapter on Discussion and Limitations, and discussed potential ways and related work to the mitigated reported side.
+
+\item \textbf{Improve Grammar.}
+
+Dr. Larus helped me fix many grammar issues. I have revised the dissertation multiple times. In addition, I used Grammarly to proofread my dissertation.
 \end{enumerate}
-\section{Other Changes}
+
+I have Incorporated some discussions into my dissertation. Please let me know if you have any feedback.
 

### 2021-05-23 changelog.tex
Updates from Overleaf

@@
 
-It is possible to extend the quantification part to include other side channel signals.
-The key here is to model the noise in reality.
-In my dissertation, I assume an attacker can have a noise-free observation.
+It is possible to extend the quantification part to include other side-channel signals.
+The key is to model the noise (e.g., Sound, CPU usages, EM signals) properly.
+In my dissertation, I assume that an attacker can have a noise-free observation.
+While a noise-free observation is possible for some address-based side-channel attacks, the assumption is too ideal for many other side-channel attacks.
+The good news is that there are some mature methods in information theory to model the noises (e.g., Gaussian noise).
+The noisy-channel coding theorem provides a computable method to estimate the information can be reliably transferred between the source (confidential data) and the destination (attackers).
+From a research project aspect, I hope to have a stronger motivation before starting the project.
 \item \textbf{A bits vs. Q bits. Lower bounds?
@@
 \item \textbf{iid assumption – does it fit your research on side-channel?}
+
+The research in the dissertation
 

### 2021-05-23 changelog.tex
Updates from Overleaf

@@
 \begin{enumerate}
-\item \textbf{Fuzzing – need stronger motivation.}
+\item \textbf{Fuzzing – Why did you use fuzzing?}
+
+Abacus identifies and quantifies side-channel leakages in a single trace.
+So it suffers from the problem of code coverage.
+That is, Abacus may miss some-channel leakages.
+I have two choices at that time.
+First, I can use static analysis methods.
+
 \item \textbf{Discuss the limitations of your research
@@
 
-I have Incorporated some discussions into my dissertation. Please let me know if you have any feedback.
+I have incorporated some discussions into my dissertation. Please let me know if you have any feedback.
 

### 2021-05-24 changelog.tex
Updates from Overleaf

@@
 So it suffers from the problem of code coverage.
-That is, Abacus may miss some-channel leakages.
-I have two choices at that time.
-First, I can use static analysis methods.
+That is, Abacus misses side-channel leakages in the unexecuted code path.
+I have a few choices.
+I can use static analysis (model checking or static program analysis).
+Although I am interested in the static analysis, I am not a big fan of current static analysis tools, especially for side-channel analysis.
+There are several papers on static side-channel analysis.
+But nearly all of them have high false positive rates.
+My personal experience with Coverity is similar.
+It is a commercial static program analysis tool but still has plenty of false positives.
+
+On the other hand, there are many successful stories
 

### 2021-05-24 changelog.tex
Updates from Overleaf
update

@@
 My personal experience with Coverity is similar.
-It is a commercial static program analysis tool but still has plenty of false positives.
+It is a commercial static program analysis tool but still generates plenty of false positives.
 
@@
 It is possible to extend the quantification part to include other side-channel signals.
-The key is to model the noise (e.g., Sound, CPU usages, EM signals) properly.
+The key is to model the noises (e.g., Sound, CPU usages, EM signals) properly.
 In my dissertation, I assume that an attacker can have a noise-free observation.

### 2021-05-24 changelog.tex
Updates from Overleaf

@@
 
-Abacus identifies and quantifies side-channel leakages in a single trace.
-So it suffers from the problem of code coverage.
-That is, Abacus misses side-channel leakages in the unexecuted code path.
+There is no real reason for me to choose fuzzing over other methods. It is just my personal choice.
+
+Abacus identifies and quantifies side-channel leakages in a single trace. So it suffers from the problem of code coverage.  That is, Abacus misses side-channel leakages in the unexecuted code path.
+
 I have a few choices.
-I can use static analysis (model checking or static program analysis).
+First, I can use static analysis (model checking or static program analysis).
 Although I am interested in the static analysis, I am not a big fan of current static analysis tools, especially for side-channel analysis.
@@
 
-On the other hand, there are many successful stories
+On the other hand, there are many successful stories with dynamic tools (e.g., SAGE, AFL, Valgrind) in recent years.
 

### 2021-05-24 changelog.tex
Updates from Overleaf

@@
 Thank you for reviewing my dissertation.
-I have gone through the details of each comment and revised my dissertation multiple rounds to eliminate any logic flow and fix all the typos and grammar errors.
+I have gone through the details of each comment and revised my dissertation multiple rounds to eliminate any logic flows and fix all the typos and grammar errors.
 In summary, the revisions cover the following aspects.
@@
 
-I have a few choices.
+I have a few choices to address the limitations.
 First, I can use static analysis (model checking or static program analysis).
-Although I am interested in the static analysis, I am not a big fan of current static analysis tools, especially for side-channel analysis.
+Although I am interested in static analysis, I am not a big fan of current static analysis tools, especially for side-channel research.
 There are several papers on static side-channel analysis.
-But nearly all of them have high false positive rates.
-My personal experience with Coverity is similar.
-It is a commercial static program analysis tool but still generates plenty of false positives.
+Nearly all of these tools are used to prove the absence of side-channel leakages.
+However, most of them have high false-positive rates.
 
-On the other hand, there are many successful stories with dynamic tools (e.g., SAGE, AFL, Valgrind) in recent years.
+On the other hand, there are many success stories with dynamic tools (e.g., SAGE, AFL, Valgrind) in recent years.
+In particular, I find fuzzing is becoming a hot trend these years, especially after DARPA CGC in 2016.
 
@@
 you might want to include some discussion on the points (3), (4), and (5) below.}
+
+Like many other research projects,
+
 \item \textbf{Can you extend your research (especially the quantification part) to include other side channel signals?}

### 2021-05-24 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-This paper makes the following contributions:
+This chapter makes the following contributions:
 
@@
 \section{Background and Threat Model}
-In the section, we give an overview of the background knowledge of information theory and present the threat model of the paper.
+In the section, we give an overview of the background knowledge of information theory and present the threat model of the chapter.
 
@@
 
-In the paper, we use the channel capacity to describe the amount of information leakages through a channel.
+In the chapter, we use the channel capacity to describe the amount of information leakages through a channel.
 In information theory, the channel capacity is used to quantify the rate of information can be reliably transmitted over a channel.
@@
 Still, he can infer whether some memory addresses are accessed or not at various granularities after \textit{each run} of the victim program.
-We call the memory access information as the observation ($O$) in the rest of the paper.
+We call the memory access information as the observation ($O$) in the rest of the chapter.
 This is a typical scenario for most side-channel attacks.
@@
 
-In this paper, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs).
+In thios chapter, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs).
 To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.
@@
 And the two leakages Figure~\ref{chapter5:fig:multiple} (b) are dependent.
-In this paper, for any two leakages, if $p < 0.03$, we think the two leakage sites are independent.
+In thios chapter, for any two leakages, if $p < 0.03$, we think the two leakage sites are independent.
 We use the above method to test if any two leakage sites are independent for each leakage point.
@@
 \subsubsection{Leakage Detection} The access of the address is secret-dependent if $ \exists\, k_{i1}, k_{i2} \in K, \, B^{addr}_{k_i1} \oplus  B^{addr}_{k_i2} =1 $.
-In the paper, we perform the logical exclusive OR operation on every boolearn value in the same address.
+In the chapter, we perform the logical exclusive OR operation on every boolearn value in the same address.
 If the result is $1$, then the address is vulnerable to the side-channel attacks.

### 2021-05-24 changelog.tex
Updates from Overleaf

@@
 
-I have a few choices to address the limitations.
+I have a few choices to address the limitation.
 First, I can use static analysis (model checking or static program analysis).
@@
 
-Like many other research projects,
+Like many other research projects, the research presented in the dissertation has a few limitations.
+
+a. It is true that the methods in the dissertation can not find all kinds of side-channel leakages. No tool can find all forms of leakages. Even for address-based side-channel leakages, Abacus
 

### 2021-05-24 changelog.tex
Updates from Overleaf

@@
 
-There is no real reason for me to choose fuzzing over other methods. It is just my personal choice.
+It is just my personal choice.
 
@@
 
-a. It is true that the methods in the dissertation can not find all kinds of side-channel leakages. No tool can find all forms of leakages. Even for address-based side-channel leakages, Abacus
+a.
+It is true that the methods in the dissertation can not find all kinds of side-channel leakages.
+No tool can find all forms of leakages.
+Even for address-based side-channel leakages, Abacus and Quincunx can not find all the leakages due to the code coverage problem.
+
+b.
+The quantification result only applies to specific threat models.
+For example, Abacus quantifies the number of leaked bits during one real execution.
+So it is possible that one leakage site leaks little information in one execution but leaks much information in another execution.
+
+c.
+It is true that the research in the dissertation can only handle address-based side-channel attacks.
+Many side-channel attacks infer secret data based on other side-channel signals (e.g, timing, EM signals).
+However, the root cause of many of those attacks is still the same.
+That is, the program accesses different addresses when it processes different input secrets.
 
@@
 The key is to model the noises (e.g., Sound, CPU usages, EM signals) properly.
-In my dissertation, I assume that an attacker can have a noise-free observation.
+In my dissertation, we assume that an attacker can have a noise-free observation.
 While a noise-free observation is possible for some address-based side-channel attacks, the assumption is too ideal for many other side-channel attacks.
@@
        Etc.}
+
+To address the above concerns, I have made the following revisions.
+
+a. I revised the description in Chapter 5. I abandoned the term lower bound.
+
+d. I revised Table 5.3. The evaluation section does not compare Quincunx with Abacus in the current version because they have different threat models.
 \item \textbf{iid assumption – does it fit your research on side-channel?}
 
-The research in the dissertation
+It is true that Quincunx requires the random input variables to be independent and identically distributed.
+That's why I applied a blackbox fuzzing instead of a coverage-guided fuzzing.
+As long as each time we get a random input from the whole input space (Populations) that is independent of the previous input, the input variables should satisfy the i.i.d.
+assumption.
+For AES-128 encryption, each time we randomly generate a 128 bit key from $0$ to $2^{128}$, the sequence of key values follows the i.i.d.
+assumption.
+
+The situation is a little different for a deep learning model.
+In the dissertation, we evaluated Quincunx on a deep learning model.
+Each time, we randomly select an item from a dataset (Samples).
+If the dataset is biased, then we can not get the correct results.
+The good news is that the most well-known data in machine learning is i.i.d.
+i.i.d.
+is the foundation of supervised machine learning algorithms.
+In my dissertation, we used MINIST, a well-known handwriting dataset.
+We believe the dataset is i.i.d.
+
+I have revised my dissertation to include the discussion on iid.
 

### 2021-05-24 changelog.tex
Updates from Overleaf

@@
        Etc.}
+       \textbf{}
+It is hard to understand Entropy.
+There is a rumor about entropy between John von Neumann and Claude Shannon.
+When Shannon developed the concept of information theory, he did not have a good idea to name the measurement of uncertainty in a system.
+Neumann told Shannon, ``You should call it entropy, for two reasons.
+In the first place your uncertainty function has been used in statistical mechanics under that name, so it already has a name.
+\textbf{In the second place, and more important, nobody knows what entropy really is, so in a debate you will always have the advantage.}''
 

### 2021-05-25 changelog.tex
Updates from Overleaf

@@
        Etc.}
-       \textbf{}
+
 It is hard to understand Entropy.
@@
 
-As suggested by Dr. Wu, I added a new chapter on Discussion and Limitations, and discussed potential ways and related work to the mitigated reported side.
+As suggested by Dr. Wu, I added a new chapter on Discussion and Limitations (Chapter 6), and discussed potential ways and related work to the mitigated reported side (Chapter 2).
 
@@
 
-I have incorporated some discussions into my dissertation. Please let me know if you have any feedback.
+I have incorporated some discussions above into my dissertation. Please let me know if you have any feedback.
 

### 2021-05-25 changelog.tex
Updates from Overleaf

@@
 
-It is hard to understand Entropy.
+It is hard to explain Entropy.
 There is a rumor about entropy between John von Neumann and Claude Shannon.
@@
 In the first place your uncertainty function has been used in statistical mechanics under that name, so it already has a name.
-\textbf{In the second place, and more important, nobody knows what entropy really is, so in a debate you will always have the advantage.}''
+In the second place, and more important, nobody knows what entropy really is, so in a debate you will always have the advantage.''
 
@@
 
-d. I revised Table 5.3. The evaluation section does not compare Quincunx with Abacus in the current version because they have different threat models.
+b. I revised Table 5.3. The evaluation section does not compare Quincunx with Abacus in the current version because they have different threat models.
 \item \textbf{iid assumption – does it fit your research on side-channel?}

### 2021-05-25 changelog.tex
Updates from Overleaf

@@
 In the first place your uncertainty function has been used in statistical mechanics under that name, so it already has a name.
-In the second place, and more important, nobody knows what entropy really is, so in a debate you will always have the advantage.''
+In the second place, and more important, nobody knows what entropy really is, so in a debate you will always have the advantage.'' In my dissertation proposal, everyone does not really understand how we quantify the amount of leaked information in Abacus.
+In my final defense, everyone is confused with the term ``lower bounds'' except Dr.
+Wu.
 

### 2021-05-25 changelog.tex
Updates from Overleaf

@@
 In the second place, and more important, nobody knows what entropy really is, so in a debate you will always have the advantage.'' In my dissertation proposal, everyone does not really understand how we quantify the amount of leaked information in Abacus.
-In my final defense, everyone is confused with the term ``lower bounds'' except Dr.
-Wu.
+In my final defense, everyone is confused with the term ``lower bounds'' except my advisor.
+
+a. Abacus quantifies the amount of leaked information for a given address access behavior.
+
+b.
+
+c. I agree with Dr. Liu's comments that the quantification metrics in Chapter 4 and Chapter 5 are different. I
 
@@
 
-b. I revised Table 5.3. The evaluation section does not compare Quincunx with Abacus in the current version because they have different threat models.
+b. I revised Table 5.3. The evaluation section does not compare Quincunx with Abacus in the current version because they are calculated with different methods and have different threat models.
 \item \textbf{iid assumption – does it fit your research on side-channel?}

### 2021-05-25 changelog.tex
Updates from Overleaf

@@
 b.
+Quincunx defines the amount of leaked information by the empirical entropy of the observations.
+For a determinism program, channel capacity is the tight upper bound of the the empirical entropy of the observations.
 
-c. I agree with Dr. Liu's comments that the quantification metrics in Chapter 4 and Chapter 5 are different. I
+c.
+I agree with Dr.
+Liu's comments that the quantification metrics in Chapter 4 and Chapter 5 are different.
+The reason that I compare them together in Table 5.3 is that they have the same dimensional unit (bit) under the dimensional analysis.
+I have removed the comparison in the current version.
 

### 2021-05-25 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 In 1996, Kocher published the first side-channel attack in the literature~\cite{kocher1996timing}.
-He demonstrated that an attacker could break cryptosystems like RSA or Diffie-Hellman by measuring the execution time of a simple modular exponentiation operation.
+He demonstrated that an attacker could break cryptosystems such as RSA or Diffie-Hellman by measuring the execution time of a simple modular exponentiation operation.
 The simple modular exponentiation calculates the remainder of an exponent divided by an integer.

### 2021-05-25 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 CacheD performs better than CaSym.
-However, it still can not handle large programs like RSA directly.
+However, it still can not handle large programs such as RSA directly.
 It uses some domain knowledge to analyze only part of the program.
@@
 It is a true leakage.
-The leakage can also be identified by previous tools like CacheD.
+The leakage can also be identified by previous tools such as CacheD.
 Similarly, we can model the memory access at line 6 with the formula:  $10 + m + (k_1 \mod 32) >> 6  \neq 10 + m + (k_2 \mod 32) >> 6$.
@@
 There are two kinds of control-transfer instructions: the unconditional control-transfer instructions and the conditional transfer instructions.
-The unconditional instructions, like CALL, JUMP, RET transfer control from one code segment location to another.
+The unconditional instructions, such as CALL, JUMP, RET transfer control from one code segment location to another.
 Since the transfer is independent of the input sensitive information, an attacker was not able to infer any sensitive information from the control-flow.
@@
 
-The conditional control-flow transfer instructions, like conditional jumps, depending on CPU states, may or may not transfer control flows.
+The conditional control-flow transfer instructions, such as conditional jumps, depending on CPU states, may or may not transfer control flows.
 For conditional jumps, the CPU will test if certain condition flag

### 2021-05-25 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 Second, the
-precise model counting approaches, like Davis-Putnam-Logemann-Loveland (DPLL)
+precise model counting approaches, such as Davis-Putnam-Logemann-Loveland (DPLL)
 search, have difficulty scaling up to large problem sizes.
@@
 We analyze the table lookup with \tool{}.
-It is a common operation used by symmetric ciphers like AES.
+It is a common operation used by symmetric ciphers such as AES.
 Figure~\ref{fig:chapter4:big_lookup} is from the original AES reference implementation.

### 2021-05-25 Chapter-7/Chapter-7.tex
Updates from Overleaf

@@
 \textbf{Kernel Space Side-channel Vulnerability Detection.} There are several side-channel vulnerability detection tools together with the dissertation tool.
-Most of the tools are designed to analyze the side-channel leakages in user-level applications like cryptographic libraries.
+Most of the tools are designed to analyze the side-channel leakages in user-level applications such as cryptographic libraries.
 It is reasonable since many side-channel attacks are used to break cryptographic applications.
@@
 First, our proposed tools in the dissertation rely on the dynamic binary instrumentation frameworks to collect the runtime information.
-As for kernel programs, a similar task can be achieved by some whole system emulators like BitBlaze~\cite{song2008bitblaze} and S2E~\cite{chipounov2012s2e}.
+As for kernel programs, a similar task can be achieved by some whole system emulators such as BitBlaze~\cite{song2008bitblaze} and S2E~\cite{chipounov2012s2e}.
 S2E uses a modified Linux kernel and QEMU to trace the kernel components.

### 2021-05-25 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 Recent work can identify side-channel leakages.
-But those tools can only work on small programs or need to apply domain knowledge of the target program to simplify the analysis.
+But these tools can only work on small programs or need to apply domain knowledge of the target program to simplify the analysis.
     \item Side-channel vulnerabilities are ubiquitous.
@@
 Moreover, some vulnerable implementations perform better.
-Recent work can identify thousands of leaked points, but most of them are not patched by developers because those leakages are either false positives or leaked very little information.
+Recent work can identify thousands of leaked points, but most of them are not patched by developers because these leakages are either false positives or leaked very little information.
 \end{enumerate}

### 2021-05-25 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 The DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort.
-After we manually analyze those leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which partially explain why developers are not interested in fix all the leakages.
+After we manually analyze these leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which partially explain why developers are not interested in fix all the leakages.
 \section{Precise Analysis on Single-trace Attacks}
@@
 estimate of the amount of leaked information by address-based
-side-channel attacks. Those attacks exploit the data-flow from secrets
+side-channel attacks. These attacks exploit the data-flow from secrets
 to load address and the data-flow from the data-flow from secrets to
 branch conditions to retrieve secrets based on the observation on the
-memory accesses. Although those kinds of side-channel leakages have
+memory accesses. Although these kinds of side-channel leakages have
 been discovered for decades, the up-to-date software still has some
-side-channel leakages. For some of those vulnerabilities, developers
-do not fix them because they think those side-channel vulnerabilities
-are not important. To show the importance of those side-channel
+side-channel leakages. For some of these vulnerabilities, developers
+do not fix them because they think these side-channel vulnerabilities
+are not important. To show the importance of these side-channel
 leakages, one way is to demonstrate an end-to-end attack based on the
@@
 which is not often the case in practice. It is good to have a tool
-that automatically assesses the severity level of those side-channel
+that automatically assesses the severity level of these side-channel
 leakages. So it would be better to have a proper metric to quantify
@@
 quantify the leakage. For example, CacheAudit estimates that a 128-bit
-AES encryption can leak more than 128 bits. As a result, even those
+AES encryption can leak more than 128 bits. As a result, even these
 tools report severe leakage, it does not mean the program has a truly
@@
 It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control flow under various inputs.
-For other libraries like graphic rendering, machine learning, \ctool{} is very likely to miss some side-channel vulnerabilities.
+For other libraries such as graphic rendering, machine learning, \ctool{} is very likely to miss some side-channel vulnerabilities.
 However, \ctool{} is not designed to find side-channel vulnerabilities.
@@
 However, users of \ctool{} should be aware of the code coverage problem.
-
-\section{Limitations}

### 2021-05-25 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
     \item We design a symbolic analysis method that can detect secret-dependent control-flow transfers and secret-dependent data accesses.
-The key idea is to only symbolically execute those machine instructions that are relevant to vulnerabilities while executing other instructions natively.
+The key idea is to only symbolically execute machine instructions that are relevant to vulnerabilities while executing other instructions natively.
 We implement the above method in a tool called \detect{}.
@@
 In addition, \detect{} finds new leakages which are not identified by previous tools.
-We confirmed those findings with developers.
+We confirmed these findings with developers.
 \end{itemize}

### 2021-05-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 For a detailed overview of recent side-channel attacks, we refer to the following survey paper~\cite{ge2018survey}.
-We classified those side-channel attacks into two categories: cache-level channels and page-level channels.
+We classified these side-channel attacks into two categories: cache-level channels and page-level channels.
 
@@
 Access-based attacks often happen in the cloud computing environment when the attacker and victim share the same hardware (e.g., LLC cache).
-Examples of those attacks include cache template attacks~\cite{191010}, Prime+Probe attacks~\cite{liu2015last}, and Flush+Reload attacks~\cite{yarom2014flush+}.
+Examples of these attacks include cache template attacks~\cite{191010}, Prime+Probe attacks~\cite{liu2015last}, and Flush+Reload attacks~\cite{yarom2014flush+}.
 \subsubsection*{Trace-based Attacks}
@@
 However, such implementations are vulnerable to side-channels and can be exploited to retrieve the whole key~\cite{bonneau2006cache}.
-In addition to the reference implementation, those libraries also have side-channel mitigated versions.
-However, recent studies also show those versions (e.g., AES-NI) also have side-channel vulnerabilities caused by compiler optimizations and human mistakes~\cite{217537}.
+In addition to the reference implementation, these libraries also have side-channel mitigated versions.
+However, recent studies also show these versions (e.g., AES-NI) also have side-channel vulnerabilities caused by compiler optimizations and human mistakes~\cite{217537}.
 The situation is even worse for asymmetric ciphers (e.g., Diffie-Hellman, RSA, ECDSA).
 These ciphers have a lot of big number calculations.
-It is hard to implement those calculations to be completely side-channel resistant.
-Recent work~\cite{arnaud2013timing,yarom2017cachebleed,yarom2014flush+} has demonstrated several end-to-end attacks to recover the private key of those ciphers.
+It is hard to implement these calculations to be completely side-channel resistant.
+Recent work~\cite{arnaud2013timing,yarom2017cachebleed,yarom2014flush+} has demonstrated several end-to-end attacks to recover the private key of these ciphers.
 
@@
 
-\textbf{Abstraction.} The second category of those tools belongs to the field of abstractions.
+\textbf{Abstraction.} The second category of these tools belongs to the field of abstractions.
 Tools based on these approaches use abstraction to generate approximations to model the semantics of computer programs.

### 2021-05-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 
-Those methods usually follow the steps below.
+These methods usually follow the steps below.
 Suppose a program $P$ has $k$ as the input.
-Those approaches first retrieve the relationship between the $k$ and temporary values during the execution.
+These approaches first retrieve the relationship between the $k$ and temporary values during the execution.
 After that, they should have a cache or memory access model and model the side-channel leakage as a math constraint.
-By using SMT solvers to find different secret inputs that lead accesses to different locations in the memory or the cache, those approaches can determine if the program is vulnerable to side-channel attacks.
+By using SMT solvers to find different secret inputs that lead accesses to different locations in the memory or the cache, these approaches can determine if the program is vulnerable to side-channel attacks.
 Unlike to the trace comparison, the method is quite precise.
-Moreover, it can model multiple leakages precisely as the conjunction of those formulas.
+Moreover, it can model multiple leakages precisely as the conjunction of these formulas.
 However, these approaches have the following limitations.
@@
 For some projects, the tools can only handle the benchmarks in their papers properly.
-    \item Those tools heavily rely on SMT solvers.
-Despite SMT solvers having made incredible progress in performance, SMT solving is still the main bottleneck of those tools.
+    \item These tools heavily rely on SMT solvers.
+Despite SMT solvers having made incredible progress in performance, SMT solving is still the main bottleneck of these tools.
 SMT solvers are not good at non-linear arithmetic.
@@
 Recent studies show existing solvers still have bugs when dealing with real number calculations.
-Those calculations are also common in media libraries and machine learning applications.
+These calculations are also common in media libraries and machine learning applications.
 \end{itemize}
@@
 Side-channel attacks usually require attackers and victims to share some hardware resources (e.g., CPU cache, MMU).
-A straightforward way to defend those attacks is to partition the resources and ensure the attacker and the victim never share the same hardware resource~\cite{Page2005PartitionedCA,shi2011limiting,liu2016catalyst}.
-For example, in a cloud computing environment, several virtual machines (VMs) can be hosted on the same physical machine and those VMs share the same last-level cache (LLC).
+A straightforward way to defend these attacks is to partition the resources and ensure the attacker and the victim never share the same hardware resource~\cite{Page2005PartitionedCA,shi2011limiting,liu2016catalyst}.
+For example, in a cloud computing environment, several virtual machines (VMs) can be hosted on the same physical machine and these VMs share the same last-level cache (LLC).
 Researchers proposed different methods to partition the LLC such as cache coloring~\cite{shi2011limiting}, using Intel Cache Allocation Technology~\cite{liu2016catalyst}.
@@
 the number of solutions. Intuitively, such a model counter should traverse the whole
-search space to find all the satisfying solutions. Consequently, the exact model counter is very slow. Those model counters have difficulty scaling up to real-world programs.
+search space to find all the satisfying solutions. Consequently, the exact model counter is very slow. These model counters have difficulty scaling up to real-world programs.
 On the other hand, the approximate model counter is much faster compared with the exact model counter.
@@
 Some IR-level branches can be compiled into non-branch instructions like conditional moves.
-Those above limitations motivate us to implement a new trace-based binary analysis framework.
+The above limitations motivate us to implement a new trace-based binary analysis framework.

### 2021-05-25 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 First, although some tools~\cite{Brotzman19Casym} can find side-channel leakages in real-world software products, they can only analyze one code fragment at a time due to the expensive performance overhead.
-As a result, users of those tools sometimes need to cut off manually irrelevant code based on their experience.
+As a result, users of these tools sometimes need to cut off manually irrelevant code based on their experience.
 The trimming process is tedious and needs domain knowledge of the target software (e.g., which part of the code is more likely to have side-channel leakage sites).
-More importantly, if serious leakage sites are on the trimmed code, those tools will miss those leakage sites as well.
+More importantly, if serious leakage sites are on the trimmed code, these tools will miss leakage sites as well.
 
@@
 However, existing tools (e.g., CacheD) use a concrete base address.
-Under the circumstance, those tools may miss such vulnerabilities.
+Under the circumstance, these tools may miss such vulnerabilities.
 
 \subsection{Performance}
-The second limitation of current side-channel detection tools is the performance bottleneck, especially for those tools based on symbolic analysis.
+The second limitation of current side-channel detection tools is the performance bottleneck, especially for tools based on symbolic analysis.
 For example, CaSym can only analyze small programs.
@@
 some observations ($O$) of the program.
-Examples of those observations include the timing, CPU usages, and electromagnetic signals (EM).
+Examples of these observations include the timing, CPU usages, and electromagnetic signals (EM).
 In this dissertation, we use secret-dependent control flows and secret-dependent data
@@
 domain knowledge~\cite{Wang:2007:NCD:1250662.1250723} to simplify the analysis.
-Those tools interpret each
+These tools interpret each
 instruction and update memory cells and registers with formulas that
@@
 The primary purpose of the step is to generate constraints of the input sensitive information from the execution trace.
-If we give the target program a new input which is different from the original input that was used to generate the execution trace but still satisfies those constraints, as an attacker, he will have the same observations on control-flow transfers and data-access patterns.
+If we give the target program a new input which is different from the original input that was used to generate the execution trace but still satisfies these constraints, as an attacker, he will have the same observations on control-flow transfers and data-access patterns.
 
@@
 For some crypto libraries, we evaluate multiple versions.
-After that, we compare the evaluation results with the version history to track those leakages' patches.
+After that, we compare the evaluation results with the version history to track these leakages' patches.
 In summary, we evaluate our tool on the following libraries.
@@
 
-We refer to the examples or test cases of those libraries and write simple
+We refer to the examples or test cases of these libraries and write simple
 programs that use the crypto libraries. For symmetric encryption, the length
@@
 the analysis.
-While those optimizations do not introduce false positives, they may miss some
+While these optimizations do not introduce false positives, they may miss some
 vulnerabilities.
@@
 leakages as we have discussion the previous sections.
-We notice that the number of instructions in those traces are different due to the different analysis starting functions and building options during the evaluation.
+We notice that the number of instructions in these traces are different due to the different analysis starting functions and building options during the evaluation.
 Table~\ref{eval:cacheD} shows that
@@
 have a new \emph{secret input}, \detect{} can test more input secrets
-on those formulas within the same time to achieve better precision.
+on these formulas within the same time to achieve better precision.
 c) DATA tries to use leakage models (domain knowledge) to classify each leakage.
 The strength of \ctool{} is that it does not need such domain knowledge.
-DATA reports 278 control-flow and 460 memory-access leaks for the RSA implementation in OpenSSL 1.1.0f. Among those leakages, they find one new vulnerability in RSA after some manual analysis.
+DATA reports 278 control-flow and 460 memory-access leaks for the RSA implementation in OpenSSL 1.1.0f. Among these leakages, they find one new vulnerability in RSA after some manual analysis.
 \detect{} finds the vulnerability.  For each leakage site, \detect{} can provide
@@
 designed to be side-channel resistant from the library.
-Because those ciphers have no
+Because these ciphers have no
 data flow from secrets to branch conditions and load addresses.
 Monocypher should be safe under our threat models.
-We analyze those ciphers with \detect{}, and it reports no leaks.
+We analyze these ciphers with \detect{}, and it reports no leaks.
 This indicates that \detect{} is effective for validating countermeasures.

### 2021-05-25 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 input secrets and calculates an ``average'' estimation, which is different from real attack scenarios when the secret that an attacker wants to retrieve is fixed.
-As a consequence, those results are less useful to assess the severity level of each leakage site.
+As a consequence, these results are less useful to assess the severity level of each leakage site.
 
@@
 formulas precisely model side-channel vulnerabilities.
-Then we use the conjunction of those formulas to model the
+Then we use the conjunction of these formulas to model the
 leaks at a statement that appears in different location in
@@
 that some branches (e.g., A) or traces leak much more information than some others.
-Those kinds of branches can be vulnerable when an attacker's data is incorporate.
+These kinds of branches can be vulnerable when an attacker's data is incorporate.
 For example, the code will skip some of the calculation if the value is 0 in big
@@
 possible inputs that satisfy the logic formula groups. The key idea is to split
-those constraints into several small formulas and sample them independently.
+these constraints into several small formulas and sample them independently.
 We will introduce the method in the following subsection.
@@
 Suppose the address of the leakage site is $\addr{i}$, we use $c_{\addr{i}}$ to denote the constraint that models its side-channel leakage.
-For multiple leakage sites, we take the conjunction of those constraints to represent those leakage sites.
+For multiple leakage sites, we take the conjunction of these constraints to represent these leakage sites.
 
@@
 
-After we split those constraints into several small constraints, we count the number of solutions for each constraint. Even though the dimension has been
+After we split these constraints into several small constraints, we count the number of solutions for each constraint. Even though the dimension has been
 significantly reduced by the previous step, this is still a \#P problem.
@@
 software only use a few number of different cryptography libraries. Second, we choose some
-libraries which are well studied in the previous work. We can refer to those conslusions to
+libraries which are well studied in the previous work. We can refer to these conclusions to
 verify our results. Based on the two requirements, we evaluate \tool{} on the following libraries:
@@
 Symmetric encryption implementations in OpenSSL and mbedTLS have significant leakage due to their lookup table implementations. 
-\tool{} confirms that those leakage comes from table lookups.
+\tool{} confirms that these leakage comes from table lookups.
 The new implementation of OpenSSL has adopted several methods (e.g., one single S-box instead of four lookup tables, smaller lookup tables) to mitigate the problem.
-Those changes are rather easy but significantly decrease the total amount of leaked information as the quantification result indicates.
+These changes are rather easy but significantly decrease the total amount of leaked information as the quantification result indicates.
 

### 2021-05-25 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 Examples of these non-functional behaviors include acoustics, CPU usages, timing, EM signals, etc~\cite{agrawal2002side,hund2013practical,halevi2015keyboard,batina2019csi}.
-In summary, if the program has different execution behaviors when it processes various keys, an attacker can infer nontrivial information by observing those secret-dependent behaviors.
+In summary, if the program has different execution behaviors when it processes various keys, an attacker can infer nontrivial information by observing secret-dependent behaviors.
 While separate side-channel attacks may have different forms and patterns, we find that a large portion of them share the same fundamental reasons.
@@
 
-While removing those dependent memory-access patterns in existing software completely is hard and tedious, fixing some of the most dangerous leakages appears to be a feasible solution.
+While removing secret-dependent memory-access patterns in existing software completely is hard and tedious, fixing some of the most dangerous leakages appears to be a feasible solution.
 Previous studies on side-channel detections have shown their effectiveness in finding such code patterns.
-Developers can run the tool to analyze the side-channels leakages and fix those patterns.
-However, fixing all those leakages seem impossible for the following reasons.
+Developers can run the tool to analyze the side-channels leakages and fix these patterns.
+However, fixing all these leakages seem impossible for the following reasons.
 First, side-channels are inevitable.
@@
 Suppose one program has two leakage sites.
-It is hard to estimate the total effect of those two leakages.
+It is hard to estimate the total effect of two leakages.
 Any two leakages have some underlying complex relationships.
@@
 Attackers can guess the values of some temporary values.
-But those temporary values contain some knowledge of the original secret buffer.
+But temporary values contain some knowledge of the original secret buffer.
 
 Second, many side-channel leakage detection tools rely on some techniques like symbolic executions, taint analysis, and abstract interpretations~\cite{203878,182946,Brotzman19Casym,236338}.
-It is hard to implement those techniques from scratch.
+It is hard to implement these techniques from scratch.
 So they build the tool on top of existing binary analysis frameworks.
 Due to the limitations of existing binary analysis frameworks, it is hard to apply existing methods to analyze side-channels in non-cryptography libraries.
-For many other applications like machine learning, media, and graphic libraries built on the top architecture-dependent libraries (e.g., Intel MKL~\cite{wang2014intel}), those tools can not handle it.
+For many other applications like machine learning, media, and graphic libraries built on the top architecture-dependent libraries (e.g., Intel MKL~\cite{wang2014intel}), these tools can not handle it.
 Moreover, some binary analysis frameworks (e.g., Angr~\cite{shoshitaishvili2016state}) are limited in analyzing floating-point instructions.
-But the functionality of those applications heavily depends on floating-point calculations.
+But the functionality of these applications heavily depends on floating-point calculations.
 
-Third, while many existing tools can detect side-channel leakages, few of them can assess how severity level of those vulnerabilities~\cite{203878,182946,Brotzman19Casym,236338,217537,Wichelmann:2018:MFF:3274694.3274741}.
+Third, while many existing tools can detect side-channel leakages, few of them can assess how severity level of these vulnerabilities~\cite{203878,182946,Brotzman19Casym,236338,217537,Wichelmann:2018:MFF:3274694.3274741}.
 There are some tools~\cite{182946,Chattopadhyay:2017:QIL:3127041.3127044} that can quantify the information leakage.
-Those tools can give an upper bound estimation of each leakage site, which is useful to justify the software is secure if the reported leakage is zero.
-But those tools can not tell software developers how severe each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage.
+These tools can give an upper bound estimation of each leakage site, which is useful to justify the software is secure if the reported leakage is zero.
+But these tools can not tell software developers how severe each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage.
 The best way to estimate each leakage's severe level is to exploit the leakage and recover the information.
@@
 If the patterns can uniquely distinguish the input space, then we think the information is leaked totally.
-However, in real cases, many of those side-channel leakage patterns are not enough to distinguish each leakage site but can still discern some secret inputs.
-In those cases, we call those partial leakages leaks.
+However, in real cases, many of these side-channel leakage patterns are not enough to distinguish each leakage site but can still discern some secret inputs.
+In those cases, we call them partial leakages leaks.
 
@@
 Accordingly, if Definition~\ref{chapter5:def} says the vulnerability leakage has $m$ bits of leakages, then the vulnerability leaks at least $m$ bits of leakages.
-We can use the definition to detect those severe leakages.
+We can use the definition to detect these severe leakages.
 In the examples of Figure~\ref{chapter5:fig:example1} and Figure~\ref{chapter5:fig:example2}, because the secret input range from $0$ to $255$, we can calculate the precise value of the amount of information leakage by iterating each input keys.
@@
 At the point the memory is allocated, we use the tuple $(start\ address, length)$ to represent the buffer.
-In the following execution, we check if any memory access falls into the range of those tuples.
+In the following execution, we check if any memory access falls into the range of these tuples.
 If so, we add the memory access into the tuple.
@@
 Real-world software can have many side-channel vulnerabilities.
-Those vulnerabilities may spread throughout the whole program.
+These vulnerabilities may spread throughout the whole program.
 An adversary may exploit more than one side-channel vulnerabilities to gain more information~\cite{7163052, 191010}.
 In order to precisely quantify the
-total information leakage, we need to know the relation of those leakage sites.
+total information leakage, we need to know the relation of these leakage sites.
 
@@
 The front-end of \ctool{} is implemented in Python.
-It can generate random inputs and test the program with those inputs many times.
+It can generate random inputs and test the program with these inputs many times.
 The address record part is implemented as an Intel Pin tool plugin in C++ to record the bitmap for each input.
@@
 \ctool{} identify several functions that are vulnerable to side-channel attacks.
-We are interested if those leaked functions are fixed in the updated version.
+We are interested if these leaked functions are fixed in the updated version.
 Note that \ctool{} can analyze the side-channel leakages at both the byte granularity and the cache line granularity. We show the result analyzed with cache line granularity.
@@
 We find developers forget to propagate the flag in the caller, which results in the vulnerabilities in \textsf{BN\_div} and \textsf{int\_bn\_mod\_inverse}.
-Second, for those leakage sites that are not fixed by the developers, both \tool{} and \ctool{} report that they leak less amount of information.
+Second, for leakage sites that are not fixed by the developers, both \tool{} and \ctool{} report that they leak less amount of information.
 For example, function \textsf{BN\_mod\_exp\_mont\_consttime} check if the modulus is odd.

### 2021-05-25 Chapter-7/Chapter-7.tex
Updates from Overleaf

@@
 We model side-channel leakage sites as math constraints and use dynamic symbolic execution to generate constraints for possible leakages.
-Using statistical testing, \detect{} can identify the true leakages from those constraints.
+Using statistical testing, \detect{} can identify the true leakages from these constraints.
 \detect{} analyzes the side-channel leakages directly from X86 execution traces.
@@
 For example, GNU toolchains inset LFENCE before any possible vulnerable instructions, including all load instructions, all indirect branches, and return instructions.
-We plan only to change those points that are likely to leak sensitive information.
+We plan only to change points that are likely to leak sensitive information.
 Finally, with the tool presented in the dissertation, we can modify only part of the ``severe'' leakage sites.

### 2021-05-25 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 
+\ctool{} requires the random input variables to be independent and identically distributed (i.i.d.).
+That's why I applied a blackbox fuzzing instead of a coverage-guided fuzzing.
+As long as each time we get a random input from the whole input space (Populations) that is independent of the previous input, the input variables should satisfy the i.i.d.
+assumption.
+For AES-128 encryption, each time we randomly generate a 128 bit key from $0$ to $2^{128}$, the sequence of key values follows the i.i.d.
+assumption.
+The situation is a little different for a deep learning model.
+In the dissertation, we evaluated \ctool{} on a deep learning model.
+Each time, we randomly select an item from a dataset (Samples).
+If the dataset is biased, then we can not get the correct results.
+The good news is that the most well-known data in machine learning is i.i.d..
+i.i.d.
+is the foundation of supervised machine learning algorithms.
+In my dissertation, we used MINIST, a well-known handwriting dataset.
+We believe the dataset is i.i.d..
+
 \ctool{} is a dynamic approach.
@@
 However, \ctool{} is not designed to find side-channel vulnerabilities.
-The goal of \ctool{} is to pick up those really serious side-channel vulnerabilities from the numerous vulnerabilities.
+The goal of \ctool{} is to pick up really serious side-channel vulnerabilities from the numerous vulnerabilities.
 So we do not think it is the main limitation of \ctool{}.

### 2021-05-25 changelog.tex
Updates from Overleaf

@@
 a.
-It is true that the methods in the dissertation can not find all kinds of side-channel leakages.
+You are right that the methods in the dissertation can not find all kinds of side-channel leakages.
 No tool can find all forms of leakages.
@@
 For a determinism program, channel capacity is the tight upper bound of the the empirical entropy of the observations.
+That's why I used the term ``lower bound'' during my PhD defense.
+I have removed the term ``lower bound'' right know.
 
@@
 Dr. Larus helped me fix many grammar issues. I have revised the dissertation multiple times. In addition, I used Grammarly to proofread my dissertation.
+
 \end{enumerate}

### 2021-05-25 changelog.tex
update'

@@
 
-It is just my personal choice.
-
 Abacus identifies and quantifies side-channel leakages in a single trace. So it suffers from the problem of code coverage.  That is, Abacus misses side-channel leakages in the unexecuted code path.
@@
 Although I am interested in static analysis, I am not a big fan of current static analysis tools, especially for side-channel research.
-There are several papers on static side-channel analysis.
+There are many papers on static side-channel analysis.
 Nearly all of these tools are used to prove the absence of side-channel leakages.
@@
 On the other hand, there are many success stories with dynamic tools (e.g., SAGE, AFL, Valgrind) in recent years.
-In particular, I find fuzzing is becoming a hot trend these years, especially after DARPA CGC in 2016.
+In particular, fuzzing is becoming a hot trend these years, especially after DARPA CGC in 2016.
+The fuzzing method is suitable for a task such as side-channel detection.
+If a program executes two different code paths or accesses two different addresses with two different input values, the program is vulnerable to side-channel attacks.
+When we report the leakages sites to developers, we can tell them the two inputs.
+Developers can quickly reproduce the leakage sites with the inputs.
+Interestingly, there are a few (not many) related papers.
+That's why I used fuzzing at the beginning of the project.
 
@@
 
-Like many other research projects, the research presented in the dissertation has a few limitations.
+The research presented in the dissertation has a few limitations.
 
 a.
-You are right that the methods in the dissertation can not find all kinds of side-channel leakages.
+The methods in my dissertation can not find all kinds of side-channel leakages.
 No tool can find all forms of leakages.
 Even for address-based side-channel leakages, Abacus and Quincunx can not find all the leakages due to the code coverage problem.
+Some verification tools can prove the absence of side-channel leakages for some small code snippets.
+However, to the best of my knowledge, one tools as yet can prove the absence of side-channel leakages in production software.
 
@@
 c.
-It is true that the research in the dissertation can only handle address-based side-channel attacks.
+The research in the dissertation can only handle address-based side-channel attacks.
 Many side-channel attacks infer secret data based on other side-channel signals (e.g, timing, EM signals).
-However, the root cause of many of those attacks is still the same.
+However, the root cause of these attacks is still the same.
 That is, the program accesses different addresses when it processes different input secrets.
+Under the circumstance, our methods can still detect these attacks.
 
@@
 The good news is that there are some mature methods in information theory to model the noises (e.g., Gaussian noise).
-The noisy-channel coding theorem provides a computable method to estimate the information can be reliably transferred between the source (confidential data) and the destination (attackers).
+The noisy-channel coding theorem provides a computable method to estimate the information that can be reliably transferred over a channel between secret data and attackers' observations.
 From a research project aspect, I hope to have a stronger motivation before starting the project.
@@
 Neumann told Shannon, ``You should call it entropy, for two reasons.
-In the first place your uncertainty function has been used in statistical mechanics under that name, so it already has a name.
+In the first place,your uncertainty function has been used in statistical mechanics under that name, so it already has a name.
 In the second place, and more important, nobody knows what entropy really is, so in a debate you will always have the advantage.'' In my dissertation proposal, everyone does not really understand how we quantify the amount of leaked information in Abacus.

### 2021-05-25 changelog.tex
Updates from Overleaf

@@
 Some verification tools can prove the absence of side-channel leakages for some small code snippets.
-However, to the best of my knowledge, one tools as yet can prove the absence of side-channel leakages in production software.
+However, to the best of my knowledge, no tools as yet can prove the absence of side-channel leakages in production software.
 
@@
 That is, the program accesses different addresses when it processes different input secrets.
-Under the circumstance, our methods can still detect these attacks.
+Under the circumstance, our methods can still detect these leakage sites.
 
@@
 
-a. Abacus quantifies the amount of leaked information for a given address access behavior.
+a.
+Abacus quantifies the amount of leaked information for a given address access behavior.
+It is a measure of the amount of leaked information that an attacker can get, given that another event has already occurred.
 
@@
 Quincunx defines the amount of leaked information by the empirical entropy of the observations.
-For a determinism program, channel capacity is the tight upper bound of the the empirical entropy of the observations.
+For a determinism program, channel capacity is the tight upper bound of the the empirical entropy of the observation.
 That's why I used the term ``lower bound'' during my PhD defense.
-I have removed the term ``lower bound'' right know.
+I have removed the term ``lower bound'' to avoid any confusion in my dissertation.
 

### 2021-05-25 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 assumption.
-The situation is a little different for a deep learning model.
+The situation is a little different for machine learning libraries.
 In the dissertation, we evaluated \ctool{} on a deep learning model.
@@
 If the dataset is biased, then we can not get the correct results.
-The good news is that the most well-known data in machine learning is i.i.d..
+The good news is that the most well-known data set in machine learning is i.i.d..
 i.i.d.
@@
 In my dissertation, we used MINIST, a well-known handwriting dataset.
+The dataset is widely used in many supervised machine learning tasks.
 We believe the dataset is i.i.d..

### 2021-05-25 Chapter-5/Chapter-5.tex
Update Chapter-5.tex
Updates from Overleaf

@@
 However, in real cases, many of these side-channel leakage patterns are not enough to distinguish each leakage site but can still discern some secret inputs.
-In those cases, we call them partial leakages leaks.
+In these cases, we call them partial leakages leaks.
 
@@
 
-This chapter makes the following contributions:
+In this work, we make the following contributions:
 
@@
 
-  \item We propose a novel method that automatically detects and analyzes the effect of each side-channel leakage site.
-Our analysis combines information from both the source code and the runtime execution, which makes the method more effective in finding the leakages.
-The method can combine multiple leakage sites to retrieve more information as well.
+  \item We propose a method that automatically detects and analyzes the
+  effect of each side-channel leakage site. Our analysis combines
+  information from both the source code and the run-time execution,
+  which makes the method more effective in finding the leakages. The
+  technique can combine multiple leakage sites to retrieve more
+  information as well.
 
-  \item We analyze the amount of information leakage from side-channel vulnerabilities based on the channel capacity.
-We propose a method that can estimate the lower bound of information leakages.
-The theory can serve as the foundation of future work on quantifying the information leakage based on the fuzzing.
+  \item We analyze the amount of information leakage from side-channel
+  vulnerabilities based on the channel capacity.   The
+  information leakage our tool reports for each leakage
+  site is quite precise and thus can reflect the severity level of the
+  leakage.
 
-  \item We implement the above method in a tool called \ctool{} and evaluate the tool with several benchmarks and several real-world applications such as OpenSSL, mbedTLS, TinyDNN, and GTK.
-The results show that our tool can detect and quantify the side-channel leakages effectively.
-Moreover, the leakage reports given by the \ctool{} can help developers fix the reported vulnerabilities.
+  \item We implement the above method in a tool called \ctool{} and
+  evaluate the tool with several benchmarks and several real-world
+  applications such as OpenSSL, mbedTLS, TinyDNN, and GTK\@. The results
+  show that our tool can detect and quantify the side-channel leakages
+  effectively. Moreover, the leakage reports given by the \ctool{} can
+  help developers fix the reported vulnerabilities.
 \end{itemize}

### 2021-05-25 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 \section{Fast and Precise Side-channel Vulnerability Detection}
-\textbf{Coverage.} \detect{} works on native x86 execution traces.
+\subsection*{Coverage} \detect{} works on native x86 execution traces.
 The design, which is very precise in terms of true leakages compared to other static source code method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also share the common limitations of dynamic approaches.
@@
 
-\textbf{Design Choices.} At the early stage of the project, we use SMT solvers to get the solutions of constraints.
+\subsection*{Design Choices.} At the early stage of the project, we use SMT solvers to get the solutions of constraints.
 However, we find for some ciphers (RSA), \detect{} times out after several days.
@@
 
-\textbf{Cache Model.} We use a simple cache model in this work.
+\subsection*{Cache Model} We use a simple cache model in this work.
 Recent work~\cite{Brotzman19Casym,182946} uses an LRU cache.
@@
 
-\textbf{Leakages.} While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers.
+\subsection*{Leakages.} While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers.
 The DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort.

### 2021-05-25 changelog.tex
Updates from Overleaf

@@
 
-It is possible to extend the quantification part to include other side-channel signals.
-The key is to model the noises (e.g., Sound, CPU usages, EM signals) properly.
+It is possible to extend the quantification part to include other side-channel signals (e.g., Sound, CPU usages, EM signals).
+The key is to model the noises properly.
 In my dissertation, we assume that an attacker can have a noise-free observation.
@@
 
-The situation is a little different for a deep learning model.
+The situation is a little different for a machine learning library.
 In the dissertation, we evaluated Quincunx on a deep learning model.
 Each time, we randomly select an item from a dataset (Samples).
-If the dataset is biased, then we can not get the correct results.
+If the dataset is biased, then we can not get correct results.
 The good news is that the most well-known data in machine learning is i.i.d.

### 2021-05-25 changelog.tex
Updates from Overleaf

@@
 I have a few choices to address the limitation.
-First, I can use static analysis (model checking or static program analysis).
+First, I can use static methods (verification or static program analysis).
 Although I am interested in static analysis, I am not a big fan of current static analysis tools, especially for side-channel research.
@@
 The fuzzing method is suitable for a task such as side-channel detection.
-If a program executes two different code paths or accesses two different addresses with two different input values, the program is vulnerable to side-channel attacks.
+If a program executes two different code paths or accesses two different variables with two different input values, the program is vulnerable to side-channel attacks.
 When we report the leakages sites to developers, we can tell them the two inputs.
@@
 While a noise-free observation is possible for some address-based side-channel attacks, the assumption is too ideal for many other side-channel attacks.
-The good news is that there are some mature methods in information theory to model the noises (e.g., Gaussian noise).
+The good news is that there are some mature methods in information theory to model noises (e.g., Gaussian noise).
 The noisy-channel coding theorem provides a computable method to estimate the information that can be reliably transferred over a channel between secret data and attackers' observations.
@@
 The reason that I compare them together in Table 5.3 is that they have the same dimensional unit (bit) under the dimensional analysis.
-I have removed the comparison in the current version.
+I have removed the comparison from the evaluation section in the current version.
 
@@
 
-a. I revised the description in Chapter 5. I abandoned the term lower bound.
+a. I revised the description in Chapter 5. I avoided the use of ``term lower bound''.
 
@@
 
-It is true that Quincunx requires the random input variables to be independent and identically distributed.
+It is true that Quincunx requires the input variables to be independent and identically distributed.
 That's why I applied a blackbox fuzzing instead of a coverage-guided fuzzing.
@@
 The situation is a little different for a machine learning library.
-In the dissertation, we evaluated Quincunx on a deep learning model.
+In my dissertation, we also evaluated Quincunx on a deep learning model.
 Each time, we randomly select an item from a dataset (Samples).
@@
 In my dissertation, we used MINIST, a well-known handwriting dataset.
-We believe the dataset is i.i.d.
+We believe the dataset is i.i.d..
 
@@
 
-Dr. Larus helped me fix many grammar issues. I have revised the dissertation multiple times. In addition, I used Grammarly to proofread my dissertation.
+Dr. Larus helped me fix many grammar issues. I also revised the dissertation multiple times. In addition, I used Grammarly to proofread my dissertation.
 

### 2021-05-25 SupplementaryMaterial/Acknowledgments.tex
(Acknowledgements) Jim's edit
Updates from Overleaf

@@
 The knowledge and skills I learned from him will also help me make progress in my future career.
-I also thank him for treating me as an independent researcher since the fourth year of my Ph.D.
+I also thank him for treating me as an independent researcher during my Ph.D.
 study.
@@
 This research was supported in part by the National Science Foundation (NSF) under grant CNS-1652790, and the Office of Naval Research (ONR) under grants N00014-16-1-2912, N00014-16-1-2265, and N00014-17-1-2894.
-Any opinions, conclusions in the paper do not reflect the views of funding agencies.
+Any opinions, or conclusions in the paper do not reflect the views of funding agencies.

### 2021-05-27 changelog.tex
Updates from Overleaf

@@
 
-\title{Changelog}
+\title{Response to the defense feedback}
 \author{Qinkun Bao}
@@
 If a program executes two different code paths or accesses two different variables with two different input values, the program is vulnerable to side-channel attacks.
-When we report the leakages sites to developers, we can tell them the two inputs.
+When we report side-channel leakages sites to developers, we can tell them the two inputs.
 Developers can quickly reproduce the leakage sites with the inputs.
@@
 In the first place,your uncertainty function has been used in statistical mechanics under that name, so it already has a name.
-In the second place, and more important, nobody knows what entropy really is, so in a debate you will always have the advantage.'' In my dissertation proposal, everyone does not really understand how we quantify the amount of leaked information in Abacus.
-In my final defense, everyone is confused with the term ``lower bounds'' except my advisor.
+In the second place, and more important, nobody knows what entropy really is, so in a debate you will always have the advantage.'' During my dissertation proposal, everyone does not really understand how we quantify the amount of leaked information in Abacus.
+In my final oral exam, everyone is confused with the term ``lower bounds'' except my advisor.
 
@@
 
-a. I revised the description in Chapter 5. I avoided the use of ``term lower bound''.
+a. I revised the description in Chapter 5. I avoided the use of term ``lower bound''.
 

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 Examples of these non-functional behaviors include acoustics, CPU usages, timing, EM signals, etc~\cite{agrawal2002side,hund2013practical,halevi2015keyboard,batina2019csi}.
-In summary, if the program has different execution behaviors when it processes various keys, an attacker can infer nontrivial information by observing secret-dependent behaviors.
-While separate side-channel attacks may have different forms and patterns, we find that a large portion of them share the same fundamental reasons.
+In summary, if a program has different execution behaviors when it processes various keys, an attacker can infer nontrivial information by observing secret-dependent behaviors.
+While separate side-channel attacks may have different forms and patterns, a large portion of them share the same fundamental reasons.
 That is, the memory access pattern is dependent on the original sensitive input.
 
-While removing secret-dependent memory-access patterns in existing software completely is hard and tedious, fixing some of the most dangerous leakages appears to be a feasible solution.
-Previous studies on side-channel detections have shown their effectiveness in finding such code patterns.
+While removing secret-dependent memory-access patterns in existing software completely is hard and tedious, fixing some of the most dangerous leakages appears to be feasible.
+Previous studies~\cite{182946,203878,182946,236338,217537,langley2010ctgrind,xiao2017stacco,wang2019time,Wichelmann:2018:MFF:3274694.3274741,bao2021abacus} on side-channel detections have shown their effectiveness in finding such code patterns.
 Developers can run the tool to analyze the side-channels leakages and fix these patterns.

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 Developers can run the tool to analyze the side-channels leakages and fix these patterns.
-However, fixing all these leakages seem impossible for the following reasons.
-First, side-channels are inevitable.
-For example, tremendous efforts have been made to remove the side-channel vulnerabilities in cryptography libraries in the past decade.
-However, we still find that there are plenty of side-channel leakages in the latest version of OpenSSL.
-Second, many side-channel vulnerable versions usually have better performance, such as the T-table lookups in AES, CRT optimizations in RSA, and Fast Discrete Fourier Transform (FDFT) in many media processing libraries.
-Third, some developers are not interested in fixing side-channels vulnerabilities unless people can show them an attack demo, even for the cryptography developers.
-For many non-cryptography developers, side-channels are not in the threat model.
-However, recent studies have shown a series of attacks on the non-cryptography libraries.
+However, fixing all
+those leakages seem not feasible in practice.  Tremendous efforts havebeen made to remove the side-channel vulnerabilities in cryptography
+libraries in the past decade. However,  there are
+several side-channel leakages in the recent versions of OpenSSL~\cite{OpenSSL-1.1.1-note}. Besides, many side-channel vulnerable versions usually
+have better performance, such as the T-table lookups in AES, CRT
+optimizations in RSA, and Fast Fourier Transform (FFT) in many media
+processing libraries. For many non-cryptography developers, side
+channels are not in consideration usually. However, recent
+studies~\cite{xu2015controlled,191010,hahnel2017high} have shown a series of attacks on the non-cryptography libraries.
 

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 have better performance, such as the T-table lookups in AES, CRT
-optimizations in RSA, and Fast Fourier Transform (FFT) in many media
-processing libraries. For many non-cryptography developers, side
-channels are not in consideration usually. However, recent
-studies~\cite{xu2015controlled,191010,hahnel2017high} have shown a series of attacks on the non-cryptography libraries.
+optimizations in RSA, and Fast Fourier Transform (FFT) in many media processing libraries.
+For many non-cryptography developers, side-channels are not in consideration usually.
+However, recent studies~\cite{xu2015controlled,191010,hahnel2017high} have shown a series of attacks on the non-cryptography libraries.
 
-The key to solving the problem is looking for a proper metric to assess the side-channel leakages' sensitive level.
-Many side-channel analysis tools focus on detecting leakages, which is fine because most side-channel attacks target cryptography libraries.
-For cryptography libraries, even a minor leakage can be severe because the leakage can reduce the encryption algorithm's strength.
-However, many attacks also exploit non-cryptography libraries and applications like machine learning applications~\cite{yan2020cache,hong2018security}, graphic libraries~\cite{wang2019unveiling}, spell checking tools~\cite{xu2015controlled}, etc.
-Unlike side-channel attacks on cryptography libraries that exploit one vulnerability at a time, attacks on non-cryptography rely on multiple side-channel leakage sites to retrieve more information.
-Suppose one program has two leakage sites.
-It is hard to estimate the total effect of two leakages.
-Any two leakages have some underlying complex relationships.
-That is, the two leakages could be completely independent, which means they leak different information.
-Alternatively, the two leakages could leak the same information.
-A typical situation, that is, the two leakage sites, can leak some common knowledge.
-Apart from that, they have their unique leakages.
-However, no existing tools that can estimate the total effect of multiple leakage sites.
-For real-world applications with thousands of lines, it is hard to estimate the amount of leaked information.
-Attackers can guess the values of some temporary values.
-But temporary values contain some knowledge of the original secret buffer.
+Even a minor leakage can be severe for cryptography libraries because
+the leakage can reduce the encryption algorithm's strength. However,
+many attacks also exploit non-cryptography libraries and applications
+like machine learning
+applications~\cite{yan2020cache,hong2018security}, graphic
+libraries~\cite{wang2019unveiling}, spell checking
+tools~\cite{xu2015controlled}, etc. Unlike side-channel attacks on
+cryptography libraries that exploit one vulnerability at a time,
+attacks on non-cryptography rely on multiple side-channel leakage
+sites to retrieve more information. Suppose one program has two
+leakage sites. It is hard to estimate the total effect of those two
+leakages. However, no existing tools that can estimate the total
+effect of multiple leakage sites. For real-world applications with
+thousands of lines, it is hard to estimate the amount of leaked
+information. Attackers can guess the values of some temporary
+values. And those temporary values contain some knowledge of the
+original secret buffer.
 
-Second, many side-channel leakage detection tools rely on some techniques like symbolic executions, taint analysis, and abstract interpretations~\cite{203878,182946,Brotzman19Casym,236338}.
-It is hard to implement these techniques from scratch.
-So they build the tool on top of existing binary analysis frameworks.
-Due to the limitations of existing binary analysis frameworks, it is hard to apply existing methods to analyze side-channels in non-cryptography libraries.
-For many other applications like machine learning, media, and graphic libraries built on the top architecture-dependent libraries (e.g., Intel MKL~\cite{wang2014intel}), these tools can not handle it.
-Moreover, some binary analysis frameworks (e.g., Angr~\cite{shoshitaishvili2016state}) are limited in analyzing floating-point instructions.
-But the functionality of these applications heavily depends on floating-point calculations.
+Second, many side-channel leakage detection tools rely on
+techniques such as symbolic executions, taint analysis, and abstract interpretations~\cite{203878,182946,Brotzman19Casym,236338}. Due
+to the limitations of existing binary analysis techniques, it is hard to apply existing methods to analyze side-channels in non-cryptography
+libraries. For many other applications like machine learning, media,
+and graphic libraries built on the top architecture-dependent
+libraries (e.g., Intel MKL~\cite{wang2014intel}), those tools are not able to
+handle them. Moreover, some binary analysis frameworks (e.g.,
+Angr~\cite{shoshitaishvili2016state}) are limited in analyzing
+floating-point instructions. However, the functionality of those
+applications heavily depends on floating-point calculations.
 
-Third, while many existing tools can detect side-channel leakages, few of them can assess how severity level of these vulnerabilities~\cite{203878,182946,Brotzman19Casym,236338,217537,Wichelmann:2018:MFF:3274694.3274741}.
-There are some tools~\cite{182946,Chattopadhyay:2017:QIL:3127041.3127044} that can quantify the information leakage.
-These tools can give an upper bound estimation of each leakage site, which is useful to justify the software is secure if the reported leakage is zero.
-But these tools can not tell software developers how severe each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage.
-The best way to estimate each leakage's severe level is to exploit the leakage and recover the information.
-However, the process itself is very tedious and needs a lot of domain knowledge.
+Third, while many existing works can detect side-channel leakages, few
+of them can assess the severity levels of those
+vulnerabilities~\cite{182946,203878,182946,236338,217537,langley2010ctgrind,xiao2017stacco,wang2019time,Wichelmann:2018:MFF:3274694.3274741,bao2021abacus,236334,wang2021data,sung2018canal}.
+Some existing tools~\cite{182946,chattopadhyay2019quantifying, biondi2018scalable,5207642,pasareanu2016multi,AskarovC12,phan2017synthesis} quantify the information leakage by giving an upper
+bound estimation of each leakage site.  This is helpful to justify that the software is secure if the reported leakage is zero. However,
+those tools cannot report to software developers how severe each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage.
+Often the over-approximated estimate is very far away from the amount of real leakage.
+For example, CacheAudit~\cite{182946} estimates that a 128-bit
+AES encryption can leak more than 128 bits. As a result, even those
+tools report severe leakage, it does not mean the program has a truly severe leakage.
 

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \subsection{Channel Capacity}
+$K$ is a random variable.
 Let $k$ be one of the possible
-value of $K$. The Shannon entropy $H(K)$ is defined as
+values of $K$. The Shannon entropy $H(K)$ is defined as
 \begin{equation}\label{chapter5:eq1}
@@
 
-Shannon entropy can be used to quantify the initial uncertainty about the sensitive information.
+Shannon entropy can be used to quantify the initial uncertainty about sensitive information.
 It measures the amount of information in a system.
@@
 
-In the chapter, we use the channel capacity to describe the amount of information leakages through a channel.
+In this chapter, we use the channel capacity to describe the amount of information leakages through a channel.
 In information theory, the channel capacity is used to quantify the rate of information can be reliably transmitted over a channel.

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \end{equation}
-$|K|$ represents the number of symbols in $K$.
+$|K|$ represents the number of possible variables in $K$.
 
@@
 Once the input symbol is determined, the output symbol is also determined.
-As we can see, the channel has a unique output ($o \in O$) for every input ($k \in K$).
+Shown in Figure~\ref{fig:channel}(b), the channel has the unique output ($o \in O$) for every input ($k \in K$).
 
@@
 
-We consider an attacker who shares the same hardware resource with the victim.
+We consider an access-based attack~\cite{DBLP:journals/jce/GeYCH18}, where an adversary can probe one time for each run only after the termination of a deterministic program.
 The attacker may not know the memory access the victim program accesses directly.
 Still, he can infer whether some memory addresses are accessed or not at various granularities after \textit{each run} of the victim program.
-We call the memory access information as the observation ($O$) in the rest of the chapter.
-This is a typical scenario for most side-channel attacks.
+We call the memory access information as the observation ($O$) in the rest of the paper.
+It is a typical scenario for most side-channel attacks.
 We also assume the attacker can have access to the source code of the victim program ($\beta$).

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-Side-channel attacks can be seen as a process that infers the secret ($K$) based on the observations ($O$) shown in the figure~\ref{fig:side_channel}.
-As an attacker, he can observe the memory address of the victim program.
+Side-channel attacks can be seen as a process that infers the secret ($K$) based on the observations ($O$).
+As shown in the figure~\ref{fig:side_channel}, we assume that an attacker can observe the memory address of the victim program.
 He wants to infer the original secret ($k$) based on the observation.
 We also assume the attacker knows the known message $m \in M$.
-In the rest of paper, we use $\beta(K) \rightarrow O$ to denote a victim program with side-channel vulnerabilities.
+In the rest of the paper, we use $\beta(K) \rightarrow O$ to denote a victim program that may have side-channel leakage sites.
 
-In thios chapter, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs).
+In this chapter, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs).
 To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.
@@
 \subsection{An Example}
-Figure~\ref{fig:example1} shows a function that is vulnerable to side-channel attacks.
+Figure~\ref{chapter5:fig:example1} shows a function that is vulnerable to side-channel attacks.
 The function takes an input secret from the caller.

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \section{Method}
-In this section, we first provide two examples that show how we rank the side-channel vulnerability. After that, we prove that our method is the conservative estimate of the amount of each leakage.
+In this section, we first provide two examples that show how we rank the side-channel vulnerability. After that, we prove that our method is a conservative estimate of the amount of each leakage.
 
@@
 Still, we test the program with input from $0, 1, \dots, 7$.
-However, we find the attacker can not uniquely determine the secret based on the observation of table $T$, for example.
+However, we find the attacker cannot uniquely determine the secret based on the observation of table $T$, for example.
 Both $0$ and $4$ read the first item of the table.
-Therefore, we think the vulnerability is minor than the previous one.
-Here comes the definition of the amount of leaked information of the vulnerability.
+Therefore, we think the vulnerability is less severe than the previous one.
+
+Let's formally define the amount of leaked information based on the above observation.
 
@@
   \label{chapter5:def}
-  Suppose we have a program $\beta$ with the input set $K$. We randomly select $k_1, k_2, \dots, k_n \in K' \subseteq K$ as the input. We denote it as
-  $$\beta(K') \rightarrow	O'$$
-
-  Here $O$ is a set that consists of various observations $o_1, o_2, \dots, o_m$. The amount of leaked information $L_{\beta(K')\rightarrow O'}$ based on the observation ($o$) is
-  $$L_{\beta(K')\rightarrow O'} = H(O') $$
+    Suppose we have a program $\beta$ with the input space $K$ and observation set $O$.
+We randomly select $k_1, k_2, \ldots, k_n \in K$ as the input and get observations $o_1, o_2, \ldots, o_n \in O$.
+Assume $K'=\{k_1, k_2, \ldots, k_n\}$  ($K' \subseteq K$) and
+    $O'=\{o_1, o_2, \ldots, o_n\}$  ($O' \subseteq O$).
+    We denote it as
+    $$\beta(K') \rightarrow	O'.$$
+    %Here $O$ is a set that consists of various observations $o_1, o_2, \dots, o_m$.
+    The amount of leaked information $L_{\beta(K')\rightarrow O'}$ based on the observations ($O'$) is
+    $$L_{\beta(K')\rightarrow O'} = H(O'). $$
 \end{mydef}
 
-With Definition~\ref{chapter5:def}, we can calculate the information leakage in Figure~\ref{chapter5:fig:example1} and Figure~\ref{chapter5:fig:example2} respectively.
+With Definition~\ref{chapter5:def}, we can calculate the information leakage in Figure~\ref{chapter5:fig:example1} and Figure~\ref{chapter5:fig:example2}, respectively.
 In Figure~\ref{chapter5:fig:example1}, we have $8$ kinds of observations and each observation is uniformly distributed.
-Therefore, the information leakage is $log_2{8} = 3$ bits.
+Therefore, the information leakage is $\log_2{8} = 3$ bits.
 In Figure~\ref{chapter5:fig:example2}, we have $4$ kinds of observations and each observation is also uniformly distributed.
-Therefore, the information leakage is $log_2{4} = 2$ bits.
+Therefore, the information leakage is $\log_2{4} = 2$ bits.
 We test the program with $8$ inputs.
-Therefore, the Shannon entropy of the original K $H(K)$ is also $3\,\mathrm{bits}$.
-According to Equation~\ref{chapter5:eq1}.
-the secret-dependent data accesses in Figure~\ref{chapter5:fig:example1} can leak the sensitive information totally.
+Therefore, the Shannon entropy of the original K $H(K)$ is also $3\,\mathrm{bits}$, according to Equation~\ref{chapter5:eq1}.
+Therefore, the leakage in Figure~\ref{chapter5:fig:example1} show the input secret is leaked totally.
 

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \subsection{A Conservative Estimation}
-In this section, we prove Definition~\ref{chapter5:def} is the conservative estimation of the amount of leaked information based on the channel capacity.
+In this section, we prove Definition~\ref{chapter5:def} is a conservative estimation of the amount of leaked information based on the channel capacity.
 
@@
 
-Accordingly, if Definition~\ref{chapter5:def} says the vulnerability leakage has $m$ bits of leakages, then the vulnerability leaks at least $m$ bits of leakages.
+Accordingly, if Definition~\ref{chapter5:def} says the vulnerability leakage has $m$ bits of leakages, then the vulnerability leaks at least $m$ bits of information.
 We can use the definition to detect these severe leakages.
-In the examples of Figure~\ref{chapter5:fig:example1} and Figure~\ref{chapter5:fig:example2}, because the secret input range from $0$ to $255$, we can calculate the precise value of the amount of information leakage by iterating each input keys.
+In the examples of Figure~\ref{chapter5:fig:example1} and Figure~\ref{chapter5:fig:example2}, the secret input ranges from $0$ to $255$.
+We can calculate the precise value of the amount of leaked by iterating each input keys.
 In Figure~\ref{chapter5:fig:example1}, each item in the array could be read.

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-Considering the example in figure~\ref{fig:align}, it read the data from the array \textsf{T} based on the index (i).
-If index (i) is associated with a key, it could be a side-channel vulnerability.
+Considering the example in figure~\ref{fig:align}, it read data from the array \textsf{T} based on the index ($i$).
+If secret can affect the value of index ($i$), it could be a side-channel vulnerability.
 Unlike the example in the previous section, the array \textsf{T} is on the heap.
-Data on the heap are allocated in different addresses each time.
+Data on the heap are allocated at different addresses each time.
 Suppose during the first run, \textsf{T} is allocated at the address \textsf{0xff124800} and \textsf{T} is allocated at the address \textsf{0xff124801} at the second run.

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 Data on the heap are allocated at different addresses each time.
-Suppose during the first run, \textsf{T} is allocated at the address \textsf{0xff124800} and \textsf{T} is allocated at the address \textsf{0xff124801} at the second run.
+Suppose during the first run, \textsf{T} is allocated at the address \texttt{0xff124800} and \textsf{T} is allocated at the address \texttt{0xff124801} at the second run.
 For the example in Figure~\ref{fig:align}(a), the index that is used to access the array is always $1$, so it should not be a side-channel vulnerability here, however, because the based address is different.

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 Considering the example in figure~\ref{fig:align}, it read data from the array \textsf{T} based on the index ($i$).
-If secret can affect the value of index ($i$), it could be a side-channel vulnerability.
+If the value of index ($i$) is associated with secret information, the example is vulnerable to side-channel attacks.
 Unlike the example in the previous section, the array \textsf{T} is on the heap.
@@
 Suppose during the first run, \textsf{T} is allocated at the address \texttt{0xff124800} and \textsf{T} is allocated at the address \texttt{0xff124801} at the second run.
-For the example in Figure~\ref{fig:align}(a), the index that is used to access the array is always $1$, so it should not be a side-channel vulnerability here, however, because the based address is different.
-So we get two different memory accesses.
+For the example in Figure~\ref{fig:align}(a), the index that is used to access the array is always $1$, so it should not be a side-channel vulnerability here.
+However, because base addresses are different (\texttt{0xff124800} and \texttt{0xff124801}), we get two different memory accesses.
 Under the circumstance, it is a false positive.
-Besides, it can cause false negatives, as the example shown in Figure~\ref{fig:align}(b).
+Without proper alignment, it can cause false negatives, as the example shown in Figure~\ref{fig:align}(b).
 In the example, different keys lead to different indexes.
-However, as $T_0 + i_0$ equals to $T_1 + i_0$, \ctool{} can not observe the difference here, which can cause a false positive.
+However, as $T_0 + i_0$ equals to $T_1 + i_0$, \ctool{} can not observe the difference here, which is a false positive.
 

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 For the example in Figure~\ref{fig:align}(a), the index that is used to access the array is always $1$, so it should not be a side-channel vulnerability here.
-However, because base addresses are different (\texttt{0xff124800} and \texttt{0xff124801}), we get two different memory accesses.
+However, base addresses are different (\texttt{0xff124800} and \texttt{0xff124801}) so we get two different memory accesses.
 Under the circumstance, it is a false positive.
@@
 
-There are some possible solutions that can assign the value.
+There are some possible solutions to assign the value.
+
 \textbf{Run-time Information.} One example here is the concrete memory address during the runtime.
@@
 However, as the example shown in Figure~\ref{fig:align}, it does not have the alignment property.
+
 \textbf{Source Code Information.} Alternatively, we can use the information from the source code.

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-There are some possible solutions to assign the value.
+There are two types of possible solutions to assign the value.
 
@@
 Recent work~\cite{sumner2010memory} proposes using the execution point that allocates the memory cell as the index and tracking the pointer arithmetic to track the pointer that points to the memory.
-However, such a method may miss the alias symbol that points to the same memory cell.
+However, such a method may miss aliased symbols that point to the same memory cell.
 
 We propose to combine both the information from the source code and the runtime to align the memory access during the execution.
-At the point the memory is allocated, we use the tuple $(start\ address, length)$ to represent the buffer.
+At the point the memory is allocated, we use the tuple $\texttt{(start\ address, length)}$ to represent the buffer.
 In the following execution, we check if any memory access falls into the range of these tuples.

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 If so, we add the memory access into the tuple.
-After the execution, the tuple can be mapped into the location of the source code, and we only compare the memory access that belongs to the same lines in the source code.
+After the execution, the tuple can be mapped into the location of the source code, and we only compare memory accesses that belong to the same lines in the source code.
 

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 An adversary may exploit more than one side-channel vulnerabilities to gain more information~\cite{7163052, 191010}.
-In order to precisely quantify the
-total information leakage, we need to know the relation of these leakage sites.
+In order to quantify the
+total information leakage precisely, we need to know the relation of these leakage sites.
 
@@
 
-Suppose one program has two side-channel vulnerabilities A and B, which can leak $L_A$ and $L_B$ bits respectively, according to the definition~\ref{chapter5:def}. 
+Suppose one program has two side-channel vulnerabilities $A$ and $B$, which can leak $L_A$ and $L_B$ bits, respectively, according to Definition~\ref{chapter5:def}. 
 Depending on the relation between A and B, the total leaked information $L_{\mathit{total}}$ will be:

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-We use the chi-square test to check if two leakage sites are independent.
+We use the chi-squared test to check if two leakage sites are independent.
 A chi-squared test can determine if there is a relationship between two categorical variables.
 Suppose we can summarize the data in a $r*c$  two-way contingency table.
-The chi-square test statistic and the degrees of freedom $v$ are calculated with the below formula:
+The chi-squared test statistic and the degrees of freedom $v$ are calculated with the below formula:
 \[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k} \qquad	 v = (r - 1)(c - 1)\]
@@
 For each time, the execution is independent of the previous execution.
-The times of the same observation for each event should satisfy the normal distribution.
+The times of the same observation for each event should satisfy the binomial distribution.
 After that, we can use the chi-squared test to test whether the two leakage sites are independent.

### 2021-05-31 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 The null hypothesis is that the two leakages are independent.
-We generate random inputs as the secret and record the memory access for each execution.
-For each time, the execution is independent of the previous execution.
-The times of the same observation for each event should satisfy the binomial distribution.
+We generate random inputs as the secret input and record the memory access for each execution.
+Each time, the execution is independent of the previous execution, and the target program is the same as the program executed in the previous experiment.
+So the times of the same observation for each event should satisfy the binomial distribution.
 After that, we can use the chi-squared test to test whether the two leakage sites are independent.
@@
 Assume we generate $1024$ random inputs and record the memory access each time.
-For the example in Figure~\ref{chapter5:fig:multiple}, we use $a$ to denote the function \textsf{a} executes and $\lnot a$ to denote the function \textsf{a} does not execute during the execution.
+For the example in Figure~\ref{chapter5:fig:multiple}, we use $a$ to denote that the function \textsf{a} executes, and $\lnot a$ to denote that the function \textsf{a} does not execute during the execution.
 After calculating the number of the same observation, we get the contingency table shown in Figure~\ref{chapter5:fig:con_table}.
@@
 And the two leakages Figure~\ref{chapter5:fig:multiple} (b) are dependent.
-In thios chapter, for any two leakages, if $p < 0.03$, we think the two leakage sites are independent.
+In this chapter, for any two leakages, if $p < 0.03$, we think the two leakage sites are independent.
 We use the above method to test if any two leakage sites are independent for each leakage point.

### 2021-05-31 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 Each time, the execution is independent of the previous execution, and the target program is the same as the program executed in the previous experiment.
-So the times of the same observation for each event should satisfy the binomial distribution.
+Therefore, the times of the same observation for each event should satisfy the binomial distribution.
 After that, we can use the chi-squared test to test whether the two leakage sites are independent.
@@
 
-Based on the equation, we calculate the chi-square test statistic for two leakage sites in Figure~\ref{chapter5:fig:multiple} (a) and (b).
+Based on the equation, we calculate the chi-squared test statistic for two leakage sites in Figure~\ref{chapter5:fig:multiple} (a) and (b).
 
@@
 
-According to Chi-squared distribution table, we have the probability $p\approx0.95$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (a).
+According to chi-squared distribution table, we have the probability $p\approx0.95$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (a).
 We have the probability $p\approx0.00$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (b).
@@
 We evaluate \ctool{} on TinyDNN, a deep learning framework in C++.
-We construct a LeNet-5 model~\cite{lecun1998gradient} and trained it with the MINIST dataset.
+We construct a LeNet-5 model~\cite{lecun1998gradient} and train it with the MINIST dataset.
 LeNet-5 network has six layers, including three convolutional layers, one fully connected layer and two pooling layers.

### 2021-05-31 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 Each time, the execution is independent of the previous execution, and the target program is the same as the program executed in the previous experiment.
+For one type of event(e.g., function $a$ executes), we use $p$ to denote the probability of the event.
+Suppose the target program is executed $n$ times, the probability that we observe the event happens $k \,(k < n)$ times is $P = \binom{k}{n}p^n(1-p)^{n-k}$.
 Therefore, the times of the same observation for each event should satisfy the binomial distribution.
@@
 After calculating the number of the same observation, we get the contingency table shown in Figure~\ref{chapter5:fig:con_table}.
-Suppose the observations of function \textsf{a} and function \textsf{b} are independent.
+Suppose the observations of the execution of function \textsf{a} and the execution of function \textsf{b} are independent.
 We calculate the expected value for the observation $ab$ based on the frequency.

### 2021-05-31 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \begin{equation}\label{chapter5:eq1}
-  H(K) = - \sum_{k {\in} K}p(k)\log_2(k)
+  H(K) = - \sum_{k {\in} K}p(k)\log_2(p(k))
 \end{equation}
@@
     The amount of leaked information $L_{\beta(K')\rightarrow O'}$ based on the observations ($O'$) is
-    $$L_{\beta(K')\rightarrow O'} = H(O'). $$
+    $$L_{\beta(K')\rightarrow O'} = H(O') = - \sum_{o {\in} O'}p(o)\log_2(p(o)). $$
 \end{mydef}
@@
 Suppose one program has two side-channel vulnerabilities $A$ and $B$, which can leak $L_A$ and $L_B$ bits, respectively, according to Definition~\ref{chapter5:def}. 
-Depending on the relation between A and B, the total leaked information $L_{\mathit{total}}$ will be:
+For the example in Figure~\ref{chapter5:fig:multiple}, we use $a$ to denote that the function \textsf{a} executes, and $\lnot a$ to denote that the function \textsf{a} does not execute during the execution.
+Depending on the relation between A and B, the total leaked information $L_{\mathit{AB}}$ will be:
 
 \subsection{Independent Leakages}
-If A and B are independent leakages, the total information leakage will be:
-\[L_{\mathit{total}} = L_A + L_B \]
+If any observation of A does not affect the probability of occurrence of the any observation leakage B, we call the two leakage sites A and B are independent.
+If A and B are two independent leakages, the total amount of leaked information is:
+\[L_{\mathit{AB}} = - \sum_{k {\in} K}p(k)\log_2(p(k)) = L_A + L_B \]
 
@@
 If A and B are dependent leakages, the total information leakage will be:
-\[\max{\{L_A, L_B\}}  \leq L_{\mathit{total}} < L_A + L_B\]
+\[\max{\{L_A, L_B\}}  \leq L_{\mathit{AB}} < L_A + L_B\]
 
@@
 Assume we generate $1024$ random inputs and record the memory access each time.
-For the example in Figure~\ref{chapter5:fig:multiple}, we use $a$ to denote that the function \textsf{a} executes, and $\lnot a$ to denote that the function \textsf{a} does not execute during the execution.
 After calculating the number of the same observation, we get the contingency table shown in Figure~\ref{chapter5:fig:con_table}.

### 2021-05-31 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 For the example in Figure~\ref{chapter5:fig:multiple}, we use $a$ to denote that the function \textsf{a} executes, and $\lnot a$ to denote that the function \textsf{a} does not execute during the execution.
-Depending on the relation between A and B, the total leaked information $L_{\mathit{AB}}$ will be:
+Depending on the relation between $A$ and $B$, the total leaked information $L_{\mathit{AB}}$ will be:
 
 \subsection{Independent Leakages}
-If any observation of A does not affect the probability of occurrence of the any observation leakage B, we call the two leakage sites A and B are independent.
-If A and B are two independent leakages, the total amount of leaked information is:
-\[L_{\mathit{AB}} = - \sum_{k {\in} K}p(k)\log_2(p(k)) = L_A + L_B \]
+If any observation of $A$ does not affect the probability of occurrence of any observation of $B$, we call the two leakage sites $A$ and $B$ are independent. $p_{ab} = p_ap_b$.
+If $A$ and $B$ are two independent leakages, the total amount of leaked information is:
+\begin{align*} 
+L_{\mathit{AB}} &= - \sum_{}p_{ab}\log_2p_{ab} = - \sum_{}p_ap_b\log_2p_ap_b \\
+                &= - \sum_{}p_{a}\log_2p_{a} - \sum_{}p_{b}\log_2p_{b} \\
+                &= L_A + L_B
+\end{align*}
 

### 2021-05-31 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \subsection{Independent Leakages}
-If any observation of $A$ does not affect the probability of occurrence of any observation of $B$, we call the two leakage sites $A$ and $B$ are independent. $p_{ab} = p_ap_b$.
+Given a leakage site $A$, the site has different memory access patterns under different secrets.
+We call each memory access pattern as an observation.
+If any observation of $A$ does not affect the probability of occurrence of any observation of $B$, we call the two leakage sites $A$ and $B$ are independent.
+$p_{ab} = p_ap_b$.
 If $A$ and $B$ are two independent leakages, the total amount of leaked information is:

### 2021-05-31 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \subsection{Step 1: Fuzzing}
-After we build the software into the binary executable, we give the binary code the random inputs.
-For cryptography libraries, the input is the encryption key.
-For non-cryptography libraries, the input could be images, text, and information in other formats.
-Encryption algorithms like AES, DES take an array representing the secrets.
-We generate the random input by flipping each bit of the keys.
-Some other programs also take a buffer as the input.
-The buffer may contain the redundancy information and follow a specific format.
-So not any input that satisfies the input length is a valid input.
-Under the circumstance, we have a dictionary that contains the input.
-For example, Crypto libraries usually take PKCS \#1 as the input of RSA private key.
-We use some other tools to generate a list of valid keys and use the key to sample the program.
-Due to the enormous search space, we can not iterate every input.
-However, our method can give a conservative estimate of each leakage site.
+After we build the software into the binary executable, we give the
+binary code the random inputs. For cryptography libraries, the input
+is the encryption key. For non-cryptography libraries, the input could
+be images, text, and information in another format. Encryption
+algorithms like AES and DES take an array representing the secrets. We
+generate the random input by flipping each bit of the keys. Some other
+programs also take a buffer as the input. The buffer may contain the
+redundancy information and follow a specific format. So not any input
+that satisfies the input length is a valid input. Under the
+circumstance, we have a dictionary that contains the input. For
+example, crypto libraries usually take PKCS \#1 as the input of the
+RSA private key. We use some other tools to generate a list of valid
+keys and use the key to sample the program. Due to the enormous search
+space, we can not iterate every input. However, our method can give a
+conservative estimate of each leakage site.
 \subsection{Step 2: Address Record}
-Next, we record the memory access information based on the input secret.
-We use the dynamic binary instrumentation (DBI) tool to record whether a particular memory access information is accessed or not.
-Inspired by the AFL and Valgrind, we use the bitmap to represent whether a particular memory is accessed or not.
-For example, the bitmap ${0101}$ of address $address_1, address_2, address_3, address_4$ means that $address_2, address_4$ are hit during the execution.
-During the execution, the direct information we get is the virtual memory address (VMA).
-However, we transfer the address into the offset (Load Memory Address (LMA)) in the original binary file.
-It has two benefits.
-First, modern computer systems employ the Address Space Layout Randomization (ASLR).
-With ASLR, the operating system randomly puts the enclave code and data at various memory offset.
-As a result, the code will get different execution traces even for the same input because the enclave image is loaded at a different address each time.
-Second, it helps us find the leakage site in the source code.
+Next, we record the memory access information based on the input
+secret. We use the dynamic binary instrumentation (DBI) tool to record
+whether a particular memory access information is accessed or
+not. Inspired by the AFL and Valgrind, we use the bitmap to represent
+whether a particular memory is accessed or not. For example, the
+bitmap ${0101}$ of address $l_1, l_2, l_3, l_4$ means that $l_2, l_4$
+are hit during the execution. During the execution, the direct
+information we get is the virtual memory address (VMA). However, we
+transfer the address into the offset (Load Memory Address (LMA)) in
+the original binary file. It has two benefits. First, modern computer
+systems employ the Address Space Layout Randomization (ASLR). With
+ASLR, the operating system randomly puts the enclave code and data at
+various memory offset. As a result, the code will get different
+execution traces even for the same input because the enclave image is
+loaded at a different address each time. Second, it helps us find the
+leakage site in the source code.
 
-We rely on the program header and symbol information to recover the offset in the binary.
-During the loading process, the operating system maps each segment into a contiguous memory region.
-So the offset of the virtual memory address between the code within the same segment is the same as the offset within the binary file.
-We choose the start address of some common functions (e.g, $main$) ($b$) as the navigation function.
-We get the virtual memory address of the start of the function ($\mathit{VMA_b}$) from the DBI tool and the load memory address of the function ($\mathit{LMA_b}$) from the symbol information.
-For any virtual address, we use Equation~\ref{equ:eq6} to calculate the offset in the original address.
+We rely on the program header and symbol information to recover the
+offset in the binary. During the loading process, the operating system
+maps each segment into a contiguous memory region. So the offset of
+the virtual memory address between the code within the same segment is
+the same as the offset within the binary file. We choose the start
+address of some common functions (e.g, $\mathit{main}$) ($b$) as the navigation
+function. We get the virtual memory address of the start of the
+function ($\mathit{VMA}_b$) from the DBI tool and the load memory
+address of the function ($\mathit{LMA}_b$) from the symbol
+information. For any virtual address, we use Equation~\ref{equ:eq6} to
+calculate the offset in the original address.
 \begin{equation}\label{equ:eq6}
-  \mathit{LMA_a} = \mathit{LMA_b} - VMA_b - VMA_a
+    \mathit{LMA}_a = \mathit{LMA}_b - \mathit{VMA}_b - \mathit{VMA}_a
 \end{equation}
 
-There are two kinds of memory accesses: accesses to the code and accesses to the data.
+There are two kinds of memory access: access to the code and access to the data. 
 \begin{itemize}
 \item Code Access.
-The memory address of the code is the value of $rip$ register.
+The memory address of the code is the value of $\mathit{rip}$ register.
 However, the length of x86 instructions can be from 1 byte to 15 bytes.
-For instructions whose length is longer than one byte, we also update the address after the value $rip$ until the address reaches the instruction's boundary.
+For instructions whose length is longer than one byte, we also update the address after the value $\mathit{rip}$ until the address reaches the instruction's boundary.
 \item Data Access.
@@
 We have the bitmap of the memory access at the byte level.
-An attacker who has the coarse-grained observation at address space may not distinguish the address difference.
+An attacker who has the coarse-grained observation at address space may not be able to distinguish the address difference.
 For example, modern X64 computer systems use 48-bit virtual memory addresses.
@@
 
-Suppose a program reads one byte at memory $\mathsf{0x7ffff7ffd001}$ when the secret is $k_1$ and reads a different byte at memory $\mathsf{0x7ffff7ffda01}$ when the secret is $k_2$, an attacker who has the page-level observation can not launch the attack but an attacker who launches the cache attack can know the input is $k_1$ or $k_2$.
-We update the new bitmap of the large unit by merging the bitmaps of small units that fall into the large unit.
-That is, $\forall addr_1, addr_2, \dots, addr_n \in addr_N, B^{addr_N}_{k_i} = B^{addr_1}_{k_i} \lor,\dots,\lor B^{addr_N}_{k_n}$.
+Suppose a program reads one byte at memory address
+$\mathtt{0x7ffff7ffd001}$ when the secret is $k_1$ and reads a
+different byte at memory $\mathtt{0x7ffff7ffda01}$ when the secret is
+$k_2$, an attacker who has the page-level observation can not launch
+the attack but an attacker who launches the cache attack can know the
+input is $k_1$ or $k_2$. We update the new bitmap of the large unit by
+merging the bitmaps of small units that fall into the large unit. That
+is, $\forall
+  l_1, l_2, \dots, l_n \in l_N, B^{l_N}_{k_i} = B^{l_1}_{k_i} \lor,\dots,\lor B^{l_n}_{k_n}$.
 
-\subsubsection{Leakage Detection} The access of the address is secret-dependent if $ \exists\, k_{i1}, k_{i2} \in K, \, B^{addr}_{k_i1} \oplus  B^{addr}_{k_i2} =1 $.
-In the chapter, we perform the logical exclusive OR operation on every boolearn value in the same address.
+\subsubsection{Leakage Detection} 
+The access of the address is secret-dependent if $ \exists\, k_{i_1}, k_{i_2} \in K, \, B^{l}_{k_{i_1}} \oplus  B^{l}_{k_{i_2}} =1 $.
+In the step, we perform the logical exclusive OR operation on every boolearn value in the same address.
 If the result is $1$, then the address is vulnerable to the side-channel attacks.
@@
 \begin{myexample}
-Suppose we sample a program from $k1$ to $k8$ and record the memory access at the granularity of each byte from $\mathsf{7ffff7ffd000}$ to $\mathsf{7ffff7ffd03f}$ (One cache line).
+Suppose we sample a program from $k1$ to $k8$ and record the memory access at the granularity of each byte from $\mathtt{7ffff7ffd000}$ to $\mathtt{7ffff7ffd03f}$ (One cache line).
 We perform the bit-wise or operation of each address with the address range.

### 2021-05-31 SupplementaryMaterial/Vita.tex
Updates from Overleaf

@@
 His research interests span reverse engineering, binary analysis, and trusted computing.
-Before he went to Penn State, he received his bachelor's degree in Electronic Engineering and Information Science from University of Science and Technology of China.
+Before he went to Penn State, he received his bachelor's degree in Electronic Engineering and Information Science (EEIS) from University of Science and Technology of China.

### 2021-05-31 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 However, fixing all
-those leakages seem not feasible in practice.  Tremendous efforts havebeen made to remove the side-channel vulnerabilities in cryptography
+these leakages seems not feasible in practice.  Tremendous efforts have been made to remove the side-channel vulnerabilities in cryptography
 libraries in the past decade. However,  there are

### 2021-05-31 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 libraries in the past decade. However,  there are
-several side-channel leakages in the recent versions of OpenSSL~\cite{OpenSSL-1.1.1-note}. Besides, many side-channel vulnerable versions usually
+still several side-channel leakages in the recent versions of OpenSSL~\cite{OpenSSL-1.1.1-note}. Besides, many side-channel vulnerable versions usually
 have better performance, such as the T-table lookups in AES, CRT
@@
 Previous work~\cite{217537} also reported a similar result.
-During our experiment, we continue running the experiment until the observed value for the same observation is at least 5 to satisfy the Chi-square test requirement.
+During our experiment, we continue running the experiment until the observed value for the same observation is at least 5 to satisfy the requirement of chi-squared test.
 Therefore, we choose to run all the cipher with different inputs for $4096$ times.

### 2021-05-31 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \begin{equation} \label{chapter:eq:5}
-  C(K;O) = \max_{p(x)} I(K;O) = \max_{p(x)} H |O| = \log_2 {|O|}
+  C(K;O) = \max_{p(x)} I(K;O) = \max_{p(x)} H |O| 
 \end{equation}
@@
 \subsubsection{Leakage Detection} 
-The access of the address is secret-dependent if $ \exists\, k_{i_1}, k_{i_2} \in K, \, B^{l}_{k_{i_1}} \oplus  B^{l}_{k_{i_2}} =1 $.
+The access of one address is secret-dependent if $ \exists\, k_{i_1}, k_{i_2} \in K, \, B^{l}_{k_{i_1}} \oplus  B^{l}_{k_{i_2}} =1 $.
 In the step, we perform the logical exclusive OR operation on every boolearn value in the same address.

### 2021-05-31 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \begin{myexample}
-Suppose we sample a program from $k1$ to $k8$ and record the memory access at the granularity of each byte from $\mathtt{7ffff7ffd000}$ to $\mathtt{7ffff7ffd03f}$ (One cache line).
-We perform the bit-wise or operation of each address with the address range.
+Suppose we sample a program from $k1$ to $k8$ and record memory accesses at the granularity of one byte from $\mathtt{7ffff7ffd000}$ to $\mathtt{7ffff7ffd03f}$ (One cache line).
+We perform a bit-wise operation of each address within the range.
 Because the cache line is always accessed.

### 2021-05-31 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 After calculating the number of the same observation, we get the contingency table shown in Figure~\ref{chapter5:fig:con_table}.
-Suppose the observations of the execution of function \textsf{a} and the execution of function \textsf{b} are independent.
-We calculate the expected value for the observation $ab$ based on the frequency.
-\[ E_{ab} = \frac{(255+256)*(255+253)}{1024} = 255.5\]
+Suppose the observations of the execution of function \textsf{a} and the execution of function \textsf{b} are independent ($p_{ab} = p_a*p_b$),  we calculate the expected value for the observation $ab$ based on the frequency.
+\[ E_{ab} = 1024*p_{ab} = 1024*p_a*p_b = 1024*\frac{515}{1024}*\frac{508}{1024} = 255.5\]
 Similarly, we calculate the rest expected values with the hypothesis that the leakages are independent and fill in them in Figure~\ref{chapter5:fig:con_table}.

### 2021-05-31 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 It is a valid assumption since most side-channel attacks target open-source software.
-Also, like recent works, we assume the attacker has a noise-free observation.
-For some side-channel channels like the controlled-channel attacks, it is already true.
+Similar to recent work, we assume the attacker has a noise-free observation.
 The program ($\beta$) has $K$ as the sensitive input.
@@
 \item \textbf{Effectiveness:} Can \ctool{} quantify the information leakage with an conservative estimation? If so, what is the loss compared with the real leakage?
-\item \textbf{Performance:} What are overhead costs of \ctool{}?
+%\item \textbf{Performance:} What are overhead costs of \ctool{}?
 \item \textbf{Usage:}  Can \ctool{} help developers find and fix side-channel leakages?
@@
 \textbf{Evaluation setup.} We run all the following experiments in a machine with Ubuntu 18.04 LTS.
-The machine equips with a 2.30GHz Intel Core i9-9880 CPU with 16GB RAM memory.
+The machine equips with a 2.30GHz Intel Core i9-9880H CPU with 16GB RAM memory.
 We use the default release settings to build the software's source code into ELF 64-bit executables with GCC 7.5.
@@
 
-\textit{Cryptography Applications:} Our benchmarks include the most popular cryptography libraries, such as mebdTLS, OpenSSL, Libgcrypt, and wolfSSL.
+\textit{Cryptography Applications:} Our benchmarks include most of the popular cryptography libraries, such as mebdTLS, OpenSSL, Libgcrypt, and wolfSSL.
 Encryption ciphers can be divided into three categories:  symmetric ciphers and asymmetric ciphers.
-For stream ciphers, we use RC4.
 For symmetric ciphers, we choose AES.
@@
 
-\textit{Graphic Libraries:} We evaluate the tool on GTK, a popular graphic library. Previous research has demonstrated attacks to infer the keystroke.
+\textit{Graphic Libraries:} We evaluate the tool on GDK, a popular graphic library. Previous research has demonstrated attacks to infer the keystroke.
 
@@
 We measure the side-channel leakages at two different granularities: the byte level and the cache line level.
-The result shows that the program has more leaked vulnerabilities and tends to leak more information at the byte level compare with the cache line level.
+The result shows that the program has more leaked vulnerabilities and tends to leak more information at the byte level than the cache line level.
 Each time we run the target program under random inputs and record memory accesses.
@@
 During the experiment, we find AES ciphers reach the fixed point after about 300 rounds, and RSA can reach the fixed point after around 500 rounds.
-Previous work~\cite{217537} also reported a similar result.
-During our experiment, we continue running the experiment until the observed value for the same observation is at least 5 to satisfy the requirement of chi-squared test.
+Previous work~\cite{weiser2018data} also reported a similar result.
+We continue running the experiment during our experiment until the observed value for the same observation is at least 5 to satisfy the Chi-square test requirement.
 Therefore, we choose to run all the cipher with different inputs for $4096$ times.

### 2021-05-31 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-We evaluate \ctool{} on TinyDNN, a deep learning framework in C++.
-We construct a LeNet-5 model~\cite{lecun1998gradient} and train it with the MINIST dataset.
-LeNet-5 network has six layers, including three convolutional layers, one fully connected layer and two pooling layers.
-The batch size in our experiment is 10, and the number of epochs is 30.
-After the training, the accuracy of the neural networks on test set images is 99.5\%.
-Then we use the model to infer the images.
-The inference dataset consists of $10000$ images.
-During the inference, we record the memory access information.
-The evaluation shows that all three types of layers have different memory accesses under different inputs.
-In addition, we find that the leakages primarily come from the activation function and the image convert function.
+We evaluate \ctool{} on TinyDNN, a deep learning framework in C++. We
+construct a LeNet-5 model~\cite{lecun1998gradient} and trained it with
+the MINIST dataset. LeNet-5 network has six layers, including three
+convolutional layers, one fully connected layer, and two pooling
+layers. The batch size in our experiment is 10, and the number of
+epochs is 30. After the training, the accuracy of the neural networks
+on test set images is 99.5\%. Then we use the model to infer the
+images. The inference dataset consists of $10,000$ images.  During the
+inference, we record the memory access information. The evaluation
+shows all three types of layers have different memory accesses under
+different inputs. We find that the leakages primarily come from the
+activation function and the image convert function.

### 2021-05-31 changelog.tex
Updates from Overleaf

@@
 I have gone through the details of each comment and revised my dissertation multiple rounds to eliminate any logic flows and fix all the typos and grammar errors.
-In summary, the revisions cover the following aspects.
+In summary, the revision covers the following aspects.
 
@@
 I have a few choices to address the limitation.
-First, I can use static methods (verification or static program analysis).
+First, I can use static methods (verification or program analysis).
 Although I am interested in static analysis, I am not a big fan of current static analysis tools, especially for side-channel research.
@@
 In my dissertation, we used MINIST, a well-known handwriting dataset.
-We believe the dataset is i.i.d..
+We believe the i.i.d.
+assumption holds under the circumstance.
 
@@
 
-Dr. Larus helped me fix many grammar issues. I also revised the dissertation multiple times. In addition, I used Grammarly to proofread my dissertation.
+Dr. Larus helped me a lot on fixing grammar issues. I also revised the dissertation multiple times. In addition, I used Grammarly to proofread my dissertation.
 

### 2021-06-01 SupplementaryMaterial/Acknowledgments.tex
Updates from Overleaf

@@
 A large portion of the research presented in the dissertation was finished when I worked in Switzerland.
-The knowledge and skills I learned from him will also help me make progress in my future career.
 I also thank him for treating me as an independent researcher during my Ph.D.
@@
 
-Besides my advisor, I also thank my committee members, Dr.
-Peng Liu, Dr.
-Sencun Zhu, Dr.
-Benjamin Hanrahan, and Dr.
-James Larus, for their time, reviewing my dissertation.
-Without the strong encouragement from Dr.
-Peng Liu's former students in 2015, I would not have applied for Penn State.
+Besides my advisor, I thank my committee members, Dr. Peng Liu, Dr. Sencun Zhu, Dr. Benjamin Hanrahan, and Dr. James Larus, for their time, reviewing my dissertation.
 

### 2021-06-01 SupplementaryMaterial/Acknowledgments.tex
Updates from Overleaf

@@
 % Place acknowledgments below.
-I am tremendously fortunate to have been advised by Dr.
-Dinghao Wu.
+I am tremendously fortunate to have been advised by Dinghao Wu.
 I thank Dinghao for inviting me to EPFL on his sabbatical.
@@
 
-Besides my advisor, I thank my committee members, Dr. Peng Liu, Dr. Sencun Zhu, Dr. Benjamin Hanrahan, and Dr. James Larus, for their time, reviewing my dissertation.
+Besides my advisor, I thank my committee members, Peng Liu, Sencun Zhu, Benjamin Hanrahan, and James Larus, for their time, reviewing my dissertation.
 
@@
 can be extremely stressful, and summer internships are always the relaxing and productive moments during my study.
-I would like to thank Dr.
-Kang Li, Mr.
-Zhaofeng Chen, Dr.
-Mingshen Sun, Dr.
-Greg Zaverucha, Dr.
-Kevin Kane, and Dr.
-Brian LaMacchia for their help during my internships at Baidu X-Lab and Microsoft Research.
+I would like to thank Kang Li, Zhaofeng Chen, Mingshen Sun, Greg Zaverucha, Kevin Kane, and Brian LaMacchia for their help during my internships at Baidu X-Lab and Microsoft Research.
 I also thank my friends and collaborators at Penn State University and EPFL.

### 2021-06-01 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \subsection{Channel Capacity}
-$K$ is a random variable.
-Let $k$ be one of the possible
-values of $K$. The Shannon entropy $H(K)$ is defined as
+Given a discrete random variable $K$,
+$k$ is one of the possible
+values occurring with the probability $p(k)$. The Shannon entropy $H(K)$ is defined as
 \begin{equation}\label{chapter5:eq1}
-  H(K) = - \sum_{k {\in} K}p(k)\log_2(p(k))
+  H(K) = - \sum_{k {\in} K}p(k)\log_2p(k)
 \end{equation}
@@
 
+For a deterministic program, the program should always have the same memory access patterns under the same input.
+Therefore, an address-based side-channel attack can be seen as a communication channel between the memory access patterns and secret inputs.
 In this chapter, we use the channel capacity to describe the amount of information leakages through a channel.
@@
 During the experiment, we find AES ciphers reach the fixed point after about 300 rounds, and RSA can reach the fixed point after around 500 rounds.
-Previous work~\cite{weiser2018data} also reported a similar result.
+Previous work~\cite{217537} also reported a similar result.
 We continue running the experiment during our experiment until the observed value for the same observation is at least 5 to satisfy the Chi-square test requirement.

### 2021-06-01 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \subsubsection{Noiseless Lossless Channel}
-An information channel is noiseless and lossless if
-
+An information channel is noiseless and lossless if every $k$ corresponds to exactly one unique $o$. The channel capacity of a noiseless lossless channel equals to
 \begin{equation} \label{chapter5:eq4}
@@
 \subsubsection{Noiseless Loss Channel}
-In reality, noiseless loss channel is more common. We define the channel is noiseless loss if
+In reality, noiseless loss channel is more common. The channel capacity of a noiseless loss channel equals to
 
@@
 
-Figure~\ref{fig:channel}(b) shows the example of the type of the channel.
-Once the input symbol is determined, the output symbol is also determined.
+Figure~\ref{fig:channel}(b) shows an example of the type of the channel.
+Once the input value is determined, the output value is also determined.
 Shown in Figure~\ref{fig:channel}(b), the channel has the unique output ($o \in O$) for every input ($k \in K$).

### 2021-06-01 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 
-\subsection*{Design Choices.} At the early stage of the project, we use SMT solvers to get the solutions of constraints.
+\subsection*{Design Choices} At the early stage of the project, we use SMT solvers to get the solutions of constraints.
 However, we find for some ciphers (RSA), \detect{} times out after several days.
@@
 
-\subsection*{Leakages.} While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers.
+\subsection*{Leakages} While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers.
 The DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort.
@@
 \ctool{} requires the random input variables to be independent and identically distributed (i.i.d.).
-That's why I applied a blackbox fuzzing instead of a coverage-guided fuzzing.
+That's why I apply a black box fuzzing instead of a coverage-guided fuzzing.
 As long as each time we get a random input from the whole input space (Populations) that is independent of the previous input, the input variables should satisfy the i.i.d.
@@
 Each time, we randomly select an item from a dataset (Samples).
-If the dataset is biased, then we can not get the correct results.
+If the dataset is biased, then we can not get correct results.
 The good news is that the most well-known data set in machine learning is i.i.d..
@@
 The dataset is widely used in many supervised machine learning tasks.
-We believe the dataset is i.i.d..
+We believe the i.i.d.
+assumption holds under the circumstance.
 

### 2021-06-01 changelog.tex
Updates from Overleaf

@@
 i.i.d.
-is the foundation of supervised machine learning algorithms.
-In my dissertation, we used MINIST, a well-known handwriting dataset.
+is the foundation of supervised machine learning methods.
+The assumption of i.i.d.
+simplify many methods by assuming the data won't change over the time.
+In my dissertation, we used MINIST, a well-known handwriting digit dataset.
 We believe the i.i.d.
@@
 
-I have revised my dissertation to include the discussion on iid.
+I have revised my dissertation to include the discussion on i.i.d.
 

### 2021-06-01 changelog.tex
Updates from Overleaf

@@
 Quincunx defines the amount of leaked information by the empirical entropy of the observations.
-For a determinism program, channel capacity is the tight upper bound of the the empirical entropy of the observation.
-That's why I used the term ``lower bound'' during my PhD defense.
+For a determinism program, channel capacity is the tight upper bound of the empirical entropy of the observation.
+In the early draft of the paper, I use the term ``conservative''.
+Dr.
+Wu thinks ``conservative'' might be a confusing term and suggests me with the term ``lower bound''.
+That's the reason that I used the term ``lower bound'' during my PhD defense.
 I have removed the term ``lower bound'' to avoid any confusion in my dissertation.
@@
 
-a. I revised the description in Chapter 5. I avoided the use of term ``lower bound''.
+a. I revised the description in Chapter 5. I avoided the use of term ``lower bound'' and tune my presentation.
 

### 2021-06-01 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 \section{Fast and Precise Side-channel Vulnerability Detection}
-\subsection*{Coverage} \detect{} works on native x86 execution traces.
-The design, which is very precise in terms of true leakages compared to other static source code method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also share the common limitations of dynamic approaches.
+\subsection*{Code Coverage} \detect{} works on native x86 execution traces.
+The design, which is very precise in terms of true leakages compared to many static source code methods~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, however, share common limitations of dynamic approaches.
 \detect{} may only cover part of the code.

### 2021-06-01 Chapter-6/Chapter-6.tex
Updates from Overleaf

--- 2021-06-01 Chapter-6/Chapter-6.tex
@@
 \section{Fast and Precise Side-channel Vulnerability Detection}
-\subsection*{Coverage} \detect{} works on native x86 execution traces.
-The design, which is very precise in terms of true leakages compared to other static source code method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also share the common limitations of dynamic approaches.
+\subsection*{Code Coverage} \detect{} analyzes one native x86 execution trace each time.
+The design, which is very precise in terms of true leakages compared to many static source code methods~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, share common limitations of dynamic approaches.
 \detect{} may only cover part of the code.
@@
 Therefore, we may neglect some side-channel vulnerabilities not covered by the traces analyzed.
-However, this is not a crucial problem for analyzing cryptographic libraries, because cryptographic libraries are designed to have the same code coverage for various inputs.
-Our evaluation also confirms the above intuition.
+However, this is not a crucial problem for analyzing cryptographic libraries, because cryptographic libraries are designed to have the same code coverage under various inputs.
+The evaluation result also confirms the above intuition.
 For symmetric encryption, there is no secret-dependent control-flow transfers during our evaluation.
@@
 However, we find for some ciphers (RSA), \detect{} times out after several days.
-The profiling result shows that it is spending most its time in Z3.
+The profiling result shows that the tool spends most its time in Z3.
 Later, we use a sampling method to detect side-channel leakages.
@@
 \subsection*{Cache Model} We use a simple cache model in this work.
-Recent work~\cite{Brotzman19Casym,182946} uses an LRU cache.
+Recent work such as CaSym~\cite{Brotzman19Casym,182946} uses an LRU cache.
 First, there is no fundamental difficulties for us to adopt a more realistic cache models.
 Second, the LRU model is still a substantial simplification of a real cache.
-However, the choice of a logical model of cache can bring expensive overheads.
+However, their choice of a logical model of cache can bring expensive overheads.
 

### 2021-06-01 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 However, their choice of a logical model of cache can bring expensive overheads.
+As a result, CaSym can only analyze small code snippets.
 
 \subsection*{Leakages} While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers.
-The DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort.
-After we manually analyze these leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which partially explain why developers are not interested in fix all the leakages.
+The DES implementation of OpenSSL has a few side-channel leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort.
+\detect{} also detects several leakages in asymmetric ciphers such as RSA.
+After we manually analyze these leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which may partially explain why developers are not interested in fix all the side-channel leakages.
+
 \section{Precise Analysis on Single-trace Attacks}
 While recent work found many side-channel vulnerabilities,
-we note that many of them have not been patched by developers.
-Side-channels are ubiquitous in software and it would be difficult to fix all of them.
+we note that many of them are been patched by developers.
+Side-channels are ubiquitous in software, and it is difficult to fix all of them.
 We need a tool that estimates the sensitivity of each vulnerability
@@
 The design, which is more precise in reporting true leakages as compared with other static
-methods~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, obviously misses
-leakages on unexplored traces. The amount of leaked information also depends on the secret key.
+methods~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, obviously misses leakages on unexplored traces.
+The amount of leaked information quantified by \tool{} also depends on the value of secret keys.
 However, as the tool is intended for debugging and testing,

### 2021-06-01 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 That's why I apply a black box fuzzing instead of a coverage-guided fuzzing.
-As long as each time we get a random input from the whole input space (Populations) that is independent of the previous input, the input variables should satisfy the i.i.d.
+As long as each time we get a random input from the whole input space (Population) that is independent of the previous input, the input variables should satisfy the i.i.d.
 assumption.
@@
 In the dissertation, we evaluated \ctool{} on a deep learning model.
-Each time, we randomly select an item from a dataset (Samples).
+Each time, we randomly select an item from a dataset (Sample).
 If the dataset is biased, then we can not get correct results.

### 2021-06-01 response.txt
Updates from Overleaf

Dear xxx,

Thank you for reviewing my dissertation. I have gone through the details of each
comment and revised my dissertation multiple rounds to eliminate any logic flows and
fix all the typos and grammar errors. In summary, the revision covers the following aspects.

1. Fuzzing – Why did you use fuzzing?

Abacus identifies and quantifies side-channel leakages in a single trace. So it
suffers from the problem of code coverage.  That is, Abacus misses side-channel
leakages in the unexecuted code path.

I have a few choices to address the limitation. First, I can use static methods
(verification or program analysis). Although I am interested in static analysis, I am
not a big fan of current static analysis tools, especially for side-channel research.
There are many papers on static side-channel analysis. Nearly all of these tools are
used to prove the absence of side-channel leakages. However, most of them have high
false-positive rates.

On the other hand, there are many success stories with dynamic tools (e.g., SAGE,
AFL, Valgrind) in recent years. In particular, fuzzing is becoming a hot trend these
years, especially after DARPA CGC in 2016. The fuzzing method is suitable for a task
such as side-channel detection. If a program executes two different code paths or
accesses two different variables with two different input values, the program is
vulnerable to side-channel attacks. When we report side-channel leakages sites to
developers, we can tell them the two inputs. Developers can quickly reproduce the
leakage sites with the inputs.  Interestingly, there are a few (not many) related
papers. That's why I used fuzzing at the beginning of the project.

2. Discuss the limitations of your research e.g., can only handle address based …
you might want to include some discussion on the points (3), (4), and (5) below.
The research presented in the dissertation has a few limitations.

a. The methods in my dissertation can not find all kinds of side-channel leakages. No
tool can find all forms of leakages. Even for address-based side-channel leakages,
Abacus and Quincunx can not find all the leakages due to the code coverage problem.
Some verification tools can prove the absence of side-channel leakages for some small
code snippets. However, to the best of my knowledge, no tools as yet can prove the
absence of side-channel leakages in production software.

b. The quantification result only applies to specific threat models. For example,
Abacus quantifies the number of leaked bits during one real execution. So it is
possible that one leakage site leaks little information in one execution but leaks
much information in another execution.

c. The research in the dissertation can only handle address-based side-channel
attacks. Many side-channel attacks infer secret data based on other side-channel
signals (e.g, timing, EM signals). However, the root cause of these attacks is still
the same. That is, the program accesses different addresses when it processes
different input secrets. Under the circumstance, our methods can still detect these
leakage sites.

3. Can you extend your research (especially the quantification part) to include other
side-channel signals?

It is possible to extend the quantification part to include other side-channel
signals (e.g., Sound, CPU usages, EM signals). The key is to model the noises
properly. In my dissertation, we assume that an attacker can have a noise-free
observation. While a noise-free observation is possible for some address-based
side-channel attacks, the assumption is too ideal for many other side-channel
attacks. The good news is that there are some mature methods in information theory to
model noises (e.g., Gaussian noise). The noisy-channel coding theorem provides a
computable method to estimate the information that can be reliably transferred over a
channel between secret data and attackers' observations. From a research project
aspect, I hope to have a stronger motivation before starting the project.

4.  bits vs. Q bits. Lower bounds?       Improve the presentation
       Make the comparison more meaningful
       Etc.

It is hard to explain Entropy. There is a rumor about entropy between John von
Neumann and Claude Shannon. When Shannon developed the concept of information theory,
he did not have a good idea to name the measurement of uncertainty in a system.
Neumann told Shannon, ``You should call it entropy, for two reasons. In the first
place, your uncertainty function has been used in statistical mechanics under that
name, so it already has a name. In the second place, and more important, nobody knows
what entropy really is, so in a debate, you will always have the advantage.'' During
my dissertation proposal, everyone does not really understand how we quantify the
amount of leaked information in Abacus. In my final oral exam, everyone is confused
with the term ``lower bounds'' except my advisor.

a. Abacus quantifies the amount of leaked information for a given address access
behavior. It is a measure of the amount of leaked information that an attacker can
get, given that another event has already occurred.

b. Quincunx defines the amount of leaked information by the empirical entropy of the
observations. For a determinism program, channel capacity is the tight upper bound of
the empirical entropy of the observation. In the early draft of the paper, I use the
term ``conservative''. Dr. Wu thinks ``conservative'' might be a confusing term and
suggests me with the term ``lower bound''. That's the reason that I used the term
``lower bound'' during my PhD defense. I have removed the term ``lower bound'' to
avoid any confusion in my dissertation.

c. I agree with Dr. Liu's comments that the quantification metrics in Chapter 4 and
Chapter 5 are different. The reason that I compare them together in Table 5.3 is that
they have the same dimensional unit (bit) under the dimensional analysis. I have
removed the comparison from the evaluation section in the current version.

To address the above concerns, I have made the following revisions.

a. I revised the description in Chapter 5. I avoided the use of term ``lower bound''
and tune my presentation.

b. I revised Table 5.3. The evaluation section does not compare Quincunx with Abacus
in the current version because they are calculated with different methods and have
different threat models.

5. iid assumption – does it fit your research on side-channel?

It is true that Quincunx requires the input variables to be independent and
identically distributed. That's why I applied a blackbox fuzzing instead of a
coverage-guided fuzzing. As long as each time we get a random input from the whole
input space (Populations) that is independent of the previous input, the input
variables should satisfy the i.i.d. assumption. For AES-128 encryption, each time we
randomly generate a 128 bit key from $0$ to $2^{128}$, the sequence of key values
follows the i.i.d. assumption.

The situation is a little different for a machine learning library. In my
dissertation, we also evaluated Quincunx on a deep learning model. Each time, we
randomly select an item from a dataset (Samples). If the dataset is biased, then we
can not get correct results. The good news is that the most well-known data in
machine learning is i.i.d. i.i.d. is the foundation of supervised machine learning
methods. The assumption of i.i.d. simplify many methods by assuming the data won't
change over the time. In my dissertation, we used MINIST, a well-known handwriting
digit dataset. We believe the i.i.d. assumption holds under the circumstance.

I have revised my dissertation to include the discussion on i.i.d.

6. Some feedback I gave before your defense.

As suggested by Dr. Wu, I added a new chapter on Discussion and Limitations (Chapter 6),
and discussed potential ways and related work to the mitigated reported side
(Chapter 2).

7. Improve Grammar.

Dr. Larus helped me a lot in fixing grammar issues. I also revised the dissertation
multiple times. In addition, I used Grammarly to proofread my dissertation.

I have incorporated some discussions above into my dissertation. Please let me know if you
have any feedback. Thank you for reviewing my dissertation again.

Thanks,
Qinkun

### 2021-06-01 SupplementaryMaterial/Acknowledgments.tex
Updates from Overleaf

@@
 
-Besides my advisor, I thank my committee members, Peng Liu, Sencun Zhu, Benjamin Hanrahan, and James Larus, for their time, reviewing my dissertation.
+The members of my committee, Peng Liu, Sencun Zhu, Benjamin Hanrahan, and James Larus, provided helpful comments on my dissertation.
+Prof.
+Liu and Prof.
+Zhu greatly improved this dissertation with their comments from a security research aspect.
+Prof.
+Hanrahan and Prof.
+Larus helped me improve the grammar of my dissertation.
+Jim has a keen observation about Abacus.
+His comments are very close to the reviewers.
+However, I did not take his comments seriously at the very beginning.
 
@@
 
+Finally, I would like to thank my parents for their continuous emotional and financial support.
+My parents always hope that I can find a job that is near to them.
+However, they still expressed their full support for me when I decided to come to U.S.
+as a graduate student.
+
 This research was supported in part by the National Science Foundation (NSF) under grant CNS-1652790, and the Office of Naval Research (ONR) under grants N00014-16-1-2912, N00014-16-1-2265, and N00014-17-1-2894.

### 2021-06-01 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 The CPU cache is a smaller but faster memory designed to bridge the gap of the access time between the main memory and CPU registers by storing copies of recently accessed data.
-Because software may access different memory addresses when it processes different input data, and the size of the cache is significantly smaller than the size of the main memory, the CPU may only find part of the data in the cache.
+Because the size of the cache is significantly smaller than the size of the main memory, the CPU may only find part of the data in the cache.
+Accessing data from the cache is faster than Accessing data from the main memory.
 Such differences can be reflected in the variance in the program execution time.
-Hence we have cache side-channel attacks.
+Hence we have cache channel attacks.
 
 Various countermeasures have been proposed to defend against side-channel attacks.
-Based on the above discussion, existing countermeasures can be further divided into two categories, the hardware-based method and the software-based method.
+Existing countermeasures can be divided into two categories, hardware-based methods and software-based methods.
 Hardware-level solutions, such as reducing shared resources, oblivious RAM, and transnational memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need to adopt new hardware features and change  today's modern complex computer systems, which are hard to adopt in reality.
-Therefore, a promising and universal direction is software countermeasures, detecting and eliminating side-channel vulnerabilities (data flow from secrets to load addresses, and data flow from secrets to branch conditions) in existing code base.
+Therefore, a promising and universal direction is software countermeasures, detecting and eliminating side-channel vulnerabilities in existing software code base.
 For example, when we examine recent side-channel attacks, many of them exploit two kinds of code patterns: \emph{secret-dependent control-flow transfers} and \emph{secret-dependent data accesses}.
@@
 Figure~\ref{fig:secret:cf} shows an example.
-Depending on the value of \textsf{secret}, the code may or may not execute line 6.
-An attacker can retrieve some information based on the execution control-flow.
+Depending on the value of \textsf{secret}, the code may or may not execute the code at line 6.
+An attacker can retrieve some information by observing the execution control-flow.
 
@@
 
-Secret-dependent data accesses happen when the value of the secret can affect which memory location the code reads or writes.
+Secret-dependent data accesses happen when values of secret data affect which memory location the code reads or writes.
 Figure~\ref{fig:secret:da} shows an example.
@@
     \item We analyze the amount of information leakage from side-channel vulnerabilities based on the channel capacity.
-We propose a method that can estimate the lower bound of information leakages.
 The theory can serve as the foundation of the future work on quantifying the information leakage based on the fuzzing.

### 2021-06-01 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 Although some vulnerabilities result in the key being entirely compromised~\cite{184415, aumuller2002fault}, many others are less severe in reality.
-Therefore, we need a proper quantification metric to assess the sensitivity of side-channel vulnerabilities, so a developer can efficiently triage them.
+Therefore, developers are often reluctant to fixing all of them.
+We need a proper quantification metric to assess the sensitivity of side-channel vulnerabilities, so a developer can efficiently triage them.
 Third, many side-channel vulnerable implementations (e.g., the CRT optimization and lookup tables) have better performance.
@@
 Chapter~\ref{chapter5} extends the approach and quantifies the side-channel leakage in a multiple-trace attack.
-Chapter~\ref{chapter6} concludes the dissertation and proposes the future work.
+Chapter~\ref{chapter6} and Chapter~\ref{chapter7} discuss limitations of the dissertation and propose the future work.

### 2021-06-01 Chapter-7/Chapter-7.tex
Updates from Overleaf

@@
-\chapter{Conclusion}\label{chapter6}
+\chapter{Conclusion}\label{chapter7}
 This dissertation research studies the address-based side-channel leakages in two aspects: detection and quantification.

### 2021-06-01 SupplementaryMaterial/Vita.tex
Updates from Overleaf

--- 2021-05-14 SupplementaryMaterial/Vita.tex
@@
 
-Qinkun Bao earned his Ph.D. at the College of Information Sciences
+Qinkun Bao finished his Ph.D. at the College of Information Sciences
 and Technology, The Pennsylvania State University. He was a member of the Software 
@@
 His research interests span reverse engineering, binary analysis, and trusted computing.
-Before he went to Penn State, he received his bachelor's degree in Electronic Engineering and Information Science from University of Science and Technology of China.
+Before he went to Penn State, he received his bachelor's degree in Electronic Engineering and Information Science (EEIS) from University of Science and Technology of China (USTC).

### 2021-06-01 SupplementaryMaterial/Acknowledgments.tex
Updates from Overleaf

@@
 Liu and Prof.
-Zhu greatly improved this dissertation with their comments from a security research aspect.
+Zhu greatly improved this dissertation with their comments from a security research angle.
 Prof.
@@
 Larus helped me improve the grammar of my dissertation.
-Jim has a keen observation about Abacus.
-His comments are very close to the reviewers.
+Jim is my last English teacher.
+I learned a lot on the written English from him.
+His comments are also very close to what I get from reviewers later.
 However, I did not take his comments seriously at the very beginning.
@@
 Finally, I would like to thank my parents for their continuous emotional and financial support.
-My parents always hope that I can find a job that is near to them.
+My parents always hope that I can study in a university that is near to them.
 However, they still expressed their full support for me when I decided to come to U.S.

### 2021-06-02 Chapter-7/Chapter-7.tex
Updates from Overleaf

@@
 \chapter{Conclusion}\label{chapter7}
-This dissertation research studies the address-based side-channel leakages in two aspects: detection and quantification.
+This dissertation research studies address-based side-channel leakages in two aspects: detection and quantification.
 In the side-channel vulnerability detection research, we explore and solve the two bottlenecks in today's automated side-channel vulnerability detection tool, performance and precision.

### 2021-06-02 SupplementaryMaterial/Acknowledgments.tex
Updates from Overleaf

@@
 Prof.
-Hanrahan and Prof.
-Larus helped me improve the grammar of my dissertation.
-Jim is my last English teacher.
+Hanrahan helped me improve the grammar of my dissertation proposal and my dissertation.
+Prof.
+Larus is a senior researcher and my last English teacher.
 I learned a lot on the written English from him.
-His comments are also very close to what I get from reviewers later.
+His comments on the early draft are also very close to what I got from reviewers later.
 However, I did not take his comments seriously at the very beginning.

### 2021-06-02 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 The minimum unit of the program during the experiment is the function.
-Suppose the function has more than one access map, then the function that is vulnerable to side-channel attacks.
+If a function has more than one access bitmap, then the function is vulnerable to side-channel attacks.
 We measure the side-channel leakages at two different granularities: the byte level and the cache line level.
-The result shows that the program has more leaked vulnerabilities and tends to leak more information at the byte level than the cache line level.
-Each time we run the target program under random inputs and record memory accesses.
+The result shows that programs have more vulnerable functions and tend to leak more information at the byte level than the cache line level.
+We run the target program under random inputs and record memory accesses.
 For cryptography programs, we run the target program with $4096$ different inputs.
@@
 From the side-channel detection aspect, it is not necessary to continue running the experiments since more rounds do not reveal new leakages.
-During the experiment, we find AES ciphers reach the fixed point after about 300 rounds, and RSA can reach the fixed point after around 500 rounds.
+During the experiment, we find AES ciphers reach the fixed point after about $300$ rounds, and RSA can reach the fixed point after around $500$ rounds.
 Previous work~\cite{217537} also reported a similar result.
-We continue running the experiment during our experiment until the observed value for the same observation is at least 5 to satisfy the Chi-square test requirement.
+We continue running the experiment during our experiment until the observed value for the same observation is at least $5$ to satisfy the chi-square test requirement.
 Therefore, we choose to run all the cipher with different inputs for $4096$ times.
@@
 AES encryption can be divided into three steps.
-In the first step, the round keys are derived from the encryption keys called the AES key schedule, and the state array is initialized with the plain-text and the initial round step.
+In the first step, the round keys are derived from the encryption keys called the AES key schedule, and a state array is initialized with the plain-text and the initial round step.
 In the second step, the AES performs eleven rounds of state manipulation.
@@
 
-RSA implementations are blinding the data on a random value before operating on it.
+RSA implementations blind the secret data on a random value before operating on it.
 We use a fixed RSA blinding value to avoid non-deterministic behaviors during the execution.
@@
 Table~\ref{chapter5:tab:RSAOpenSSL1.1.0} shows the leaked function and the amount of leakage reported by \tool{} and \ctool{}.
-First, as the result indicates, the leakage sites that leak more information (> 5.0 bits) are all fixed in OpenSSL 1.1.1.
-The result indicates that \ctool{} can help developers identify side-channel leakages and pick the severe from them automatically.
-As expected, we find most of the leakages are from the big number calculations.
+First, as the result indicates, the leakage sites that leak a lot of information (> 5.0 bits) are all fixed in OpenSSL 1.1.1.
+The result indicates that \ctool{} can help developers identify side-channel leakages and pick severe ones from them automatically.
+As expected, we find that most of the leakages are from big number calculations.
 OpenSSL has a side-channel mitigated big number implementation.
@@
 We find developers forget to propagate the flag in the caller, which results in the vulnerabilities in \textsf{BN\_div} and \textsf{int\_bn\_mod\_inverse}.
-Second, for leakage sites that are not fixed by the developers, both \tool{} and \ctool{} report that they leak less amount of information.
+Second, for leakage sites that are not fixed by the developers, \ctool{} reports that they leak less amount of information.
 For example, function \textsf{BN\_mod\_exp\_mont\_consttime} check if the modulus is odd.
 However, it is not a side-channel leakage vulnerability.
-Both tools report that the leakage site can leak one bit of information.
-Third, even \tool{} reports some leakage sites to leak little information, \ctool{} can report the vulnerability is severe.
+\ctool{} reports that the leakage site can leak one bit of information.
+Third, previous work~\cite{bao2021abacus} reports some leakage sites leak little information, but \ctool{} reports the vulnerability is severe.
 \tool{} quantifies the amount of leaked information for one execution.
@@
 We run the chi-squared test to determine if any two leaked functions have independent leakages.
-However, we can not conclude that any two leakages are independent under the chi-squared test.
+However, we can not conclude that any two leakages from cryptography benchmarks are independent under the chi-squared test.
 We think it is due to the avalanche effect in cryptography.

### 2021-06-02 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
-\chapter{Discussion and Limitations}
+\chapter{Discussion and Limitations}\label{chapter6}
 \section{Fast and Precise Side-channel Vulnerability Detection}
@@
 \subsection*{Cache Model} We use a simple cache model in this work.
-Recent work such as CaSym~\cite{Brotzman19Casym,182946} uses an LRU cache.
+Recent works such as CacheAudit and CaSym~\cite{Brotzman19Casym,182946} use an LRU cache.
 First, there is no fundamental difficulties for us to adopt a more realistic cache models.
 Second, the LRU model is still a substantial simplification of a real cache.
-However, their choice of a logical model of cache can bring expensive overheads.
-As a result, CaSym can only analyze small code snippets.
+However, the choice of a logical model of cache can bring expensive overheads.
+For example, CaSym can only analyze small code snippets.
 

### 2021-06-02 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 \subsection*{Cache Model} We use a simple cache model in this work.
-Recent works such as CacheAudit and CaSym~\cite{Brotzman19Casym,182946} use an LRU cache.
+Recent works such as CacheAudit and CaSym~\cite{Brotzman19Casym,182946} use a Least Recently Used (LRU) cache.
 First, there is no fundamental difficulties for us to adopt a more realistic cache models.
 Second, the LRU model is still a substantial simplification of a real cache.
-However, the choice of a logical model of cache can bring expensive overheads.
+For example, Intel Sandy Bridge CPUs use an undisclosed hash function to map memory addresses to L3 cache lines~\cite{farshin2019make}.
+However, the choice of a LRU model of cache can bring expensive overheads.
 For example, CaSym can only analyze small code snippets.

### 2021-06-02 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 For example, Intel Sandy Bridge CPUs use an undisclosed hash function to map memory addresses to L3 cache lines~\cite{farshin2019make}.
-However, the choice of a LRU model of cache can bring expensive overheads.
+However, the choice of LRU  cache models can bring expensive overheads.
 For example, CaSym can only analyze small code snippets.
@@
 So it bears the same limitations of dynamic approaches as well.
-\ctool{} may have the coverage problem and can miss some side-channel vulnerabilities.
+\ctool{} can not cover all the paths and may miss some side-channel vulnerabilities.
 It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control flow under various inputs.
 For other libraries such as graphic rendering, machine learning, \ctool{} is very likely to miss some side-channel vulnerabilities.
-However, \ctool{} is not designed to find side-channel vulnerabilities.
+However, \ctool{} is not designed to find every side-channel vulnerabilities.
 The goal of \ctool{} is to pick up really serious side-channel vulnerabilities from the numerous vulnerabilities.

### 2021-06-02 response.txt
Updates from Overleaf

@@
 
-It is true that Quincunx requires the input variables to be independent and
-identically distributed. That's why I applied a blackbox fuzzing instead of a
-coverage-guided fuzzing. As long as each time we get a random input from the whole
-input space (Populations) that is independent of the previous input, the input
-variables should satisfy the i.i.d. assumption. For AES-128 encryption, each time we
-randomly generate a 128 bit key from $0$ to $2^{128}$, the sequence of key values
-follows the i.i.d. assumption.
+It is true that Quincunx requires the assumption that input variables are
+independent and identically distributed. That's why I applied a blackbox fuzzing 
+instead of a coverage-guided fuzzing. As long as each time we get a random input from 
+the whole input space (Population) that is independent of the previous input, the input
+variables should satisfy the i.i.d. assumption. Take AES-128 encryption for example, 
+each time we randomly generate a 128 bit key from $0$ to $2^{128}$, the sequence of key 
+values follows the i.i.d. assumption.
 
@@
 dissertation, we also evaluated Quincunx on a deep learning model. Each time, we
-randomly select an item from a dataset (Samples). If the dataset is biased, then we
-can not get correct results. The good news is that the most well-known data in
-machine learning is i.i.d. i.i.d. is the foundation of supervised machine learning
-methods. The assumption of i.i.d. simplify many methods by assuming the data won't
-change over the time. In my dissertation, we used MINIST, a well-known handwriting
-digit dataset. We believe the i.i.d. assumption holds under the circumstance.
+randomly select an item from a dataset (Sample). If the dataset is biased, then we
+can not get correct results. The good news is that the most well-known dataset in
+machine learning is i.i.d. i.i.d. is the foundation of many machine learning
+techniques (e.g., cross-validation, SVM, back-propagation). The assumption of i.i.d. 
+simplify many methods by assuming the data won't change over the time. 
+In my dissertation, we used MINIST, a well-known handwriting digit dataset. 
+We believe the i.i.d. assumption holds under the circumstance, although the
+assumption can be violated in some real-world scenarios.
 
@@
 
-7. Improve Grammar.
+7. Improve English grammar.
 
-Dr. Larus helped me a lot in fixing grammar issues. I also revised the dissertation
+Dr. Larus helped me fix a lot of grammar issues. I also revised the dissertation
 multiple times. In addition, I used Grammarly to proofread my dissertation.

### 2021-06-02 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 If the dataset is biased, then we can not get correct results.
-The good news is that the most well-known data set in machine learning is i.i.d..
-i.i.d.
-is the foundation of supervised machine learning algorithms.
-In my dissertation, we used MINIST, a well-known handwriting dataset.
-The dataset is widely used in many supervised machine learning tasks.
-We believe the i.i.d.
-assumption holds under the circumstance.
+The good news is that the most well-known dataset in
+machine learning is i.i.d. i.i.d. is the foundation of many machine learning
+techniques (e.g., cross-validation, SVM, back-propagation). The assumption of i.i.d. 
+simplify many methods by assuming the data won't change over the time. 
+In my dissertation, we used MINIST, a well-known handwriting digit dataset. 
+We believe the i.i.d. assumption holds under the circumstance, although the
+assumption can be violated in some real-world scenarios.
 

### 2021-06-02 response.txt
Updates from Overleaf

@@
 The situation is a little different for a machine learning library. In my
-dissertation, we also evaluated Quincunx on a deep learning model. Each time, we
+dissertation, we also evaluated Quincunx on a deep learning library. Each time, we
 randomly select an item from a dataset (Sample). If the dataset is biased, then we
-can not get correct results. The good news is that the most well-known dataset in
-machine learning is i.i.d. i.i.d. is the foundation of many machine learning
+can not get correct results. The good news is that the most well-known data sets in
+machine learning are i.i.d. i.i.d. is the foundation of many machine learning
 techniques (e.g., cross-validation, SVM, back-propagation). The assumption of i.i.d. 

### 2021-06-02 response.txt
Updates from Overleaf

@@
 used to prove the absence of side-channel leakages. However, most of them have high
-false-positive rates.
+false-positive rates. Besides, there are many talented researchers working on the 
+same direction (e.g., Project Everest).
 
@@
 years, especially after DARPA CGC in 2016. The fuzzing method is suitable for a task
-such as side-channel detection. If a program executes two different code paths or
+such as side-channel detections. If a program executes two different code paths or
 accesses two different variables with two different input values, the program is
@@
 behavior. It is a measure of the amount of leaked information that an attacker can
-get, given that another event has already occurred.
+get, based on that another event has already occurred. I agree that the result from the tool 
+can be counterintuitive (e.g., the password checker example in my dissertation).
+Let's compare the quantification method in my dissertation to Bayes' theorem.
+I think they are similar in some ways. Bayes' theorem describes the probability of 
+an event, based on prior knowledge of an event has happened. The result from Bayes' theorem 
+can also be counterintuitive (e.g. drug testing).
 
@@
 term ``conservative''. Dr. Wu thinks ``conservative'' might be a confusing term and
-suggests me with the term ``lower bound''. That's the reason that I used the term
-``lower bound'' during my PhD defense. I have removed the term ``lower bound'' to
+we decided to use the term ``lower bound''. It turns out that the term ``lower bound''
+is misleading and in some cases incorrect. I have removed the term ``lower bound'' to
 avoid any confusion in my dissertation.
@@
 c. I agree with Dr. Liu's comments that the quantification metrics in Chapter 4 and
-Chapter 5 are different. The reason that I compare them together in Table 5.3 is that
+Chapter 5 are different. The reason that I compared them together in Table 5.3 is that
 they have the same dimensional unit (bit) under the dimensional analysis. I have
@@
 
-To address the above concerns, I have made the following revisions.
+To address the above concerns, I made the following revisions.
 
@@
 different threat models.
+
+c. Chapter 5 was an early draft. We submitted the work to a conference later and
+my advisor helped me revise the paper. I updated the chapter from the submitted 
+paper.
 

### 2021-06-02 response.txt
Updates from Overleaf

@@
 attacks. Many side-channel attacks infer secret data based on other side-channel
-signals (e.g, timing, EM signals). However, the root cause of these attacks is still
+signals (e.g., timing, EM signals). However, the root cause of these attacks is still
 the same. That is, the program accesses different addresses when it processes
@@
 an event, based on prior knowledge of an event has happened. The result from Bayes' theorem 
-can also be counterintuitive (e.g. drug testing).
+can also be counterintuitive (e.g., drug testing).
 
@@
 variables should satisfy the i.i.d. assumption. Take AES-128 encryption for example, 
-each time we randomly generate a 128 bit key from $0$ to $2^{128}$, the sequence of key 
+each time we randomly generate a 128 bit key from 0 to 2^{128}, the sequence of key 
 values follows the i.i.d. assumption.

### 2021-06-02 response.txt
Updates from Overleaf

@@
 I have a few choices to address the limitation. First, I can use static methods
-(verification or program analysis). Although I am interested in static analysis, I am
+(verification or program analysis). Although I am interested in the static analysis, I am
 not a big fan of current static analysis tools, especially for side-channel research.
@@
 
-4.  bits vs. Q bits. Lower bounds?       Improve the presentation
+4.  bits vs. Q bits. Lower bounds?       
+    Improve the presentation
     Make the comparison more meaningful
@@
 It is true that Quincunx requires the assumption that input variables are
-independent and identically distributed. That's why I applied a blackbox fuzzing 
+independent and identically distributed. That's why I applied a black box fuzzing 
 instead of a coverage-guided fuzzing. As long as each time we get a random input from 
@@
 techniques (e.g., cross-validation, SVM, back-propagation). The assumption of i.i.d. 
-simplify many methods by assuming the data won't change over the time. 
+simplifies many methods by assuming the data won't change over the time. 
 In my dissertation, we used MINIST, a well-known handwriting digit dataset. 

### 2021-06-02 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 However, we find for some ciphers (RSA), \detect{} times out after several days.
-The profiling result shows that the tool spends most its time in Z3.
-Later, we use a sampling method to detect side-channel leakages.
+The profiling result showed that the tool spent most its time in Z3.
+Later, we used a sampling method to detect side-channel leakages.
 The sampling method seems simple and may miss some leakages in theory.
@@
 Recent works such as CacheAudit and CaSym~\cite{Brotzman19Casym,182946} use a Least Recently Used (LRU) cache.
-First, there is no fundamental difficulties for us to adopt a more realistic cache models.
+First, there is no fundamental difficulties that prevent us from adopting a more realistic cache models.
 Second, the LRU model is still a substantial simplification of a real cache.
@@
 \subsection*{Leakages} While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers.
-The DES implementation of OpenSSL has a few side-channel leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort.
+The DES implementation of OpenSSL has a few side-channel leakages, but given the end of life status of DES, it is still unpatched for the worth of engineering effort.
 \detect{} also detects several leakages in asymmetric ciphers such as RSA.
@@
 If the dataset is biased, then we can not get correct results.
-The good news is that the most well-known dataset in
-machine learning is i.i.d. i.i.d. is the foundation of many machine learning
+The good news is that the most well-known data sets in
+machine learning are i.i.d. i.i.d. is the foundation of many machine learning
 techniques (e.g., cross-validation, SVM, back-propagation). The assumption of i.i.d. 

### 2021-06-02 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 \subsection*{Code Coverage} \detect{} analyzes one native x86 execution trace each time.
-The design, which is very precise in terms of true leakages compared to many static source code methods~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, share common limitations of dynamic approaches.
+The design, which is very precise in terms of true leakages compared to many static source code methods~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, but shares common limitations of dynamic approaches.
 \detect{} may only cover part of the code.
 Each time we only get one single execution trace.
-Therefore, we may neglect some side-channel vulnerabilities not covered by the traces analyzed.
+Therefore, we may miss some side-channel vulnerabilities not covered by the analyzed trace.
 However, this is not a crucial problem for analyzing cryptographic libraries, because cryptographic libraries are designed to have the same code coverage under various inputs.

### 2021-06-02 Chapter-7/Chapter-7.tex
Updates from Overleaf

@@
 In Chapter~\ref{chapter5}, we propose a fuzzing method to automatically detect and quantify the address-based side-channel leakages automatically.
-The proposed method can produce a conservative estimation of the side-channel leakage of the deterministic program.
+The proposed method can produce an estimation of the side-channel leakage of the deterministic program.
 As a result, any severe leakage reported by \ctool{} is the true severe leakage.
@@
 \textbf{Compiler-assisted Side-channel Vulnerability Analysis and Mitigation.}
-We propose to mitigate the side-channel leakages on a compiler backend.
+We propose to mitigate the side-channel leakages in a compiler backend.
 For example, the conditional execution can be eliminated by using the masks.

### 2021-06-02 Chapter-4/Chapter-4.tex
Update Chapter-4.tex

@@
 \end{figure}
-In this paper we assume an attacker can observe the secret-dependent control-flows in Figure~\ref{fig:side-channel}.
+In this chapter, we assume an attacker can observe the secret-dependent control-flows in Figure~\ref{fig:side-channel}.
 Therefore, an attacker can have two different observations for each leak site
@@
 and $M$ represents the set consisting of all plaintext messages to be encrypted. In a real execution, an adversary may have
-some observations ($O$) of the program. This paper only
+some observations ($O$) of the program. This dissertation only
 uses secret-dependent control flows and secret-dependent data

### 2021-06-02 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 \subsection*{Design Choices} At the early stage of the project, we use SMT solvers to get the solutions of constraints.
-However, we find for some ciphers (RSA), \detect{} times out after several days.
+However, we find for some ciphers (RSA), \detect{} timed out after several days.
 The profiling result showed that the tool spent most its time in Z3.
@@
 \section{Precise Analysis on Multiple-trace Attacks}
-This paper presents an approach that tries to give a conservative
-estimate of the amount of leaked information by address-based
+In this work, we present an approach that tries to give a 
+estimation of the amount of leaked information by access-based
 side-channel attacks. These attacks exploit the data-flow from secrets

### 2021-06-02 SupplementaryMaterial/Acknowledgments.tex
Updates from Overleaf

@@
 Prof.
-Hanrahan helped me improve the grammar of my dissertation proposal and my dissertation.
+Hanrahan and Prof.
+Larus helped me improve the grammar of my dissertation proposal and my dissertation.
 Prof.
@@
 This research was supported in part by the National Science Foundation (NSF) under grant CNS-1652790, and the Office of Naval Research (ONR) under grants N00014-16-1-2912, N00014-16-1-2265, and N00014-17-1-2894.
-Any opinions, or conclusions in the paper do not reflect the views of funding agencies.
+Any opinions, or conclusions in the dissertation do not reflect the views of funding agencies.

### 2021-06-02 Chapter-6/Chapter-6.tex
Update Chapter-6.tex

@@
 affected by the input, which is useful because we cannot
-assume the input secrets of the software in practice. In the paper, we
+assume the input secrets of the software in practice. In the chapter, we
 use the sampling result to approximate the true value of the
-channel capacity. We prove the sampling method presented in the paper can only give the conservative estimation of the amount of the true leakage.
+channel capacity. We prove the sampling method presented in the chapter can only give the conservative estimation of the amount of the true leakage.
 

### 2021-06-02 Chapter-5/Chapter-5.tex
Update Chapter-5.tex

@@
 Still, he can infer whether some memory addresses are accessed or not at various granularities after \textit{each run} of the victim program.
-We call the memory access information as the observation ($O$) in the rest of the paper.
+We call the memory access information as the observation ($O$) in the rest of the chapter.
 It is a typical scenario for most side-channel attacks.
@@
 We also assume the attacker knows the known message $m \in M$.
-In the rest of the paper, we use $\beta(K) \rightarrow O$ to denote a victim program that may have side-channel leakage sites.
+In the rest of the chapter, we use $\beta(K) \rightarrow O$ to denote a victim program that may have side-channel leakage sites.
 

### 2021-06-03 SupplementaryMaterial/Acknowledgments.tex
Updates from Overleaf

@@
 I learned a lot on the written English from him.
-His comments on the early draft are also very close to what I got from reviewers later.
+I am extremely grateful for his wise counsel.
+Jim's comments on the early draft are also very close to what I got from reviewers later.
 However, I did not take his comments seriously at the very beginning.
@@
 Finally, I would like to thank my parents for their continuous emotional and financial support.
-My parents always hope that I can study in a university that is near to them.
+My parents always hope that I can study in an institution that is near to them.
 However, they still expressed their full support for me when I decided to come to U.S.

### 2021-06-03 response.txt
Updates from Overleaf

@@
-Dear xxx,
+Dear Jim,
 
@@
 comment and revised my dissertation multiple rounds to eliminate any logic flows and
-fix all the typos and grammar errors. In summary, the revision covers the following aspects.
+fixed all the typos and grammar errors. In summary, the revision covers the following aspects.
 
@@
 false-positive rates. Besides, there are many talented researchers working on the
-same direction (e.g., Project Everest).
+same areas (e.g., Project Everest).
 
@@
 I think they are similar in some ways. Bayes' theorem describes the probability of
-an event, based on prior knowledge of an event has happened. The result from Bayes' theorem 
-can also be counterintuitive (e.g., drug testing).
+an event, based on prior knowledge of an event that has happened. The result from 
+Bayes' theorem can also be counterintuitive (e.g., drug testing).
 
@@
 
-a. I revised the description in Chapter 5. I avoided the use of term ``lower bound''
+a. I revised the description in Chapter 5. I avoided the use of the term ``lower bound''
 and tune my presentation.
@@
 
-It is true that Quincunx requires the assumption that input variables are
+You are right that Quincunx requires the assumption that input variables are
 independent and identically distributed. That's why I applied a black box fuzzing
@@
 randomly select an item from a dataset (Sample). If the dataset is biased, then we
-can not get correct results. The good news is that the most well-known data sets in
+can not get the correct results. The good news is that the most well-known data sets in
 machine learning are i.i.d. i.i.d. is the foundation of many machine learning
@@
 
-Dr. Larus helped me fix a lot of grammar issues. I also revised the dissertation
+Thank you for helping me fix a lot of grammar issues. I also revised the dissertation
 multiple times. In addition, I used Grammarly to proofread my dissertation.

### 2021-06-03 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 The simple modular exponentiation operation executes faster when the exponent bit is 0 and slower when the exponent bit is 1.
-An attacker can infer the whole secret key by measuring the execution time of the operation.
+As a result, an attacker can infer the whole secret key by measuring the execution time of the operation.
 Since then, researchers have proposed numerous side-channel attacks which exploit different kinds of ``side-channel'' information, including execution timing~\cite{184415,disselkoen2017prime+}, power consumption~\cite{kar20178}, electromagnetic radiation~\cite{agrawal2002side,217605}, and even sound~\cite{chari1999towards}.
@@
 Because the size of the cache is significantly smaller than the size of the main memory, the CPU may only find part of the data in the cache.
-Accessing data from the cache is faster than Accessing data from the main memory.
+Accessing data from the cache is faster than accessing data from the main memory.
 Such differences can be reflected in the variance in the program execution time.
@@
 Chapter~\ref{chapter5} extends the approach and quantifies the side-channel leakage in a multiple-trace attack.
-Chapter~\ref{chapter6} and Chapter~\ref{chapter7} discuss limitations of the dissertation and propose the future work.
+Chapter~\ref{chapter6} and Chapter~\ref{chapter7} discuss limitations of the dissertation research and propose the future work.

### 2021-06-03 Chapter-3/Chapter-3.tex
Updates from Overleaf
update

@@
 Symbolic execution can be used to explore all the possible paths, which is useful for many tasks.
-Nevertheless, it is significantly less likely for cache side channel bugs in crypto primitives.
-Cryptography primitives are more likely to have an even coverage of different paths (based on pseudo-random cipher states), and a branch-based side channel is vulnerable from the very first branch on secret data, making complex path conditions less often relevant.
+Nevertheless, it is significantly less likely for cache side-channel bugs in crypto primitives.
+Cryptography primitives are more likely to have an even coverage of different paths (based on pseudo-random cipher states), and a branch-based side-channel is vulnerable from the very first branch on secret data, making complex path conditions less often relevant.
 Therefore, we choose to analyze a trace instead of the whole path.
@@
 determined, $t_i$ is also fixed. Therefore, $ t_i = f_i(\beta, k, m)$, where $f_
-  i$ is a function that maps between $t_i$ and ($\beta$, $k$, $m$). In the paper,
+  i$ is a function that maps between $t_i$ and ($\beta$, $k$, $m$). In the chapter,
 we consider two code patterns that can be exploited by an attacker,
@@
 existing trace-based side-channel detection tools on vulnerability detections.
-For other tools, we use the data in the paper.
+For other tools, we use the reported results in their papers.
 As other tools do not quantify leakage sites, we only include the time of detecting vulnerabilities to perform a fair comparison.

### 2021-06-03 Chapter-4/Chapter-4.tex
Updates from Overleaf
update

@@
 Then, we introduce our model, the mathematical notation used in the
-paper, and our method.
+chapter, and our method.
 
@@
 \subsubsection*{Bit-slicing}
-Bit-slicing is an efficient method to construct constant-time implementation for side channel to mitigation.
+Bit-slicing is an efficient method to construct constant-time implementations to mitigate side-channels.
 The basic concept is to implement a function in terms of single-bit logical gate operations, such as AND, XOR, OR, and NOT\@.

### 2021-06-03 SupplementaryMaterial/Abstract.tex
Updates from Overleaf
update

@@
 leakage site. Finally, we extend our approach to quantify side-channel 
-leakages from multiple trace attacks. We present a method to quantify
-the lower bound of side-channel leakages. Unlike the previous side-channel 
+leakages from multiple trace attacks.  Unlike the previous side-channel 
 detection tools, our approach can identify severe side-channel
@@
 The experiments also show that 
-our side channel analysis reports quite precise leakage information
+our side-channel analysis reports quite precise leakage information
 that can help developers better triage the reported vulnerabilities.
@@
 As a result, developers can use our tools to develop more secure systems and the academic and industry
-communities can further advance side channel analysis on top of our research.
+communities can further advance side-channel analysis on top of our research.

### 2021-06-03 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 Figure~\ref{fig:secret:cf} shows an example.
-Depending on the value of \textsf{secret}, the code may or may not execute the code at line 6.
+Depending on the value of \textsf{secret}, the code may or may not execute line 6.
 An attacker can retrieve some information by observing the execution control-flow.
@@
 
-Secret-dependent data accesses happen when values of secret data affect which memory location the code reads or writes.
+Secret-dependent data accesses happen when the value of secret data affect which memory cell the code reads or writes.
 Figure~\ref{fig:secret:da} shows an example.

### 2021-06-03 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 
-Secret-dependent data accesses happen when the value of secret data affect which memory cell the code reads or writes.
+Secret-dependent data accesses happen when the value of secret data affect which memory location the code reads or writes.
 Figure~\ref{fig:secret:da} shows an example.
@@
 For example, cache channels can observe cache accesses at the level of cache sets~\cite{liu2015last}, cache lines~\cite{184415} or other granularities~\cite{yarom2017cachebleed}.
-Other types of side-channel attacks such as controlled-channel attack~\cite{7163052}, can observe a memory access at the level of memory pages.
+Other types of side-channel attacks such as controlled-channel attacks~\cite{7163052}, can observe a memory access at the level of memory pages.
 So a natural defense approach is to remove the above code patterns in the software.
@@
 The theory can serve as the foundation of the future work on quantifying the information leakage based on the fuzzing.
-    \item We implement the above method in a tool called \ctool{} and evaluate the tool with several benchmarks and real-world applications such as OpenSSL, mbedTLS, Libgcrpyt, TinyDNN, and GTK.
+    \item We implement above methods in a tool called \ctool{} and evaluate the tool with several benchmarks and real-world applications such as OpenSSL, mbedTLS, Libgcrpyt, TinyDNN, and GTK.
 The results show that our tool can detect and quantify the side-channel leakages effectively.

### 2021-06-03 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 \subsection{Attack Models}
-Previous work~\cite{182946} classifies side-channel attacks into three types based on the type of information that an attacker can learn during the attack.
+Previous work~\cite{182946} classifies side-channel attacks into three types based on the type of information that an attacker can learn during an attack.
 \subsubsection*{Timing-based Attacks}

### 2021-06-03 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 We find that all existing approaches need a lot of domain knowledge and expertise to launch the attacks.
+
 \subsubsection*{Media and Graphic Libraries}
@@
 SMT solvers are not good at non-linear arithmetic.
-However, such non-linear arithmetics are quite common in cryptography algorithms.
+However, non-linear arithmetics are quite common in cryptography algorithms.
 Recent studies show existing solvers still have bugs when dealing with real number calculations.
@@
 However, it still cannot solve the problem.
-First, many widely-used libraries (e.g., Intel MKL) do not open the source code.
+First, many widely-used libraries (e.g., Intel MKL) do not provide source code.
 Second, some libraries use hard-coded assembly code to pursue maximum performance.
-Here, we introduce several tools. CacheAudit~\cite{182946} uses abstract domains to compute an
+CacheAudit~\cite{182946} uses abstract domains to compute an
 over-approximation of cache-based side-channel information leakage upper bound.
@@
 secret-related code. Like CacheAudit, CacheS cannot
-indicate the sensitive level of side-channel vulnerabilities.
+measure the amount of leaked information in each side-channel vulnerability.
 CaSym~\cite{Brotzman19Casym} introduces a static cache-aware symbolic reasoning technique to cover multiple paths in a target program.
@@
 We adopted a similar approach to model the secret-dependent data accesses in the dissertation.
-\tool{} differs from CacheD in that we do not use traditional taint tracking or domain knowledge to cut the trace when identifying secret-dependent data access vulnerabilities.
+\tool{} differs from CacheD in that we do not use traditional taint tracking or domain knowledge to cut the execution trace when identifying secret-dependent data access vulnerabilities.
 \tool{} works on machine instructions directly instead of intermediate representations.
@@
 It uses statistical hypothesis testing to find true leakages.
-However, both imperfect trace alignment and a statistical testing result that DATA can produce false positives.
-MicroWalk~\cite{Wichelmann:2018:MFF:3274694.3274741} adopts a similar approach from DATA by comparing all accessed addresses.
+However, both imperfect trace alignment and the statistical testing that DATA uses can produce false positives.
+MicroWalk~\cite{Wichelmann:2018:MFF:3274694.3274741} adopts a similar approach as DATA by comparing all accessed addresses.
 It uses mutual information (MI) between sensitive input and execution state to quantify the information.

### 2021-06-03 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 Some tools (e.g., CacheD~\cite{203878}, CaSym~\cite{Brotzman19Casym}) have successfully identified unknown leakage sites in software products automatically.
-However, those tools have limitations.
+However, these tools have limitations.
 
@@
 Because instructions and data have different access patterns, separating iCache and dCache makes it possible for CPUs to fetch the code and data simultaneously and improve performance.
-Followed by the level-1 cache, each core also has the unified private level-2 cache for both the code and the data.
+Followed by the level-1 cache, each core also has the unified, private level-2 cache for both the code and the data.
 The level-3 cache is the last level cache (LLC).
@@
 We observe that finding side-channels using symbolic execution differs from
-traditional symbolic execution, and it can be optimized to be as efficient
+traditional symbolic execution, and the symbolic analysis approach can be optimized to be as efficient
 as other methods.

### 2021-06-03 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 is time-consuming. Also, as the SAT problem is a well-known NP-complete
-problem, it is hard to deal when it comes to
-practical uses with huge formulas. Despite the rapid improvement
+problem, it is hard to deal for huge formulas. Despite the rapid improvement
 in SMT solvers in recent years, constraint solving remains one of
@@
 The primary purpose of the step is to generate constraints of the input sensitive information from the execution trace.
-If we give the target program a new input which is different from the original input that was used to generate the execution trace but still satisfies these constraints, as an attacker, he will have the same observations on control-flow transfers and data-access patterns.
+If we give the target program a new input which is different from the original input that was used to generate the execution trace but still satisfies these constraints, an attacker will have the same observations on control-flow transfers and data-access patterns.
 
@@
 At the beginning of the symbolic execution, the tool creates new symbols for each byte in the raw buffer.
-For other data in the register or memory at the beginning, we use actual values from the runtime information collected during the runtime.
+For other data in the register or memory at the beginning, we use actual values from the runtime information.
 During the symbolic execution for each instruction, the tool updates every variable in the memory and registers with a math formula.
-The formula is made up of concrete values and the input key as the symbols accumulated through the symbolic execution.
+The formula is made up of concrete values and symbols accumulated through the symbolic execution.
 We implement several rules to simplify the formulas.
-For each formula, the tool will check weather it can be reduced into a concrete values (e.g., $k_1+12-k_1 = 12$ ).
+For each formula, the tool will check whether it can be reduced into a concrete values (e.g., $k_1+12-k_1 = 12$ ).
 If so, the tool will only use the concrete values in the following symbolic execution.

### 2021-06-03 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \subsubsection{Verification and Optimization}
-We run the symbolic execution (SE) on top of x86 instructions.
+We run the symbolic execution (SE) on the x86 instructions.
 In other words, we do not rely on any intermediate languages to simplify the implementation of symbolic execution.
-While the implementation itself has a lot of benefits (Better performance, accurate memory model), we need to implement the symbolic execution rules for each x86 instruction.
-However, due to the complexity of x86, it is inevitable to make mistakes. Therefore, we verify the correctness of the SE engine during the execution.
-The tool will collect the runtime information (Register values, memory values) and compare them with the formula generated from the symbolic execution.
+While the implementation itself has a lot of benefits (better performance, accurate memory model), we need to implement the symbolic execution rules for each x86 instruction.
+However, due to the complexity of x86, mistakes inevitable. Therefore, we verify the correctness of the SE engine during the execution.
+The tool will collect the runtime information (register values, memory values) and compare them with the formula generated from the symbolic execution.
 Whenever the tool finishes the symbolic execution of each instruction, the tool will compare the formula for each symbol and its actual value.
@@
 The unconditional instructions, such as CALL, JUMP, RET transfer control from one code segment location to another.
-Since the transfer is independent of the input sensitive information, an attacker was not able to infer any sensitive information from the control-flow.
-So the unconditional control-transfer does not leak any information based on our threat model.
+Since the transfer is independent of the input sensitive information, an attacker is not able to infer any sensitive information from the control-flow.
+So unconditional control-transfer does not leak any information based on our threat model.
 During the symbolic execution, we update the register information and memory cells with new formulas accordingly.
@@
 We generate the memory addressing
-formulas. As discussed before, every symbols in the formula is the input key. If the formula does not contain any symbols, the memory access is independent
+formulas. As discussed before, every symbol in the formula is the input key. If the formula does not contain any symbols, the memory access is independent
 from the input sensitive information and will not leak any sensitive information according to our threat model. Otherwise, we will generate the constraint for
@@
 
-$L$ represents the minimum memory address granularity that an attacker can observe. For example, Flush and Reload can distinguish between different cache lines, which means the value of L is 6.
+$L$ represents the minimum memory address granularity that an attacker can observe.
+For example, Flush and Reload can distinguish between different cache lines, which means the value of L is 6 for 64 byte cache line.
 

### 2021-06-03 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 Libgcrypt is a cryptographic library from the GunPG.
-As some previous work (e.g., CacheD) choose to evaluate their tools on Libgcrypt, we can compare the evaluation results by applying the tool on Libgcrypt.
+As some previous work (e.g., CacheD) choose to evaluate their tools on Libgcrypt, we can compare the evaluation results by applying our tool on Libgcrypt.
 
@@
 simplify the analysis. Our tool identifies all leakage sites
-reported by CacheD~\cite{203878} and find new leaks in less time.
+reported by CacheD~\cite{203878} and find a new leak in shorter time.
 We also find newer versions of RSA in OpenSSL have fewer leaks. Our tool can
@@
 existing trace-based side-channel detection tools on vulnerability detections.
-For other tools, we use the reported results in their papers.
+For other tools, we use the reported results in their papers~\cite{203878}.
 As other tools do not quantify leakage sites, we only include the time of detecting vulnerabilities to perform a fair comparison.
 
-The comparison result with CacheD~\cite{203878} is shown in Table~\ref{eval:cacheD}.
+The comparison result with CacheD~\cite{203878,217537} is shown in Table~\ref{eval:cacheD}.
 Note that one statement in the source code can be compiled into several machine instructions.
 So it is possible that one statement can have multiple leakage points.
-Under the circumstance, we think it is only a leakage.
+In the circumstance, we consider it takes only one leakage.
 We have confirmed that \detect{} can identify all the secret-dependent data access vulnerabilities reported by CacheD. In addition, \detect{} finds many new ones.
@@
 vulnerabilities. \detect{} can detect secret-dependent control-flows as well.
-Second, according to the CacheD paper, CacheD times out after 20 hours to process
+Second, according to the CacheD paper, CacheD times out after 20 hours when processing
 asymmetric ciphers. CacheD applies some domain knowledge to simplify and speed up
@@
 vulnerabilities.
-Third, CacheD only symbolizes the encryption keys. Some side-channel leakages when the input messages equal to some certain values. It is possible that CacheD miss some
+Third, CacheD only symbolizes the encryption keys. Some side-channel leakages occurs when the input messages equal to some certain values. It is possible that CacheD misses some
 leakages as we have discussion the previous sections.
-We notice that the number of instructions in these traces are different due to the different analysis starting functions and building options during the evaluation.
+We notice that the number of instructions in these traces are different due to the different analysis starting functions and build options during the evaluation.
 Table~\ref{eval:cacheD} shows that

### 2021-06-03 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 We also notice that later version of OpenSSL (after 1.0.1) uses a modified version with smaller S-table.
-However, \detect{} also find the leakage sites in the version.
+However, \detect{} also finds leakage sites in the version.
 Recent work also finds the sites through theoretical analysis.
@@
 \subsubsection*{RSA}
-We also evaluates our tool on the RSA implementations. With the optimizations
+We also evaluate our tool on the RSA implementations. With the optimizations
 introduced in the previous section, we do not apply any domain knowledge to
@@
 leakages in RSA occur in the big number implementation. We also find the newer
-versions of RSA in OpenSSL tend to have fewer leakages detected by \detect{}.
+versions of RSA in OpenSSL tend to have fewer leakages.
 
@@
 \end{lstlisting}
-    \caption{Unknown sensitive secret-dependent branch leaks from function 
+    \caption{Previously unknown sensitive secret-dependent branch leaks from function 
              \textsf{int\_bn\_mod\_inverse} in OpenSSL 1.1.1. The function can leak the last digit from big number \textbf{X}. However, the leak is more severe because of the 
-             function \textsf{BN\_rshift1}. Each time function \textsf{BN\_rshift1}
-             will shift \textbf{X} right by one and places the result in \textbf{X}. Therefore,
+             function \textsf{BN\_rshift1}. Each time, function \textsf{BN\_rshift1}
+             shifts \textbf{X} right by one and places the result in \textbf{X}. Therefore,
              an attacker can infer multiple bits of \textbf{X} by observing the branch at line 3.}
@@
 designed to be side-channel resistant from the library.
-Because these ciphers have no
+These ciphers have no
 data flow from secrets to branch conditions and load addresses.

### 2021-06-03 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 However, many reported leakage sites are not patched by developers.
-Recent work on side-channel vulnerabilities identification~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} also faces the same situation.
+Recent work on side-channel vulnerabilities identification~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} also faced the same situation.
 For example, DATA~\cite{217537} reports 2,248 potential leakage sites for the RSA implementation in OpenSSL 1.1.0f\@.
@@
 input secrets and calculates an ``average'' estimation, which is different from real attack scenarios when the secret that an attacker wants to retrieve is fixed.
-As a consequence, these results are less useful to assess the severity level of each leakage site.
+As a consequence, these results are less useful in assessing the severity level of each leakage site.
 
@@
 
-where $P(k_i, o_i)$ is the joint discrete distribution of $K$ and $O$.
+where $p(k_i, o_i)$ is the joint discrete distribution of $K$ and $O$.
 Alternatively, the mutual information can also be equivalently expressed as:
@@
 
-According to the Definition~\ref{chapter4:def}, to calculate the amount of leaked
+According to Definition~\ref{chapter4:def}, to calculate the amount of leaked
 information, the key is to calculate the cardinality

### 2021-06-03 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 We apply the ``counting by sampling'' method. For
-the constraint $g_{i}= c_{i_1} \land c_{i_2} \land ,\ldots, \land c_{i_j} \land ,\ldots, \land c_{i_m}$, if the solution satisfies $g_{i}$, it should also
+the constraint $g_{i}= c_{i_1} \land c_{i_2} \land ,\ldots, \land c_{i_j}\\ \land ,\ldots, \land c_{i_m}$, if the solution satisfies $g_{i}$, it should also
 satisfy any constraint from $c_{i_1}$ to $c_{i_m}$. In other words, $K_{c_gi}$

### 2021-06-03 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
     \small
-    \caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks),
+    \caption{Evaluation results overview: Side-channel Leaks\,(Leaks),
         Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF),
@@
 Monocyper is designed to be side-channel resistant. We use the library to test if our tool has any
-false positives. Besides, we also test \tool{} on some simple countermeasure implementations.
+false positives. We also test \tool{} on some simple countermeasure implementations.
 
@@
 the latter case, it means \tool{} cannot estimate the amount of leakage with a
-probabilistic guarantee. We manually check these leakage sites and find most of them are quite severe.
+probabilistic guarantee. \tool{} times out on around 10\% reported side-channel leakage sites. We manually check these leakage sites and find most of them are quite severe.
 We will present the details in the subsequent sections.
@@
 \end{figure*}
-We also evaluate \tool{} on RSA. Due to the page limit,
-we do not present the detailed leakage report. %, which is available online at the tool release website.
+We also evaluate \tool{} on RSA.  %, which is available online at the tool release website.
 %% \jl{where?}. In general,

### 2021-06-03 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 While removing secret-dependent memory-access patterns in existing software completely is hard and tedious, fixing some of the most dangerous leakages appears to be feasible.
-Previous studies~\cite{182946,203878,182946,236338,217537,langley2010ctgrind,xiao2017stacco,wang2019time,Wichelmann:2018:MFF:3274694.3274741,bao2021abacus} on side-channel detections have shown their effectiveness in finding such code patterns.
-Developers can run the tool to analyze the side-channels leakages and fix these patterns.
+Previous studies~\cite{182946,203878,182946,236338,217537,langley2010ctgrind,xiao2017stacco,wang2019time,Wichelmann:2018:MFF:3274694.3274741,bao2021abacus} on side-channel detection have shown their effectiveness in finding such code patterns.
+Developers can run a tool to analyze the side-channels leakages and fix these patterns.
 However, fixing all
@@
 optimizations in RSA, and Fast Fourier Transform (FFT) in many media processing libraries.
-For many non-cryptography developers, side-channels are not in consideration usually.
+For many non-cryptography developers, side-channels are not in their threat model.
 However, recent studies~\cite{xu2015controlled,191010,hahnel2017high} have shown a series of attacks on the non-cryptography libraries.
@@
 the leakage can reduce the encryption algorithm's strength. However,
-many attacks also exploit non-cryptography libraries and applications
-like machine learning
+some attacks also exploit non-cryptography libraries and applications
+such as machine learning
 applications~\cite{yan2020cache,hong2018security}, graphic
@@
 attacks on non-cryptography rely on multiple side-channel leakage
-sites to retrieve more information. Suppose one program has two
+sites to retrieve more information. Suppose a program has two
 leakage sites. It is hard to estimate the total effect of those two
@@
 and graphic libraries built on the top architecture-dependent
-libraries (e.g., Intel MKL~\cite{wang2014intel}), those tools are not able to
+libraries (e.g., Intel MKL~\cite{wang2014intel}), these tools are not able to
 handle them. Moreover, some binary analysis frameworks (e.g.,
@@
 To solve the above problem, we propose a method to estimate the effect of side-channel leakages automatically.
-We compare the side-channel attack to a communication system and use the channel capacity to quantify the amount of the information flow from the original secret to an attacker's observation.
+We treat the side-channel attack as a communication system and use the channel capacity to quantify the amount of the information flow from the original secret to an attacker's observation.
 The method also allows us to combine multiple leakages sites to retrieve the information.
@@
 If the patterns can uniquely distinguish the input space, then we think the information is leaked totally.
-However, in real cases, many of these side-channel leakage patterns are not enough to distinguish each leakage site but can still discern some secret inputs.
-In these cases, we call them partial leakages leaks.
+However, in real cases, many of these side-channel leakage patterns are not sufficient to distinguish each leakage site but can still discern some secret inputs.
+In these cases, we call them partial leakages.
 
@@
 With the debug information, we can precisely know the address access information of the source code.
-In the third phase, we exam the source code.
+In the third phase, we examine the source code.
 If one function has two memory access patterns, then the function is vulnerable to side-channel attacks.
@@
 In the rest of the chapter, we use $\beta(K) \rightarrow O$ to denote a victim program that may have side-channel leakage sites.
-
-In this chapter, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs).
-To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.
 

### 2021-06-03 Chapter-7/Chapter-7.tex
Updates from Overleaf

@@
 This dissertation research studies address-based side-channel leakages in two aspects: detection and quantification.
-In the side-channel vulnerability detection research, we explore and solve the two bottlenecks in today's automated side-channel vulnerability detection tool, performance and precision.
+In the side-channel vulnerability detection research, we explore and solve the two bottlenecks in today's automated side-channel vulnerability detection tool: performance and precision.
 In the side-channel vulnerability quantification research, we propose two different side-channel leakage quantification tools based on information theory.
@@
 The evaluation results show that \detect{} is three times to one hundred times faster than the state of art tools while finding all the leakages reported by the previous tools.
-In addition, \detect{} identity new leakages.
+In addition, \detect{} identifies new leakages.
 The new leakages were later confirmed by other researchers and software developers.
@@
 The proposed method can produce an estimation of the side-channel leakage of the deterministic program.
-As a result, any severe leakage reported by \ctool{} is the true severe leakage.
+As a result, any severe leakage reported by \ctool{} is a true severe leakage.
 We also study the total effect of two leakages.
 Using statistical hypothesis testing, we are able to determine if the two leakages are independent.
-If so, we can calculate the sum of the amount of leakage by adding two leakages.
+If so, we can calculate the sum of the amount of leakage by adding them.
 Our evaluation result on both several libraries and benchmarks show that \ctool{} is effective and accurate in detecting the side-channel leakage.
@@
 Take the method in the dissertation, for example.
-We may have the following challenges.
-First, our proposed tools in the dissertation rely on the dynamic binary instrumentation frameworks to collect the runtime information.
-As for kernel programs, a similar task can be achieved by some whole system emulators such as BitBlaze~\cite{song2008bitblaze} and S2E~\cite{chipounov2012s2e}.
+We will have the following challenges.
+First, our proposed tools in the dissertation rely on dynamic binary instrumentation frameworks to collect the runtime information.
+For kernel programs, a similar task can be achieved by some whole system emulators such as BitBlaze~\cite{song2008bitblaze} and S2E~\cite{chipounov2012s2e}.
 S2E uses a modified Linux kernel and QEMU to trace the kernel components.
@@
 For example, GNU toolchains inset LFENCE before any possible vulnerable instructions, including all load instructions, all indirect branches, and return instructions.
-We plan only to change points that are likely to leak sensitive information.
+We suggest only changing points that are likely to leak sensitive information.
 Finally, with the tool presented in the dissertation, we can modify only part of the ``severe'' leakage sites.

### 2021-06-03 Chapter-7/Chapter-7.tex
Updates from Overleaf

@@
 We evaluate \detect{} on popular cryptographic libraries including OpenSSL, mbedTLS, Libgcrypt, and Monocyper.
-The evaluation results show that \detect{} is three times to one hundred times faster than the state of art tools while finding all the leakages reported by the previous tools.
+The evaluation results show that \detect{} is three times to one hundred times faster than the state-of-art tools while finding all the leakages reported by the previous tools.
 In addition, \detect{} identifies new leakages.

### 2021-06-03 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 attacks on non-cryptography rely on multiple side-channel leakage
-sites to retrieve more information. Suppose a program has two
-leakage sites. It is hard to estimate the total effect of those two
-leakages. However, no existing tools that can estimate the total
+sites to retrieve more information. A program  usually has more than two
+leakage sites. However, no existing tools that can estimate the total
 effect of multiple leakage sites. For real-world applications with
-thousands of lines, it is hard to estimate the amount of leaked
-information. Attackers can guess the values of some temporary
-values. And those temporary values contain some knowledge of the
+thousands of lines, attacker can exploit more than one leakage sites
+to retrieve more information. Attackers can guess the values of many temporary
+values. And these temporary values contain some knowledge of the
 original secret buffer.
@@
 the same as the offset within the binary file. We choose the start
-address of some common functions (e.g, $\mathit{main}$) ($b$) as the navigation
+address of some common functions (e.g., $\textsf{main}$) ($b$) as the navigation
 function. We get the virtual memory address of the start of the

### 2021-06-03 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 Angr~\cite{shoshitaishvili2016state}) are limited in analyzing
-floating-point instructions. However, the functionality of those
+floating-point instructions. However, the functionality of these
 applications heavily depends on floating-point calculations.
@@
 Third, while many existing works can detect side-channel leakages, few
-of them can assess the severity levels of those
+of them can assess the severity levels of these
 vulnerabilities~\cite{182946,203878,182946,236338,217537,langley2010ctgrind,xiao2017stacco,wang2019time,Wichelmann:2018:MFF:3274694.3274741,bao2021abacus,236334,wang2021data,sung2018canal}.
@@
 bound estimation of each leakage site.  This is helpful to justify that the software is secure if the reported leakage is zero. However,
-those tools cannot report to software developers how severe each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage.
+these tools cannot report to software developers how severe each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage.
 Often the over-approximated estimate is very far away from the amount of real leakage.

### 2021-06-03 Appendix-A/Appendix-A.tex
Updates from Overleaf

@@
 It uses dynamic binary instrumentation tools to collect execution traces.
-After that, \tool{} analyzes those traces and produces the vulnerability report.
+After that, \tool{} analyzes these traces and produces the vulnerability report.
 While \tool{} can work on the stripped binary executable, \tool{} can also read the symbol and debugging information to give a more fine-grained (e.g., line numbers) report.
@@
 However, we strongly recommend you to build \tool{} inside a container to avoid any dependency problems.
-To simplify the illustration, we only include the instructions of installations within the docker in this paper.
+To simplify the illustration, we only include the instructions of installations within the docker in this chapter.
 \begin{itemize}

### 2021-06-04 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 As a result, an attacker can infer the whole secret key by measuring the execution time of the operation.
-Since then, researchers have proposed numerous side-channel attacks which exploit different kinds of ``side-channel'' information, including execution timing~\cite{184415,disselkoen2017prime+}, power consumption~\cite{kar20178}, electromagnetic radiation~\cite{agrawal2002side,217605}, and even sound~\cite{chari1999towards}.
+Since then, researchers have proposed numerous side-channel attacks which exploit different kinds of ``side-channel'' information, including execution timing~\cite{184415,disselkoen2017prime+,7163050}, power consumption~\cite{kar20178}, electromagnetic radiation~\cite{agrawal2002side,217605}, and even sound~\cite{chari1999towards}.
 
@@
 \end{lstlisting}
-    \caption{Secret-dependent data accesses}
+    \caption{Secret-dependent data access}
     \label{fig:secret:da}
@@
 We model the information quantification problem as a counting problem and use a Monte Carlo sampling method to estimate the information leakage.
-    \item We implement the method into a tool and apply it to several pieces of real software.
+    \item We implement the method into a tool called \tool{} and apply it to several pieces of real software.
 \tool{}\footnote{Abacus is open source under the MIT license.

### 2021-06-04 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \section{Background and Threat Model}
+In this chapter, we treat the side-channel attack as a communication system between two parties.
 In the section, we give an overview of the background knowledge of information theory and present the threat model of the chapter.

### 2021-06-04 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 For example, CacheAudit~\cite{182946} estimates that a 128-bit
-AES encryption can leak more than 128 bits. As a result, even those
-tools report severe leakage, it does not mean the program has a truly severe leakage.
+AES encryption can leak more than 128 bits. As a result, even these
+tools report that some leakages can leak lots of information, it does not mean the program has truly severe side-channel vulnerabilities.
 
@@
 In this chapter, we use the channel capacity to describe the amount of information leakages through a channel.
-In information theory, the channel capacity is used to quantify the rate of information can be reliably transmitted over a channel.
+In information theory, the channel capacity is used to quantify the maximum rate of information can be reliably transmitted over a channel.
 If we use $K$ to represent the input secrets and $O$ to represent the output observation.

### 2021-06-04 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 Based on the discussion in \S\ref{chapter1} and \S\ref{chapter2}, fixing side-channel leakage sites in software is usually easier than adopting new hardware to defend against side-channel attacks.
-In order to eliminate those leakage sites, developers need to find potential leakage sites in a large code base.
+In order to eliminate these leakage sites, developers need to find potential leakage sites in a large code base.
 However, the manual process is tedious and error-prone.
@@
   \item The operands of each instruction and their concrete values during the runtime.
-  \item The value of EFLAGS register.
+  \item The value of EFLAGS registers.
   \item The memory address and the length of the sensitive information.
-        Most crypto libraries stores sensitive information in arrays,
+        Most crypto libraries store sensitive information in arrays,
         variables or contiguous buffer.

### 2021-06-08 response.txt
update

@@
 
-a. The methods in my dissertation can not find all kinds of side-channel leakages. No
+a. The methods in my dissertation cannot find all kinds of side-channel leakages. No
 tool can find all forms of leakages. Even for address-based side-channel leakages,
-Abacus and Quincunx can not find all the leakages due to the code coverage problem.
+Abacus and Quincunx cannot find all the leakages due to the code coverage problem.
 Some verification tools can prove the absence of side-channel leakages for some small
@@
 randomly select an item from a dataset (Sample). If the dataset is biased, then we
-can not get the correct results. The good news is that the most well-known data sets in
+cannot get the correct results. The good news is that the most well-known data sets in
 machine learning are i.i.d. i.i.d. is the foundation of many machine learning

### 2021-06-08 Chapter-3/Chapter-3.tex
Updates from Overleaf
update

@@
 CacheD performs better than CaSym.
-However, it still can not handle large programs such as RSA directly.
+However, it still cannot handle large programs such as RSA directly.
 It uses some domain knowledge to analyze only part of the program.
@@
 above definition, $m$ is also a variable. So it is possible for some $m \in M$,
-we can not find a pair of two different $k_{i1}$ and $k_{i2}$ to satisfy the above inequation.
+we cannot find a pair of two different $k_{i1}$ and $k_{i2}$ to satisfy the above inequation.
 For example, in Figure~\ref{fig:chapter3:cf}, if $m = \mathtt{0}$, the function \textsf{example1} will always execute the branch 2.
@@
 Similarly, we can model the memory access at line 6 with the formula:  $10 + m + (k_1 \mod 32) >> 6  \neq 10 + m + (k_2 \mod 32) >> 6$.
-If $m = 0$, we can not find satisfiable $k_1$ and $k_2$ for the above inequation, which indicates that it will always access the same cache line at line 6.
+If $m = 0$, we cannot find satisfiable $k_1$ and $k_2$ for the above inequation, which indicates that it will always access the same cache line at line 6.
 However, it is possible that for some $m \in M$, we can find such a pair of $k_1$ and $k_2$ ($m = 53, k_1 = 1, k_2 = 0$).
@@
 length of the key is 384 bit. The input public message is ``Hello World!''.
-We mark variables and buffers that store a secret.
+We mark variables and buffers that store the sensitive data.
 For DES and AES, we mark symmetric keys as secrets.

### 2021-06-08 Chapter-5/Chapter-5.tex
Updates from Overleaf
update

@@
 Therefore, the Shannon entropy of the original K $H(K)$ is also $3\,\mathrm{bits}$, according to Equation~\ref{chapter5:eq1}.
-Therefore, the leakage in Figure~\ref{chapter5:fig:example1} show the input secret is leaked totally.
+Therefore, the leakage in Figure~\ref{chapter5:fig:example1} shows the input secret is leaked totally.
 
@@
 In the example, different keys lead to different indexes.
-However, as $T_0 + i_0$ equals to $T_1 + i_0$, \ctool{} can not observe the difference here, which is a false positive.
+However, as $T_0 + i_0$ equals to $T_1 + i_0$, \ctool{} cannot observe the difference here, which is a false positive.
 
@@
 keys and use the key to sample the program. Due to the enormous search
-space, we can not iterate every input. However, our method can give a
+space, we cannot iterate every input. However, our method can give a
 conservative estimate of each leakage site.
@@
 different byte at memory $\mathtt{0x7ffff7ffda01}$ when the secret is
-$k_2$, an attacker who has the page-level observation can not launch
+$k_2$, an attacker who has the page-level observation cannot launch
 the attack but an attacker who launches the cache attack can know the
@@
 We run the chi-squared test to determine if any two leaked functions have independent leakages.
-However, we can not conclude that any two leakages from cryptography benchmarks are independent under the chi-squared test.
+However, we cannot conclude that any two leakages from cryptography benchmarks are independent under the chi-squared test.
 We think it is due to the avalanche effect in cryptography.

### 2021-06-08 changelog.tex
update

@@
 a.
-The methods in my dissertation can not find all kinds of side-channel leakages.
+The methods in my dissertation cannot find all kinds of side-channel leakages.
 No tool can find all forms of leakages.
-Even for address-based side-channel leakages, Abacus and Quincunx can not find all the leakages due to the code coverage problem.
+Even for address-based side-channel leakages, Abacus and Quincunx cannot find all the leakages due to the code coverage problem.
 Some verification tools can prove the absence of side-channel leakages for some small code snippets.
@@
 Each time, we randomly select an item from a dataset (Samples).
-If the dataset is biased, then we can not get correct results.
+If the dataset is biased, then we cannot get correct results.
 The good news is that the most well-known data in machine learning is i.i.d.
@@
 
-Dr. Larus helped me a lot on fixing grammar issues. I also revised the dissertation multiple times. In addition, I used Grammarly to proofread my dissertation.
+Dr. Larus helped me a lot in fixing grammar issues. I also revised the dissertation multiple times. In addition, I used Grammarly to proofread my dissertation.
 

### 2021-06-08 Chapter-2/Chapter-2.tex
update
Updates from Overleaf

@@
 usually easy to implement. Coppens et
-al.~\cite{Coppens:2009:PMT:1607723.1608124} uses a compiler
+al.~\cite{Coppens:2009:PMT:1607723.1608124} use a compiler
 to eliminate key-dependent control-flow transfers. Crane et
-al.~\cite{crane2015thwarting} mitigates side-channels by randomizing software.
+al.~\cite{crane2015thwarting} mitigate side-channels by randomizing software.
 As for crypto libraries, the basic idea is to eliminate key-dependent
@@
     %\centering
-    \caption{Many leakage detection tools are only evaluated on cryptography libraries.  All of them can not reason about the total effect of multiple leakages.}
+    \caption{Many leakage detection tools are only evaluated on cryptography libraries.  All of them cannot reason about the total effect of multiple leakages.}
     \label{table:side_channel_detection_tool}

### 2021-06-08 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \centering
-\caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0.
-According to \tool{}\cite{bao2021abacus}, the mark ``$*$'' means timeout, which indicates more severe leakages.
-$0.0$ means very small amount of leakage, but not exactly zero.}\label{chapter5:tab:RSAOpenSSL1.1.0}
+\caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0.}\label{chapter5:tab:RSAOpenSSL1.1.0}
 %\resizebox{\columnwidth}{!}{

### 2021-06-08 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-Table~\ref{chapter5:tab:RSAOpenSSL1.1.0} shows the leaked function and the amount of leakage reported by \tool{} and \ctool{}.
+Table~\ref{chapter5:tab:RSAOpenSSL1.1.0} shows the leaked function and the amount of leakage reported by \ctool{}.
 First, as the result indicates, the leakage sites that leak a lot of information (> 5.0 bits) are all fixed in OpenSSL 1.1.1.
@@
 Third, previous work~\cite{bao2021abacus} reports some leakage sites leak little information, but \ctool{} reports the vulnerability is severe.
-\tool{} quantifies the amount of leaked information for one execution.
+Previous work \tool{} quantifies the amount of leaked information for one execution.
 So it is possible that some leakage sites leak little information for one input but leak more information for a different input.

### 2021-06-10 Chapter-6/Chapter-6.tex
update
Updates from Overleaf

@@
 \detect{} also detects several leakages in asymmetric ciphers such as RSA.
-After we manually analyze these leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which may partially explain why developers are not interested in fix all the side-channel leakages.
+After we manually analyze these leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which may partially explain why developers are not interested in fixing all the side-channel leakages.
 
@@
 Each time, we randomly select an item from a dataset (Sample).
-If the dataset is biased, then we can not get correct results.
+If the dataset is biased, then we cannot get correct results.
 The good news is that the most well-known data sets in
@@
 So it bears the same limitations of dynamic approaches as well.
-\ctool{} can not cover all the paths and may miss some side-channel vulnerabilities.
+\ctool{} cannot cover all the paths and may miss some side-channel vulnerabilities.
 It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control flow under various inputs.

### 2021-06-10 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 \begin{displaymath}
-    Leakage = H(K;o) = H(K) - H(K|o)
+    Leakage = I(K;o) = H(K) - H(K|o)
 \end{displaymath}
@@
 \begin{align*}
-    H(K;o) & = - \sum_{k {\in} K^o}{p(k|o)\log_2p(k|o)}                         \\
+    I(K;o) & = - \sum_{k {\in} K^o}{p(k|o)\log_2p(k|o)}                         \\
            & \qquad   - \sum_{k` {\in} (K \setminus K^o)}{p(k'|o)\log_2p(k'|o)} \\
@@
 
-Based on the Definition~\ref{independentC}, we can split the constraint
-$c_t(\addr{1},\addr{2},\ldots,\addr{n})$ into several independent constraints.
+Based on Definition~\ref{independentC}, we can split the constraint
+$c_t(\addr{1},\addr{2},\addr{3},\ldots,\addr{n})$ into several independent constraints.
 There are many partitions. For our project, we are interested in the following
@@
 same. They both use a pre-computed lookup table to speed up computation.
-However, \tool{} reports leakage 1, 2, 3 typically leak more information
-compared to leakage 4, 5, 6, 7. We check the source code and find leakage 1, 2,
+However, \tool{} reports leakage 1, 2, 3 typically leak more information (7.6 - 8.1 bits)
+compared to leakage 4, 5, 6, 7 (4.0 bits). We check the source code and find leakage 1, 2,
 3 use secret to access the lookup table \emph{RT0, RT1, RT2, RT3}, which is 8K

### 2021-06-14 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 However, many reported leakage sites are not patched by developers.
-Recent work on side-channel vulnerabilities identification~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} also faced the same situation.
+Recent work on side-channel vulnerability identification~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} also faced the same situation.
 For example, DATA~\cite{217537} reports 2,248 potential leakage sites for the RSA implementation in OpenSSL 1.1.0f\@.

### 2021-06-14 Appendix-A/Appendix-A.tex
Updates from Overleaf

@@
 % !TEX root = ../YourName-Dissertation.tex
-\Appendix{Abacus Usage Manual}
+\Appendix[Abacus Usage Manual]{Abacus Usage Manual\footnote{The original manual was published in~\cite{9402288}.}}
 
@@
 
-Abacus analyzes vulnerabilities on the binary executable.
+\tool{} analyzes vulnerabilities on the binary executable.
 Here we build it into  a 32-bit ELF executable.
-Note that while Abacus can work on stripped binaries without the source code, we use debug information to get a more detailed result (e.g., the line number in the source code) in this example.
+Note that while \tool{} can work on stripped binaries without the source code, we use debug information to get a more detailed result (e.g., the line number in the source code) in this example.
 \begin{lstlisting}[language=bash]
@@
 
-As expected, it shows that the function \textsf{is\_odd} has one secret-dependent control-flow vulnerability at line 5. Also, Abacus shows the vulnerability leaks 1 bit information.
+As expected, it shows that the function \textsf{is\_odd} has one secret-dependent control-flow vulnerability at line 5. Also, \tool{} shows the vulnerability leaks 1 bit information.
 

### 2021-06-14 Appendix-A/Appendix-A.tex
Updates from Overleaf

@@
 \begin{table}[h!]
-\centering\tiny\scriptsize
+\centering%\tiny\scriptsize
 \caption{A sample leakage report}\label{tab:DESOpenSSL1.1.1}
@@
 You can refer to the continuous integration scripts to build \tool{} on your operating system.
-However, we strongly recommend you to build \tool{} inside a container to avoid any dependency problems.
+However, it is strongly recommended to build \tool{} inside a container to avoid any dependency problems.
 To simplify the illustration, we only include the instructions of installations within the docker in this chapter.
@@
 
-\begin{lstlisting}[language=bash]
+\begin{lstlisting}[language=bash, frame=none, numbers=none]
 $ ./build.sh
@@
 Note that while \tool{} can work on stripped binaries without the source code, we use debug information to get a more detailed result (e.g., the line number in the source code) in this example.
-\begin{lstlisting}[language=bash]
+\begin{lstlisting}[language=bash, frame=none, numbers=none]
 $ cd examples
@@
 We use the pin tool to collect the execution trace. The tool can automatically collect the trace and other necessary runtime information.
-\begin{lstlisting}[language=bash]
+\begin{lstlisting}[language=bash, frame=none, numbers=none]
 $ cd /abacus/Pintools
@@
 \subsection*{Quantify the leakage}
-To analyze the execution trace and generate the report, run the below command:
-\begin{lstlisting}[language=bash]
+To analyze the execution trace and generate the report, run the following command:
+\begin{lstlisting}[language=bash, frame=none, numbers=none]
 $ ./build/App/QIF/QIF ./Inst_data.txt -f Function.txt \ 
@@
 
-\begin{lstlisting}[language=bash]
+\begin{lstlisting}[language=bash, frame=none, numbers=none]
 Start Computing Constraints
@@
 
-\begin{lstlisting}[language=bash]
+\begin{lstlisting}[language=bash, frame=none, numbers=none]
 $ cd /abacus/script/AES_MBEDTLS_2.5
@@
 If you do not specify the option, \tool{} can automatically terminate the sampling when the tool has 95\% confidence that the error of estimated leaked information is less than 1 bit.
-Please refer to the paper if you want to learn more about the details.
+Refer to the paper~\cite{bao2021abacus} to learn more about the details.
 \vspace{6pt}

### 2021-06-14 Chapter-7/Chapter-7.tex
update
Updates from Overleaf

@@
 In the side-channel vulnerability detection research, we explore and solve the two bottlenecks in today's automated side-channel vulnerability detection tool: performance and precision.
-In the side-channel vulnerability quantification research, we propose two different side-channel leakage quantification tools based on information theory.
+In the side-channel vulnerability quantification research, we propose two different side-channel leakage quantification methods based on information theory.
 
@@
 \detect{} analyzes the side-channel leakages directly from X86 execution traces.
-Existing binary analysis tools usually transfer the x86 instruction to intermediate languages (IR) simplify the implementation.
+Existing binary analysis tools usually transfer x86 instructions to intermediate languages (IR) simplify the implementation.
 However, such designs have expensive overheads and imprecise analysis results.
-To tackle these problem, we take the engineering efforts and implement the analysis from scratch  based on Intel developer's manual.
+To tackle these problems, we take the engineering efforts and implement the analysis from scratch  based on the Intel developer's manual.
 We evaluate \detect{} on popular cryptographic libraries including OpenSSL, mbedTLS, Libgcrypt, and Monocyper.
@@
 We rely on \detect{} to detect side-channel leakages.
-After that, we use approximate model counting to quantify the leakage site.
+After that, we use approximate model counting to quantify the leakage sites.
 The method is implemented in a prototype tool called \tool{}.
 We show its effectiveness in quantifying side-channel leakage.
-With the new definition of information leakage that models actual side-channel attackers, quantifying the number of leaked bits helps understand the severity level of side-channel vulnerabilities.
+With a new definition of information leakage that models actual side-channel attackers, quantifying the number of leaked bits helps understand the severity level of side-channel vulnerabilities.
 The evaluation confirms that \tool{} is useful in estimating the amount of leaked information in real-world applications.
@@
 The evaluation results show the effeteness and generality of our proposed method.
-We open source the tools in the dissertation to facilitate future research in the area.
+We also release the prototypes to facilitate future research in the area.
 \section{Future Directions}
-In the future, we plan to explore the following directions based on the dissertation research.
+There are a few potential directions the dissertation research.
 
-\textbf{Kernel Space Side-channel Vulnerability Detection.} There are several side-channel vulnerability detection tools together with the dissertation tool.
+\textbf{Kernel Space Side-channel Vulnerability Detection.} There are several side-channel vulnerability detection tools.
 Most of the tools are designed to analyze the side-channel leakages in user-level applications such as cryptographic libraries.
@@
 Some vulnerabilities need to be triggered by specific input from the user space applications or devices.
-Our tool can not handle interruptions and exceptions.
+Our tool cannot handle interruptions and exceptions.
 But they are common inside the kernel.
 On the positive side, we expect there are plenty of leakage sites inside the kernel.
-The dissertation provides the approaches to pick up ``severe'' leakages automatically.
+The dissertation provides methods to identify ``severe'' leakages automatically.
 
 \textbf{Compiler-assisted Side-channel Vulnerability Analysis and Mitigation.}
-We propose to mitigate the side-channel leakages in a compiler backend.
-For example, the conditional execution can be eliminated by using the masks.
+It is promising to mitigate the side-channel leakages in a compiler backend.
+For example, the conditional execution can be eliminated by using masks.
 Eliminating side-channel leakages from compilers is not a brand new idea.
@@
 The LVI harden binaries generated from GNU toolchains takes 6-10x longer to run.
-For example, GNU toolchains inset LFENCE before any possible vulnerable instructions, including all load instructions, all indirect branches, and return instructions.
+For example, GNU toolchains insert LFENCE before any possible vulnerable instructions, including all load instructions, indirect branches, and return instructions.
 We suggest only changing points that are likely to leak sensitive information.
-Finally, with the tool presented in the dissertation, we can modify only part of the ``severe'' leakage sites.
+Finally, with the tool presented in the dissertation, we can fix only part of the ``severe'' leakage sites.

### 2021-06-14 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
     \centering
-    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
+    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth]
 uint8_t key[2], t1, t2;
@@
 \begin{table}[ht]
-    \centering\small\footnotesize
+    \centering%\small\footnotesize
     \caption{The distribution of observation}\label{shtable}
@@
 Based on Shannon entropy, the respective amount of information in A and B equals to
-    {\footnotesize
+    {%\footnotesize
         \begin{align*}
@@
     \centering
-    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
+    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth]
 char key[9] = input();
@@
 \begin{table}[ht]
-    \centering\small\footnotesize
+    \centering%\small\footnotesize
     \caption{New leakage modeling results}
@@
     \centering
-    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
+    \begin{lstlisting}[ frame=none]
 int mbedtls_internal_aes_encrypt( mbedtls_aes_context *ctx,
@@
     \centering
-    \vspace*{-9pt}
-    \hspace*{-15pt}
+    %\vspace*{-9pt}
+    %\hspace*{-15pt}
     \subfloat[OpenSSL 0.9.7]{
@@
     \centering
-    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
+    \begin{lstlisting}[xleftmargin=.08\textwidth, xrightmargin=.0\textwidth, frame=none]
 # define mul_add_c2(a,b,c0,c1,c2)                    \
@@
     \centering
-    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
+    \begin{lstlisting}[xleftmargin=.08\textwidth, xrightmargin=.0\textwidth, frame=none]
 # define mul_add_c2(a,b,c0,c1,c2)      do { \
@@
 
-To evaluate the effectiveness of the leaked bits reported by \tool{}, we conduct a case study of all the leaked sites identidied by \tool{} in OpenSSL 1.1.0f.
+To evaluate the effectiveness of the leaked bits reported by \tool{}, we conduct a case study of all the leaked sites identified by \tool{} in OpenSSL 1.1.0f.
 Table~\ref{chapter4:tab:RSAOpenSSL1.1.0} shows the result.
@@
 %\resizebox{\columnwidth}{!}{
-\begin{tabular}{rrrrc}
+\begin{tabular}{lrrrc}
 \hline
@@
     \centering
-    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
+    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.0\textwidth, frame=none]
 uint8_t password = input();
@@
 \centering
-    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth, frame=none]
+    \begin{lstlisting}[xleftmargin=.05\textwidth, xrightmargin=.05\textwidth, frame=none]
 static const uint8_t T[1024] = {
@@
 \centering
-    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth, frame=none]
+    \begin{lstlisting}[xleftmargin=.05\textwidth, xrightmargin=.05\textwidth, frame=none]
 static const uint32_t T[256] = {
@@
 \begin{figure}
-  \begin{minipage}{0.45\linewidth}
-    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
+  \begin{minipage}{0.8\linewidth}
+    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
 bool pwcheck(uint8_t *key, uint8_t *pub) {
@@
 }
-\end{lstlisting}
+\end{lstlisting}\caption{A vulnerable password checker.}\label{fig:chapter4:pwcheck1}
   \end{minipage}
-  \hfill
-  \begin{minipage}{0.45\linewidth}
-    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none]
+  \vfill
+  \begin{minipage}{0.8\linewidth}
+    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.00\textwidth, frame=none]
 bool pwcheck(uint8_t *key, uint8_t *pub) {
@@
 }
-\end{lstlisting}
+\end{lstlisting}\caption{A safe password checker.}\label{fig:chapter4:pwcheck2}
 \end{minipage}
-  \caption{A password checker. The left version is vulnerable to side-channel attacks. The right version is the fixed version.}\label{fig:chapter4:pwcheck}
 \end{figure}
 
-We illustrate the quantification method on a password checking example.
-As shown in Figure~\ref{fig:chapter4:pwcheck}, the left version is vulnerable to side-channel attacks because of the early return at line 4.
+We illustrate the quantification method on two password checking examples.
+As shown in Figure~\ref{fig:chapter4:pwcheck1}, the version is vulnerable to side-channel attacks because of the early return at line 4.
 If the first bytes of \textsf{key} and \textsf{pub} are the same, the function will continue running and access the second byte.
-The right version fixes the vulnerability because the function will continue comparing the second byte even if the first byte is different.
-\tool{} identifies the leakage site in the left figure successfully and estimates the amount of leakage is $16$ bits.
+Figure~\ref{fig:chapter4:pwcheck2} fixes the vulnerability because the function will continue comparing the second byte even if the first byte is different.
+\tool{} identifies the leakage site in Figure~\ref{fig:chapter4:pwcheck1} successfully, and estimates the amount of leakage is $16$ bits.

### 2021-06-14 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \begin{figure}[h]
-  \begin{minipage}{0.6\linewidth}
-    \begin{lstlisting}[xleftmargin=.15\textwidth,xrightmargin=.30\textwidth]
+  \begin{minipage}{0.49\linewidth}
+    \begin{lstlisting}[xleftmargin=.05\textwidth,xrightmargin=.08\textwidth]
 void bar(uint8_t secret)
@@
   \hfill
-  \begin{minipage}{0.4\linewidth}
-    \resizebox{0.8\textwidth}{!}{%
-
+  \begin{minipage}{0.42\linewidth}
+    \resizebox{0.999\textwidth}{!}{%
       \begin{tabular}{cccccccccc}
@@
 \begin{figure}[h]
-  \begin{minipage}{0.60\linewidth}
-    \begin{lstlisting}[xleftmargin=.15\textwidth,xrightmargin=.30\textwidth]
+  \begin{minipage}{0.49\linewidth}
+    \begin{lstlisting}[xleftmargin=.05\textwidth,xrightmargin=.08\textwidth]
 void bar(uint8_t secret)
@@
   \hfill
-  \begin{minipage}{0.4\linewidth}
-    \resizebox{0.8\textwidth}{!}{%
+  \begin{minipage}{0.42\linewidth}
+    \resizebox{0.999\textwidth}{!}{%
 
@@
   \begin{minipage}{0.45\linewidth}
-    \begin{lstlisting}[numbers=none,xleftmargin=.1\textwidth,xrightmargin=.2\textwidth]
+    \begin{lstlisting}[numbers=none,xleftmargin=.1\textwidth,xrightmargin=.15\textwidth]
 uint8_t *T = malloc(4);
@@
 \begin{figure}[h]
-\begin{minipage}{0.4\linewidth}
+\begin{minipage}{0.46\linewidth}
 \begin{lstlisting}
@@
 \hfill
-\begin{minipage}{0.4\linewidth}
+\begin{minipage}{0.46\linewidth}
 \begin{lstlisting}
@@
 Third, previous work~\cite{bao2021abacus} reports some leakage sites leak little information, but \ctool{} reports the vulnerability is severe.
-Previous work \tool{} quantifies the amount of leaked information for one execution.
+Previous work \tool{}~\cite{bao2021abacus} quantifies the amount of leaked information for one execution.
 So it is possible that some leakage sites leak little information for one input but leak more information for a different input.

### 2021-06-14 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 \subsection*{Code Coverage} \detect{} analyzes one native x86 execution trace each time.
-The design, which is very precise in terms of true leakages compared to many static source code methods~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, but shares common limitations of dynamic approaches.
+The design is very precise in terms of true leakages compared to many static source code methods~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, but shares common limitations of dynamic approaches.
 \detect{} may only cover part of the code.
@@
 
-\subsection*{Design Choices} At the early stage of the project, we use SMT solvers to get the solutions of constraints.
-However, we find for some ciphers (RSA), \detect{} timed out after several days.
+\subsection*{Design Choices} At the early stage of the project, we used SMT solvers to get the solutions of constraints.
+However, we found for some ciphers (RSA), \detect{} timed out after several days.
 The profiling result showed that the tool spent most its time in Z3.
@@
 \subsection*{Cache Model} We use a simple cache model in this work.
-Recent works such as CacheAudit and CaSym~\cite{Brotzman19Casym,182946} use a Least Recently Used (LRU) cache.
+Recent works such as CacheAudit~\cite{182946} and CaSym~\cite{Brotzman19Casym} use a Least Recently Used (LRU) cache.
 First, there is no fundamental difficulties that prevent us from adopting a more realistic cache models.
@@
 While recent work found many side-channel vulnerabilities,
-we note that many of them are been patched by developers.
+we note that many of them are not patched by developers.
 Side-channels are ubiquitous in software, and it is difficult to fix all of them.
@@
 
-We use the amount of leaked information to represent the sensitivity level of
+We use the amount of leaked information to represent the severity level of
 each side-channel vulnerability. Although imperfect, \tool{} produces a reasonable
@@
 formula and the conjunction of the formulas to describe its total effect.
-Some leakage sites (e.g., square and multiply)
+Some leakage sites (e.g., square and multiply in RSA)
 can leak one particular bit of the original key, but some leakage sites leak one bit
@@
 \tool{} reaches full precision if the number of estimated leaked bits
-equals to Definition~\ref{chapter4:def}.
+equals to Definition~\ref{chapter4:def} in Chapter~\ref{chapter4}.
 \tool{} may lose precision from the
@@
 the amount of leakage for some leakage sites in a reasonable time,
-which means the number of $K^o$ is very small. According to Definition~\ref{chapter4:def}, it means the leakage is very severe. 
+which means the number of $K^o$ is very small. According to Definition~\ref{chapter4:def} in Chapter~\ref{chapter4}, it means the leakage is very severe. 
 \section{Precise Analysis on Multiple-trace Attacks}
@@
 affected by the input, which is useful because we cannot
-assume the input secrets of the software in practice. In the chapter, we
+assume the input secrets of the software in practice. In Chapter~\ref{chapter5}, we
 use the sampling result to approximate the true value of the
@@
 \ctool{} requires the random input variables to be independent and identically distributed (i.i.d.).
-That's why I apply a black box fuzzing instead of a coverage-guided fuzzing.
+That's why we apply a black box fuzzing instead of a coverage-guided fuzzing.
 As long as each time we get a random input from the whole input space (Population) that is independent of the previous input, the input variables should satisfy the i.i.d.
@@
 The situation is a little different for machine learning libraries.
-In the dissertation, we evaluated \ctool{} on a deep learning model.
+In this dissertation, we evaluated \ctool{} on a deep learning model.
 Each time, we randomly select an item from a dataset (Sample).
@@
 The good news is that the most well-known data sets in
-machine learning are i.i.d. i.i.d. is the foundation of many machine learning
-techniques (e.g., cross-validation, SVM, back-propagation). The assumption of i.i.d. 
-simplify many methods by assuming the data won't change over the time. 
+machine learning are independent and identically distributed. The assumption of i.i.d. is required by many machine learning
+techniques (e.g., cross-validation, SVM, back-propagation). The i.i.d. assumption
+simplifies many methods by assuming the data will not change over the time. 
 In my dissertation, we used MINIST, a well-known handwriting digit dataset. 
@@
 It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control flow under various inputs.
-For other libraries such as graphic rendering, machine learning, \ctool{} is very likely to miss some side-channel vulnerabilities.
-However, \ctool{} is not designed to find every side-channel vulnerabilities.
-The goal of \ctool{} is to pick up really serious side-channel vulnerabilities from the numerous vulnerabilities.
+For other libraries such as graphic rendering and machine learning, \ctool{} is very likely to miss some side-channel vulnerabilities.
+However, \ctool{} is not designed to find every side-channel vulnerability.
+The goal of \ctool{} is to identify severe side-channel vulnerabilities from many less severe vulnerabilities.
 So we do not think it is the main limitation of \ctool{}.

### 2021-06-14 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
   \centering
-  \includegraphics[width=.5\columnwidth]{./figures/chapter3/architecture.pdf}
+  \includegraphics[width=.65\columnwidth]{./figures/chapter3/architecture.pdf}
   \caption{Computer memory hierarchy.
@@
   \begin{minipage}{0.45\linewidth}
-    \begin{lstlisting}[xleftmargin=.15\textwidth, xrightmargin=.0\textwidth, frame=none]
-int example1(uint8_t k, uint32_t m) { // m = 0
-  uint32_t b = (k & m) >> 7;
+    \begin{lstlisting}[xleftmargin=.05\textwidth, xrightmargin=.0\textwidth, frame=none]
+int example1(uint8_t k, uint32_t m) { 
+  uint32_t b = (k & m) >> 7; // m = 0
   if (b) {
@@
   \begin{minipage}{0.45\linewidth}
-    \begin{lstlisting}[xleftmargin=.15\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
+    \begin{lstlisting}[xleftmargin=.05\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
 push  ebp
@@
   \begin{minipage}{0.45\linewidth}
-    \begin{lstlisting}[xleftmargin=.15\textwidth, xrightmargin=.0\textwidth, frame=none]
+    \begin{lstlisting}[xleftmargin=.05\textwidth, xrightmargin=.0\textwidth, frame=none]
 int example2(uint16_t k) {
@@
   \begin{minipage}{0.45\linewidth}
-    \begin{lstlisting}[xleftmargin=.15\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
+    \begin{lstlisting}[xleftmargin=.05\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
 xor   eax, eax
@@
 data flow from secrets to branch conditions and load addresses.
-Monocypher should be safe under our threat models.
+Monocypher should be side-channel resistant under our threat models.
 We analyze these ciphers with \detect{}, and it reports no leaks.

### 2021-06-14 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \centering
-\begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
+\begin{lstlisting}[xleftmargin=.1\textwidth,xrightmargin=.01\textwidth]
 while (!BN_is_bit_set(B, shift)) { /* note that 0 < B */

### 2021-06-15 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
     \centering
-    \caption{Due to the page limit, we only show some representations of the vast side-channel attacks: the shared resources with attackers, the granularity of the attacker can observe, is there any published attacks on non-cryptography libraries, and if the type of attack has been used to exploit multiple leakage sites.}
+    \caption{Here are some representations of the vast side-channel attacks: the shared resources, the granularity of the attacker can observe, is there any published attacks on non-cryptography libraries, and if the type of attack has been used to exploit multiple leakage sites.}
     \label{table:side_channel_attack}
@@
 Table~\ref{table:side_channel_attack} shows some representations of recent side-channel attacks.
-For a detailed overview of recent side-channel attacks, we refer to the following survey paper~\cite{ge2018survey}.
+For a detailed overview of recent side-channel attacks, we refer to the survey paper by Ge et al.~\cite{ge2018survey}.
 We classified these side-channel attacks into two categories: cache-level channels and page-level channels.
@@
 If the victim enclave program accesses the memory in the  page, then the OS can observe the page faults and know which page is accessed.
-While the granularity of the controlled-channel attacks is more coarse-grained compared with cache channel attacks, controlled-channel attacks allow the attacker to have a noise-free observation.
+While the granularity of controlled-channel attacks is more coarse-grained compared with cache channel attacks, controlled-channel attacks allow the attacker to have a noise-free observation.
 Other examples such as TLB side-channel attacks and DDRAM attacks share the same page-level granularity.
 
-Based on the above discussion, we consider three types of granularities in the dissertation: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs).
+Based on the above discussion, we consider three types of granularities in the dissertation: byte (1 byte), cache line size (64 bytes), page size (4 KBs).
 To the best of our knowledge, these three types of granularities can cover most of the side-channel attacks in the literature.
@@
 In timing-based attacks, an adversary can measure and compare the execution time of victim programs.
-It could be the overall execution time or the execution time of some interesting points (e.g., a function).
-The execution time is correlated to some events (e.g., cache hits and misses, page faults, the number of instructions).
-Timing-based attacks are perilous because these attacks are able to be carried out remotely over the networks remotely~\cite{brumley2005remote}.
+It could be the overall execution time or the execution time of some interesting components (e.g., a function).
+The execution time is correlated to some events (e.g., cache hits and misses, page faults, the number of instructions, optimizations).
+Timing-based attacks are perilous because these attacks are able to be carried out remotely over the networks~\cite{brumley2005remote}.
 Examples of these attacks include remote timing attacks~\cite{brumley2005remote}, Bernstein's attack on AES~\cite{bernstein2005cache}, and Kocher’s original attack~\cite{kocher1996timing} from CRYPTO 96.
@@
 \subsection{Target Applications}
-There is a vast number of studies\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last} on side-channel attacks.
+There is a large number of studies\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last} on side-channel attacks.
 Most early works targeted retrieving encryption keys from cryptography libraries.
@@
     \centering
-    \caption{This table shows some common vulnerable points in cryptography implementations and corresponding software mitigation methods.}
+    \caption{Some common vulnerable components in cryptography implementations and corresponding software mitigation methods.}
     \label{chapter2:table:crypto}
@@
 The first side-channel attack on cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996.
-It exploits the simple modular exponentiation algorithm function in many algorithms (Diffie-Hellman, RSA) implementations.
+It exploits the simple modular exponentiation algorithm function in many cryptography (Diffie-Hellman, RSA) implementations.
 The function does not run in a fixed time.
@@
 Note that cryptography libraries usually have several implementations for some ciphers.
-For example, AES can have more than five different implementations in OpenSSL.
+For example, AES has more than five different implementations in OpenSSL.
 Depending on the build configuration and the return value of \textsf{CPUID}, the code may execute any implementation of them.
@@
 In addition to the reference implementation, these libraries also have side-channel mitigated versions.
-However, recent studies also show these versions (e.g., AES-NI) also have side-channel vulnerabilities caused by compiler optimizations and human mistakes~\cite{217537}.
+However, recent studies show these versions (e.g., AES-NI) also have side-channel vulnerabilities caused by compiler optimizations and human mistakes~\cite{217537}.
 The situation is even worse for asymmetric ciphers (e.g., Diffie-Hellman, RSA, ECDSA).
@@
 Wei et al.~\cite{wei2018know} perform the side-channel attacks on an FPG-based convolution neural network by using the power consumption to recover inputs to the networks.
-For an image classification task trained by the MNIST dataset, their attacks can achieve up 89\% accuracy.
+For an image classification task trained by the MNIST dataset, their attacks can achieve up to 89\% accuracy.
 CSI NN~\cite{batina2019csi} reverse engineered the multi-layer perception and convolution neural network based on the electromagnetic signals (EMs).
@@
 Daimeng et al.~\cite{wang2019unveiling} present a cache attack on graphic libraries.
-Their approaches uses a machine learning approach to pick cache lines that can be exploitable to leak the most information.
+Their approaches uses a machine learning approach to pick cache lines that can be exploited to leak the most information.
 \subsubsection*{Others}
@@
 By exploiting the differences of memory accesses when the program renders different characters, an attacker can recover parts of the original sensitive information.
-Other side-channel attacks target the OS's kernel.
+Other side-channel attacks target operating system kernels.
 One example is using the side-channel attack to break the kernel address space randomization (KASLR).
@@
 \subsubsection*{Software Vulnerability Identification}
-For many software countermeasures, the first step is identifying side-channel leakages in software manually. It can be done manually or by some program analysis tools.
+For many software countermeasures, the first step to identify side-channel leakages in software manually. It can be done manually or by some program analysis tools.
 There are several existing works on side-channel leakage detections.
-According to Table~\ref{table:side_channel_detection_tool}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction.
+As shown in Table~\ref{table:side_channel_detection_tool}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction.
 
-\textbf{Trace comparison.} If a program has two different execution traces under two different sensitive inputs, then attackers can distinguish the sensitive input by observing the execution trace.
+\textbf{Trace comparison.} If a program has two different execution traces under two different sensitive inputs, then attackers can distinguish the sensitive input by observing the execution traces.
 Therefore, we can conclude the program is vulnerable to side-channel attacks.
@@
 On the negative side, comparing the trace can find the leakage, but it cannot find the complex relationship between the leakage site and the original secret input.
-For example, if two leakage sites leak the same information, these approaches cannot find out the two leakage sites are the same.
+For example, if two leakage sites leak the same information, these approaches cannot find out the two leakages are the same.
 
@@
 This type of defense randomizes the behaviors of hardware resources to make it harder for attackers to infer secrets based on side-channel information.
-For example, Random Permutation Cache (PRcache)~\cite{wang2007new} uses a dynamically randomized memory to cache mapping table for each different process.
+For example, Random Permutation Cache ~\cite{wang2007new} uses a dynamically randomized memory to cache mapping table for each different process.
 Vattikonda et al.~\cite{vattikonda2011eliminating} add noises to the result of the system timer to mitigate timing-based channels.
@@
 Their approach only scales to small programs, which limits its usage in
-real-world applications. On the contrary, \tool{} assesses the sensitive level
+real-world applications. On the contrary, \tool{}~\cite{bao2021abacus} assesses the sensitive level
 of side channels with different granularities. It can also analyze side channels in real-world cryptographic libraries.
@@
 the number of solutions. Intuitively, such a model counter should traverse the whole
-search space to find all the satisfying solutions. Consequently, the exact model counter is very slow. These model counters have difficulty scaling up to real-world programs.
+search space to find all the satisfying solutions. Consequently, the exact model counter is very slow. These model counters have difficulty in scaling up to real-world programs.
 On the other hand, the approximate model counter is much faster compared with the exact model counter.
@@
 \section{Trace-based Binary Analysis}
-Trace-based binary analysis can be seen as a type of dynamic analysis. It analyzes one concrete program path one time rather than trying to cover
+Since our work relies on binary analysis, we briefly mention the related work here.
+Trace-based binary analysis can be seen as a type of dynamic analysis. It analyzes one concrete program execution path each time rather than trying to cover
 as many paths as possible. Compared to static analysis, trace-based analysis
 is usually more precise as it can incorporate runtime information. It usually has
-two steps. The first step is collecting trace information. Existing
-approaches usually often rely on binary instrumentation frameworks or emulators (e.g., Intel Pin~\cite{luk2005pin},
-Valgrind~\cite{nethercote2007valgrind}, and QEMU). The second step is analyzing the trace using techniques, such
-as symbolic execution, taint analysis. Depending on when the analysis is launched,
-there are two kinds of trace-based analysis, online analysis, and offline analysis.
+two steps. The first step is to collect trace information. Existing
+approaches often rely on binary instrumentation frameworks or emulators (e.g., Intel Pin~\cite{luk2005pin},
+Valgrind~\cite{nethercote2007valgrind}, and QEMU). The second step to analyze the trace using techniques, such
+as symbolic execution and taint analysis. Depending on when the analysis is launched,
+there are two kinds of trace-based analysis, online analysis and offline analysis.
 As the name suggests, online analysis is performed during the program execution.
@@
 It uses the tracecap plugin to collect execution traces and convert the trace into Vine IR.
-Binary Analysis Platform (BAP)
+Binary Analysis Platform (BAP)~\cite{10.1007/978-3-642-22110-1_37}
 is another binary analysis platform. Similar to BitBlaze, it uses a Pintrace tool to

### 2021-06-15 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \section{Problem}
-Side channels are ubiquitous in modern computer systems as sensitive information can leak through many mechanisms such as power, electromagnetic radiation, and even sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}.
+Side channels are ubiquitous in modern computer systems as sensitive information can leak through many mechanisms such as power consumption, execution time, electromagnetic radiation, and even sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}.
 Among them, software side-channel attacks, such as cache attacks, memory page attacks, and controlled-channel attacks, are especially problematic as they do not require physical proximity~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}.
@@
 The evaluation results show that our tool can identify previous side-channel leakages as well as find new leakages.
-Compared with recent tools~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741}, our tool is 3-100x faster while finding all the leakages when we evaluate on the same benchmarks.
+Compared with recent tools~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741}, our tool is 3--100x faster while finding all the leakages when we evaluate on the same benchmarks.
 In addition, our tool finds new side-channel vulnerabilities missed by the previous work.
@@
 In reality, attackers may face many possible obstacles, such as the noisy observations of the memory or cache.
-However, for this project, we assume the attacker has noise-free observations as in previous work~\cite{203878,182946,Brotzman19Casym}.
+However, in this research, we assume the attacker has noise-free observations as in previous work~\cite{203878,182946,Brotzman19Casym}.
 The threat model captures most address-based side-channel attacks and apply to the three attack models: 1) time-based attacks, 2) access-based attacks, 3) trace-based attacks.
@@
 
-\section{Limitations of Current Side-channel Leakage Detection Tools}
+\section{Limitations of Previous Side-channel Leakage Detection Tools}
 In this section, we introduce two limitations of current side-channel leakage detection tools.
@@
 
-Figure~\ref{fig:chapter3:da} shows an example of the secret-dependent data access.
+Figure~\ref{fig:chapter3:da} shows an example of secret-dependent data access.
 \textsf{T} is an array with 128 elements.
@@
 Therefore, such a code may still be vulnerable to side-channel vulnerabilities.
-However, existing tools (e.g., CacheD) use a concrete base address.
+However, existing tools (e.g., CacheD~\cite{203878}) use a concrete base address.
 Under the circumstance, these tools may miss such vulnerabilities.
@@
 The second limitation of current side-channel detection tools is the performance bottleneck, especially for tools based on symbolic analysis.
-For example, CaSym can only analyze small programs.
+For example, CaSym~\cite{Brotzman19Casym} can only analyze small programs.
 CacheD performs better than CaSym.
@@
 But the decision problems that an SMT solver handles are typically at least NP-hard.
-On the other hand, we can use some methods to avoid the solver and find side-channel leakages more efficiently.
+On the other hand, we can use some methods to avoid the expensive SMT solving and find side-channel leakages more efficiently.
 
@@
 
-In the section, we give necessary definitions and notations for dealing with
+In this section, we give necessary definitions and notations for dealing with
 programs and side-channels.
@@
 ($K$) can lead to different branch conditions.
-We define a branch to be secret-dependent if:
-$$\exists k_{i1}, k_{i2} \in K, m \in M, \,f_i(\beta, k_{i1}, m) \neq f_i(\beta, k_{i2}, m) \land PC$$
+We define a branch to be secret-dependent if
+$$\exists k_{i1}, k_{i2} \in K, m \in M, \,f_i(\beta, k_{i1}, m) \neq f_i(\beta, k_{i2}, m) \land PC,$$
 
-$PC$ represents the path condition. An adversary can observe which branch the code executes if the branch condition
+where $PC$ represents the path condition. An adversary can observe which branch the code executes if the branch condition
 equals $t_b$. We use the constraint $c_i : f_i(\beta, k, m) = t_b$ to model
@@
 
-A data access is secret-dependent if:
+A data access is secret-dependent if
 
-$$\exists k_{i1}, k_{i2} \in K, m \in M,\,f_i(\beta, k_{i1}, m) >> L \neq f_i(\beta, k_{i2}, m) >> L \land PC$$
+$$\exists k_{i1}, k_{i2} \in K, m \in M,\,f_i(\beta, k_{i1}, m) >> L \neq f_i(\beta, k_{i2}, m) >> L \land PC.$$
 
@@
   f_i(\beta, k, m) >> L = t_b >> L$ to model the observation on secret-dependent
-data accesses. Let's take a look the examples in Figure~\ref{fig:chapter3:da}(a).
+data accesses. Let us take a look at the examples in Figure~\ref{fig:chapter3:da}(a).
 Suppose the base address of the array \textsf{T} is 10.
@@
 The formula that represents the memory access at line 6 is $10 + m + (k \mod 128)$.
-Therefore, we have the formula: $(10 + m + (k_1 \mod 128)) >> 6  \neq (10 + m + (k_2 \mod 128)) >> 6$.
+Therefore, we have the formula $(10 + m + (k_1 \mod 128)) >> 6  \neq (10 + m + (k_2 \mod 128)) >> 6$.
 Here is one possible solution: $m = 0, k_1 = 0, k_2 = 127$.
@@
 
-\textbf{Our Solution:}
+\textbf{Our Solution}
 We abandoned IR and expended the effort to implement
@@
 
-\textbf{Our Solution:}
+\textbf{Our Solution}
 Instead of feeding the formula $f_a(k_1) \neq f_a(k_2)$ into a SMT solver, we
@@
 \subsection{Trace Logging}
-The trace information can be logged via some emulators (e.g., QEMU) or dynamic binary instrumentation tools (DBI).
+The trace information can be logged via some emulators (e.g., QEMU~\cite{bellard2005qemu}) or dynamic binary instrumentation tools (DBI).
 In this work, we run a program with the concrete input under the DBI to record execution traces.
@@
 At the beginning of the symbolic execution, the tool creates new symbols for each byte in the raw buffer.
-For other data in the register or memory at the beginning, we use actual values from the runtime information.
+For other data in the register or memory at the beginning, we use actual values from the runtime execution information.
 During the symbolic execution for each instruction, the tool updates every variable in the memory and registers with a math formula.
@@
 However, due to the complexity of x86, mistakes inevitable. Therefore, we verify the correctness of the SE engine during the execution.
-The tool will collect the runtime information (register values, memory values) and compare them with the formula generated from the symbolic execution.
+The tool will collect the runtime execution information (register values, memory values) and compare them with the formula generated from the symbolic execution.
 Whenever the tool finishes the symbolic execution of each instruction, the tool will compare the formula for each symbol and its actual value.
@@
 There are two kinds of control-transfer instructions: the unconditional control-transfer instructions and the conditional transfer instructions.
-The unconditional instructions, such as CALL, JUMP, RET transfer control from one code segment location to another.
+The unconditional instructions, such as CALL, JUMP, and RET, transfer control flows from one code segment location to another.
 Since the transfer is independent of the input sensitive information, an attacker is not able to infer any sensitive information from the control-flow.
@@
 
-For examples, considering the below x86 code snippet,
+For examples, considering the following x86 code snippet,
 
@@
 \subsubsection{Secret-dependent Data Accesses}
-Like input-dependent control-flow transfers, an adversary can also infer sensitive information from the data access pattern as well.
+Like input-dependent control-flow transfers, an adversary can also infer sensitive information from the data access patterns as well.
 We try to find this kind of leakages by checking every memory operand of the instruction.
@@
 Because we also have the concrete value of the memory address $\mathtt{Addr1}$.
-Inspired by the work from~\cite{203878}, the formula can be written as:
+Inspired by the work CacheD~\cite{203878}, the formula can be written as
 
-$$F(\vec{K}) >> L = \mathtt{Addr1} >> L$$
+$$F(\vec{K}) >> L = \mathtt{Addr1} >> L,$$
 
-$L$ represents the minimum memory address granularity that an attacker can observe.
+where $L$ represents the minimum memory address granularity that an attacker can observe.
 For example, Flush and Reload can distinguish between different cache lines, which means the value of L is 6 for 64 byte cache line.
@@
 programs that use the crypto libraries. For symmetric encryption, the length
-of the keys are 256 bit. For RSA, the length of the keys is 1024. For ECDSA, the
+of keys is 256 bits. For RSA, the length of the keys is 1024 bits. For ECDSA, the
 length of the key is 384 bit. The input public message is ``Hello World!''.
@@
 Table~\ref{table:over_result} summarizes the results.
-\detect{} finds 913 leaks in the crypto libraries.
-Among these 913 leaks, 241 are due to secret-dependent
+\detect{} finds 913 leaks in the crypto libraries,
+among which, 241 are due to secret-dependent
 control-flow transfers and 672 are due to secret-dependent data accesses.
@@
 Most of the side-channel leakages in symmetric implementations are from the lookup tables.
-The new implementation of OpenSSL has adopted several methods (e.g., one single S-box instead of four lookup tables, smaller lookup tables) to mitigate the problem.
+The new implementation of OpenSSL has adopted some methods (e.g., one single S-box instead of four lookup tables, smaller lookup tables) to mitigate the problem.
 
@@
   \label{eval:cacheD}
-
+    \resizebox{.9\columnwidth}{!}{%
     \begin{tabular}{@{}l|r@{~~}r@{~~}r|r@{~~}r@{~}r@{}}
@@
     \end{tabular}
-
+}
 \end{table*}
@@
 DATA reports 278 control-flow and 460 memory-access leaks for the RSA implementation in OpenSSL 1.1.0f. Among these leakages, they find one new vulnerability in RSA after some manual analysis.
-\detect{} finds the vulnerability.  For each leakage site, \detect{} can provide
+\detect{} also finds a new vulnerability.  For each leakage site, \detect{} can provide
 concrete examples to trigger the issue.
@@
 However, as the branch is inside a loop and a bit shift function causes the branch leak different bits from the sensitive buffer.
+The function can leak the last digit from big number \textbf{X}.
+The leakage is severe due to the
+function \textsf{BN\_rshift1}. Each time, function \textsf{BN\_rshift1}
+shifts \textbf{X} right by one and places the result in \textbf{X}. Therefore,
+an attacker can infer multiple bits of \textbf{X} by observing the branch at line 3.
 
@@
     \caption{Previously unknown sensitive secret-dependent branch leaks from function 
-             \textsf{int\_bn\_mod\_inverse} in OpenSSL 1.1.1. The function can leak the last digit from big number \textbf{X}. However, the leak is more severe because of the 
-             function \textsf{BN\_rshift1}. Each time, function \textsf{BN\_rshift1}
-             shifts \textbf{X} right by one and places the result in \textbf{X}. Therefore,
-             an attacker can infer multiple bits of \textbf{X} by observing the branch at line 3.}
+             \textsf{int\_bn\_mod\_inverse} in OpenSSL 1.1.1. }
     \label{chapter3:fig:unknown_leakage}

### 2021-06-15 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 In Chapter~\ref{chapter3}, we present a method to identify address-based side-channel leakage sites in cryptography libraries ~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.
-However, many reported leakage sites are not patched by developers.
+However, many reported leakage sites are not patched by the developers.
 Recent work on side-channel vulnerability identification~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} also faced the same situation.
 For example, DATA~\cite{217537} reports 2,248 potential leakage sites for the RSA implementation in OpenSSL 1.1.0f\@.
-Further analysis shows 1,510 leaks can be dismissed.
-But that leaves 460 data-access leaks and 278 control-flow leaks.
-Many of these vulnerabilities have not been fixed by developers for a variety of reasons.
+Further analysis shows 1,510 leaks can be dismissed, but that still leaves 460 data-access leaks and 278 control-flow leaks.
+Many of these vulnerabilities have not been fixed by the developers for a variety of reasons.
 
 First, some vulnerable implementations perform better. For example,
-RSA implementations usually adopt the CRT optimization, which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}. Second, fixing vulnerabilities can introduce new
+RSA implementations usually adopt the Chinese Remainder Theorem (CRT) optimization, which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}.
+Second, fixing vulnerabilities can introduce new
 weaknesses.
@@
 To overcome these limitations, we propose a novel method to quantify information
-leakage precisely. We quantify the number of bits that can leak during a real
+leakage precisely. We quantify the number of bits that can be leaked during a real
 execution and define the amount of leaked information as the cardinality of
 possible secrets based on an attacker's observation. Before an attack, an adversary has a large but finite input space.
-Whenever the adversary observes a leakage site, they can eliminate some impossible
+Whenever the adversary observes a leakage site, he can eliminate some impossible
 inputs and reduce the input space's size.

### 2021-06-15 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 
-where $PC$ represents the path condition. An adversary can observe which branch the code executes if the branch condition
+\noindent where $PC$ represents the path condition. An adversary can observe which branch the code executes if the branch condition
 equals $t_b$. We use the constraint $c_i : f_i(\beta, k, m) = t_b$ to model
@@
 
-For examples, considering the following x86 code snippet,
+For examples, considering the following x86 code snippet.
 
-\begin{lstlisting}[xleftmargin=.3\textwidth, xrightmargin=.2\textwidth, frame=none][ht]
+\begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth, frame=none][ht]
 ...
@@
 
-where $L$ represents the minimum memory address granularity that an attacker can observe.
+\noindent where $L$ represents the minimum memory address granularity that an attacker can observe.
 For example, Flush and Reload can distinguish between different cache lines, which means the value of L is 6 for 64 byte cache line.

### 2021-06-15 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 
-The threat model is similar to our previous work. That is, we assume
+The threat model in this chapter is similar to the threat model in our previous work from Chapter~\ref{chapter3}.
+Prior work~\cite{203878,182946,Brotzman19Casym} also shares the same threat model.
+That is, we assume
 an attacker can share some hardware resource with the victim. The attacker has
@@
 an attacker has noise-free observations. The attacker has the access to the victim's
-binary executable. The threat mode is similar to
-the previous work~\cite{203878,182946,Brotzman19Casym} and can catch most of
-the address-based side-channel attacks in the literature.
+binary executable.  We believe that the majority of address-based side-channel attacks in the literature applies to the thread model.
 
@@
 \begin{displaymath}
-    H(K) = - \sum_{k {\in} K}p(k)\log_2(p(k))
+    H(K) = - \sum_{k {\in} K}p(k)\log_2(p(k)).
 \end{displaymath}
@@
 \end{lstlisting}
-    \vspace*{-1pt}
     \caption{Side-channel leakage}
@@
     \centering%\small\footnotesize
-    \caption{The distribution of observation}\label{shtable}
+    \caption{The distribution of observations}\label{shtable}
     %    \resizebox{\columnwidth}{!}{
@@
 
-\textbf{Min Entropy.}
+\subsubsection*{Min Entropy}
 As $p_{A\mathit{max}} = 0.9998$ and $p_{B\mathit{max}} = 0.5$,
@@
 
-\textbf{Max Entropy.}
+\subsubsection*{Max Entropy}
 Depending on the value of key, the code can run two different branches for each leakage site.
@@
 
-\textbf{Shannon Entropy.}
+\subsubsection*{Shannon Entropy}
 Based on Shannon entropy, the respective amount of information in A and B equals to
@@
                                               & = 0.000\ \mathrm{bits}         \\
-            \mathit{Shannon\text{-}entropy_B} & = -(0.5*\log_{2}0.5            \\
-                                              & \qquad+ 0.5*\log_{2}0.5)       \\
+            \mathit{Shannon\text{-}entropy_B} & = -(0.5*\log_{2}0.5 + 0.5*\log_{2}0.5)       \\
                                               & = 1.000\ \mathrm{bits}
@@
 \end{lstlisting}
-    \vspace*{-10pt}
     \caption{A dummy password checker}
@@
 However, prior static approaches cannot precisely capture the amount of leakage. According to the definition of Shannon entropy, the leakage will be
-$\frac{1}{2^{64}}*\log_{2}\frac{1}{2^{64}} + \frac{2^{64}-1}{2^{64}}
-    *\log_{2}\frac{2^{64}-1}{2^{64}} \approx 0$ bits. Max-entropy is defined from the
+$$\frac{1}{2^{64}}*\log_{2}\frac{1}{2^{64}} + \frac{2^{64}-1}{2^{64}}
+    *\log_{2}\frac{2^{64}-1}{2^{64}} \approx 0\, \mathrm{bits}.$$ Max-entropy is defined from the
 number of possible observations. Because the program has two
-branches, tools based on max-entropy will report the code has a $\log_2{2} = 1$
+branches, tools based on max-entropy will report the code has a $\log_2{2} = 1.0$
 bit leakage.
@@
     \includegraphics[width=.65\columnwidth]{./figures/chapter4/RA.pdf}
-    \caption{The gap between the real attack and previous models}\label{fig:gap}
+    \caption{The gap between real attacks and previous models}\label{fig:gap}
 \end{figure}
@@
 
-We assume a program ($\beta$) has $K$ as its sensitive input. $K$ should be
+We assume a program ($\beta$) has $K$ as its sensitive input. The input $K$ should be
 a finite set of keys. The program also takes known messages $M$ as its input.
 During an AES encryption, for example,
-$\beta$ is the encryption function. $K$ is the set of all possible AES keys,
+$\beta$ is the encryption function. Here $K$ is the set of all possible AES keys,
 and $M$ represents the set consisting of all plaintext messages to be encrypted. In a real execution, an adversary may have
@@
 \begin{displaymath}
-    \beta(K, M) \rightarrow O
+    \beta(K, M) \rightarrow O.
 \end{displaymath}
@@
 
+\
 \emph{How much uncertainty of $K$ is reduced if an attacker knows $\beta$, $m$, and $o$?}
+\
 
@@
 dependence between original sensitive keys ($K$) and attackers' observations ($O$),
-which is defined as:
+which is defined as
 
@@
 
-where $p(k_i, o_i)$ is the joint discrete distribution of $K$ and $O$.
-Alternatively, the mutual information can also be equivalently expressed as:
+\noindent where $p(k_i, o_i)$ is the joint discrete distribution of $K$ and $O$.
+Alternatively, the mutual information can also be equivalently expressed as
 
@@
 
-$H(K|O)$ is the entropy of $K$ with the condition $O$. It quantifies the
+\noindent where $H(K|O)$ is the entropy of $K$ with the condition $O$. It quantifies the
 uncertainty of $K$ given the value of $O$. In other word, the conditional
@@
 
-In this project, we hope to give a very precise definition of information
+In this research, we hope to give a very precise definition of information
 leakages. Suppose an attacker runs the target program with one
@@
 
-Next we compare the Eq.~(\ref{eq:2}) with the above slogan, we find $H(K)$
-is the $\mathit{Initial\ uncertainty}$ and $H(K|O)$ is $\mathit{Remaining\
+Next we compare the Eq.~(\ref{eq:2}) with the above slogan, we find that $H(K)$
+is the $\mathit{Initial\ uncertainty}$ and $H(K|O)$ is the $\mathit{Remaining\
         uncertainty}$. During a real attack, the observation ($o$) is known.  Thus we
@@
 \begin{displaymath}
-    Leakage = I(K;o) = H(K) - H(K|o)
+    Leakage = I(K;o) = H(K) - H(K|o).
 \end{displaymath}
@@
     \frac{1}{|K|}$. So we have
-$$H(K) = \sum_{k {\in} K}\frac{1}{|K|}\log_2{|K|} = \log_2{|K|}$$
+$$H(K) = \sum_{k {\in} K}\frac{1}{|K|}\log_2{|K|} = \log_2{|K|}.$$
 For any $k' \in K \setminus K^o$, $p(k'|o) = 0$. We get
@@
            & = \sum_{k {\in} K^o}\frac{1}{|K^o|}\log_2{|K^o|}                   \\
-           & = \log_2{|K^o|}
+           & = \log_2{|K^o|}.
 \end{align*}
@@
     We denote it as
-    $$\beta(K^o, m) \rightarrow	o$$
+    $$\beta(K^o, m) \rightarrow	o.$$
 
     The amount of leaked information $L_{\beta(k)\rightarrow o}$ based on the observation ($o$) is
-    $$L_{\beta(k)\rightarrow o} = \log_2{|K|} - \log_2{|K^o|}$$
+    $$L_{\beta(k)\rightarrow o} = \log_2{|K|} - \log_2{|K^o|}.$$
 \end{mydef}
@@
 However, the program has a side-channel leakage site. After the program finishes execution, the
-attacker get some leaked information and only need to find the key by performing
+attacker gets some leaked information and only needs to find the key by performing
 exhaustive search over $2^{120}$ possible keys. Then we can say that 8 bits of the information
@@
     \label{shtable2}
-    \vspace*{-9pt}
     %    \resizebox{\columnwidth}{!}{
@@
 Intuitively, we can use symbolic execution to capture math formulas and model counting to obtain the number of satisfying input keys ($K^o$).
-However, preliminary experiments showed that this approach was far too expensive to use with real-world applications.
+However, some preliminary experiments showed that this approach was far too expensive to use with real-world applications.
 In this section, we discuss the bottlenecks in this approach and propose a practical solution.
@@
     \end{tablenotes}
-    \vspace*{-20pt}
 
@@
 \end{lstlisting}
-    \vspace*{-6pt}
     \caption{Macro \textsf{sqr\_add\_c2} in OpenSSL 0.9.7}
     \label{fig:old_sqr2}
-    \vspace*{-8pt}
 \end{figure}

### 2021-06-15 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 there are various propositional model counters (e.g., \#SAT), they are not
-sufficient scalable for production cryptosystem analysis.
-there is no open source modulo theories counter (\#SMT) available.
-
-One straightforward method approximating the number of solutions is based on Monte Carlo
+sufficiently scalable for production cryptosystem analysis.
+Besides, there is no open source modulo theories counter (\#SMT) available.
+
+One straightforward method to approximate the number of solutions is based on Monte Carlo
 sampling. However, the number of satisfying values could be exponentially small.
@@
 these constraints into several small formulas and sample them independently.
-We will introduce the method in the following subsection.
+We will introduce the method in the following subsection. In this section, we present the algorithm to calculate the information leakage based on Definition~\ref{chapter4:def}.
 
@@
 \renewcommand{\addr}[1]{{\xi}_{#1}}
-
-In this section, we present the algorithm to calculate the information leakage based on Definition~\ref{chapter4:def}.
 
@@
 
-However, the above sampling method fails in practice due to the following two problems:
+However, the above sampling method fails in practice due to the following two problems.
 
@@
     \item The number of satisfying assignments could be exponentially small.
-          According to Chernoff bound, we need exponentially many samples to
+          According to the Chernoff bound~\cite{hoeffding1994probability}, we need exponentially many samples to
           get a tight bound.
@@
 
-However, despite above two problems, we also observe two characteristics of the
+However, despite the above two problems, we also observe two characteristics of the
 problem:
@@
 
-For a constraint $c_{\addr{i}}$, we define function $\pi$, which maps the
+For a constraint $c_{\addr{i}}$, we define function $\pi$, which projects the
 constraint into a set of different input symbols. For example, $\pi(k1 + k2 >
@@
     $K_c$ is the input set that satisfies constraint $c$. We have the following
-    equation in regard to the size of $K_c$
+    equation with regard to the size of $K_c$
     $$|K_{c_t(\addr{1},\addr{2},\ldots,\addr{n})}| = |K_{g_{1}}|*|K_{g_{2}}|*\ldots*|K_{g_{n}}|$$
@@
 
-We apply the following
-algorithm~\ref{algo:max-inde} to get the Maximum Independent Partition of the
+We apply 
+Algorithm~\ref{algo:max-inde} to get the Maximum Independent Partition of the
 $c_t(\addr{1},\addr{2},\ldots,\addr{n})$.
@@
 \IncMargin{1em}
-\begin{algorithm}[th]\small
+\begin{algorithm}[th]\normalsize
     \DontPrintSemicolon
@@
 we only generate random input numbers for the other input variables in
-constraint $g_{i}$. With this simple yet effective trick, we reduce the number of input while still ensuring accuracy. The detailed of the algorithm is shown in Algorithm~\ref{chapter4:alg2}.
+constraint $g_{i}$. With this simple yet effective trick, we reduce the number of input while still ensuring accuracy. The details of the algorithm is shown in Algorithm~\ref{chapter4:alg2}.
 
 \IncMargin{1em}
-\begin{algorithm}\small
+\begin{algorithm}\normalsize
     \SetAlgoLined
@@
         $S_{g_i}$ $\leftarrow$ $\pi(g_i)$ \;
-        $v \leftarrow R(S_{g_i})$
+        $v \leftarrow R(S_{g_i})$ \;
         \If{$v$ satisfies $g_i$}
@@
 
-    $|K_{g_{i}}|$ $\leftarrow$ $n_s|K| / (n * r * range(k))$
+    $|K_{g_{i}}|$ $\leftarrow$ $n_s|K| / (n * r * \mathrm{range(k)})$
     \caption{Multiple Step Monte Carlo Sampling}\label{chapter4:alg2}
@@
 information is less than 1 bit under the Central Limit Theorem (CLT) and uncertainty
-propagation theorem.
+propagation theorem~\cite{walpole1993probability}.
 
@@
 theorem, the mean value should follow the normal distribution
-$ \frac{\bar{p}-E(p)}{\sigma\sqrt{n}} \rightarrow N(0,1) $. Here $E(p)$ is the
+$$ \frac{\bar{p}-E(p)}{\sigma\sqrt{n}} \rightarrow N(0,1). $$ Here $E(p)$ is the
 mean value of $p$, and $\sigma$ is the standard variance of $p$. If we use the
@@
 confidence that the error $\Delta p= \bar{p} - E(p)$ falls in the interval:
-$$ |\Delta p| \leq 1.96\sqrt{\frac{ \hat{p} (1- \hat{p} )}{n}}$$
+$$ |\Delta p| \leq 1.96\sqrt{\frac{ \hat{p} (1- \hat{p} )}{n}}.$$
 
@@
 information ($\Delta L$) to be less than 1 bit. So we get $\frac{\Delta
-        p}{p\ln2} \leq 1$. Therefore, as long as $ n \geq \frac{1.96^2(1-p)}{p(\ln2)^2}$, we have
-95\% confidence that the error of estimated leaked information is less than 1 bit.
+        p}{p\ln2} \leq 1$. Therefore, as long as $$ n \geq \frac{1.96^2(1-p)}{p(\ln2)^2},$$ 
+\noindent we have 95\% confidence that the error of estimated leaked information is less than 1 bit.
 During the simulation, if $n$ and $p$ satisfy this inequality, the Monte Carlo
@@
     \centering
-    \includegraphics[width=0.85\textwidth]{./figures/chapter4/workflow.pdf}
+    \includegraphics[width=0.95\textwidth]{./figures/chapter4/workflow.pdf}
     \caption{The workflow of \tool{}.}
@@
 
-\subsection{Instruction Level Symbolic Execution} We model attackers'
+\subsection{Instruction Level Symbolic Execution} We model an attacker's
 observations from side-channel vulnerabilities with logic formulas.
-Each formula captures the fine-grained information between input
+Each formula captures the fine-grained information between the input
 secrets and leakage sites. The engine only symbolically executes
@@
 
+\subsection{Implementation}
+
 \tool{} consists of 16,729 lines of code in C++17 and Python. It has three components: an Intel Pin tool that collects the execution trace, the
@@
 \begin{table}[ht]
-    \centering
+    \centering\normalsize
     %    \resizebox{.8\columnwidth}{!}{
@@
         Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF),
-        The number of instructions\,(\# Instructions), Symbolic Execution\,(SE) and Monte Carlo\,(MC) time.
+        the number of instructions\,(\# Instructions), Symbolic Execution\,(SE) and Monte Carlo\,(MC) time.
     }\label{chapter4:table:over_result}
@@
 \subsection{Overview}
-In this section, we evaluate \tool{} on a series of popular crypto libraries.
+In this section, we evaluate \tool{} on a set of popular crypto libraries.
 In particular, we are interested in following aspects:
@@
 
-Table~\ref{chapter4:table:over_result} shows the overview of evaluation results. 
+Table~\ref{chapter4:table:over_result} shows an overview of the evaluation results. 
 \tool{} also finds that most side-channel
-vulnerabilities leak very little information in practice, which confirms our
+vulnerabilities leak very little information, which confirms our
 initial assumption.  
@@
 With our tool, developers can
-distinguish non-critical ``vulnerabilities'' from severe ones.
+distinguish non-critical ``vulnerabilities'' from the severe ones.
 
@@
 
-We find that the DES implementations in both mbedTLS and OpenSSL have several severe information leakages in the key schedule function. We do not see any mitigation
+We find that the DES implementations in both mbedTLS and OpenSSL have several severe information leakages in the key-schedule function. We do not see any mitigation
 in the new version. We think it is not seen as worth the engineering efforts given the life cycles of DES\@.
@@
 \emph{mbedtls\_internal\_aes\_decrypt}. (Other leakage sites are in function
-\emph{mbedtls\_aes\_setkey\_enc}.) All leakages are caused by secret-dependent
+\emph{mbedtls\_aes\_setkey\_enc}.) All leakages are caused by the secret-dependent
 memory accesses. Shown in Figure~\ref{mbedtls_aes}, there are seven leakage
@@
  As shown in Figure~\ref{fig:rsa}, the result indicates that the newer
-versions of OpenSSL leak less information than earlier
+versions of OpenSSL leak less information than the earlier
 versions. After version 0.9.7g, OpenSSL adopts a fixed-window \textsf{mod\_exp\_mont}
@@
 secret-dependent control flow at line 8.
-The value of the function parameter \textbf{a} is derived from
+The value of the function parameter \texttt{a} is derived from
 the secret key. 
@@
 and the code can leak some information each time.
-\tool{} indicates the vulnerability is quite serious. 
+\tool{} indicates the vulnerability is quite severe. 
 It was patched in OpenSSL 1.1.1\@. In 
@@
 \textsf{sqr\_add\_c2} in OpenSSL 1.1.1\@. We note
-that line 4 and 9 in Figure~\ref{fig:old_sqr2} both contain if branches.
+that line 4 and 9 in Figure~\ref{fig:old_sqr2} both contain \texttt{if} branches.
 However, they are not leaks because
@@
 For example, OpenSSL 0.9.7 adds a fixed windows version of function \textsf{BN\_mod\_exp\_mont\_consttime} to replace original function \textsf{BN\_mod\_exp\_mont}.
-\tool{} detects a minor vulnerability in the original function that can leak the last bit of the big number \textbf{m}.
+\tool{} detects a minor vulnerability in the original function that can leak the last bit of the big number \texttt{m}.
 In the updated version, developers make the fixed windows the default option and rewrite most of the function.
@@
 \begin{table}[!ht]
-\centering\tiny\scriptsize
+\centering\normalsize
 \caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0f.
@@
 $0.0$ means very small amount of leakage, but not exactly zero.}\label{chapter4:tab:RSAOpenSSL1.1.0}
-%\resizebox{\columnwidth}{!}{
+\resizebox{\columnwidth}{!}{
 \begin{tabular}{lrrrc}
 \hline
-\textbf{File}  & \textbf{Line Number} & \textbf{Vulnerable Function} & \textbf{Leaked Information (bits)} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
+\textbf{File}  & \textbf{Line Number} & \textbf{Vulnerable Function} & \textbf{Result (bits)} & \textbf{Fixed} \\\hline
 bn\_lib.c& 143&BN\_num\_bits\_word&*& \cmark\\
@@
 \end{tabular}
+}
 \end{table}
@@
 \subsection{Benchmarks}\label{sec:eval_countermeasures}
+We also tested \tool{} on a set of small benchmarks.
 \subsubsection*{Bit-slicing}
@@
     \centering
-    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.0\textwidth, frame=none]
+    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
 uint8_t password = input();
@@
 $L_{\beta(k)\rightarrow o} = \log_2{|K|} - \log_2{|K^o|} = 8-3 = 5$ bit, which
-confirms the result from \tool. Similarly, we can verify the result of the other
-leakage site. \tool{} reports no leakage on the bit-slicing implementation.
+confirms the result from \tool. Similarly, we can verify the result of other
+leakage sites. \tool{} reports no leakage on the bit-slicing implementation.
 

### 2021-06-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 Side-channel attacks allow attackers to infer sensitive information based on the non-functional behaviors of the computer system.
-Examples of these non-functional behaviors include acoustics, CPU usages, timing, EM signals, etc~\cite{agrawal2002side,hund2013practical,halevi2015keyboard,batina2019csi}.
-In summary, if a program has different execution behaviors when it processes various keys, an attacker can infer nontrivial information by observing secret-dependent behaviors.
+Examples of these non-functional behaviors include acoustics, CPU usages, timing, and EM signals~\cite{agrawal2002side,hund2013practical,halevi2015keyboard,batina2019csi}.
+In general, if a program has different execution behaviors when it processes various keys, an attacker can infer nontrivial information by observing secret-dependent behaviors.
 While separate side-channel attacks may have different forms and patterns, a large portion of them share the same fundamental reasons.
@@
 applications~\cite{yan2020cache,hong2018security}, graphic
-libraries~\cite{wang2019unveiling}, spell checking
-tools~\cite{xu2015controlled}, etc. Unlike side-channel attacks on
+libraries~\cite{wang2019unveiling}, and spell checking
+tools~\cite{xu2015controlled}. Unlike side-channel attacks on
 cryptography libraries that exploit one vulnerability at a time,
@@
 leakage sites. However, no existing tools that can estimate the total
-effect of multiple leakage sites. For real-world applications with
+effect of multiple leakage sites. Are they independent or have the same root cause? For real-world applications with
 thousands of lines, attacker can exploit more than one leakage sites
 to retrieve more information. Attackers can guess the values of many temporary
-values. And these temporary values contain some knowledge of the
+values. These temporary values may contain some knowledge of the
 original secret buffer.
 
-Second, many side-channel leakage detection tools rely on
+Many side-channel leakage detection tools rely on
 techniques such as symbolic executions, taint analysis, and abstract interpretations~\cite{203878,182946,Brotzman19Casym,236338}. Due
@@
 
-Third, while many existing works can detect side-channel leakages, few
+While many existing works can detect side-channel leakages, few
 of them can assess the severity levels of these
@@
 We treat the side-channel attack as a communication system and use the channel capacity to quantify the amount of the information flow from the original secret to an attacker's observation.
-The method also allows us to combine multiple leakages sites to retrieve the information.
+The method also allows us to combine multiple leakages sites to estimate the overall effect.
 The attack can be seen as a process that reduces the search space of the original sensitive inputs.
@@
   effect of each side-channel leakage site. Our analysis combines
-  information from both the source code and the run-time execution,
-  which makes the method more effective in finding the leakages. The
+  information from both the source code and the runtime execution,
+  which makes the method more effective in finding leakages. The
   technique can combine multiple leakage sites to retrieve more
@@
 In this chapter, we treat the side-channel attack as a communication system between two parties.
-In the section, we give an overview of the background knowledge of information theory and present the threat model of the chapter.
+Here we first give an overview of the background knowledge of information theory and present the threat model.
 
@@
 \begin{equation}\label{chapter5:eq1}
-  H(K) = - \sum_{k {\in} K}p(k)\log_2p(k)
+  H(K) = - \sum_{k {\in} K}p(k)\log_2p(k).
 \end{equation}
@@
 \begin{equation}\label{chapter5:eq2}
-  C(K;O) = \max_{p(x)} I(K;O)
+  C(K;O) = \max_{p(x)} I(K;O).
 \end{equation}
@@
 \subsubsection{Noiseless Lossless Channel}
-An information channel is noiseless and lossless if every $k$ corresponds to exactly one unique $o$. The channel capacity of a noiseless lossless channel equals to
+An information channel is noiseless and lossless if every $k$ corresponds to exactly one unique $o$. The channel capacity of a noiseless lossless channel equals
 \begin{equation} \label{chapter5:eq4}
-  C(K;O) = \max_{p(k)} I(K;O) = \max_{p(k)} H|O| =\max_{p(k)} H|K|
+  C(K;O) = \max_{p(k)} I(K;O) = \max_{p(k)} H|O| =\max_{p(k)} H|K|,
 \end{equation}
-$|K|$ represents the number of possible variables in $K$.
+\noindent where $|K|$ represents the number of possible variables in $K$.
 
@@
 Under the circumstance, we always have $P(o_i/k_i) = 1$ and $P(k_i/o_i) = 1$.
-As we can see, the channel have the unique output ($o \in O$) for every input ($k \in K$).
+As we can see, the channel has the unique output ($o \in O$) for every input ($k \in K$).
 
@@
 \subsubsection{Noiseless Loss Channel}
-In reality, noiseless loss channel is more common. The channel capacity of a noiseless loss channel equals to
+In reality, noiseless loss channels are more common. The channel capacity of a noiseless loss channel equals
 
 \begin{equation} \label{chapter:eq:5}
-  C(K;O) = \max_{p(x)} I(K;O) = \max_{p(x)} H |O| 
+  C(K;O) = \max_{p(x)} I(K;O) = \max_{p(x)} H |O|.
 \end{equation}
 
-Figure~\ref{fig:channel}(b) shows an example of the type of the channel.
+Figure~\ref{fig:channel}(b) shows an example of this type of channels.
 Once the input value is determined, the output value is also determined.
@@
 Similar to recent work, we assume the attacker has a noise-free observation.
-The program ($\beta$) has $K$ as the sensitive input.
-$K$ is a finite set that consists of every possible key ($k \in K$).
+The program ($\beta$) has $K$ as the sensitive input, which is a finite set consisted of every possible key ($k \in K$).
 The program also takes known messages $M$ as the input.
@@
   \centering
-  \includegraphics[width=.8\columnwidth]{./figures/chapter5/channel.pdf}
+  \includegraphics[width=.75\columnwidth]{./figures/chapter5/channel.pdf}
   \caption{The relationship between the side-channel attack and the channel capacity.
@@
 
-With the above definitions, we define the following mapping between $\beta$,
+With the above setting, we define the following mapping between $\beta$,
 $K$, $M$, and $O$:
@@
 \begin{displaymath}
-  \beta(K, M) \rightarrow O
+  \beta(K, M) \rightarrow O.
 \end{displaymath}
@@
 Side-channel attacks can be seen as a process that infers the secret ($K$) based on the observations ($O$).
-As shown in the figure~\ref{fig:side_channel}, we assume that an attacker can observe the memory address of the victim program.
+As shown in Figure~\ref{fig:side_channel}, we assume that an attacker can observe the memory addresses of the victim program.
 He wants to infer the original secret ($k$) based on the observation.
@@
 
-To assess the sensitive level of the vulnerability, we use the sampling method to estimate the leakage.
+To assess the severity level of the vulnerability, we use the sampling method to estimate the leakage.
 Suppose we give the function input from $0, 1, \dots, 7$ and observe the array $T$, we can find each different input has one unique observation.
@@
 \begin{figure}[h]
-  \begin{minipage}{0.40\linewidth}
+  \begin{minipage}{0.45\linewidth}
       \begin{tabular}{rrrr}
@@
   \end{minipage}
-\hspace{-15pt}
+%\hspace{-15pt}
 \hfill
-\hspace{-15pt}
-  \begin{minipage}{0.40\linewidth}
+%\hspace{-15pt}
+  \begin{minipage}{0.45\linewidth}
       \begin{tabular}{rrrr}

### 2021-06-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 Both $0$ and $4$ read the first item of the table.
-Therefore, we think the vulnerability is less severe than the previous one.
+Therefore, the vulnerability is less severe than the previous one.
 
-Let's formally define the amount of leaked information based on the above observation.
+Let us formally define the amount of leaked information based on the above analysis.
 
@@
 \begin{theorem}\label{the1}
-  If an attacker launches a side-channel attack on deterministic programs, then the channel between the secret and the observation is a noiseless loss channel.
+  If an attacker launches a side-channel attack on a deterministic program, then the channel between the secret and the observation is a noiseless loss channel.
 \end{theorem}

### 2021-06-15 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \subsection{Case Studies}
-\subsubsection*{DES and AES}
+\subsubsection{DES and AES}
 Our tool confirms that both implementations in OpenSSL and mbedTLS have side-channel leakages
@@
 
-\subsubsection*{RSA}
+\subsubsection{RSA}
 We also evaluate our tool on the RSA implementations. With the optimizations
@@
 
-\subsubsection*{Monocypher}\label{eval:mono}
+\subsubsection{Monocypher}\label{eval:mono}
 Monocypher is a small, easy to use cryptographic library with

### 2021-06-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-\section{Method}
+\section{Method}\label{chapter5:method}
 In this section, we first provide two examples that show how we rank the side-channel vulnerability. After that, we prove that our method is a conservative estimate of the amount of each leakage.
@@
 
-With THEOREM~\ref{the1}, we can have
+With Theorem~\ref{the1}, we can have
 \begin{align*}
@@
 \section{Align Address Access Across Multiple Executions}
-We compare address accesses of different executions generated by different inputs to quantify the amount of leakage information.
+We compare the address accesses of different executions generated by different inputs to quantify the amount of leakage information.
 A meaningful comparison requires that we align executions across multiple runs before we quantify the leakage.
@@
 
-Considering the example in figure~\ref{fig:align}, it read data from the array \textsf{T} based on the index ($i$).
-If the value of index ($i$) is associated with secret information, the example is vulnerable to side-channel attacks.
-Unlike the example in the previous section, the array \textsf{T} is on the heap.
-Data on the heap are allocated at different addresses each time.
-Suppose during the first run, \textsf{T} is allocated at the address \texttt{0xff124800} and \textsf{T} is allocated at the address \texttt{0xff124801} at the second run.
+Considering the example in Figure~\ref{fig:align}, it read data from the array \textsf{T} based on the index ($i$).
+If the value of index ($i$) is associated with the secret information, the example is vulnerable to side-channel attacks.
+Unlike the example in Section~\ref{chapter5:method}, the array \textsf{T} is on the heap.
+Data on the heap are often allocated at different addresses each time.
+Suppose during the first run, \textsf{T} is allocated at the address \texttt{0xff124800}, and \textsf{T} is allocated at the address \texttt{0xff124801} during the second run.
 For the example in Figure~\ref{fig:align}(a), the index that is used to access the array is always $1$, so it should not be a side-channel vulnerability here.
-However, base addresses are different (\texttt{0xff124800} and \texttt{0xff124801}) so we get two different memory accesses.
+However, the base addresses are different (\texttt{0xff124800} and \texttt{0xff124801}) so we get two different memory accesses.
 Under the circumstance, it is a false positive.
@@
 
-\textbf{Our Strategy: } We assign a value for each memory location~\cite{sumner2010memory}. The value should satisfy the following characteristics.
+\subsubsection*{Our Strategy} We assign a value for each memory location~\cite{sumner2010memory}. The value should satisfy the following characteristics.
 \begin{itemize}
@@
 
-\textbf{Run-time Information.} One example here is the concrete memory address during the runtime.
+\textbf{Runtime Information.} One example here is the concrete memory address during execution.
 Such a value satisfies the uniqueness characteristic.

### 2021-06-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
     \begin{lstlisting}[numbers=none,xleftmargin=.1\textwidth,xrightmargin=.15\textwidth]
-uint8_t *T = malloc(4);
+uint8_t* T = malloc(4);
 if (T==NULL) exit(1);
@@
 These vulnerabilities may spread throughout the whole program.
-An adversary may exploit more than one side-channel vulnerabilities to gain more information~\cite{7163052, 191010}.
+An adversary may exploit more than one side-channel vulnerability to gain more information~\cite{7163052, 191010}.
 In order to quantify the
@@
 
-Considering the examples in Figure~\ref{chapter5:fig:multiple}, Figure~\ref{chapter5:fig:multiple}(a) show a code snippet with two leakage sites at line 6 and line 8 respectively.
-For example, if an adversary observes that function \textsf{a} executes, then the attacker can infer the first byte in buffer \textsf{secret} is larger than the second byte.
+Considering the examples in Figure~\ref{chapter5:fig:multiple}, Figure~\ref{chapter5:fig:multiple}(a) show a code snippet with two leakage sites at line 6 and line 8, respectively.
+For example, if an adversary observes that function \textsf{a} executes, then the attacker can infer that the first byte in buffer \textsf{secret} is larger than the second byte.
 Similarly, if an adversary observes that function \textsf{b} executes, then the attacker can infer that the sum of the first two bytes in buffer \textsf{secret} is smaller than $256$.
@@
 
-Suppose one program has two side-channel vulnerabilities $A$ and $B$, which can leak $L_A$ and $L_B$ bits, respectively, according to Definition~\ref{chapter5:def}. 
+Suppose a program has two side-channel vulnerabilities $A$ and $B$, which can leak $L_A$ and $L_B$ bits, respectively, according to Definition~\ref{chapter5:def}. 
 For the example in Figure~\ref{chapter5:fig:multiple}, we use $a$ to denote that the function \textsf{a} executes, and $\lnot a$ to denote that the function \textsf{a} does not execute during the execution.
-Depending on the relation between $A$ and $B$, the total leaked information $L_{\mathit{AB}}$ will be:
+Depending on the relation between $A$ and $B$, the total leaked information $L_{\mathit{AB}}$ can be calculated as follows.
 
@@
 We call each memory access pattern as an observation.
-If any observation of $A$ does not affect the probability of occurrence of any observation of $B$, we call the two leakage sites $A$ and $B$ are independent.
-$p_{ab} = p_ap_b$.
+If any observation of $A$ does not affect the probability of occurrence of any observation of $B$, we call the two leakage sites $A$ and $B$ are independent, $p_{ab} = p_ap_b$.
 If $A$ and $B$ are two independent leakages, the total amount of leaked information is:
@@
 \subsection{Dependent Leakages}
-If A and B are dependent leakages, the total information leakage will be:
+If $A$ and $B$ are dependent leakages, the total information leakage will be:
 \[\max{\{L_A, L_B\}}  \leq L_{\mathit{AB}} < L_A + L_B\]
@@
 A chi-squared test can determine if there is a relationship between two categorical variables.
-Suppose we can summarize the data in a $r*c$ two-way contingency table.
-The chi-squared test statistic and the degrees of freedom $v$ are calculated with the below formula:
-\[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k} \qquad	 v = (r - 1)(c - 1)\]
-Here $O$ is the observed value, and $E$ is the expected value. A low value means that there is a high correlation between the two variables.
+Suppose we can summarize the data in a $r \cdot c$ two-way contingency table.
+The chi-squared test statistic and the degrees of freedom $v$ are calculated with the formula below.
+\[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k} \qquad and	 v = (r - 1)(c - 1)\]
+Here $O$ is the observed value and $E$ is the expected value. A low value means that there is a high correlation between the two variables.
 
@@
 Each time, the execution is independent of the previous execution, and the target program is the same as the program executed in the previous experiment.
-For one type of event(e.g., function $a$ executes), we use $p$ to denote the probability of the event.
+For one type of event (e.g., function $a$ executes), we use $p$ to denote the probability of the event.
 Suppose the target program is executed $n$ times, the probability that we observe the event happens $k \,(k < n)$ times is $P = \binom{k}{n}p^n(1-p)^{n-k}$.
@@
 \begin{figure}[h]
-  \begin{minipage}{0.45\linewidth}
+  \begin{minipage}{0.46\linewidth}
       \begin{tabular}{rrrr}
@@
   \end{minipage}
-%\hspace{-15pt}
 \hfill
-%\hspace{-15pt}
-  \begin{minipage}{0.45\linewidth}
+  \begin{minipage}{0.46\linewidth}
       \begin{tabular}{rrrr}
@@
   \end{minipage}
-  \caption{The contingency table for the experiments. The numbers in the bracket are expected values. }\label{chapter5:fig:con_table}
+  \caption{The contingency table for the experiments. The numbers in the parenthesis are expected values. }\label{chapter5:fig:con_table}
 \end{figure}
@@
 After calculating the number of the same observation, we get the contingency table shown in Figure~\ref{chapter5:fig:con_table}.
-Suppose the observations of the execution of function \textsf{a} and the execution of function \textsf{b} are independent ($p_{ab} = p_a*p_b$),  we calculate the expected value for the observation $ab$ based on the frequency.
-\[ E_{ab} = 1024*p_{ab} = 1024*p_a*p_b = 1024*\frac{515}{1024}*\frac{508}{1024} = 255.5\]
+Suppose the observations of the execution of function \textsf{a} and the execution of function \textsf{b} are independent ($p_{ab} = p_a \cdot p_b$),  we calculate the expected value for the observation $ab$ based on the frequency.
+\[ E_{ab} = 1024 \cdot p_{ab} = 1024\cdot p_a \cdot p_b = 1024  \cdot \frac{515}{1024} \cdot \frac{508}{1024} = 255.5\]
 Similarly, we calculate the rest expected values with the hypothesis that the leakages are independent and fill in them in Figure~\ref{chapter5:fig:con_table}.
-The degree of freedom $v$ is $(2-1)*(2-1) = 1$.
+The degree of freedom $v$ is $(2-1)\cdot(2-1) = 1$.
 
@@
 According to Definition~\ref{chapter5:def}, we quantify the information leakage based on the distribution of the observation.
-If we calculate the information leakage from a $4MB$ memory area, then the length of the byte-level bitmap is $4*1024*1024 = 4194304$.
+If we calculate the information leakage from a $4MB$ memory area, then the length of the byte-level bitmap is $4 \cdot 1024 \cdot 1024 = 4194304$.
 While it is possible to compute the distribution of the bitmap theoretically, it is hard to compare the bitmap of such length in practice.
@@
 \begin{displaymath}
-  H(O') = - \frac{3}{8}*\log_2{\frac{3}{8}}- \frac{1}{2}*\log_2{\frac{1}{2}}
-  - \frac{1}{8}*\log_2{\frac{1}{8}} = 1.4 \,\mathrm{bits}
+  H(O') = - \frac{3}{8} \cdot \log_2{\frac{3}{8}}- \frac{1}{2} \cdot \log_2{\frac{1}{2}}
+  - \frac{1}{8} \cdot \log_2{\frac{1}{8}} = 1.4 \,\mathrm{bits}
 \end{displaymath}

### 2021-06-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 The chi-squared test statistic and the degrees of freedom $v$ are calculated with the formula below.
-\[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k} \qquad and	 v = (r - 1)(c - 1)\]
+\[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k}, \qquad 	 v = (r - 1)(c - 1)\]
 Here $O$ is the observed value and $E$ is the expected value. A low value means that there is a high correlation between the two variables.

### 2021-06-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 We use the above method to test if any two leakage sites are independent for each leakage point.
-We combine them into a leakage are calculate the total amount of the leakage.
+We combine them into a leakage and calculate the total amount of the leakage.
 \section{Design}
-In this section, we explain the implementation of \ctool{}.
+In this section, we explain the design of \ctool{}.
 We first present the overview of \ctool{}. After that, we discuss some design details to implement \ctool{}.
@@
 Figure~\ref{chapter5:fig:workflow} shows an overview of our side-channel leakages quantification tool.
-Given the source code of the victim program, \ctool{} can find the address-based side-channel leakages by fuzzing the victim program.
+Given the source code of a victim program, \ctool{} can find the address-based side-channel leakages by fuzzing the victim program.
 To assist the illustration, we divide the workflow of ~\ctool{} into three steps.
 For the first step, we build the target program from the source code.
-After that, we give them random inputs to the victim program and run the target program and record each of the addresses in the binary file is hit or not, and store the information in a bitmap.
+After that, we give them random inputs to the victim program and run the target program and record the each of the addresses in the binary file is hit or not, and store the information in a bitmap.
 Next, we analyze the side-channel leakage from the address access bitmap.
-We split the address space into several segments to speed up the comparison according to Meta information.
-Finally, \ctool{} Generate the final leakage report.
-For each leakage site, \ctool{} gives the conservative estimation of the information leakage.
+We split the address space into several segments to speed up the comparison according to the meta information.
+Finally, \ctool{} generates the final leakage report.
+For each leakage site, \ctool{} gives a conservative estimation of the information leakage.
 Every leakage site in the report is a true leakage, and there are no false positives.
@@
   \centering
-  \includegraphics[width=\columnwidth]{./figures/chapter5/workflow.pdf}
-  \caption{The workflow of \ctool{}. We try to divide the \ctool{} into three steps to assist the illustration. }\label{chapter5:fig:workflow}
+  \includegraphics[width=.9\columnwidth]{./figures/chapter5/workflow.pdf}
+  \caption{The workflow of \ctool{}. We divide \ctool{} into three steps to help the illustrate the process. }\label{chapter5:fig:workflow}
 \end{figure}

### 2021-06-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 After we build the software into the binary executable, we give the
-binary code the random inputs. For cryptography libraries, the input
+binary executable random inputs. For cryptography libraries, the input
 is the encryption key. For non-cryptography libraries, the input could
@@
 generate the random input by flipping each bit of the keys. Some other
-programs also take a buffer as the input. The buffer may contain the
+programs also take a buffer as the input. The buffer may contain 
 redundancy information and follow a specific format. So not any input

### 2021-06-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 programs also take a buffer as the input. The buffer may contain 
-redundancy information and follow a specific format. So not any input
+redundancy information and follow a specific format. So not every input
 that satisfies the input length is a valid input. Under the
@@
 example, crypto libraries usually take PKCS \#1 as the input of the
-RSA private key. We use some other tools to generate a list of valid
-keys and use the key to sample the program. Due to the enormous search
+RSA private key. We generate a list of valid
+keys and use the keys to sample the program. Due to the enormous search
 space, we cannot iterate every input. However, our method can give a
 conservative estimate of each leakage site.
+
 \subsection{Step 2: Address Record}

### 2021-06-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 whether a particular memory access information is accessed or
-not. Inspired by the AFL and Valgrind, we use the bitmap to represent
+not. Inspired by AFL and Valgrind, we use a bitmap to represent
 whether a particular memory is accessed or not. For example, the
@@
 information we get is the virtual memory address (VMA). However, we
-transfer the address into the offset (Load Memory Address (LMA)) in
+transfer the address into the offset LMA (Load Memory Address) in
 the original binary file. It has two benefits. First, modern computer
 systems employ the Address Space Layout Randomization (ASLR). With
-ASLR, the operating system randomly puts the enclave code and data at
+ASLR, the operating system randomly puts the code and data at
 various memory offset. As a result, the code will get different
-execution traces even for the same input because the enclave image is
+execution traces even for the same input because the image is
 loaded at a different address each time. Second, it helps us find the
@@
 the same as the offset within the binary file. We choose the start
-address of some common functions (e.g., $\textsf{main}$) ($b$) as the navigation
-function. We get the virtual memory address of the start of the
+address of some common functions (e.g., $\textsf{main}$) as the navigation
+function. Let $b$ be the navigation function here. 
+We get the virtual memory address of the start of the
 function ($\mathit{VMA}_b$) from the DBI tool and the load memory

### 2021-06-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 \item Code Access.
-The memory address of the code is the value of $\mathit{rip}$ register.
+The memory address of the code is the value of the program counter $\mathit{rip}$ register.
 However, the length of x86 instructions can be from 1 byte to 15 bytes.
@@
 \item Data Access.
-For instructions with memory access, we identify all the operands of each instruction and.
-Same as the code address, the instruction can read or write multiple bytes one time.
+For instructions with memory access, we identify all the operands of each instruction.
+Same as the code addresses, the instruction can read or write multiple bytes one time.
 Instructions like \textsf{push} and \textsf{pop} have implicit memory access.
@@
 In this step, we detect and quantify the side-channel leakage.
-For each $k \in K$, we have a boolean number ($0$ or $1$) to describe whether the address $addr$ is accessed or not during the execution when the input is $k$.
-For the brevity of description, For the brevity of description, we use $B^{addr}_{k_i}$ to denote the boolean number.
+For each $k \in K$, we have a boolean number ($0$ or $1$) to describe whether the address $l$ is accessed or not during the execution when the input is $k$.
+For the brevity of description, we use $B^{l}_{k_i}$ to denote the boolean number.
 
-\subsubsection{Various Granularities Side-channel Detection}
-\ctool{} can detect the side-channel vulnerabilities in different granularities.
+\subsubsection{Multi-granularity Side-channel Detection}
+\ctool{} can detect side-channel vulnerabilities in different granularities.
 For each granularity, we calculate a new bitmap that represents access information of each unit.
@@
 The access of one address is secret-dependent if $ \exists\, k_{i_1}, k_{i_2} \in K, \, B^{l}_{k_{i_1}} \oplus  B^{l}_{k_{i_2}} =1 $.
-In the step, we perform the logical exclusive OR operation on every boolearn value in the same address.
+In this step, we perform the logical exclusive OR operation on every boolearn value in the same address.
 If the result is $1$, then the address is vulnerable to the side-channel attacks.
@@
 \begin{myexample}
-Suppose we sample a program from $k1$ to $k8$ and record memory accesses at the granularity of one byte from $\mathtt{7ffff7ffd000}$ to $\mathtt{7ffff7ffd03f}$ (One cache line).
+Suppose we sample a program from $k_1$ to $k_8$ and record memory accesses at the granularity of one byte from $\mathtt{7ffff7ffd000}$ to $\mathtt{7ffff7ffd03f}$ (one cache line).
 We perform a bit-wise operation of each address within the range.
 Because the cache line is always accessed.
-We think it is not a leak here.
+It is not a leak here.
 \begin{center}
@@
 
-\subsubsection{Estimate The Leaked Information}
+\subsubsection{Estimate the Leaked Information}
 According to Definition~\ref{chapter5:def}, we quantify the information leakage based on the distribution of the observation.
-If we calculate the information leakage from a $4MB$ memory area, then the length of the byte-level bitmap is $4 \cdot 1024 \cdot 1024 = 4194304$.
+If we calculate the information leakage from a $4 \mathrm{MB}$ memory area, then the length of the byte-level bitmap is $4 \times 1024 \times 1024 = 4194304$.
 While it is possible to compute the distribution of the bitmap theoretically, it is hard to compare the bitmap of such length in practice.

### 2021-06-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 Each segment maps the address access situation of the function in the source code.
-In our setting, the max length of the bitmap of each segment is $1024$, the length of \textsf{uint1024\_t}.
+In our setting, the maximal length of the bitmap of each segment is $1024$, the length of \textsf{uint1024\_t}.
 So we can put the bitmap into a variable.
 The split operation eases the computation.
-However, it also adds the limitation of the max address range when we quantify the side-channel leakage shown in Table~\ref{tab:size_limitation}.
-We think the range of the memory is big enough for us to quantify most of the cache side-channel attacks.
+However, it also adds the limitation of the max address range when we quantify the side-channel leakage, as shown in Table~\ref{tab:size_limitation}.
+We believe the range of the memory is big enough for us to quantify most of the cache side-channel attacks.
 
@@
 We have implemented a prototype of \ctool{}.
-It takes an input of ELF binary as well as the source code of the corresponding problem.
+It takes an input of ELF binary as well as the source code of the corresponding program.
 The front-end of \ctool{} is implemented in Python.

### 2021-06-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
   \hfill
-  \begin{minipage}{0.2\linewidth}
+  \begin{minipage}{0.15\linewidth}
     {
@@
   \hfill
-  \begin{minipage}{0.25\linewidth}
-    \resizebox{\linewidth}{!}{
+  \begin{minipage}{0.3\linewidth}
+    \resizebox{.8\linewidth}{!}{
 
@@
 It can generate random inputs and test the program with these inputs many times.
-The address record part is implemented as an Intel Pin tool plugin in C++ to record the bitmap for each input.
+The address recording part is implemented as an Intel Pin tool plugin in C++ to record the bitmap for each input.
 The main component uses \textsf{libelfin}, an open-source library to parse ELF binaries and read DWARF debug information.
@@
 \textit{Cryptography Applications:} Our benchmarks include most of the popular cryptography libraries, such as mebdTLS, OpenSSL, Libgcrypt, and wolfSSL.
-Encryption ciphers can be divided into three categories:  symmetric ciphers and asymmetric ciphers.
+Encryption ciphers can be divided into two categories:  symmetric ciphers and asymmetric ciphers.
 For symmetric ciphers, we choose AES.
-We also evaluate the tool on RSA, a widely used algorithm in the public-key cryptosystem.
+We also evaluate the tool on RSA, a widely used algorithm in the public-key cryptosystems.
 

### 2021-06-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-\textit{Graphic Libraries:} We evaluate the tool on GDK, a popular graphic library. Previous research has demonstrated attacks to infer the keystroke.
+\textit{Graphic Libraries:} We evaluate the tool on GDK, a popular graphic library. Previous research has demonstrated attacks to infer the keystroke~\cite{191010,wang2019unveiling}.
 
@@
 \footnotesize
-\caption{Evaluation results overview: Name of the benchmark, The Size of the Input Data, The number of leaked functions, The Maximum Leakage, The size of the benchmark, and Performance.}\label{chapter5:table:over_result}
+\caption{Evaluation results overview: Name of the benchmark, size of the Input Data, number of leaked functions, maximum Leakage, size of the benchmark, and performance.}\label{chapter5:table:over_result}
 \centering
@@
 Table~\ref{chapter5:table:over_result} presents the overview result.
-The minimum unit of the program during the experiment is the function.
+The minimum unit of the program during the experiment is one function.
 If a function has more than one access bitmap, then the function is vulnerable to side-channel attacks.
@@
 For cryptography programs, we run the target program with $4096$ different inputs.
-During the fuzzing process, if the program does not have a new memory access bitmap after several rounds.
-We call the fuzzing step is fixed.
+During the fuzzing process, if the program does not have a new memory access bitmap after several rounds, we call the fuzzing step is fixed.
 From the side-channel detection aspect, it is not necessary to continue running the experiments since more rounds do not reveal new leakages.
@@
 AES encryption can be divided into three steps.
-In the first step, the round keys are derived from the encryption keys called the AES key schedule, and a state array is initialized with the plain-text and the initial round step.
+In the first step, the round keys are derived from the encryption keys (AES key schedule), and a state array is initialized with the plain-text and the initial round step.
 In the second step, the AES performs eleven rounds of state manipulation.
@@
 
-RSA implementations blind the secret data on a random value before operating on it.
+The RSA implementations blind the secret data on a random value before operating on it.
 We use a fixed RSA blinding value to avoid non-deterministic behaviors during the execution.

### 2021-06-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 The result shows that \ctool{} can identify all leakage sites reported in the previous work.
-In addition, \ctool{} identify new leakages in the private key decoded function (\textsf{conv\_ascii2bin}) in OpenSSL 1.1.1.
+In addition, \ctool{} identifies new leakages in the private key decode function (\textsf{conv\_ascii2bin}) in OpenSSL 1.1.1.
 To evaluate the effectiveness of the quantification result, we compare the two RSA implementations between OpenSSL 1.1.0 and OpenSSL 1.1.1.
-\ctool{} identify several functions that are vulnerable to side-channel attacks.
-We are interested if these leaked functions are fixed in the updated version.
+We are interested if these leaked functions in OpenSSL 1.1.0 are fixed in OpenSSL 1.1.1.
 Note that \ctool{} can analyze the side-channel leakages at both the byte granularity and the cache line granularity. We show the result analyzed with cache line granularity.
@@
 \begin{table}[!ht]
-\centering
-\caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0.}\label{chapter5:tab:RSAOpenSSL1.1.0}
+\centering\normalsize
+\caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0. We manually check if these leaked functions are fixed in OpenSSL 1.1.1.}\label{chapter5:tab:RSAOpenSSL1.1.0}
 %\resizebox{\columnwidth}{!}{
 \begin{threeparttable}
-\begin{tabular}{llrc}
+\begin{tabular}{llrrc}
 \hline
-\textbf{File}  & \textbf{Vulnerable Function} & \textbf{Result (bits)} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
-bn\_lib.c& BN\_num\_bits\_word& 5.7 & \cmark\\
-bn\_lib.c& bn\_correct\_top&  7.6 & \cmark\\
-bn\_lib.c& BN\_ucmp& 6.7 & \cmark\\
-ct\_b64.c& \_\_udivdi3&4.3 & \cmark\\
-bn\_gcd.c& int\_bn\_mod\_inverse & 7.7 & \cmark\tnote{1} \\
-bn\_exp.c& BN\_mod\_exp\_mont\_consttime&  1.0 & \xmark\\
-bn\_mont.c& BN\_from\_montgomery\_word\tnote{2}& 9.7 &\cmark\\
-bn\_mont.c& BN\_from\_montgomery\_word&  0.1 &\xmark\\
+\textbf{File}  & \textbf{Vulnerable Function} & \textbf{A\tnote{a} (bits)} & \textbf{Q\tnote{b} (bits)} & \textbf{Fixed} \\\hline
+bn\_lib.c& BN\_num\_bits\_word&(*, *, *, *, *, 17.2, 12.6)& 5.7 & \cmark\\
+bn\_lib.c& bn\_correct\_top& 1.7 & 7.6 & \cmark\\
+bn\_lib.c& BN\_ucmp&*& 6.7 & \cmark\\
+ct\_b64.c& \_\_udivdi3&5.9 &4.3 & \cmark\\
+bn\_gcd.c& int\_bn\_mod\_inverse&(14.9, 9.2, 8.2, 7.9, 1.0) & 7.7 & \cmark\tnote{1} \\
+bn\_exp.c& BN\_mod\_exp\_mont\_consttime& (1.0, 1.0) & 1.0 & \xmark\\
+bn\_mont.c& BN\_from\_montgomery\_word\tnote{2}& (*, *, *, *, *, *, 0.0)& 9.7 &\cmark\\
+bn\_mont.c& BN\_from\_montgomery\_word& 0.0& 0.1 &\xmark\\
 
-bn\_asm.c& bn\_sqr\_comba8&5.0& \cmark\\
-bn\_div.c& BN\_div & 7.3  & \cmark\\
-rsa\_ossl.c& rsa\_ossl\_mod\_exp& 4.8 & \cmark\\
-encode.c & conv\_bin2ascii & 1.2 & \xmark\\
+bn\_asm.c& bn\_sqr\_comba8&9.3&5.0& \cmark\\
+bn\_div.c& BN\_div&(17.2, 11.9, 3,8, 0.3, 0.3) & 7.3  & \cmark\\
+rsa\_ossl.c& rsa\_ossl\_mod\_exp& 1.0 & 4.8 & \cmark\\
+encode.c & conv\_bin2ascii & Not Found & 1.2 & \xmark\\
 \hline
@@
 \begin{tablenotes}
+    \item[a] \tool{} \item[b] \ctool{}\\
     \item[1] The leakage site at line 144 (OpenSSL 1.1.1) are not fixed.\\
@@
 
-Table~\ref{chapter5:tab:RSAOpenSSL1.1.0} shows the leaked function and the amount of leakage reported by \ctool{}.
-First, as the result indicates, the leakage sites that leak a lot of information (> 5.0 bits) are all fixed in OpenSSL 1.1.1.
+Table~\ref{chapter5:tab:RSAOpenSSL1.1.0} shows the leaked function and the amount of leakage reported by \ctool{} and \tool{}~\cite{bao2021abacus}.
+According to \tool{}\cite{bao2021abacus}, the mark ``$*$'' means timeout, which indicates more severe leakages.
+$0.0$ means very small amount of leakage, but not exactly zero.
+As the result indicates, the leakage sites that leak a lot of information (> 5.0 bits) are all fixed in OpenSSL 1.1.1.
 The result indicates that \ctool{} can help developers identify side-channel leakages and pick severe ones from them automatically.
-As expected, we find that most of the leakages are from big number calculations.
+As expected, we find that most of the leakages are from the big number calculations.
 OpenSSL has a side-channel mitigated big number implementation.
-As long as big numbers are derived from secret data, the big number should be enabled with the flag \textsf{BN\_FLG\_CONSTTIME}.
+As long as big numbers are derived from the secret data, the big number should be enabled with the flag \textsf{BN\_FLG\_CONSTTIME}.
 However, the flag is off by default.
-We find developers forget to propagate the flag in the caller, which results in the vulnerabilities in \textsf{BN\_div} and \textsf{int\_bn\_mod\_inverse}.
-Second, for leakage sites that are not fixed by the developers, \ctool{} reports that they leak less amount of information.
+We find that the developers forget to propagate the flag in the caller, which results in the vulnerabilities in \textsf{BN\_div} and \textsf{int\_bn\_mod\_inverse}.
+
+For leakage sites that are not fixed by the developers, \ctool{} reports that they leak less amount of information.
 For example, function \textsf{BN\_mod\_exp\_mont\_consttime} check if the modulus is odd.
-However, it is not a side-channel leakage vulnerability.
+However, it is not a side-channel leakage vulnerability since the modulus is a prime number and all prime numbers except $2$ are odd.
 \ctool{} reports that the leakage site can leak one bit of information.
-Third, previous work~\cite{bao2021abacus} reports some leakage sites leak little information, but \ctool{} reports the vulnerability is severe.
+
+Previous work~\cite{bao2021abacus} reports some leakage sites leak little information, but \ctool{} reports the vulnerabilities are severe.
 Previous work \tool{}~\cite{bao2021abacus} quantifies the amount of leaked information for one execution.
@@
 However, we cannot conclude that any two leakages from cryptography benchmarks are independent under the chi-squared test.
-We think it is due to the avalanche effect in cryptography.
+We think it is probably due to the avalanche effect in cryptography.
 

### 2021-06-16 SupplementaryMaterial/Vita.tex
Updates from Overleaf

@@
 His research interests span reverse engineering, binary analysis, and trusted computing.
-Before he went to Penn State, he received his bachelor's degree in Electronic Engineering and Information Science (EEIS) from University of Science and Technology of China (USTC).
+Before he went to Penn State, he received his bachelor's degree in Electronic Engineering and Information Science (EEIS) from University of Science and Technology of China (USTC) in 2016.

### 2021-06-16 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 One example is cache channel attacks.
-The CPU cache is a smaller but faster memory designed to bridge the gap of the access time between the main memory and CPU registers by storing copies of recently accessed data.
+The CPU cache is a smaller but faster memory to bridge the gap of the access time between the main memory and CPU registers by storing copies of recently accessed data.
 Because the size of the cache is significantly smaller than the size of the main memory, the CPU may only find part of the data in the cache.
@@
 Hardware-level solutions, such as reducing shared resources, oblivious RAM, and transnational memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need to adopt new hardware features and change  today's modern complex computer systems, which are hard to adopt in reality.
-Therefore, a promising and universal direction is software countermeasures, detecting and eliminating side-channel vulnerabilities in existing software code base.
+Therefore, a promising and universal direction is software countermeasures, detecting and eliminating side-channel vulnerabilities in existing software codebase.
 For example, when we examine recent side-channel attacks, many of them exploit two kinds of code patterns: \emph{secret-dependent control-flow transfers} and \emph{secret-dependent data accesses}.
 \begin{figure}[h]
-    \begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
+    \begin{lstlisting}[xleftmargin=.3\textwidth, xrightmargin=.32\textwidth]
 int secret[32];
@@
 \begin{figure}[h]
-    \begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
+    \begin{lstlisting}[xleftmargin=.3\textwidth, xrightmargin=.2\textwidth]
 static char FSb[256] = {...}
@@
 
-However, eliminating side-channel vulnerabilities from real-world software code base is not easy.
+However, eliminating side-channel vulnerabilities from real-world software codebase is not easy.
 First, side-channels are a low-level problem in computer systems.
 As a non-functional property, it can be difficult for programmers to reason about or test.
-While recent work~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} can detect many side-channel vulnerabilities, it either suffers from expensive computation costs or high false positives and false negatives.
+While recent work~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} can detect many side-channel vulnerabilities, it suffers from either expensive computation costs or high false positives and false negatives.
 Second, most vulnerabilities pose a negligible risk.
@@
 We need a proper quantification metric to assess the sensitivity of side-channel vulnerabilities, so a developer can efficiently triage them.
-Third, many side-channel vulnerable implementations (e.g., the CRT optimization and lookup tables) have better performance.
+Third, many side-channel vulnerable implementations (e.g., using the Chinese Remainder Theorem optimization in RSA and lookup tables in AES) have better performance.
 This is a dilemma between the performance and the security.
@@
 Chapter~\ref{chapter5} extends the approach and quantifies the side-channel leakage in a multiple-trace attack.
-Chapter~\ref{chapter6} and Chapter~\ref{chapter7} discuss limitations of the dissertation research and propose the future work.
+Chapter~\ref{chapter6} and Chapter~\ref{chapter7} discuss limitations and future work.

### 2021-06-16 SupplementaryMaterial/Abstract.tex
Updates from Overleaf

@@
 information can leak through many mechanisms such as power consumption, 
-execution timing, and even electromagnetic radiation. Among them, 
+execution time, and even electromagnetic radiation. Among them, 
 address-based side-channel attacks, such as cache-based attacks, 
@@
 are often reluctant to address them. Existing tools do not provide sufficient 
-information, such as the amount of information leakage through side channels, 
+information, such as the amount of information leaked through side channels, 
 to evaluate the severity of a vulnerability.
@@
 This dissertation research develops fundamental and practical techniques for precise side-channel 
-analysis in software systems. We have also open sourced our research software prototypes.
+analysis in software systems. We have also released our research software prototypes.
 As a result, developers can use our tools to develop more secure systems and the academic and industry

### 2021-06-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 
-We consider an access-based attack~\cite{DBLP:journals/jce/GeYCH18}, where an adversary can probe one time for each run only after the termination of a deterministic program.
+We consider an access-based attack~\cite{ge2018survey}, where an adversary can probe one time for each run only after the termination of a deterministic program.
 The attacker may not know the memory access the victim program accesses directly.

### 2021-06-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
   \end{minipage}
-  \caption{Two Kinds of Channels}\label{fig:channel}
+  \caption{Two kinds of information channels}\label{fig:channel}
 \end{figure}
@@
     {
-      \begin{lstlisting}[frame=none]
+      \begin{lstlisting}[frame=none,numbers=none]
               k1  k2  k3  k4  k5  k6  k7  k8   Result  
@@
   \end{minipage}
-  \caption{Example 2}\label{fig:design:example2}
+  \caption{We estimate the amount of leaked information by traversing a binary tree.}\label{fig:design:example2}
 \end{figure}

### 2021-06-16 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 
-To address Problem 1, we make the following contributions on detecting side-channel leakages:
+On detecting side-channel leakages from real-world software, we make the following contributions:
 
@@
 
-To address Problem 2, we make the following contributions on quantifying side-channel leakages in a single trace attack:
+On quantifying fine-grained leaked information in a single trace attack, we make the following contributions:
 
@@
 
-To address Problem 2, we make the following contributions on quantifying side-channel leakages on a multiple trace attack:
+On quantifying side-channel leakages through a multiple-trace attack, we make the following contributions:
 \begin{itemize}

### 2021-06-16 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 \subsubsection*{Password Checker}
+
 \begin{figure}
@@
   \end{minipage}
+
   \vfill
+
   \begin{minipage}{0.8\linewidth}
     \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.00\textwidth, frame=none]
+
 bool pwcheck(uint8_t *key, uint8_t *pub) {

### 2021-06-16 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 It has a conditional jump instruction \textsf{jne}.
-The sensitive input \textsf{k} can affect the program counter (the rip register), which is the root cause of the side-channel leakages.
+The sensitive input \textsf{k} can affect the program counter (the \textsf{rip} register), which is the root cause of the side-channel leakages.
 
@@
 
-\begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth, frame=none][ht]
+\begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth, frame=none,numbers=none][h]
 ...
@@
 \begin{table*}
-  \centering\small\footnotesize
+  \centering\small
   \caption{Evaluation results overview: Algorithm, Implementation, Side-channel Leaks\,(Leaks),
@@
     \resizebox{.9\columnwidth}{!}{%
-    \begin{tabular}{@{}l|r@{~~}r@{~~}r|r@{~~}r@{~}r@{}}
+    %TODO
+    \begin{tabular}{l|rrr|rrr}
       \hline
@@
       Total                 & 22,788.0                    & 55,738,546                 & 84 & 4,125.0  & 51,514,721      & 155+178 \\ \hline
-      \multicolumn{7}{l}{\# of Instructions per second \qquad  CacheD: 2,445 \qquad \tool: 12,489}                                 \\ \hline
+      \multicolumn{7}{l}{\# of Instructions per second \qquad  CacheD: 2,445 \qquad \qquad \qquad \qquad \tool: 12,489}                                 \\ \hline
     \end{tabular}

### 2021-06-17 Chapter-4/Chapter-4.tex
Updates from Overleaf

--- 2021-06-15 Chapter-4/Chapter-4.tex
@@
     \caption{\tool{}' main components and sizes}\label{tbl:implementation}
-    \begin{tabular}{lr@{~}@{}l}
+    \begin{tabular}{lr@{~}l}
         \hline
@@
     \centering
-    \begin{lstlisting}[ frame=none]
-int mbedtls_internal_aes_encrypt( mbedtls_aes_context *ctx,
+    \begin{lstlisting}[frame=none]
+int mbedtls_internal_aes_encrypt(mbedtls_aes_context *ctx,
 const unsigned char input[16],
@@
 ...
-return( 0 );
+return 0;
 }
@@
 \resizebox{\columnwidth}{!}{
-\begin{tabular}{lrrrc}
+\begin{tabular}{lrlrc}
 \hline
@@
 
-\begin{figure}
+\begin{figure}[h]
 \centering
@@
 \subsubsection*{Password Checker}
-\begin{figure}
-  \begin{minipage}{0.8\linewidth}
+
+\begin{figure}[h]
     \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
@@
 \end{lstlisting}\caption{A vulnerable password checker.}\label{fig:chapter4:pwcheck1}
-  \end{minipage}
-  \vfill
-  \begin{minipage}{0.8\linewidth}
+\end{figure}
+
+\begin{figure}[h]
     \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.00\textwidth, frame=none]
@@
 \end{lstlisting}\caption{A safe password checker.}\label{fig:chapter4:pwcheck2}
-\end{minipage}
 \end{figure}

### 2021-06-17 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 \chapter{Introduction} \label{chapter1}
+Software is becoming increasingly complex today. Half a century ago, the Appollo 11's flight software was done with around 100,000 lines of code. 
+Today, a mobile application such as Telegram contains more than 2,000,000 lines of code. It is estimated that engineers built Google's infrastructure with 2 billion lines of code.
+
 \section{Side-channels}
@@
 Chapter~\ref{chapter5} extends the approach and quantifies the side-channel leakage in a multiple-trace attack.
-Chapter~\ref{chapter6} and Chapter~\ref{chapter7} discuss limitations and future work.
+Chapter~\ref{chapter6} and Chapter~\ref{chapter7} discuss limitations and future work of the dissertation research.

### 2021-06-17 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 \chapter{Introduction} \label{chapter1}
-Software is becoming increasingly complex today. Half a century ago, the Appollo 11's flight software was done with around 100,000 lines of code. 
-Today, a mobile application such as Telegram contains more than 2,000,000 lines of code. It is estimated that engineers built Google's infrastructure with 2 billion lines of code.
+Software is becoming increasingly complex today. Half a century ago, the Appollo 11's flight software~\cite{hamilton19690apollo} was done with around 100,000 lines of code. 
+Today, a mobile application such as Telegram~\cite{telegram} contains more than 2,000,000 lines of code.
+It is estimated that engineers built Google's infrastructure with 2 billion lines of code~\cite{potvin2016google}.
+The complexity in today's software systems makes it hard for software developers to understand the codebase and find defects manually.
+So an automated bug detection tool is often needed.
+In this dissertation, we present techniques to analyze side-channel vulnerabilities in real-world applications.
+The side-channel vulnerability is a type of information leakage bug in software systems.
+Unlike many ordinary bugs, attackers can exploit the side-channel vulnerability from the implementation of the software with various methods rather than the weaknesses of the software.
 

### 2021-06-17 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 The side-channel vulnerability is a type of information leakage bug in software systems.
-Unlike many ordinary bugs, attackers can exploit the side-channel vulnerability from the implementation of the software with various methods rather than the weaknesses of the software.
+Unlike many ordinary bugs, attackers can exploit the side-channel vulnerability from the implementation of the software with various different methods rather than the weaknesses of the software.
+SO it is sometimes harder for developers to reason about these vulnerabilities.
 

### 2021-06-17 Chapter-1/Chapter-1.tex
Updates from Overleaf

--- 2021-06-17 Chapter-1/Chapter-1.tex
@@
 The side-channel vulnerability is a type of information leakage bug in software systems.
-Unlike many ordinary bugs, attackers can exploit the side-channel vulnerability from the implementation of the software with various methods rather than the weaknesses of the software.
+Unlike many ordinary bugs, attackers can exploit side-channel vulnerabilities from the implementation of the software with various different methods rather than the weaknesses of the software.
+So it is sometimes harder for developers to reason about these vulnerabilities.
 

### 2021-06-17 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
     equation with regard to the size of $K_c$
-    $$|K_{c_t(\addr{1},\addr{2},\ldots,\addr{n})}| = |K_{g_{1}}|*|K_{g_{2}}|*\ldots*|K_{g_{n}}|$$
+    $$|K_{c_t(\addr{1},\addr{2},\ldots,\addr{n})}| = |K_{g_{1}}| \cdot |K_{g_{2}}| \cdot \ldots \cdot|K_{g_{n}}|$$
 \end{theorem}

### 2021-06-17 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 
-Our tool can give a conservative estimation of the
+\ctool{} can give a conservative estimation of the
 side-channel leakage based on Channel Capacity. The channel capacity
@@
 
+\section{Limitations}
+The methods in my dissertation cannot find all kinds of side-channel leakages. No
+tool can find all forms of leakages.
+Even for address-based side-channel leakages, \tool{} and \ctool{} cannot find all the leakages due to the code coverage problem.
+Some verification tools can prove the absence of side-channel leakages for some small code snippets.
+However, to the best of my knowledge, no tools as yet can prove the absence of side-channel leakages in production software.
+
+The quantification result only applies to specific threat models. For example,
+\tool{} quantifies the number of leaked bits during one real execution. So it is
+possible that one leakage site leaks little information in one execution but leaks much more information in another execution.
+
+The research in the dissertation can only handle address-based side-channel
+attacks. Many side-channel attacks infer secret data based on other side-channel
+signals (e.g., timing, EM signals).
+However, the root cause of many of these attacks is still the same.
+That is, the program accesses different addresses when it processes different input secrets.
+Under the circumstance, our methods can still detect these leakage sites.
+
 \ctool{} is a dynamic approach.

### 2021-06-17 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 \section{Limitations}
-The methods in my dissertation cannot find all kinds of side-channel leakages. No
-tool can find all forms of leakages.
+The dissertation research has a few limitations.
+
+\begin{enumerate}
+\item The methods in this dissertation cannot find all kinds of side-channel leakages.
+No tool can find all forms of leakages.
 Even for address-based side-channel leakages, \tool{} and \ctool{} cannot find all the leakages due to the code coverage problem.
@@
 However, to the best of my knowledge, no tools as yet can prove the absence of side-channel leakages in production software.
-
-The quantification result only applies to specific threat models. For example,
-\tool{} quantifies the number of leaked bits during one real execution. So it is
-possible that one leakage site leaks little information in one execution but leaks much more information in another execution.
-
-The research in the dissertation can only handle address-based side-channel
-attacks. Many side-channel attacks infer secret data based on other side-channel
-signals (e.g., timing, EM signals).
+\item The quantification result only applies to specific threat models.
+For example,\tool{} quantifies the number of leaked bits during one real execution.
+So it is possible that one leakage site leaks little information in one execution but leaks much more information in another execution.
+\item \tool{} and \ctool{} can only handle address-based side-channel attacks.
+Many side-channel attacks infer secret data based on other side-channel signals (e.g., timing, EM signals).
 However, the root cause of many of these attacks is still the same.
@@
 Under the circumstance, our methods can still detect these leakage sites.
-
-\ctool{} is a dynamic approach.
+\item \ctool{} is a dynamic approach.
 So it bears the same limitations of dynamic approaches as well.
@@
 However, users of \ctool{} should be aware of the code coverage problem.
+\end{enumerate}

### 2021-06-17 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 \chapter{Introduction} \label{chapter1}
-Software is becoming increasingly complex today. Half a century ago, the Appollo 11's flight software~\cite{hamilton19690apollo} was done with around 100,000 lines of code. 
+Software is becoming increasingly complex nowadays. Half a century ago, the Appollo 11's flight system software~\cite{hamilton19690apollo} was done with around 100,000 lines of code. 
 Today, a mobile application such as Telegram~\cite{telegram} contains more than 2,000,000 lines of code.

### 2021-06-17 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 \chapter{Introduction} \label{chapter1}
-Software is becoming increasingly complex nowadays. Half a century ago, the Appollo 11's flight system software~\cite{hamilton19690apollo} was done with around 100,000 lines of code. 
-Today, a mobile application such as Telegram~\cite{telegram} contains more than 2,000,000 lines of code.
+Software is becoming increasingly complex nowadays. Half a century ago, the Appollo 11's flight system software~\cite{hamilton19690apollo} was done with around one hundred thousand lines of code. 
+Today, a mobile application such as Telegram~\cite{telegram} contains more than two millions lines of code.
 It is estimated that engineers built Google's infrastructure with 2 billion lines of code~\cite{potvin2016google}.

### 2021-06-17 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 Software is becoming increasingly complex nowadays. Half a century ago, the Appollo 11's flight system software~\cite{hamilton19690apollo} was done with around one hundred thousand lines of code. 
-Today, a mobile application such as Telegram~\cite{telegram} contains more than two millions lines of code.
+Today, a mobile instant messaging application such as Telegram~\cite{telegram} contains more than two millions lines of code.
 It is estimated that engineers built Google's infrastructure with 2 billion lines of code~\cite{potvin2016google}.
-The complexity in today's software systems makes it hard for software developers to understand the codebase and find defects manually.
+The complexity in today's software systems makes it hard for developers to understand the codebase and find defects manually.
 So an automated bug detection tool is often needed.

### 2021-06-18 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 Software is becoming increasingly complex nowadays. Half a century ago, the Appollo 11's flight system software~\cite{hamilton19690apollo} was done with around one hundred thousand lines of code. 
-Today, a mobile instant messaging application such as Telegram~\cite{telegram} contains more than two millions lines of code.
+Today, a mobile instant messaging application such as Telegram~\cite{telegram} contains more than two million lines of code.
 It is estimated that engineers built Google's infrastructure with 2 billion lines of code~\cite{potvin2016google}.
@@
 The side-channel vulnerability is a type of information leakage bug in software systems.
-Unlike many ordinary bugs, attackers can exploit side-channel vulnerabilities from the implementation of the software with various different methods rather than the weaknesses of the software.
-So it is sometimes harder for developers to reason about these vulnerabilities.
+Unlike many ordinary bugs, attackers exploit side-channel vulnerabilities from the implementation of the software rather than weaknesses in the implementation itself.
+So it is sometimes harder for developers to identify these vulnerabilities.
 

### 2021-06-18 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 For example, a control flow leakage happens when different secret inputs lead to different paths.
-Software developers can mitigate the leakage by executing both branches and select the result with bit-wise operations.
+Software developers can mitigate the leakage by executing both branches and select the result with bit-wise operations~\cite{Coppens:2009:PMT:1607723.1608124}.
 However, for exiting code base, it is hard to migrate all the code into a side-channel free implementation.
@@
 An attacker can launch an attack to retrieve the binding value to recover the secret input.
+
+\subsubsection{New Implementation}
+Recent work~\cite{bernstein2012security,libsodium} also proposes to design and implement clean-slate side-channel free software from scratch.
+
 \subsection{Hardware Countermeasures}

### 2021-06-18 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 \subsubsection{New Implementation}
-Recent work~\cite{bernstein2012security,libsodium} also proposes to design and implement clean-slate side-channel free software from scratch.
+Recent work~\cite{bernstein2012security,libsodium,zinzindohoue2017hacl} also proposes to design and implement clean-slate side-channel free software from scratch.
 

### 2021-06-18 Chapter-2/Chapter-2.tex
Updates from Overleaf

--- 2021-06-18 Chapter-2/Chapter-2.tex
@@
 \subsubsection{New Implementation}
-Recent work~\cite{bernstein2012security,libsodium} also proposes to design and implement clean-slate side-channel free software from scratch.
+Recent work~\cite{bernstein2012security,libsodium,zinzindohoue2017hacl,monocypher} also proposes to design and implement clean-slate side-channel free libraries from scratch.
+We notice that most of these new libraries are cryptographic.
 

### 2021-06-18 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 
-\subsubsection{New Implementation}
+\subsubsection*{New Implementation}
 Recent work~\cite{bernstein2012security,libsodium,zinzindohoue2017hacl,monocypher} also proposes to design and implement clean-slate side-channel free libraries from scratch.

### 2021-06-18 Chapter-2/Chapter-2.tex
Updates from Overleaf

--- 2021-06-18 Chapter-2/Chapter-2.tex
@@
 
-\subsubsection{New Implementation}
-Recent work~\cite{bernstein2012security,libsodium,zinzindohoue2017hacl} also proposes to design and implement clean-slate side-channel free software from scratch.
+\subsubsection*{New Implementation}
+Recent work~\cite{bernstein2012security,libsodium,zinzindohoue2017hacl,monocypher} proposes to design and implement clean-slate side-channel free libraries from scratch.
+Researchers~\cite{bernstein2008chacha,langley2016chacha20} also design new cryptographic algorithms (e.g., ChaCha20) that are resilient to cache side-channel attacks.
 

### 2021-06-18 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 Recent work~\cite{bernstein2012security,libsodium,zinzindohoue2017hacl,monocypher} proposes to design and implement clean-slate side-channel free libraries from scratch.
-Researchers~\cite{bernstein2008chacha,langley2016chacha20} also design new cryptographic algorithms (e.g., ChaCha20) that are resilient to cache side-channel attacks.
+Researchers~\cite{bernstein2008chacha,langley2016chacha20} also design new constant-time cryptographic algorithms (e.g., ChaCha20) to defend against timing side-channel attacks.
+Unfortunately, writing side-channel resistant cryptography code and validating the security property can be tedious and error-prone.
+Computer-aided cryptography~\cite{barbosa2021sok} is proposed to address the challenge, which compasses formal verification methods to design, analyze and implement the cryptography libraries.
+Formal verification on side-channel leakages start with a leakage model, which abstract what an attacker can observe during an attack.
 

### 2021-06-18 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 Computer-aided cryptography~\cite{barbosa2021sok} is proposed to address the challenge, which compasses formal verification methods to design, analyze and implement the cryptography libraries.
-Formal verification on side-channel leakages start with a leakage model, which abstract what an attacker can observe during an attack.
+Formal verification on side-channel leakages starts with a leakage model, which abstracts what an attacker can observe during an attack.
+After defining a leakage model, the implementation is secure (under the leakage model) to side-channel attacks if and only if it can be proved that the observation is independent of the input secrets.
+The property is an example of non-interference or secure information flow.
 
@@
 In this dissertation, we propose side-channel analysis methods to address the problem.
-\section{Information Quantification}
+
+\section{Information Quantification}\label{sec:qif}
 Proposed by Denning~\cite{robling1982cryptography} and Gray~\cite{gray1992toward},

### 2021-06-18 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 After defining a leakage model, the implementation is secure (under the leakage model) to side-channel attacks if and only if it can be proved that the observation is independent of the input secrets.
-The property is an example of non-interference or secure information flow.
+The property is an example of \textit{noninterference} or \textit{secure information flow}.
+However, achieving noninterferecne for complex software is often impractical.
+Therefore, researchers also seek to access leakages (see Section~\ref{sec:qif}).
 

### 2021-06-18 Chapter-7/Chapter-7.tex
Updates from Overleaf

@@
 \section{Future Directions}
-There are a few potential directions the dissertation research.
+There are a few potential directions to extend the dissertation research.
 
@@
 Finally, with the tool presented in the dissertation, we can fix only part of the ``severe'' leakage sites.
+
+\textbf{Side-channel Leakage Quantification with A Noisy Observation.}It is possible to extend the quantification part to include other side-channel
+signals (e.g., sound, CPU usages, EM signals). The key is to model the noises
+properly. In my dissertation, we assume that an attacker can have a noise-free
+observation. While a noise-free observation is possible for some address-based
+side-channel attacks, the assumption is too ideal for many real side-channel
+attacks. The good news is that there are some mature methods in information theory to model noises (e.g., Gaussian noise). The noisy-channel coding theorem provides a
+computable method to estimate the information that can be reliably transferred over a channel between secret data and attackers' observations.

### 2021-06-18 Chapter-7/Chapter-7.tex
Updates from Overleaf

@@
 
-\textbf{Side-channel Leakage Quantification with A Noisy Observation.}It is possible to extend the quantification part to include other side-channel
+\textbf{Side-channel Leakage Quantification with A Noisy Observation.} It is possible to extend the quantification part to include other side-channel
 signals (e.g., sound, CPU usages, EM signals). The key is to model the noises

### 2021-06-18 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 The property is an example of \textit{noninterference} or \textit{secure information flow}.
-However, achieving noninterferecne for complex software is often impractical.
-Therefore, researchers also seek to access leakages (see Section~\ref{sec:qif}).
+However, achieving noninterferecne for complex software is often impractical and researchers also seek to compromised solutions such as quantitative information flow (see Section~\ref{sec:qif}).
 

### 2021-06-18 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
   \end{minipage}
-  \caption{A severe leakage.}\label{chapter5:fig:example1}
+  \caption{A severe side-channel leakage.}\label{chapter5:fig:example1}
 \end{figure}
@@
   \end{minipage}
-  \caption{A minor leakage. }\label{chapter5:fig:example2}
+  \caption{A minor side-channel leakage. }\label{chapter5:fig:example2}
 \end{figure}
@@
 
-\subsection{Step 3: Leakages Detection and Quantification}
+\subsection{Step 3: Leakage Detection and Quantification}
 In this step, we detect and quantify the side-channel leakage.

### 2021-06-18 Chapter-2/Chapter-2.tex
Updates from Overleaf

--- 2021-06-18 Chapter-2/Chapter-2.tex
@@
 Recent work~\cite{bernstein2012security,libsodium,zinzindohoue2017hacl,monocypher} proposes to design and implement clean-slate side-channel free libraries from scratch.
-Researchers~\cite{bernstein2008chacha,langley2016chacha20} also design new constant-time cryptographic algorithms (e.g., ChaCha20) to defend against timing side-channel attacks.
+Researchers~\cite{bernstein2008chacha,langley2016chacha20} design and implement new constant-time cryptographic algorithms (e.g., ChaCha20) to defend against timing side-channel attacks.
 Unfortunately, writing side-channel resistant cryptography code and validating the security property can be tedious and error-prone.
-Computer-aided cryptography~\cite{barbosa2021sok} is proposed to address the challenge, which compasses formal verification methods to design, analyze and implement the cryptography libraries.
+Computer-aided cryptography~\cite{barbosa2021sok} is proposed to address the challenge, which encompasses formal verification methods to design, analyze and implement the cryptography libraries.
 Formal verification on side-channel leakages starts with a leakage model, which abstracts what an attacker can observe during an attack.
-After defining a leakage model, the implementation is secure (under the leakage model) to side-channel attacks if and only if it can be proved that the observation is independent of the input secrets.
+After defining a leakage model, the implementation is secure (under the leakage model) to side-channel attacks if and only if it can be proved that observations are independent of the input secrets.
 The property is an example of \textit{noninterference} or \textit{secure information flow}.
-However, achieving noninterferecne for complex software is often impractical.
-Therefore, researchers also seek to access leakages (see Section~\ref{sec:qif}).
+However, achieving noninterferecne for real-world software is often impractical and researchers also seek to compromised solutions such as quantitative information flow (see Section~\ref{sec:qif}).
 

### 2021-06-18 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 \chapter{Introduction} \label{chapter1}
-Software is becoming increasingly complex nowadays. Half a century ago, the Appollo 11's flight system software~\cite{hamilton19690apollo} was done with around one hundred thousand lines of code. 
+Software is becoming increasingly complex nowadays. Half a century ago, the Appollo 11's flight system software~\cite{hamilton19690apollo} was done with less than one hundred thousand lines of code. 
 Today, a mobile instant messaging application such as Telegram~\cite{telegram} contains more than two million lines of code.
@@
 In this dissertation, we present techniques to analyze side-channel vulnerabilities in real-world applications.
-The side-channel vulnerability is a type of information leakage bug in software systems.
+The side-channel vulnerability is a type of information leakage bugs in software systems.
 Unlike many ordinary bugs, attackers exploit side-channel vulnerabilities from the implementation of the software rather than weaknesses in the implementation itself.

### 2021-06-18 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 uint8_t password = input();
-
 a = *password & 0b001;
@@
 c = (*password & 0b100) >> 2;
-
 na = ~a & 1;
@@
 nc = ~c & 1;
-
 t0 = (b & nc);
 t1 = (b | nc);
-
 l = (a & nb) | t0;
 r = (na & t1) | t0;
-
 ret = l << 1 + r;

### 2021-06-18 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 
+\ctool{} defines the amount of leaked information by the empirical entropy of the
+observations.
+For a determinism program, channel capacity is the tight upper bound of the entropy of the observation.
+The quantification result is always smaller than the channel capacity and can approximate the value of the channel capacity in some cases.
 \ctool{} can give a conservative estimation of the
@@
 affected by the input, which is useful because we cannot
-assume the input secrets of the software in practice. In Chapter~\ref{chapter5}, we
-use the sampling result to approximate the true value of the
-channel capacity. We prove the sampling method presented in the chapter can only give the conservative estimation of the amount of the true leakage.
+assume the input secrets of the software in practice. In Chapter~\ref{chapter5}, we use the sampling result to approximate the true value of the
+channel capacity. We show that the sampling method presented in the chapter can only give the conservative estimation of the amount of the true leakage.
 

### 2021-06-18 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 Some leakage sites (e.g., square and multiply in RSA)
-can leak one particular bit of the original key, but some leakage sites leak one bit
-from several bytes in the original key. \tool{} can capture the dependency among the leaks and
-reports more precise leakage information.
+can leak one particular bit of the original key, but some leakage sites leak one bit from several bytes in the original key.
+\tool{} can capture the dependency among the leaks and reports more precise leakage information.
 
@@
 
-\begin{enumerate}
-\item The methods in this dissertation cannot find all kinds of side-channel leakages.
+The methods in this dissertation cannot find all kinds of side-channel leakages.
 No tool can find all forms of leakages.
@@
 However, to the best of my knowledge, no tools as yet can prove the absence of side-channel leakages in production software.
-\item The quantification result only applies to specific threat models.
+
+The quantification result only applies to specific threat models.
 For example,\tool{} quantifies the number of leaked bits during one real execution.
@@
 Under the circumstance, our methods can still detect these leakage sites.
-\item \ctool{} is a dynamic approach.
+
+\ctool{} is a dynamic approach.
 So it bears the same limitations of dynamic approaches as well.
@@
 However, users of \ctool{} should be aware of the code coverage problem.
-\end{enumerate}

### 2021-06-18 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 The property is an example of \textit{noninterference} or \textit{secure information flow}.
+Eldib et al.~\cite{eldib2014smt} propose using a SMT solver based method to formally verifying masked implementations.
+Bayrak et al.~\cite{bayrak2013sleuth} verify power-based side-channel countermeasures.
 However, achieving noninterferecne for real-world software is often impractical and researchers also seek to compromised solutions such as quantitative information flow (see Section~\ref{sec:qif}).
@@
 Researchers proposed different methods to partition the LLC such as cache coloring~\cite{shi2011limiting}, using Intel Cache Allocation Technology~\cite{liu2016catalyst}.
+Recent work also uses machine checkable methods to verify side-channel resistance in hardware~\cite{Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,236334}.
 \subsubsection*{Randomization}

### 2021-06-18 Chapter-7/Chapter-7.tex
Updates from Overleaf

--- 2021-06-18 Chapter-7/Chapter-7.tex
@@
 
-\textbf{Side-channel Leakage Quantification with A Noisy Observation.}It is possible to extend the quantification part to include other side-channel
+\textbf{Side-channel Leakage Quantification from Noisy Observations.} It is possible to extend the quantification part to include other side-channel
 signals (e.g., sound, CPU usages, EM signals). The key is to model the noises

### 2021-06-18 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 these tools cannot report to software developers how severe each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage. 
-Often the over-approximated estimate is very far away from the amount of real leakage.
 For example, CacheAudit~\cite{182946} estimates that a 128-bit
@@
 
-\subsection{Step 2: Address Record}
+\subsection{Step 2: Address Recording}
 Next, we record the memory access information based on the input

### 2021-06-19 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 Software is becoming increasingly complex nowadays. Half a century ago, the Appollo 11's flight system software~\cite{hamilton19690apollo} was done with less than one hundred thousand lines of code. 
-Today, a mobile instant messaging application such as Telegram~\cite{telegram} contains more than two million lines of code.
+Today, a mobile instant messaging (IM) application such as Telegram~\cite{telegram} contains more than two million lines of code.
 It is estimated that engineers built Google's infrastructure with 2 billion lines of code~\cite{potvin2016google}.
@@
 Unlike many ordinary bugs, attackers exploit side-channel vulnerabilities from the implementation of the software rather than weaknesses in the implementation itself.
-So it is sometimes harder for developers to identify these vulnerabilities.
+So it is sometimes harder for developers to identify side-channel vulnerabilities.
 

### 2021-06-19 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 An attacker can probe the shared hardware resource to infer the memory accesses of the victim.
-While the root cause of the attack is the same, there are many approaches, and an attacker can exploit side-channel leakage sites in different methods to retrieve the information at different granularities.
+While the root cause of the attack is the same, an attacker can exploit side-channel leakage sites in different methods to retrieve the information at different granularities.
 
@@
 Eldib et al.~\cite{eldib2014smt} propose using a SMT solver based method to formally verifying masked implementations.
-Bayrak et al.~\cite{bayrak2013sleuth} verify power-based side-channel countermeasures.
+Bayrak et al.~\cite{bayrak2013sleuth} verify power-based side-channel countermeasures by transferring the verification problem into a set of Boolean satisfiability problems.
 However, achieving noninterferecne for real-world software is often impractical and researchers also seek to compromised solutions such as quantitative information flow (see Section~\ref{sec:qif}).

### 2021-06-19 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 Cache channel attacks can observe cache accesses at the level of cache sets, cache lines or other granularities.
-We introduce two common attack strategies, namely Prime+Probe and Flush+Reload.
+We introduce two common attack strategies, namely Prime+Probe~\cite{liu2015last}  and Flush+Reload~\cite{yarom2014flush+}.
 
@@
 Then the attacker probes the cache by reading previously loaded data.
-If the victim accesses the cache set and evicts some lines of the data, the attacker will experience a slow measurement.
-Under the circumstance, the attacker can know that the victim must have touched some data that map to the same cache set.
+If the victim accesses the cache set and evicts the data loaded by the attacker, the attacker will experience a slow measurement.
+Under the circumstance, the attacker can know that the victim must have touched some data that maps to the same cache set.
 

### 2021-06-19 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 memory'' from the cache and waits for the victim to access the memory, which may be a load of the sensitive information to the cache line.  In the next phase,
-the attacker reloads the ``monitored memory''. The attacker's process read all data in the `monitored
-memory''. If the time is relatively fast, it indicate that the data has been accessed by the victim program and the cache has loaded the data. 
+the attacker reloads the ``monitored memory''. The attacker's process reads all data in the `monitored
+memory''. If the time is relatively fast, it indicates that the data has been accessed by the victim program and the cache has loaded the data. 
 On X86-64 machines, the two steps can be combined by measuring the time differences of the \textsf{clflush} instruction.
 
-Based on the above attacks, some work~\cite{brickell2011technologies} suggests having secret-dependent memory accesses at finer than the size of one cache line should be secure enough.
+Based on the above attacks, some work~\cite{brickell2011technologies} suggests ensuring secret-dependent memory accesses within the size of one cache line should be secure enough.
 However, recent studies show that having different memory accesses within a cache line is also dangerous.

### 2021-06-19 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 \subsection{Page-level Channel}
-Page channel attacks allow an attacker can observe the memory access at the granularity of memory pages.
+Page channel attacks allow an attacker to observe the memory access at the granularity of memory pages.
 One example is the controlled-channel attack~\cite{xu2015controlled}.
@@
 A malicious OS can proactively revoke a virtual enclave memory page from the virtual memory.
-If the victim enclave program accesses the memory in the  page, then the OS can observe the page faults and know which page is accessed.
+If the victim enclave program accesses the memory in the  page, then the OS can observe the page faults and know pages that are accessed.
 While the granularity of controlled-channel attacks is more coarse-grained compared with cache channel attacks, controlled-channel attacks allow the attacker to have a noise-free observation.
-Other examples such as TLB side-channel attacks and DDRAM attacks share the same page-level granularity.
+Other examples such as TLB side-channel attacks~\cite{gras_translation_2018} and DDRAM attacks~\cite{gruss2019page} share the same page-level granularity.
 

### 2021-06-19 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 \subsubsection*{Timing-based Attacks}
-In timing-based attacks, an adversary can measure and compare the execution time of victim programs.
+In timing-based attacks, an adversary measures and compares the execution time of victim programs.
 It could be the overall execution time or the execution time of some interesting components (e.g., a function).
@@
 \subsubsection*{Access-based Attacks}
-In access-based attacks, an adversary can learn the memory addresses that are accessed during the execution after the termination of the victim program. 
+In access-based attacks, an adversary can learn the memory addresses that are accessed during the execution after the termination of a victim program. 
 For example, a cache-based channel attack can know which memory access incurs a cache hit and which memory access incurs a cache miss to infer addresses that the victim program accesses.
-Since the attacker can probe the victim program after the execution, the attacker does not know the order of memory accesses.
+Since the attacker probes the victim program after the execution, the attacker does not know the order of memory accesses.
 Access-based attacks often happen in the cloud computing environment when the attacker and victim share the same hardware (e.g., LLC cache).
@@
 Suppose the victim program has two functions \textsf{a} and \textsf{b}.
-In an access-based attacks, the attacker can only learn both \textsf{a} and \textsf{b} are executed.
+In an access-based attack, the attacker can only learn both \textsf{a} and \textsf{b} are executed.
 In a trace-based attack, the attacker can know the execution sequence of two functions (e.g., $\mathtt{aabbb}$).
-Controlled-channel attacks~\cite{moghimi2020copycat, xu2015controlled} belong to this category where a malicious operating system can interrupt the victim application and probe the program at any time.
-In general, the trace-based attack has the strongest assumption about the threat model,  but it can retrieve more information compared to the other two types of attacks.
+Controlled-channel attacks~\cite{moghimi2020copycat, xu2015controlled} belong to this category where a malicious operating system interrupts the victim application and probes the program at any time.
+In general, the trace-based attack has the strongest assumption about the threat model,  but it can also retrieve more information compared to the other two types of attacks.
 \subsection{Target Applications}
@@
 The first side-channel attack on cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996.
-It exploits the simple modular exponentiation algorithm function in many cryptography (Diffie-Hellman, RSA) implementations.
+It exploits a simple modular exponentiation algorithm function in many cryptography (Diffie-Hellman, RSA) implementations.
 The function does not run in a fixed time.
-By measuring the time differences between the modular exponentiation algorithm computes the exponent bits (0 or 1), Kocher's attack can recover the whole secret key bit by bit.
+By measuring the timing differences between the modular exponentiation algorithm computes exponent bits (0 or 1), Kocher's attack can recover the whole secret key bit by bit.
 Since then, researchers start to break all kinds of cipher implementation through side-channel attacks.
@@
 It is hard to implement these calculations to be completely side-channel resistant.
-Recent work~\cite{arnaud2013timing,yarom2017cachebleed,yarom2014flush+} has demonstrated several end-to-end attacks to recover the private key of these ciphers.
+Recent work~\cite{arnaud2013timing,yarom2017cachebleed,yarom2014flush+} demonstrated several end-to-end attacks to recover the private key of these ciphers.
 
@@
 Hua et al.~\cite{hua2018reverse} were the first in the literature to reverse engineer the architecture of convolutional neural networks (CNNs) through the memory access patterns.
-Wei et al.~\cite{wei2018know} perform the side-channel attacks on an FPG-based convolution neural network by using the power consumption to recover inputs to the networks.
+Wei et al.~\cite{wei2018know} perform side-channel attacks on an FPG-based convolution neural network by using the power consumption to recover inputs to the networks.
 For an image classification task trained by the MNIST dataset, their attacks can achieve up to 89\% accuracy.
@@
 Cache Telepathy~\cite{yan2020cache} introduces the cache-based side-channel attack to extract DNNs' architectures.
-We find that all existing approaches need a lot of domain knowledge and expertise to launch the attacks.
+We find that all existing approaches need a lot of domain knowledge and expertise to launch side-channel attacks.
 
 \subsubsection*{Media and Graphic Libraries}
-Recent work also studies the side-channel attacks in media and graphic libraries.
+Recent work also studies side-channel attacks in media and graphic libraries.
 Gruss et at.~\cite{191010} show an attack that can infer keystrokes by exploiting secret-dependent memory accesses in the GDK library.
-In the controlled-channel attack~\cite{xu2015controlled}, Yuanzhong et al.
+In the controlled-channel attack~\cite{xu2015controlled}, Xu et al.
 demonstrate an attack to recover the outline of an image by exploiting the vulnerability in the inverse DCT function in libjpeg.
-Daimeng et al.~\cite{wang2019unveiling} present a cache attack on graphic libraries.
-Their approaches uses a machine learning approach to pick cache lines that can be exploited to leak the most information.
+Wang et al.~\cite{wang2019unveiling} present a cache attack on graphic libraries.
+Their approaches use a machine learning approach to pick cache lines that can be exploited to leak the most information.
 \subsubsection*{Others}

### 2021-06-19 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 In the controlled-channel attack~\cite{xu2015controlled}, Xu et al.
-demonstrate an attack to recover the outline of an image by exploiting the vulnerability in the inverse DCT function in libjpeg.
+demonstrate an attack to recover the outline of an image by exploiting vulnerabilities in the inverse DCT function in libjpeg.
 Wang et al.~\cite{wang2019unveiling} present a cache attack on graphic libraries.
 Their approaches use a machine learning approach to pick cache lines that can be exploited to leak the most information.
+
 \subsubsection*{Others}
@@
 After that, they detect kernel modules with unique size signatures to break KASLR.
-The second example relies on the side-channel vulnerabilities~\cite{cao2019principled} inside kernels to infer the TCP sequence numbers, which can be used by a third party to hijack connections between the client and the server~\cite{cao2016off}.
+The second example relies on the kernel space side-channel vulnerabilities~\cite{cao2019principled} to infer TCP sequence numbers, which can be used by a third party to hijack connections between a client and a server~\cite{cao2016off}.
 
@@
 usually easy to implement. Coppens et
-al.~\cite{Coppens:2009:PMT:1607723.1608124} use a compiler
+al.~\cite{Coppens:2009:PMT:1607723.1608124} develop a compiler extension
 to eliminate key-dependent control-flow transfers. Crane et
@@
 
-\textbf{Trace comparison.} If a program has two different execution traces under two different sensitive inputs, then attackers can distinguish the sensitive input by observing the execution traces.
+\textbf{Trace comparison.} If a program has two different execution traces under two different sensitive inputs, then attackers can distinguish the two inputs by observing the execution traces.
 Therefore, we can conclude the program is vulnerable to side-channel attacks.
@@
 However, non-linear arithmetics are quite common in cryptography algorithms.
-Recent studies show existing solvers still have bugs when dealing with real number calculations.
+Recent studies show existing solvers still have bugs when dealing with floating number calculations.
 These calculations are also common in media libraries and machine learning applications.

### 2021-06-19 Chapter-2/Chapter-2.tex
Updates from Overleaf

@@
 
-According to Table~\ref{table:side_channel_detection_tool}, some methods may choose to analyze the source code or the intermediate representations of the vulnerable software.
-However, it still cannot solve the problem.
-First, many widely-used libraries (e.g., Intel MKL) do not provide source code.
-Second, some libraries use hard-coded assembly code to pursue maximum performance.
+Table~\ref{table:side_channel_detection_tool} covers some representations of existing side-channel leakage detection tools. 
 CacheAudit~\cite{182946} uses abstract domains to compute an
@@
 CaSym can work on two threat models: trace-based attacks and access-based attacks.
-Again, their
+Similarly, their
 approaches cannot evaluate the sensitive level for each side-channel vulnerability, and it only works on small code snippets.
@@
 Developers can use a random value to blend the secret key but still generate the same encrypted data with a carefully designed algorithm.
-Binding values can alter the program execution to some unpredictable states and introduce the randomization to the execution.
+Binding values alters the program execution to some unpredictable states and introduce the randomization to the execution.
 However, the binding value can also be retrieved by an attacker through other methods, including side-channel attacks.
@@
 Researchers~\cite{bernstein2008chacha,langley2016chacha20} design and implement new constant-time cryptographic algorithms (e.g., ChaCha20) to defend against timing side-channel attacks.
-Unfortunately, writing side-channel resistant cryptography code and validating the security property can be tedious and error-prone.
+Unfortunately, writing side-channel resistant cryptography code and validating the security property using pen-and-paper arguments can be tedious and error-prone.
 Computer-aided cryptography~\cite{barbosa2021sok} is proposed to address the challenge, which encompasses formal verification methods to design, analyze and implement the cryptography libraries.
-Formal verification on side-channel leakages starts with a leakage model, which abstracts what an attacker can observe during an attack.
+Formal verification on side-channel leakages starts with defining a leakage model, which abstracts what an attacker can observe during an attack.
 After defining a leakage model, the implementation is secure (under the leakage model) to side-channel attacks if and only if it can be proved that observations are independent of the input secrets.
@@
 Side-channel attacks usually require attackers and victims to share some hardware resources (e.g., CPU cache, MMU).
-A straightforward way to defend these attacks is to partition the resources and ensure the attacker and the victim never share the same hardware resource~\cite{Page2005PartitionedCA,shi2011limiting,liu2016catalyst}.
+A way to defend these attacks is to partition the resources and ensure the attacker and the victim never share the same hardware resource~\cite{Page2005PartitionedCA,shi2011limiting,liu2016catalyst}.
 For example, in a cloud computing environment, several virtual machines (VMs) can be hosted on the same physical machine and these VMs share the same last-level cache (LLC).
@@
 For example, Random Permutation Cache ~\cite{wang2007new} uses a dynamically randomized memory to cache mapping table for each different process.
-Vattikonda et al.~\cite{vattikonda2011eliminating} add noises to the result of the system timer to mitigate timing-based channels.
+Vattikonda et al.~\cite{vattikonda2011eliminating} add noises to the result of the system timer to mitigate timing side-channel attacks.
 
@@
 In general, hardware countermeasures usually require new hardware designs and are harder to adopt in practice.
-In addition, some hardware methods (e.g., Oblivious RAM) may introduce expensive computation overhead.
+In addition, some hardware methods (e.g., Oblivious RAM~\cite{fletchery2014suppressing}) may introduce expensive computation overhead.
 Therefore, many practical solutions are still software countermeasures.
-However, software methods are not very general, and it is hard to find many side-channel leakages in large code bases manually.
+However, software methods are not very general, and it is hard to identify many side-channel leakages in large software manually.
 In this dissertation, we propose side-channel analysis methods to address the problem.
@@
 Proposed by Denning~\cite{robling1982cryptography} and Gray~\cite{gray1992toward},
-Quantitative Information Flow (QIF) aims to provide an estimation of the amount of leaked information from the sensitive information given the public output. If zero bits
-of the information are leaked, the program is called non-interference. 
+Quantitative Information Flow (QIF) aims to provide an estimation of the amount of leaked information from the sensitive information given the public output. 
 McCamant and Ernst~\cite{McCamantE2008} quantify the information leakage as the network
-flow capacity. They model the possible information leakage as a network of limited-capacity
+flow capacity. They model possible information leakage as a network of limited-capacity
 channel. After that, they use the maximum rate of the channel to represent the amount of secret information that the execution can reveal.
@@
 Phan et al.~\cite{Phan:2012:SQI:2382756.2382791} propose symbolic QIF. The goal of their
-work is to ensure a program is non-interference. They adopt an over-approximation method to estimate the total information leakage, and their method
+work is to ensure a program is \textit{noninterference}. They adopt an over-approximation method to estimate the total information leakage, and their method
 does not work for secret-dependent memory access side-channels.
@@
 It symbolically reasons about cache
-behavior and estimates the amount of leaked information based on cache miss/hit.
+behaviors and estimates the amount of leaked information based on cache miss/hit.
 Their approach only scales to small programs, which limits its usage in
@@
 approaches often rely on binary instrumentation frameworks or emulators (e.g., Intel Pin~\cite{luk2005pin},
-Valgrind~\cite{nethercote2007valgrind}, and QEMU). The second step to analyze the trace using techniques, such
+Valgrind~\cite{nethercote2007valgrind}, and QEMU~\cite{bellard2005qemu}). The second step to analyze the trace using techniques such
 as symbolic execution and taint analysis. Depending on when the analysis is launched,
-there are two kinds of trace-based analysis, online analysis and offline analysis.
+there are two kinds of approaches, online analysis and offline analysis.
 As the name suggests, online analysis is performed during the program execution.
-The target program's data can be modified directly in memory, which is useful to tasks like fuzzing because the analysis
+The target program's data can be modified directly in memory, which is useful to tasks such as fuzzing because the analysis
 can force the program to execute a specific branch. 
 Offline analysis or post-analysis happens after the program finishes executions. 
-Trace-based binary analysis has been adopted in several tasks like algorithm
+Trace-based binary analysis has been adopted in several tasks such as algorithm
 detection, vulnerability detection, and malware analysis. We only mention a few of
-the most related works here. Xu et al.~\cite{xu2017cryptographic} introduce bitwise symbolic execution, which can
-identify crypto algorithms in obfuscated binaries. Ming et al.~\cite{ming2017binsim} use system call sliced segment equivalence checking to do binary diffing. Jia et al.~\cite{jia2017towards}
-perform an offline analysis on execution traces to identify heap overflows.
+the most related works here. Xu et al.~\cite{xu2017cryptographic} introduce bitwise symbolic execution, which 
+detects crypto algorithms in obfuscated binaries.
+Ming et al.~\cite{ming2017binsim} use the method called sliced segment equivalence checking to do binary diffing.
+Jia et al.~\cite{jia2017towards} perform an offline analysis on execution traces to identify heap overflows.
 
-There are several known binary analysis frameworks that can help users to launch analysis on binary executables.
+There are several well-known binary analysis frameworks that can help users to perform analysis on binary executables.
 BitBlaze~\cite{brumley2011bap} is a binary analysis platform that provides both static and dynamic analysis.
@@
 Binary Analysis Platform (BAP)~\cite{10.1007/978-3-642-22110-1_37}
-is another binary analysis platform. Similar to BitBlaze, it uses a Pintrace tool to
-collect execution traces and convert the trace into BAP IR. Angr~\cite{shoshitaishvili2016state}, the most popular
-binary analysis platform recently, also supports trace-based analysis. It converts each instruction into VEX IR and interprets each IR in Python.
+is another binary analysis platform. Similar to BitBlaze, it uses a pintrace tool to
+collect execution traces and convert the trace into BAP IRs. Angr~\cite{shoshitaishvili2016state}, the most popular
+binary analysis platform recently, also supports trace-based analysis. It converts X86 instructions into VEX IRs and interprets each IR in Python.
 
-The above existing well-known binary analysis frameworks adopt the IR layer, which makes it easy to implement the analysis and support multiple architectures.
+All above binary analysis frameworks adopt IR layers, which makes it easy to implement the analysis and support multiple architectures.
 However, it can have very low efficiency and long traces.
-All IR must be interpreted no matter if symbolic variables are involved or not.
+All IRs must be interpreted no matter symbolic variables are involved or not.
 As side-channels are low-level problems in general, the IR will lose some information.

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 Among them, software side-channel attacks, such as cache attacks, memory page attacks, and controlled-channel attacks, are especially problematic as they do not require physical proximity~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}.
-These attacks arise from shared micro-architectural components in a computer processor.
+These attacks arise from shared micro-architectural components in computer architectures.
 By observing inadvertent interactions between two programs, attackers can infer program execution flows that manipulate secrets and guess secrets such as encryption keys~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.
@@
 Existing countermeasures can be classified into two categories: fixing the software and adopting new hardware.
-Based on the discussion in \S\ref{chapter1} and \S\ref{chapter2}, fixing side-channel leakage sites in software is usually easier than adopting new hardware to defend against side-channel attacks.
-In order to eliminate these leakage sites, developers need to find potential leakage sites in a large code base.
+Based on the discussion in Chapter~\ref{chapter1} and Chapter~\ref{chapter2}, fixing side-channel leakage sites in software is usually easier than adopting new hardware to defend against side-channel attacks.
+In order to eliminate these leakage sites, developers need to find potential leakage sites in a large codebase.
 However, the manual process is tedious and error-prone.
-Recent work~\cite{203878} also suggests fixing old vulnerabilities can sometimes introduce new leakages.
+Recent work~\cite{203878} also shows fixing old vulnerabilities can sometimes introduce new leakages.
 

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 Besides, compiler optimizations can eliminate the IR-level branches with conditional moves, and the converse could also happen.
-Moreover, translating the machine code into IRs can cause a significant overhead for the trace analysis, as we will discuss in the dissertation.
+Moreover, translating the machine code into IRs causes a significant overhead for the trace analysis, as we will discuss in the dissertation.
 
@@
 During the evolution of the computer architecture, researchers found that CPUs process data much faster than the main memory (DRAM) can supply.
-As a result, CPUs adopted a hierarchy memory architecture to bridge the performance gap between the CPUs and the main memory.
-By storing extra copies of recently accessed data and code in a smaller but faster memory, the software can get its most recently accessed code and data in a shorter time.
+As a result, CPUs adopted a hierarchy memory architecture to bridge the performance gap between the CPU and the main memory.
+By caching extra copies of recently accessed data and code in a smaller but faster memory, the software can get its most recently accessed code and data in a shorter time.
 

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 As a result, CPUs adopted a hierarchy memory architecture to bridge the performance gap between the CPU and the main memory.
-By caching extra copies of recently accessed data and code in a smaller but faster memory, the software can get its most recently accessed code and data in a shorter time.
+By caching extra copies of recently accessed data and code in a smaller but faster memory, the CPU can get its most recently accessed code and data in a shorter time.
 

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 Figure~\ref{fig:memory_hierarchy} shows the overview of one example of the hierarchy memory architecture.
-For a CPU with multiple cores, each core has two private level-1 (L1) cache, an instruction cache (iCache), and a data cache (dCache).
-Because instructions and data have different access patterns, separating iCache and dCache makes it possible for CPUs to fetch the code and data simultaneously and improve performance.
+For a CPU with multiple cores, each core has two private level-1 (L1) cache: an instruction cache (iCache), and a data cache (dCache).
+Because instructions and data have different access patterns, separating iCache and dCache makes it possible for CPUs to fetch the code and data simultaneously and improve the performance.
 Followed by the level-1 cache, each core also has the unified, private level-2 cache for both the code and the data.

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 Followed by the level-1 cache, each core also has the unified, private level-2 cache for both the code and the data.
-The level-3 cache is the last level cache (LLC).
-The LLC is shared among all the cores.
+The level-3 cache is also called the last level cache (LLC).
+The LLC is shared among all CPU cores within a CPU package.
 The main memory is at the bottom of the memory hierarchy.
@@
   \includegraphics[width=.65\columnwidth]{./figures/chapter3/architecture.pdf}
-  \caption{Computer memory hierarchy.
-The hierarchy is designed to minimise the access time with the relatively low cost.
-It is the root cause of many side-channel attacks.}\label{fig:memory_hierarchy}
+  \caption{Computer memory hierarchy. The hierarchy is designed to minimise the access time with a relatively low cost. It is the root cause of many side-channel attacks.}\label{fig:memory_hierarchy}
 \end{figure}

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 Given an address, the CPU uses the \textsf{Index} field of the address to locate the cache set that the address should reside in.
-After that, it tries to use the \textsf{Tag} field to match every cache line inside the set line.
+After that, it uses the \textsf{Tag} field to match every cache line inside the set line.
 If the CPU can locate a cache line with the same tag and the valid bit is set, then a cache hit occurs.
-The CPUs use a similar process to manage the main memory.
+The CPU uses a similar process to manage the main memory.
 The main memory is divided into many units called pages.

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 As shown in Figure~\ref{fig:memory_address},
-the translation process keeps the bottom bits same while using the top bits to map the Physical Page Numbers to Virtual Page Numbers.
+the translation process keeps the bottom bits same while using the top bits to map the Physical Page Numbers (PPN) to Virtual Page Numbers (VPN).
 

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \begin{enumerate}
-  \item A host machine has several virtual machines (VMs). The victim runs the application inside one VM. An attacker can control one VM and probe the process running on the other VM.
+  \item A host machine has several virtual machines (VMs). The victim runs the application inside one VM. An attacker can control a different VM and probe the process running on other VMs.
   \item  In a shielding system~\cite{arnautov2016scone,schuster2015vc3}, a malicious operating system can extract sensitive information from protected user-level applications.
-  \item A ring-3 application can probe some sensitive information inside the kernel.
+  \item A ring-3 application can infer some sensitive information inside the kernel.
 \end{enumerate}

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 However, in this research, we assume the attacker has noise-free observations as in previous work~\cite{203878,182946,Brotzman19Casym}.
-The threat model captures most address-based side-channel attacks and apply to the three attack models: 1) time-based attacks, 2) access-based attacks, 3) trace-based attacks.
+The threat model captures most address-based side-channel attacks and applies to the three attack: 1) time-based attacks, 2) access-based attacks, 3) trace-based attacks.
 We only consider deterministic programs and assume an attacker has access to the source code or binary executable of the target program.

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 We refer them as \textit{secret-dependent control flow transfers} and \textit{secret-dependent data accesses}.
-Unlike previous work, our tool works on the machine code, which is more precise than previous tools that work on the source code or the intermediate representation.
+Unlike previous work, our tool works on the machine code, which is more precise than previous tools that analyze the source code or the intermediate representation.
 \subsubsection{Control Flow}

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 It has a conditional jump instruction \textsf{jne}.
-The sensitive input \textsf{k} can affect the program counter (the \textsf{rip} register), which is the root cause of the side-channel leakages.
+The sensitive input \textsf{k} can affect the program counter (the \textsf{rip} register), which is the root cause of the side-channel leakage here.
 
-However, the if-else branch does not always indicate there is a potential leakage site.
+However, a if-else branch does not always indicate there is a potential leakage site.
 Figure~\ref{fig:chapter3:cf}(b) shows a different situation.
@@
 For example, recent work tries to use bit masking to rewrite the program with control flows.
-However, for some situations~\cite{Coppens:2009:PMT:1607723.1608124}, compilers (e.g., GCC) optimize the code too much (from a security view) and remove the unnecessary copy by reintroducing conditional moves.
+However, for some situations~\cite{Coppens:2009:PMT:1607723.1608124}, compilers (e.g., GCC) optimize the code too much (from a security view) and remove the unnecessary copy by reintroducing conditional jump instructions.
 \subsubsection{Data Flow}

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \end{lstlisting}
-  \end{minipage}\caption*{(a) A False Negative}
+  \end{minipage}\caption*{(a) A false negative}
 
@@
 \end{lstlisting}
-  \end{minipage}\caption*{(b) A False Positive}
+  \end{minipage}\caption*{(b) A false positive}
   \caption{Secret-dependent control-flow transfers}\label{fig:chapter3:cf}
@@
 \end{lstlisting}
-  \end{minipage}\caption*{(a) A True Leakage}
+  \end{minipage}\caption*{(a) A true leakage}
 
@@
 \end{lstlisting}
-  \end{minipage}\caption*{(b) A False Positive}
+  \end{minipage}\caption*{(b) A false positive}
   \caption{Secret-dependent data accesses}\label{fig:chapter3:da}
@@
 So the total size of the array is 128 bytes.
-Suppose an attacker can observe the memory access at the granularity of one cache lines (64 Bytes), then it is not possible to hold all the data inside the one cache line.
+Suppose an attacker can observe the memory access at the granularity of one cache lines (64 bytes), then it is not possible to hold all the data inside the one cache line.
 An attacker can get some information of the value \textsf{secret} in Figure~\ref{fig:chapter3:da}(a) by observing the cache line access.

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 Another bottleneck is that the IR.
-While the IR can significantly decrease the difficulty of the implementation, it also gives introduce an average of 10x of the overall overhead.
-Third, using SMT solving can be convenient because of its generality, and it is commonly used for its precision when checking branch feasibility in symbolic execution.
+While the IR can significantly decrease the difficulty of the implementation, it also introduces an average of 10x of the overall overhead.
+Third, using SMT solvers can be convenient because of its generality, and it is commonly used for its precision when checking branch feasibility in symbolic execution.
 But the decision problems that an SMT solver handles are typically at least NP-hard.

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 determined, $t_i$ is also fixed. Therefore, $ t_i = f_i(\beta, k, m)$, where $f_
-  i$ is a function that maps between $t_i$ and ($\beta$, $k$, $m$). In the chapter,
+  i$ is a function that maps between $t_i$ and ($\beta$, $k$, $m$). In this dissertation,
 we consider two code patterns that can be exploited by an attacker,
@@
 \subsection{Secret-dependent Control Transfers}
-A control-flow path is secret-dependent if different input-sensitive keys
-($K$) can lead to different branch conditions.
+A control-flow path is secret-dependent if there are two different input-sensitive keys
+($K$) that can lead to different branch conditions.
 We define a branch to be secret-dependent if
@@
 above definition, $m$ is also a variable. So it is possible for some $m \in M$,
-we cannot find a pair of two different $k_{i1}$ and $k_{i2}$ to satisfy the above inequation.
+we cannot find a pair of two different $k_{i1}$ and $k_{i2}$ satisfying the above inequation.
 For example, in Figure~\ref{fig:chapter3:cf}, if $m = \mathtt{0}$, the function \textsf{example1} will always execute the branch 2.

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 For example, in Figure~\ref{fig:chapter3:cf}, if $m = \mathtt{0}$, the function \textsf{example1} will always execute the branch 2.
-However, if $m = \mathtt{0xffffffff}$ and $k = \mathtt{0}$, the function \textsf{example1} executes the branch 1 and the function \textsf{example1} executes the branch 2 when $k = \mathtt{0xf000000}$.
+However, if $m = \mathtt{0xffffffff}$, the function \textsf{example1} executes the branch 1 when $k = \mathtt{0}$ and the function \textsf{example1} executes the branch 2 when $k = \mathtt{0xf000000}$.
 

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

--- 2021-06-19 Chapter-3/Chapter-3.tex
@@
 For example, in Figure~\ref{fig:chapter3:cf}, if $m = \mathtt{0}$, the function \textsf{example1} will always execute the branch 2.
-However, if $m = \mathtt{0xffffffff}$ and $k = \mathtt{0}$, the function \textsf{example1} executes the branch 1 and the function \textsf{example1} executes the branch 2 when $k = \mathtt{0xf000000}$.
+However, if $m = \mathtt{0xffffffff}$, the function \textsf{example1} executes the branch 1 when $k = \mathtt{0}$, and the function \textsf{example1} executes the branch 2 when $k = \mathtt{0xf000000}$.
 

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 Similar to secret-dependent control-flow transfers, a data access operation is
-secret-dependent if different input sensitive keys ($K$) cause access to different memory addresses.
+secret-dependent if different input sensitive keys ($K$) cause accesses to different memory addresses.
 We use the model from CacheD~\cite{203878}.

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 can lead to different execution behaviors using a constraint solver.
-We implement the approach presented in \S\ref{chapter3:method} and model the side-channels as formulas.
+We implement the approach presented in Section~\ref{chapter3:method} and model the side-channels as formulas.
 While the tools can analyze some simple cases such as AES, it cannot handle complicated examples such as RSA.
@@
 \subsection{Interpret Instructions Symbolically}
-Existing binary analysis frameworks~\cite{shoshitaishvili2016state,
+Current binary analysis frameworks~\cite{shoshitaishvili2016state,
   10.1007/978-3-642-22110-1_37, song2008bitblaze} translate machine instructions into

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 analysis because
-IR-based or source code side-channels analyses do not represent the executed instructions accurate enough to analyze fully their control and memory accesses.
+IR-based or source code side-channels analyses do not represent the executed instructions accurately enough to analyze fully their control and memory accesses.
 For example, a compiler may use conditional moves or bitwise operations to eliminate

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 For example, a compiler may use conditional moves or bitwise operations to eliminate
-branches. Also, as some IRs are not a superset or a subset of ISA,
+branches. Also, as IRs are not a superset or a subset of ISA,
 it is hard to rule out conditional jumps introduced by IR and add real branches

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 \textbf{Our Solution}
-We abandoned IR and expended the effort to implement
+We abandoned IR layers and expended the effort to implement
 symbolic execution directly on x86 instructions.
@@
 At the beginning of the symbolic execution, the tool creates new symbols for each byte in the raw buffer.
-For other data in the register or memory at the beginning, we use actual values from the runtime execution information.
+For other data in the register or memory at the beginning, we use concrete values from the runtime execution information.
 During the symbolic execution for each instruction, the tool updates every variable in the memory and registers with a math formula.

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 While the implementation itself has a lot of benefits (better performance, accurate memory model), we need to implement the symbolic execution rules for each x86 instruction.
-However, due to the complexity of x86, mistakes inevitable. Therefore, we verify the correctness of the SE engine during the execution.
+However, due to the complexity of x86, mistakes are inevitable. Therefore, we verify the correctness of the SE engine during the execution.
 The tool will collect the runtime execution information (register values, memory values) and compare them with the formula generated from the symbolic execution.
@@
 The conditional control-flow transfer instructions, such as conditional jumps, depending on CPU states, may or may not transfer control flows.
-For conditional jumps, the CPU will test if certain condition flag
-(e.g., CF = 0, ZF =1) is met and jump to certain branches, respectively.
-The symbolic engine will compute the flag and represent the flag in a symbol
+For conditional jumps, the CPU will test if certain condition flags
+(e.g., CF = 0, ZF =1) are met and jump to certain branches, respectively.
+The symbolic engine computes the flag and represents the flag in a symbol
 formula. Because we are running on a symbolic execution on an execution trace, we know which branch is executed.
@@
 
-The formula, together with the memory address ($\mathtt{0x0000e789}$) is stored as a \textit{formula tuple (address, formula)}. Each formula tuple represents one potential leakage site.
+The formula, together with the memory address ($\mathtt{0x0000e789}$), is stored as a \textit{formula tuple (address, formula)}. Each formula tuple represents one potential leakage site.
 

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 formulas. As discussed before, every symbol in the formula is the input key. If the formula does not contain any symbols, the memory access is independent
-from the input sensitive information and will not leak any sensitive information according to our threat model. Otherwise, we will generate the constraint for
+from the input sensitive information and does not leak any sensitive information according to our threat model. Otherwise, we generate the constraint for
 the memory addressing.
@@
 \noindent where $L$ represents the minimum memory address granularity that an attacker can observe.
-For example, Flush and Reload can distinguish between different cache lines, which means the value of L is 6 for 64 byte cache line.
+For example, Flush and Reload attacks target on one cache line, which means the value of L is 6 for 64 byte cache line.
 

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 buffer.
-The step can be seen as the multiple-tag taint analysis. With the help of the information from symbolic execution, we can implement a relatively simple but relatively precise information flow track.
+The step can be seen as the multiple-tag taint analysis. With the help of the information from symbolic execution, we can implement a simple but relatively precise information flow track.
 At the beginning of the analysis, \detect{} keep track of each byte in
 the original buffer.
-When \detect{} symbolically executes each instruction in the trace, it will check every value read from registers or memory.
+When \detect{} symbolically executes each instruction in the trace, it will check every value read from registers or memories.
 If the value is concrete, it means the instruction has nothing to do with the original buffer.

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 We also evaluate Monocypher, a new cryptographic library that resists to most side-channel attacks.
-According to the developers, Monocypher is designed to have no secret dependent indices and secret dependent branches.
+According to the manual of Monocypher, Monocypher is designed to have no secret dependent indices and secret dependent branches.
 Therefore, Monocypher should be secure under our threat model.
@@
 
-We refer to the examples or test cases of these libraries and write simple
+We refer to the test cases of these libraries and write simple
 programs that use the crypto libraries. For symmetric encryption, the length

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 Our findings is similar to the previous work.
-We also notice that later version of OpenSSL (after 1.0.1) uses a modified version with smaller S-table.
+We also notice that recent versions of OpenSSL (after 1.0.1) use a modified implementation with smaller S-tables.
 However, \detect{} also finds leakage sites in the version.
-Recent work also finds the sites through theoretical analysis.
 
 \subsubsection{RSA}
-We also evaluate our tool on the RSA implementations. With the optimizations
-introduced in the previous section, we do not apply any domain knowledge to
+We also evaluate our tool on RSA implementations. With the optimizations
+introduced in this chapter, we do not apply any domain knowledge to
 simplify the analysis. Therefore, our tools can identify all the leakage sites

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@
 function \textsf{BN\_rshift1}. Each time, function \textsf{BN\_rshift1}
-shifts \textbf{X} right by one and places the result in \textbf{X}. Therefore,
-an attacker can infer multiple bits of \textbf{X} by observing the branch at line 3.
+shifts \textsf{X} right by one and places the result in \textsf{X}. Therefore,
+an attacker can infer multiple bits of \textsf{X} by observing the branch at line 3.
 

### 2021-06-19 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 RSA implementations usually adopt the Chinese Remainder Theorem (CRT) optimization, which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}.
-Second, fixing vulnerabilities can introduce new
+Second, fixing old vulnerabilities can introduce new
 weaknesses.
@@
 
-Existing works on information leakage quantification typically use Shannon
+Existing work on information leakage quantification typically uses Shannon
 entropy~\cite{clark2007static,Wichelmann:2018:MFF:3274694.3274741},
@@
     \centering
-    %\vspace*{-9pt}
-    %\hspace*{-15pt}
     \subfloat[OpenSSL 0.9.7]{

### 2021-06-19 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 and checks if the input is the correct password. If an attacker uses a side-channel attack to determine that the code executes branch
-$\{{1\}}$, they can infer the password equals to
+$\{{1\}}$, they can infer that the password equals to
 ``password'', in which case the attacker retrieves the full password.

### 2021-06-19 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 the program multiple times with many different or random sensitive inputs. As
-shown in Figure~\ref{fig:gap}(a), previous models, both Shannon entropy and max
+shown in Figure~\ref{fig:gap}(a), previous methods, both Shannon entropy and max
 entropy, give an ``average'' estimate of the information leakage. However, it is
@@
 $K$, $M$, and $O$:
-%\vspace*{-0pt}
+
 \begin{displaymath}
@@
 
-In information theory, the mutual information (I) is a measure of the mutual
-dependence between two variables. Here we use I to describe the
+In information theory, the mutual information ($I$) is a measure of the mutual
+dependence between two variables. Here we use $I$ to describe the
 dependence between original sensitive keys ($K$) and attackers' observations ($O$),
@@
 \begin{equation} \label{eq:1}
-    I(K;O) = \sum_{k {\in} K}{\sum_{o {\in} O}{p(k, o)\log_2\frac{p(k, o)}{p(k)p(o)}}}
+    I(K;O) = \sum_{k {\in} K}{\sum_{o {\in} O}{p(k, o)\log_2\frac{p(k, o)}{p(k)p(o)}}},
 \end{equation}
@@
 \begin{equation} \label{eq:2}
-    I(K;O) = H(K) - H(K|O)
+    I(K;O) = H(K) - H(K|O),
 \end{equation}
@@
 that some branches (e.g., A) or traces leak much more information than some others.
-These kinds of branches can be vulnerable when an attacker's data is incorporate.
+These kinds of branches can be vulnerable when an attacker's data is incorporated.
 For example, the code will skip some of the calculation if the value is 0 in big

### 2021-06-19 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 
-In contrast, an \emph{average} estimate based on random secret input information is around 1 bit, as shown in the previous section and Table~\ref{shtable}, is not very useful in practice as an attacker is able to get much more leaked
-information in some attack scenarios.
+In contrast, an \emph{average} estimate based on random secret input information is around $1$ bit, as shown in the previous section and Table~\ref{shtable}, is not very useful in practice as an attacker is able to get much more leaked
+information in some attack scenarios. As the size of input-sensitive information is
+usually public, the problem of quantifying the leaked information is equivalent to the problem of estimating the size of input key $|K^o|$ under
+the condition $o \in O$.
 
@@
 \label{MCreasons}
-In the previous section, we propose an information leakage definition for realistic attack scenarios to model two types of address-based side-channel leakages and showed how to quantify them by calculating the number of input keys ($K^o$) that satisfy the formulas.
+In the previous section, we propose an information leakage definition for realistic attack scenarios to model two types of address-based side-channel leakages and show how to quantify them by calculating the number of input keys ($K^o$) that satisfy the formulas.
 Intuitively, we can use symbolic execution to capture math formulas and model counting to obtain the number of satisfying input keys ($K^o$).

### 2021-06-19 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 \end{theorem}
-With Theorem~\ref{IndependentConstraint}, we change the problem of counting the number of solutions to a complicated constraint in a high-dimension
+With Theorem~\ref{IndependentConstraint}, we transfer the problem of counting the number of solutions to a complicated constraint in a high-dimension
 space into counting solutions to several small constraints. We compute the maximum independent partition by iterating each $\addr{i}$ and applying the function $\pi$ over the constraint $\addr{i}$.

### 2021-06-19 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
     Given two constraints $c_m$ and $c_n$, we call them independent iff
-    $$\pi(c_m) \cap \pi(c_n) = \emptyset$$
+    $$\pi(c_m) \cap \pi(c_n) = \emptyset.$$
 \end{mydef}
@@
     \begin{enumerate}
-        \item $g_{1} \land g_{2} \land \ldots \land g_{m} = c_t(\addr{1},\addr{2},\ldots,\addr{n})$
+        \item $g_{1} \land g_{2} \land \ldots \land g_{m} = c_t(\addr{1},\addr{2},\ldots,\addr{n})$,
         \item $\forall i, j \in \{1, \ldots, m\} \quad \textrm{and} \quad
-                  i \neq j,\quad\pi(g_{i}) \cap \pi(g_{j}) = \emptyset $
+                  i \neq j,\quad\pi(g_{i}) \cap \pi(g_{j}) = \emptyset $,
         \item For any other partitions  $h_{1}, h_{2}, \ldots, h_{m'}$ satisfy 1) and
-              2), $m \geq m'$
+              2), $m \geq m'$.
     \end{enumerate}
@@
     equation with regard to the size of $K_c$
-    $$|K_{c_t(\addr{1},\addr{2},\ldots,\addr{n})}| = |K_{g_{1}}| \cdot |K_{g_{2}}| \cdot \ldots \cdot|K_{g_{n}}|$$
+    $$|K_{c_t(\addr{1},\addr{2},\ldots,\addr{n})}| = |K_{g_{1}}| \cdot |K_{g_{2}}| \cdot \ldots \cdot|K_{g_{n}}|.$$
 \end{theorem}
@@
 we only generate random input numbers for the other input variables in
-constraint $g_{i}$. With this simple yet effective trick, we reduce the number of input while still ensuring accuracy. The details of the algorithm is shown in Algorithm~\ref{chapter4:alg2}.
+constraint $g_{i}$. With this simple yet effective trick, we reduce the number of inputs while still ensuring accuracy. The details of the algorithm is shown in Algorithm~\ref{chapter4:alg2}.
 

### 2021-06-19 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 secrets and leakage sites. The engine only symbolically executes
-instruction that might be affected by the input sensitive data.
+instructions that might be affected by the input sensitive data.
 \tool{} works on one path at a time.
@@
 \subsection{Leakage Estimation} 
-We change the information leakage quantification problem into the counting problem. We propose a
+We change the information leakage quantification problem into a counting problem. We propose a
 Monte Carlo method to estimate the number of satisfying solutions. With the help of the Central Limit Theorem (CLT), we also give an error

### 2021-06-19 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 Our current implementation supports most Intel 32-bit instructions that are essential to find address-based side-channel vulnerabilities, including bitwise operations, control transfer, data movement, and logic instructions.
-The tool uses the real values to update the registers and memory for instructions that the implementation does not support.
+The tool uses concrete values to update the registers and memory for instructions that the implementation does not support.
 Therefore, the tool may miss some leakages but will not raise false positives.
@@
 In general, it is hard to implement a secure cryptography library from scratch. So most
-software only use a few number of different cryptography libraries. Second, we choose some
+software only use a few number of well-known cryptography libraries. Second, we choose some
 libraries which are well studied in the previous work. We can refer to these conclusions to

### 2021-06-19 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 verify our results. Based on the two requirements, we evaluate \tool{} on the following libraries:
-OpenSSL, Libgcrypt, mbedTLS, Monocypher. OpenSSL, Libgcrypt, and mebdTLS are the most widely used
+OpenSSL, Libgcrypt, mbedTLS, and Monocypher. OpenSSL, Libgcrypt, and mebdTLS are the most widely used
 cryptography libraries. OpenSSL and mbedTLS have been widely studied in the previous research.
@@
 However, \tool{} finds some vulnerabilities with severe
-leakages. Prior research has confirmed that some of these
+leakages. Prior research~\cite{Bonneau11894063_16,Gullasch:2011:CGB:2006077.2006784} has confirmed that some of these
 vulnerabilities can be exploited in real attacks.
@@
 Symmetric encryption implementations in OpenSSL and mbedTLS have significant leakage due to their lookup table implementations. 
-\tool{} confirms that these leakage comes from table lookups.
+\tool{} confirms that these leakage come from table lookups.
 The new implementation of OpenSSL has adopted several methods (e.g., one single S-box instead of four lookup tables, smaller lookup tables) to mitigate the problem.

### 2021-06-19 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 much information is leaked from each vulnerability. During the evaluation,
-for each leakage site, \tool{} will stop once 1) it has 95\% confidence
-that the error of the estimated leaked information is less than 1 bit,
+for each leakage site, \tool{} will stop once 1) it has $95\%$ confidence
+that the error of the estimated leaked information is less than $1.0$ bit,
 which gives the leakage quantification a \emph{precision guarantee}, 
-or 2) it cannot reach the termination condition after 10 minutes.  In
+or 2) it cannot reach the termination condition after $10$ minutes.  In
 the latter case, it means \tool{} cannot estimate the amount of leakage with a
-probabilistic guarantee. \tool{} times out on around 10\% reported side-channel leakage sites. We manually check these leakage sites and find most of them are quite severe.
+probabilistic guarantee. \tool{} times out on around $10\%$ reported side-channel leakage sites. We manually check these leakage sites and find most of them are quite severe.
 We will present the details in the subsequent sections.
@@
 sites in total. Leakage 1, 2, 3 are the same and leakage 4, 5, 6, 7 are the
-same. They both use a pre-computed lookup table to speed up computation.
+same. They both use a pre-computed lookup table to speed up the computation.
 However, \tool{} reports leakage 1, 2, 3 typically leak more information (7.6 - 8.1 bits)

### 2021-06-19 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 most leakages effectively because the four newer versions have fewer
-leakages than version 0.9.7, which introduced this change.
+leakages than version 0.9.7.
 OpenSSL version 1.0.2f, 1.0.2k, and 1.1.0f almost have the
@@
 developers are more reluctant to fix them or fixing them unintentionally.
-For example, OpenSSL 0.9.7 adds a fixed windows version of function \textsf{BN\_mod\_exp\_mont\_consttime} to replace original function \textsf{BN\_mod\_exp\_mont}.
+For example, OpenSSL 0.9.7 adds a fixed windows version of function \textsf{BN\_mod\_exp\_mont\_consttime} to replace the original function \textsf{BN\_mod\_exp\_mont}.
 \tool{} detects a minor vulnerability in the original function that can leak the last bit of the big number \texttt{m}.

### 2021-06-19 Chapter-4/Chapter-4.tex
Updates from Overleaf

@@
 First, all leakage sites that leak more than 5 bits information are fixed by developers.
-Second, for all leakages that are not patched by developers, the quantification result shows that they leak less than 1.0 bits information.
+Second, for all leakages that are not patched by developers, the quantification result shows that they leak less than $1.0$ bits information.
 The evaluation results show that \tool{} can help developers find severe leakages automatically.
@@
 Figure~\ref{fig:chapter4:pwcheck2} fixes the vulnerability because the function will continue comparing the second byte even if the first byte is different.
-\tool{} identifies the leakage site in Figure~\ref{fig:chapter4:pwcheck1} successfully, and estimates the amount of leakage is $16$ bits.
+\tool{} identifies the leakage site in Figure~\ref{fig:chapter4:pwcheck1} successfully, and estimates the amount of leakage is $16.0$ bits.

### 2021-06-19 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 In this chapter, we treat the side-channel attack as a communication system between two parties.
-Here we first give an overview of the background knowledge of information theory and present the threat model.
+Here we first give an overview of the background knowledge of information theory.
 
@@
 We consider an access-based attack~\cite{ge2018survey}, where an adversary can probe one time for each run only after the termination of a deterministic program.
-The attacker may not know the memory access the victim program accesses directly.
+The attacker may not know the memory accesses of the victim program directly.
 Still, he can infer whether some memory addresses are accessed or not at various granularities after \textit{each run} of the victim program.
@@
 It is a typical scenario for most side-channel attacks.
-We also assume the attacker can have access to the source code of the victim program ($\beta$).
+We also assume that the attacker can have access to the source code of the victim program ($\beta$).
 It is a valid assumption since most side-channel attacks target open-source software.
@@
   \caption{The relationship between the side-channel attack and the channel capacity.
-For a deterministic program, the side-channel attack can be seen as the communication between the observation ($o \in O$) and the secret ($k \in K$) via a discrete memoryless channel.}
+For a deterministic program, the side-channel attack can be seen as a communication channel between the observation ($o \in O$) and the secret ($k \in K$).}
   \label{fig:side_channel}

### 2021-06-19 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 Still, we test the program with input from $0, 1, \dots, 7$.
-However, we find the attacker cannot uniquely determine the secret based on the observation of table $T$, for example.
+However, we find the attacker cannot uniquely determine the secret based on the observation of array $T$, for example.
 Both $0$ and $4$ read the first item of the table.
@@
 These vulnerabilities may spread throughout the whole program.
-An adversary may exploit more than one side-channel vulnerability to gain more information~\cite{7163052, 191010}.
+An adversary can exploit more than one side-channel vulnerability to gain more information~\cite{7163052, 191010}.
 In order to quantify the
@@
 Considering the examples in Figure~\ref{chapter5:fig:multiple}, Figure~\ref{chapter5:fig:multiple}(a) show a code snippet with two leakage sites at line 6 and line 8, respectively.
-For example, if an adversary observes that function \textsf{a} executes, then the attacker can infer that the first byte in buffer \textsf{secret} is larger than the second byte.
+For example, if an adversary observes that function \textsf{a} executes, then the attacker can infer that the first byte in buffer \textsf{secret} is larger than the second byte in buffer \textsf{secret}.
 Similarly, if an adversary observes that function \textsf{b} executes, then the attacker can infer that the sum of the first two bytes in buffer \textsf{secret} is smaller than $256$.
 The interesting part here is that if the attacker observes that function \textsf{a} executes, then he still has zero knowledge about the function \textsf{b}.
-The two leakage sites in Figure~\ref{chapter5:fig:multiple}(b) are different.
+The two leakage sites in Figure~\ref{chapter5:fig:multiple} (b) are different.
 If an attacker observes function \textsf{c} executes, then it is likely the attacker can observe that function \textsf{d} also executes.

### 2021-06-19 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 Therefore, the times of the same observation for each event should satisfy the binomial distribution.
-After that, we can use the chi-squared test to test whether the two leakage sites are independent.
+After that, we can use the chi-squared test to examine whether the two leakage sites are independent.
 
@@
 We have the probability $p\approx0.00$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (b).
-Therefore, we infer that the two leakages in Figure~\ref{chapter5:fig:multiple} (a) are independent.
+Therefore, we infer that the two leakages in Figure~\ref{chapter5:fig:multiple} (a) are likely to independent.
 And the two leakages Figure~\ref{chapter5:fig:multiple} (b) are dependent.
@@
 We use the above method to test if any two leakage sites are independent for each leakage point.
-We combine them into a leakage and calculate the total amount of the leakage.
+If any two leakages are independent, we combine them into one leakage and calculate the total amount of the leaked information.
 \section{Design}

### 2021-06-19 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 For the first step, we build the target program from the source code.
-After that, we give them random inputs to the victim program and run the target program and record the each of the addresses in the binary file is hit or not, and store the information in a bitmap.
+After that, we give them random inputs to the victim program and run the target program and record each of the addresses in the binary file is hit or not, and store the information in a bitmap.
 Next, we analyze the side-channel leakage from the address access bitmap.
@@
 \subsection{Step 1: Fuzzing}
-After we build the software into the binary executable, we give the
+After we build the software into a binary executable, we give the
 binary executable random inputs. For cryptography libraries, the input

### 2021-06-19 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 not. Inspired by AFL and Valgrind, we use a bitmap to represent
-whether a particular memory is accessed or not. For example, the
+whether a particular memory address is accessed or not. For example, the
 bitmap ${0101}$ of address $l_1, l_2, l_3, l_4$ means that $l_2, l_4$
@@
 execution traces even for the same input because the image is
-loaded at a different address each time. Second, it helps us find the
+loaded at a different address each time. Second, it helps us locate the
 leakage site in the source code.
@@
 For instructions with memory access, we identify all the operands of each instruction.
-Same as the code addresses, the instruction can read or write multiple bytes one time.
-Instructions like \textsf{push} and \textsf{pop} have implicit memory access.
+Same as the code address, the instruction can read or write multiple bytes one time.
+Instructions like \textsf{push} and \textsf{pop} have implicit memory accesses.
 We all update the bitmap of the address correspondingly.

### 2021-06-19 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 Instructions like \textsf{push} and \textsf{pop} have implicit memory accesses.
-We all update the bitmap of the address correspondingly.
+We all update the bitmap correspondingly.
 \end{itemize}
@@
 The memory management unit (MMU) transfers the virtual address into the physical address by mapping the Virtual Page Number (VPN) into the Physical Page Number (PPN) while keeping the offset of the address.
-So two addresses with the Same VPN but different offset are not distinguishable by an attacker who only has the page-level observation.
+So two addresses with the same VPN but different offsets are not distinguishable by an attacker who only has the page-level observation.
 

### 2021-06-19 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 The memory management unit (MMU) transfers the virtual address into the physical address by mapping the Virtual Page Number (VPN) into the Physical Page Number (PPN) while keeping the offset of the address.
-So two addresses with the same VPN but different offsets are not distinguishable by an attacker who only has the page-level observation.
+So two addresses with the same VPN but different offsets are not distinguishable by an attacker who can perform the page-level observation.
 
 Suppose a program reads one byte at memory address
-$\mathtt{0x7ffff7ffd001}$ when the secret is $k_1$ and reads a
+$\mathtt{0x7ffff7ffd001}$ when the secret is $k_1$, and reads a
 different byte at memory $\mathtt{0x7ffff7ffda01}$ when the secret is
@@
 \begin{myexample}
-Shown in Figure~\ref{fig:design:example2}, we have the following observation from $k_1$ to $k_8$, then we count the distribution of  the observation.
+Shown in Figure~\ref{fig:design:example2}, we have the following observation from $k_1$ to $k_8$.
+We count the distribution of  the observation.
 The process is like traversing a binary tree and increase the counter of the child node.

### 2021-06-19 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 We have implemented a prototype of \ctool{}.
-It takes an input of ELF binary as well as the source code of the corresponding program.
+It takes an ELF binary as well as the source code of the corresponding program.
 The front-end of \ctool{} is implemented in Python.
@@
 For cryptography programs, we run the target program with $4096$ different inputs.
-During the fuzzing process, if the program does not have a new memory access bitmap after several rounds, we call the fuzzing step is fixed.
+During the fuzzing process, if the program does not have a new memory access bitmap after several rounds, we call the fuzzing step reaches a fixed point.
 From the side-channel detection aspect, it is not necessary to continue running the experiments since more rounds do not reveal new leakages.
@@
 AES encryption can be divided into three steps.
-In the first step, the round keys are derived from the encryption keys (AES key schedule), and a state array is initialized with the plain-text and the initial round step.
+In the first step, the round keys are derived from the encryption keys (AES key schedule), and a state array is initialized with the plain-text.
 In the second step, the AES performs eleven rounds of state manipulation.
@@
 To evaluate the effectiveness of the quantification result, we compare the two RSA implementations between OpenSSL 1.1.0 and OpenSSL 1.1.1.
-We are interested if these leaked functions in OpenSSL 1.1.0 are fixed in OpenSSL 1.1.1.
-Note that \ctool{} can analyze the side-channel leakages at both the byte granularity and the cache line granularity. We show the result analyzed with cache line granularity.
+We are interested if these leaked functions from OpenSSL 1.1.0 are fixed in OpenSSL 1.1.1.
+Note that \ctool{} can analyze the side-channel leakages at both the byte granularity and the cache line granularity. We show the result analyzed with the cache line granularity.
 

### 2021-06-19 Chapter-5/Chapter-5.tex
Updates from Overleaf

@@
 Table~\ref{chapter5:tab:RSAOpenSSL1.1.0} shows the leaked function and the amount of leakage reported by \ctool{} and \tool{}~\cite{bao2021abacus}.
-According to \tool{}\cite{bao2021abacus}, the mark ``$*$'' means timeout, which indicates more severe leakages.
+According to \tool{}, the mark ``$*$'' means timeout, which indicates more severe leakages.
 $0.0$ means very small amount of leakage, but not exactly zero.
@@
 Previous work~\cite{bao2021abacus} reports some leakage sites leak little information, but \ctool{} reports the vulnerabilities are severe.
-Previous work \tool{}~\cite{bao2021abacus} quantifies the amount of leaked information for one execution.
+\tool{} quantifies the amount of leaked information for one execution.
 So it is possible that some leakage sites leak little information for one input but leak more information for a different input.
@@
 We evaluate \ctool{} on TinyDNN, a deep learning framework in C++. We
-construct a LeNet-5 model~\cite{lecun1998gradient} and trained it with
+construct a LeNet-5 model~\cite{lecun1998gradient} and train it with
 the MINIST dataset. LeNet-5 network has six layers, including three

### 2021-06-19 Chapter-6/Chapter-6.tex
Updates from Overleaf

--- 2021-06-18 Chapter-6/Chapter-6.tex
@@
 \section{Fast and Precise Side-channel Vulnerability Detection}
-\subsection*{Code Coverage} \detect{} analyzes one native x86 execution trace each time.
+\subsection*{Code Coverage} \detect{} analyzes one x86 execution trace each time.
 The design is very precise in terms of true leakages compared to many static source code methods~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, but shares common limitations of dynamic approaches.
@@
 \section{Precise Analysis on Multiple-trace Attacks}
-In this work, we present an approach that tries to give a 
+In this work, we present an approach that tries to give an 
 estimation of the amount of leaked information by access-based

### 2021-06-19 Chapter-7/Chapter-7.tex
Updates from Overleaf

@@
 signals (e.g., sound, CPU usages, EM signals). The key is to model the noises
-properly. In my dissertation, we assume that an attacker can have a noise-free
+properly. In this dissertation, we assume that an attacker can have a noise-free
 observation. While a noise-free observation is possible for some address-based
-side-channel attacks, the assumption is too ideal for many real side-channel
-attacks. The good news is that there are some mature methods in information theory to model noises (e.g., Gaussian noise). The noisy-channel coding theorem provides a
-computable method to estimate the information that can be reliably transferred over a channel between secret data and attackers' observations.
+side-channel attacks, the assumption is still too ideal for many real side-channel
+attacks. The good news is that there are some mature methods in information theory to model some types of noises (e.g., Gaussian noise). The noisy-channel coding theorem provides a
+computable method to estimate the information that can be reliably transferred over a channel between the secret data and attackers' observations.

### 2021-06-19 Chapter-7/Chapter-7.tex
Updates from Overleaf

@@
 The LVI harden binaries generated from GNU toolchains takes 6-10x longer to run.
-For example, GNU toolchains insert LFENCE before any possible vulnerable instructions, including all load instructions, indirect branches, and return instructions.
+For example, GNU toolchains insert \textsf{LFENCE} before any possible vulnerable instructions, including all load instructions, indirect branches, and return instructions.
 We suggest only changing points that are likely to leak sensitive information.

### 2021-06-19 Chapter-6/Chapter-6.tex
Updates from Overleaf

@@
 simplifies many methods by assuming the data will not change over the time. 
-In my dissertation, we used MINIST, a well-known handwriting digit dataset. 
+In this dissertation, we used MINIST, a well-known handwriting digit dataset. 
 We believe the i.i.d. assumption holds under the circumstance, although the
@@
 \item The quantification result only applies to specific threat models.
-For example,\tool{} quantifies the number of leaked bits during one real execution.
+For example, \tool{} quantifies the number of leaked bits during one real execution.
 So it is possible that one leakage site leaks little information in one execution but leaks much more information in another execution.

### 2021-06-19 Chapter-7/Chapter-7.tex
Updates from Overleaf

@@
 side-channel attacks, the assumption is still too ideal for many real side-channel
-attacks. The good news is that there are some mature methods in information theory to model some types of noises (e.g., Gaussian noise). The noisy-channel coding theorem provides a
+attacks.
+The good news is that there are some mature methods in information theory to model some types of noises (e.g., Gaussian noise).
+The noisy-channel coding theorem~\cite{shannon1948mathematical} provides a
 computable method to estimate the information that can be reliably transferred over a channel between the secret data and attackers' observations.

### 2021-06-19 Chapter-1/Chapter-1.tex
Updates from Overleaf

@@
 
-Secret-dependent data accesses happen when the value of secret data affect which memory location the code reads or writes.
+Secret-dependent data accesses happen when the value of secret data affects which memory location the code reads or writes.
 Figure~\ref{fig:secret:da} shows an example.
@@
 As shown in Figure~\ref{fig:secret:cf} and Figure~\ref{fig:secret:da}, if a program shows different patterns in control transfers or data accesses when the program processes different sensitive inputs, the program could have side-channel vulnerabilities.
-Various techniques can be used to exploit the above leakage site at different granularities.
+Various techniques can be used to exploit side-channel leakage sites at different granularities.
 For example, cache channels can observe cache accesses at the level of cache sets~\cite{liu2015last}, cache lines~\cite{184415} or other granularities~\cite{yarom2017cachebleed}.

### 2021-06-22 Chapter-7/Chapter-7.tex
Updates from Overleaf

@@
 
-In Chapter~\ref{chapter5}, we propose a fuzzing method to automatically detect and quantify the address-based side-channel leakages automatically.
-The proposed method can produce an estimation of the side-channel leakage of the deterministic program.
+In Chapter~\ref{chapter5}, we propose a fuzzing method to detect and quantify the address-based side-channel leakages automatically.
+The proposed method can produce an estimation of the severity level of each side-channel leakage of a deterministic program.
 As a result, any severe leakage reported by \ctool{} is a true severe leakage.
 We also study the total effect of two leakages.
-Using statistical hypothesis testing, we are able to determine if the two leakages are independent.
+Using statistical hypothesis testing, we are able to determine if any two different leakages are independent.
 If so, we can calculate the sum of the amount of leakage by adding them.
-Our evaluation result on both several libraries and benchmarks show that \ctool{} is effective and accurate in detecting the side-channel leakage.
+Our evaluation result on several libraries and benchmarks show that \ctool{} is effective and accurate in detecting the side-channel leakage.
 
@@
 For each proposed method, we implement and evaluate it on real-world software.
-The evaluation results show the effeteness and generality of our proposed method.
+The evaluation results show the effectiveness and generality of our proposed method.
 We also release the prototypes to facilitate future research in the area.

### 2021-06-22 Chapter-7/Chapter-7.tex
Updates from Overleaf

@@
 Using statistical testing, \detect{} can identify the true leakages from these constraints.
-\detect{} analyzes the side-channel leakages directly from X86 execution traces.
-Existing binary analysis tools usually transfer x86 instructions to intermediate languages (IR) simplify the implementation.
+\detect{} analyzes the side-channel leakages directly from x86 execution traces.
+Existing binary analysis tools usually transfer x86 instructions to intermediate languages (IR) to simplify the implementation.
 However, such designs have expensive overheads and imprecise analysis results.

### 2021-06-23 Chapter-1/Chapter-1.tex
last revision from D.

@@
 The complexity in today's software systems makes it hard for developers to understand the codebase and find defects manually.
-So an automated bug detection tool is often needed.
-In this dissertation, we present techniques to analyze side-channel vulnerabilities in real-world applications.
-The side-channel vulnerability is a type of information leakage bugs in software systems.
+So an automated %bug detection
+tool is often needed. In this dissertation, we present techniques to analyze side-channel vulnerabilities in real-world applications. 
+%The side-channel vulnerability is a type of information leakage bugs in software systems.
 Unlike many ordinary bugs, attackers exploit side-channel vulnerabilities from the implementation of the software rather than weaknesses in the implementation itself.

### 2021-06-23 Chapter-6/Chapter-6.tex
last revision from D.

@@
 \chapter{Discussion and Limitations}\label{chapter6}
-\section{Fast and Precise Side-channel Vulnerability Detection}
+%\section{Fast and Precise Side-channel Vulnerability Detection}
+\section{Side-channel Vulnerability Detection}
 \subsection*{Code Coverage} \detect{} analyzes one x86 execution trace each time.
@@
 
-\section{Precise Analysis on Single-trace Attacks}
+%\section{Precise Analysis on Single-trace Attacks}
+\section{Analysis on Single-trace Attacks}
 While recent work found many side-channel vulnerabilities,
@@
 which means the number of $K^o$ is very small. According to Definition~\ref{chapter4:def} in Chapter~\ref{chapter4}, it means the leakage is very severe.
-\section{Precise Analysis on Multiple-trace Attacks}
+
+%\section{Precise Analysis on Multiple-trace Attacks}
+\section{Analysis on Multiple-trace Attacks}
 In this work, we present an approach that tries to give an 

### 2021-06-23 Chapter-3/Chapter-3.tex
last revision from D.
last CRC from D.

@@
   \centering
-  \includegraphics[width=.65\columnwidth]{./figures/chapter3/architecture.pdf}
-  \caption{Computer memory hierarchy. The hierarchy is designed to minimise the access time with a relatively low cost. It is the root cause of many side-channel attacks.}\label{fig:memory_hierarchy}
+  \includegraphics[width=.75\columnwidth]{./figures/chapter3/architecture.pdf}
+  \caption{Computer memory hierarchy.
+The memory hierarchy is designed to minimise the access time with a relatively low cost.
+It is the root cause of many side-channel attacks.}\label{fig:memory_hierarchy}
 \end{figure}
@@
     RSA                & Libgcrypt 1.7.3          & 14                & 14                & 0              & 10,513,606  & 14      & 2,701 \\
-    RSA                & Libgcrypt 1.8.5          & 8                 & 8                 & 0              & 27,407,986  & 113     & 4,701 \\
+    RSA                & Libgcrypt 1.8.5          & 8                 & 8                 & 0              & 27,407,986  & 113     & 4,701 \\\hline
 

### 2021-06-23 Chapter-6/Chapter-6.tex
last CRC from D.

@@
 \chapter{Discussion and Limitations}\label{chapter6}
+
+In this chapter, we discuss some of the design choices and limitations.
+
 %\section{Fast and Precise Side-channel Vulnerability Detection}
@@
 The dissertation research has a few limitations. 
-
-\begin{enumerate}
-\item The methods in this dissertation cannot find all kinds of side-channel leakages.
+First, the methods in this dissertation cannot find all kinds of side-channel leakages.
 No tool can find all forms of leakages.
@@
 However, to the best of my knowledge, no tools as yet can prove the absence of side-channel leakages in production software.
-\item The quantification result only applies to specific threat models.
+
+Second, the quantification result only applies to specific threat models.
 For example, \tool{} quantifies the number of leaked bits during one real execution.
 So it is possible that one leakage site leaks little information in one execution but leaks much more information in another execution.
-\item \tool{} and \ctool{} can only handle address-based side-channel attacks.
+
+Third, \tool{} and \ctool{} can only handle address-based side-channel attacks.
 Many side-channel attacks infer secret data based on other side-channel signals (e.g., timing, EM signals).
@@
 Under the circumstance, our methods can still detect these leakage sites.
-\item \ctool{} is a dynamic approach.
+
+Also, \ctool{} is a dynamic approach.
 So it bears the same limitations of dynamic approaches as well.

### 2021-06-24 Chapter-2/Chapter-2.tex
Final Version

@@
 memory''. If the time is relatively fast, it indicates that the data has been accessed by the victim program and the cache has loaded the data. 
-On X86-64 machines, the two steps can be combined by measuring the time differences of the \textsf{clflush} instruction.
+On x86-64 machines, the two steps can be combined by measuring the time differences of the \textsf{clflush} instruction.
 
@@
 On the other hand, the approximate model counter is much faster compared with the exact model counter.
-The related work focuses on approximate model counting since it is close to our approach.
+We focus on approximate model counting since it is close to our approach.
 Wei and Selman~\cite{wei2005new} introduce
@@
 collect execution traces and convert the trace into BAP IRs. Angr~\cite{shoshitaishvili2016state}, the most popular
-binary analysis platform recently, also supports trace-based analysis. It converts X86 instructions into VEX IRs and interprets each IR in Python.
+binary analysis platform recently, also supports trace-based analysis. It converts x86 instructions into VEX IRs and interprets each IR in Python.
 

### 2021-06-24 Chapter-5/Chapter-5.tex
Final Version

@@
 \subsection{Overview}
-Figure~\ref{chapter5:fig:workflow} shows an overview of our side-channel leakages quantification tool.
-Given the source code of a victim program, \ctool{} can find the address-based side-channel leakages by fuzzing the victim program.
-To assist the illustration, we divide the workflow of ~\ctool{} into three steps.
+Figure~\ref{chapter5:fig:workflow} shows an overview of our side-channel leakage quantification tool.
+Given the source code of a victim program, \ctool{} can find address-based side-channel leakages by fuzzing the victim program.
+To assist the illustration, we divide the workflow of \ctool{} into three steps.
 For the first step, we build the target program from the source code.
-After that, we give them random inputs to the victim program and run the target program and record each of the addresses in the binary file is hit or not, and store the information in a bitmap.
-Next, we analyze the side-channel leakage from the address access bitmap.
+After that, we give them random inputs to the victim program, run the target program, record each address in the binary file is hit or not, and store the information in a bitmap.
+Next, we analyze side-channel leakages from the bitmaps.
 We split the address space into several segments to speed up the comparison according to the meta information.
@@
 be images, text, and information in another format. Encryption
-algorithms like AES and DES take an array representing the secrets. We
-generate the random input by flipping each bit of the keys. Some other
+algorithms like AES and DES take an array representing the secrets. Some other
 programs also take a buffer as the input. The buffer may contain 
@@
 that satisfies the input length is a valid input. Under the
-circumstance, we have a dictionary that contains the input. For
+circumstance, we have a dictionary that contains the valid inputs. For
 example, crypto libraries usually take PKCS \#1 as the input of the
@@
 secret. We use the dynamic binary instrumentation (DBI) tool to record
-whether a particular memory access information is accessed or
+whether a particular address is accessed or
 not. Inspired by AFL and Valgrind, we use a bitmap to represent
@@
 The memory address of the code is the value of the program counter $\mathit{rip}$ register.
-However, the length of x86 instructions can be from 1 byte to 15 bytes.
+However, the length of x86 instructions vary from 1 byte to 15 bytes.
 For instructions whose length is longer than one byte, we also update the address after the value $\mathit{rip}$ until the address reaches the instruction's boundary.
 \item Data Access.
-For instructions with memory access, we identify all the operands of each instruction.
+For instructions with memory accesses, we identify all the operands of each instruction.
 Same as the code address, the instruction can read or write multiple bytes one time.
@@
 \subsection{Step 3: Leakage Detection and Quantification}
-In this step, we detect and quantify the side-channel leakage.
-For each $k \in K$, we have a boolean number ($0$ or $1$) to describe whether the address $l$ is accessed or not during the execution when the input is $k$.
+In this step, we detect and quantify side-channel leakages.
+For each $k \in K$, we have a boolean number ($0$ or $1$) to describe whether the address $l$ is accessed or not during the execution.
 For the brevity of description, we use $B^{l}_{k_i}$ to denote the boolean number.
@@
 An attacker who has the coarse-grained observation at address space may not be able to distinguish the address difference.
-For example, modern X64 computer systems use 48-bit virtual memory addresses.
+For example, modern x64 computer systems use 48-bit virtual memory addresses.
 The top 36 bit of the virtual address is called Virtual Page Number (VPN), and the bottom 12 bits of the virtual address is called offset.
@@
 $\mathtt{0x7ffff7ffd001}$ when the secret is $k_1$, and reads a
-different byte at memory $\mathtt{0x7ffff7ffda01}$ when the secret is
+different byte at address $\mathtt{0x7ffff7ffda01}$ when the secret is
 $k_2$, an attacker who has the page-level observation cannot launch
-the attack but an attacker who launches the cache attack can know the
+the attack, but an attacker who launches the cache attack can know the
 input is $k_1$ or $k_2$. We update the new bitmap of the large unit by
@@
 
-\subsubsection{Leakage Detection} 
+%\subsubsection{Leakage Detection} 
 The access of one address is secret-dependent if $ \exists\, k_{i_1}, k_{i_2} \in K, \, B^{l}_{k_{i_1}} \oplus  B^{l}_{k_{i_2}} =1 $.
 In this step, we perform the logical exclusive OR operation on every boolearn value in the same address.
-If the result is $1$, then the address is vulnerable to the side-channel attacks.
+If the result is $1$, then the address is vulnerable to side-channel attacks.
 
